### 2014-11-03 paper/e6ssm-tuning-paper.tex
Added paper to git for editing

\documentclass[preprint,amsmath,amssymb,aps,superscriptaddress,prd,showpacs,floatfix]{revtex4-1}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}
\usepackage{hyperref}

%\nofiles
% For draft, uncomment to avoid huge spaces
\raggedbottom
%
\begin{document}

\title{Fine tuning in the E$_6$SSM}

\author{P. Athron}
 \email{peter.athron@adelaide.edu.au}
 \affiliation{
ARC Centre of Excellence for Particle Physics at the Terascale, School of Chemistry and Physics, The University of Adelaide,
Adelaide, South Australia 5005, Australia}

\author{D. Harries}
 \email{dylan.harries@adelaide.edu.au}
 \affiliation{
ARC Centre of Excellence for Particle Physics at the Terascale, School of Chemistry and Physics, The University of Adelaide,
Adelaide, South Australia 5005, Australia}

\author{A. G. Williams}
 \email{anthony.williams@adelaide.edu.au}
 \affiliation{
ARC Centre of Excellence for Particle Physics at the Terascale, School of Chemistry and Physics, The University of Adelaide,
Adelaide, South Australia 5005, Australia}

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
% Copied SUSY2014 abstract as placeholder
With the discovery of a 125 GeV Standard Model (SM) like Higgs boson
and rising lower bounds on the masses of superpartners, minimal models
of low energy supersymmetry (SUSY) appear to be increasingly fine
tuned. In the Minimal Supersymmetric Standard Model (MSSM) large stop
masses, needed to obtain the observed Higgs mass, give a significant
contribution to fine tuning. $U(1)$ extensions of the MSSM that solve
the $\mu$-problem have new F- and D-term contributions to the Higgs mass,
allowing a 125 GeV Higgs with lighter stops and so alleviating the
associated fine tuning. However, it was recently demonstrated, within
a constrained version of the Exceptional Supersymmetric Standard Model (E$_6$SSM)
defined at the Grand Unification (GUT) scale, that the presence of a massive $Z'$ boson introduces a 
substantial new source of tuning in these theories at tree level. Here we
consider the impact of this tuning when we remove the fine tuning that depends
on assumptions about the SUSY breaking scale, by setting the SUSY
breaking parameters at low energies. We find that the existing
experimental bounds on the $Z'$ mass impose an effective lower bound on
the fine tuning, which does not depend on assumptions about SUSY breaking. 
We compare our results against the tuning in
the phenomenological MSSM (pMSSM), where the SUSY breaking terms are also
defined at low energies.

\end{abstract}

\pacs{12.60.Jv, 11.30.Pb, 12.60.-i, 14.80.Bn}
\keywords{naturalness, fine tuning, supersymmetry}%Use showkeys class option if keyword
                              %display desired
\maketitle

\section{\label{sec:intro}Introduction}
\section{\label{sec:model}The Model}
% Table of U(1)' charges, which may or may not be useful to include.
\begin{table}[h]
\centering
\begin{ruledtabular}
\begin{tabular}{cccccccccccccc}
 & $\hat{Q}$ & $\hat{u}^C$ & $\hat{d}^C$ & $\hat{L}$ & $\hat{e}^C$ & $\hat{N}^C$ & $\hat{S}$ & $\hat{H}_2$ & $\hat{H}_1$ & $\hat{D}$ & $\hat{\overline{D}}$ & $\hat{H}'$ & $\hat{\overline{H'}}$ \\[1mm]
\hline
$\sqrt{\frac{5}{3}}Q_i^Y$ & $\frac{1}{6}$ & $-\frac{2}{3}$ & $\frac{1}{3}$ & $-\frac{1}{2}$ & $1$ & $0$ & $0$ & $\frac{1}{2}$ & $-\frac{1}{2}$ & $-\frac{1}{3}$ & $\frac{1}{3}$ & $-\frac{1}{2}$ & $\frac{1}{2}$ \\[1mm]
%\hline
$2\sqrt{6}Q_i^\psi$ & $1$ & $1$ & $1$ & $1$ & $1$ & $1$ & $4$ & $-2$ & $-2$ & $-2$ & $-2$ & $1$ & $-1$\\[1mm]
%\hline
$2\sqrt{10}Q_i^\chi$ & $-1$ & $-1$ & $3$ & $3$ & $-1$ & $-5$ & $0$ & $2$ & $-2$ & $2$ & $-2$ & $3$ & $-3$\\[1mm]
%\hline
$\sqrt{40}Q_i^N$ & $1$ & $1$ & $2$ & $2$ & $1$ & $0$ & $5$ & $-2$ & $-3$ & $-2$ & $-3$ & $2$ & $-2$ \\[1mm]
\end{tabular}
\end{ruledtabular}
\caption{The $U(1)_Y$, $U(1)_\psi$, $U(1)_\chi$ and $U(1)_N$ charges of the chiral superfields in the $E_6$ model. The specific case of $U(1)_N$, corresponding to the E$_6$SSM, is obtained for $\theta_{E_6}=\arctan\sqrt{15}$.}
\label{tab:E6charges}
\end{table}
\section{\label{sec:ewsb}Electroweak Symmetry Breaking}
% EWSB conditions in E6SSM
The Higgs scalar potential for the E$_6$ model considered is \cite{King:2005jy} 
\begin{equation}\label{eq:E6VeffOneLoop}
V_{E_6}=V_{E_6}^F+V_{E_6}^D+V_{E_6}^{\textrm{soft}}+\Delta V_{E_6}.
\end{equation}
where
\begin{align}
V_{E_6}^F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|(H_1\cdot H_2)|^2,\label{eq:E6VFterms}\\
V_{E_6}^D&=\frac{\bar{g}^2}{8}\left ( |H_2|^2-|H_1|^2\right )^2+\frac{g_2^2}{2}|H_1^\dagger H_2|^2+\frac{g_1'^2}{2}(\tilde{Q}_1|H_1|^2+\tilde{Q}_2|H_2|^2+\tilde{Q}_S|S|^2)^2,\label{eq:E6VDterms}\\
V_{E_6}^{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big [\lambda A_\lambda S(H_1\cdot H_2)+\textrm{h.c.}\Big ].\label{eq:E6Vsoft}
\end{align}
In these expressions $g_2$, $g'=\sqrt{3/5}g_1$, and $g_1'$ are the $SU(2)$, (non-GUT normalized) $U(1)_Y$ and $U(1)'$ gauge couplings, respectively, and $\bar{g}^2=g_2^2+g'^2$. The charges $\tilde{Q}_1$, $\tilde{Q}_2$ and $\tilde{Q}_S$ are effective $U(1)'$ charges for $H_1$, $H_2$ and $S$, respectively. Note that the $SU(2)$ dot product is defined by $A\cdot B\equiv \epsilon_{\alpha\beta}A^\alpha B^\beta=A^2B^1-A^1B^2$. The term $\Delta V_{E_6}$ contains the Coleman-Weinberg contributions to the effective potential. In the case of the $U(1)_\chi$ model, $V_{E_6}^F$ may also contain an elementary $\mu$ term contribution, as occurs in the MSSM.\\ \\
Demanding that the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real VEVs of the form
\begin{equation}\label{eq:E6vevs}
\langle H_1 \rangle = \frac{1}{\sqrt{2}}\begin{pmatrix} v_1 \\ 0\end{pmatrix}, \; \langle H_2 \rangle = \frac{1}{\sqrt{2}}\begin{pmatrix} 0 \\ v_2 \end{pmatrix}, \; \langle S \rangle =\frac{s}{\sqrt{2}}
\end{equation}
at the physical minimum leads to the minimization conditions
\begin{subequations}\label{eq:E6EWSBConditions}
\begin{align}
&f_1=m_{H_d}^2v_1+\frac{\lambda^2}{2}(v_2^2+s^2)v_1-\frac{\lambda A_\lambda}{\sqrt{2}}sv_2-\frac{\bar{g}^2}{8}
(v_2^2-v_1^2)v_1+D_{H_d}v_1+\frac{\partial \Delta V_{E_6}}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\
&f_2=m_{H_u}^2v_2+\frac{\lambda^2}{2}(v_1^2+s^2)v_2-\frac{\lambda A_\lambda}{\sqrt{2}}sv_1+\frac{\bar{g}^2}{8}
(v_2^2-v_1^2)v_2+D_{H_u}v_2+\frac{\partial \Delta V_{E_6}}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\
&f_3=m_S^2s+\frac{\lambda^2}{2}(v_2^2+v_1^2)s-\frac{\lambda A_\lambda}{\sqrt{2}}v_2v_1+D_Ss+\frac{\partial \Delta V_{E_6}}{\partial s}=0.\label{eq:E6EWSBcondition3}
\end{align}
\end{subequations}
The quantities $D_{H_1}$, $D_{H_2}$ and $D_S$ appearing above are $U(1)'$ $D$-term contributions that are absent in the MSSM and NMSSM and are given by
\begin{equation}\label{eq:E6Dterms}
D_\phi\equiv \frac{g_1'^2}{2}\left ( \tilde{Q}_1v_1^2+\tilde{Q}_2v_2^2+\tilde{Q}_Ss^2\right )\tilde{Q}_\phi.
\end{equation}
As was noted in \cite{Athron:2013ipa}, the first two of these conditions may be rewritten in the form
\begin{equation}\label{eq:E6MZequation}
\frac{M_Z^2}{2}=-\frac{\lambda^2s^2}{2}+\frac{\tilde{m}_{H_d}^2-\tilde{m}_{H_u}^2\tan^2\beta}{\tan^2\beta-1}+\frac{D_{H_d}-D_{H_u}\tan^2\beta}{\tan^2\beta-1},
\end{equation}
\begin{equation}\label{eq:E6sin2bequation}
\sin 2\beta=\frac{\sqrt{2}\lambda A_{\lambda} s}{\tilde{m}_{H_d}^2+\tilde{m}_{H_u}^2+\lambda^2s^2+D_{H_d}+D_{H_u}},
\end{equation}
with $M_Z^2=\bar{g}^2v^2/4$, $v^2=v_1^2+v_2^2$ and $\tan\beta = v_2/v_1$ and where we have for convenience absorbed the effects of the loop corrections into the soft masses, 
\begin{align*}
\tilde{m}_{H_d}^2&=m_{H_d}^2+\frac{1}{v_1}\frac{\partial \Delta V_{E_6}}{\partial v_1},\\
\tilde{m}_{H_u}^2&=m_{H_u}^2+\frac{1}{v_2}\frac{\partial \Delta V_{E_6}}{\partial v_2}.
\end{align*}
Written in the form of Eq. (\ref{eq:E6MZequation}) we see the potential new source of fine tuning alluded to above, in the form of the third term on the right-hand side. For large values of the VEV $s$, the $D$-term contributions can be quite a bit larger than $M_Z^2$. In particular, recent experimental limits \cite{Aad:2014cka} require that the $Z'$ mass be large, with bounds of $M_{Z'}\gtrsim 2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim 2.62$ TeV in $U(1)_\chi$ models. To satisfy these limits typically requires large values of $s$, for example $s\gtrsim 6$ TeV is required in the E$_6$SSM with $U(1)'=U(1)_N$, so that $|D_{H_u}|,|D_{H_d}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq 0$. As a result the remaining terms on the right-hand side of Eq. (\ref{eq:E6MZequation}) must be tuned to cancel the resulting very large contribution to $M_Z$. Moreover, because this is a large \textit{tree level} fine tuning, it may negate the increase in naturalness that is associated with having a reduced need for heavy superpartners.
\section{\label{sec:tuning}Fine Tuning}
% Introduce tuning measure - BG measure (maybe Peter will add in a justification
% here).
% Explain that we derived the master formula in the E6SSM as given in Maien's 
% paper, but including extra effects not in that formula. 
% Full result is given in appendix.
% Numerical technique for calculating 1-loop tunings and including RG effects
% Outline is given here, full equations for RGE effects etc. given in appendix.
% How we calculate the tuning using spectrum generator, for E6SSM uses
% FlexibleSUSY (cite FlexibleSUSY and SARAH).
\subsection{\label{subsec:tuningmeasure}The Fine Tuning Measure}
To quantify the resulting fine tuning we apply the traditional Ellis-Barbieri-Giudice measure \cite{Ellis:1986yg,Barbieri:1987fn}. A specific model is characterised by a set of $n$ model parameters $\{p_i\}$ and is defined at some input scale $M_X$. For a given parameter $p$ in this set, one computes an associated sensitivity coefficient \cite{Feng:2013pwa}
\begin{equation}\label{eq:bgmeasure}
\Delta_p=\left | \frac{\partial \log M_Z^2}{\partial \log p}\right |=\left | \frac{p}{M_Z^2}\frac{\partial M_Z^2}{\partial p}\right |,
\end{equation}
where $M_Z^2=\bar{g}^2v^2/4$. The coefficient $\Delta_p$ measures the fractional variation in $M_Z^2$ resulting from a given variation in the parameter $p$. The overall fine tuning is then taken to be $\Delta = \underset{i}{\max}\,\{\Delta_{p_i}\}$.\\ \\
The sensitivity coefficients $\Delta_p$ may be calculated directly from the expression for $M_Z^2$ in terms of the $p_i$ for a particular model, which leads to a so-called master formula for calculating the fine tuning. A master formula for the E$_6$SSM, obtained from the tree level scalar potential, was presented in \cite{Athron:2013ipa}. In order to derive the expression presented there, the fact that $s \gg v$ was made use of to neglect certain $\mathcal{O}(v^2)$ terms in the EWSB conditions, greatly simplifying the final result.
% Important question:
% Impact of varying charges, is it picked up by the approximate CE6SSM master formula?
% e.g. how different are things in the limit Q_S --> 0?
For the purposes of exploring a wider class of $E_6$ inspired models, we have derived the master formula without neglecting any $\mathcal{O}(v^2)$ terms. The more complete tree-level master formula is somewhat complicated. This is because, unlike in the MSSM, even at tree level it is not possible to solve explicitly for the VEVs $v_1$, $v_2$ in terms of the Lagrangian parameters. It may be written in the form
\begin{equation}\label{eq:E6masterformula}
\frac{\Delta_p}{2|p|}=\bigg|\tilde{\Delta}_\lambda\frac{\partial\lambda}{\partial p}+\tilde{\Delta}_{A_\lambda}\frac{\partial A_\lambda}{\partial p}+\tilde{\Delta}_{m_{H_d}^2}\frac{\partial m_{H_d}^2}{\partial p}+\tilde{\Delta}_{m_{H_u}^2}\frac{\partial m_{H_u}^2}{\partial p}+\tilde{\Delta}_{m_S^2}\frac{\partial m_S^2}{\partial p}\bigg|.
\end{equation}
Explicit expressions for the $\tilde{\Delta}_i$ appearing above are given in Appendix \ref{app:masterformula}. It should be noted that variations in the gauge couplings are neglected in Eq. (\ref{eq:E6masterformula}), so that the formula above is valid at the level of 1-loop RG running and provided that the gauge couplings are excluded from the set $\{p_i\}$. In general, any dimensionless SUSY parameters in $\{p_i\}$ will contribute to the running of the gauge couplings at 2-loops and so terms proportional to $\partial g_i /\partial p$ are also present. For dimensionless $p$, the resulting contributions are $\mathcal{O}(g_1^2p^2)$, $\mathcal{O}(g_1'^2p^2)$, $\mathcal{O}(g_2^2p^2)$ or higher order, and can therefore usually be safely neglected.\\ \\
Evaluating the fine tuning directly using a master formula approach rapidly becomes impractical, as a brief inspection of the expressions for the $\tilde{\Delta}_i$ should make clear. It is well known in the MSSM that radiative corrections can significantly change (indeed, reduce) the fine tuning \cite{Cassel:2010px}. It is therefore important when studying the fine tuning to include 1- and 2-loop corrections in the fine tuning measure. To do so it is most convenient to work in terms of the EWSB conditions Eq. (\ref{eq:E6EWSBConditions}), rather than Eq. (\ref{eq:E6MZequation}). The general procedure is as follows \cite{Ellwanger:2011mu}. For a model in which $m$ fields develop real VEVs (e.g. $m=2$ in the MSSM, $m=3$ in the NMSSM and in the $E_6$ models considered), we require that the $m$ minimization conditions
\begin{equation}\label{eq:EWSBconditions}
f_1=f_2=\dotsb=f_m=0
\end{equation}
continue to hold under an arbitrary variation in a model parameters $p\rightarrow p+\delta p$, so that the variations $\delta f_i$ satisfy
\begin{equation}\label{eq:EWSBvariations}
\delta f_1 = \delta f_2=\dotsb =\delta f_m =0.
\end{equation}
Each $f_i$ is a function of the VEVs $v_j$ and $l$ running parameters $q_k$ evaluated at the scale of EWSB, $f_i=f_i(v_j,q_k)$. Thus for each $f_i$ we have that
\begin{equation}\label{eq:EWSBchainrule}
\delta f_i = \sum_{j=1}^m \frac{\partial f_i}{\partial v_j}\frac{\partial v_j}{\partial p}+\sum_{k=1}^l \frac{\partial f_i}{\partial q_k}\frac{\partial q_k}{\partial p}=0.
\end{equation}
The quantities $\frac{\partial f_i}{\partial v_j}$ are the elements of the CP-even Higgs squared mass matrix $M_h^2$ of the model before rotating into the mass eigenstate basis. When evaluated for all $n$ model parameters, the above system of equations can be concisely expressed as
\begin{equation}\label{eq:tuningsystem}
M_h^2\begin{pmatrix}
\frac{\partial v_1}{\partial p_1} & \cdots & \frac{\partial v_1}{\partial p_n} \\
\vdots & \ddots & \vdots \\
\frac{\partial v_m}{\partial p_1} & \cdots & \frac{\partial v_m}{\partial p_n}
\end{pmatrix}=
-\begin{pmatrix}
\frac{\partial f_1}{\partial q_1} & \cdots & \frac{\partial f_1}{\partial q_l} \\
\vdots & \ddots & \vdots \\
\frac{\partial f_m}{\partial q_1} & \cdots & \frac{\partial f_m}{\partial q_l}
\end{pmatrix}
\begin{pmatrix}
\frac{\partial q_1}{\partial p_1} & \cdots & \frac{\partial q_1}{\partial p_n} \\
\vdots & \ddots & \vdots \\
\frac{\partial q_l}{\partial p_1} & \cdots & \frac{\partial q_l}{\partial p_n}
\end{pmatrix}.
\end{equation} 
The quantities forming the first matrix on the right-hand side, along with $M_h^2$, are easily calculated analytically. The remaining derivatives $\partial q_k /\partial p$ must be determined using the RGEs. Once these have been obtained, it is straightforward to solve for the $\partial v_i /\partial p$. The sensitivity coefficients $\Delta_p$ are then simply linear combinations of the $\partial v_i/\partial p$ and $\partial q_k/\partial p$. Radiative corrections may be easily incorporated by including the Coleman-Weinberg potential contributions in the EWSB conditions.\\ \\
The most involved step in the process of getting $\Delta_p$ is evaluating the matrix containing the derivatives $\partial q_k/\partial p$. In general this must be done numerically, by evaluating the running using the 1- and 2-loop RGEs. This is an obstacle to doing large scans of the parameter space, as the process of numerically evaluating $n\times l$ derivatives is computationally expensive. In general, for example for models defined at the GUT scale, accurately calculating the fine tuning is better done by numerically differentiating $M_Z^2$ directly to reduce the number of derivatives that must be computed. For studying models defined at low energies, as we do here, we can take advantage of the fact that the amount of running involved is small. This makes it possible to use approximate analytic solutions to the RGEs that exhibit good accuracy over the range of scales considered. Given the 2-loop RG equation for a parameter $q$,
\begin{equation}\label{eq:rge}
\frac{\textrm{d}q}{\mathrm{d}t}=\frac{1}{16\pi^2}\beta_q^{(1)}+\frac{1}{(16\pi^2)^2}\beta_q^{(2)},\qquad t\equiv \log\frac{Q}{M_X},
\end{equation}
a Taylor series expansion of the solution may be used to obtain the parameter at the scale $Q$,
\begin{align}\label{eq:rgeapproxsoln}
q(Q)&=q(M_X)+\int_0^t q(t')\;\textrm{d}t'\approx q(M_X)+\frac{t}{16\pi^2}\left ( \beta_q^{(1)}+\frac{\beta_q^{(2)}}{16\pi^2}\right )+\frac{t^2}{32\pi^2}\frac{\textrm{d}\beta_q^{(1)}}{\textrm{d}t}+\mathcal{O}(t^2).
\end{align}
Expanded to this order we obtain the leading log (LL) and next-to-LL (NLL) contributions at 2-loop order. The $\mathcal{O}(t^2)$ terms not displayed above are formally of 3-loop order and are neglected. The derivative of the 1-loop $\beta$ function is given by
\begin{equation}\label{eq:1loopbetaderivative}
\frac{\textrm{d}\beta_q^{(1)}}{\textrm{d}t}=\frac{1}{16\pi^2}\sum_{q_k}\beta_{q_k}^{(1)}\frac{\partial \beta_q^{(1)}}{\partial q_k},
\end{equation}
where the sum is over all running parameters appearing in $\beta_q^{(1)}$. The $\beta$ functions appearing on the right hand side of Eqs. (\ref{eq:rgeapproxsoln}) and (\ref{eq:1loopbetaderivative}) are evaluated at the input scale $M_X$, giving a simple analytic expression for the parameters at the scale of EWSB in terms of the model parameters at $M_X$. Explicit results for the relevant series expansions in the MSSM and $E_6$ models are presented in Appendix \ref{app:rges}.
\subsection{\label{subsec:numericalprocedure}Numerical Procedure}
Using the approach outlined above, we have scanned the low energy parameter space of the MSSM and E$_6$SSM and calculated the fine tuning in each of the models considered. To do so, we implemented the above expressions for computing the fine tuning in a modified version of the E$_6$SSM spectrum generator that was used in \cite{Athron:2013ipa}. In order to include effects coming from 2-loop RG running, the 2-loop RGEs generated by SARAH \cite{Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta} and FlexibleSUSY \cite{Athron:2014yba} were used instead of the 1-loop results that had previously been implemented. The CP-even Higgs masses are calculated including the leading 1-loop effective potential contributions given in \cite{Athron:2009bs}. To scan over the MSSM parameter space, the equivalent MSSM fine tuning expressions were implemented into a modifed version of SOFTSUSY 3.3.10 \cite{Allanach:2001kg,Allanach:2013kza}. For consistency with the results produced in the $E_6$ models, and for computational speed, for our main scans only the dominant 1- and 2-loop corrections to the CP-even Higgs masses were included. The parameter ranges that were scanned over are presented in Table \ref{tab:scanranges}. With the exception of the stop mixing $A_t$, which was logarithmically scanned, all parameters were linearly scanned. In order to ensure the validity of the approximate RGE solutions, the input scale $M_X$ was set to $M_X=20$ TeV for both the MSSM and the $E_6$ models. Finally, the fine tuning was evaluated at the scale $Q=M_{\textrm{SUSY}}=\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop masses evaluated at $Q=M_{\textrm{SUSY}}$. 
\begin{table}[h]
\centering
\begin{ruledtabular}
\begin{tabular}{cc}
MSSM & E$_6$SSM \\
\hline
$2 \leq \tan\beta \leq 50$& $2 \leq \tan\beta \leq 50$ \\
$-1\textrm{ TeV } \leq \mu \leq 1 \textrm{ TeV}$ & $-3 \leq \lambda \leq 3$\\
$-1\textrm{ TeV } \leq B \leq 1\textrm{ TeV}$ & $-10\textrm{ TeV } \leq A_\lambda \leq 10\textrm{ TeV}$ \\
$ 200 \textrm{ GeV } \leq m_{Q_3} \leq 2000 \textrm { GeV}$ & $ 200 \textrm{ GeV } \leq m_{Q_3} \leq 2000 \textrm { GeV}$\\
$ 200 \textrm{ GeV } \leq m_{u_3} \leq 2000 \textrm { GeV}$ & $ 200 \textrm{ GeV } \leq m_{u_3} \leq 2000 \textrm { GeV}$\\
$ -10 \textrm{ TeV } \leq A_t \leq 10 \textrm { TeV}$ & $ -10 \textrm{ TeV } \leq A_t \leq 10 \textrm { TeV}$\\
$M_2=100\textrm{ GeV, } 1050\textrm{ GeV, } 2000 \textrm{ GeV}$ & $M_2=100\textrm{ GeV, } 1050\textrm{ GeV, } 2000 \textrm{ GeV}$ \\
\end{tabular}
\end{ruledtabular}
\caption{The parameters scanned over and the ranges of values used in the MSSM and the $E_6$ models.}
\label{tab:scanranges}
\end{table}
\section{\label{sec:results}Results}
% Our results. Plots to go in here:
%    - tuning as a function of stop mass for the MSSM and E6SSM
%    - full scatter plots of MSSM and E6SSM, including different
%      M_Z' values
%    - plots of chargino bound impacts
%    - if room, plots for different U(1)' charges
\section{\label{sec:conclusion}Conclusions}
% Our conclusions: at low scales stops are not a big contributor,
% Z' causes a significant fine tuning in the E6SSM (dominant -> lower
% bound), chargino bounds will be important for fine tuning in the MSSM
% but not as much for the E6SSM, and possibly discuss different U(1)' charges.
\appendix
\section{\label{app:masterformula}Fine Tuning Master Formula}
% Tree level master formula for the E6SSM
\section{\label{app:rges}RGE Contributions}
% List the derivatives needed in the Taylor series approximation
% to the RGE solutions.

% NB before submission replace this with a copy-paste of the bbl file?
\bibliography{bibliography}
\end{document}

### 2014-11-03 fs-spectrum/models/lowE6SSM/lowE6SSM_two_scale_tuning_calculator.cpp
Moved initialisation of underflow to constructor

@@ -6,11 +6,12 @@
 namespace flexiblesusy {
 
    lowE6SSM_tuning_calculator::lowE6SSM_tuning_calculator(const lowE6SSM<Two_scale>& m)
-         : model(m)
-         , input_scale(0.)
-         , tuning_scale(0.)
-         , tolerance(1.0e-4)
-         , max_iterations(100)
+      : underflow(1.0e-100) 
+      , model(m)
+      , input_scale(0.)
+      , tuning_scale(0.)
+      , tolerance(1.0e-4)
+      , max_iterations(100)
    {
       tuning_ewsb_loop_order = m.get_ewsb_loop_order();
       tuning_beta_loop_order = m.get_loops();

### 2014-11-03 fs-spectrum/models/lowE6SSM/lowE6SSM_two_scale_tuning_calculator.hpp

@@ -76,7 +76,7 @@ namespace flexiblesusy {
       static const std::size_t num_one_loop_ewsb_pars = 4;
       static const std::size_t num_tuning_pars = 12;
 
-      const double underflow = 1.0e-100;
+      const double underflow;
 
       struct numerical_deriv_pars {
          lowE6SSM<Two_scale> model;

### 2014-11-03 fs-spectrum/models/lowE6SSM/tuning_scan_lowE6SSM.cpp

@@ -1065,7 +1065,8 @@ int main()
 
       std::vector<std::size_t> position;
       while (!scan.has_finished()) {
-
+         double wall_start = get_wall_time();
+         double cpu_start = get_cpu_time();
          bool has_serious_problem = false;
          position = scan.get_position();
          input.TanBeta = TanBeta_vals(position.at(0));
@@ -1238,6 +1239,10 @@ int main()
                          << std::setw(12) << std::left << tuning_problem << ' '
                          << std::setw(12) << std::left << (problems.have_serious_problem() || has_serious_problem)
                          << '\n';
+               double wall_end = get_wall_time();
+               double cpu_end = get_cpu_time();
+               std::cout << "wall time = " << wall_end - wall_start << " seconds\n";
+               std::cout << "cpu time  = " << cpu_end - cpu_start << " second\n";
                   }
          }
       }

### 2014-11-03 fs-spectrum/models/lowE6SSM/tuning_scan_lowE6SSM.cpp
Added step forward in scan, so that it actually terminates

@@ -1245,6 +1245,8 @@ int main()
                std::cout << "cpu time  = " << cpu_end - cpu_start << " second\n";
                   }
          }
+         // of course, this would help with program termination...
+         scan.step_forward();
       }
 
    }

### 2014-11-03 fs-spectrum/models/lowE6SSM/tuning_scan_lowE6SSM.cpp
Added calculation of charged Higgs mass

@@ -1052,6 +1052,7 @@ int main()
                          << std::setw(12) << std::left << "tachyon(VZp)" << ' '
                          << std::setw(12) << std::left << "tachyon(hh)" << ' '
                          << std::setw(12) << std::left << "tachyon(Ah)" << ' '
+                         << std::setw(12) << std::left << "tachyon(Hpm)" << ' '
                          << std::setw(12) << std::left << "tuning_err" << ' '
                          << std::setw(12) << std::left << "error"
                          << '\n';
@@ -1065,8 +1066,7 @@ int main()
 
       std::vector<std::size_t> position;
       while (!scan.has_finished()) {
-         double wall_start = get_wall_time();
-         double cpu_start = get_cpu_time();
+
          bool has_serious_problem = false;
          position = scan.get_position();
          input.TanBeta = TanBeta_vals(position.at(0));
@@ -1143,6 +1143,7 @@ int main()
             model.calculate_MCha();
             model.calculate_Mhh();
             model.calculate_MAh();
+            model.calculate_MHpm();
 
             model.set_mHd2(mHd2);
             model.set_mHu2(mHu2);
@@ -1236,13 +1237,10 @@ int main()
                          << std::setw(12) << std::left << problems.is_tachyon(lowE6SSM_info::VZp) << ' '
                          << std::setw(12) << std::left << problems.is_tachyon(lowE6SSM_info::hh) << ' '
                          << std::setw(12) << std::left << problems.is_tachyon(lowE6SSM_info::Ah) << ' '
+                         << std::setw(12) << std::left << problems.is_tachyon(lowE6SSM_info::Hpm) << ' '
                          << std::setw(12) << std::left << tuning_problem << ' '
                          << std::setw(12) << std::left << (problems.have_serious_problem() || has_serious_problem)
                          << '\n';
-               double wall_end = get_wall_time();
-               double cpu_end = get_cpu_time();
-               std::cout << "wall time = " << wall_end - wall_start << " seconds\n";
-               std::cout << "cpu time  = " << cpu_end - cpu_start << " second\n";
                   }
          }
          // of course, this would help with program termination...

### 2014-11-07 paper/e6ssm-tuning-paper.tex
changed title. started to sketch out introduction and added references.

@@
 
-\title{Fine tuning in the E$_6$SSM}
+\title{Naturalness in U(1) exentions of the MSSM}
 
@@
  \affiliation{
-ARC Centre of Excellence for Particle Physics at the Terascale, School of Chemistry and Physics, The University of Adelaide,
-Adelaide, South Australia 5005, Australia}
+ARC Centre of Excellence for Particle Physics at the Terascale, School of Physics, Monash University, Melbourne VIC 3800, Australia
+}
 
@@
 \section{\label{sec:intro}Introduction}
+The discovery of an approximately 125 GeV Higgs
+\cite{Aad:2012tfa,Chatrchyan:2012ufa} at the large hadron collider
+(LHC) has interesting implications for physics beyond the standard
+model (SM) and supersymmetry (SUSY).  On the one hand it provides a
+light Higgs boson in fitting with expectations from supersymmetry, and
+can be fitted in the minimal supersymmetric standard model (MSSM).  On
+the other hand it is slightly heavier than the constrained versions of the 
+MSSM (cMSSM) can accommodate naturally \cite{Cassel:2011zd,Ghilencea:2012gz}.
+
+The Higgs causes a naturalness problem because at tree level it has an
+upper bound of $m_Z$. The dominant higher order corrections to the
+Higgs mass come from stops and to obtain a $125$ GeV Higgs they need
+be rather heavy. Heavy stops will provide a large contribution to the
+soft breaking mass for the up-type Higgs scalar, $m_{H_u}^2$ at low
+energies, through the evolution of the renormalisation group equations
+(RGEs) from the grand unification (GUT) scale to the electroweak (EW)
+scale. This affects the SUSY prediction of the electroweak VEV, v, or
+the mass of the $Z$ boson, $m_Z$.  This naturalness problem motivates
+both further examination of non-minimal SUSY models that can raise the
+Higgs mass without the need for heavy stops and alternative
+possibilities for how the soft breaking parameters get generated,
+which might set them them at lower energies, reducing the influence
+the stops have on the soft breaking mass for the up-type Higgs scalar,
+$m_{H_u}^2$.
+
+In addition to that naturalness issue, often referred to as the little
+hierarchy problem, the MSSM also suffers fromn the $\mu$-problem. This
+is also a naturalness problem since there should be a natural explanation
+of how the $\mu$ superpotential parameter can be set to the same scale
+as the soft breaking masses.
+
+U(1) extensions of the MSSM provide a very elegant solution to this
+$\mu$-problem \cite{} and also raise the Higgs mass with new $F$- and
+$D$-terms. Nonetheless, as was recently demonstrated in the context of
+the exceptional supersymmetric standard model (E$_6$SSM)
+\cite{King:2005jy,King:2005my,Athron:2010zz}, can still suffer from
+naturalness problems with the mass of the new $Z^\prime$ associated
+with break down of the new U(1) appearing in the electroweak symmetry
+breaking conditions at tree level \cite{Athron:2013ipa}.  Nonetheless
+the constrained version of E$_6$SSM (cE$_6$SSM) \cite{Athron:2009ue,
+  Athron:2009bs} still turned out to be significantly less tuned than
+the cMSSM.
+
+However this comparison of fine tuning depends crucially upon the
+assumptions of these gravity mediated SUSY breaking motivated
+constrained models and in particular the way the universality
+constraints are applied at the GUT scale.  As mentioned above, given
+the findings at the LHC it is worth considering other possibilities,
+which may allow the soft masses to be set at lower energies. As the
+scale at which the parameters fufill some breaking inspired
+constraints is lowered the stop masses contribute less to the fine
+tuning.
+
+At the same time in U(1) extensions, lowering the UV boundary scale
+for the RGE evolution also allows even larger $F$-term contriubutions
+to the Higgs mass, so long as one only requires $\lambda$, the
+coupling between the Singlet Higgs, $S$ and the up- and down-type
+Higgs bosons, $H_u$ and $H_d$, to remain perbative up to the UV scale
+and not the all teh up to the GUT scale.
+
+However the tuning from the
+$Z^\prime$ mass limit does not disappear as the UV boundary condition is lowered.
+This tuning  appears in the EWSB conditions at tree level and is quite difficult to avoid without introducing a pure gauge singlet \cite{Athron:2014pua}.
+
+In this paper we investigate how big this tuning is if we bring this
+scale all the way down to 20 TeV, effectively minimising contribution
+from the stops. We find that the $Z^\prime$ limit is enough to already
+require moderate fine tuning.  We also show this is comparable to the
+situation in the MSSM defined at smae scalew if chargino limit is
+$700$ GeV, which is the most conservative limit on can obtain and
+above the tuning from the stops, in both the MSSM and U(1) extensions.
+We also show that the tuning from the stops becomes larger when the
+high scale is raied to ?? wheares for the E$_6$SSM the minimum tuning
+is lower than the MSSM above this scale.  Therefore iot is clear that
+which model is preferred and how large the tuning is depends on our
+assumptions about SUSY breaking models.
+
+However we also show that if the $Z^\prime$ limit is the extended to
+?? then $U(1)$ extensions of the MSSM will already suffer from a
+severe tuning, irrespectiove of the UV boundary condition for th RGE
+evolution.  Therefore the $Z^\prime$ constraint is amongst the most
+important in terms of tuning and attacking natural supersymmtry
+experimentally and the next run of the LHC will be crucial.
+
+U(1) literature review  \newline
+
+E6 literature review \newline
+ Exceptional Supersymmetric Standard Model is a very well U(1) extension where....
+
+fine tuning literature review...
+\newline  It has also been shown that the NMSSM is less fine tuned than in it's minimal model rather than with the inclusion of extra matter \cite{Binjonaid:2014oga}.
+\newline
+
+summary of paper
+
 \section{\label{sec:model}The Model}
@@
 % NB before submission replace this with a copy-paste of the bbl file?
-\bibliography{bibliography}
+\bibliography{bibliography}{}
 \end{document}

### 2014-11-09 paper/e6ssm-tuning-paper.tex
added more references.

@@
 U(1) literature review  \newline
+ Here we will refer to U(1) extensions of the MSSM, which solve the $\mu$-problem as the USSM \cite{Fayet:1977yc,Suematsu:1994qm,Cvetic:1995rj}, while will sometimes specify that the models are inspired by $E_6$ by referring to them as such.
+Finally we will aslo discuss specific models with complete $E_6$ matter multiplets at low energies and an extra $U(1)$ under which the right handed neutrino remains interactionless as E$_6$SSM-variants, with the E$_6$SSM reserved for the original formualtion of this model \cite{King:2005jy,King:2005my,Athron:2010zz} original formulation of the model.
+
+$U(1)$ and $E_6$ inspired extensions of the MSSM have been studied very widely in the literature \cite{Gunion:1989we,Gunion:1992hs,Binetruy:1985xm,Ellis:1986yg,Ibanez:1986si,Gunion:1986ky,Haber:1986gz,Baer:1987eb,Gunion:1987jd,Grifols:1986vr,Morris:1987fm,Suematsu:1997tv,Suematsu:1997qt,Suematsu:1997au,Keith:1996fv,Gherghetta:1996yr} (or for reviews see \cite{Hewett:1988xc,Langacker:2008yv}).
+More recently...
 
@@
 
-\section{\label{sec:model}The Model}
+The structure of this paper is as follows.
+In section \ref{sec:model} we review the models we consider.
+In section \ref{sec:ewsb} we speciofy the EWSB conditions of the moidels, with particular focus on how the $Z^\prime$ mass influences the predition of $M_Z$.
+Then in section \ref{sec:tuning} we introduce our fine tuning measure and our approach to evaluating it to obtain the individual sensitivities.
+The numerical procedure we use to obtain our results is given in \ref{subsec:numericalprocedure} and then the reulst are specified in section \ref{sec:results}.
+
+\section{\label{sec:model}U(1) extensiosn and the E$_6$SSM}
 % Table of U(1)' charges, which may or may not be useful to include.

### 2014-11-10 paper/e6ssm-tuning-paper.tex
added more references and some E6SSM literature review.

--- 2014-11-07 paper/e6ssm-tuning-paper.tex
@@
 U(1) extensions of the MSSM provide a very elegant solution to this
-$\mu$-problem \cite{} and also raise the Higgs mass with new $F$- and
-$D$-terms. Nonetheless, as was recently demonstrated in the context of
-the exceptional supersymmetric standard model (E$_6$SSM)
+$\mu$-problem \cite{Fayet:1977yc, Kim:1983dt, Suematsu:1994qm, Cvetic:1995rj,  Cvetic:1996mf, Jain:1995cb, Nir:1995bu, Cvetic:1997ky} and also
+raise the Higgs mass with new $F$- and $D$-terms. Nonetheless, as was
+recently demonstrated in the context of the exceptional supersymmetric
+standard model (E$_6$SSM)
 \cite{King:2005jy,King:2005my,Athron:2010zz}, can still suffer from
@@
 
-However the tuning from the
-$Z^\prime$ mass limit does not disappear as the UV boundary condition is lowered.
-This tuning  appears in the EWSB conditions at tree level and is quite difficult to avoid without introducing a pure gauge singlet \cite{Athron:2014pua}.
+However the tuning from the $Z^\prime$ mass limit does not disappear
+as the UV boundary condition is lowered. This tuning appears in the
+EWSB conditions at tree level and is quite difficult to avoid without
+introducing a pure gauge singlet \cite{Athron:2014pua}.
 
@@
 
-U(1) literature review  \newline
+Here we will refer to U(1) extensions of the MSSM, which solve the
+$\mu$-problem as the USSM
+\cite{Cvetic:1995rj, Jain:1995cb, Nir:1995bu, Cvetic:1996mf, Cvetic:1997ky}, while we will
+sometimes specify that the models are inspired by $E_6$ by referring
+to them as such. Finally we will also discuss specific models with
+complete $E_6$ matter multiplets at low energies and an extra $U(1)$
+under which the right handed neutrino remains interactionless as
+E$_6$SSM-variants\cite{Howl:2007zi, Braam:2009fi,
+  Braam:2010sy, Hall:2011zq, Nevzorov:2012hs, Athron:2014pua}, with the E$_6$SSM reserved for the original
+formualtion of this model \cite{King:2005jy,King:2005my,Athron:2010zz}
+original formulation of the model.
 
-E6 literature review \newline
- Exceptional Supersymmetric Standard Model is a very well U(1) extension where....
+$U(1)$ and $E_6$ inspired extensions of the MSSM have been studied
+very widely in the literature \cite{Gunion:1989we, Gunion:1992hs,
+  Binetruy:1985xm, Ellis:1986yg, Ibanez:1986si, Gunion:1986ky,
+  Haber:1986gz, Baer:1987eb, Gunion:1987jd, Grifols:1986vr,
+  Ellis:1986ip, Morris:1987fm, Drees:1987tp, Ma:1995xk,
+  Suematsu:1997tv, Suematsu:1997qt, Suematsu:1997au, Keith:1996fv,
+  Keith:1997zb, Gherghetta:1996yr, Demir:1998dk,L angacker:1998tc,
+  Hambye:2000bn, Ma:2000jf} (or for reviews see
+\cite{Hewett:1988xc,Langacker:2008yv}).  There has also been a lot of
+work recently including investigations of the neutralino sector
+\cite{Hesselbach:2001ri, Barger:2005hb, Choi:2006fz,
+  Barger:2007nv};the relic abundance of dark matter
+\cite{Kalinowski:2008iq}; GUT scale family symmetries which can
+explain the hierarchy of masses in the fermion sector and their
+associated mixings \cite{Stech:2008wd}; neurtrino physics
+\cite{Kang:2004ix}; explanations of the matter-anti-matter asymmetry
+of the universe though EW baryogensis or leptogensis
+\cite{Hambye:2000bn,Ma:2000jf,Kang:2004pp}; dipole moments
+\cite{GutierrezRodriguez:2006hb}; anomaly mediated SUSY breaking with
+D-term contributions \cite{Asano:2008ju} and the (extended) Higgs
+sectors \cite{Daikoku:2000ep,Ham:2008xf}.
+
+In this paper we will focus a lot on a very well motivated $E_6$
+inspired $U(1)$ exension, the Exceptional Supersymmetric Standard
+Model (E$_6$SSM)\cite{King:2005jy,King:2005my,Athron:zz}.  In this
+model since the right handed neutrino remains interactionless they may
+explain the tiny observed masses of neutrinos via the see-saw
+mechanism andp the baryon asymmetry in the universe via leptogensis
+\cite{Hambye:2000bn,King:2008qb}.
+
+The gauge coupling running in the E$_6$SSM at the two-loop level leads
+to unification more precisely than in the MSSM \cite{King:2007uj} or
+in slightly modified scenarios two-step unification can take place
+\cite{Howl:2007hq,Howl:2007zi}. If the exotic particles are light in
+these models this can open up non-standard decays of the SM--like
+Higgs boson \cite{Hall:2010ix,Nevzorov:2013tta,Athron:2014pua}. The
+correct relic abundance could be obtained entirely through an almost
+decoupled ``inert'' neutralino sector \cite{Hall:2009aj} no longer
+seem phenomenologically viable due to limits from direct detection of
+dark matter \cite{} and limits on invisible Higgs decays \cite{}.
+
+Alternatively one may specilaize to scenarios known as the EZSSM
+\cite{Hall:2011zq} where the inert singlinos, which cause these
+problems are entirely decoupled and the relic abundance is fitted with
+a bino-like candidate with a novel mechanism involving back-scattering
+into a Heavier inert Higgsino. Finally one may obtain...
+
+In the
+constrained version of the of the E$_6$SSM the particle spectrum,
+collider signatures and fine tuning have been studied
+\cite{cE6SSM1,cE6SSM2,cE6SSM3,cE6SSM4,Athron:2013ipa}. The threshold
+corrections to the $\overline{DR}$ gauge and Yukawa couplings in the
+\essm were calculated and the numerical impact in the constrained
+version examined \cite{Athron:2012pw}. The impact of gauge kinetic
+mixing in the case where both of the extra U(1)'s appearing from the
+breakdown of E$_6$ are present at low energy was studied in
+\cite{Rizzo:2012rf}.  The \essm was also included in a studies looking
+at how first or second generation sfermion masses can be used to
+constrain the GUT scale parameters \cite{Miller:2012vn} and the
+renormalization of VEVs \cite{Sperling:2013-1, Sperling:2013-2}.
 

### 2014-11-11 paper/e6ssm-tuning-paper.tex
updated references, introduction mostly complete.

--- 2014-11-07 paper/e6ssm-tuning-paper.tex
@@
 
-\title{Naturalness in U(1) exentions of the MSSM}
+\title{Naturalness in U(1) extensions of the MSSM}
 
@@
 the fine tuning, which does not depend on assumptions about SUSY breaking. 
-We compare our results against the tuning in
-the phenomenological MSSM (pMSSM), where the SUSY breaking terms are also
-defined at low energies.
+We compare our results against the tuning in the MSSM WITH the SUSY breaking terms also defined at low energies.
 
@@
 can be fitted in the minimal supersymmetric standard model (MSSM).  On
-the other hand it is slightly heavier than the constrained versions of the 
+the other hand it is slightly heavier than the constrained version of the 
 MSSM (cMSSM) can accommodate naturally \cite{Cassel:2011zd,Ghilencea:2012gz}.
@@
 The Higgs causes a naturalness problem because at tree level it has an
-upper bound of $m_Z$. The dominant higher order corrections to the
-Higgs mass come from stops and to obtain a $125$ GeV Higgs they need
-be rather heavy. Heavy stops will provide a large contribution to the
-soft breaking mass for the up-type Higgs scalar, $m_{H_u}^2$ at low
-energies, through the evolution of the renormalisation group equations
-(RGEs) from the grand unification (GUT) scale to the electroweak (EW)
-scale. This affects the SUSY prediction of the electroweak VEV, v, or
-the mass of the $Z$ boson, $m_Z$.  This naturalness problem motivates
-both further examination of non-minimal SUSY models that can raise the
-Higgs mass without the need for heavy stops and alternative
-possibilities for how the soft breaking parameters get generated,
-which might set them them at lower energies, reducing the influence
-the stops have on the soft breaking mass for the up-type Higgs scalar,
-$m_{H_u}^2$.
+upper bound of the mass of the $Z$ boson, $m_Z$. The dominant higher
+order corrections to the Higgs mass come from stops and to obtain a
+$125$ GeV Higgs they need be rather heavy. Heavy stops will provide a
+large contribution to the soft breaking mass for the up-type Higgs
+scalar, $m_{H_u}^2$ at low energies, through the evolution of the
+renormalisation group equations (RGEs) from the grand unification
+(GUT) scale to the electroweak (EW) scale. This affects the SUSY
+prediction of the electroweak VEV, v, or $m_Z$.  This naturalness
+problem motivates both further examination of non-minimal SUSY models
+that can raise the Higgs mass without the need for heavy stops and
+alternative possibilities for how the soft breaking parameters get
+generated, which might set them them at lower energies, reducing the
+influence the stops have on the soft breaking mass for the up-type
+Higgs scalar, $m_{H_u}^2$.
 
 In addition to that naturalness issue, often referred to as the little
-hierarchy problem, the MSSM also suffers fromn the $\mu$-problem. This
+hierarchy problem, the MSSM also suffers from the $\mu$-problem. This
 is also a naturalness problem since there should be a natural explanation
@@
 U(1) extensions of the MSSM provide a very elegant solution to this
-$\mu$-problem \cite{} and also raise the Higgs mass with new $F$- and
-$D$-terms. Nonetheless, as was recently demonstrated in the context of
-the exceptional supersymmetric standard model (E$_6$SSM)
-\cite{King:2005jy,King:2005my,Athron:2010zz}, can still suffer from
+$\mu$-problem \cite{Fayet:1977yc, Kim:1983dt, Suematsu:1994qm, Cvetic:1995rj,  Cvetic:1996mf, Jain:1995cb, Nir:1995bu, Cvetic:1997ky} and also
+raise the Higgs mass with new $F$- and $D$-terms. Nonetheless, as was
+recently demonstrated in the context of the exceptional supersymmetric
+standard model (E$_6$SSM)
+\cite{King:2005jy,King:2005my,Athron:2010zz}, such models can still suffer from
 naturalness problems with the mass of the new $Z^\prime$ associated
@@
 which may allow the soft masses to be set at lower energies. As the
-scale at which the parameters fufill some breaking inspired
+scale at which the parameters fulfill some breaking inspired
 constraints is lowered the stop masses contribute less to the fine
@@
 At the same time in U(1) extensions, lowering the UV boundary scale
-for the RGE evolution also allows even larger $F$-term contriubutions
+for the RGE evolution also allows even larger $F$-term contributions
 to the Higgs mass, so long as one only requires $\lambda$, the
 coupling between the Singlet Higgs, $S$ and the up- and down-type
-Higgs bosons, $H_u$ and $H_d$, to remain perbative up to the UV scale
-and not the all teh up to the GUT scale.
+Higgs bosons, $H_u$ and $H_d$, to remain perturbative up to the UV scale
+and not the all the way up to the GUT scale.
 
-However the tuning from the
-$Z^\prime$ mass limit does not disappear as the UV boundary condition is lowered.
-This tuning  appears in the EWSB conditions at tree level and is quite difficult to avoid without introducing a pure gauge singlet \cite{Athron:2014pua}.
+However the tuning from the $Z^\prime$ mass limit does not disappear
+as the UV boundary condition is lowered. This tuning appears in the
+EWSB conditions at tree level and is quite difficult to avoid without
+introducing a pure gauge singlet \cite{Athron:2014pua}.
 
@@
 require moderate fine tuning.  We also show this is comparable to the
-situation in the MSSM defined at smae scalew if chargino limit is
+situation in the MSSM defined at the same scale if chargino limit is
 $700$ GeV, which is the most conservative limit on can obtain and
@@
 We also show that the tuning from the stops becomes larger when the
-high scale is raied to ?? wheares for the E$_6$SSM the minimum tuning
-is lower than the MSSM above this scale.  Therefore iot is clear that
+high scale is raised to ?? whereas for the E$_6$SSM the minimum tuning
+is lower than the MSSM above this scale.  Therefore it is clear that
 which model is preferred and how large the tuning is depends on our
@@
 ?? then $U(1)$ extensions of the MSSM will already suffer from a
-severe tuning, irrespectiove of the UV boundary condition for th RGE
+severe tuning, irrespective of the UV boundary condition for the RGE
 evolution.  Therefore the $Z^\prime$ constraint is amongst the most
-important in terms of tuning and attacking natural supersymmtry
+important in terms of tuning and attacking natural supersymmetry
 experimentally and the next run of the LHC will be crucial.
 
-U(1) literature review  \newline
+Here we will refer to U(1) extensions of the MSSM, which solve the
+$\mu$-problem as the USSM
+\cite{Cvetic:1995rj, Jain:1995cb, Nir:1995bu, Cvetic:1996mf, Cvetic:1997ky}, while we will
+sometimes specify that the models are inspired by $E_6$ by referring
+to them as such. Finally we will also discuss specific models with
+complete $E_6$ matter multiplets at low energies and an extra $U(1)$
+under which the right handed neutrino remains interaction-less as
+E$_6$SSM-variants\cite{Howl:2007zi, Braam:2009fi, Braam:2010sy, Hall:2011zq, Nevzorov:2012hs, Athron:2014pua}, with the E$_6$SSM reserved for the original
+formulation of this model \cite{King:2005jy,King:2005my,Athron:2010zz}
+original formulation of the model.
 
-E6 literature review \newline
- Exceptional Supersymmetric Standard Model is a very well U(1) extension where....
+$U(1)$ and $E_6$ inspired extensions of the MSSM have been studied
+very widely in the literature \cite{Gunion:1989we, Gunion:1992hs,
+  Binetruy:1985xm, Ellis:1986yg, Ibanez:1986si, Gunion:1986ky,
+  Haber:1986gz, Baer:1987eb, Gunion:1987jd, Grifols:1986vr,
+  Ellis:1986ip, Morris:1987fm, Drees:1987tp, Ma:1995xk,
+  Suematsu:1997tv, Suematsu:1997qt, Suematsu:1997au, Keith:1996fv,
+  Keith:1997zb, Gherghetta:1996yr, Demir:1998dk, Langacker:1998tc,
+  Hambye:2000bn, Ma:2000jf} (or for reviews see
+\cite{Hewett:1988xc,Langacker:2008yv}).  There has also been a lot of
+work recently including investigations of the neutralino sector
+\cite{Hesselbach:2001ri, Barger:2005hb, Choi:2006fz,
+  Barger:2007nv};the relic abundance of dark matter
+\cite{Kalinowski:2008iq}; GUT scale family symmetries which can
+explain the hierarchy of masses in the fermion sector and their
+associated mixings \cite{Stech:2008wd}; neurtrino physics
+\cite{Kang:2004ix}; explanations of the matter-anti-matter asymmetry
+of the universe though EW baryogensis or leptogensis
+\cite{Hambye:2000bn,Ma:2000jf,Kang:2004pp}; dipole moments
+\cite{GutierrezRodriguez:2006hb}; anomaly mediated SUSY breaking with
+D-term contributions \cite{Asano:2008ju} and the (extended) Higgs
+sectors \cite{Daikoku:2000ep,Ham:2008xf}.
 
-fine tuning literature review...
-\newline  It has also been shown that the NMSSM is less fine tuned than in it's minimal model rather than with the inclusion of extra matter \cite{Binjonaid:2014oga}.
-\newline
+In this paper we will often focus on a very well motivated $E_6$
+inspired $U(1)$ extension, the Exceptional Supersymmetric Standard
+Model (E$_6$SSM)\cite{King:2005jy,King:2005my,Athron:2010zz}.  In this
+model since the right handed neutrino remains interaction-less they may
+explain the tiny observed masses of neutrinos via the see-saw
+mechanism and the baryon asymmetry in the universe via leptogenesis
+\cite{Hambye:2000bn,King:2008qb, King:2008gw}.
 
-summary of paper
+The gauge coupling running in the E$_6$SSM at the two-loop level leads
+to unification more precisely than in the MSSM \cite{King:2007uj} or
+in slightly modified scenarios two-step unification can take place
+\cite{Howl:2007hq,Howl:2007zi}. If the exotic particles are light in
+these models this can open up non-standard decays of the SM--like
+Higgs boson \cite{Hall:2010ix,Nevzorov:2013tta,Athron:2014pua}. The
+correct relic abundance could be obtained entirely through an almost
+decoupled ``inert'' neutralino sector \cite{Hall:2009aj},.  However
+this is no longer phenomenologically viable due to limits from
+direct detection of dark matter
+\cite{2011PhRvL.107m1302A,2012PhRvL.109r1301A, Akerib:2013tjd} and due
+to a significant suppression of the decay of the lightest Higgs boson
+into SM states, due to a new channel into inert singlinos opening up.
 
-\section{\label{sec:model}The Model}
+There are still several remaining options. One may specialize to
+scenarios known as the EZSSM \cite{Hall:2011zq} where the inert
+singlinos, which cause these problems are entirely decoupled and the
+relic abundance is fitted with a bino-like candidate with a novel
+mechanism involving back-scattering into a Heavier inert
+Higgsino. Another well motivated scenario admits two possible dark
+matter candidates \cite{Nevzorov:2012hs}, where one will be an inert
+singlino and the other will have a similar composition to MSSM
+neutralinos. The simplest phenomenologically viable solution in that
+case is to make the singlinos extremely light hot dark matter
+candidate and explains almost all the relic abundance density with
+
+The impact of gauge kinetic
+mixing in the case where both of the extra U(1)'s appearing from the
+breakdown of E$_6$ are present at low energy was studied in
+\cite{Rizzo:2012rf}.  The E$_6$SSM was also included in a studies looking
+at how first or second generation sfermion masses can be used to
+constrain the GUT scale parameters \cite{Miller:2012vn} and the
+renormalization of VEVs \cite{Sperling:2013eva, Sperling:2013xqa}.
+The particle spectrum and  collider signatures of constrained version of the E$_6$SSM have been studied in a series of papers,
+\cite{Athron:2009ue,Athron:2009bs,Athron:2011wu,Athron:2012sq}. The threshold
+corrections to the $\overline{DR}$ gauge and Yukawa couplings in the
+E$_6$SSM were calculated and the numerical impact in the constrained
+version examined \cite{Athron:2012pw}.
+
+As mentioned earlier the fine tuning of the cE$_6$SSM was recently studied
+\cite{Athron:2013ipa} and there it was revealed that the associated
+$Z^\prime$ boson leads to a new source of fine tuning since it's mass
+appears in the EWSB conditions.
+
+In this paper we will examine this source of fine tuning in more detail by considering low energy constructions where the usual fine tuning problem from the Higgs is minimised.
+We will also consider  alternate charges for the extra $U(1)$ symmetry to relax the focus on the E$_6$SSM and demonstrate that this is quite a generic result.
+
+To quantify the fine tuning we will employ the traditional
+Barbieri-Giudice measure \cite{Ellis:1986yg,Barbieri:1987fn}.  This has
+been used extensively within the literature
+e.g.
+\cite{deCarlos:1993yy, deCarlos:1993ca, Chankowski:1997zh, Agashe:1997kn, Wright:1998mk, Kane:1998im, BasteroGil:1999gu, Feng:1999zg, Allanach:2000ii, Dermisek:2005ar, Barbieri:2005kf, Allanach:2006jc, Gripaios:2006nn, Dermisek:2006py, Barbieri:2006dq, Kobayashi:2006fh, Perelstein:2012qg, Antusch:2012gv,Cheng:2012pe, CahillRowley:2012rv, Ross:2012nr, Basak:2012bd, Kang:2012sy, Athron:2013ipa,Miller:2013jra, Binjonaid:2014oga, Miller:2014jza}.
+
+A number of alternative measures have also been applied in the
+literature \cite{Anderson:1994dz, Anderson:1994tr,
+  Anderson:1995cp,Anderson:1996ew,Ciafaloni:1996zh,Chan:1997bi,
+  Barbieri:1998uv,
+  Giusti:1998gz,Casas:2003jx,Casas:2004uu,Casas:2004gh,Casas:2006bd,Kitano:2005wc,
+  Athron:2007ry, Athron:2007qr, Baer:2012up} with varying motivations.
+A very different approach is to work within a Bayesian analysis.
+There the concept of naturalness is automatically incorporated since
+in models where one must fine tune parameters to fit measured values
+of the observables, the region with high likelihood will occupy a tiny
+prior volume \cite{Allanach:2007qk, Cabrera:2008tj, Ghilencea:2012gz,
+  Ghilencea:2012qk, Fichet:2012sn, Kim:2013uxa} suppressing the
+posterior.  Indeed in the MSSM and NMSSM if one transforms GUT scale
+parameters to the VEVs, the inverse of the Jacobian for this
+transformation looks quite like the derivatives that appear in the
+traditional fine tuning measure \cite{Allanach:2007qk, Cabrera:2008tj,
+  Kim:2013uxa}.  If one thinks more generally then a model without
+fine tuning is one where the parametrisation is such that all the
+parameters are observables \cite{Fichet:2012sn, Kim:2013uxa}.  This
+provides a quite general definition of fine tuning as $1/|J|$ where
+$|J|$ is the determinant of the Jacobian for the co-ordinate
+transformation between the parameters and the
+observables. Interestingly this means the tuning is the ratio of the
+infinitesimal observable space space volume element to the
+infinitesimal parameter space element and coincides with the measure
+proposed in \cite{Athron:2007ry} when the interval of variation is
+taken to zero.
+
+While this approach has many merits here will employ the traditional
+measure of fine tuning because it is both simple to apply and easy top
+compare with previous results due to it's widespread use.  Fortunately
+the derivatives which appear in these tuning are also similar to the
+Bayesian motivated measure so there should not be too large a discrepancy between the two approaches.
+
+The structure of this paper is as follows.
+In section \ref{sec:model} we review the models we consider.
+In section \ref{sec:ewsb} we specify the EWSB conditions of the models, with particular focus on how the $Z^\prime$ mass influences the prediction of $M_Z$.
+Then in section \ref{sec:tuning} we introduce our fine tuning measure and our approach to evaluating it to obtain the individual sensitivities.
+The numerical procedure we use to obtain our results is given in \ref{subsec:numericalprocedure} and then the results are specified in section \ref{sec:results}.
+
+\section{\label{sec:model}U(1) extensions and the E$_6$SSM}
 % Table of U(1)' charges, which may or may not be useful to include.
@@
 The overall fine tuning is then taken to be $\Delta = \underset{i}{\max}\,\{\Delta_{p_i}\}$.\\ \\
+
 The sensitivity coefficients $\Delta_p$ may be calculated directly from the expression for $M_Z^2$ in terms of the $p_i$ for a particular model, which leads to a so-called master formula for calculating the fine tuning.

### 2014-11-11 paper/e6ssm-tuning-paper.tex
added some detail to the model section.

@@
 \usepackage{hyperref}
+
+% macros
+\newcommand{\be}{\begin{equation}}
+\newcommand{\ee}{\end{equation}}
+\newcommand{\ba}{\begin{eqnarray}}
+\newcommand{\ea}{\end{eqnarray}}
+\newcommand{\SuperField}[1]{\hat{#1}}
 
@@
 \section{\label{sec:model}U(1) extensions and the E$_6$SSM}
+In this paper we consider U(1) extensions of the MSSM where the gauge group at low energies is,
+ \be
+SU(3)_C\times SU(2)_W\times U(1)_Y\times U(1)^\prime, \ee 
+where $U(1)^\prime$ is the new gauge group beyond that of the SM and MSSM.
+The minimal superfield content of $U(1)$ extensions which solve the $\mu$-problem should be ordinary left handed quark, $\hat{Q}_i$ and lepton $\hat{L}_i$ ($i=1,2,3$)superfields along with right handed superfields $\hat{u}^c_i$, $\hat{d}^c_i$,  $\hat{e}^c_i$ ($i=1,2,3$) for the up-type (s)quarks, down-type (s)quarks and charged (s)leptons respectively and three Higgs superfields, up-type $\hat{H}_u$, down-type $\hat{H}_d$ and a singlet under the SM gauge group $\hat{S}$.
+
+  The couplings for the $U(1)^\prime$ gauge group should allow the following renormalisable superpotential terms required in the USSM,
+\be
+W_{USSM} =  y^U_{ijk} \hat{u}^c_i \hat{H}^u_{j} \hat{Q}_k + y^D_{ijk} \hat{d}^c_i \hat{H}^d_{j} \hat{Q}_k + y^E_{ijk} \hat{e}^c_i \hat{H}^d_{j} \hat{L}_k + \lambda \hat{S} \hat{H}^d \hat{H},
+\ee, with $i,j,k \in \{1,2,3\}$.
+
+The $U(1)^\prime$ charges should allow for cancellations of gauge
+anomalies. The most elegant way to do this is to use an extra $U(1)$
+gauge symmetry that can be obtained from the break down of the $E_6$
+gauge symmetry which is anomaly free and have all matter multiplets
+from the $Z7$-plet representation of $E_6$ survive down to low energies.
+
+The breaking of $E_6$ into $SO(10)$, gives rise to $E_6\to
+SO(10)\times U(1)_{\psi}$, and the subsequent breaking of $SO(10)$
+into $SU(5)$, gives $SO(10)\to SU(5)\times U(1)_{\chi}$ (this is
+reviewed in e.g.~\cite{Langacker:2008yv})). The extar $U(1)$ gauge symmetry at low energies should then be a linear combination of these in the $E_6$ inspired case,
+\be
+U(1)^\prime = \cos(\theta) U(1)_{\chi} + \sin(\theta) U(1)_{\psi}.
+\ee In table \ref{tab:E6charges} the charges for several popular $E_6$ inspired $U(1)$ extensions are shown.
 % Table of U(1)' charges, which may or may not be useful to include.
@@
 \end{table}
+
+To ensure anomaly cancellation in these cases the full matter content
+from three generations of $27$-plets should survive to low energies.
+the low energy matter content would then be extended to, \be
+(\hat{Q}_i,\,\hat{u}^c_i,\,\hat{d}^c_i,\,\hat{L}_i,\,\hat{e}^c_i)
++(\hat{D}_i,\,\hat{\overline{D}}_i)+(\hat{S}_{i})+(\hat{H}^u_i)+(\hat{H}^d_i),\ee
+where the $\hat{S}_{i}$, $(\hat{H}^u_i$ and $\hat{H}^d_i$ are three
+generations of doublets, whose quantum numbers will be like the
+singlet, and up-, down-type Higgs fields and the $\hat{D}_i$ and
+$\hat{\overline{D}}_i$ being $SU(3)_C$ triplets that reside in the same $SU(5)$
+multiplets as these Higgs-like states.
+
+If one wishes to maintain gauge coupling unification this set of
+states should be augmented by two extra $SU(2)$ doublet states
+$H^\prime$ and $\overline{H}^\prime$ belonging to other $27^\prime$
+and $\overline{27}^\prime$ multiplets that must be incomplete at low
+energies.
+
+The full superpotential for $E_6$ inspired models will then be,
+
+\be
+W_{E6} = W_0 + W_1 + W_2,
+\label{Eq:e6-superpot}
+\ee where
+\begin{eqnarray}
+W_0 &=& \lambda_{ijk} \hat{S}_i \hat{H}^d_{j} \hat{H}^u_{k} + \kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\bar{D}}_k + h^N_{ijk} \hat{N}^c_i \hat{H}^u_{j} \hat{L}_k \nonumber \\
+& & + h^U_{ijk} \hat{u}^c_i \hat{H}^u_{j} \hat{Q}_k + h^D_{ijk} \hat{d}^c_i \hat{H}^d_{j} \hat{Q}_k + h^E_{ijk} \hat{e}^c_i \hat{H}^d_{j} \hat{L}_k, \\
+W_1 &=& g^Q_{ijk} \hat{D}_i \hat{Q}_j \hat{Q}_k + g^q_{ijk} \hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k, \\
+W_2 &=& g^N_{ijk} \hat{N}^c_i \hat{D}_j \hat{d}^c_k + g^E_{ijk} \hat{e}^c_i \hat{D}_j \hat{u}^c_k + g^D_{ijk} \hat{Q}_i \hat{L}_j \hat{\bar{D}}_k.
+\label{Eq:e6-superpot-parts}
+\end{eqnarray}
+
+Nonetheless while this model is very elegant so far, the  superpotential, \ref{Eq:e6-superpot} contains dangerous terms which can induce proton decay and lead to large flavour changing neutral currents (FCNCs).
+There are a number of approaches to suppress these terms, involving the use of different discrete symmetries.
+Here for the purposes of renormalisation group running we will simply include the following unsuppressed superpotential terms, which follows the approach taking in work on the cE$_6$SSM \cite{Athron:2009ue, Athron:2009bs},
+%
+%% \begin{align}
+%%   \begin{split}
+    \ba
+    W &\approx& - y_{\tau} (\SuperField{H}_d
+    \SuperField{L}_3) \SuperField{e}^C_3 - y_b (\SuperField{H}_d
+    \SuperField{Q}_3) \SuperField{d}_3^C - y_t (\SuperField{Q}_3
+    \SuperField{H}_u) \SuperField{u}_3^C\\
+    &&
+    + \lambda_i \SuperField{S} (\SuperField{H}_{1i}
+    \SuperField{H}_{2i}) + \kappa_i \SuperField{S} \SuperField{D}_i
+    \SuperField{\overline{D}}_i + \mu' (\SuperField{H}'
+    \SuperField{\overline{H'}}),
+    \ea
+  %% \end{split}
+  \label{SuPot_RGE}
+%%\end{align}
+%
+
 \section{\label{sec:ewsb}Electroweak Symmetry Breaking}

### 2014-11-11 paper/e6ssm-tuning-paper.tex
fix typo top --> to.

@@
 While this approach has many merits here will employ the traditional
-measure of fine tuning because it is both simple to apply and easy top
+measure of fine tuning because it is both simple to apply and easy to
 compare with previous results due to it's widespread use.  Fortunately

### 2014-11-11 paper/e6ssm-tuning-paper.tex
remove anomalous bracket.

@@
 +(\hat{D}_i,\,\hat{\overline{D}}_i)+(\hat{S}_{i})+(\hat{H}^u_i)+(\hat{H}^d_i),\ee
-where the $\hat{S}_{i}$, $(\hat{H}^u_i$ and $\hat{H}^d_i$ are three
+where the $\hat{S}_{i}$, $\hat{H}^u_i$ and $\hat{H}^d_i$ are three
 generations of doublets, whose quantum numbers will be like the

### 2014-11-11 paper/e6ssm-tuning-paper.tex
fixed c+p errors in USSM superpotential.
fixed typo extar --> extra.
WITH --> with.

@@
 the fine tuning, which does not depend on assumptions about SUSY breaking. 
-We compare our results against the tuning in the MSSM WITH the SUSY breaking terms also defined at low energies.
+We compare our results against the tuning in the MSSM with the SUSY breaking terms also defined at low energies.
 
@@
 \be
-W_{USSM} =  y^U_{ijk} \hat{u}^c_i \hat{H}^u_{j} \hat{Q}_k + y^D_{ijk} \hat{d}^c_i \hat{H}^d_{j} \hat{Q}_k + y^E_{ijk} \hat{e}^c_i \hat{H}^d_{j} \hat{L}_k + \lambda \hat{S} \hat{H}^d \hat{H},
-\ee, with $i,j,k \in \{1,2,3\}$.
+W_{USSM} =  y^U_{ij} \hat{u}^c_i \hat{H}_u \hat{Q}_j + y^D_{ij} \hat{d}^c_i \hat{H}_d \hat{Q}_j + y^E_{ij} \hat{e}^c_i \hat{H}_d \hat{L}_j + \lambda \hat{S} \hat{H}_d \hat{H}_u,
+\ee with $i,j \in \{1,2,3\}$.
 
@@
 into $SU(5)$, gives $SO(10)\to SU(5)\times U(1)_{\chi}$ (this is
-reviewed in e.g.~\cite{Langacker:2008yv})). The extar $U(1)$ gauge symmetry at low energies should then be a linear combination of these in the $E_6$ inspired case,
+reviewed in e.g.~\cite{Langacker:2008yv})). The extra $U(1)$ gauge symmetry at low energies should then be a linear combination of these in the $E_6$ inspired case,
 \be

### 2014-11-12 fs-spectrum/models/lowE6SSM/estimate_gN_lowE6SSM.cpp
Added extra benchmarks

@@ -1,0 +1,121 @@
+// ====================================================================
+// Estimate g_N at the SUSY scale based on 1-loop gauge unification,
+// (no threshold corrections).
+// For comparison, for \theta_{E_6}, should have g0 ~
+// ====================================================================
+
+#include "lowE6SSM_input_parameters.hpp"
+#include "lowE6SSM_slha_io.hpp"
+#include "lowE6SSM_spectrum_generator.hpp"
+
+#include "command_line_options.hpp"
+#include "error.hpp"
+#include "lowe.h"
+#include "spectrum_generator_settings.hpp"
+
+#include <iostream>
+#include <cstdlib>
+
+int main(int argc, const char* argv[])
+{
+   using namespace flexiblesusy;
+   using namespace softsusy;
+   typedef Two_scale algorithm_type;
+
+   Command_line_options options(argc, argv);
+   if (options.must_print_model_info())
+      lowE6SSM_info::print(std::cout);
+   if (options.must_exit())
+      return options.status();
+
+   const std::string rgflow_file(options.get_rgflow_file());
+   const std::string slha_input_file(options.get_slha_input_file());
+   const std::string slha_output_file(options.get_slha_output_file());
+   const std::string spectrum_file(options.get_spectrum_file());
+   lowE6SSM_slha_io slha_io;
+   Spectrum_generator_settings spectrum_generator_settings;
+   QedQcd oneset;
+   lowE6SSM_input_parameters input;
+
+   if (slha_input_file.empty()) {
+      ERROR("No SLHA input file given!\n"
+            "   Please provide one via the option --slha-input-file=");
+      return EXIT_FAILURE;
+   }
+
+   try {
+      slha_io.read_from_file(slha_input_file);
+      slha_io.fill(oneset);
+      slha_io.fill(input);
+      slha_io.fill(spectrum_generator_settings);
+   } catch (const Error& error) {
+      ERROR(error.what());
+      return EXIT_FAILURE;
+   }
+
+   oneset.toMz(); // run SM fermion masses to MZ
+
+   lowE6SSM_spectrum_generator<algorithm_type> spectrum_generator;
+   spectrum_generator.set_precision_goal(
+      spectrum_generator_settings.get(Spectrum_generator_settings::precision));
+   spectrum_generator.set_max_iterations(
[…]

### 2014-11-12 fs-spectrum/models/lowE6SSM/lowE6SSM_spectrum_generator.hpp

@@ -187,7 +187,8 @@ void lowE6SSM_spectrum_generator<T>::write_running_couplings(const std::string& 
    Coupling_monitor<lowE6SSM<T>, lowE6SSM_parameter_getter>
       coupling_monitor(tmp_model, parameter_getter);
 
-   coupling_monitor.run(low_scale, susy_scale, 100, true);
+   //coupling_monitor.run(low_scale, susy_scale, 100, true);
+   coupling_monitor.run(low_scale, 2.0e16, 1000, true);
    coupling_monitor.write_to_file(filename);
 }
 

### 2014-11-12 src/essmScanInputsGenerator.cpp

@@ -480,9 +480,9 @@ using namespace softsusy;
 	  At_ub = log(At_ub);
 	}
 
-      Alambda_lb = Alambda_vals(Alambda_indices(n));
-      Alambda_ub = Alambda_vals(Alambda_indices(n+1)-1);
-      Alambda_subnpts = Alambda_indices(n+1)-Alambda_indices(n);
+      Alambda_lb = Alambda_vals(Alambda_indices(j));
+      Alambda_ub = Alambda_vals(Alambda_indices(j+1)-1);
+      Alambda_subnpts = Alambda_indices(j+1)-Alambda_indices(j);
 
       if (alambdalogscan)
 	{

### 2014-11-12 paper/e6ssm-tuning-paper.tex
Fixed/clarified status of RGEs in code, added a reference to Martin's RGE paper, shortened bibtex entries for some of the XENON100 papers

@@
 To do so, we implemented the above expressions for computing the fine tuning in a modified version of the E$_6$SSM spectrum generator that was used in \cite{Athron:2013ipa}.
-In order to include effects coming from 2-loop RG running, the 2-loop RGEs generated by SARAH \cite{Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta} and FlexibleSUSY \cite{Athron:2014yba} were used instead of the 1-loop results that had previously been implemented.
-The CP-even Higgs masses are calculated including the leading 1-loop effective potential contributions given in \cite{Athron:2009bs}.
+This code implemented 2-loop RGEs for all parameters except the soft scalar masses.
+In order to properly include the fine tuning impact of the $SU(3)$ gaugino soft mass $M_3$, we have extended the original code to make use of the 2-loop RGEs generated by SARAH \cite{Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta} and FlexibleSUSY \cite{Athron:2014yba}.
+The CP-even Higgs masses are calculated including the leading 1-loop effective potential contributions given in \cite{Athron:2009bs} and the leading 2-loop contributions.
 To scan over the MSSM parameter space, the equivalent MSSM fine tuning expressions were implemented into a modifed version of SOFTSUSY 3.3.10 \cite{Allanach:2001kg,Allanach:2013kza}.
@@
 With the exception of the stop mixing $A_t$, which was logarithmically scanned, all parameters were linearly scanned.
-In order to ensure the validity of the approximate RGE solutions, the input scale $M_X$ was set to $M_X=20$ TeV for both the MSSM and the $E_6$ models.
+All other parameters were decoupled by setting the remaining soft masses to values of $5$ TeV, while the first and second generation Yukawa couplings and their associated soft trilinears were taken to vanish.
+The $U(1)$ gaugino soft mass $M_1$ was fixed to $M_1=300$ GeV, and we fix $M_3=2000$ GeV.
+The input scale $M_X$ was set to $M_X=20$ TeV for both the MSSM and the $E_6$ models.
 Finally, the fine tuning was evaluated at the scale $Q=M_{\textrm{SUSY}}=\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop masses evaluated at $Q=M_{\textrm{SUSY}}$.
@@
 % to the RGE solutions.
+Provided that one does not run over the too large a range of scales, the solutions to the
+RG equations for a model can be reasonably well approximated by a Taylor series, Eq. (\ref{eq:rgeapproxsoln}).
+Computing the first few terms of the series requires only the 1- and 2-loop RGEs, which are well known for
+the MSSM and may be obtained from general results \cite{Martin:1993zk} for other models.
 

### 2014-11-12 paper/e6ssm-tuning-paper.tex
Added MSSM RGE approximate solutions to appendix

@@
 \newcommand{\SuperField}[1]{\hat{#1}}
-
+\allowdisplaybreaks
 %\nofiles
@@
 Computing the first few terms of the series requires only the 1- and 2-loop RGEs, which are well known for
-the MSSM and may be obtained from general results \cite{Martin:1993zk} for other models.
+the MSSM and may be obtained from general results \cite{Martin:1993zk} for other models. To calculate the fine
+tuning it is necessary to expand out all of the parameters appearing in the EWSB conditions in terms
+of the high scale parameters.\\ \\
+In the MSSM, the relevant parameters are $\mu$, $B$, $m_{H_u}^2$, $m_{H_d}^2$, $m_{Q3}^2$, $m_{u3}^2$ and $A_t$ when
+the 1-loop top and stop effective potential terms are included (as no dimensionless couplings are varied
+in the fine tuning calculation, we neglect expanding the gauge and Yukawa couplings). For a parameter $p$, the series expansion
+Eq. (\ref{eq:rgeapproxsoln}) reads
+\begin{equation*}
+q(Q)=q(M_X)+\int_0^t q(t')\;\textrm{d}t'\approx q(M_X)+\frac{t}{16\pi^2}\left ( \beta_q^{(1)}+\frac{\beta_q^{(2)}}{16\pi^2}\right )+\frac{t^2}{(16\pi^2)^2}b_q^{(2)}(M_X),
+\end{equation*}
+where we have for convenience defined
+\begin{equation*}
+b_q^{(2)}(M_X)=\frac{1}{2!}\left [ \sum_{q_k}\beta_{q_k}^{(1)}\frac{\partial \beta_q}{\partial q_k}\right ]_{M_X}
+\end{equation*}
+and the notation $[\ldots]_Q$ indicates that everything within the brackets is evaluated at the scale $Q$. It is straightforward 
+to get the explicit series expansions for the MSSM parameters listed above. Due to the smallness of the first and second
+generation Yukawa couplings, we neglect them in our calculations. Similarly we neglect the corresponding soft SUSY breaking 
+trilinears. Additionally, all soft mass matrices are assumed diagonal, and the gaugino masses are taken to be real.
+For the MSSM, we then obtain the following results. For the parameter $\mu$, one has the coefficients
+\begin{subequations}\label{eq:mubetas}
+\begin{align}
+\beta_\mu^{(1)}&=\mu\left ( 3y_t^2+3y_b^2+y_\tau^2-3g_2^2-\frac{3}{5}g_1^2\right ),\label{eq:mubeta1}\\
+\beta_\mu^{(2)}&=\mu \bigg ( -9y_t^4-9y_b^4-6y_t^2y_b^2-3y_\tau^4+16g_3^2y_t^2+\frac{4}{5}g_1^2y_t^2+16g_3^2y_b^2-\frac{2}{5}g_1^2y_b^2\nonumber\\
+&\qquad{}+\frac{6}{5}g_1^2y_\tau^2+\frac{15}{2}g_2^4+\frac{9}{5}g_1^2g_2^2+\frac{207}{50}g_1^4\bigg ),\label{eq:mubeta2}\\
+b_\mu^{(2)}&=\frac{\mu}{2}\Bigg [ 45y_t^4+45y_b^4+9y_\tau^2+30y_t^2y_b^2+6y_t^2y_\tau^2+18y_b^2y_\tau^2-32g_3^2(y_t^2+y_b^2)\nonumber\\
+&\quad{}-12g_2^2(3y_t^2+3y_b^2+y_\tau^2)-\frac{4}{5}g_1^2(11y_t^2+8y_b^2+6y_\tau^2)+3g_2^4-\frac{189}{25}g_1^4+\frac{18}{5}g_1^2g_2^2\Bigg ].\label{eq:mub2}
+\end{align}
+\end{subequations}
+The coefficients for $B$ are 
+\begin{subequations}\label{eq:Bbetas}
+\begin{align}
+\beta_B^{(1)}&=6y_t^2A_t+6y_b^2A_b+2y_\tau^2A_\tau+6g_2^2M_2+\frac{6}{5}g_1^2M_1,\label{eq:Bbeta1}\\
+\beta_B^{(2)}&=-36y_t^4A_t-36y_b^4A_b-12y_\tau^4A_\tau-12y_t^2y_b^2(A_t+A_b)+32g_3^2y_t^2(A_t-M_3)\nonumber\\
+&\quad{}+32g_3^2y_b^2(A_b-M_3)+\frac{8}{5}g_1^2y_t^2(A_t-M_1)-\frac{4}{5}g_1^2y_b^2(A_b-M_1)+\frac{12}{5}g_1^2y_\tau^2(A_\tau-M_1)\nonumber\\
+&\quad{}-30g_2^4M_2-\frac{18}{5}g_1^2g_2^2(M_1+M_2)-\frac{414}{25}g_1^4M_1,\label{eq:Bbeta2}\\
+b_B^{(2)}&=72y_t^4A_t+72y_b^4A_b+16y_\tau^4A_\tau+12y_t^2y_b^2(A_t+A_b)+12y_\tau^2y_b^2(A_b+A_\tau)\nonumber\\
+&\quad{}-32g_3^2y_t^2(A_t-M_3)-32g_3^2y_b^2(A_b-M_3)\nonumber\\
+&\quad{}-18g_2^2y_t^2(A_t-M_2)-18g_2^2y_b^2(A_b-M_2)-6g_2^2y_\tau^2(A_\tau-M_2)\nonumber\\
+&\quad{}-\frac{26}{5}g_1^2y_t^2(A_t-M_1)-\frac{14}{5}g_1^2y_b^2(A_b-M_1)-\frac{18}{5}g_1^2y_\tau^2(A_\tau-M_1)\nonumber\\
+&\quad{}+12g_2^4M_2+\frac{396}{25}g_1^4M_1.\label{eq:Bb2}
+\end{align}
+\end{subequations}
+The coefficients for $m_{H_d}^2$ and $m_{H_u}^2$ are 
+\begin{subequations}\label{eq:mHd2Betas}
+\begin{align}
+\beta_{m_{H_d}^2}^{(1)}&=6y_b^2\left (m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2 \right )+2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+A_\tau^2\right )\nonumber\\
+&\quad{}-6g_2^2M_2^2-\frac{3}{5}g_1^2\left ( \mathcal{S}+2M_1^2\right ),\label{eq:mHd2beta1}\\
+\beta_{m_{H_d}^2}^{(2)}&=-36y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
+&\quad{}-6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
+&\quad{}-12y_\tau^4\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2A_\tau^2\right )\nonumber\\
+&\quad{}+32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_3A_b+2M_3^2\right )\nonumber\\
+&\quad{}+\frac{6}{5}g_1^2y_t^2\left ( 3m_{H_u}^2+m_{Q3}^2-4m_{u3}^2\right )\nonumber\\
+&\quad{}-\frac{2}{5}g_1^2y_b^2\left ( 11m_{H_d}^2-m_{Q3}^2-4m_{d3}^2+2A_b^2-4M_1A_b+4M_1^2\right )\nonumber\\
+&\quad{}+\frac{6}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+4m_{e3}^2+2A_\tau^2-4M_1A_\tau+4M_1^2\right )\nonumber\\
+&\quad{}-\frac{16}{5}g_3^2g_1^2\left (\sum_{i=1}^3 m_{Qi}^2-2m_{ui}^2+m_{di}^2 \right )\nonumber\\
+&\quad{}+3g_2^4\left ( 11M_2^2+m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3 [3m_{Qi}^2+m_{Li}^2]\right )\nonumber\\
+&\quad{}+\frac{9}{5}g_1^2g_2^2\left ( 2M_1^2+2M_2^2+2M_1M_2-m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3[m_{Li}^2-m_{Qi}^2]\right )\nonumber\\
+&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_d}^2+\sum_{i=1}^3[18m_{Li}^2+2m_{Qi}^2+56m_{ui}^2+2m_{di}^2-18m_{ei}^2]\right ),\label{eq:mHd2beta2}\\
+b_{m_{H_d}^2}^{(2)}&=72y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
+&\quad{}+6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
+&\quad{}+12y_\tau^2y_b^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{d3}^2+m_{L3}^2+m_{e3}^2+(A_\tau+A_b)^2\right )\nonumber\\
+&\quad{}+16y_\tau^4\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2A_\tau^2\right )\nonumber\\
+&\quad{}-32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_3A_b+2M_3^2\right )\nonumber\\
+&\quad{}-18g_2^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_2A_b+2M_2^2\right )\nonumber\\
+&\quad{}-6g_2^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+A_\tau^2-2M_2A_\tau+2M_2^2\right )\nonumber\\
+&\quad{}-\frac{14}{5}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_1A_b+2M_1^2\right )\nonumber\\
+&\quad{}-\frac{18}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+A_\tau^2-2M_1A_\tau+2M_1^2\right )\nonumber\\
+&\quad{}-18g_2^4M_2^2-\frac{198}{25}g_1^4\left ( \mathcal{S}+3M_1^2\right ),\label{eq:mHd2b2}
+\end{align}
+\end{subequations}
+\begin{subequations}\label{eq:mHu2Betas}
+\begin{align}
+\beta_{m_{H_u}^2}^{(1)}&=6y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-6g_2^2M_2^2+\frac{3}{5}g_1^2\left ( \mathcal{S}-2M_1^2\right ),\label{eq:mHu2beta1}\\
+\beta_{m_{H_u}^2}^{(2)}&=-36y_t^4(m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2)\nonumber\\
+&\quad{}-6y_t^2y_b^2(m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2)\nonumber\\
+&\quad{}+32g_3^2y_t^2(m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2A_tM_3+2M_3^2)\nonumber\\
+&\quad{}+\frac{2}{5}g_1^2y_t^2(-5m_{H_u}^2+m_{Q3}^2+16m_{u3}^2+4A_t^2-8A_tM_1+8M_1^2)\nonumber\\
+&\quad{}+\frac{6}{5}g_1^2y_b^2(3m_{H_d}^2-m_{Q3}^2-2m_{d3}^2)+\frac{6}{5}g_1^2y_\tau^2(m_{H_d}^2+m_{L3}^2-2m_{e3}^2)\nonumber\\
+&\quad{}+\frac{16}{5}g_1^2g_3^2\left(\sum_{i=1}^3m_{Qi}^2-2m_{ui}^2+m_{di}^2\right )\nonumber\\
+&\quad{}+\frac{9}{5}g_1^2g_2^2\left ( 2M_2^2+2M_1^2+2M_1M_2+m_{H_u}^2-m_{H_d}^2+\sum_{i=1}^3m_{Qi}^2-m_{Li}^2\right )\nonumber\\
+&\quad{}+3g_2^4\left ( 11M_2^2+m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3[3m_{Qi}^2+m_{Li}^2]\right )\nonumber\\
+&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_u}^2+\sum_{i=1}^3[4m_{Qi}^2-8m_{ui}^2+10m_{di}^2+54m_{ei}^2]\right ),\label{eq:mHu2beta2}\\
+b_{m_{H_u}^2}^{(2)}&=72y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
+&\quad{}+6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
+&\quad{}-32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2A_tM_3+2M_3^2\right )\nonumber\\
+&\quad{}-18g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2A_tM_2+2M_2^2\right )\nonumber\\
+&\quad{}-\frac{26}{5}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2A_tM_1+2M_1^2\right )\nonumber\\
+&\quad{}+\frac{198}{25}g_1^4\left ( \mathcal{S}-3M_1^2\right )-18g_2^4M_2^2.\label{eq:mHu2b2}
+\end{align}
+\end{subequations}
+In these expressions the quantity $\mathcal{S}$ is defined by
+\begin{equation}\label{eq:gaugeBetaContribution}
+\mathcal{S}=m_{H_u}^2-m_{H_d}^2+\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2\right ).
+\end{equation}
+If additional loop corrections are included from the 1-loop effective potential, it is also
+necessary to construct the expansions for $m_{Q3}^2$, $m_{u3}^2$ and $A_t$. The coefficients for $m_{Q3}^2$ and
+$m_{u3}^2$ are
+\begin{subequations}\label{eq:mq32Betas}
+\begin{align}
+\beta_{m_{Q3}^2}^{(1)}&=2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )+2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2\right )\\
+&\quad{}-\frac{32}{3}g_3^2M_3^2-6g_2^2M_2^2+\frac{1}{5}g_1^2\left ( \mathcal{S}-\frac{2}{3}M_1^2\right ),\label{eq:mQ32beta1}\\
+\beta_{m_{Q3}^2}^{(2)}&=-20y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )-20y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
+&\quad{}-2y_\tau^2y_b^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{L3}^2+m_{d3}^2+m_{e3}^2+(A_b+A_\tau)^2\right )\nonumber\\
+&\quad{}+\frac{2}{5}g_1^2y_t^2\left ( m_{H_u}^2+3m_{Q3}^2+8m_{u3}^2+4A_t^2-8A_tM_1+8M_1^2\right )\nonumber\\
+&\quad{}+\frac{2}{5}g_1^2y_b^2\left ( 5m_{H_d}^2+m_{Q3}^2+2A_b^2-4A_bM_1+4M_1^2\right )\nonumber\\
+&\quad{}+\frac{2}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
+&\quad{}+\frac{16}{3}g_3^4\left ( \sum_{i=1}^3 \left [ 2m_{Qi}^2+m_{ui}^2+m_{di}^2\right ]-8M_3^2\right )\nonumber\\
+&\quad{}+32g_3^2g_2^2\left ( M_2^2+M_3^2+M_2M_3\right )\nonumber\\
+&\quad{}+\frac{16}{45}g_3^2g_1^2\left ( 3\sum_{i=1}^3\left [ m_{Qi}^2-2m_{ui}^2+m_{di}^2\right ]+2M_1^2+2M_3^2+2M_1M_3\right )\nonumber\\
+&\quad{}+3g_2^4\left ( m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3\left [ 3m_{Qi}^2+m_{Li}^2\right ]+11M_2^2\right )\nonumber\\
+&\quad{}+\frac{1}{5}g_1^2g_2^2\left ( 2M_1^2+2M_2^2+2M_1M_2+3m_{H_u}^2-3m_{H_d}^2+3\sum_{i=1}^3\left [ m_{Qi}^2-m_{Li}^2\right ]\right )\nonumber\\
+&\quad{}+\frac{1}{75}g_1^4\bigg ( 199M_1^2+12m_{H_u}^2-6m_{H_d}^2\nonumber\\
+&\qquad\qquad\qquad{}+\sum_{i=1}^3\left [ 2m_{Qi}^2-6m_{Li}^2-24m_{ui}^2+6m_{di}^2+42m_{ei}^2\right ]\bigg ),\label{eq:mQ32beta2}\\
+b_{m_{Q3}^2}^{(2)}&=24y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )+24y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
+&\quad{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
+&\quad{}+2y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{L3}^2+m_{d3}^2+m_{e3}^2+(A_b+A_\tau)^2\right )\nonumber\\
+&\quad{}-\frac{32}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_3A_t+2M_3^2\right )\nonumber\\
+&\quad{}-\frac{32}{3}g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_3A_b+2M_3^2\right )\nonumber\\
+&\quad{}-6g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_2A_t+2M_2^2\right )\nonumber\\
+&\quad{}-6g_2^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_2A_b+2M_2^2\right )\nonumber\\
+&\quad{}-\frac{26}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
+&\quad{}-\frac{14}{15}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_1A_b+2M_1^2\right )\nonumber\\
+&\quad{}+96g_3^4M_3^2-18g_2^4M_2^2+\frac{66}{25}g_1^4(\mathcal{S}-M_1^2),\label{eq:mQ32b2}
+\end{align}
+\end{subequations}
+\begin{subequations} \label{eq:mu32Betas}
+\begin{align}
+\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-\frac{32}{3}g_3^2M_3^2-\frac{4}{5}g_1^2\left ( \mathcal{S}+\frac{8}{3}M_1^2\right ),\label{eq:mu32beta1}\\
+\beta_{m_{u3}^2}^{(2)}&=-32y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
+&\quad{}-4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
+&\quad{}+12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_2A_t+2M_2^2\right )\nonumber\\
+&\quad{}-\frac{4}{5}g_1^2y_t^2\left ( 9m_{u3}^2-5m_{H_u}^2-m_{Q3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
+&\quad{}-\frac{8}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q3}^2-2m_{d3}^2\right )-\frac{8}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
+&\quad{}+\frac{16}{3}g_3^4\left ( \sum_{i=1}^3\left [2m_{Qi}^2+m_{ui}^2+m_{di}^2 \right ]-8M_3^2\right )\nonumber\\
+&\quad{}+\frac{64}{45}g_3^2g_1^2\left ( 8M_1^2+8M_3^2+8M_1M_3-3\sum_{i=1}^3\left [ m_{Qi}^2-2m_{ui}^2+m_{di}^2\right ]\right )\nonumber\\
+&\quad{}-\frac{12}{5}g_1^2g_2^2\left ( m_{H_u}^2-m_{H_d}^2+\sum_{i=1}^3\left [ m_{Qi}^2-m_{Li}^2\right ]\right )\nonumber\\
+&\quad{}+\frac{4}{75}g_1^4\left ( 856M_1^2+3m_{H_u}^2+21m_{H_d}^2+\sum_{i=1}^3\left [ 3m_{Qi}^2+21m_{Li}^2+64m_{ui}^2+4m_{di}^2-12m_{ei}^2\right ]\right ),\label{eq:mu32beta2}\\
+b_{m_{u3}^2}^{(2)}&=48y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
+&\quad{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
+&\quad{}-\frac{64}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_3A_t+2M_3^2\right )\nonumber\\
+&\quad{}-12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_2A_t+2M_2^2\right )\nonumber\\
+&\quad{}-\frac{52}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
+&\quad{}+96g_3^4M_3^2-\frac{264}{25}g_1^4\left ( \mathcal{S}+4M_1^2\right ).\label{eq:mu32b2}
+\end{align}
+\end{subequations}
+Finally, the coefficients for $A_t$ read
+\begin{subequations}\label{eq:AtBetas}
+\begin{align}
+\beta_{A_t}^{(1)}&=12y_t^2A_t+2y_b^2A_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1,\label{eq:Atbeta1}\\
+\beta_{A_t}^{(2)}&=-88y_t^4A_t-20y_b^4A_b-10y_t^2y_b^2(A_t+A_b)-2y_b^2y_\tau^2(A_b+A_\tau)\nonumber\\
+&\quad{}+32g_3^2y_t^2(A_t-M_3)+12g_2^2y_t^2(A_t-M_2)+\frac{12}{5}g_1^2y_t^2(A_t-M_1)+\frac{4}{5}g_1^2y_b^2(A_b-M_1)\nonumber\\
+& \quad{}+\frac{64}{9}g_3^4M_3-16g_3^2g_2^2(M_2+M_3)-\frac{272}{45}g_3^2g_1^2(M_1+M_3)-30g_2^4M_2\nonumber\\
+&\quad{}-2g_2^2g_1^2(M_1+M_2)-\frac{5486}{225}g_1^4M_1,\label{eq:Atbeta2}\\
+b_{A_t}^{(2)}&=144y_t^4A_t+24y_b^4A_b+14y_t^2y_b^2(A_t+A_b)+2y_b^2y_\tau^2(A_b+A_\tau)\nonumber\\
+&\quad{}-64g_3^2y_t^2(A_t-M_3)-36g_2^2y_t^2(A_t-M_2)-\frac{52}{5}g_1^2y_t^2(A_t-M_1)\nonumber\\
+&\quad{}-\frac{32}{3}g_3^2y_b^2(A_b-M_3)-6g_2^2y_b^2(A_b-M_2)-\frac{14}{15}g_1^2y_b^2(A_b-M_1)\nonumber\\
+&\quad{}-64g_3^4M_3+12g_2^4M_2+\frac{572}{25}g_1^4M_1.\label{eq:Atb2}
+\end{align}
+\end{subequations}
+It is then trivial to extract the relevant terms for the fine tuning calculation in the MSSM from these expressions.\\ \\
+In $U(1)$ extended models the 2-loop RGEs are lengthy even if $U(1)$ mixing effects are
+neglected. As for the MSSM, we present simplified expressions in which it is assumed that the first and 
+second generation Yukawas are zero along with the soft SUSY breaking trilinears.
 

### 2014-11-13 paper/e6ssm-tuning-paper.tex
Starting to add approximate RGE solutions for U(1) model

@@
 \begin{equation*}
-q(Q)=q(M_X)+\int_0^t q(t')\;\textrm{d}t'\approx q(M_X)+\frac{t}{16\pi^2}\left ( \beta_q^{(1)}+\frac{\beta_q^{(2)}}{16\pi^2}\right )+\frac{t^2}{(16\pi^2)^2}b_q^{(2)}(M_X),
+q(Q)=q(M_X)+\frac{t}{16\pi^2}\left ( \beta_q^{(1)}+\frac{\beta_q^{(2)}}{16\pi^2}\right )+\frac{t^2}{(16\pi^2)^2}b_q^{(2)}(M_X),
 \end{equation*}
@@
 For the MSSM, we then obtain the following results. For the parameter $\mu$, one has the coefficients
-\begin{subequations}\label{eq:mubetas}
+\begin{subequations}\label{eq:MSSMmubetas}
 \begin{align}
-\beta_\mu^{(1)}&=\mu\left ( 3y_t^2+3y_b^2+y_\tau^2-3g_2^2-\frac{3}{5}g_1^2\right ),\label{eq:mubeta1}\\
+\beta_\mu^{(1)}&=\mu\left ( 3y_t^2+3y_b^2+y_\tau^2-3g_2^2-\frac{3}{5}g_1^2\right ),\label{eq:MSSMmubeta1}\\
 \beta_\mu^{(2)}&=\mu \bigg ( -9y_t^4-9y_b^4-6y_t^2y_b^2-3y_\tau^4+16g_3^2y_t^2+\frac{4}{5}g_1^2y_t^2+16g_3^2y_b^2-\frac{2}{5}g_1^2y_b^2\nonumber\\
-&\qquad{}+\frac{6}{5}g_1^2y_\tau^2+\frac{15}{2}g_2^4+\frac{9}{5}g_1^2g_2^2+\frac{207}{50}g_1^4\bigg ),\label{eq:mubeta2}\\
+&\qquad{}+\frac{6}{5}g_1^2y_\tau^2+\frac{15}{2}g_2^4+\frac{9}{5}g_1^2g_2^2+\frac{207}{50}g_1^4\bigg ),\label{eq:MSSMmubeta2}\\
 b_\mu^{(2)}&=\frac{\mu}{2}\Bigg [ 45y_t^4+45y_b^4+9y_\tau^2+30y_t^2y_b^2+6y_t^2y_\tau^2+18y_b^2y_\tau^2-32g_3^2(y_t^2+y_b^2)\nonumber\\
-&\quad{}-12g_2^2(3y_t^2+3y_b^2+y_\tau^2)-\frac{4}{5}g_1^2(11y_t^2+8y_b^2+6y_\tau^2)+3g_2^4-\frac{189}{25}g_1^4+\frac{18}{5}g_1^2g_2^2\Bigg ].\label{eq:mub2}
+&\quad{}-12g_2^2(3y_t^2+3y_b^2+y_\tau^2)-\frac{4}{5}g_1^2(11y_t^2+8y_b^2+6y_\tau^2)+3g_2^4-\frac{189}{25}g_1^4+\frac{18}{5}g_1^2g_2^2\Bigg ].\label{eq:MSSMmub2}
 \end{align}
@@
 The coefficients for $B$ are 
-\begin{subequations}\label{eq:Bbetas}
+\begin{subequations}\label{eq:MSSMBbetas}
 \begin{align}
-\beta_B^{(1)}&=6y_t^2A_t+6y_b^2A_b+2y_\tau^2A_\tau+6g_2^2M_2+\frac{6}{5}g_1^2M_1,\label{eq:Bbeta1}\\
+\beta_B^{(1)}&=6y_t^2A_t+6y_b^2A_b+2y_\tau^2A_\tau+6g_2^2M_2+\frac{6}{5}g_1^2M_1,\label{eq:MSSMBbeta1}\\
 \beta_B^{(2)}&=-36y_t^4A_t-36y_b^4A_b-12y_\tau^4A_\tau-12y_t^2y_b^2(A_t+A_b)+32g_3^2y_t^2(A_t-M_3)\nonumber\\
 &\quad{}+32g_3^2y_b^2(A_b-M_3)+\frac{8}{5}g_1^2y_t^2(A_t-M_1)-\frac{4}{5}g_1^2y_b^2(A_b-M_1)+\frac{12}{5}g_1^2y_\tau^2(A_\tau-M_1)\nonumber\\
-&\quad{}-30g_2^4M_2-\frac{18}{5}g_1^2g_2^2(M_1+M_2)-\frac{414}{25}g_1^4M_1,\label{eq:Bbeta2}\\
+&\quad{}-30g_2^4M_2-\frac{18}{5}g_1^2g_2^2(M_1+M_2)-\frac{414}{25}g_1^4M_1,\label{eq:MSSMBbeta2}\\
 b_B^{(2)}&=72y_t^4A_t+72y_b^4A_b+16y_\tau^4A_\tau+12y_t^2y_b^2(A_t+A_b)+12y_\tau^2y_b^2(A_b+A_\tau)\nonumber\\
@@
 &\quad{}-\frac{26}{5}g_1^2y_t^2(A_t-M_1)-\frac{14}{5}g_1^2y_b^2(A_b-M_1)-\frac{18}{5}g_1^2y_\tau^2(A_\tau-M_1)\nonumber\\
-&\quad{}+12g_2^4M_2+\frac{396}{25}g_1^4M_1.\label{eq:Bb2}
+&\quad{}+12g_2^4M_2+\frac{396}{25}g_1^4M_1.\label{eq:MSSMBb2}
 \end{align}
@@
 The coefficients for $m_{H_d}^2$ and $m_{H_u}^2$ are 
-\begin{subequations}\label{eq:mHd2Betas}
+\begin{subequations}\label{eq:MSSMmHd2Betas}
 \begin{align}
 \beta_{m_{H_d}^2}^{(1)}&=6y_b^2\left (m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2 \right )+2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+A_\tau^2\right )\nonumber\\
-&\quad{}-6g_2^2M_2^2-\frac{3}{5}g_1^2\left ( \mathcal{S}+2M_1^2\right ),\label{eq:mHd2beta1}\\
+&\quad{}-6g_2^2M_2^2-\frac{3}{5}g_1^2\left ( \mathcal{S}+2M_1^2\right ),\label{eq:MSSMmHd2beta1}\\
 \beta_{m_{H_d}^2}^{(2)}&=-36y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
@@
 &\quad{}+\frac{9}{5}g_1^2g_2^2\left ( 2M_1^2+2M_2^2+2M_1M_2-m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3[m_{Li}^2-m_{Qi}^2]\right )\nonumber\\
-&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_d}^2+\sum_{i=1}^3[18m_{Li}^2+2m_{Qi}^2+56m_{ui}^2+2m_{di}^2-18m_{ei}^2]\right ),\label{eq:mHd2beta2}\\
+&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_d}^2+\sum_{i=1}^3[18m_{Li}^2+2m_{Qi}^2+56m_{ui}^2+2m_{di}^2-18m_{ei}^2]\right ),\label{eq:MSSMmHd2beta2}\\
 b_{m_{H_d}^2}^{(2)}&=72y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
@@
 &\quad{}-\frac{18}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+A_\tau^2-2M_1A_\tau+2M_1^2\right )\nonumber\\
-&\quad{}-18g_2^4M_2^2-\frac{198}{25}g_1^4\left ( \mathcal{S}+3M_1^2\right ),\label{eq:mHd2b2}
+&\quad{}-18g_2^4M_2^2-\frac{198}{25}g_1^4\left ( \mathcal{S}+3M_1^2\right ),\label{eq:MSSMmHd2b2}
 \end{align}
 \end{subequations}
-\begin{subequations}\label{eq:mHu2Betas}
+\begin{subequations}\label{eq:MSSMmHu2Betas}
 \begin{align}
-\beta_{m_{H_u}^2}^{(1)}&=6y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-6g_2^2M_2^2+\frac{3}{5}g_1^2\left ( \mathcal{S}-2M_1^2\right ),\label{eq:mHu2beta1}\\
+\beta_{m_{H_u}^2}^{(1)}&=6y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-6g_2^2M_2^2+\frac{3}{5}g_1^2\left ( \mathcal{S}-2M_1^2\right ),\label{eq:MSSMmHu2beta1}\\
 \beta_{m_{H_u}^2}^{(2)}&=-36y_t^4(m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2)\nonumber\\
@@
 &\quad{}+3g_2^4\left ( 11M_2^2+m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3[3m_{Qi}^2+m_{Li}^2]\right )\nonumber\\
-&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_u}^2+\sum_{i=1}^3[4m_{Qi}^2-8m_{ui}^2+10m_{di}^2+54m_{ei}^2]\right ),\label{eq:mHu2beta2}\\
+&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_u}^2+\sum_{i=1}^3[4m_{Qi}^2-8m_{ui}^2+10m_{di}^2+54m_{ei}^2]\right ),\label{eq:MSSMmHu2beta2}\\
 b_{m_{H_u}^2}^{(2)}&=72y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
@@
 &\quad{}-\frac{26}{5}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2A_tM_1+2M_1^2\right )\nonumber\\
-&\quad{}+\frac{198}{25}g_1^4\left ( \mathcal{S}-3M_1^2\right )-18g_2^4M_2^2.\label{eq:mHu2b2}
+&\quad{}+\frac{198}{25}g_1^4\left ( \mathcal{S}-3M_1^2\right )-18g_2^4M_2^2.\label{eq:MSSMmHu2b2}
 \end{align}
@@
 In these expressions the quantity $\mathcal{S}$ is defined by
-\begin{equation}\label{eq:gaugeBetaContribution}
+\begin{equation}\label{eq:MSSMgaugeBetaContribution}
 \mathcal{S}=m_{H_u}^2-m_{H_d}^2+\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2\right ).
@@
 $m_{u3}^2$ are
-\begin{subequations}\label{eq:mq32Betas}
+\begin{subequations}\label{eq:MSSMmq32Betas}
 \begin{align}
 \beta_{m_{Q3}^2}^{(1)}&=2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )+2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2\right )\\
-&\quad{}-\frac{32}{3}g_3^2M_3^2-6g_2^2M_2^2+\frac{1}{5}g_1^2\left ( \mathcal{S}-\frac{2}{3}M_1^2\right ),\label{eq:mQ32beta1}\\
+&\quad{}-\frac{32}{3}g_3^2M_3^2-6g_2^2M_2^2+\frac{1}{5}g_1^2\left ( \mathcal{S}-\frac{2}{3}M_1^2\right ),\label{eq:MSSMmQ32beta1}\\
 \beta_{m_{Q3}^2}^{(2)}&=-20y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )-20y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
@@
 &\quad{}+\frac{1}{75}g_1^4\bigg ( 199M_1^2+12m_{H_u}^2-6m_{H_d}^2\nonumber\\
-&\qquad\qquad\qquad{}+\sum_{i=1}^3\left [ 2m_{Qi}^2-6m_{Li}^2-24m_{ui}^2+6m_{di}^2+42m_{ei}^2\right ]\bigg ),\label{eq:mQ32beta2}\\
+&\qquad\qquad\qquad{}+\sum_{i=1}^3\left [ 2m_{Qi}^2-6m_{Li}^2-24m_{ui}^2+6m_{di}^2+42m_{ei}^2\right ]\bigg ),\label{eq:MSSMmQ32beta2}\\
 b_{m_{Q3}^2}^{(2)}&=24y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )+24y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
@@
 &\quad{}-\frac{14}{15}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_1A_b+2M_1^2\right )\nonumber\\
-&\quad{}+96g_3^4M_3^2-18g_2^4M_2^2+\frac{66}{25}g_1^4(\mathcal{S}-M_1^2),\label{eq:mQ32b2}
+&\quad{}+96g_3^4M_3^2-18g_2^4M_2^2+\frac{66}{25}g_1^4(\mathcal{S}-M_1^2),\label{eq:MSSMmQ32b2}
 \end{align}
 \end{subequations}
-\begin{subequations} \label{eq:mu32Betas}
+\begin{subequations} \label{eq:MSSMmu32Betas}
 \begin{align}
-\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-\frac{32}{3}g_3^2M_3^2-\frac{4}{5}g_1^2\left ( \mathcal{S}+\frac{8}{3}M_1^2\right ),\label{eq:mu32beta1}\\
+\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-\frac{32}{3}g_3^2M_3^2-\frac{4}{5}g_1^2\left ( \mathcal{S}+\frac{8}{3}M_1^2\right ),\label{eq:MSSMmu32beta1}\\
 \beta_{m_{u3}^2}^{(2)}&=-32y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
@@
 &\quad{}-\frac{12}{5}g_1^2g_2^2\left ( m_{H_u}^2-m_{H_d}^2+\sum_{i=1}^3\left [ m_{Qi}^2-m_{Li}^2\right ]\right )\nonumber\\
-&\quad{}+\frac{4}{75}g_1^4\left ( 856M_1^2+3m_{H_u}^2+21m_{H_d}^2+\sum_{i=1}^3\left [ 3m_{Qi}^2+21m_{Li}^2+64m_{ui}^2+4m_{di}^2-12m_{ei}^2\right ]\right ),\label{eq:mu32beta2}\\
+&\quad{}+\frac{4}{75}g_1^4\left ( 856M_1^2+3m_{H_u}^2+21m_{H_d}^2+\sum_{i=1}^3\left [ 3m_{Qi}^2+21m_{Li}^2+64m_{ui}^2+4m_{di}^2-12m_{ei}^2\right ]\right ),\label{eq:MSSMmu32beta2}\\
 b_{m_{u3}^2}^{(2)}&=48y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
@@
 &\quad{}-\frac{52}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
-&\quad{}+96g_3^4M_3^2-\frac{264}{25}g_1^4\left ( \mathcal{S}+4M_1^2\right ).\label{eq:mu32b2}
+&\quad{}+96g_3^4M_3^2-\frac{264}{25}g_1^4\left ( \mathcal{S}+4M_1^2\right ).\label{eq:MSSMmu32b2}
 \end{align}
@@
 Finally, the coefficients for $A_t$ read
-\begin{subequations}\label{eq:AtBetas}
+\begin{subequations}\label{eq:MSSMAtBetas}
 \begin{align}
-\beta_{A_t}^{(1)}&=12y_t^2A_t+2y_b^2A_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1,\label{eq:Atbeta1}\\
+\beta_{A_t}^{(1)}&=12y_t^2A_t+2y_b^2A_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1,\label{eq:MSSMAtbeta1}\\
 \beta_{A_t}^{(2)}&=-88y_t^4A_t-20y_b^4A_b-10y_t^2y_b^2(A_t+A_b)-2y_b^2y_\tau^2(A_b+A_\tau)\nonumber\\
@@
 & \quad{}+\frac{64}{9}g_3^4M_3-16g_3^2g_2^2(M_2+M_3)-\frac{272}{45}g_3^2g_1^2(M_1+M_3)-30g_2^4M_2\nonumber\\
-&\quad{}-2g_2^2g_1^2(M_1+M_2)-\frac{5486}{225}g_1^4M_1,\label{eq:Atbeta2}\\
+&\quad{}-2g_2^2g_1^2(M_1+M_2)-\frac{5486}{225}g_1^4M_1,\label{eq:MSSMAtbeta2}\\
 b_{A_t}^{(2)}&=144y_t^4A_t+24y_b^4A_b+14y_t^2y_b^2(A_t+A_b)+2y_b^2y_\tau^2(A_b+A_\tau)\nonumber\\
@@
 &\quad{}-\frac{32}{3}g_3^2y_b^2(A_b-M_3)-6g_2^2y_b^2(A_b-M_2)-\frac{14}{15}g_1^2y_b^2(A_b-M_1)\nonumber\\
-&\quad{}-64g_3^4M_3+12g_2^4M_2+\frac{572}{25}g_1^4M_1.\label{eq:Atb2}
+&\quad{}-64g_3^4M_3+12g_2^4M_2+\frac{572}{25}g_1^4M_1.\label{eq:MSSMAtb2}
 \end{align}
@@
 It is then trivial to extract the relevant terms for the fine tuning calculation in the MSSM from these expressions.\\ \\
-In $U(1)$ extended models the 2-loop RGEs are lengthy even if $U(1)$ mixing effects are
+In $U(1)$ extended models the 2-loop RGEs are somewhat more lengthy even if $U(1)$ mixing effects are
 neglected. As for the MSSM, we present simplified expressions in which it is assumed that the first and 
-second generation Yukawas are zero along with the soft SUSY breaking trilinears.
-
+second generation Yukawas are zero along with the soft SUSY breaking trilinears. At tree level in the EWSB conditions
+the parameters that must be expanded are $\lambda$, $A_\lambda$, $m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and $g_1'$.
+The coefficients in the expansion of $\lambda$ may be written
+\begin{subequations}\label{eq:USSMLambdaBetas}
+\begin{align}
+\beta_{\lambda}^{(1)}&=\lambda\Big (2\lambda^2+2\Sigma_\lambda +3\Sigma_\kappa+ 3y_t^2 + 3y_b^2 + y_\tau^2-\frac{3}{5}g_1^2-3g_2^2-2g_1'^2\left (\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\Big ), \label{eq:USSMLambdabeta1}
+\beta_{\lambda}^{(2)}&=\lambda
+\end{align}
+\end{subequations}
+where
+\begin{equation*}
+\Sigma_\lambda=\lambda_1^2+\lambda_2^2+\lambda_3^2,\qquad \Sigma_\kappa=\kappa_1^2+\kappa_2^2+\kappa_3^2.
+\end{equation*}
 % NB before submission replace this with a copy-paste of the bbl file?

### 2014-12-02 fs-spectrum/models/lowE6SSM/full_tuning_scan_lowE6SSM.cpp
Fixed wrong beta loop order in check scan

@@ -366,7 +366,7 @@ int main()
          tuning_calc.set_tuning_scale(Sqrt(model.get_MSu()(0) * model.get_MSu()(1)));
          tuning_calc.set_input_scale(mx);
          tuning_calc.set_tuning_ewsb_loop_order(1);
-         tuning_calc.set_tuning_beta_loop_order(1);
+         tuning_calc.set_tuning_beta_loop_order(2);
          try {
             tuning_problem = tuning_calc.calculate_fine_tunings_approximately();
          } catch (const std::string & a) {

### 2014-12-02 fs-spectrum/models/lowE6SSM/run_lowE6SSM.cpp

@@ -95,7 +95,7 @@ int main(int argc, const char* argv[])
       = spectrum_generator.get_model();
    const Problems<lowE6SSM_info::NUMBER_OF_PARTICLES>& problems
       = spectrum_generator.get_problems();
-
+   
    // output
    slha_io.set_spinfo(problems);
    slha_io.set_sminputs(oneset);

### 2014-12-02 paper/e6ssm-tuning-paper.tex
Removed unfinished equation so that it isn't forgotten about and left unfinished
added recent baryogensis paper.
Fixed minor typos

@@
 mechanism and the baryon asymmetry in the universe via leptogenesis
-\cite{Hambye:2000bn,King:2008qb, King:2008gw}.
+\cite{Hambye:2000bn,King:2008qb, King:2008gw}.  Recently it has also been studied in the context of electroweak baryogenesis \cite{Chao:2014hya}.
 
@@
 In particular, recent experimental limits \cite{Aad:2014cka} require that the $Z'$ mass be large, with bounds of $M_{Z'}\gtrsim 2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim 2.62$ TeV in $U(1)_\chi$ models.
-To satisfy these limits typically requires large values of $s$, for example $s\gtrsim 6$ TeV is required in the E$_6$SSM with $U(1)'=U(1)_N$, so that $|D_{H_u}|,|D_{H_d}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq 0$.
+To satisfy these limits typically requires large values of the singlet VEV $s$.
+For example $s\gtrsim 6$ TeV is required in the E$_6$SSM with $U(1)'=U(1)_N$, so that $|D_{H_u}|,|D_{H_d}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq 0$.
 As a result the remaining terms on the right-hand side of Eq.
@@
 \subsection{\label{subsec:tuningmeasure}The Fine Tuning Measure}
-To quantify the resulting fine tuning we apply the traditional Ellis-Barbieri-Giudice measure \cite{Ellis:1986yg,Barbieri:1987fn}.
+As stated above, in order to quantify the resulting fine tuning we apply the traditional Ellis-Barbieri-Giudice measure \cite{Ellis:1986yg,Barbieri:1987fn}.
 A specific model is characterised by a set of $n$ model parameters $\{p_i\}$ and is defined at some input scale $M_X$.
@@
 \end{equation}
-continue to hold under an arbitrary variation in a model parameters $p\rightarrow p+\delta p$, so that the variations $\delta f_i$ satisfy
+continue to hold under an arbitrary variation in a model parameter $p\rightarrow p+\delta p$, so that the variations $\delta f_i$ satisfy
 \begin{equation}\label{eq:EWSBvariations}
@@
 \beta_{\lambda}^{(1)}&=\lambda\Big (2\lambda^2+2\Sigma_\lambda +3\Sigma_\kappa+ 3y_t^2 + 3y_b^2 + y_\tau^2-\frac{3}{5}g_1^2-3g_2^2-2g_1'^2\left (\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\Big ), \label{eq:USSMLambdabeta1}
-\beta_{\lambda}^{(2)}&=\lambda
 \end{align}

### 2014-12-03 paper/e6ssm-tuning-paper.tex
Started adding master formula expressions to appendix

@@
 It may be written in the form
-\begin{equation}\label{eq:E6masterformula}
-\frac{\Delta_p}{2|p|}=\bigg|\tilde{\Delta}_\lambda\frac{\partial\lambda}{\partial p}+\tilde{\Delta}_{A_\lambda}\frac{\partial A_\lambda}{\partial p}+\tilde{\Delta}_{m_{H_d}^2}\frac{\partial m_{H_d}^2}{\partial p}+\tilde{\Delta}_{m_{H_u}^2}\frac{\partial m_{H_u}^2}{\partial p}+\tilde{\Delta}_{m_S^2}\frac{\partial m_S^2}{\partial p}\bigg|.
-\end{equation}
-Explicit expressions for the $\tilde{\Delta}_i$ appearing above are given in Appendix \ref{app:masterformula}.
-It should be noted that variations in the gauge couplings are neglected in Eq.
-(\ref{eq:E6masterformula}), so that the formula above is valid at the level of 1-loop RG running and provided that the gauge couplings are excluded from the set $\{p_i\}$.
-In general, any dimensionless SUSY parameters in $\{p_i\}$ will contribute to the running of the gauge couplings at 2-loops and so terms proportional to $\partial g_i /\partial p$ are also present.
-For dimensionless $p$, the resulting contributions are $\mathcal{O}(g_1^2p^2)$, $\mathcal{O}(g_1'^2p^2)$, $\mathcal{O}(g_2^2p^2)$ or higher order, and can therefore usually be safely neglected.\\ \\
+\be
+\Delta_p=|C|^{-1}\times \frac{|p|}{M_Z}\bigg|\sum_{q}\tilde{\Delta}_q\frac{\partial q}{\partial p}\bigg|,
+\label{eq:E6masterformula}
+\ee
+where the sum is over all low energy running parameters appearing in the tree level EWSB conditions, i.e.
+$q\in\{\lambda, A_\lambda, m_{H_d}^2,m_{H_u}^2,m_S^2,g_1,g_2,g_1'\}$.
+Explicit expressions for the function $C$ and the $\tilde{\Delta}_q$ appearing above are given in Appendix \ref{app:masterformula}.
+It should be noted that the effects of $U(1)$ mixing are neglected in deriving Eq.
+(\ref{eq:E6masterformula}).\\ \\
 Evaluating the fine tuning directly using a master formula approach rapidly becomes impractical, as a brief inspection of the expressions for the $\tilde{\Delta}_i$ should make clear.
@@
 % Tree level master formula for the E6SSM
+To write down the tree level master formula, it is convenient to define the quantities
+\begin{eqnarray}
+z_1 &=& \frac{\partial f_2}{\partial s}\frac{\partial f_3}{\partial \tan\beta}-\frac{\partial f_2}{\partial \tan\beta}\frac{\partial f_3}{\partial s}\nonumber\\
+z_2 &=& \frac{\partial f_3}{\partial s}\frac{\partial f_1}{\partial \tan\beta}-\frac{\partial f_3}{\partial \tan\beta}\frac{\partial f_1}{\partial s}\nonumber\\
+z_3 &=& \frac{\partial f_1}{\partial s}\frac{\partial f_2}{\partial \tan\beta}-\frac{\partial f_1}{\partial \tan\beta}\frac{\partial f_2}{\partial s}\nonumber,
+\end{eqnarray}
+with $f_1,f_2,f_3$ as given in Eq.
+(\ref{eq:E6EWSBConditions}).
+For a running parameter $q$ appearing in the tree level EWSB conditions, the corresponding contribution to the sensitivity coefficient may be written
+\be
+\tilde{\Delta}_q=z_1\frac{\partial f_1}{\partial q}+z_2\frac{\partial f_2}{\partial q}+z_3\frac{\partial f_3}{\partial q}.
+\label{eq:tuningContribution}
+\ee
+Similarly, the quantity $C$ appearing in Eq. (\ref{eq:E6masterformula}) is given by
+\be
+C=\frac{1}{2}\Big ( z_1\frac{\partial f_1}{\partial M_Z}+z_2\frac{\partial f_2}{\partial M_Z}+z_3\frac{\partial f_3}{\partial M_Z}\Big ).
+\label{eq:tuningDenominator}
+\ee
 \section{\label{app:rges}RGE Contributions}

### 2014-12-03 paper/e6ssm-tuning-paper.tex
Added more components of the tree level master formula to the appendix, added an extra pair of brackets and in-line equation, removed extra bracket in sentence, changed m_z --> M_Z for consistency with previous tuning paper

@@
 The Higgs causes a naturalness problem because at tree level it has an
-upper bound of the mass of the $Z$ boson, $m_Z$. The dominant higher
+upper bound of the mass of the $Z$ boson, $M_Z$. The dominant higher
 order corrections to the Higgs mass come from stops and to obtain a
@@
 (GUT) scale to the electroweak (EW) scale. This affects the SUSY
-prediction of the electroweak VEV, v, or $m_Z$.  This naturalness
+prediction of the electroweak VEV, $v$, or $M_Z$.  This naturalness
 problem motivates both further examination of non-minimal SUSY models
@@
 into $SU(5)$, gives $SO(10)\to SU(5)\times U(1)_{\chi}$ (this is
-reviewed in e.g.~\cite{Langacker:2008yv})). The extra $U(1)$ gauge symmetry at low energies should then be a linear combination of these in the $E_6$ inspired case,
+reviewed in e.g.~\cite{Langacker:2008yv}). The extra $U(1)$ gauge symmetry at low energies should then be a linear combination of these in the $E_6$ inspired case,
 \be
@@
 \caption{The $U(1)_Y$, $U(1)_\psi$, $U(1)_\chi$ and $U(1)_N$ charges of the chiral superfields in the $E_6$ model.
-The specific case of $U(1)_N$, corresponding to the E$_6$SSM, is obtained for $\theta_{E_6}=\arctan\sqrt{15}$.}
+The specific case of $U(1)_N$, corresponding to the E$_6$SSM, is obtained for $\theta=\arctan\sqrt{15}$.}
 \label{tab:E6charges}
@@
 
-Nonetheless while this model is very elegant so far, the  superpotential, \ref{Eq:e6-superpot} contains dangerous terms which can induce proton decay and lead to large flavour changing neutral currents (FCNCs).
+Nonetheless while this model is very elegant so far, the  superpotential, (\ref{Eq:e6-superpot}) contains dangerous terms which can induce proton decay and lead to large flavour changing neutral currents (FCNCs).
 There are a number of approaches to suppress these terms, involving the use of different discrete symmetries.
@@
 \end{eqnarray}
-with $f_1,f_2,f_3$ as given in Eq.
-(\ref{eq:E6EWSBConditions}).
+with $f_1,f_2,f_3$ as given in Eq. (\ref{eq:E6EWSBConditions}). Explicitly, we find that
+\begin{eqnarray*}
+z_1&=&%\frac{M_Z\cos^2\beta}{2\bar{g}^3}\Big [ 4M_Z^2\Big ( \sqrt{2}\lambda A_\lambda \cos\beta-2s(\lambda^2+g_1'^2\tilde{Q}_2\tild%e{Q}_S )\sin\beta\Big )\nonumber\\
+%&& \times \Big ( \sqrt{2}\lambda A_\lambda \cos 2\beta+g_1'^2(\tilde{Q}_1-\tilde{Q}_2)\tilde{Q}_Ss\sin 2\beta \Big )\Big ]
+\end{eqnarray*}
 For a running parameter $q$ appearing in the tree level EWSB conditions, the corresponding contribution to the sensitivity coefficient may be written 
@@
 \be
-C=\frac{1}{2}\Big ( z_1\frac{\partial f_1}{\partial M_Z}+z_2\frac{\partial f_2}{\partial M_Z}+z_3\frac{\partial f_3}{\partial M_Z}\Big ).
+C=\frac{1}{2}\left ( z_1\frac{\partial f_1}{\partial M_Z}+z_2\frac{\partial f_2}{\partial M_Z}+z_3\frac{\partial f_3}{\partial M_Z}\right ),
 \label{eq:tuningDenominator}
 \ee
+with 
+\ba
+\frac{\partial f_1}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\cos\beta\left ( m_{H_d}^2+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}\tilde{Q}_1\tilde{Q}_Ss^2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_1^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\sin\beta\nonumber \\
+&&+\frac{3M_Z^2}{\bar{g}}\,\cos\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\sin\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left(\tilde{Q}_1\tilde{Q}_2-\tilde{Q}_1^2\right )\right ],\nonumber\\
+\frac{\partial f_2}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\sin\beta\left ( m_{H_u^2}+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}\tilde{Q}_2\tilde{Q}_Ss^2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_2^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\cos\beta \nonumber\\
+&&-\frac{3M_Z^2}{\bar{g}}\,\sin\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\cos\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left ( \tilde{Q}_1\tilde{Q}_2-\tilde{Q_2}^2\right )\right ],\nonumber \\
+\frac{\partial f_3}{\partial M_Z}&=&\frac{4M_Z}{\bar{g}^2}\left [ \lambda^2s-\frac{\lambda A_\lambda}{\sqrt{2}}\,\sin 2\beta+g_1'^2\tilde{Q}_Ss\left ( \tilde{Q}_1\,\cos^2\beta+\tilde{Q}_2\,\sin^2\beta \right )\right ].\nonumber
+\ea
 \section{\label{app:rges}RGE Contributions}
@@
 % to the RGE solutions.
-Provided that one does not run over the too large a range of scales, the solutions to the
+Provided that one does not run over too large a range of scales, the solutions to the
 RG equations for a model can be reasonably well approximated by a Taylor series, Eq. (\ref{eq:rgeapproxsoln}).
@@
 \begin{equation*}
-b_q^{(2)}(M_X)=\frac{1}{2!}\left [ \sum_{q_k}\beta_{q_k}^{(1)}\frac{\partial \beta_q}{\partial q_k}\right ]_{M_X}
+b_q^{(2)}(M_X)=\frac{1}{2!}\left . \sum_{q_k}\beta_{q_k}^{(1)}\frac{\partial \beta_q}{\partial q_k}\right |_{M_X}
 \end{equation*}
-and the notation $[\ldots]_Q$ indicates that everything within the brackets is evaluated at the scale $Q$. It is straightforward 
-to get the explicit series expansions for the MSSM parameters listed above. Due to the smallness of the first and second
+It is straightforward to get the explicit series expansions for the MSSM parameters listed above. Due to the smallness of the first and second
 generation Yukawa couplings, we neglect them in our calculations. Similarly we neglect the corresponding soft SUSY breaking 

### 2014-12-04 paper/e6ssm-tuning-paper.tex
Added partial derivatives needed for master formula
Changed phrasing in some sentences

@@
 A master formula for the E$_6$SSM, obtained from the tree level scalar potential, was presented in \cite{Athron:2013ipa}.
-In order to derive the expression presented there, the fact that $s \gg v$ was made use of to neglect certain $\mathcal{O}(v^2)$ terms in the EWSB conditions, greatly simplifying the final result.
-% Important question:
-% Impact of varying charges, is it picked up by the approximate CE6SSM master formula?
-% e.g. how different are things in the limit Q_S --> 0?
-For the purposes of exploring a wider class of $E_6$ inspired models, we have derived the master formula without neglecting any $\mathcal{O}(v^2)$ terms.
+In order to derive the expression presented there, the fact that $s \gg v$ was made use of to neglect certain $O(v^2)$ terms in the EWSB conditions, greatly simplifying the final result.
+For the purposes of exploring a wider class of $E_6$ inspired models, we have rederived the master formula without neglecting any $O(v^2)$ terms.
 The more complete tree-level master formula is somewhat complicated.
@@
 $q\in\{\lambda, A_\lambda, m_{H_d}^2,m_{H_u}^2,m_S^2,g_1,g_2,g_1'\}$.
-Explicit expressions for the function $C$ and the $\tilde{\Delta}_q$ appearing above are given in Appendix \ref{app:masterformula}.
+Expressions for the quantity $C$ and the $\tilde{\Delta}_q$ appearing above are given in Appendix \ref{app:masterformula}.
 It should be noted that the effects of $U(1)$ mixing are neglected in deriving Eq.
 (\ref{eq:E6masterformula}).\\ \\
-Evaluating the fine tuning directly using a master formula approach rapidly becomes impractical, as a brief inspection of the expressions for the $\tilde{\Delta}_i$ should make clear.
-It is well known in the MSSM that radiative corrections can significantly change (indeed, reduce) the fine tuning \cite{Cassel:2010px}.
-It is therefore important when studying the fine tuning to include 1- and 2-loop corrections in the fine tuning measure.
+However, it is well known in the MSSM that radiative corrections can significantly change (indeed, reduce) the fine tuning \cite{Cassel:2010px}.
+It is therefore important when studying the fine tuning to include 1- and 2-loop corrections to the effective potential in the fine tuning measure.
 To do so it is most convenient to work in terms of the EWSB conditions Eq.
@@
 Radiative corrections may be easily incorporated by including the Coleman-Weinberg potential contributions in the EWSB conditions.\\ \\
-The most involved step in the process of getting $\Delta_p$ is evaluating the matrix containing the derivatives $\partial q_k/\partial p$.
-In general this must be done numerically, by evaluating the running using the 1- and 2-loop RGEs.
-This is an obstacle to doing large scans of the parameter space, as the process of numerically evaluating $n\times l$ derivatives is computationally expensive.
-In general, for example for models defined at the GUT scale, accurately calculating the fine tuning is better done by numerically differentiating $M_Z^2$ directly to reduce the number of derivatives that must be computed.
+Evaluating the derivatives $\partial q_k/\partial p$ must (in general) be done numerically, by numerically integrating the 2-loop RGEs.
+This is time consuming and presents an obstacle to doing large scans of the parameter space.
 For studying models defined at low energies, as we do here, we can take advantage of the fact that the amount of running involved is small.
@@
 To write down the tree level master formula, it is convenient to define the quantities
-\begin{eqnarray}
-z_1 &=& \frac{\partial f_2}{\partial s}\frac{\partial f_3}{\partial \tan\beta}-\frac{\partial f_2}{\partial \tan\beta}\frac{\partial f_3}{\partial s}\nonumber\\
-z_2 &=& \frac{\partial f_3}{\partial s}\frac{\partial f_1}{\partial \tan\beta}-\frac{\partial f_3}{\partial \tan\beta}\frac{\partial f_1}{\partial s}\nonumber\\
-z_3 &=& \frac{\partial f_1}{\partial s}\frac{\partial f_2}{\partial \tan\beta}-\frac{\partial f_1}{\partial \tan\beta}\frac{\partial f_2}{\partial s}\nonumber,
-\end{eqnarray}
-with $f_1,f_2,f_3$ as given in Eq. (\ref{eq:E6EWSBConditions}). Explicitly, we find that
-\begin{eqnarray*}
-z_1&=&%\frac{M_Z\cos^2\beta}{2\bar{g}^3}\Big [ 4M_Z^2\Big ( \sqrt{2}\lambda A_\lambda \cos\beta-2s(\lambda^2+g_1'^2\tilde{Q}_2\tild%e{Q}_S )\sin\beta\Big )\nonumber\\
-%&& \times \Big ( \sqrt{2}\lambda A_\lambda \cos 2\beta+g_1'^2(\tilde{Q}_1-\tilde{Q}_2)\tilde{Q}_Ss\sin 2\beta \Big )\Big ]
-\end{eqnarray*}
-For a running parameter $q$ appearing in the tree level EWSB conditions, the corresponding contribution to the sensitivity coefficient may be written 
+\begin{equation}
+z_i =\epsilon_{ijk} \frac{\partial f_j}{\partial s}\frac{\partial f_k}{\partial \tan\beta}
+\label{eq:masterformulacoefficients}
+\end{equation}
+with $f_1,f_2,f_3$ as given in Eq. (\ref{eq:E6EWSBConditions}). The relevant partial derivatives are
+\ba
+\frac{\partial f_1}{\partial \tan\beta}&=&-\frac{2M_Z}{\bar{g}}\,\cos^2\beta\left \{ \frac{\lambda A_\lambda s}{\sqrt{2}}\,\cos\beta+\sin\beta \left [ m_{H_d}^2+\frac{s^2}{2}\left ( \lambda^2+g_1'^2\tilde{Q}_1\tilde{Q}_S \right )\right.\right.\nonumber\\
+&&\left.\left.+M_Z^2\left ( \frac{5}{2}-\frac{4\lambda^2}{\bar{g}^2}-\frac{4g_1'^2}{\bar{g}^2}\tilde{Q}_1\tilde{Q}_2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_1^2\right )\right ]+3M_Z^2\,\sin^3\beta\left [ \frac{2\lambda^2}{\bar{g}^2}-1\right.\right.\nonumber\\
+&&\left.\left.+\frac{2g_1'^2}{\bar{g}^2}\left ( \tilde{Q}_1\tilde{Q}_2-\tilde{Q}_1^2\right )\right ]\right \},\nonumber\\
+\frac{\partial f_1}{\partial s}&=&\frac{2M_Z}{\bar{g}}\left [ s\left ( \lambda^2+g_1'^2\tilde{Q}_1\tilde{Q}_S\right )\,\cos\beta-\frac{\lambda A_\lambda}{\sqrt{2}}\,\sin\beta \right ],\nonumber\\
+\frac{\partial f_2}{\partial \tan\beta}&=&\frac{2M_Z}{\bar{g}}\,\cos^2\beta\left \{ \frac{\lambda A_\lambda s}{\sqrt{2}}\,\sin\beta+\cos\beta\left [ m_{H_u}^2+\frac{s^2}{2}\left ( \lambda^2+g_1'^2\tilde{Q}_2\tilde{Q}_S \right )\right.\right.\nonumber\\
+&&\left.+M_Z^2\left ( \frac{5}{2}-\frac{4\lambda^2}{\bar{g}^2}-\frac{4g_1'^2}{\bar{g}^2}\tilde{Q}_1\tilde{Q}_2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_2^2\right )\right ]+3M_Z^2\,\cos^3\beta \left [ \frac{2\lambda^2}{\bar{g}^2}-1\right.\nonumber\\
+&&\left.\left.+\frac{2g_1'^2}{\bar{g}^2}\left ( \tilde{Q}_1\tilde{Q}_2-\tilde{Q}_2^2\right )\right ]\right \},\nonumber\\
+\frac{\partial f_2}{\partial s}&=&\frac{2M_Z}{\bar{g}}\left [ s\left ( \lambda^2+g_1'^2\tilde{Q}_2\tilde{Q}_S\right )\,\sin\beta-\frac{\lambda A_\lambda}{\sqrt{2}}\,\cos\beta\right ],\nonumber\\
+\frac{\partial f_3}{\partial \tan\beta}&=&\frac{2M_Z^2}{\bar{g}^2}\,\cos^2\beta\left [ g_1'^2\tilde{Q}_Ss\left ( \tilde{Q}_2-\tilde{Q}_1\right )\,\sin 2\beta-\sqrt{2}\lambda A_\lambda\,\cos 2\beta\right ],\nonumber\\
+\frac{\partial f_3}{\partial s}&=&m_S^2+\frac{2\lambda^2M_Z^2}{\bar{g}^2}+\frac{g_1'^2}{2}\tilde{Q}_S\left [\frac{4M_Z^2}{\bar{g}^2}\left ( \tilde{Q}_1\,\cos^2\beta+\tilde{Q}_2\,\sin^2\beta\right ) +3\tilde{Q}_S s^2\right ].\nonumber
+\ea
+For a running parameter $q$ appearing in the tree level EWSB conditions, the corresponding contribution to the sensitivity coefficient can then be written 
 \be
@@
 &&+\frac{3M_Z^2}{\bar{g}}\,\cos\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\sin\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left(\tilde{Q}_1\tilde{Q}_2-\tilde{Q}_1^2\right )\right ],\nonumber\\
-\frac{\partial f_2}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\sin\beta\left ( m_{H_u^2}+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}\tilde{Q}_2\tilde{Q}_Ss^2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_2^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\cos\beta \nonumber\\
+\frac{\partial f_2}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\sin\beta\left ( m_{H_u}^2+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}\tilde{Q}_2\tilde{Q}_Ss^2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_2^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\cos\beta \nonumber\\
 &&-\frac{3M_Z^2}{\bar{g}}\,\sin\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\cos\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left ( \tilde{Q}_1\tilde{Q}_2-\tilde{Q_2}^2\right )\right ],\nonumber \\

### 2014-12-16 paper/e6ssm-tuning-paper.tex
Removed MSSM betas since they are available elsewhere. Will still need U(1) extended betas, since in the cE6SSM the charges have not been left explicit

@@
 However, it is well known in the MSSM that radiative corrections can significantly change (indeed, reduce) the fine tuning \cite{Cassel:2010px}.
-It is therefore important when studying the fine tuning to include 1- and 2-loop corrections to the effective potential in the fine tuning measure.
+It is therefore important when studying the fine tuning to include one- and two-loop corrections to the effective potential in the fine tuning measure.
 To do so it is most convenient to work in terms of the EWSB conditions Eq.
@@
 Radiative corrections may be easily incorporated by including the Coleman-Weinberg potential contributions in the EWSB conditions.\\ \\
-Evaluating the derivatives $\partial q_k/\partial p$ must (in general) be done numerically, by numerically integrating the 2-loop RGEs.
+Evaluating the derivatives $\partial q_k/\partial p$ must (in general) be done by numerically integrating the two-loop RGEs.
 This is time consuming and presents an obstacle to doing large scans of the parameter space.
@@
 This makes it possible to use approximate analytic solutions to the RGEs that exhibit good accuracy over the range of scales considered.
-Given the 2-loop RG equation for a parameter $q$,
+Given the two-loop RG equation for a parameter $q$,
 \begin{equation}\label{eq:rge}
@@
 \end{align}
-Expanded to this order we obtain the leading log (LL) and next-to-LL (NLL) contributions at 2-loop order.
+Expanded to this order we obtain the leading log (LL) and next-to-LL (NLL) contributions at two-loop order.
 The $\mathcal{O}(t^2)$ terms not displayed above are formally of 3-loop order and are neglected.
-The derivative of the 1-loop $\beta$ function is given by
+The derivative of the one-loop $\beta$ function is given by
 \begin{equation}\label{eq:1loopbetaderivative}
@@
 To do so, we implemented the above expressions for computing the fine tuning in a modified version of the E$_6$SSM spectrum generator that was used in \cite{Athron:2013ipa}.
-This code implemented 2-loop RGEs for all parameters except the soft scalar masses.
-In order to properly include the fine tuning impact of the $SU(3)$ gaugino soft mass $M_3$, we have extended the original code to make use of the 2-loop RGEs generated by SARAH \cite{Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta} and FlexibleSUSY \cite{Athron:2014yba}.
-The CP-even Higgs masses are calculated including the leading 1-loop effective potential contributions given in \cite{Athron:2009bs} and the leading 2-loop contributions.
+This code implemented two-loop RGEs for all parameters except the soft scalar masses.
+In order to properly include the fine tuning impact of the $SU(3)$ gaugino soft mass $M_3$, we have extended the original code to make use of the two-loop RGEs generated by SARAH \cite{Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta} and FlexibleSUSY \cite{Athron:2014yba}.
+The CP-even Higgs masses are calculated including the leading one-loop effective potential contributions given in \cite{Athron:2009bs} and the leading two-loop contributions.
 To scan over the MSSM parameter space, the equivalent MSSM fine tuning expressions were implemented into a modifed version of SOFTSUSY 3.3.10 \cite{Allanach:2001kg,Allanach:2013kza}.
-For consistency with the results produced in the $E_6$ models, and for computational speed, for our main scans only the dominant 1- and 2-loop corrections to the CP-even Higgs masses were included.
+For consistency with the results produced in the $E_6$ models, and for computational speed, for our main scans only the dominant one- and two-loop corrections to the CP-even Higgs masses were included.
 The parameter ranges that were scanned over are presented in Table \ref{tab:scanranges}.
@@
 \ee
-Similarly, the quantity $C$ appearing in Eq. (\ref{eq:E6masterformula}) is given by
+It is straightforward to compute the appropriate derivatives directly from the EWSB conditions (\ref{eq:E6EWSBConditions}).
+Similarly, the quantity $C$ appearing in Eq.
+(\ref{eq:E6masterformula}) is given by
 \be
@@
 RG equations for a model can be reasonably well approximated by a Taylor series, Eq. (\ref{eq:rgeapproxsoln}). 
-Computing the first few terms of the series requires only the 1- and 2-loop RGEs, which are well known for
-the MSSM and may be obtained from general results \cite{Martin:1993zk} for other models. To calculate the fine
-tuning it is necessary to expand out all of the parameters appearing in the EWSB conditions in terms
-of the high scale parameters.\\ \\
-In the MSSM, the relevant parameters are $\mu$, $B$, $m_{H_u}^2$, $m_{H_d}^2$, $m_{Q3}^2$, $m_{u3}^2$ and $A_t$ when
-the 1-loop top and stop effective potential terms are included (as no dimensionless couplings are varied
-in the fine tuning calculation, we neglect expanding the gauge and Yukawa couplings). For a parameter $p$, the series expansion
-Eq. (\ref{eq:rgeapproxsoln}) reads
+For a parameter $p$, this reads
 \begin{equation*}
@@
 \begin{equation*}
-b_q^{(2)}(M_X)=\frac{1}{2!}\left . \sum_{q_k}\beta_{q_k}^{(1)}\frac{\partial \beta_q}{\partial q_k}\right |_{M_X}
+b_q^{(2)}(M_X)=\frac{1}{2!}\left . \sum_{q_k}\beta_{q_k}^{(1)}\frac{\partial \beta_q}{\partial q_k}\right |_{M_X}.
 \end{equation*}
-It is straightforward to get the explicit series expansions for the MSSM parameters listed above. Due to the smallness of the first and second
-generation Yukawa couplings, we neglect them in our calculations. Similarly we neglect the corresponding soft SUSY breaking 
-trilinears. Additionally, all soft mass matrices are assumed diagonal, and the gaugino masses are taken to be real.
-For the MSSM, we then obtain the following results. For the parameter $\mu$, one has the coefficients
-\begin{subequations}\label{eq:MSSMmubetas}
+We have constructed the necessary series solutions in both the MSSM and the $U(1)$ extended models.
+Due to the smallness of the first and second generation Yukawa couplings, we neglect them in our calculations.
+The corresponding soft SUSY breaking
+trilinears are likewise omitted. Additionally, all soft mass matrices are assumed diagonal, and the gaugino masses are taken to be real.\\ \\
+In the MSSM, the relevant parameters for the fine tuning calculation are $\mu$, $B$, $m_{H_u}^2$, $m_{H_d}^2$ at tree level.
+The one- and two-loop RGEs for these parameters may be found in \cite{Martin:1993zk}.
+The corresponding $O(t^2)$ contributions are
+\begin{subequations}\label{eq:MSSMTreeLevelCoeffs}
 \begin{align}
-\beta_\mu^{(1)}&=\mu\left ( 3y_t^2+3y_b^2+y_\tau^2-3g_2^2-\frac{3}{5}g_1^2\right ),\label{eq:MSSMmubeta1}\\
-\beta_\mu^{(2)}&=\mu \bigg ( -9y_t^4-9y_b^4-6y_t^2y_b^2-3y_\tau^4+16g_3^2y_t^2+\frac{4}{5}g_1^2y_t^2+16g_3^2y_b^2-\frac{2}{5}g_1^2y_b^2\nonumber\\
-&\qquad{}+\frac{6}{5}g_1^2y_\tau^2+\frac{15}{2}g_2^4+\frac{9}{5}g_1^2g_2^2+\frac{207}{50}g_1^4\bigg ),\label{eq:MSSMmubeta2}\\
 b_\mu^{(2)}&=\frac{\mu}{2}\Bigg [ 45y_t^4+45y_b^4+9y_\tau^2+30y_t^2y_b^2+6y_t^2y_\tau^2+18y_b^2y_\tau^2-32g_3^2(y_t^2+y_b^2)\nonumber\\
-&\quad{}-12g_2^2(3y_t^2+3y_b^2+y_\tau^2)-\frac{4}{5}g_1^2(11y_t^2+8y_b^2+6y_\tau^2)+3g_2^4-\frac{189}{25}g_1^4+\frac{18}{5}g_1^2g_2^2\Bigg ].\label{eq:MSSMmub2}
-\end{align}
-\end{subequations}
-The coefficients for $B$ are 
-\begin{subequations}\label{eq:MSSMBbetas}
-\begin{align}
-\beta_B^{(1)}&=6y_t^2A_t+6y_b^2A_b+2y_\tau^2A_\tau+6g_2^2M_2+\frac{6}{5}g_1^2M_1,\label{eq:MSSMBbeta1}\\
-\beta_B^{(2)}&=-36y_t^4A_t-36y_b^4A_b-12y_\tau^4A_\tau-12y_t^2y_b^2(A_t+A_b)+32g_3^2y_t^2(A_t-M_3)\nonumber\\
-&\quad{}+32g_3^2y_b^2(A_b-M_3)+\frac{8}{5}g_1^2y_t^2(A_t-M_1)-\frac{4}{5}g_1^2y_b^2(A_b-M_1)+\frac{12}{5}g_1^2y_\tau^2(A_\tau-M_1)\nonumber\\
-&\quad{}-30g_2^4M_2-\frac{18}{5}g_1^2g_2^2(M_1+M_2)-\frac{414}{25}g_1^4M_1,\label{eq:MSSMBbeta2}\\
+&\quad{}-12g_2^2(3y_t^2+3y_b^2+y_\tau^2)-\frac{4}{5}g_1^2(11y_t^2+8y_b^2+6y_\tau^2)+3g_2^4-\frac{189}{25}g_1^4+\frac{18}{5}g_1^2g_2^2\Bigg ],\label{eq:MSSMmub2}\\
 b_B^{(2)}&=72y_t^4A_t+72y_b^4A_b+16y_\tau^4A_\tau+12y_t^2y_b^2(A_t+A_b)+12y_\tau^2y_b^2(A_b+A_\tau)\nonumber\\
@@
 &\quad{}-\frac{26}{5}g_1^2y_t^2(A_t-M_1)-\frac{14}{5}g_1^2y_b^2(A_b-M_1)-\frac{18}{5}g_1^2y_\tau^2(A_\tau-M_1)\nonumber\\
-&\quad{}+12g_2^4M_2+\frac{396}{25}g_1^4M_1.\label{eq:MSSMBb2}
-\end{align}
-\end{subequations}
-The coefficients for $m_{H_d}^2$ and $m_{H_u}^2$ are 
-\begin{subequations}\label{eq:MSSMmHd2Betas}
-\begin{align}
-\beta_{m_{H_d}^2}^{(1)}&=6y_b^2\left (m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2 \right )+2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+A_\tau^2\right )\nonumber\\
-&\quad{}-6g_2^2M_2^2-\frac{3}{5}g_1^2\left ( \mathcal{S}+2M_1^2\right ),\label{eq:MSSMmHd2beta1}\\
-\beta_{m_{H_d}^2}^{(2)}&=-36y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
-&\quad{}-6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
-&\quad{}-12y_\tau^4\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2A_\tau^2\right )\nonumber\\
-&\quad{}+32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_3A_b+2M_3^2\right )\nonumber\\
-&\quad{}+\frac{6}{5}g_1^2y_t^2\left ( 3m_{H_u}^2+m_{Q3}^2-4m_{u3}^2\right )\nonumber\\
-&\quad{}-\frac{2}{5}g_1^2y_b^2\left ( 11m_{H_d}^2-m_{Q3}^2-4m_{d3}^2+2A_b^2-4M_1A_b+4M_1^2\right )\nonumber\\
-&\quad{}+\frac{6}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+4m_{e3}^2+2A_\tau^2-4M_1A_\tau+4M_1^2\right )\nonumber\\
-&\quad{}-\frac{16}{5}g_3^2g_1^2\left (\sum_{i=1}^3 m_{Qi}^2-2m_{ui}^2+m_{di}^2 \right )\nonumber\\
-&\quad{}+3g_2^4\left ( 11M_2^2+m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3 [3m_{Qi}^2+m_{Li}^2]\right )\nonumber\\
-&\quad{}+\frac{9}{5}g_1^2g_2^2\left ( 2M_1^2+2M_2^2+2M_1M_2-m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3[m_{Li}^2-m_{Qi}^2]\right )\nonumber\\
-&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_d}^2+\sum_{i=1}^3[18m_{Li}^2+2m_{Qi}^2+56m_{ui}^2+2m_{di}^2-18m_{ei}^2]\right ),\label{eq:MSSMmHd2beta2}\\
+&\quad{}+12g_2^4M_2+\frac{396}{25}g_1^4M_1,\label{eq:MSSMBb2}\\
 b_{m_{H_d}^2}^{(2)}&=72y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
@@
 &\quad{}-\frac{18}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+A_\tau^2-2M_1A_\tau+2M_1^2\right )\nonumber\\
-&\quad{}-18g_2^4M_2^2-\frac{198}{25}g_1^4\left ( \mathcal{S}+3M_1^2\right ),\label{eq:MSSMmHd2b2}
-\end{align}
-\end{subequations}
-\begin{subequations}\label{eq:MSSMmHu2Betas}
-\begin{align}
-\beta_{m_{H_u}^2}^{(1)}&=6y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-6g_2^2M_2^2+\frac{3}{5}g_1^2\left ( \mathcal{S}-2M_1^2\right ),\label{eq:MSSMmHu2beta1}\\
-\beta_{m_{H_u}^2}^{(2)}&=-36y_t^4(m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2)\nonumber\\
-&\quad{}-6y_t^2y_b^2(m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2)\nonumber\\
-&\quad{}+32g_3^2y_t^2(m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2A_tM_3+2M_3^2)\nonumber\\
-&\quad{}+\frac{2}{5}g_1^2y_t^2(-5m_{H_u}^2+m_{Q3}^2+16m_{u3}^2+4A_t^2-8A_tM_1+8M_1^2)\nonumber\\
-&\quad{}+\frac{6}{5}g_1^2y_b^2(3m_{H_d}^2-m_{Q3}^2-2m_{d3}^2)+\frac{6}{5}g_1^2y_\tau^2(m_{H_d}^2+m_{L3}^2-2m_{e3}^2)\nonumber\\
-&\quad{}+\frac{16}{5}g_1^2g_3^2\left(\sum_{i=1}^3m_{Qi}^2-2m_{ui}^2+m_{di}^2\right )\nonumber\\
-&\quad{}+\frac{9}{5}g_1^2g_2^2\left ( 2M_2^2+2M_1^2+2M_1M_2+m_{H_u}^2-m_{H_d}^2+\sum_{i=1}^3m_{Qi}^2-m_{Li}^2\right )\nonumber\\
-&\quad{}+3g_2^4\left ( 11M_2^2+m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3[3m_{Qi}^2+m_{Li}^2]\right )\nonumber\\
-&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_u}^2+\sum_{i=1}^3[4m_{Qi}^2-8m_{ui}^2+10m_{di}^2+54m_{ei}^2]\right ),\label{eq:MSSMmHu2beta2}\\
+&\quad{}-18g_2^4M_2^2-\frac{198}{25}g_1^4\left ( \mathcal{S}+3M_1^2\right ),\label{eq:MSSMmHd2b2}\\
 b_{m_{H_u}^2}^{(2)}&=72y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
@@
 \end{equation}
-If additional loop corrections are included from the 1-loop effective potential, it is also
-necessary to construct the expansions for $m_{Q3}^2$, $m_{u3}^2$ and $A_t$. The coefficients for $m_{Q3}^2$ and
-$m_{u3}^2$ are
-\begin{subequations}\label{eq:MSSMmq32Betas}
+If in addition the one-loop contributions to the effective potential from top and stop loops are included, it is also
+necessary to construct the expansions for $m_{Q3}^2$, $m_{u3}^2$ and $A_t$. The coefficients read
+\begin{subequations}\label{eq:MSSMsEffPotCoeffs}
 \begin{align}
-\beta_{m_{Q3}^2}^{(1)}&=2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )+2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2\right )\\
-&\quad{}-\frac{32}{3}g_3^2M_3^2-6g_2^2M_2^2+\frac{1}{5}g_1^2\left ( \mathcal{S}-\frac{2}{3}M_1^2\right ),\label{eq:MSSMmQ32beta1}\\
-\beta_{m_{Q3}^2}^{(2)}&=-20y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )-20y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
-&\quad{}-2y_\tau^2y_b^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{L3}^2+m_{d3}^2+m_{e3}^2+(A_b+A_\tau)^2\right )\nonumber\\
-&\quad{}+\frac{2}{5}g_1^2y_t^2\left ( m_{H_u}^2+3m_{Q3}^2+8m_{u3}^2+4A_t^2-8A_tM_1+8M_1^2\right )\nonumber\\
-&\quad{}+\frac{2}{5}g_1^2y_b^2\left ( 5m_{H_d}^2+m_{Q3}^2+2A_b^2-4A_bM_1+4M_1^2\right )\nonumber\\
-&\quad{}+\frac{2}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
-&\quad{}+\frac{16}{3}g_3^4\left ( \sum_{i=1}^3 \left [ 2m_{Qi}^2+m_{ui}^2+m_{di}^2\right ]-8M_3^2\right )\nonumber\\
-&\quad{}+32g_3^2g_2^2\left ( M_2^2+M_3^2+M_2M_3\right )\nonumber\\
-&\quad{}+\frac{16}{45}g_3^2g_1^2\left ( 3\sum_{i=1}^3\left [ m_{Qi}^2-2m_{ui}^2+m_{di}^2\right ]+2M_1^2+2M_3^2+2M_1M_3\right )\nonumber\\
-&\quad{}+3g_2^4\left ( m_{H_u}^2+m_{H_d}^2+\sum_{i=1}^3\left [ 3m_{Qi}^2+m_{Li}^2\right ]+11M_2^2\right )\nonumber\\
-&\quad{}+\frac{1}{5}g_1^2g_2^2\left ( 2M_1^2+2M_2^2+2M_1M_2+3m_{H_u}^2-3m_{H_d}^2+3\sum_{i=1}^3\left [ m_{Qi}^2-m_{Li}^2\right ]\right )\nonumber\\
-&\quad{}+\frac{1}{75}g_1^4\bigg ( 199M_1^2+12m_{H_u}^2-6m_{H_d}^2\nonumber\\
-&\qquad\qquad\qquad{}+\sum_{i=1}^3\left [ 2m_{Qi}^2-6m_{Li}^2-24m_{ui}^2+6m_{di}^2+42m_{ei}^2\right ]\bigg ),\label{eq:MSSMmQ32beta2}\\
 b_{m_{Q3}^2}^{(2)}&=24y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )+24y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
@@
 &\quad{}-\frac{14}{15}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_1A_b+2M_1^2\right )\nonumber\\
-&\quad{}+96g_3^4M_3^2-18g_2^4M_2^2+\frac{66}{25}g_1^4(\mathcal{S}-M_1^2),\label{eq:MSSMmQ32b2}
-\end{align}
-\end{subequations}
-\begin{subequations} \label{eq:MSSMmu32Betas}
-\begin{align}
-\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-\frac{32}{3}g_3^2M_3^2-\frac{4}{5}g_1^2\left ( \mathcal{S}+\frac{8}{3}M_1^2\right ),\label{eq:MSSMmu32beta1}\\
-\beta_{m_{u3}^2}^{(2)}&=-32y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
-&\quad{}-4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
-&\quad{}+12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_2A_t+2M_2^2\right )\nonumber\\
-&\quad{}-\frac{4}{5}g_1^2y_t^2\left ( 9m_{u3}^2-5m_{H_u}^2-m_{Q3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
-&\quad{}-\frac{8}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q3}^2-2m_{d3}^2\right )-\frac{8}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
-&\quad{}+\frac{16}{3}g_3^4\left ( \sum_{i=1}^3\left [2m_{Qi}^2+m_{ui}^2+m_{di}^2 \right ]-8M_3^2\right )\nonumber\\
-&\quad{}+\frac{64}{45}g_3^2g_1^2\left ( 8M_1^2+8M_3^2+8M_1M_3-3\sum_{i=1}^3\left [ m_{Qi}^2-2m_{ui}^2+m_{di}^2\right ]\right )\nonumber\\
-&\quad{}-\frac{12}{5}g_1^2g_2^2\left ( m_{H_u}^2-m_{H_d}^2+\sum_{i=1}^3\left [ m_{Qi}^2-m_{Li}^2\right ]\right )\nonumber\\
-&\quad{}+\frac{4}{75}g_1^4\left ( 856M_1^2+3m_{H_u}^2+21m_{H_d}^2+\sum_{i=1}^3\left [ 3m_{Qi}^2+21m_{Li}^2+64m_{ui}^2+4m_{di}^2-12m_{ei}^2\right ]\right ),\label{eq:MSSMmu32beta2}\\
+&\quad{}+96g_3^4M_3^2-18g_2^4M_2^2+\frac{66}{25}g_1^4(\mathcal{S}-M_1^2),\label{eq:MSSMmQ32b2}\\
 b_{m_{u3}^2}^{(2)}&=48y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
@@
 &\quad{}-\frac{52}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
-&\quad{}+96g_3^4M_3^2-\frac{264}{25}g_1^4\left ( \mathcal{S}+4M_1^2\right ).\label{eq:MSSMmu32b2}
-\end{align}
-\end{subequations}
-Finally, the coefficients for $A_t$ read
-\begin{subequations}\label{eq:MSSMAtBetas}
-\begin{align}
-\beta_{A_t}^{(1)}&=12y_t^2A_t+2y_b^2A_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1,\label{eq:MSSMAtbeta1}\\
-\beta_{A_t}^{(2)}&=-88y_t^4A_t-20y_b^4A_b-10y_t^2y_b^2(A_t+A_b)-2y_b^2y_\tau^2(A_b+A_\tau)\nonumber\\
-&\quad{}+32g_3^2y_t^2(A_t-M_3)+12g_2^2y_t^2(A_t-M_2)+\frac{12}{5}g_1^2y_t^2(A_t-M_1)+\frac{4}{5}g_1^2y_b^2(A_b-M_1)\nonumber\\
-& \quad{}+\frac{64}{9}g_3^4M_3-16g_3^2g_2^2(M_2+M_3)-\frac{272}{45}g_3^2g_1^2(M_1+M_3)-30g_2^4M_2\nonumber\\
-&\quad{}-2g_2^2g_1^2(M_1+M_2)-\frac{5486}{225}g_1^4M_1,\label{eq:MSSMAtbeta2}\\
+&\quad{}+96g_3^4M_3^2-\frac{264}{25}g_1^4\left ( \mathcal{S}+4M_1^2\right ),\label{eq:MSSMmu32b2}\\
 b_{A_t}^{(2)}&=144y_t^4A_t+24y_b^4A_b+14y_t^2y_b^2(A_t+A_b)+2y_b^2y_\tau^2(A_b+A_\tau)\nonumber\\
@@
 \end{subequations}
-It is then trivial to extract the relevant terms for the fine tuning calculation in the MSSM from these expressions.\\ \\
-In $U(1)$ extended models the 2-loop RGEs are somewhat more lengthy even if $U(1)$ mixing effects are
-neglected. As for the MSSM, we present simplified expressions in which it is assumed that the first and 
-second generation Yukawas are zero along with the soft SUSY breaking trilinears. At tree level in the EWSB conditions
-the parameters that must be expanded are $\lambda$, $A_\lambda$, $m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and $g_1'$.
-The coefficients in the expansion of $\lambda$ may be written
+Similarly we can obtain the two-loop $\beta$ functions and coefficients $b_p^{(2)}$ for a general set of $U(1)'$ charges.
+Two-loop RGEs for the gauge and Yukawa couplings, gaugino masses and soft trilinears, along with the one-loop RGEs for the soft scalar masses, were given in \cite{Athron:2009bs} for the particular case of the E$_6$SSM.
+At tree level in the EWSB conditions the parameters that must be considered are $\lambda$, $A_\lambda$, $m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and $g_1'$.
+The one- and two-loop contributions to the $\beta$ function for $\lambda$ are
 \begin{subequations}\label{eq:USSMLambdaBetas}
 \begin{align}
-\beta_{\lambda}^{(1)}&=\lambda\Big (2\lambda^2+2\Sigma_\lambda +3\Sigma_\kappa+ 3y_t^2 + 3y_b^2 + y_\tau^2-\frac{3}{5}g_1^2-3g_2^2-2g_1'^2\left (\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\Big ), \label{eq:USSMLambdabeta1}
+\beta_\lambda^{(1)}&=,\label{eq:USSMLambdaBetaOneLoop}\\
+\beta_\lambda^{(2)}&=.\label{eq:USSMLambdaBetaTwoLoop}
 \end{align}
 \end{subequations}
-where
-\begin{equation*}
-\Sigma_\lambda=\lambda_1^2+\lambda_2^2+\lambda_3^2,\qquad \Sigma_\kappa=\kappa_1^2+\kappa_2^2+\kappa_3^2.
-\end{equation*}
 % NB before submission replace this with a copy-paste of the bbl file?

### 2014-12-16 paper/e6ssm-tuning-paper.tex
sketeched out some of the results discussion. very rough, needs details added, expamnsion and improvement of phrasing.

@@
 %    - tuning as a function of stop mass for the MSSM and E6SSM
+Many recent papers have focussed on light stops as allowing natural
+SUSY and there has been a lot of theoretical effort to find SUSY
+models with a $125$ GeV Higgs bosons while still having light stops
+and experimental efforts to search for light stops.  This is entirely
+appropriate, however the fine tning problem from the stops depends
+crucially on the RG evolution from the GUT scale, since this is how
+the squark masses feed into the soft Higgs masses that appear in the
+EWSB conditions.
+
+In Fig. \ref{} we fix blah blah bah [Dylan insert details please] and
+show how fine tuning varies as we increase the stop masses. However
+thius tuning inly really becomes large for very large stop masses.  On
+the other hand if cuttoff is increased then stop masses of severalk
+TeV can result in tuning of [insert] as shown in Fig.~\ref{}.
+
 %    - full scatter plots of MSSM and E6SSM, including different
 %      M_Z' values
+
+Since the stop mass does not have a large impact on the fine tuning
+when the cutoff scale is very low we can use this to see more clearly
+the impact of the $Z^\prime$ mass on fine tuning. To do se we cjoose a
+cutoff of [insert cutoff] look at the fine tuning for two different
+values of the $Z^\prime$ mass, $2.5$ TeV, which is just above the
+current limits and $4.5$ TeV which could be in reach of the LHC run
+II, and compare these to the MSSM.
+
+For this we also fix [what we fix + explain different choices to
+  before and their impact].
+\begin{figure}[h]
+\begin{center}
+\resizebox{!}{10cm}{%
+\includegraphics{all_models_tuning_vs_higgs.png}}
+\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
+  MSSM (green), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue) and
+  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red).}
+\label{Fig:e6ssmvsmssm}
+\end{center}
+\end{figure}
+In Fig \ref{Fig:e6ssmvsmssm} we see that as expected the minimum
+tuning in the model for the E$_6$SSM is increased by the mass of the
+$Z^\prime$ boson.  Since with such a low cutoff the stop masses have
+little impact on the tuning, the tuning here also does not depend much
+on the Higgs mass.  However the tuning from the $Z^\prime$ mass
+appears already at tree level and is unavoidable regardless of the
+cutoff scale chosen.
+
+Therefore the tuning in these models depends on less assumptions than
+the tuning which concerns people in the MSSM and the owest tuned
+models are adderessed directly with $Z^\prime$ searches.
+
+In the MSSM the tuning can also be attcked more directly by looking at
+chargino mass limikts as this rasies $\mu$ directly.  [Stuff aboiut
+  chargino limits stiuts, then show plots in MSSM and E6SSM]
 %    - plots of chargino bound impacts
-%    - if room, plots for different U(1)' charges
+
+The exact level of tuning from the $Z^\prime$ depends on the charges of
+the extra $U(1)$ gauge symmetry it is associated with.  In Fig \ref{}
+we look at the fine tuning for other U(1) extensions for the same
+$Z^\prime$ masses as we did for the E$_6$SSM.
+ % - if room, plots for different U(1)' charge Here we see that the As
+can be seen in Fig.~\ref{} the severity of the tunings varies quite a
+bit.  This is because the charges appear as coefficients in front of
+the $Z^\prime$ mass in the EWSB condition.  These cagres change the
+value of the coefficient $d$ in Eq.~\ref{}.  The values of the
+coefficient $d$ in each model is [insert], and this determines which
+of the models are most tuned.
+
+[We should add some discussion about the $U(1)_I$ and the physics of
+  that model here, since it has the lowest tuning.]
+
+Finally we want to emphasise that while in Fig.~\ref{} the E$_6$SSM
+looks more fine tuned than the MSSM this is depends on the cutoff
+scale.  Indeed in \cite{} a constrained version of the E$_6$SSM, with
+the cuttoff at the GUT scale, is considered and there the cE$_6$SSM
+was found to be less tuned than the cMSSM. Since a 125 GeV Higgs can
+be achieved in the E$_6$SSM with ligher stops, then if the cutoff is
+large, the larger stop masses can make that model more
+fine tuned due to large RGE effects.
+
+As is shown in Fig.~\cite{} the tuning in the MSSM becomes larger
+than that of the E$_6$SSM when the cuttoff scale is ?
+
 \section{\label{sec:conclusion}Conclusions}

### 2014-12-17 paper/e6ssm-tuning-paper.tex
Replaced 1-loop beta for lambda
Moved scan details from section on numerical procedure to results section

@@
 \subsection{\label{subsec:numericalprocedure}Numerical Procedure}
-Using the approach outlined above, we have scanned the low energy parameter space of the MSSM and E$_6$SSM and calculated the fine tuning in each of the models considered.
+Using the approach outlined above, we are able to scan the low energy parameter space of the MSSM and E$_6$SSM and calculate the fine tuning in each.
 To do so, we implemented the above expressions for computing the fine tuning in a modified version of the E$_6$SSM spectrum generator that was used in \cite{Athron:2013ipa}.
@@
 For consistency with the results produced in the $E_6$ models, and for computational speed, for our main scans only the dominant one- and two-loop corrections to the CP-even Higgs masses were included.
-The parameter ranges that were scanned over are presented in Table \ref{tab:scanranges}.
-With the exception of the stop mixing $A_t$, which was logarithmically scanned, all parameters were linearly scanned.
-All other parameters were decoupled by setting the remaining soft masses to values of $5$ TeV, while the first and second generation Yukawa couplings and their associated soft trilinears were taken to vanish.
+Finally, in all of the results below the fine tuning was evaluated at the scale $Q=M_{\textrm{SUSY}}=\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop masses evaluated at $Q=M_{\textrm{SUSY}}$.
+
+\section{\label{sec:results}Results}
+% Our results. Plots to go in here:
+%    - tuning as a function of stop mass for the MSSM and E6SSM
+Many recent papers have focussed on light stops as allowing natural
+SUSY and there has been a lot of theoretical effort to find SUSY
+models with a $125$ GeV Higgs boson while still having light stops
+and experimental efforts to search for light stops.  This is entirely
+appropriate, however the fine tning problem from the stops depends
+crucially on the RG evolution from the GUT scale, since this is how
+the squark masses feed into the soft Higgs masses that appear in the
+EWSB conditions.
+
+In Fig. \ref{} we fix blah blah bah [Dylan insert details please] and
+show how fine tuning varies as we increase the stop masses. However
+thius tuning inly really becomes large for very large stop masses.  On
+the other hand if cuttoff is increased then stop masses of severalk
+TeV can result in tuning of [insert] as shown in Fig.~\ref{}.
+
+%    - full scatter plots of MSSM and E6SSM, including different
+%      M_Z' values
+
+Since the stop mass does not have a large impact on the fine tuning when the 
+cutoff scale is very low we can use this to see more clearly the impact of the
+$Z^\prime$ mass on fine tuning. To do so we select a fixed low cutoff of $M_X=20$ TeV and compare the
+fine tuning for two different values of the $Z^\prime$ mass. We choose to look at
+$M_{Z^\prime}=2.5$ TeV, which is just above the current limits, and $M_{Z^\prime}=4.5$ TeV, 
+which should be in reach in run II at the LHC. We also compare the fine tuning calculated
+in each case to the tuning in the MSSM. For this, we have performed a parameter space scan in both the 
+MSSM and E$_6$SSM, scanning over those parameters that appear at tree level in the EWSB conditions in the
+models. While the contribution from large stop masses to the fine tuning is small for such a low cut-off scale, the 
+stop contributions to the effective potential can play a significant role in reducing the fine tuning.
+For this reason it is still important to properly treat the tuning associated with stop contributions to the one-loop effective potential, and so we also scan over the soft masses $m_{Q_3}^2$, $m_{u_3}^2$ and the stop mixing $A_t$.
+The relevant parameters and ranges that were scanned over are summarised in Table \ref{tab:scanranges}.
+With the exception of the stop mixing $A_t$ and the soft trilinear $A_\lambda$, which are logarithmically scanned, all parameters are linearly scanned.
+In both the MSSM and E$_6$SSM, we then decouple all other parameters by setting the remaining soft masses to values of $5$ TeV, while the first and second generation Yukawa couplings and their associated soft trilinears are taken to vanish.
 The $U(1)$ gaugino soft mass $M_1$ was fixed to $M_1=300$ GeV, and we fix $M_3=2000$ GeV.
-The input scale $M_X$ was set to $M_X=20$ TeV for both the MSSM and the $E_6$ models.
-Finally, the fine tuning was evaluated at the scale $Q=M_{\textrm{SUSY}}=\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop masses evaluated at $Q=M_{\textrm{SUSY}}$.
+Additionally, in the E$_6$SSM the $U(1)_N$ gaugino soft mass $M_1'$ is held fixed with $M_1'=M_1=300$ GeV, and $\mu^\prime=5$ TeV.
 \begin{table}[h]
@@
 \end{table}
-\section{\label{sec:results}Results}
-% Our results. Plots to go in here:
-%    - tuning as a function of stop mass for the MSSM and E6SSM
-Many recent papers have focussed on light stops as allowing natural
-SUSY and there has been a lot of theoretical effort to find SUSY
-models with a $125$ GeV Higgs bosons while still having light stops
-and experimental efforts to search for light stops.  This is entirely
-appropriate, however the fine tning problem from the stops depends
-crucially on the RG evolution from the GUT scale, since this is how
-the squark masses feed into the soft Higgs masses that appear in the
-EWSB conditions.
 
-In Fig. \ref{} we fix blah blah bah [Dylan insert details please] and
-show how fine tuning varies as we increase the stop masses. However
-thius tuning inly really becomes large for very large stop masses.  On
-the other hand if cuttoff is increased then stop masses of severalk
-TeV can result in tuning of [insert] as shown in Fig.~\ref{}.
+%   Since the stop mass does not have a large impact on the fine tuning
+%   when the cutoff scale is very low we can use this to see more clearly
+%   the impact of the $Z^\prime$ mass on fine tuning. To do se we choose a
+%   cutoff of  look at the fine tuning for two different
+%   values of the $Z^\prime$ mass, $2.5$ TeV, which is just above the
+%   current limits and $4.5$ TeV which could be in reach of the LHC run
+%   II, and compare these to the MSSM.
 
-%    - full scatter plots of MSSM and E6SSM, including different
-%      M_Z' values
-
-Since the stop mass does not have a large impact on the fine tuning
-when the cutoff scale is very low we can use this to see more clearly
-the impact of the $Z^\prime$ mass on fine tuning. To do se we cjoose a
-cutoff of [insert cutoff] look at the fine tuning for two different
-values of the $Z^\prime$ mass, $2.5$ TeV, which is just above the
-current limits and $4.5$ TeV which could be in reach of the LHC run
-II, and compare these to the MSSM.
-
-For this we also fix [what we fix + explain different choices to
-  before and their impact].
+%   For this we also fix [what we fix + explain different choices to
+%   before and their impact].
 \begin{figure}[h]
@@
 \begin{align}
-\beta_\lambda^{(1)}&=,\label{eq:USSMLambdaBetaOneLoop}\\
-\beta_\lambda^{(2)}&=.\label{eq:USSMLambdaBetaTwoLoop}
+\beta_\lambda^{(1)}&=\lambda  \left[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2-\frac{3}{5} g_1^2 -2 \left ( \tilde{Q}_1^2 + \tilde{Q}_2^2 + \tilde{Q}_S^2\right )g_1'^2 \right],\label{eq:USSMLambdaBetaOneLoop}\\
+\beta_\lambda^{(2)}&=\lambda \left [ \left ( \right )g_1'^4\right ],\label{eq:USSMLambdaBetaTwoLoop}
 \end{align}
 \end{subequations}
+where
+\begin{equation*}
+\Sigma_\lambda=\lambda_1^2+\lambda_2^2+\lambda_3^2, \qquad \Sigma_\kappa=\kappa_1^2+\kappa_2^2+\kappa_3^2.
+\end{equation*}
 % NB before submission replace this with a copy-paste of the bbl file?

### 2014-12-17 paper/e6ssm-tuning-paper.tex
Added details of what is fixed for stop scans

@@
 
-In Fig. \ref{} we fix blah blah bah [Dylan insert details please] and
-show how fine tuning varies as we increase the stop masses. However
+To illustrate this, in Fig. \ref{} we show the variation in fine tuning when we fix $\mu=-97$ GeV and $B=-85$ GeV, 
+and scan over the stop masses and mixing, with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
+However
 thius tuning inly really becomes large for very large stop masses.  On
 the other hand if cuttoff is increased then stop masses of severalk
-TeV can result in tuning of [insert] as shown in Fig.~\ref{}.
+TeV can result in tuning of [insert] as shown in Fig.~\ref{}.\\ \\
 

### 2014-12-17 paper/e6ssm-tuning-paper.tex
fix a couple of typos. there will be many more.

@@
 and scan over the stop masses and mixing, with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
-However
-thius tuning inly really becomes large for very large stop masses.  On
-the other hand if cuttoff is increased then stop masses of severalk
+However this tuning only really becomes large for very large stop masses.  On
+the other hand if cuttoff is increased then stop masses of several
 TeV can result in tuning of [insert] as shown in Fig.~\ref{}.\\ \\

### 2014-12-17 paper/e6ssm-tuning-paper.tex
fix a couple of my typos. there will be more.

@@
 and experimental efforts to search for light stops.  This is entirely
-appropriate, however the fine tning problem from the stops depends
+appropriate, however the fine tuning problem from the stops depends
 crucially on the RG evolution from the GUT scale, since this is how
@@
 
-To illustrate this, in Fig. \ref{} we show the variation in fine tuning when we fix $\mu=-97$ GeV and $B=-85$ GeV, 
-and scan over the stop masses and mixing, with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
-However this tuning only really becomes large for very large stop masses.  On
-the other hand if cuttoff is increased then stop masses of several
-TeV can result in tuning of [insert] as shown in Fig.~\ref{}.\\ \\
+To illustrate this, in Fig. \ref{} we show the variation in fine
+tuning when we fix $\mu=-97$ GeV and $B=-85$ GeV, and scan over the
+stop masses and mixing, with $500 \textrm{ GeV} \leq
+m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq
+A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
+However this tuning only really becomes large for very large stop
+masses.  On the other hand if cuttoff is increased then stop masses of
+several TeV can result in tuning of [insert] as shown in
+Fig.~\ref{}.\\ \\
 
@@
 Therefore the tuning in these models depends on less assumptions than
-the tuning which concerns people in the MSSM and the owest tuned
+the tuning which concerns people in the MSSM and the lowest tuned
 models are adderessed directly with $Z^\prime$ searches.

### 2014-12-17 paper/e6ssm-tuning-paper.tex
Added in possible paragraph for describing why fine tuning depends on charges

--- 2014-12-17 paper/e6ssm-tuning-paper.tex
@@
 $Z^\prime$ masses as we did for the E$_6$SSM.
- % - if room, plots for different U(1)' charge Here we see that the As
-can be seen in Fig.~\ref{} the severity of the tunings varies quite a
+% - plots for different U(1)' charge 
+% DH:: not quite sure of the standard way of setting up subfigures...
+
+As can be seen in Fig.~\ref{} the severity of the tunings varies quite a
 bit.  This is because the charges appear as coefficients in front of
@@
 coefficient $d$ in each model is [insert], and this determines which
-of the models are most tuned.
+of the models are most tuned.\\ \\
+
+% DH:: I didn't use the d notation in the section on EWSB, would this
+% work to introduce it here instead?
+While the $Z^\prime$ mass does set a lower limit on the tuning, the exact
+value of this tuning depends quite strongly on the charges of the extra
+$U(1)$ gauge symmetry it is associated with. This is illustrated in Fig~\ref{}, 
+in which we show the fine tuning for several other commonly studied
+$U(1)$ extensions for the same set of $Z^\prime$ masses as were considered in the
+E$_6$SSM. As can be seen in Fig.~\ref{}, the severity of the tunings varies
+quite a bit. This can be understood from the fact that the $D$-terms $D_{H_d}$, $D_{H_u}$
+that enter the EWSB condition Eq. (\ref{eq:E6MZequation}) are proportional to
+the $U(1)'$ charges. It is therefore possible to significantly reduce the size
+of the additional $D$-term contributions to the EWSB conditions by choosing the $U(1)'$ 
+charges appropriately. For $s\gg v$, as is
+required in all of the $U(1)$ extended models considered in order to have $M_{Z^\prime}\geq 2.5$ TeV,
+the $D$-term contribution to Eq. (\ref{eq:E6MZequation}) is well approximated by
+\begin{equation*}
+\frac{D_{H_d}-D_{H_u}\tan^2\beta}{\tan^2-1}\approx \frac{g_1'^2}{2}\tilde{Q}_Ss^2\left ( \frac{\tilde{Q}_1-\tilde{Q}_2\tan^2\beta}{\tan^2\beta-1}\right )\approx d(\theta,\tan\beta)\frac{M_{Z^\prime}^2}{2},\qquad d(\theta,\tan\beta)\equiv \left ( \frac{\tilde{Q}_1-\tilde{Q}_2\tan^2\beta}{\tilde{Q}_S\left ( \tan^2\beta - 1\right )}\right )
+\end{equation*}
+for models with $\tilde{Q}_S\neq 0$. Written in this form one might expect that the fine tuning
+associated with this contribution will be reduced when this expression is 
+minimised.
+This is indeed the case.
+For example, in the E$_6$SSM with $\theta=\arctan\sqrt{15}$ one finds that for $\tan\beta=10$, $d\approx 0.398$.
+This can be compared to the $U(1)_\psi$ ($\theta=\pi/2$) and $U(1)_\eta$ ($\theta=-\arctan\sqrt{5/3}$) models, for which $d=0.5$ and $d\approx 0.806$, respectively.
+The larger values of the $D$-term contributions in these models result in them having a larger fine tuning than in the E$_6$SSM, as is evident from Fig.~\ref{}.
+Of particular note is the inert $U(1)_I$ model ($\theta=\pi+\arctan\sqrt{3/5}$), which has $\tilde{Q}_2=0$, resulting in the coefficient $d$ being suppressed by $\tan^2\beta$.
+For this model we find that $d\approx-0.01$, and so the $D$-term contribution is much smaller than in the other models described.
+The fine tuning is as a result somewhat smaller, not being much greater than that found in the MSSM.
 

### 2014-12-17 paper/e6ssm-tuning-paper.tex
added values of d coefficient.

--- 2014-12-17 paper/e6ssm-tuning-paper.tex
@@
 In the MSSM the tuning can also be attcked more directly by looking at
-chargino mass limikts as this rasies $\mu$ directly.  [Stuff aboiut
-  chargino limits stiuts, then show plots in MSSM and E6SSM]
+chargino mass limikts as this rasies $\mu$ directly.  [Stuff about
+  chargino limits, then show plots in MSSM and E6SSM]
 %    - plots of chargino bound impacts
@@
 bit.  This is because the charges appear as coefficients in front of
-the $Z^\prime$ mass in the EWSB condition.  These cagres change the
+the $Z^\prime$ mass in the EWSB condition.  These charges change the
 value of the coefficient $d$ in Eq.~\ref{}.  The values of the
-coefficient $d$ in each model is [insert], and this determines which
+coefficient $d$ in each model is $\{-0.01, 0.40, 0.50, 0.81 \}$ for
+$\{U(1)_I, U(1)_N, U(1)_\psi, U(1)_\eta \}$ and this determines which
 of the models are most tuned.
@@
 
-Finally we want to emphasise that while in Fig.~\ref{} the E$_6$SSM
-looks more fine tuned than the MSSM this is depends on the cutoff
-scale.  Indeed in \cite{} a constrained version of the E$_6$SSM, with
-the cuttoff at the GUT scale, is considered and there the cE$_6$SSM
-was found to be less tuned than the cMSSM. Since a 125 GeV Higgs can
-be achieved in the E$_6$SSM with ligher stops, then if the cutoff is
-large, the larger stop masses can make that model more
-fine tuned due to large RGE effects.
+Finally we want to emphasise that while in Fig.~\ref{Fig:e6ssmvsmssm}
+the E$_6$SSM looks more fine tuned than the MSSM this is depends on
+the cutoff scale.  Indeed in \cite{Athron:2013ipa} a constrained
+version of the E$_6$SSM, with the cuttoff at the GUT scale, is
+considered and there the cE$_6$SSM was found to be less tuned than the
+cMSSM. Since a 125 GeV Higgs can be achieved in the E$_6$SSM with
+ligher stops, then if the cutoff is large, the larger stop masses can
+make that model more fine tuned due to large RGE effects.
 
-As is shown in Fig.~\cite{} the tuning in the MSSM becomes larger
+As is shown in Fig.~\ref{} the tuning in the MSSM becomes larger
 than that of the E$_6$SSM when the cuttoff scale is ?

### 2014-12-17 paper/e6ssm-tuning-paper.tex

--- 2014-12-17 paper/e6ssm-tuning-paper.tex
@@
 
-To illustrate this, in Fig. \ref{} we show the variation in fine tuning when we fix $\mu=-97$ GeV and $B=-85$ GeV, 
-and scan over the stop masses and mixing, with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
-However this tuning only really becomes large for very large stop masses.  On
-the other hand if cuttoff is increased then stop masses of several
-TeV can result in tuning of [insert] as shown in Fig.~\ref{}.\\ \\
+To illustrate this, in Fig. \ref{} we show the variation in fine
+tuning when we fix $\mu=-97$ GeV and $B=-85$ GeV, and scan over the
+stop masses and mixing, with $500 \textrm{ GeV} \leq
+m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq
+A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
+However this tuning only really becomes large for very large stop
+masses.  On the other hand if the cuttoff is increased then stop masses of
+several TeV can result in tuning of [insert] as shown in
+Fig.~\ref{}.\\ \\
 
@@
 bit.  This is because the charges appear as coefficients in front of
-the $Z^\prime$ mass in the EWSB condition.  These cagres change the
+the $Z^\prime$ mass in the EWSB condition.  These charges change the
 value of the coefficient $d$ in Eq.~\ref{}.  The values of the
-coefficient $d$ in each model is [insert], and this determines which
-of the models are most tuned.\\ \\
+coefficient $d$ in each model is $\{-0.01, 0.40, 0.50, 0.81 \}$ for
+$\{U(1)_I, U(1)_N, U(1)_\psi, U(1)_\eta \}$ and this determines which
+of the models are most tuned.
 
@@
 The fine tuning is as a result somewhat smaller, not being much greater than that found in the MSSM.
+>>>>>>> 9210c662723efc5e3c4599b1702311631b8f859c
 

### 2014-12-18 paper/e6ssm-tuning-paper.tex
fixed merge problem that I missed.  ugh..
Moved definition of d coefficient to EWSB section, removed additional discussion from results section

--- 2014-12-17 paper/e6ssm-tuning-paper.tex
@@
 Moreover, because this is a large \textit{tree level} fine tuning, it may negate the increase in naturalness that is associated with having a reduced need for heavy superpartners.
+In $U(1)$ extended models for which $\tilde{Q}_S\neq 0$, the importance of the $Z^\prime$ mass to the fine tuning in these models can be made even clearer by writing Eq.
+(\ref{eq:E6MZequation}) in the form given in \cite{Athron:2013ipa},
+\begin{equation}\label{eq:originalE6MZequation}
+c(\theta,\tan\beta)\frac{M_Z^2}{2}=-\frac{\lambda^2 s^2}{2}+\frac{\tilde{m}_{H_d}^2-\tilde{m}_{H_u}^2\tan^2\beta}{\tan^2\beta-1}+d(\theta,\tan\beta)\frac{M_{Z^\prime}^2}{2}
+\end{equation}
+where 
+\begin{align}
+c(\theta,\tan\beta)&=1-\frac{4}{\left ( \tan^2\beta-1\right )}\frac{g_1'^2}{\bar{g}^2}\left ( \tilde{Q}_1-\tilde{Q}_2\tan^2\beta \right )\left ( \tilde{Q}_1\cos^2\beta+\tilde{Q}_2\sin^2\beta \right ),\label{eq:cdefn}\\
+d(\theta,\tan\beta)&= \frac{\tilde{Q}_1-\tilde{Q}_2\tan^2\beta}{\tilde{Q}_S\left ( \tan^2\beta - 1\right )}.\label{eq:ddefn}
+\end{align}
+Written like so it is evident that the fine tuning contribution coming from the new $D$-terms depends both on the $U(1)'$ charges and the $Z^\prime$ mass, and that the tuning can be expected to increase with $M_{Z^\prime}$.
+As shall be shown below, the exact size of this tuning then depends strongly on the choice of $U(1)'$ charges, via the coefficient $d$.
 \section{\label{sec:tuning}Fine Tuning}
@@
 However this tuning only really becomes large for very large stop
-masses.  On the other hand if cuttoff is increased then stop masses of
+masses.  On the other hand if the cuttoff is increased then stop masses of
 several TeV can result in tuning of [insert] as shown in
@@
 $Z^\prime$ masses as we did for the E$_6$SSM.
- % - if room, plots for different U(1)' charge Here we see that the As
-can be seen in Fig.~\ref{} the severity of the tunings varies quite a
+% - plots for different U(1)' charge
+
+% DH:: for reference:
+%      U(1)_I \theta = \pi+\arctan\sqrt{3/5}
+%      U(1)_\psi \theta = \pi / 2
+%      U(1)_\eta \theta = -\arctan\sqrt{5/3}
+
+As can be seen in Fig.~\ref{} the severity of the tunings varies quite a
 bit.  This is because the charges appear as coefficients in front of
 the $Z^\prime$ mass in the EWSB condition.  These charges change the
-value of the coefficient $d$ in Eq.~\ref{}.  The values of the
-coefficient $d$ in each model is $\{-0.01, 0.40, 0.50, 0.81 \}$ for
+value of the coefficient $d$ in Eq. (\ref{eq:originalE6MZequation}).  The values of the
+coefficient $d$ in each model, for $\tan\beta = 10$, is $\{-0.01, 0.40, 0.50, 0.81 \}$ for
 $\{U(1)_I, U(1)_N, U(1)_\psi, U(1)_\eta \}$ and this determines which

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Added stop fine tuning plot into draft

@@
 
-To illustrate this, in Fig. \ref{} we show the variation in fine
+\begin{figure}[h]
+\begin{center}
+\resizebox{!}{10cm}{%
+\includegraphics{mssm_stop_tuning.png}}
+\caption{Scatter plot of fine tuning in the MSSM as a function of
+the lightest stop mass, $m_{\tilde{t}_1}$ for the cut-off scales (from 
+bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
+\label{Fig:mssmstoptuning}
+\end{center}
+\end{figure}
+To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the variation in fine
 tuning when we fix $\mu=-97$ GeV and $B=-85$ GeV, and scan over the

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Added plot of MSSM tuning as function of Higgs mass into draft, and disclaimer in text in case it is important to be clear that in the cut-off scan the Higgs mass is allowed to vary

@@
 \caption{Scatter plot of fine tuning in the MSSM as a function of
-the lightest stop mass, $m_{\tilde{t}_1}$ for the cut-off scales (from 
+the lightest stop mass, $m_{\tilde{t}_1}$, for the cut-off scales (from 
 bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
 \label{Fig:mssmstoptuning}
+\end{center}
+\end{figure}
+
+% DH:: I'm not sure if this is worth including? I've put a disclaimer in the
+% text, as well.
+\begin{figure}[h]
+\begin{center}
+\resizebox{!}{10cm}{%
+\includegraphics{mssm_higgs_tuning.png}}
+\caption{Scatter plot of fine tuning in the MSSM as a function of
+the lightest Higgs mass, $m_{h_1}$, for the cut-off scales (from 
+bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
+\label{Fig:mssmhiggstuning}
 \end{center}
@@
 A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
+Note that the Higgs mass is also allowed to vary over the scan, as shown in 
+Fig.~\ref{Fig:mssmhiggstuning}.
 However this tuning only really becomes large for very large stop
@@
 several TeV can result in tuning of [insert] as shown in
-Fig.~\ref{}.\\ \\
+Fig.~\ref{Fig:mssmstopstuning}.\\ \\
 

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Added complete list of fixed parameters for first set of plots, if they are needed, and fixed broken figure reference

@@
 To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the variation in fine
-tuning when we fix $\mu=-97$ GeV and $B=-85$ GeV, and scan over the
+tuning when we scan over the
 stop masses and mixing, with $500 \textrm{ GeV} \leq
@@
 A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
+The remaining parameters we fix such that at $M_{SUSY}$ they have the values $\mu=-97.5$ GeV, $B=-84.8$ GeV,
+$M_1=92.1$ GeV, $M_2=95.9$ GeV, $M_3=352$ GeV, $A_b=-117.9$ GeV, $A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV, $m_{e_i}=204$ GeV,
+$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV ($i=1,2,3$). 
 Note that the Higgs mass is also allowed to vary over the scan, as shown in 
@@
 several TeV can result in tuning of [insert] as shown in
-Fig.~\ref{Fig:mssmstopstuning}.\\ \\
+Fig.~\ref{Fig:mssmstoptuning}.\\ \\
 

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Added sentence justifying the light parameter values, may need to expand on it

@@
 $M_1=92.1$ GeV, $M_2=95.9$ GeV, $M_3=352$ GeV, $A_b=-117.9$ GeV, $A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV, $m_{e_i}=204$ GeV,
-$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV ($i=1,2,3$). 
+$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV ($i=1,2,3$). By making this choice for the 
+remaining parameters we ensure that fine tuning due to each is small, allowing us to see the fine tuning
+impact of the stops for stop masses of less than 1 TeV. For models in which the spectrum is heavier the fine tuning
+reaches a lower bound imposed by other heavier parameters as the stop masses become very small.
 Note that the Higgs mass is also allowed to vary over the scan, as shown in 

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Fixed inconsistency in notation for D-terms

@@
 &f_1=m_{H_d}^2v_1+\frac{\lambda^2}{2}(v_2^2+s^2)v_1-\frac{\lambda A_\lambda}{\sqrt{2}}sv_2-\frac{\bar{g}^2}{8}
-(v_2^2-v_1^2)v_1+D_{H_d}v_1+\frac{\partial \Delta V_{E_6}}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\
+(v_2^2-v_1^2)v_1+D_{H_1}v_1+\frac{\partial \Delta V_{E_6}}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\
 &f_2=m_{H_u}^2v_2+\frac{\lambda^2}{2}(v_1^2+s^2)v_2-\frac{\lambda A_\lambda}{\sqrt{2}}sv_1+\frac{\bar{g}^2}{8}
-(v_2^2-v_1^2)v_2+D_{H_u}v_2+\frac{\partial \Delta V_{E_6}}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\
+(v_2^2-v_1^2)v_2+D_{H_2}v_2+\frac{\partial \Delta V_{E_6}}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\
 &f_3=m_S^2s+\frac{\lambda^2}{2}(v_2^2+v_1^2)s-\frac{\lambda A_\lambda}{\sqrt{2}}v_2v_1+D_Ss+\frac{\partial \Delta V_{E_6}}{\partial s}=0.\label{eq:E6EWSBcondition3}
@@
 \begin{equation}\label{eq:E6MZequation}
-\frac{M_Z^2}{2}=-\frac{\lambda^2s^2}{2}+\frac{\tilde{m}_{H_d}^2-\tilde{m}_{H_u}^2\tan^2\beta}{\tan^2\beta-1}+\frac{D_{H_d}-D_{H_u}\tan^2\beta}{\tan^2\beta-1},
+\frac{M_Z^2}{2}=-\frac{\lambda^2s^2}{2}+\frac{\tilde{m}_{H_d}^2-\tilde{m}_{H_u}^2\tan^2\beta}{\tan^2\beta-1}+\frac{D_{H_1}-D_{H_2}\tan^2\beta}{\tan^2\beta-1},
 \end{equation}
 \begin{equation}\label{eq:E6sin2bequation}
-\sin 2\beta=\frac{\sqrt{2}\lambda A_{\lambda} s}{\tilde{m}_{H_d}^2+\tilde{m}_{H_u}^2+\lambda^2s^2+D_{H_d}+D_{H_u}},
+\sin 2\beta=\frac{\sqrt{2}\lambda A_{\lambda} s}{\tilde{m}_{H_d}^2+\tilde{m}_{H_u}^2+\lambda^2s^2+D_{H_1}+D_{H_2}},
 \end{equation}
@@
 To satisfy these limits typically requires large values of the singlet VEV $s$.
-For example $s\gtrsim 6$ TeV is required in the E$_6$SSM with $U(1)'=U(1)_N$, so that $|D_{H_u}|,|D_{H_d}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq 0$.
+For example $s\gtrsim 6$ TeV is required in the E$_6$SSM with $U(1)'=U(1)_N$, so that $|D_{H_1}|,|D_{H_2}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq 0$.
 As a result the remaining terms on the right-hand side of Eq.

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Removed italicised text, removed reference to 2-loop corrections to the effective potential - could be confusing if not distinguished between 2-loop RGE effects and the 2-loop effective potential

@@
 (\ref{eq:E6MZequation}) must be tuned to cancel the resulting very large contribution to $M_Z$.
-Moreover, because this is a large \textit{tree level} fine tuning, it may negate the increase in naturalness that is associated with having a reduced need for heavy superpartners.
+Moreover, because this is a large tree level fine tuning, it may negate the increase in naturalness that is associated with having a reduced need for heavy superpartners.
 In $U(1)$ extended models for which $\tilde{Q}_S\neq 0$, the importance of the $Z^\prime$ mass to the fine tuning in these models can be made even clearer by writing Eq.
@@
 However, it is well known in the MSSM that radiative corrections can significantly change (indeed, reduce) the fine tuning \cite{Cassel:2010px}.
-It is therefore important when studying the fine tuning to include one- and two-loop corrections to the effective potential in the fine tuning measure.
+It is therefore important when studying the fine tuning to include loop corrections to the effective potential in the fine tuning measure.
 To do so it is most convenient to work in terms of the EWSB conditions Eq.

### 2014-12-18 paper/e6ssm-tuning-paper.tex
got rid of end of line symbols that were visiable in emacs due to mess up between editors.
Changed discussion about figure 1 for clarity.

@@
-\documentclass[preprint,amsmath,amssymb,aps,superscriptaddress,prd,showpacs,floatfix]{revtex4-1}
+\documentclass[preprint,amsmath,amssymb,aps,superscriptaddress,prd,showpacs,floatfix,nofootinbib]{revtex4-1}
 
@@
 \usepackage{hyperref}
-
+\usepackage{footmisc}
 % macros
@@
 \newcommand{\SuperField}[1]{\hat{#1}}
+
+ \renewcommand\footnotelayout{\fontsize{10}{9}\selectfont}
+
 \allowdisplaybreaks
@@
 \section{\label{sec:model}U(1) extensions and the E$_6$SSM}
-In this paper we consider U(1) extensions of the MSSM where the gauge group at low energies is,
- \be
-SU(3)_C\times SU(2)_W\times U(1)_Y\times U(1)^\prime, \ee 
-where $U(1)^\prime$ is the new gauge group beyond that of the SM and MSSM.
-The minimal superfield content of $U(1)$ extensions which solve the $\mu$-problem should be ordinary left handed quark, $\hat{Q}_i$ and lepton $\hat{L}_i$ ($i=1,2,3$)superfields along with right handed superfields $\hat{u}^c_i$, $\hat{d}^c_i$,  $\hat{e}^c_i$ ($i=1,2,3$) for the up-type (s)quarks, down-type (s)quarks and charged (s)leptons respectively and three Higgs superfields, up-type $\hat{H}_u$, down-type $\hat{H}_d$ and a singlet under the SM gauge group $\hat{S}$.
+In this paper we consider U(1) extensions of the MSSM where the gauge
+group at low energies is, \be SU(3)_C\times SU(2)_W\times U(1)_Y\times
+U(1)^\prime, \ee where $U(1)^\prime$ is the new gauge group beyond
+that of the SM and MSSM. The minimal superfield content of $U(1)$
+extensions which solve the $\mu$-problem should be ordinary left
+handed quark, $\hat{Q}_i$ and lepton $\hat{L}_i$
+($i=1,2,3$)superfields along with right handed superfields
+$\hat{u}^c_i$, $\hat{d}^c_i$, $\hat{e}^c_i$ ($i=1,2,3$) for the
+up-type (s)quarks, down-type (s)quarks and charged (s)leptons
+respectively and three Higgs superfields, up-type $\hat{H}_u$,
+down-type $\hat{H}_d$ and a singlet under the SM gauge group
+$\hat{S}$.
 
-  The couplings for the $U(1)^\prime$ gauge group should allow the following renormalisable superpotential terms required in the USSM,
-\be
-W_{USSM} =  y^U_{ij} \hat{u}^c_i \hat{H}_u \hat{Q}_j + y^D_{ij} \hat{d}^c_i \hat{H}_d \hat{Q}_j + y^E_{ij} \hat{e}^c_i \hat{H}_d \hat{L}_j + \lambda \hat{S} \hat{H}_d \hat{H}_u,
-\ee with $i,j \in \{1,2,3\}$.
+  The couplings for the $U(1)^\prime$ gauge group should allow the
+  following renormalisable superpotential terms required in the USSM,
+  \be W_{USSM} = y^U_{ij} \hat{u}^c_i \hat{H}_u \hat{Q}_j + y^D_{ij}
+  \hat{d}^c_i \hat{H}_d \hat{Q}_j + y^E_{ij} \hat{e}^c_i \hat{H}_d
+  \hat{L}_j + \lambda \hat{S} \hat{H}_d \hat{H}_u, \ee with $i,j \in
+  \{1,2,3\}$.
 
@@
 
-Nonetheless while this model is very elegant so far, the  superpotential, (\ref{Eq:e6-superpot}) contains dangerous terms which can induce proton decay and lead to large flavour changing neutral currents (FCNCs).
-There are a number of approaches to suppress these terms, involving the use of different discrete symmetries.
-Here for the purposes of renormalisation group running we will simply include the following unsuppressed superpotential terms, which follows the approach taking in work on the cE$_6$SSM \cite{Athron:2009ue, Athron:2009bs},
+Nonetheless while this model is very elegant so far, the
+superpotential, (\ref{Eq:e6-superpot}) contains dangerous terms which
+can induce proton decay and lead to large flavour changing neutral
+currents (FCNCs).  There are a number of approaches to suppress these
+terms, involving the use of different discrete symmetries.  Here for
+the purposes of renormalisation group running we will simply include
+the following unsuppressed superpotential terms, which follows the
+approach taking in work on the cE$_6$SSM \cite{Athron:2009ue,
+  Athron:2009bs},
 %
@@
 \end{align}
-In these expressions $g_2$, $g'=\sqrt{3/5}g_1$, and $g_1'$ are the $SU(2)$, (non-GUT normalized) $U(1)_Y$ and $U(1)'$ gauge couplings, respectively, and $\bar{g}^2=g_2^2+g'^2$.
-The charges $\tilde{Q}_1$, $\tilde{Q}_2$ and $\tilde{Q}_S$ are effective $U(1)'$ charges for $H_1$, $H_2$ and $S$, respectively.
-Note that the $SU(2)$ dot product is defined by $A\cdot B\equiv \epsilon_{\alpha\beta}A^\alpha B^\beta=A^2B^1-A^1B^2$.
-The term $\Delta V_{E_6}$ contains the Coleman-Weinberg contributions to the effective potential.
-In the case of the $U(1)_\chi$ model, $V_{E_6}^F$ may also contain an elementary $\mu$ term contribution, as occurs in the MSSM.\\ \\
-Demanding that the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real VEVs of the form
+In these expressions $g_2$, $g'=\sqrt{3/5}g_1$, and $g_1'$ are the
+$SU(2)$, (non-GUT normalized) $U(1)_Y$ and $U(1)'$ gauge couplings,
+respectively, and $\bar{g}^2=g_2^2+g'^2$. The charges $\tilde{Q}_1$,
+$\tilde{Q}_2$ and $\tilde{Q}_S$ are effective $U(1)'$ charges for
+$H_1$, $H_2$ and $S$, respectively. Note that the $SU(2)$ dot product
+is defined by $A\cdot B\equiv \epsilon_{\alpha\beta}A^\alpha
+B^\beta=A^2B^1-A^1B^2$. The term $\Delta V_{E_6}$ contains the
+Coleman-Weinberg contributions to the effective potential. In the case
+of the $U(1)_\chi$ model, $V_{E_6}^F$ may also contain an elementary
+$\mu$ term contribution, as occurs in the MSSM.\\ \\ Demanding that
+the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real VEVs of
+the form
 \begin{equation}\label{eq:E6vevs}
@@
 \end{align*}
-Written in the form of Eq.
-(\ref{eq:E6MZequation}) we see the potential new source of fine tuning alluded to above, in the form of the third term on the right-hand side.
-For large values of the VEV $s$, the $D$-term contributions can be quite a bit larger than $M_Z^2$.
-In particular, recent experimental limits \cite{Aad:2014cka} require that the $Z'$ mass be large, with bounds of $M_{Z'}\gtrsim 2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim 2.62$ TeV in $U(1)_\chi$ models.
-To satisfy these limits typically requires large values of the singlet VEV $s$.
-For example $s\gtrsim 6$ TeV is required in the E$_6$SSM with $U(1)'=U(1)_N$, so that $|D_{H_1}|,|D_{H_2}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq 0$.
-As a result the remaining terms on the right-hand side of Eq.
-(\ref{eq:E6MZequation}) must be tuned to cancel the resulting very large contribution to $M_Z$.
-Moreover, because this is a large tree level fine tuning, it may negate the increase in naturalness that is associated with having a reduced need for heavy superpartners.
-In $U(1)$ extended models for which $\tilde{Q}_S\neq 0$, the importance of the $Z^\prime$ mass to the fine tuning in these models can be made even clearer by writing Eq.
-(\ref{eq:E6MZequation}) in the form given in \cite{Athron:2013ipa},
+Written in the form of Eq. (\ref{eq:E6MZequation}) we see the
+potential new source of fine tuning alluded to above, in the form of
+the third term on the right-hand side. For large values of the VEV
+$s$, the $D$-term contributions can be quite a bit larger than
+$M_Z^2$. In particular, recent experimental limits \cite{Aad:2014cka}
+require that the $Z'$ mass be large, with bounds of $M_{Z'}\gtrsim
+2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim 2.62$ TeV in
+$U(1)_\chi$ models. To satisfy these limits typically requires large
+values of the singlet VEV $s$. For example $s\gtrsim 6$ TeV is
+required in the E$_6$SSM with $U(1)'=U(1)_N$, so that
+$|D_{H_1}|,|D_{H_2}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq
+0$. As a result the remaining terms on the right-hand side of
+Eq. (\ref{eq:E6MZequation}) must be tuned to cancel the resulting very
+large contribution to $M_Z$. Moreover, because this is a large tree
+level fine tuning, it may negate the increase in naturalness that is
+associated with having a reduced need for heavy superpartners. In
+$U(1)$ extended models for which $\tilde{Q}_S\neq 0$, the importance
+of the $Z^\prime$ mass to the fine tuning in these models can be made
+even clearer by writing Eq. (\ref{eq:E6MZequation}) in the form given
+in \cite{Athron:2013ipa},
 \begin{equation}\label{eq:originalE6MZequation}
@@
 \subsection{\label{subsec:tuningmeasure}The Fine Tuning Measure}
-As stated above, in order to quantify the resulting fine tuning we apply the traditional Ellis-Barbieri-Giudice measure \cite{Ellis:1986yg,Barbieri:1987fn}.
-A specific model is characterised by a set of $n$ model parameters $\{p_i\}$ and is defined at some input scale $M_X$.
-For a given parameter $p$ in this set, one computes an associated sensitivity coefficient \cite{Feng:2013pwa}
+As stated above, in order to quantify the resulting fine tuning we
+apply the traditional Ellis-Barbieri-Giudice measure
+\cite{Ellis:1986yg,Barbieri:1987fn}. A specific model is characterised
+by a set of $n$ model parameters $\{p_i\}$ and is defined at some
+input scale $M_X$. For a given parameter $p$ in this set, one computes
+an associated sensitivity coefficient \cite{Feng:2013pwa}
 \begin{equation}\label{eq:bgmeasure}
@@
 %    - tuning as a function of stop mass for the MSSM and E6SSM
-Many recent papers have focussed on light stops as allowing natural
-SUSY and there has been a lot of theoretical effort to find SUSY
-models with a $125$ GeV Higgs boson while still having light stops
-and experimental efforts to search for light stops.  This is entirely
-appropriate, however the fine tuning problem from the stops depends
-crucially on the RG evolution from the GUT scale, since this is how
-the squark masses feed into the soft Higgs masses that appear in the
-EWSB conditions.
+As discussed in the introduction many recent papers have focussed on
+light stops as allowing natural SUSY and there has been a lot of
+theoretical effort to find SUSY models with a $125$ GeV Higgs boson
+while still having light stops and experimental efforts to search for
+light stops.  This is entirely appropriate since there are many good
+reasons to expect the soft masses to be set at high energies.  However
+that is not the only possibility and the fine tuning problem depends
+strongly the RG evolution from the GUT scale, as the soft Higgs masses
+that appear in the EWSB conditions pick up contributions from the soft
+squark masses.
 
@@
 \end{figure}
-To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the variation in fine
-tuning when we scan over the
-stop masses and mixing, with $500 \textrm{ GeV} \leq
-m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq
-A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
-The remaining parameters we fix such that at $M_{SUSY}$ they have the values $\mu=-97.5$ GeV, $B=-84.8$ GeV,
-$M_1=92.1$ GeV, $M_2=95.9$ GeV, $M_3=352$ GeV, $A_b=-117.9$ GeV, $A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV, $m_{e_i}=204$ GeV,
-$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV ($i=1,2,3$). By making this choice for the 
-remaining parameters we ensure that fine tuning due to each is small, allowing us to see the fine tuning
-impact of the stops for stop masses of less than 1 TeV. For models in which the spectrum is heavier the fine tuning
-reaches a lower bound imposed by other heavier parameters as the stop masses become very small.
-Note that the Higgs mass is also allowed to vary over the scan, as shown in 
-Fig.~\ref{Fig:mssmhiggstuning}.
-However this tuning only really becomes large for very large stop
-masses.  On the other hand if the cuttoff is increased then stop masses of
-several TeV can result in tuning of [insert] as shown in
-Fig.~\ref{Fig:mssmstoptuning}.\\ \\
+To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the
+variation in fine tuning when we scan over the stop masses and mixing,
+with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and
+$-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV,
+$50$ TeV and $100$ TeV.  The remaining parameters we fix such that at
+$M_{SUSY}$ they have the values $\mu=-97.5$ GeV, $B=-84.8$ GeV,
+$M_1=92.1$ GeV, $M_2=95.9$ GeV, $M_3=352$ GeV, $A_b=-117.9$ GeV,
+$A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV, $m_{e_i}=204$ GeV,
+$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV
+($i=1,2,3$). By making this choice for the remaining parameters we
+ensure that fine tuning due to each is small, so that we avoid washing
+out the fine tuning impact of the stops when the tuning is
+small \footnote{For models in which the spectrum is heavier, when the
+  stop masses become very small the fine tuning reaches a lower bound
+  imposed by other heavier parameters.} as can be the case when the
+stop masses are less than 1 TeV.  Note that the Higgs mass is also
+allowed to vary over the scan, as shown in
+Fig.~\ref{Fig:mssmhiggstuning}.  However this tuning only really
+becomes large for very large stop masses.  On the other hand if the
+cuttoff is increased then stop masses of several TeV can result in
+tuning of [insert] as shown in Fig.~\ref{Fig:mssmstoptuning}.\\ \\
 
@@
 
-As can be seen in Fig.~\ref{} the severity of the tunings varies quite a
-bit.  This is because the charges appear as coefficients in front of
+As can be seen in Fig.~\ref{} the severity of the tunings varies quite
+a bit.  This is because the charges appear as coefficients in front of
 the $Z^\prime$ mass in the EWSB condition.  These charges change the
-value of the coefficient $d$ in Eq. (\ref{eq:originalE6MZequation}).  The values of the
-coefficient $d$ in each model, for $\tan\beta = 10$, is $\{-0.01, 0.40, 0.50, 0.81 \}$ for
-$\{U(1)_I, U(1)_N, U(1)_\psi, U(1)_\eta \}$ and this determines which
-of the models are most tuned.
+value of the coefficient $d$ in Eq. (\ref{eq:originalE6MZequation}).
+The values of the coefficient $d$ in each model, for $\tan\beta = 10$,
+is $\{-0.01, 0.40, 0.50, 0.81 \}$ for $\{U(1)_I, U(1)_N, U(1)_\psi,
+U(1)_\eta \}$ and this determines which of the models are most tuned.
 

### 2014-12-18 paper/e6ssm-tuning-paper.tex
rephrased first paragraph of results section.  Hopefully reads better now.

@@
-\documentclass[preprint,amsmath,amssymb,aps,superscriptaddress,prd,showpacs,floatfix,nofootinbib]{revtex4-1}
+\documentclass[preprint,amsmath,amssymb,aps,superscriptaddress,prd,showpacs,floatfix]{revtex4-1}
 
@@
 \usepackage{hyperref}
-\usepackage{footmisc}
+
 % macros
@@
 \newcommand{\SuperField}[1]{\hat{#1}}
-
- \renewcommand\footnotelayout{\fontsize{10}{9}\selectfont}
-
 \allowdisplaybreaks
@@
 \end{figure}
-To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the
-variation in fine tuning when we scan over the stop masses and mixing,
-with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and
-$-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV,
-$50$ TeV and $100$ TeV.  The remaining parameters we fix such that at
-$M_{SUSY}$ they have the values $\mu=-97.5$ GeV, $B=-84.8$ GeV,
-$M_1=92.1$ GeV, $M_2=95.9$ GeV, $M_3=352$ GeV, $A_b=-117.9$ GeV,
-$A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV, $m_{e_i}=204$ GeV,
-$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV
-($i=1,2,3$). By making this choice for the remaining parameters we
-ensure that fine tuning due to each is small, so that we avoid washing
-out the fine tuning impact of the stops when the tuning is
-small \footnote{For models in which the spectrum is heavier, when the
-  stop masses become very small the fine tuning reaches a lower bound
-  imposed by other heavier parameters.} as can be the case when the
-stop masses are less than 1 TeV.  Note that the Higgs mass is also
-allowed to vary over the scan, as shown in
-Fig.~\ref{Fig:mssmhiggstuning}.  However this tuning only really
-becomes large for very large stop masses.  On the other hand if the
-cuttoff is increased then stop masses of several TeV can result in
-tuning of [insert] as shown in Fig.~\ref{Fig:mssmstoptuning}.\\ \\
+To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the variation in fine
+tuning when we scan over the
+stop masses and mixing, with $500 \textrm{ GeV} \leq
+m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq
+A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
+The remaining parameters we fix such that at $M_{SUSY}$ they have the values $\mu=-97.5$ GeV, $B=-84.8$ GeV,
+$M_1=92.1$ GeV, $M_2=95.9$ GeV, $M_3=352$ GeV, $A_b=-117.9$ GeV, $A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV, $m_{e_i}=204$ GeV,
+$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV ($i=1,2,3$). By making this choice for the 
+remaining parameters we ensure that fine tuning due to each is small, allowing us to see the fine tuning
+impact of the stops for stop masses of less than 1 TeV. For models in which the spectrum is heavier the fine tuning
+reaches a lower bound imposed by other heavier parameters as the stop masses become very small.
+Note that the Higgs mass is also allowed to vary over the scan, as shown in 
+Fig.~\ref{Fig:mssmhiggstuning}.
+However this tuning only really becomes large for very large stop
+masses.  On the other hand if the cuttoff is increased then stop masses of
+several TeV can result in tuning of [insert] as shown in
+Fig.~\ref{Fig:mssmstoptuning}.\\ \\
 

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Changed discussion on fig 2 a bit.

--- 2014-12-18 paper/e6ssm-tuning-paper.tex
@@
 $m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV
-($i=1,2,3$). By making this choice for the remaining parameters we
-ensure that fine tuning due to each is small, so that we avoid washing
-out the fine tuning impact of the stops when the tuning is
-small \footnote{For models in which the spectrum is heavier, when the
-  stop masses become very small the fine tuning reaches a lower bound
+($i=1,2,3$). Although we should stress that making this choice will
+lead to a spectrum which is in conflict with the LHC limits, doing so
+ensures that fine tuning due to the other parameters is small, so that
+we avoid washing out the fine tuning impact of the stops when the
+tuning is small \footnote{For models in which the spectrum is heavier,
+  when the stop masses are small the fine tuning reaches a lower bound
   imposed by other heavier parameters.} as can be the case when the
 stop masses are less than 1 TeV.  Note that the Higgs mass is also
-allowed to vary over the scan, as shown in
-Fig.~\ref{Fig:mssmhiggstuning}.  However this tuning only really
-becomes large for very large stop masses.  On the other hand if the
-cuttoff is increased then stop masses of several TeV can result in
-tuning of [insert] as shown in Fig.~\ref{Fig:mssmstoptuning}.\\ \\
+allowed to vary in this scan, as shown in
+Fig.~\ref{Fig:mssmhiggstuning}. This reveals the tuning problem which
+people have been worrying about since the discovery of the 125 GeV
+Higgs boson as we see that raising the stop masses is also pushing up
+the Higgs mass, meaning that heavier Higgs masses require more fine
+tuning.  However for a low value of the UV scale this tuning is not so
+severe unless the stops are very heavy, and a 125 geV Higgs can be
+obtained without much tuning in this unrealistic case where we have
+minimised other sources of tuning.  On the other hand the tuning
+becomes more severe as we increase the cuttoff such that for $M_X =
+10^{16}$ GeV is increased then a lightest stop masses of 1-3 TeV can
+result in a fine tuning of $\approx 200 - 1000$ as shown in
+Fig.~\ref{Fig:mssmstoptuning} and the minimum tuning we see consistent with a $125$ GeV Higgs is $\approx 200$.\\ \\
 

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Edited decscription of which parameters are fixed and varied to make argument clearer. This could still do with a lot more work though.

@@
 the derivatives which appear in these tuning are also similar to the
-Bayesian motivated measure so there should not be too large a discrepancy between the two approaches.
+Bayesian motivated measure so there should not be too large a
+discrepancy between the two approaches.
 
@@
 we avoid washing out the fine tuning impact of the stops when the
-tuning is small \footnote{For models in which the spectrum is heavier,
+tuning is small\footnote{For models in which the spectrum is heavier,
   when the stop masses are small the fine tuning reaches a lower bound
@@
 becomes more severe as we increase the cuttoff such that for $M_X =
-10^{16}$ GeV is increased then a lightest stop masses of 1-3 TeV can
-result in a fine tuning of $\approx 200 - 1000$ as shown in
-Fig.~\ref{Fig:mssmstoptuning} and the minimum tuning we see consistent with a $125$ GeV Higgs is $\approx 200$.\\ \\
+10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
+tuning of $\approx 200 - 1000$ as shown in
+Fig.~\ref{Fig:mssmstoptuning} and the minimum tuning we see consistent
+with a $125$ GeV Higgs is $\approx 200$, as shown in
+Fig.~\ref{Fig:mssmhiggstuning}.
 
@@
 
-Since the stop mass does not have a large impact on the fine tuning when the 
-cutoff scale is very low we can use this to see more clearly the impact of the
-$Z^\prime$ mass on fine tuning. To do so we select a fixed low cutoff of $M_X=20$ TeV and compare the
-fine tuning for two different values of the $Z^\prime$ mass. We choose to look at
-$M_{Z^\prime}=2.5$ TeV, which is just above the current limits, and $M_{Z^\prime}=4.5$ TeV, 
-which should be in reach in run II at the LHC. We also compare the fine tuning calculated
-in each case to the tuning in the MSSM. For this, we have performed a parameter space scan in both the 
-MSSM and E$_6$SSM, scanning over those parameters that appear at tree level in the EWSB conditions in the
-models. While the contribution from large stop masses to the fine tuning is small for such a low cut-off scale, the 
-stop contributions to the effective potential can play a significant role in reducing the fine tuning.
-For this reason it is still important to properly treat the tuning associated with stop contributions to the one-loop effective potential, and so we also scan over the soft masses $m_{Q_3}^2$, $m_{u_3}^2$ and the stop mixing $A_t$.
-The relevant parameters and ranges that were scanned over are summarised in Table \ref{tab:scanranges}.
-With the exception of the stop mixing $A_t$ and the soft trilinear $A_\lambda$, which are logarithmically scanned, all parameters are linearly scanned.
-In both the MSSM and E$_6$SSM, we then decouple all other parameters by setting the remaining soft masses to values of $5$ TeV, while the first and second generation Yukawa couplings and their associated soft trilinears are taken to vanish.
-The $U(1)$ gaugino soft mass $M_1$ was fixed to $M_1=300$ GeV, and we fix $M_3=2000$ GeV.
-Additionally, in the E$_6$SSM the $U(1)_N$ gaugino soft mass $M_1'$ is held fixed with $M_1'=M_1=300$ GeV, and $\mu^\prime=5$ TeV.
+Since the stop mass does not have such a large impact on the fine
+tuning when the cutoff scale is very low we can use this to see more
+clearly the impact of the $Z^\prime$ mass on fine tuning. To do so we
+select a fixed low cutoff of $M_X=20$ TeV and compare the fine tuning
+for two different values of the $Z^\prime$ mass. We choose to look at
+$M_{Z^\prime}=2.5$ TeV, which is just above the current limits, and
+$M_{Z^\prime}=4.5$ TeV, which should be in reach in run II at the LHC
+and then compare the fine tuning calculated in each case to the tuning
+in the MSSM.  For this, we have performed a large six dimensional
+parameter space scan in both the MSSM and E$_6$SSM, varying those
+parameters most relevant for the fine tuning and the Higgs mass.
+Therefore the set of parameters which we vary includes $\mu$, $B$ and
+$\tan \beta$ for the MSSM, and $\lambda$, $A_\lambda$ and $\tan
+\beta$, for the E$_6$SSM, which appear at tree level in the EWSB
+conditions of the models. While the contribution from large stop
+masses to the fine tuning is small for such a low cut-off scale, the
+stop contributions to the effective potential can play a significant
+role in reducing the fine tuning.  For this reason it is still
+important to properly treat the tuning associated with stop
+contributions to the one-loop effective potential, and so we also scan
+over the soft masses $m_{Q_3}^2$, $m_{u_3}^2$ and the stop mixing
+$A_t$.  The relevant parameters and ranges that were scanned over are
+summarised in Table \ref{tab:scanranges}. With the exception of the
+stop mixing $A_t$ and the soft trilinear $A_\lambda$, which are
+logarithmically scanned, all parameters are linearly scanned.  In
+addition to this we also repeat each scan for three different values
+of $M_2$ to introduce more variation in the chargino masses, which can
+also be importnat due to the link between $\mu$ and the fine tuning.
+
+ In this case we now consider realistic scenarios, where the
+ parameters that are not scanned over are set to values which keep the
+ associated states comfortably above their experimental limits.  So in
+ both the MSSM and E$_6$SSM, all other soft [scalar?] masses are set
+ to $5$ TeV.  Since we work in the third family approximation, taking
+ the first and second generation Yukawa couplings to be zero, we also
+ assume their associated soft trilinears vanish [what about
+   $A_\tau$?]. The $U(1)$ gaugino soft mass $M_1$ was fixed to
+ $M_1=300$ GeV, and we fix $M_3=2000$ GeV. Additionally, in the
+ E$_6$SSM the $U(1)_N$ gaugino soft mass $M_1'$ is held fixed with
+ $M_1'=M_1=300$ GeV, and $\mu^\prime=5$ TeV.
+
 \begin{table}[h]
@@
 \end{ruledtabular}
-\caption{The parameters scanned over and the ranges of values used in the MSSM and the $E_6$ models.}
+\caption{The parameters scanned over and the ranges of values used in the MSSM and the $E_6SSM$ models.}
 \label{tab:scanranges}

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Added some more discussion of the chargino limits.

@@
 \end{figure}
-In Fig \ref{Fig:e6ssmvsmssm} we see that as expected the minimum
+In Fig \ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
+the tuning for each case against the lightest Higgs mass.  As expected
+the dependence on the Higgs mass is now quite weak, while the minimum
 tuning in the model for the E$_6$SSM is increased by the mass of the
-$Z^\prime$ boson.  Since with such a low cutoff the stop masses have
-little impact on the tuning, the tuning here also does not depend much
-on the Higgs mass.  However the tuning from the $Z^\prime$ mass
-appears already at tree level and is unavoidable regardless of the
-cutoff scale chosen.
+$Z^\prime$ boson.  So in the case of a very low cutoff much of the
+tuning required to get a 125 GeV Higgs has gone away.  However the
+tuning from the $Z^\prime$ mass appears already at tree level and is
+unavoidable regardless of the cutoff scale chosen, so in the E$_6$SSM
+current limits on the mass of the $Z^\prime$ boson imply that the
+E$_6$SSM fine tuning must be at least 100 regardless of assumptions
+about the way SUSY breaking happens.  Additionally if run II of the
+LHC pushes the limit on the $Z^\prime$ mass to be above $4.5$ TeV then
+the fine tuning in the model will be greater than at least 350.
 
-Therefore the tuning in these models depends on less assumptions than
-the tuning which concerns people in the MSSM and the lowest tuned
-models are adderessed directly with $Z^\prime$ searches.
+This demopnstrates two important points about these $U(1)$
+extensions. Firstly that limits on the $Z^\prime$ mass play an
+incredibly important role in constraining natural scenarios in such
+models and secondly that the tuning from the $Z^\prime$ limits in
+these models depends on less assumptions about SUSY breaking than the
+tuning reqyired by the $125$ GeV Higgs measurement which concerns
+people in the MSSM.
 
-In the MSSM the tuning can also be attcked more directly by looking at
-chargino mass limikts as this rasies $\mu$ directly.  [Stuff about
-  chargino limits, then show plots in MSSM and E6SSM]
+However we should also acknowledge that there are other limits which
+play a similar role.  Chargino limits directly constrain the $\mu$
+parameter (or effective $\mu$ parameter in these $U(1)$ extensions).
+Unfortunately the chargino limits from the LHC are not general enough
+so as to provide an absolute constraint on the model [Add: XSdetails on
+  limits and what they depend on].
+
+Nonetheless the MSSM the impact of chargino limit is shown in
+Fig. \cite{}.  There we see that if the the full parameter space with
+$m_{\chi^\pm} < 700$ GeV was excluded the impact would be to make the
+tuning in the MSSM with a $20$ TeV cuttoff slightly worse than that of
+the E$_6$SSM with the same cuttoff and a $Z^\prime$ mass just larger
+than current limits.  would be similar to that can also be attcked
+more directly by looking at chargino mass limits as this rasies $\mu$
+directly.  In the E$_6$SSM, while raising the chargino limit can have
+the same impact in princuiple, due to current limits on the $Z^\prime$
+mass already imposing a significant degree of tuning, chargino masses
+do not make much of a noticable change.
+
+[show plots in MSSM and E6SSM if it gets clened up, though maybe we
+  can just leave it out if it only shows that there is no big impact?]
 %    - plots of chargino bound impacts

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Added other U(1) tunings to teh draft..

@@
 The exact level of tuning from the $Z^\prime$ depends on the charges of
-the extra $U(1)$ gauge symmetry it is associated with.  In Fig \ref{}
+the extra $U(1)$ gauge symmetry it is associated with.  In Fig.~\ref{}
 we look at the fine tuning for other U(1) extensions for the same
@@
 %      U(1)_\eta \theta = -\arctan\sqrt{5/3}
+
+\begin{figure}[h]
+\begin{center}
+\resizebox{!}{5cm}{%
+\includegraphics{e6inert_tb10_tuning_vs_higgs.png}}
+\resizebox{!}{5cm}{%
+\includegraphics{e6psi_tb10_tuning_vs_higgs.png}}\\
+\resizebox{!}{5cm}{%
+\includegraphics{e6eta_tb10_tuning_vs_higgs.png}}
+\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
+  MSSM (green), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue) and
+  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red).}
+\label{Fig:e6ssmvsmssm}
+\end{center}
+\end{figure}
 
@@
 Finally we want to emphasise that while in Fig.~\ref{Fig:e6ssmvsmssm}
-the E$_6$SSM looks more fine tuned than the MSSM this is depends on
-the cutoff scale.  Indeed in \cite{Athron:2013ipa} a constrained
-version of the E$_6$SSM, with the cuttoff at the GUT scale, is
-considered and there the cE$_6$SSM was found to be less tuned than the
-cMSSM. Since a 125 GeV Higgs can be achieved in the E$_6$SSM with
-ligher stops, then if the cutoff is large, the larger stop masses can
-make that model more fine tuned due to large RGE effects.
+the E$_6$SSM looks more fine tuned than the MSSM this depends on the
+cutoff scale.  Indeed in \cite{Athron:2013ipa} a constrained version
+of the E$_6$SSM, with the cuttoff at the GUT scale, is considered and
+there the cE$_6$SSM was found to be less tuned than the cMSSM. Since a
+125 GeV Higgs can be achieved in the E$_6$SSM with ligher stops, then
+if the cutoff is large, the larger stop masses of the MSSM can make
+that model more fine tuned due to large RGE effects.
 

### 2014-12-18 paper/e6ssm-tuning-paper.tex
half assed edit of caption, should add proper details later.
Added comments on the inert model.

@@
 Nonetheless the MSSM the impact of chargino limit is shown in
-Fig. \cite{}.  There we see that if the the full parameter space with
+Fig.~\ref{}.  There we see that if the the full parameter space with
 $m_{\chi^\pm} < 700$ GeV was excluded the impact would be to make the
@@
 
-The exact level of tuning from the $Z^\prime$ depends on the charges of
-the extra $U(1)$ gauge symmetry it is associated with.  In Fig.~\ref{}
-we look at the fine tuning for other U(1) extensions for the same
-$Z^\prime$ masses as we did for the E$_6$SSM.
+The exact level of tuning from the $Z^\prime$ depends on the charges
+of the extra $U(1)$ gauge symmetry it is associated with.  In
+Fig.~\ref{Fig:othere6modelsvsmssm} we look at the fine tuning for
+other U(1) extensions for the same $Z^\prime$ masses as we did for the
+E$_6$SSM.  To simplify the analysis we fix $\tan \beta = 10$, but scan
+over the remaining parameters as in Table \ref{tab:scanranges} and fix
+the rest to the same values we did in the scan carried out for
+Fig.~\ref{Fig:e6ssmvsmssm}
 % - plots for different U(1)' charge
@@
 \includegraphics{e6eta_tb10_tuning_vs_higgs.png}}
-\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
-  MSSM (green), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue) and
-  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red).}
-\label{Fig:e6ssmvsmssm}
+\caption{Scatter plot of fine tuning vs lightest Higgs mass in ... with $M_{Z^\prime} = 2.5$ TeV shown in blue and $M_{Z^\prime} = 4.5$ TeV in red.}
+\label{Fig:othere6modelsvsmssm}
 \end{center}
@@
 
-As can be seen in Fig.~\ref{} the severity of the tunings varies quite
+As can be seen in Fig.~\ref{Fig:othere6modelsvsmssm} the severity of the tunings varies quite
 a bit.  This is because the charges appear as coefficients in front of
@@
 U(1)_\eta \}$ and this determines which of the models are most tuned.
+
+Interestingly the coefficient $d$ is very small (and negative) in the
+case of the $U(1)_\eta$.  This allows a dramatic reduction in the fine
+tuning from the $U(1)_I$ symmetry.  This is a result of the $H_u$
+charge associated with $U(1)_I$ vansihing, which means that the
+D-terms to the lightest Higgs which is predominantly $H_u$ at large
+$\tan \beta$ are suppressed, making it difficult to raise the Higgs
+mass in the same way as happens in the other models, explaining why
+the heavier Higgs values are less well populated [can't be obtained? -
+are we sure those scattered points are valid?]  than in the other
+models.  Therefore the fine tuining behaviour in this model is closer
+to that of the MSSM, though the LHC can still constrain the most
+natural scenarions from just placing tougher limits on the $Z^\prime$
+mass .
 

### 2014-12-19 paper/e6ssm-tuning-paper.tex
Added more detail about fixed parameters, changed \eta -> I

@@
  associated states comfortably above their experimental limits.  So in
- both the MSSM and E$_6$SSM, all other soft [scalar?] masses are set
+ both the MSSM and E$_6$SSM, all other soft scalar masses are set
  to $5$ TeV.  Since we work in the third family approximation, taking
  the first and second generation Yukawa couplings to be zero, we also
- assume their associated soft trilinears vanish [what about
-   $A_\tau$?]. The $U(1)$ gaugino soft mass $M_1$ was fixed to
+ assume their associated soft trilinears vanish. Similarly we take
+$A_b=A_\tau=0$ GeV. The $U(1)$ gaugino soft mass $M_1$ was fixed to
  $M_1=300$ GeV, and we fix $M_3=2000$ GeV. Additionally, in the
@@
 Interestingly the coefficient $d$ is very small (and negative) in the
-case of the $U(1)_\eta$.  This allows a dramatic reduction in the fine
+case of the $U(1)_I$.  This allows a dramatic reduction in the fine
 tuning from the $U(1)_I$ symmetry.  This is a result of the $H_u$

### 2014-12-19 paper/e6ssm-tuning-paper.tex
Added temporary comment

@@
 mass in the same way as happens in the other models, explaining why
+% DH:: I strongly suspect that they are invalid - but running scan
+% to check this currently
 the heavier Higgs values are less well populated [can't be obtained? -

### 2014-12-19 paper/e6ssm-tuning-paper.tex
started writing conclusions badly.  may change whole thing...

--- 2014-12-18 paper/e6ssm-tuning-paper.tex
@@
 Model (E$_6$SSM)\cite{King:2005jy,King:2005my,Athron:2010zz}.  In this
-model since the right handed neutrino remains interaction-less they may
-explain the tiny observed masses of neutrinos via the see-saw
+model since the right handed neutrino remains interaction-less they
+may explain the tiny observed masses of neutrinos via the see-saw
 mechanism and the baryon asymmetry in the universe via leptogenesis
-\cite{Hambye:2000bn,King:2008qb, King:2008gw}.  Recently it has also been studied in the context of electroweak baryogenesis \cite{Chao:2014hya}.
+\cite{Hambye:2000bn,King:2008qb, King:2008gw}.  Recently it has also
+been studied in the context of electroweak baryogenesis
+\cite{Chao:2014hya}.
 
@@
 
-The impact of gauge kinetic
-mixing in the case where both of the extra U(1)'s appearing from the
-breakdown of E$_6$ are present at low energy was studied in
-\cite{Rizzo:2012rf}.  The E$_6$SSM was also included in a studies looking
-at how first or second generation sfermion masses can be used to
-constrain the GUT scale parameters \cite{Miller:2012vn} and the
-renormalization of VEVs \cite{Sperling:2013eva, Sperling:2013xqa}.
-The particle spectrum and  collider signatures of constrained version of the E$_6$SSM have been studied in a series of papers,
-\cite{Athron:2009ue,Athron:2009bs,Athron:2011wu,Athron:2012sq}. The threshold
-corrections to the $\overline{DR}$ gauge and Yukawa couplings in the
-E$_6$SSM were calculated and the numerical impact in the constrained
-version examined \cite{Athron:2012pw}.
+The impact of gauge kinetic mixing in the case where both of the extra
+U(1)'s appearing from the breakdown of E$_6$ are present at low energy
+was studied in \cite{Rizzo:2012rf}.  The E$_6$SSM was also included in
+a studies looking at how first or second generation sfermion masses
+can be used to constrain the GUT scale parameters \cite{Miller:2012vn}
+and the renormalization of VEVs \cite{Sperling:2013eva,
+  Sperling:2013xqa}.  The particle spectrum and collider signatures of
+constrained version of the E$_6$SSM have been studied in a series of
+papers,
+\cite{Athron:2009ue,Athron:2009bs,Athron:2011wu,Athron:2012sq}. The
+threshold corrections to the $\overline{DR}$ gauge and Yukawa
+couplings in the E$_6$SSM were calculated and the numerical impact in
+the constrained version examined \cite{Athron:2012pw}.
 
@@
 To quantify the fine tuning we will employ the traditional
-Barbieri-Giudice measure \cite{Ellis:1986yg,Barbieri:1987fn}.  This has
-been used extensively within the literature
-e.g.
-\cite{deCarlos:1993yy, deCarlos:1993ca, Chankowski:1997zh, Agashe:1997kn, Wright:1998mk, Kane:1998im, BasteroGil:1999gu, Feng:1999zg, Allanach:2000ii, Dermisek:2005ar, Barbieri:2005kf, Allanach:2006jc, Gripaios:2006nn, Dermisek:2006py, Barbieri:2006dq, Kobayashi:2006fh, Perelstein:2012qg, Antusch:2012gv,Cheng:2012pe, CahillRowley:2012rv, Ross:2012nr, Basak:2012bd, Kang:2012sy, Athron:2013ipa,Miller:2013jra, Binjonaid:2014oga, Miller:2014jza}.
+Barbieri-Giudice measure \cite{Ellis:1986yg,Barbieri:1987fn}.  This
+has been used extensively within the literature
+e.g. \cite{deCarlos:1993yy, deCarlos:1993ca, Chankowski:1997zh,
+  Agashe:1997kn, Wright:1998mk, Kane:1998im, BasteroGil:1999gu,
+  Feng:1999zg, Allanach:2000ii, Dermisek:2005ar, Barbieri:2005kf,
+  Allanach:2006jc, Gripaios:2006nn, Dermisek:2006py, Barbieri:2006dq,
+  Kobayashi:2006fh, Perelstein:2012qg, Antusch:2012gv,Cheng:2012pe,
+  CahillRowley:2012rv, Ross:2012nr, Basak:2012bd, Kang:2012sy,
+  Athron:2013ipa,Miller:2013jra, Binjonaid:2014oga, Miller:2014jza}.
 
 A number of alternative measures have also been applied in the
-literature \cite{Anderson:1994dz, Anderson:1994tr,
-  Anderson:1995cp,Anderson:1996ew,Ciafaloni:1996zh,Chan:1997bi,
-  Barbieri:1998uv,
-  Giusti:1998gz,Casas:2003jx,Casas:2004uu,Casas:2004gh,Casas:2006bd,Kitano:2005wc,
-  Athron:2007ry, Athron:2007qr, Baer:2012up} with varying motivations.
-A very different approach is to work within a Bayesian analysis.
-There the concept of naturalness is automatically incorporated since
-in models where one must fine tune parameters to fit measured values
-of the observables, the region with high likelihood will occupy a tiny
-prior volume \cite{Allanach:2007qk, Cabrera:2008tj, Ghilencea:2012gz,
-  Ghilencea:2012qk, Fichet:2012sn, Kim:2013uxa} suppressing the
-posterior.  Indeed in the MSSM and NMSSM if one transforms GUT scale
-parameters to the VEVs, the inverse of the Jacobian for this
-transformation looks quite like the derivatives that appear in the
-traditional fine tuning measure \cite{Allanach:2007qk, Cabrera:2008tj,
-  Kim:2013uxa}.  If one thinks more generally then a model without
-fine tuning is one where the parametrisation is such that all the
-parameters are observables \cite{Fichet:2012sn, Kim:2013uxa}.  This
-provides a quite general definition of fine tuning as $1/|J|$ where
-$|J|$ is the determinant of the Jacobian for the co-ordinate
-transformation between the parameters and the
-observables. Interestingly this means the tuning is the ratio of the
-infinitesimal observable space space volume element to the
+literature \cite{Anderson:1994dz, Anderson:1994tr, Anderson:1995cp,
+  Anderson:1996ew, Ciafaloni:1996zh, Chan:1997bi, Barbieri:1998uv,
+  Giusti:1998gz, Casas:2003jx, Casas:2004uu, Casas:2004gh,
+  Casas:2006bd, Kitano:2005wc, Athron:2007ry, Athron:2007qr,
+  Baer:2012up} with varying motivations.  A very different approach is
+to work within a Bayesian analysis.  There the concept of naturalness
+is automatically incorporated since in models where one must fine tune
+parameters to fit measured values of the observables, the region with
+high likelihood will occupy a tiny prior volume \cite{Allanach:2007qk,
+  Cabrera:2008tj, Ghilencea:2012gz, Ghilencea:2012qk, Fichet:2012sn,
+  Kim:2013uxa} suppressing the posterior.  Indeed in the MSSM and
+NMSSM if one transforms GUT scale parameters to the VEVs, the inverse
+of the Jacobian for this transformation looks quite like the
+derivatives that appear in the traditional fine tuning measure
+\cite{Allanach:2007qk, Cabrera:2008tj, Kim:2013uxa}.  If one thinks
+more generally then a model without fine tuning is one where the
+parametrisation is such that all the parameters are observables
+\cite{Fichet:2012sn, Kim:2013uxa}.  This provides a quite general
+definition of fine tuning as $1/|J|$ where $|J|$ is the determinant of
+the Jacobian for the co-ordinate transformation between the parameters
+and the observables. Interestingly this means the tuning is the ratio
+of the infinitesimal observable space space volume element to the
 infinitesimal parameter space element and coincides with the measure
@@
 \section{\label{sec:conclusion}Conclusions}
+Prior to stringent experimental constraints on the mass of the
+lightest Higgs boson and squarks in supersymmetric models, a simple
+picture of a natural SUSY model emerged from theoretcal reasoning,
+with soft masses set to similar values at the GUT scale through local
+gravity interactions with the hidden sector.  Through the use of
+renormalisation group running one can then see that at the EW scale
+the stops and soft Higgs masses (which appear directly in the EWSB
+conditions) should appear in the the EWSB condition for $M_Z$ and
+therefore it was expected that these masses should not be much bigger
+than $100$ GeV.  However to disturb this elegant picture first LEP
+placed constraints on the Higgs mass, requiring it to be above 114.4
+GeV \cite{}, which already introduced significant tuning for
+constrained models, and then the LHC meaured the Higgs to be around
+$125$ GeV.
+
+However
+
 % Our conclusions: at low scales stops are not a big contributor,

### 2014-12-19 paper/e6ssm-tuning-paper.tex
added more to conclusion.  maybe it's not so shit after all, will reread later.

@@
 contribution to fine tuning. $U(1)$ extensions of the MSSM that solve
-the $\mu$-problem have new F- and D-term contributions to the Higgs mass,
-allowing a 125 GeV Higgs with lighter stops and so alleviating the
-associated fine tuning. However, it was recently demonstrated, within
-a constrained version of the Exceptional Supersymmetric Standard Model (E$_6$SSM)
-defined at the Grand Unification (GUT) scale, that the presence of a massive $Z'$ boson introduces a 
-substantial new source of tuning in these theories at tree level. Here we
-consider the impact of this tuning when we remove the fine tuning that depends
-on assumptions about the SUSY breaking scale, by setting the SUSY
-breaking parameters at low energies. We find that the existing
-experimental bounds on the $Z'$ mass impose an effective lower bound on
-the fine tuning, which does not depend on assumptions about SUSY breaking. 
-We compare our results against the tuning in the MSSM with the SUSY breaking terms also defined at low energies.
+the $\mu$-problem have new F- and D-term contributions to the Higgs
+mass, allowing a 125 GeV Higgs with lighter stops and so alleviating
+the associated fine tuning. However, it was recently demonstrated,
+within a constrained version of the Exceptional Supersymmetric
+Standard Model (E$_6$SSM) defined at the Grand Unification (GUT)
+scale, that the presence of a massive $Z'$ boson introduces a
+substantial new source of tuning in these theories at tree level. Here
+we consider the impact of this tuning when we remove the fine tuning
+that depends on assumptions about the SUSY breaking scale, by setting
+the SUSY breaking parameters at low energies. We find that the
+existing experimental bounds on the $Z'$ mass impose an effective
+lower bound on the fine tuning, which does not depend on assumptions
+about SUSY breaking.  We compare our results against the tuning in the
+MSSM with the SUSY breaking terms also defined at low energies.
 
@@
 U(1) extensions of the MSSM provide a very elegant solution to this
-$\mu$-problem \cite{Fayet:1977yc, Kim:1983dt, Suematsu:1994qm, Cvetic:1995rj,  Cvetic:1996mf, Jain:1995cb, Nir:1995bu, Cvetic:1997ky} and also
-raise the Higgs mass with new $F$- and $D$-terms. Nonetheless, as was
-recently demonstrated in the context of the exceptional supersymmetric
-standard model (E$_6$SSM)
-\cite{King:2005jy,King:2005my,Athron:2010zz}, such models can still suffer from
-naturalness problems with the mass of the new $Z^\prime$ associated
-with break down of the new U(1) appearing in the electroweak symmetry
-breaking conditions at tree level \cite{Athron:2013ipa}.  Nonetheless
-the constrained version of E$_6$SSM (cE$_6$SSM) \cite{Athron:2009ue,
-  Athron:2009bs} still turned out to be significantly less tuned than
-the cMSSM.
+$\mu$-problem \cite{Fayet:1977yc, Kim:1983dt, Suematsu:1994qm,
+  Cvetic:1995rj, Cvetic:1996mf, Jain:1995cb, Nir:1995bu,
+  Cvetic:1997ky} and also raise the Higgs mass with new $F$- and
+$D$-terms. Nonetheless, as was recently demonstrated in the context of
+the exceptional supersymmetric standard model (E$_6$SSM)
+\cite{King:2005jy,King:2005my,Athron:2010zz}, such models can still
+suffer from naturalness problems with the mass of the new $Z^\prime$
+associated with break down of the new U(1) appearing in the
+electroweak symmetry breaking conditions at tree level
+\cite{Athron:2013ipa}.  Nonetheless the constrained version of
+E$_6$SSM (cE$_6$SSM) \cite{Athron:2009ue, Athron:2009bs} still turned
+out to be significantly less tuned than the cMSSM.
 
@@
 coupling between the Singlet Higgs, $S$ and the up- and down-type
-Higgs bosons, $H_u$ and $H_d$, to remain perturbative up to the UV scale
-and not the all the way up to the GUT scale.
+Higgs bosons, $H_u$ and $H_d$, to remain perturbative up to the UV
+scale and not the all the way up to the GUT scale.
 
@@
 Here we will refer to U(1) extensions of the MSSM, which solve the
-$\mu$-problem as the USSM
-\cite{Cvetic:1995rj, Jain:1995cb, Nir:1995bu, Cvetic:1996mf, Cvetic:1997ky}, while we will
-sometimes specify that the models are inspired by $E_6$ by referring
-to them as such. Finally we will also discuss specific models with
-complete $E_6$ matter multiplets at low energies and an extra $U(1)$
-under which the right handed neutrino remains interaction-less as
-E$_6$SSM-variants\cite{Howl:2007zi, Braam:2009fi, Braam:2010sy, Hall:2011zq, Nevzorov:2012hs, Athron:2014pua}, with the E$_6$SSM reserved for the original
-formulation of this model \cite{King:2005jy,King:2005my,Athron:2010zz}
-original formulation of the model.
+$\mu$-problem as the USSM \cite{Cvetic:1995rj, Jain:1995cb,
+  Nir:1995bu, Cvetic:1996mf, Cvetic:1997ky}, while we will sometimes
+specify that the models are inspired by $E_6$ by referring to them as
+such. Finally we will also discuss specific models with complete $E_6$
+matter multiplets at low energies and an extra $U(1)$ under which the
+right handed neutrino remains interaction-less as
+E$_6$SSM-variants\cite{Howl:2007zi, Braam:2009fi, Braam:2010sy,
+  Hall:2011zq, Nevzorov:2012hs, Athron:2014pua}, with the E$_6$SSM
+reserved for the original formulation of this model
+\cite{King:2005jy,King:2005my,Athron:2010zz} original formulation of
+the model.
 
@@
 decoupled ``inert'' neutralino sector \cite{Hall:2009aj},.  However
-this is no longer phenomenologically viable due to limits from
-direct detection of dark matter
+this is no longer phenomenologically viable due to limits from direct
+detection of dark matter
 \cite{2011PhRvL.107m1302A,2012PhRvL.109r1301A, Akerib:2013tjd} and due
@@
 
-In this paper we will examine this source of fine tuning in more detail by considering low energy constructions where the usual fine tuning problem from the Higgs is minimised.
-We will also consider  alternate charges for the extra $U(1)$ symmetry to relax the focus on the E$_6$SSM and demonstrate that this is quite a generic result.
+In this paper we will examine this source of fine tuning in more
+detail by considering low energy constructions where the usual fine
+tuning problem from the Higgs is minimised.  We will also consider
+alternate charges for the extra $U(1)$ symmetry to relax the focus on
+the E$_6$SSM and demonstrate that this is quite a generic result.
 
@@
 
-The structure of this paper is as follows.
-In section \ref{sec:model} we review the models we consider.
-In section \ref{sec:ewsb} we specify the EWSB conditions of the models, with particular focus on how the $Z^\prime$ mass influences the prediction of $M_Z$.
-Then in section \ref{sec:tuning} we introduce our fine tuning measure and our approach to evaluating it to obtain the individual sensitivities.
-The numerical procedure we use to obtain our results is given in \ref{subsec:numericalprocedure} and then the results are specified in section \ref{sec:results}.
+The structure of this paper is as follows.  In section \ref{sec:model}
+we review the models we consider.  In section \ref{sec:ewsb} we
+specify the EWSB conditions of the models, with particular focus on
+how the $Z^\prime$ mass influences the prediction of $M_Z$.  Then in
+section \ref{sec:tuning} we introduce our fine tuning measure and our
+approach to evaluating it to obtain the individual sensitivities.  The
+numerical procedure we use to obtain our results is given in
+\ref{subsec:numericalprocedure} and then the results are specified in
+section \ref{sec:results}.
 
@@
 into $SU(5)$, gives $SO(10)\to SU(5)\times U(1)_{\chi}$ (this is
-reviewed in e.g.~\cite{Langacker:2008yv}). The extra $U(1)$ gauge symmetry at low energies should then be a linear combination of these in the $E_6$ inspired case,
-\be
-U(1)^\prime = \cos(\theta) U(1)_{\chi} + \sin(\theta) U(1)_{\psi}.
-\ee In table \ref{tab:E6charges} the charges for several popular $E_6$ inspired $U(1)$ extensions are shown.
+reviewed in e.g.~\cite{Langacker:2008yv}). The extra $U(1)$ gauge
+symmetry at low energies should then be a linear combination of these
+in the $E_6$ inspired case, \be U(1)^\prime = \cos(\theta) U(1)_{\chi}
++ \sin(\theta) U(1)_{\psi}.  \ee In table \ref{tab:E6charges} the
+charges for several popular $E_6$ inspired $U(1)$ extensions are
+shown.
 % Table of U(1)' charges, which may or may not be useful to include.
@@
 singlet, and up-, down-type Higgs fields and the $\hat{D}_i$ and
-$\hat{\overline{D}}_i$ being $SU(3)_C$ triplets that reside in the same $SU(5)$
-multiplets as these Higgs-like states.
+$\hat{\overline{D}}_i$ being $SU(3)_C$ triplets that reside in the
+same $SU(5)$ multiplets as these Higgs-like states.
 
@@
 \begin{align}
-V_{E_6}^F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|(H_1\cdot H_2)|^2,\label{eq:E6VFterms}\\
-V_{E_6}^D&=\frac{\bar{g}^2}{8}\left ( |H_2|^2-|H_1|^2\right )^2+\frac{g_2^2}{2}|H_1^\dagger H_2|^2+\frac{g_1'^2}{2}(\tilde{Q}_1|H_1|^2+\tilde{Q}_2|H_2|^2+\tilde{Q}_S|S|^2)^2,\label{eq:E6VDterms}\\
-V_{E_6}^{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big [\lambda A_\lambda S(H_1\cdot H_2)+\textrm{h.c.}\Big ].\label{eq:E6Vsoft}
+V_{E_6}^F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|(H_1\cdot
+H_2)|^2,\label{eq:E6VFterms}\\ V_{E_6}^D&=\frac{\bar{g}^2}{8}\left (
+|H_2|^2-|H_1|^2\right )^2+\frac{g_2^2}{2}|H_1^\dagger
+H_2|^2+\frac{g_1'^2}{2}(\tilde{Q}_1|H_1|^2+\tilde{Q}_2|H_2|^2+\tilde{Q}_S|S|^2)^2,\label{eq:E6VDterms}\\ V_{E_6}^{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big
+[\lambda A_\lambda S(H_1\cdot H_2)+\textrm{h.c.}\Big
+].\label{eq:E6Vsoft}
 \end{align}
@@
 \end{subequations}
-The quantities $D_{H_1}$, $D_{H_2}$ and $D_S$ appearing above are $U(1)'$ $D$-term contributions that are absent in the MSSM and NMSSM and are given by
+The quantities $D_{H_1}$, $D_{H_2}$ and $D_S$ appearing above are
+$U(1)'$ $D$-term contributions that are absent in the MSSM and NMSSM
+and are given by
 \begin{equation}\label{eq:E6Dterms}
-D_\phi\equiv \frac{g_1'^2}{2}\left ( \tilde{Q}_1v_1^2+\tilde{Q}_2v_2^2+\tilde{Q}_Ss^2\right )\tilde{Q}_\phi.
-\end{equation}
-As was noted in \cite{Athron:2013ipa}, the first two of these conditions may be rewritten in the form
+D_\phi\equiv \frac{g_1'^2}{2}\left (
+\tilde{Q}_1v_1^2+\tilde{Q}_2v_2^2+\tilde{Q}_Ss^2\right
+)\tilde{Q}_\phi.
+\end{equation}
+As was noted in \cite{Athron:2013ipa}, the first two of these
+conditions may be rewritten in the form
 \begin{equation}\label{eq:E6MZequation}
@@
 \end{equation}
-with $M_Z^2=\bar{g}^2v^2/4$, $v^2=v_1^2+v_2^2$ and $\tan\beta = v_2/v_1$ and where we have for convenience absorbed the effects of the loop corrections into the soft masses, 
+with $M_Z^2=\bar{g}^2v^2/4$, $v^2=v_1^2+v_2^2$ and $\tan\beta =
+v_2/v_1$ and where we have for convenience absorbed the effects of the
+loop corrections into the soft masses,
 \begin{align*}
-\tilde{m}_{H_d}^2&=m_{H_d}^2+\frac{1}{v_1}\frac{\partial \Delta V_{E_6}}{\partial v_1},\\
-\tilde{m}_{H_u}^2&=m_{H_u}^2+\frac{1}{v_2}\frac{\partial \Delta V_{E_6}}{\partial v_2}.
+\tilde{m}_{H_d}^2&=m_{H_d}^2+\frac{1}{v_1}\frac{\partial \Delta
+  V_{E_6}}{\partial
+  v_1},\\ \tilde{m}_{H_u}^2&=m_{H_u}^2+\frac{1}{v_2}\frac{\partial
+  \Delta V_{E_6}}{\partial v_2}.
 \end{align*}
@@
 \end{align}
-Written like so it is evident that the fine tuning contribution coming from the new $D$-terms depends both on the $U(1)'$ charges and the $Z^\prime$ mass, and that the tuning can be expected to increase with $M_{Z^\prime}$.
-As shall be shown below, the exact size of this tuning then depends strongly on the choice of $U(1)'$ charges, via the coefficient $d$.
+Written like so it is evident that the fine tuning contribution coming
+from the new $D$-terms depends both on the $U(1)'$ charges and the
+$Z^\prime$ mass, and that the tuning can be expected to increase with
+$M_{Z^\prime}$. As shall be shown below, the exact size of this tuning
+then depends strongly on the choice of $U(1)'$ charges, via the
+coefficient $d$.
 \section{\label{sec:tuning}Fine Tuning}
@@
 \begin{equation}\label{eq:bgmeasure}
-\Delta_p=\left | \frac{\partial \log M_Z^2}{\partial \log p}\right |=\left | \frac{p}{M_Z^2}\frac{\partial M_Z^2}{\partial p}\right |,
-\end{equation}
-where $M_Z^2=\bar{g}^2v^2/4$.
-The coefficient $\Delta_p$ measures the fractional variation in $M_Z^2$ resulting from a given variation in the parameter $p$.
-The overall fine tuning is then taken to be $\Delta = \underset{i}{\max}\,\{\Delta_{p_i}\}$.\\ \\
-
-The sensitivity coefficients $\Delta_p$ may be calculated directly from the expression for $M_Z^2$ in terms of the $p_i$ for a particular model, which leads to a so-called master formula for calculating the fine tuning.
-A master formula for the E$_6$SSM, obtained from the tree level scalar potential, was presented in \cite{Athron:2013ipa}.
-In order to derive the expression presented there, the fact that $s \gg v$ was made use of to neglect certain $O(v^2)$ terms in the EWSB conditions, greatly simplifying the final result.
-For the purposes of exploring a wider class of $E_6$ inspired models, we have rederived the master formula without neglecting any $O(v^2)$ terms.
-The more complete tree-level master formula is somewhat complicated.
-This is because, unlike in the MSSM, even at tree level it is not possible to solve explicitly for the VEVs $v_1$, $v_2$ in terms of the Lagrangian parameters.
-It may be written in the form
-\be
-\Delta_p=|C|^{-1}\times \frac{|p|}{M_Z}\bigg|\sum_{q}\tilde{\Delta}_q\frac{\partial q}{\partial p}\bigg|,
+\Delta_p=\left | \frac{\partial \log M_Z^2}{\partial \log p}\right
+|=\left | \frac{p}{M_Z^2}\frac{\partial M_Z^2}{\partial p}\right |,
+\end{equation}
+where $M_Z^2=\bar{g}^2v^2/4$. The coefficient $\Delta_p$ measures the
+fractional variation in $M_Z^2$ resulting from a given variation in
+the parameter $p$. The overall fine tuning is then taken to be $\Delta
+= \underset{i}{\max}\,\{\Delta_{p_i}\}$.\\ \\
+
+The sensitivity coefficients $\Delta_p$ may be calculated directly
+from the expression for $M_Z^2$ in terms of the $p_i$ for a particular
+model, which leads to a so-called master formula for calculating the
+fine tuning. A master formula for the E$_6$SSM, obtained from the tree
+level scalar potential, was presented in \cite{Athron:2013ipa}. In
+order to derive the expression presented there, the fact that $s \gg
+v$ was made use of to neglect certain $O(v^2)$ terms in the EWSB
+conditions, greatly simplifying the final result. For the purposes of
+exploring a wider class of $E_6$ inspired models, we have rederived
+the master formula without neglecting any $O(v^2)$ terms. The more
+complete tree-level master formula is somewhat complicated. This is
+because, unlike in the MSSM, even at tree level it is not possible to
+solve explicitly for the VEVs $v_1$, $v_2$ in terms of the Lagrangian
+parameters. It may be written in the form \be \Delta_p=|C|^{-1}\times
+\frac{|p|}{M_Z}\bigg|\sum_{q}\tilde{\Delta}_q\frac{\partial
+  q}{\partial p}\bigg|,
 \label{eq:E6masterformula}
-\ee
-where the sum is over all low energy running parameters appearing in the tree level EWSB conditions, i.e.
-$q\in\{\lambda, A_\lambda, m_{H_d}^2,m_{H_u}^2,m_S^2,g_1,g_2,g_1'\}$.
-Expressions for the quantity $C$ and the $\tilde{\Delta}_q$ appearing above are given in Appendix \ref{app:masterformula}.
-It should be noted that the effects of $U(1)$ mixing are neglected in deriving Eq.
-(\ref{eq:E6masterformula}).\\ \\
-However, it is well known in the MSSM that radiative corrections can significantly change (indeed, reduce) the fine tuning \cite{Cassel:2010px}.
-It is therefore important when studying the fine tuning to include loop corrections to the effective potential in the fine tuning measure.
-To do so it is most convenient to work in terms of the EWSB conditions Eq.
-(\ref{eq:E6EWSBConditions}), rather than Eq.
-(\ref{eq:E6MZequation}).
-The general procedure is as follows \cite{Ellwanger:2011mu}.
-For a model in which $m$ fields develop real VEVs (e.g.
-$m=2$ in the MSSM, $m=3$ in the NMSSM and in the $E_6$ models considered), we require that the $m$ minimization conditions
+\ee where the sum is over all low energy running parameters appearing
+in the tree level EWSB conditions, i.e. $q\in\{\lambda, A_\lambda,
+m_{H_d}^2,m_{H_u}^2,m_S^2,g_1,g_2,g_1'\}$. Expressions for the
+quantity $C$ and the $\tilde{\Delta}_q$ appearing above are given in
+Appendix \ref{app:masterformula}. It should be noted that the effects
+of $U(1)$ mixing are neglected in deriving
+Eq. (\ref{eq:E6masterformula}).\\ \\ However, it is well known in the
+MSSM that radiative corrections can significantly change (indeed,
+reduce) the fine tuning \cite{Cassel:2010px}. It is therefore
+important when studying the fine tuning to include loop corrections to
+the effective potential in the fine tuning measure. To do so it is
+most convenient to work in terms of the EWSB conditions
+Eq. (\ref{eq:E6EWSBConditions}), rather than
+Eq. (\ref{eq:E6MZequation}). The general procedure is as follows
+\cite{Ellwanger:2011mu}. For a model in which $m$ fields develop real
+VEVs (e.g. $m=2$ in the MSSM, $m=3$ in the NMSSM and in the $E_6$
+models considered), we require that the $m$ minimization conditions
 \begin{equation}\label{eq:EWSBconditions}
@@
 \end{equation}
-continue to hold under an arbitrary variation in a model parameter $p\rightarrow p+\delta p$, so that the variations $\delta f_i$ satisfy
+continue to hold under an arbitrary variation in a model parameter
+$p\rightarrow p+\delta p$, so that the variations $\delta f_i$ satisfy
 \begin{equation}\label{eq:EWSBvariations}
@@
 \end{equation}
-Each $f_i$ is a function of the VEVs $v_j$ and $l$ running parameters $q_k$ evaluated at the scale of EWSB, $f_i=f_i(v_j,q_k)$. Thus for each $f_i$ we have that
+Each $f_i$ is a function of the VEVs $v_j$ and $l$ running parameters
+$q_k$ evaluated at the scale of EWSB, $f_i=f_i(v_j,q_k)$. Thus for
+each $f_i$ we have that
 \begin{equation}\label{eq:EWSBchainrule}
-\delta f_i = \sum_{j=1}^m \frac{\partial f_i}{\partial v_j}\frac{\partial v_j}{\partial p}+\sum_{k=1}^l \frac{\partial f_i}{\partial q_k}\frac{\partial q_k}{\partial p}=0.
-\end{equation}
-The quantities $\frac{\partial f_i}{\partial v_j}$ are the elements of the CP-even Higgs squared mass matrix $M_h^2$ of the model before rotating into the mass eigenstate basis.
-When evaluated for all $n$ model parameters, the above system of equations can be concisely expressed as
+\delta f_i = \sum_{j=1}^m \frac{\partial f_i}{\partial
+  v_j}\frac{\partial v_j}{\partial p}+\sum_{k=1}^l \frac{\partial
+  f_i}{\partial q_k}\frac{\partial q_k}{\partial p}=0.
+\end{equation}
+The quantities $\frac{\partial f_i}{\partial v_j}$ are the elements of
+the CP-even Higgs squared mass matrix $M_h^2$ of the model before
+rotating into the mass eigenstate basis. When evaluated for all $n$
+model parameters, the above system of equations can be concisely
+expressed as
 \begin{equation}\label{eq:tuningsystem}
@@
 \end{equation} 
-The quantities forming the first matrix on the right-hand side, along with $M_h^2$, are easily calculated analytically.
-The remaining derivatives $\partial q_k /\partial p$ must be determined using the RGEs.
-Once these have been obtained, it is straightforward to solve for the $\partial v_i /\partial p$.
-The sensitivity coefficients $\Delta_p$ are then simply linear combinations of the $\partial v_i/\partial p$ and $\partial q_k/\partial p$.
-Radiative corrections may be easily incorporated by including the Coleman-Weinberg potential contributions in the EWSB conditions.\\ \\
-Evaluating the derivatives $\partial q_k/\partial p$ must (in general) be done by numerically integrating the two-loop RGEs.
-This is time consuming and presents an obstacle to doing large scans of the parameter space.
-For studying models defined at low energies, as we do here, we can take advantage of the fact that the amount of running involved is small.
-This makes it possible to use approximate analytic solutions to the RGEs that exhibit good accuracy over the range of scales considered.
-Given the two-loop RG equation for a parameter $q$,
+The quantities forming the first matrix on the right-hand side, along
+with $M_h^2$, are easily calculated analytically. The remaining
+derivatives $\partial q_k /\partial p$ must be determined using the
+RGEs. Once these have been obtained, it is straightforward to solve
+for the $\partial v_i /\partial p$. The sensitivity coefficients
+$\Delta_p$ are then simply linear combinations of the $\partial
+v_i/\partial p$ and $\partial q_k/\partial p$. Radiative corrections
+may be easily incorporated by including the Coleman-Weinberg potential
+contributions in the EWSB conditions.\\ \\ Evaluating the derivatives
+$\partial q_k/\partial p$ must (in general) be done by numerically
+integrating the two-loop RGEs. This is time consuming and presents an
+obstacle to doing large scans of the parameter space. For studying
+models defined at low energies, as we do here, we can take advantage
+of the fact that the amount of running involved is small. This makes
+it possible to use approximate analytic solutions to the RGEs that
+exhibit good accuracy over the range of scales considered. Given the
+two-loop RG equation for a parameter $q$,
 \begin{equation}\label{eq:rge}
@@
 \end{equation}
-a Taylor series expansion of the solution may be used to obtain the parameter at the scale $Q$,
+a Taylor series expansion of the solution may be used to obtain the
+parameter at the scale $Q$,
 \begin{align}\label{eq:rgeapproxsoln}
@@
 \end{align}
-Expanded to this order we obtain the leading log (LL) and next-to-LL (NLL) contributions at two-loop order.
-The $\mathcal{O}(t^2)$ terms not displayed above are formally of 3-loop order and are neglected.
-The derivative of the one-loop $\beta$ function is given by
+Expanded to this order we obtain the leading log (LL) and next-to-LL
+(NLL) contributions at two-loop order. The $\mathcal{O}(t^2)$ terms
+not displayed above are formally of 3-loop order and are
+neglected. The derivative of the one-loop $\beta$ function is given by
 \begin{equation}\label{eq:1loopbetaderivative}
@@
 \end{equation}
-where the sum is over all running parameters appearing in $\beta_q^{(1)}$.
-The $\beta$ functions appearing on the right hand side of Eqs.
-(\ref{eq:rgeapproxsoln}) and (\ref{eq:1loopbetaderivative}) are evaluated at the input scale $M_X$, giving a simple analytic expression for the parameters at the scale of EWSB in terms of the model parameters at $M_X$.
-Explicit results for the relevant series expansions in the MSSM and $E_6$ models are presented in Appendix \ref{app:rges}.
+where the sum is over all running parameters appearing in
+$\beta_q^{(1)}$. The $\beta$ functions appearing on the right hand
+side of Eqs. (\ref{eq:rgeapproxsoln}) and
+(\ref{eq:1loopbetaderivative}) are evaluated at the input scale $M_X$,
+giving a simple analytic expression for the parameters at the scale of
+EWSB in terms of the model parameters at $M_X$. Explicit results for
+the relevant series expansions in the MSSM and $E_6$ models are
+presented in Appendix \ref{app:rges}.
 \subsection{\label{subsec:numericalprocedure}Numerical Procedure}
-Using the approach outlined above, we are able to scan the low energy parameter space of the MSSM and E$_6$SSM and calculate the fine tuning in each.
-To do so, we implemented the above expressions for computing the fine tuning in a modified version of the E$_6$SSM spectrum generator that was used in \cite{Athron:2013ipa}.
-This code implemented two-loop RGEs for all parameters except the soft scalar masses.
-In order to properly include the fine tuning impact of the $SU(3)$ gaugino soft mass $M_3$, we have extended the original code to make use of the two-loop RGEs generated by SARAH \cite{Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta} and FlexibleSUSY \cite{Athron:2014yba}.
-The CP-even Higgs masses are calculated including the leading one-loop effective potential contributions given in \cite{Athron:2009bs} and the leading two-loop contributions.
-To scan over the MSSM parameter space, the equivalent MSSM fine tuning expressions were implemented into a modifed version of SOFTSUSY 3.3.10 \cite{Allanach:2001kg,Allanach:2013kza}.
-For consistency with the results produced in the $E_6$ models, and for computational speed, for our main scans only the dominant one- and two-loop corrections to the CP-even Higgs masses were included.
-Finally, in all of the results below the fine tuning was evaluated at the scale $Q=M_{\textrm{SUSY}}=\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop masses evaluated at $Q=M_{\textrm{SUSY}}$.
+Using the approach outlined above, we are able to scan the low energy
+parameter space of the MSSM and E$_6$SSM and calculate the fine tuning
+in each. To do so, we implemented the above expressions for computing
+the fine tuning in a modified version of the E$_6$SSM spectrum
+generator that was used in \cite{Athron:2013ipa}. This code
+implemented two-loop RGEs for all parameters except the soft scalar
+masses. In order to properly include the fine tuning impact of the
+$SU(3)$ gaugino soft mass $M_3$, we have extended the original code to
+make use of the two-loop RGEs generated by SARAH
+\cite{Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta} and
+FlexibleSUSY \cite{Athron:2014yba}. The CP-even Higgs masses are
+calculated including the leading one-loop effective potential
+contributions given in \cite{Athron:2009bs} and the leading two-loop
+contributions. To scan over the MSSM parameter space, the equivalent
+MSSM fine tuning expressions were implemented into a modifed version
+of SOFTSUSY 3.3.10 \cite{Allanach:2001kg,Allanach:2013kza}. For
+consistency with the results produced in the $E_6$ models, and for
+computational speed, for our main scans only the dominant one- and
+two-loop corrections to the CP-even Higgs masses were
+included. Finally, in all of the results below the fine tuning was
+evaluated at the scale
+$Q=M_{\textrm{SUSY}}=\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where
+$m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop
+masses evaluated at $Q=M_{\textrm{SUSY}}$.
 
@@
 minimised other sources of tuning.  On the other hand the tuning
-becomes more severe as we increase the cuttoff such that for $M_X =
+becomes more severe as we increase the cutoff such that for $M_X =
 10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
@@
 $m_{\chi^\pm} < 700$ GeV was excluded the impact would be to make the
-tuning in the MSSM with a $20$ TeV cuttoff slightly worse than that of
-the E$_6$SSM with the same cuttoff and a $Z^\prime$ mass just larger
+tuning in the MSSM with a $20$ TeV cutoff slightly worse than that of
+the E$_6$SSM with the same cutoff and a $Z^\prime$ mass just larger
 than current limits.  would be similar to that can also be attcked
@@
 cutoff scale.  Indeed in \cite{Athron:2013ipa} a constrained version
-of the E$_6$SSM, with the cuttoff at the GUT scale, is considered and
+of the E$_6$SSM, with the cutoff at the GUT scale, is considered and
 there the cE$_6$SSM was found to be less tuned than the cMSSM. Since a
@@
 As is shown in Fig.~\ref{} the tuning in the MSSM becomes larger
-than that of the E$_6$SSM when the cuttoff scale is ?
+than that of the E$_6$SSM when the cutoff scale is ?
 
 \section{\label{sec:conclusion}Conclusions}
+
 Prior to stringent experimental constraints on the mass of the
 lightest Higgs boson and squarks in supersymmetric models, a simple
-picture of a natural SUSY model emerged from theoretcal reasoning,
+picture of a natural SUSY model emerged from theoretical reasoning,
 with soft masses set to similar values at the GUT scale through local
@@
 GeV \cite{}, which already introduced significant tuning for
-constrained models, and then the LHC meaured the Higgs to be around
-$125$ GeV.
-
-However
+constrained models,and then the LHC measured the Higgs to be around
+$125$ GeV, since heavy stops are required to raised the lightest
+Higgs mass above it's tree level bound.
+
+$U(1)$ extensions motivated by the $\mu$-problem, $E_6$ GUT theories
+and the connection to string theory contain both $F-$ and $D-$ term
+contributions to the light Higgs mass which can raise the tree level
+mass, evading the need for large radiative corrections to increase it.
+However such models come with their own fine tuning problem, where the
+$Z^\prime$ mass appears in the EWSB condition for $M_Z$ at tree level.
+While in a previous study of the constrained E$_6$SSM it was found
+that the tuning is less severe than the MSSM, it was still significant.
+
+In light of such difficulties it is worth considering whether the
+simple picture which emerged is wrong in some way and if there are
+other possibilities that allow naturalness.  Or to phrase this in a
+more challenging manner are there ways to constrain the naturalness of
+these models that do not rely upon assumptions about how SUSY is
+broken?
+
+We have investigated this question here in the context of the MSSM and
+U(1) extensions.  Since the RG evolution links the soft masses
+together and causes these problems from stop and gluino masses the
+most conservative approach to placing naturalness limits is to choose
+a low cutoff. We find that in the MSSM the most direct way to
+constrain naturalness of the model, without making assumptions about
+the SUSY breaking scale is through limits on the chargino
+masses. Current LHC limits on charginos are not model independent and
+thereby leave many gaps where on can have light charginos.
+
+In contrast we find that in $U(1)$ extensions of the MSSM there is an
+additional way to constrain the naturalness of the models, which is
+through the $Z^\prime$ mass limit.  We find when we impose a low
+cutoff of $20$ TeV for setting the soft masses, the lowest tuning in
+the E$_6$SSM is compatible with a $Z^\prime$ mass of $2.5$ TeV was
+$\Delta \approx 100$, while if the LHC run II can place a limit of
+$4.5$ TeV on $M_Z^\prime$ then the tuning would be just under $400$.
+By comparison the current situation in the MSSM only requires a tuning
+of around $20-30$. [Dylan: update numbers a bit -- I suck at reading
+  them off the graphs:)] This should be interpreted as saying that in
+the most conservative limits one can place on naturalness on these
+models, the tuning in the E$_6$SSM is worse.  However if the chargino
+limits blah blah blah then the situation in the two models would be
+the same.
+
+This should also be contrasted with what happens as we raise the
+cutoff scale.  We showed that when the cutoff reaches $M_X =
+[insert]$ the tuning of the MSSM becomes larger than that of the
+E$_6$SSM.  Therefore the conclusion is not that one model is less
+tuned than another, but rather that the answer depends on what
+assumptions are made about the SUSY breaking.
+
+Finally we also looked at the tuning in different $U(1)$ extensions for
+fixed $\tan \beta = 10$.  We found that in all cases the fine tuning
+was much worse for the larger $Z^\prime$ mass, further emphasising
+the importance they play in these $U(1)$ extensions.  Interestingly
+the actual level in tuning varied quite a bit between these models
+with the $U(1)_I$ model showing the least tuning due to the vanishing
+charge of the $H_u$ state. This model is quite interesting in the
+sense that it provides a solution to the $\mu$-problem while avoiding
+the large tuning (with current limits) from the $Z^\prime$
+mass. However one should remember we are looking at conservative limits
+on naturalness here and there is no solution to the usual tuning from
+the large stops needed to get a $125$ GeV Higgs in this model.  In any
+case future LHC limits on the $Z^\prime$ mass would be especially
+interesting for this case as they would significantly raise the
+minimum level of tuning which can be obtained.
 
@@
 % to the RGE solutions.
-Provided that one does not run over too large a range of scales, the solutions to the
-RG equations for a model can be reasonably well approximated by a Taylor series, Eq. (\ref{eq:rgeapproxsoln}). 
-For a parameter $p$, this reads
+Provided that one does not run over too large a range of scales, the
+solutions to the RG equations for a model can be reasonably well
+approximated by a Taylor series, Eq. (\ref{eq:rgeapproxsoln}).  For a
+parameter $p$, this reads
 \begin{equation*}
@@
 \end{equation*}
-We have constructed the necessary series solutions in both the MSSM and the $U(1)$ extended models.
-Due to the smallness of the first and second generation Yukawa couplings, we neglect them in our calculations.
-The corresponding soft SUSY breaking
-trilinears are likewise omitted. Additionally, all soft mass matrices are assumed diagonal, and the gaugino masses are taken to be real.\\ \\
-In the MSSM, the relevant parameters for the fine tuning calculation are $\mu$, $B$, $m_{H_u}^2$, $m_{H_d}^2$ at tree level.
-The one- and two-loop RGEs for these parameters may be found in \cite{Martin:1993zk}.
-The corresponding $O(t^2)$ contributions are
+We have constructed the necessary series solutions in both the MSSM
+and the $U(1)$ extended models. Due to the smallness of the first and
+second generation Yukawa couplings, we neglect them in our
+calculations. The corresponding soft SUSY breaking trilinears are
+likewise omitted. Additionally, all soft mass matrices are assumed
+diagonal, and the gaugino masses are taken to be real.\\ \\ In the
+MSSM, the relevant parameters for the fine tuning calculation are
+$\mu$, $B$, $m_{H_u}^2$, $m_{H_d}^2$ at tree level. The one- and
+two-loop RGEs for these parameters may be found in
+\cite{Martin:1993zk}. The corresponding $O(t^2)$ contributions are
 \begin{subequations}\label{eq:MSSMTreeLevelCoeffs}
@@
 \end{equation}
-If in addition the one-loop contributions to the effective potential from top and stop loops are included, it is also
-necessary to construct the expansions for $m_{Q3}^2$, $m_{u3}^2$ and $A_t$. The coefficients read
+If in addition the one-loop contributions to the effective potential
+from top and stop loops are included, it is also necessary to
+construct the expansions for $m_{Q3}^2$, $m_{u3}^2$ and $A_t$. The
+coefficients read
 \begin{subequations}\label{eq:MSSMsEffPotCoeffs}
@@
 \end{subequations}
-Similarly we can obtain the two-loop $\beta$ functions and coefficients $b_p^{(2)}$ for a general set of $U(1)'$ charges.
-Two-loop RGEs for the gauge and Yukawa couplings, gaugino masses and soft trilinears, along with the one-loop RGEs for the soft scalar masses, were given in \cite{Athron:2009bs} for the particular case of the E$_6$SSM.
-At tree level in the EWSB conditions the parameters that must be considered are $\lambda$, $A_\lambda$, $m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and $g_1'$.
-The one- and two-loop contributions to the $\beta$ function for $\lambda$ are
+Similarly we can obtain the two-loop $\beta$ functions and
+coefficients $b_p^{(2)}$ for a general set of $U(1)'$
+charges. Two-loop RGEs for the gauge and Yukawa couplings, gaugino
+masses and soft trilinears, along with the one-loop RGEs for the soft
+scalar masses, were given in \cite{Athron:2009bs} for the particular
+case of the E$_6$SSM. At tree level in the EWSB conditions the
+parameters that must be considered are $\lambda$, $A_\lambda$,
+$m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and $g_1'$. The
+one- and two-loop contributions to the $\beta$ function for $\lambda$
+are
 \begin{subequations}\label{eq:USSMLambdaBetas}

### 2014-12-22 fs-spectrum/models/lowE6SSM/lowE6SSM_two_scale_tuning_calculator.cpp
Added fine tuning calculation using numerical derivatives of low scale parameters, fixed bug in old numerical tuning calculation where M_Z^2 is calculated at MX and not MSUSY

@@ -59,7 +59,7 @@ namespace flexiblesusy {
       unsigned ewsb_loop_order = pars->ewsb_loop_order;
       unsigned beta_loop_order = pars->beta_loop_order;
       lowE6SSM_info::Parameters p = pars->p;
-
+      
       model.set_loops(beta_loop_order);
       model.set_ewsb_loop_order(ewsb_loop_order);
 
@@ -118,7 +118,7 @@ namespace flexiblesusy {
       const double vev2 = Sqr(vu) + Sqr(vd);
 
       double MVZ2 = 0.25 * gbar2 * vev2;
-      
+
       return MVZ2;
    }
 
@@ -127,7 +127,7 @@ namespace flexiblesusy {
       bool tuning_problem = false;
 
       lowE6SSM_ew_derivs ew_derivs(model);
-      
+
       double scale = model.get_scale();
 
       if (is_equal_rel(scale, input_scale)) {
@@ -142,6 +142,12 @@ namespace flexiblesusy {
       }
 
       const double epsilon = 1.0e-5;
+      
+      if (tuning_beta_loop_order == 0) {
+         model.set_scale(tuning_scale);
+      } else {
+         model.run_to(tuning_scale);
+      }
 
       // Reference value of M_Z^2
       const double g1 = model.get_g1();
@@ -172,7 +178,7 @@ namespace flexiblesusy {
 
          if (Abs(abs_err / numeric_deriv) > 1.0 && Abs(numeric_deriv) > 1.0e-10)
             tuning_problem = true;
-
+         
          fine_tunings[it->first] = Abs((it->second / MVZ2) * numeric_deriv);
       }
 
@@ -233,6 +239,90 @@ namespace flexiblesusy {
             model.run_to(tuning_scale);
             ew_derivs.set_model(model);
          }
+      }
+
+      ew_derivs.set_ewsb_loop_order(tuning_ewsb_loop_order);
+      
+      Eigen::Matrix<double,num_ewsb_eqs,num_ewsb_eqs> mass_matrix = ew_derivs.calculate_unrotated_mass_matrix_hh();
+      
+      // N.B. extra minus sign
+      Eigen::Matrix<double, num_ewsb_eqs, Eigen::Dynamic> ewsb_derivs = -1.0 * calculate_ewsb_parameter_derivs(ew_derivs);
+      
+      // Solve system. Use inverse directly since mass matrix is small in the E6SSM (3 x 3),
+      // but note this has to change for matrices larger than 4 x 4.
+      bool invertible;
[…]

### 2014-12-22 fs-spectrum/models/lowE6SSM/lowE6SSM_two_scale_tuning_calculator.hpp

@@ -56,6 +56,7 @@ namespace flexiblesusy {
       /// Calculate the fine tunings. Returns true if there is a problem.
       bool calculate_fine_tunings_numerically();
       bool calculate_fine_tunings_approximately();
+      bool calculate_fine_tunings_using_rge_derivs();
 
       /// Coefficients at leading log order; useful for constructing
       /// Taylor series approximation to the RGE solutions
@@ -109,6 +110,9 @@ namespace flexiblesusy {
 
       Eigen::Matrix<double,num_ewsb_eqs,Eigen::Dynamic> calculate_ewsb_parameter_derivs(const lowE6SSM_ew_derivs&) const;
       Eigen::Matrix<double,Eigen::Dynamic,num_tuning_pars> calculate_beta_derivs() const;
+      Eigen::Matrix<double,Eigen::Dynamic,num_tuning_pars> calculate_beta_derivs_numerically(bool &) const;
+
+      Eigen::Matrix<double,Eigen::Dynamic,1> calculate_deriv_dlowscale_dparam_numerically(lowE6SSM_info::Parameters, bool &) const;
 
       Eigen::Matrix<double,Eigen::Dynamic,1> calculate_deriv_dlowscale_dLambdax() const;
       Eigen::Matrix<double,Eigen::Dynamic,1> calculate_deriv_dlowscale_dALambdax() const;
@@ -409,6 +413,17 @@ namespace flexiblesusy {
       double deriv_dlead_log_one_loop_ms2_dMassG() const;
       double deriv_dlead_log_one_loop_ms2_dMassBp() const;
 
+
+      /// For numerical calculations
+      struct low_scale_par_params {
+         lowE6SSM<Two_scale> model;
+         double low_scale;
+         std::size_t beta_loops;
+         lowE6SSM_info::Parameters p;
+         lowE6SSM_info::Parameters q;
+      };
+
+      static double low_scale_par(double x, void * params);
    };
 
 } // namespace flexiblesusy

### 2014-12-22 fs-spectrum/test/test_lowE6SSM_numerical_tuning_calculation.cpp

@@ -14,7 +14,7 @@
 #include "lowE6SSM_two_scale_tuning_calculator.hpp"
 
 #define BOOST_TEST_DYN_LINK
-#define BOOST_TEST_MODULE test_lowE6SSM_tuning_calculation
+#define BOOST_TEST_MODULE test_lowE6SSM_numerical_tuning_calculation
 
 #include <boost/test/unit_test.hpp>
 #include <boost/test/floating_point_comparison.hpp>
@@ -233,7 +233,7 @@ BOOST_AUTO_TEST_CASE( test_fine_tuning_tree_level_no_running )
    tuning_calc.set_input_scale(input_scale);
    tuning_calc.set_tuning_scale(tuning_scale);
 
-   bool numerical_problem = tuning_calc.calculate_fine_tunings_numerically();
+   bool numerical_problem = tuning_calc.calculate_fine_tunings_using_rge_derivs();
 
    std::map<lowE6SSM_info::Parameters, double> numerical_tunings = tuning_calc.get_fine_tunings();
 
@@ -313,7 +313,7 @@ BOOST_AUTO_TEST_CASE( test_fine_tuning_one_loop_no_running )
    tuning_calc.set_input_scale(input_scale);
    tuning_calc.set_tuning_scale(tuning_scale);
 
-   bool numerical_problem = tuning_calc.calculate_fine_tunings_numerically();
+   bool numerical_problem = tuning_calc.calculate_fine_tunings_using_rge_derivs();
 
    std::map<lowE6SSM_info::Parameters, double> numerical_tunings = tuning_calc.get_fine_tunings();
 
@@ -399,14 +399,14 @@ BOOST_AUTO_TEST_CASE( test_fine_tuning_one_loop_with_running )
    tuning_calc.set_input_scale(input_scale);
    tuning_calc.set_tuning_scale(tuning_scale);
 
-   bool numerical_problem = tuning_calc.calculate_fine_tunings_numerically();
+   bool numerical_problem = tuning_calc.calculate_fine_tunings_using_rge_derivs();
 
    std::map<lowE6SSM_info::Parameters, double> numerical_tunings = tuning_calc.get_fine_tunings();
-
 
    bool approximate_problem = tuning_calc.calculate_fine_tunings_approximately();
 
    std::map<lowE6SSM_info::Parameters, double> approximate_tunings = tuning_calc.get_fine_tunings();
+
 
[…]

### 2015-01-15 fs-spectrum/models/lowE6SSM/cutoff_scan_lowE6SSM.cpp
Various modifications to cutoff scan code, and lots of trace print output which should be cleaned up later

@@ -32,6 +32,7 @@
 #include "lowE6SSM_input_parameters.hpp"
 #include "lowE6SSM_spectrum_generator.hpp"
 #include "lowE6SSM_two_scale_tuning_calculator.hpp"
+#include "lowE6SSM_slha_io.hpp"
 
 #include "error.hpp"
 #include "grid_scanner.hpp"
@@ -43,8 +44,10 @@
 #include <boost/algorithm/string.hpp>
 #include <boost/lexical_cast.hpp>
 
+#include <chrono>
 #include <iostream>
 #include <map>
+#include <random>
 
 using namespace flexiblesusy;
 
@@ -115,165 +118,58 @@ void initialize_e6_charges(double theta, lowE6SSM_input_parameters& input)
    input.QHpbarp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::Hpbar, theta);
 }
 
-lowE6SSM_input_parameters get_default_inputs(double theta, bool is_constrained)
+void apply_constrained_bcs(lowE6SSM_input_parameters& input, double Lambda0, double Kappa0, double m12, double m0, double Azero)
 {
-   lowE6SSM_input_parameters input;
-
-   initialize_e6_charges(theta, input);
-
-   if (!is_constrained) {
-      input.KappaInput = Eigen::Matrix<double,3,3>::Zero();
-      input.KappaInput(0,0) = 0.6;
-      input.KappaInput(1,1) = 0.6;
-      input.KappaInput(2,2) = 0.6;
-      
-      input.Lambda12Input = Eigen::Matrix<double,2,2>::Zero();
-      input.Lambda12Input(0,0) = 0.2;
-      input.Lambda12Input(1,1) = 0.2;
-      
-      input.MuPrInput = 5000.; // GeV
-      
-      input.TYdInput = Eigen::Matrix<double,3,3>::Zero();
-      input.TYeInput = Eigen::Matrix<double,3,3>::Zero();
-      input.TKappaInput = Eigen::Matrix<double,3,3>::Zero();
-      input.TLambda12Input = Eigen::Matrix<double,2,2>::Zero();
-      input.TYuInput = Eigen::Matrix<double,3,3>::Zero();
-      
-      input.BMuPrInput = 5000.; // GeV^2
-      
-      input.mq2Input = Eigen::Matrix<double,3,3>::Zero();
[…]

### 2015-01-15 fs-spectrum/models/lowE6SSM/lowE6SSM_input_parameters.hpp

@@ -82,11 +82,12 @@ struct lowE6SSM_input_parameters {
    Eigen::Matrix<double,3,3>::Zero()), TYeInput(Eigen::Matrix<double,3,3>::Zero
    ()), TKappaInput(Eigen::Matrix<double,3,3>::Zero()), TLambda12Input(
    Eigen::Matrix<double,2,2>::Zero()), TLambdaxInput(0), TYuInput(Eigen::Matrix
-   <double,3,3>::Zero()), BMuPrInput(0), mq2Input(Eigen::Matrix<double,3,3>
-   ::Zero()), ml2Input(Eigen::Matrix<double,3,3>::Zero()), md2Input(
-   Eigen::Matrix<double,3,3>::Zero()), mu2Input(Eigen::Matrix<double,3,3>::Zero
-   ()), me2Input(Eigen::Matrix<double,3,3>::Zero()), mH1I2Input(Eigen::Matrix<
-   double,2,2>::Zero()), mH2I2Input(Eigen::Matrix<double,2,2>::Zero()),
+   <double,3,3>::Zero()), AYdInput(Eigen::Matrix<double,3,3>::Zero()), AYeInput(
+   Eigen::Matrix<double,3,3>::Zero()), AYuInput(Eigen::Matrix<double,3,3>::Zero()),
+   BMuPrInput(0), mq2Input(Eigen::Matrix<double,3,3>::Zero()), ml2Input(Eigen::Matrix
+   <double,3,3>::Zero()), md2Input(Eigen::Matrix<double,3,3>::Zero()), 
+   mu2Input(Eigen::Matrix<double,3,3>::Zero()), me2Input(Eigen::Matrix<double,3,3>::Zero()), 
+   mH1I2Input(Eigen::Matrix<double,2,2>::Zero()), mH2I2Input(Eigen::Matrix<double,2,2>::Zero()),
    msI2Input(Eigen::Matrix<double,2,2>::Zero()), mDx2Input(Eigen::Matrix<double
    ,3,3>::Zero()), mDxbar2Input(Eigen::Matrix<double,3,3>::Zero()), mHp2Input(0
    ), mHpbar2Input(0), MassBInput(0), MassWBInput(0), MassGInput(0),

### 2015-01-15 fs-spectrum/models/lowE6SSM/lowE6SSM_two_scale_tuning_calculator.cpp

@@ -1,6 +1,7 @@
 #include "lowE6SSM_two_scale_tuning_calculator.hpp"
 #include "numerics.hpp"
-
+//DH::note
+#include <iomanip>
 #include <gsl/gsl_deriv.h>
 
 namespace flexiblesusy {
@@ -263,7 +264,19 @@ namespace flexiblesusy {
          = mass_matrix_inverse * ewsb_derivs * beta_derivs;
 
       // Additional solution check here?
-
+      // std::cout << "-------------------------------------------------------------\n";
+      // std::cout << "MX scale pars = \n";
+      // for (std::map<lowE6SSM_info::Parameters,double>::const_iterator it = input_scale_pars.begin(),
+      //         end = input_scale_pars.end(); it != end; ++it) {
+      //    std::cout << lowE6SSM_info::parameter_names[it->first] << " = " << it->second << "\n";
+      // }
+      // std::cout << "inverse * ewsb = \n";
+      // std::cout << mass_matrix_inverse * ewsb_derivs;
+      // std::cout << "beta_derivs = \n";
+      // std::cout << beta_derivs << "\n";
+      // std::cout << "vev derivs = \n";
+      // std::cout << vev_derivs << "\n";
+      // std::cout << "-------------------------------------------------------------\n";
       double g1_at_tuning_scale = ew_derivs.get_model().get_g1();
       double g2_at_tuning_scale = ew_derivs.get_model().get_g2();
       double vd_at_tuning_scale = ew_derivs.get_model().get_vd();
@@ -348,13 +361,21 @@ namespace flexiblesusy {
 
       // Additional solution check here?
       // std::cout << "-------------------------------------------------------------\n";
+      // model.print(std::cout);
+      // std::cout << "MX scale pars = \n";
+      // for (std::map<lowE6SSM_info::Parameters,double>::const_iterator it = input_scale_pars.begin(),
+      //         end = input_scale_pars.end(); it != end; ++it) {
+      //    std::cout << lowE6SSM_info::parameter_names[it->first] << " = " << it->second << "\n";
+      // }
       // std::cout << "inverse * ewsb = \n";
-      // std::cout << mass_matrix_inverse * ewsb_derivs;
+      // std::cout << mass_matrix_inverse * ewsb_derivs << "\n";
       // std::cout << "beta_derivs = \n";
       // std::cout << beta_derivs << "\n";
       // std::cout << "vev derivs = \n";
       // std::cout << vev_derivs << "\n";
[…]

### 2015-01-15 fs-spectrum/softsusy/cutoff_scan_mssm.cpp

@@ -386,6 +386,46 @@ int main() {
                 << std::setw(12) << std::left << "error"
                 << '\n';
 
+      // DH::note
+      std::cerr << "# "
+                << std::setw(12) << std::left << "TanBeta" << ' '
+                << std::setw(12) << std::left << "Mu(MX)" << ' '
+                << std::setw(12) << std::left << "B(MX)/GeV" << ' '
+                << std::setw(12) << std::left << "AYu22(MX)/GeV" << ' '
+                << std::setw(12) << std::left << "mq222(MX)/GeV^2" << ' '
+                << std::setw(12) << std::left << "mu222(MX)/GeV^2" << ' '
+                << std::setw(12) << std::left << "MassWB(MX)/GeV" << ' '
+                << std::setw(12) << std::left << "Mhh(1)/GeV" << ' '
+                << std::setw(12) << std::left << "Mhh(2)/GeV" << ' '
+                << std::setw(12) << std::left << "mHd2/GeV^2" << ' '
+                << std::setw(12) << std::left << "mHu2/GeV^2" << ' '
+                << std::setw(12) << std::left << "MS/Gev" << ' '
+                << std::setw(12) << std::left << "MX/GeV" << ' '
+                << std::setw(12) << std::left << "Yu(2,2)" << ' '
+                << std::setw(12) << std::left << "Yd(2,2)" << ' '
+                << std::setw(12) << std::left << "Ye(2,2)" << ' '
+                << std::setw(12) << std::left << "g1" << ' '
+                << std::setw(12) << std::left << "g2" << ' '
+                << std::setw(12) << std::left << "g3" << ' '
+                << std::setw(12) << std::left << "Mu/GeV" << ' '
+                << std::setw(12) << std::left << "MassB/GeV" << ' '
+                << std::setw(12) << std::left << "MassWB/GeV" << ' '
+                << std::setw(12) << std::left << "MassG/GeV" << ' '
+                << std::setw(12) << std::left << "TYu(2,2)/GeV" << ' '
+                << std::setw(12) << std::left << "TYd(2,2)/GeV" << ' '
+                << std::setw(12) << std::left << "TYe(2,2)/GeV" << ' '
+                << std::setw(12) << std::left << "mq2(2,2)/GeV^2" << ' '
+                << std::setw(12) << std::left << "ml2(2,2)/GeV^2" << ' '
[…]

### 2015-01-15 fs-spectrum/softsusy/mssm_tuning_utils.cpp

@@ -1957,7 +1957,7 @@ double predpMSSMMzSqRun(double parVal)
    // this also in general changes M_{SUSY} as well. If M_{SUSY}
    // is allowed to vary then we need to iterate until we converge
    // to a new estimate for the right scale.
-   bool ALLOWVARYINGMSUSY = false; // < this needs to be false to get exact agreement with our analytics
+   const bool ALLOWVARYINGMSUSY = false; // < this needs to be false to get exact agreement with our analytics
 
    int maxIters = 100;
    double tol = 1.0e-5;

### 2015-01-15 fs-spectrum/softsusy/tuning_utils.h

@@ -63,7 +63,8 @@ DoubleVector doCalcFineTuning(SoftPars susyModel, void (*BCatMX)(SoftPars &, Dou
   	{
 	  hasError = false;
 
-  	  QR_solve(Q_mat, lhs_mat, n, rhsVector(susyModel, BCatMX, pars, vevs, i, mx, hasError), dVevs, sing);
+          DoubleVector rhsVec = rhsVector(susyModel, BCatMX, pars, vevs, i, mx, hasError);
+  	  QR_solve(Q_mat, lhs_mat, n, rhsVec, dVevs, sing);
 
 	  if (hasError)
 	    {

### 2015-01-15 paper/e6ssm-tuning-paper.tex
Added a note explaining notation I am using to try to shorten the expressions for the RGEs, when the numerical values of the U(1)' charges are not substituted in. The length of the general USSM 2-loop RGEs may still be an issue, though.
Adding in the 2-loop betas, however the sums over charges (unless I am missing something) don't at this stage match the special case of the cE6SSM - something to check?
Rewrote a coefficient in beta function for \lambda in more compact notation
Wrote coefficient of g_1'^4 in 2-loop beta function for \lambda more compactly
maded MSSM stop and higgs plots part of

@@
 %    - tuning as a function of stop mass for the MSSM and E6SSM
-As discussed in the introduction many recent papers have focussed on
-light stops as allowing natural SUSY and there has been a lot of
-theoretical effort to find SUSY models with a $125$ GeV Higgs boson
-while still having light stops and experimental efforts to search for
-light stops.  This is entirely appropriate since there are many good
-reasons to expect the soft masses to be set at high energies.  However
-that is not the only possibility and the fine tuning problem depends
-strongly the RG evolution from the GUT scale, as the soft Higgs masses
-that appear in the EWSB conditions pick up contributions from the soft
-squark masses.
+As discussed in the introduction many recent papers interested in
+natural supersymmetry have focussed on light stops, with much
+theoretical effort to find models where it is easier to get a $125$
+GeV Higgs boson and light stops simultaneously and much experimental
+efforts to search for light stops.  This is entirely appropriate since
+there are many good reasons to expect the soft masses to be set at
+high energies.  However that is not the only possibility and the fine
+tuning problem depends strongly on the RG evolution from the GUT
+scale, as the soft Higgs masses that appear in the EWSB conditions
+pick up contributions from the soft squark masses.
 
@@
 \begin{center}
-\resizebox{!}{10cm}{%
+\resizebox{!}{6cm}{%
 \includegraphics{mssm_stop_tuning.png}}
-\caption{Scatter plot of fine tuning in the MSSM as a function of
+\resizebox{!}{6cm}{%
+\includegraphics{mssm_higgs_tuning.png}}
+\caption{Left panel: Scatter plot of fine tuning in the MSSM as a function of
 the lightest stop mass, $m_{\tilde{t}_1}$, for the cut-off scales (from 
+bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV. 
+Right panel: Scatter plot of fine tuning in the MSSM as a function of
+the lightest Higgs mass, $m_{h_1}$, for the cut-off scales (from 
 bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
@@
 \end{figure}
-
-% DH:: I'm not sure if this is worth including? I've put a disclaimer in the
-% text, as well.
-\begin{figure}[h]
-\begin{center}
-\resizebox{!}{10cm}{%
-\includegraphics{mssm_higgs_tuning.png}}
-\caption{Scatter plot of fine tuning in the MSSM as a function of
-the lightest Higgs mass, $m_{h_1}$, for the cut-off scales (from 
-bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
-\label{Fig:mssmhiggstuning}
-\end{center}
-\end{figure}
-To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the
-variation in fine tuning when we scan over the stop masses and mixing,
-with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and
-$-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV,
-$50$ TeV and $100$ TeV.  The remaining parameters we fix such that at
-$M_{SUSY}$ they have the values $\mu=-97.5$ GeV, $B=-84.8$ GeV,
-$M_1=92.1$ GeV, $M_2=95.9$ GeV, $M_3=352$ GeV, $A_b=-117.9$ GeV,
-$A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV, $m_{e_i}=204$ GeV,
-$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV
-($i=1,2,3$). Although we should stress that making this choice will
-lead to a spectrum which is in conflict with the LHC limits, doing so
-ensures that fine tuning due to the other parameters is small, so that
-we avoid washing out the fine tuning impact of the stops when the
-tuning is small\footnote{For models in which the spectrum is heavier,
-  when the stop masses are small the fine tuning reaches a lower bound
-  imposed by other heavier parameters.} as can be the case when the
-stop masses are less than 1 TeV.  Note that the Higgs mass is also
-allowed to vary in this scan, as shown in
-Fig.~\ref{Fig:mssmhiggstuning}. This reveals the tuning problem which
-people have been worrying about since the discovery of the 125 GeV
-Higgs boson as we see that raising the stop masses is also pushing up
-the Higgs mass, meaning that heavier Higgs masses require more fine
-tuning.  However for a low value of the UV scale this tuning is not so
-severe unless the stops are very heavy, and a 125 geV Higgs can be
-obtained without much tuning in this unrealistic case where we have
-minimised other sources of tuning.  On the other hand the tuning
+To illustrate this, in the left panel of Fig.~\ref{Fig:mssmstoptuning}
+we show the variation in fine tuning when we scan over the stop masses
+and mixing, with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq
+10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq A_t\leq -20\textrm{
+  GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.  The remaining
+parameters we fix such that at $M_{SUSY}$ they have the values
+$\mu=-97.5$ GeV, $B=-84.8$ GeV, $M_1=92.1$ GeV, $M_2=95.9$ GeV,
+$M_3=352$ GeV, $A_b=-117.9$ GeV, $A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV,
+$m_{e_i}=204$ GeV, $m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and
+$m_{d_i}=438$ GeV ($i=1,2,3$). Although we should stress that making
+this choice will lead to a spectrum which is in conflict with the LHC
+limits, doing so ensures that fine tuning due to the other parameters
+is small, so that we avoid washing out the fine tuning impact of the
+stops when the tuning is small\footnote{For models in which the
+  spectrum is heavier, when the stop masses are small the fine tuning
+  reaches a lower bound imposed by other heavier parameters.} as can
+be the case when the stop masses are less than 1 TeV.  Note that the
+Higgs mass is also allowed to vary in this scan, as shown in the right
+panel of Fig.~\ref{Fig:mssmstoptuning}. This illustrates the tuning
+problem which people have been worrying about since the discovery of
+the 125 GeV Higgs boson as we see that raising the stop masses is also
+pushing up the Higgs mass, meaning that heavier Higgs masses require
+more fine tuning.  However for a low value of the UV scale this tuning
+is not so severe unless the stops are very heavy, and a 125 geV Higgs
+can be obtained without much tuning in this unrealistic case where we
+have minimised other sources of tuning.  On the other hand the tuning
 becomes more severe as we increase the cutoff such that for $M_X =
 10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
-tuning of $\approx 200 - 1000$ as shown in
-Fig.~\ref{Fig:mssmstoptuning} and the minimum tuning we see consistent
+tuning of $\approx 100 - 1000$ and the minimum tuning we see consistent
 with a $125$ GeV Higgs is $\approx 200$, as shown in
-Fig.~\ref{Fig:mssmhiggstuning}.
+Fig.~\ref{Fig:mssmstoptuning}.
 
@@
 
-As is shown in Fig.~\ref{} the tuning in the MSSM becomes larger
+To examine this further we also looked at how the tuning compares between the MSSM and E6SSM As is shown in Fig.~\ref{} the tuning in the MSSM becomes larger
 than that of the E$_6$SSM when the cutoff scale is ?
@@
 \beta_\lambda^{(1)}&=\lambda  \left[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2-\frac{3}{5} g_1^2 -2 \left ( \tilde{Q}_1^2 + \tilde{Q}_2^2 + \tilde{Q}_S^2\right )g_1'^2 \right],\label{eq:USSMLambdaBetaOneLoop}\\
-\beta_\lambda^{(2)}&=\lambda \left [ \left ( \right )g_1'^4\right ],\label{eq:USSMLambdaBetaTwoLoop}
+\beta_\lambda^{(2)}&=\lambda \bigg \{ -2\lambda^2\left ( \lambda^2+2\Sigma_\lambda+3\Sigma_\kappa\right )-4\Pi_\lambda-6\Pi_\kappa-3\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right ) \nonumber\\
+&{} -3\left ( 3y_t^4+3y_b^4+2y_t^2y_b^2+y_\tau^2 \right )+6g_2^2\Sigma_\lambda+g_1^2\left ( \frac{4}{5}y_t^2-\frac{2}{5}y_b^2+\frac{6}{5}y_\tau^2+\frac{4}{5}\Sigma_\kappa +\frac{6}{5}\Sigma_\lambda\right )\nonumber\\
+&{}\left.+g_1'^2\left [ 4\tilde{Q}_S^2\lambda^2 -6\left ( \tilde{Q}_2^2-\tilde{Q}_Q^2-\tilde{Q}_u^2\right )y_t^2-6\left ( \tilde{Q}_1^2-\tilde{Q}_Q^2-\tilde{Q}_d^2\right )y_b^2 \right.\right.\nonumber\\
+&{}\left.-2\left ( \tilde{Q}_1^2-\tilde{Q}_L^2-\tilde{Q}_e^2\right )y_\tau^2-6\left ( \tilde{Q}_S^2-\tilde{Q}_D^2-\tilde{Q}_{\overline{D}}^2 \right )\Sigma_\kappa-4\left ( \tilde{Q}_S^2-\tilde{Q}_1^2-\tilde{Q}_2^2\right )\Sigma_\lambda\right ]\nonumber\\
+&{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2\tilde{Q}_1^4+2\tilde{Q}_2^4+2\tilde{Q}_S^4+\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\Sigma_{\tilde{Q}}\right ]\nonumber\\
+&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [\tilde{Q}_1^2+\tilde{Q}_2^2+\left ( \tilde{Q}_2-\tilde{Q}_1\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}
 \end{align}
@@
 \end{equation*}
+Additionally, in order to keep our expressions compact we also use the notation
+\begin{align*}
+\Sigma_{\tilde{Q}}=\sum_i \tilde{Q}_i^2, \qquad \Pi_{\tilde{Q}}=\sum_i \tilde{Q}_i^4
+\end{align*}
+to denote sums over the $U(1)'$ charges, and
+\begin{align*}
+\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i\\
+&=-3\tilde{Q}_1+3\tilde{Q}_2+3\tilde{Q}_d-3\tilde{Q}_D+3\tilde{Q}_e-3\tilde{Q}_L+3\tilde{Q}_Q-6\tilde{Q}_u+3\tilde{Q}_{\overline{D}}+\tilde{Q}_{\overline{H'}}-\tilde{Q}_{H'}.
+\end{align*}
+Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised.
 % NB before submission replace this with a copy-paste of the bbl file?

### 2015-01-15 paper/e6ssm-tuning-paper.tex
Added more neutralino discussion.

@@
 \newcommand{\SuperField}[1]{\hat{#1}}
+\usepackage{url}
 
@@
 addition to this we also repeat each scan for three different values
-of $M_2$ to introduce more variation in the chargino masses, which can
-also be importnat due to the link between $\mu$ and the fine tuning.
+of $M_2$ to allow more variation in the chargino masses.
 
@@
 \end{ruledtabular}
-\caption{The parameters scanned over and the ranges of values used in the MSSM and the $E_6SSM$ models.}
+\caption{The parameters scanned over and the ranges of values used in
+  the MSSM and the $E_6SSM$ models.}
 \label{tab:scanranges}
@@
 tuning in the model for the E$_6$SSM is increased by the mass of the
-$Z^\prime$ boson.  So in the case of a very low cutoff much of the
-tuning required to get a 125 GeV Higgs has gone away.  However the
-tuning from the $Z^\prime$ mass appears already at tree level and is
-unavoidable regardless of the cutoff scale chosen, so in the E$_6$SSM
-current limits on the mass of the $Z^\prime$ boson imply that the
-E$_6$SSM fine tuning must be at least 100 regardless of assumptions
-about the way SUSY breaking happens.  Additionally if run II of the
-LHC pushes the limit on the $Z^\prime$ mass to be above $4.5$ TeV then
-the fine tuning in the model will be greater than at least 350.
+$Z^\prime$ boson.  So in the case of a very low cutoff the tuning
+required to get a 125 GeV Higgs is not so large.  However the tuning
+from the $Z^\prime$ mass appears already at tree level and is
+therefore not heavily suprressed when the cutoff scale is low. We find
+that in the E$_6$SSM current limits on the mass of the $Z^\prime$
+boson imply that the E$_6$SSM fine tuning is at least 100.
+Additionally if run II of the LHC pushes the limit on the $Z^\prime$
+mass to be above $4.5$ TeV then the fine tuning in the model will be
+greater than at least 350.
 
@@
 these models depends on less assumptions about SUSY breaking than the
-tuning reqyired by the $125$ GeV Higgs measurement which concerns
+tuning required by the $125$ GeV Higgs measurement which concerns
 people in the MSSM.
@@
 parameter (or effective $\mu$ parameter in these $U(1)$ extensions).
-Unfortunately the chargino limits from the LHC are not general enough
-so as to provide an absolute constraint on the model [Add: XSdetails on
-  limits and what they depend on].
+However the chargino limits from the LHC are scenario dependent and
+depending on whether there are light sleptons or sneutralinos and the mass
+difference between the lightest chargino and lightest neutralino.
+Current limits placed by CMS and ATLAS extend up to $m_{\chi^\pm_1}
+\approx 700-740$ GeV if there are light
+sleptons\cite{Khachatryan:2014qwa,Aad:2014nua} with much weaker bounds
+if there are no light sleptons or sneutrinos\footnote{Useful summary
+  plots of these limit may be found on the public pages of ATLAS,
+  \url{https://atlas.web.cern.ch/Atlas/GROUPS/PHYSICS/CombinedSummaryPlots/SUSY/ATLAS_SUSY_EWSummary/ATLAS_SUSY_EWSummary.png}
+  and CMS
+  \url{http://cms.web.cern.ch/sites/cms.web.cern.ch/files/styles/large/public/field/image/Image_03_exclusion_Combined.png?itok=8FMBpu_1}.}.
 
 Nonetheless the MSSM the impact of chargino limit is shown in
-Fig.~\ref{}.  There we see that if the the full parameter space with
-$m_{\chi^\pm} < 700$ GeV was excluded the impact would be to make the
-tuning in the MSSM with a $20$ TeV cutoff slightly worse than that of
-the E$_6$SSM with the same cutoff and a $Z^\prime$ mass just larger
-than current limits.  would be similar to that can also be attcked
-more directly by looking at chargino mass limits as this rasies $\mu$
-directly.  In the E$_6$SSM, while raising the chargino limit can have
-the same impact in princuiple, due to current limits on the $Z^\prime$
-mass already imposing a significant degree of tuning, chargino masses
-do not make much of a noticable change.
-
-[show plots in MSSM and E6SSM if it gets clened up, though maybe we
-  can just leave it out if it only shows that there is no big impact?]
-%    - plots of chargino bound impacts
+Fig.~\ref{Fig:chargino-plot}.  There we see that if the the full
+  parameter space with $m_{\chi^\pm} < 700$ GeV was excluded the
+  impact would be to make the tuning in the MSSM with a $20$ TeV
+  cutoff slightly worse than that of the E$_6$SSM with the same cutoff
+  and a $Z^\prime$ mass just larger than current limits.  would be
+  similar to that can also be attcked more directly by looking at
+  chargino mass limits as this rasies $\mu$ directly.  In the
+  E$_6$SSM, while raising the chargino limit can have the same impact
+  in principle, due to current limits on the $Z^\prime$ mass already
+  imposing a significant degree of tuning, chargino masses do not make
+  much of a noticable change.
+
+\begin{figure}[h]
+\begin{center}
+\resizebox{!}{10cm}{%
+\includegraphics{mssm_chargino_plot.png}}%%
+\caption{Scatter plot of fine tuning vs lightest Higgs mass in the MSSM with $m_{\chi^\pm_1} = 200$ GeV shown in green $m_{\chi^\pm_1} = 500$ GeV in blue and $m_{\chi^\pm_1} = 700$ GeV in red.}
+\label{Fig:chargino-plot}
+\end{center}
+\end{figure}
 
@@
 the rest to the same values we did in the scan carried out for
-Fig.~\ref{Fig:e6ssmvsmssm}
-% - plots for different U(1)' charge
-
-% DH:: for reference:
-%      U(1)_I \theta = \pi+\arctan\sqrt{3/5}
-%      U(1)_\psi \theta = \pi / 2
-%      U(1)_\eta \theta = -\arctan\sqrt{5/3}
-
-\begin{figure}[h]
+Fig.~\ref{Fig:e6ssmvsmssm}.
+
+\begin{figure}
 \begin{center}
@@
 \resizebox{!}{5cm}{%
-\includegraphics{e6eta_tb10_tuning_vs_higgs.png}}
+\includegraphics{e6eta_tb10_tuning_vs_higgs.png}}%%
 \caption{Scatter plot of fine tuning vs lightest Higgs mass in ... with $M_{Z^\prime} = 2.5$ TeV shown in blue and $M_{Z^\prime} = 4.5$ TeV in red.}
@@
 $\tan \beta$ are suppressed, making it difficult to raise the Higgs
-mass in the same way as happens in the other models, explaining why
+mass in the same way as happens in the other models and explaining why
 % DH:: I strongly suspect that they are invalid - but running scan

### 2015-01-15 paper/e6ssm-tuning-paper.tex
Started adding detailed discussion about the plots where we vary the cutoff.OH

@@
 
-To examine this further we also looked at how the tuning compares between the MSSM and E6SSM As is shown in Fig.~\ref{} the tuning in the MSSM becomes larger
-than that of the E$_6$SSM when the cutoff scale is ?
+To further illustrate point we looked at how the tuning compares for a
+low tuning benchmarks in the MSSM and E6SSM when the highscale
+boundary condition, $M_X$ is raised.  The results of this are shown in
+Fig.~\ref{Fig:BMs-varyMX} where in the top panel we see that in this
+case the dependence of the E6SSM tuning on the cutoff is rather
+complicated leading, such that any statement about which model is more
+tuned depends on the cutoff scale considered.
+
+The complicated shape of the E6SSM fine tuning curve can be understood
+by looking at the indivual sensitivities shown in bottom left panel.
+In this case one can see that the tuning is initially dominated by the
+$\Delta_\lambda$ sensitivity, which contains some terms proprtional to
+$M_Z^{\prime \, 2}$.  As the cutoff scale is raised however fine
+tuning contributions from the stops and gluino start to feed into the
+sensitivities, in particular $\Delta_{m_{H_u}^}2$ and $\Delta_\lamda$.
+In the latter these contribution have the opposite sign to those from
+$M_Z^\prime$ leading to this strange behaviour where $\Delta_\lambda$
+passes through zero.  However in $\Delta_{m_{H_u}^}2$ dominating at
+larger values of the cutoff scale we see the effect of the more common
+fine tuning problem where the stops add large contributions to
+$m_{H_u}^2$ , in this case leading to a large cancellation between
+$m_{H_u}^2(M_X)$ and $m_{Q_3}^2(M_X)$ inside $m_{H_u}^2(M_{SUSY})$.
+
+In the MSSM the panel on the bottom right shows that the largest
+tuning contributions come from $\Delta_{A_t}$ and $\Delta_{m_{H_u}^2}$
+with the former being the larger sensitivity until $M_X\approx 10^8$
+at which point $\Delta_{m_{H_u}^2}$ takes over.
+
+In this particular case the fine tuning of the E$_6$SSM benchmark becomes larger than that od the MSSM benchmark when $M_X\approx 10^{10}-10^{11}$ GeV.
+This is diue to ?
+large A_t mixing?, $M_3$?
+different RGEs?
+
+\begin{figure}
+\begin{center}
+\resizebox{!}{5.5cm}{%
+\includegraphics{e6ssm_mssm_cutoff_scan_fixed_at_ms_tuning_plot.png}}\\
+\resizebox{!}{5.5cm}{%
+\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}
+\resizebox{!}{5.5cm}{%
+\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}%%
+\caption{Top Panel: Scatter plot of fine tuning vs high scale $M_X$ for benchmark points given in (?).
+Left Panel: Individual sensitivites of E6SSM BM plotted against the high scale $M_X$.
+Right Panel: Individual sensitivites of MSSM BM plotted against the high scale $M_X$.
+}
+\label{Fig:BMs-varyMX}
+\end{center}
+\end{figure}
 

### 2015-01-16 paper/e6ssm-tuning-paper.tex
Fixed some typos that were stopping the pdf from compiling, but otherwise left the text unchanged, and added cutoff scan plots to the repository

@@
 tuning contributions from the stops and gluino start to feed into the
-sensitivities, in particular $\Delta_{m_{H_u}^}2$ and $\Delta_\lamda$.
+sensitivities, in particular $\Delta_{m_{H_u}^2}$ and $\Delta_\lambda$.
 In the latter these contribution have the opposite sign to those from
 $M_Z^\prime$ leading to this strange behaviour where $\Delta_\lambda$
-passes through zero.  However in $\Delta_{m_{H_u}^}2$ dominating at
+passes through zero.  However in $\Delta_{m_{H_u}^2}$ dominating at
 larger values of the cutoff scale we see the effect of the more common
@@
 This is diue to ?
-large A_t mixing?, $M_3$?
+large $A_t$ mixing?, $M_3$?
 different RGEs?

### 2015-01-18 fs-spectrum/models/lowE6SSM/cutoff_scan_lowE6SSM.cpp
Added large number of trace prints for looking at composition of tunings

@@ -1303,26 +1303,241 @@ int main()
                 << std::setw(12) << std::left << "vd" << ' '
                 << std::setw(12) << std::left << "vu" << ' '
                 << std::setw(12) << std::left << "vs" << ' '
-                << std::setw(12) << std::left << "ad" << ' '
-                << std::setw(12) << std::left << "bd" << ' '
-                << std::setw(12) << std::left << "cd" << ' '
-                << std::setw(12) << std::left << "dd" << ' '
-                << std::setw(12) << std::left << "au" << ' '
-                << std::setw(12) << std::left << "bu" << ' '
-                << std::setw(12) << std::left << "cu" << ' '
-                << std::setw(12) << std::left << "du" << ' '
-                << std::setw(12) << std::left << "as" << ' '
-                << std::setw(12) << std::left << "bs" << ' '
-                << std::setw(12) << std::left << "cs" << ' '
-                << std::setw(12) << std::left << "ds" << ' '
+                << std::setw(12) << std::left << "alpha(0,0)" << ' '
+                << std::setw(12) << std::left << "alpha(0,1)" << ' '
+                << std::setw(12) << std::left << "alpha(0,2)" << ' '
+                << std::setw(12) << std::left << "alpha(0,3)" << ' '
+                << std::setw(12) << std::left << "alpha(0,4)" << ' '
+                << std::setw(12) << std::left << "alpha(0,5)" << ' '
+                << std::setw(12) << std::left << "alpha(0,6)" << ' '
+                << std::setw(12) << std::left << "alpha(0,7)" << ' '
+                << std::setw(12) << std::left << "alpha(0,8)" << ' '
+                << std::setw(12) << std::left << "alpha(0,9)" << ' '
+                << std::setw(12) << std::left << "alpha(0,10)" << ' '
+                << std::setw(12) << std::left << "alpha(0,11)" << ' '
+                << std::setw(12) << std::left << "alpha(1,0)" << ' '
+                << std::setw(12) << std::left << "alpha(1,1)" << ' '
+                << std::setw(12) << std::left << "alpha(1,2)" << ' '
+                << std::setw(12) << std::left << "alpha(1,3)" << ' '
+                << std::setw(12) << std::left << "alpha(1,4)" << ' '
+                << std::setw(12) << std::left << "alpha(1,5)" << ' '
[…]

### 2015-01-18 fs-spectrum/models/lowE6SSM/lowE6SSM_two_scale_tuning_calculator.cpp

@@ -393,30 +393,246 @@ namespace flexiblesusy {
                                             get_deriv(it->first, vd_derivs), get_deriv(it->first, vu_derivs));
       }
       Eigen::Matrix<double,num_ewsb_eqs,Eigen::Dynamic> coeffs = mass_matrix_inverse * ewsb_derivs;
+      const Eigen::Array<double,1,num_tuning_pars> vs_derivs = vev_derivs.row(2);
       std::cerr << std::setw(12) << std::left << input_scale << ' '
                 << std::setw(12) << std::left << vd_at_tuning_scale << ' '
                 << std::setw(12) << std::left << vu_at_tuning_scale << ' '
                 << std::setw(12) << std::left << ew_derivs.get_model().get_vs() << ' '
                 << std::setw(12) << std::left << coeffs(0,0) << ' '
+                << std::setw(12) << std::left << coeffs(0,1) << ' '
+                << std::setw(12) << std::left << coeffs(0,2) << ' '
+                << std::setw(12) << std::left << coeffs(0,3) << ' '
+                << std::setw(12) << std::left << coeffs(0,4) << ' '
                 << std::setw(12) << std::left << coeffs(0,5) << ' '
+                << std::setw(12) << std::left << coeffs(0,6) << ' '
+                << std::setw(12) << std::left << coeffs(0,7) << ' '
+                << std::setw(12) << std::left << coeffs(0,8) << ' '
                 << std::setw(12) << std::left << coeffs(0,9) << ' '
+                << std::setw(12) << std::left << coeffs(0,10) << ' '
                 << std::setw(12) << std::left << coeffs(0,11) << ' '
                 << std::setw(12) << std::left << coeffs(1,0) << ' '
+                << std::setw(12) << std::left << coeffs(1,1) << ' '
+                << std::setw(12) << std::left << coeffs(1,2) << ' '
+                << std::setw(12) << std::left << coeffs(1,3) << ' '
+                << std::setw(12) << std::left << coeffs(1,4) << ' '
                 << std::setw(12) << std::left << coeffs(1,5) << ' '
+                << std::setw(12) << std::left << coeffs(1,6) << ' '
+                << std::setw(12) << std::left << coeffs(1,7) << ' '
+                << std::setw(12) << std::left << coeffs(1,8) << ' '
                 << std::setw(12) << std::left << coeffs(1,9) << ' '
[…]

### 2015-01-19 fs-spectrum/models/lowE6SSM/cutoff_scan_lowE6SSM.cpp
Temporarily reduced M3 to 1200 GeV in cutoff scan

@@ -809,7 +809,7 @@ lowE6SSM_input_parameters get_default_inputs(double theta, Input_set point, bool
          input.mHpbar2Input = Sqr(5000.); // GeV^2
          
          input.MassBInput = 300.; // GeV
-         input.MassGInput = 2000.; // GeV
+         input.MassGInput = 1200.0;//2000.; // GeV
          input.MassBpInput = 300.; // GeV
          break;
       }

### 2015-01-20 paper/e6ssm-tuning-paper.tex
added to paper plots I want to show for comparing mssm and e6ssm running up to GUT scale.

@@
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_mssm_cutoff_scan_fixed_at_ms_tuning_plot.png}}\\
+\includegraphics{e6ssm_mssm_cutoff_scan_3_points_tuning_plot.png}} 
+\resizebox{!}{5.5cm}{%
+\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
+\\
 \resizebox{!}{5.5cm}{%
@@
 \resizebox{!}{5.5cm}{%
-\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}%%
+\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_mssm_mixing_small_M3_all_tuning_data.png}}%%
 \caption{Top Panel: Scatter plot of fine tuning vs high scale $M_X$ for benchmark points given in (?).

### 2015-01-20 paper/e6ssm-tuning-paper.tex
moved around some details about plots and changed caption. still working on this.

@@
 
-To further illustrate point we looked at how the tuning compares for a
+To further illustrate point we looked at how the tuning compares for
 low tuning benchmarks in the MSSM and E6SSM when the highscale
-boundary condition, $M_X$ is raised.  The results of this are shown in
-Fig.~\ref{Fig:BMs-varyMX} where in the top panel we see that in this
-case the dependence of the E6SSM tuning on the cutoff is rather
-complicated leading, such that any statement about which model is more
-tuned depends on the cutoff scale considered.
+boundary condition, $M_X$ is raised.
+
+In the MSSM the panel on the bottom right shows that the largest
+tuning contributions come from $\Delta_{A_t}$ and $\Delta_{m_{H_u}^2}$
+with the former being the larger sensitivity until $M_X\approx 10^8$
+at which point $\Delta_{m_{H_u}^2}$ takes over.
+
+The results of this are shown in
+Fig.~\ref{Fig:BMs-varyMX} where in the top left panel we see that the
+dependence of the E6SSM tuning on the cutoff is rather complicated
+leading, such that any statement about which model is more tuned
+depends on the cutoff scale considered.
+
+E$_6$SSM BM1
 
@@
 
-In the MSSM the panel on the bottom right shows that the largest
-tuning contributions come from $\Delta_{A_t}$ and $\Delta_{m_{H_u}^2}$
-with the former being the larger sensitivity until $M_X\approx 10^8$
-at which point $\Delta_{m_{H_u}^2}$ takes over.
-
 In this particular case the fine tuning of the E$_6$SSM benchmark becomes larger than that od the MSSM benchmark when $M_X\approx 10^{10}-10^{11}$ GeV.
@@
 \includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_mssm_mixing_small_M3_all_tuning_data.png}}%%
-\caption{Top Panel: Scatter plot of fine tuning vs high scale $M_X$ for benchmark points given in (?).
-Left Panel: Individual sensitivites of E6SSM BM plotted against the high scale $M_X$.
-Right Panel: Individual sensitivites of MSSM BM plotted against the high scale $M_X$.
+\caption{{\bf Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in (?).
+{\bf Top right panel:}  Individual sensitivites of MSSM BM plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.
+{\bf Bottom left Panel:} Individual sensitivites of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.
+{\bf Bottom right Panel:}Individual sensitivites of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.
 }

### 2015-01-20 paper/e6ssm-tuning-paper.tex
explained the benchmark points as best I can for now.

@@
 
-To further illustrate point we looked at how the tuning compares for
+To further illustrate this point we looked at how the tuning compares for
 low tuning benchmarks in the MSSM and E6SSM when the highscale
-boundary condition, $M_X$ is raised.
-
-In the MSSM the panel on the bottom right shows that the largest
-tuning contributions come from $\Delta_{A_t}$ and $\Delta_{m_{H_u}^2}$
-with the former being the larger sensitivity until $M_X\approx 10^8$
-at which point $\Delta_{m_{H_u}^2}$ takes over.
-
-The results of this are shown in
-Fig.~\ref{Fig:BMs-varyMX} where in the top left panel we see that the
-dependence of the E6SSM tuning on the cutoff is rather complicated
-leading, such that any statement about which model is more tuned
-depends on the cutoff scale considered.
-
-E$_6$SSM BM1
-
-The complicated shape of the E6SSM fine tuning curve can be understood
-by looking at the indivual sensitivities shown in bottom left panel.
-In this case one can see that the tuning is initially dominated by the
-$\Delta_\lambda$ sensitivity, which contains some terms proprtional to
-$M_Z^{\prime \, 2}$.  As the cutoff scale is raised however fine
-tuning contributions from the stops and gluino start to feed into the
-sensitivities, in particular $\Delta_{m_{H_u}^2}$ and $\Delta_\lambda$.
-In the latter these contribution have the opposite sign to those from
-$M_Z^\prime$ leading to this strange behaviour where $\Delta_\lambda$
-passes through zero.  However in $\Delta_{m_{H_u}^2}$ dominating at
-larger values of the cutoff scale we see the effect of the more common
-fine tuning problem where the stops add large contributions to
-$m_{H_u}^2$ , in this case leading to a large cancellation between
-$m_{H_u}^2(M_X)$ and $m_{Q_3}^2(M_X)$ inside $m_{H_u}^2(M_{SUSY})$.
-
-In this particular case the fine tuning of the E$_6$SSM benchmark becomes larger than that od the MSSM benchmark when $M_X\approx 10^{10}-10^{11}$ GeV.
-This is diue to ?
-large $A_t$ mixing?, $M_3$?
-different RGEs?
+boundary condition, $M_X$ is raised.  The results of this are shown in
+Fig.~\ref{Fig:BMs-varyMX}.
+
+In the top left panel one can see that the MSSM tuning (green)
+steadily climbs as the cutoff scale is increased, as one would expect
+when the tuning originates from large soft masses entering from the
+RGEs. The panel on the top right confirms this, showing that the
+largest tuning contributions come from $\Delta_{A_t}$ and
+$\Delta_{m_{H_u}^2}$ with the former being the larger sensitivity
+until $M_X\approx 10^8$ GeV at which point $\Delta_{m_{H_u}^2}$ takes
+over, leading to the small kink in overall tuning which can be seen in
+the green curve in the top left panel. In thus case we have chosen a
+point with large mixing which reduce the MSSM tuning somewhat.  this
+does not eliminate the tuning as one there is still a string
+sensitivity to $A_t$, but we did find that increasing $A_t$ lead less
+fine tuning overall.
+
+The E$_6$SSM tunings are rather more complicated.  By comparing them
+to the MSSM tuning one can see that the scale at which the parameters
+are defined is very important for determining which point is more fine
+tuned.  In the bottom left panel one can see that the dependence of
+the E$_6$SSM tuning on the cutoff is rather complicated, illustrating
+that any statement about which model is more tuned depends on the
+cutoff scale considered.
+
+For E$_6$SSM BM1 the fine tuning is shown by the blue curve in top
+left panel of Fig.~\ref{Fig:BMs-varyMX} and the individual sensitivities
+are given in the bottom left panel. The tuning actually reduces
+initially as the cutoff is is increased from $20$ TeV.  This occurs
+because the tuning is initially dominated by $\Delta_\lambda$ (shown in
+solid blue in the bottom left panel) that contains some terms
+proportional to $M_Z^{\prime \, 2}$, which currently dominate the
+tuning.  However as the cutoff scale is increased contributions from
+the soft masses become more important and these actually start to
+cancel the large contribution to $\Delta_\lambda$ coming from
+$M_{Z^\prime}$ until $\Delta_\lambda$ passes through zero.  However at
+the same time these large soft masses also cause other sensitivities
+to grow, leading the overall tuning to start rising with $M_X$
+once. Nonetheless due to the lower stop masses and lower mixing [I'm
+  guessing slightly: Dylan I need to be able to refer to numbers
+  here!]  compared to both of the other points until $M_X \approx
+10^{11}$ GeV.  After this the tuning from $M_3$ starts to dominate in
+this point.  Although at $M_{SUSY}$ this point as the same $M_3$ value
+as the MSSM point, in the E$_6$SSM $M_3$ will be larger at $M_X$ due
+to the altered RGE running from exotic matter\footnote{This altered
+  RGE running is a result of the exotic matter introduced to keep the
+  $U(1)$ anomaly free rather than being a direct consequence of the
+  extra $U(1)$. }.  At the same time larger $M_3$ at higher scales
+reduces the soft squark masses at $M_X$.  Therefore the stop mass
+contributions are ameliorated, compared to the MSSM, both by allowing
+lighter stops at $M_{SUSY}$ and by the modified RGE running.
+Nonetheless the stops still have an impact, pushing up the sensitivity
+to $m_{H_u}^2$\footnote{$m_{H_u}^2(M_{SUSY})$ receives a positive
+  contribution to it's mass from $m_{H_u}^2(M_X)$ and a negative
+  contribution from $m_{Q_3}^2$. If $m_{H_u}^2(M_{SUSY})$ is held
+  fixed so that then as the cutoff increases the values of these
+  softmasses at $M_X$ will be larger and there we be a bigger
+  cancellation between them, making the sensitivity of $M_Z$ to both of
+  these parameters larger.}  showing the most commonly discussed
+aspect of the little hierarchy problem.
+
+By contrast the tuning for E$_6$SSM BM2 is very different.  This point
+was chosen as it had much lighter stops and a gluino mass that is just
+above the experimental limit of $1.4$ TeV \cite{}.  At $20$ TeV it was
+not amongst the lowest tuned points, since at that scale the tree
+level tuning from $M_{Z^\prime}$ dominates.  The reduction in $M_3$
+means that $\Delta_{M_3}$ is substantially lower and only becomes the
+dominant tuning very close to the GUT scale, giving a tuning at
+$10^{16}$ GeV of $\approx 900$, which is below that of the other two
+benchmark points.  Since large mixing was also used to reduce allow
+lighter stops, we see initially a large contribution from
+$\Delta_{A_t}$ as we did in the MSSM benchmark.
+[Last thing that needs to be explained - why do $\Delta_{M_3}$ and $\Delta_{m_{H_u}^2}$ start to decrease at $M_X$.
+I'm guessing something funny to do with their values and also  $m_{Q}^2$ and $M_3$ at the highscales.
+but i need to see the numbers to know.]
 
@@
 {\bf Top right panel:}  Individual sensitivites of MSSM BM plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.
-{\bf Bottom left Panel:} Individual sensitivites of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.
-{\bf Bottom right Panel:}Individual sensitivites of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.
+{\bf Bottom left panel:} Individual sensitivites of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.
+{\bf Bottom right panel:}Individual sensitivites of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.
 }

### 2015-01-20 paper/e6ssm-tuning-paper.tex
fixed small typos.

@@
 
-To further illustrate this point we looked at how the tuning compares for
-low tuning benchmarks in the MSSM and E6SSM when the highscale
+To further illustrate this point we looked at how the tuning compares
+for low tuning benchmarks in the MSSM and E6SSM when the highscale
 boundary condition, $M_X$ is raised. The results of this are shown in
-Fig.~\ref{Fig:BMs-varyMX}.
+Fig.~\ref{Fig:BMs-varyMX}. Since the behaviour is a quite complicated
+we now discuss these in detail as it provides some insight into the
+many differences in the tuning between the two models.
 
@@
 the green curve in the top left panel. In thus case we have chosen a
-point with large mixing which reduce the MSSM tuning somewhat.  this
-does not eliminate the tuning as one there is still a string
+point with large mixing which is known to reduce the MSSM tuning.  We
+found this does not eliminate the tuning as there is still a strong
 sensitivity to $A_t$, but we did find that increasing $A_t$ lead less
-fine tuning overall.
-
-The E$_6$SSM tunings are rather more complicated.  By comparing them
-to the MSSM tuning one can see that the scale at which the parameters
-are defined is very important for determining which point is more fine
-tuned.  In the bottom left panel one can see that the dependence of
-the E$_6$SSM tuning on the cutoff is rather complicated, illustrating
-that any statement about which model is more tuned depends on the
-cutoff scale considered.
+fine tuning overall fo the points we looked at.
+
+The E$_6$SSM tunings are rather more complicated as there are more
+sources of fine tuning.  By comparing them to the MSSM tuning one can
+see that the scale at which the parameters are defined is very
+important for determining which point is more fine tuned.  In the
+bottom left panel one can see that the dependence of the E$_6$SSM
+tuning on the cutoff is rather complicated, illustrating that any
+statement about which model is more tuned depends on the cutoff scale
+considered.
 
@@
 $\Delta_{A_t}$ as we did in the MSSM benchmark.
-[Last thing that needs to be explained - why do $\Delta_{M_3}$ and $\Delta_{m_{H_u}^2}$ start to decrease at $M_X$.
+[Last thing that needs to be explained - why do $\Delta_{M_3}$ and $\Delta_{m_{H_u}^2}$ start to decrease at large $M_X$.
 I'm guessing something funny to do with their values and also  $m_{Q}^2$ and $M_3$ at the highscales.

### 2015-01-20 paper/e6ssm-tuning-paper.tex
Fixed a paragraph that had been missed in editing.  Added reference to table that we need to include.

@@
 for low tuning benchmarks in the MSSM and E6SSM when the highscale
-boundary condition, $M_X$ is raised. The results of this are shown in
+boundary condition, $M_X$ is raised. These benchmarks are defined in
+table \ref{} and the results are shown in
 Fig.~\ref{Fig:BMs-varyMX}. Since the behaviour is a quite complicated
@@
 sensitivity to $A_t$, but we did find that increasing $A_t$ lead less
-fine tuning overall fo the points we looked at.
-
-The E$_6$SSM tunings are rather more complicated as there are more
-sources of fine tuning.  By comparing them to the MSSM tuning one can
-see that the scale at which the parameters are defined is very
-important for determining which point is more fine tuned.  In the
-bottom left panel one can see that the dependence of the E$_6$SSM
-tuning on the cutoff is rather complicated, illustrating that any
-statement about which model is more tuned depends on the cutoff scale
-considered.
+fine tuning overall for the points we looked at.
+
+Comparing the MSSM tuning to the E$_6$SSM tunings one can see that
+which point is more fine tuned depends on the scale at which the
+parameters are defined.  This illustrates that any statement about which
+model is more tuned depends on the cutoff scale considered.
 

### 2015-01-20 paper/e6ssm-tuning-paper.tex
More typo fixing and rephrasings for clarity.

@@
 natural scenarions from just placing tougher limits on the $Z^\prime$
-mass .
+mass.
 
@@
 the E$_6$SSM looks more fine tuned than the MSSM this depends on the
-cutoff scale.  Indeed in \cite{Athron:2013ipa} a constrained version
-of the E$_6$SSM, with the cutoff at the GUT scale, is considered and
-there the cE$_6$SSM was found to be less tuned than the cMSSM. Since a
-125 GeV Higgs can be achieved in the E$_6$SSM with ligher stops, then
-if the cutoff is large, the larger stop masses of the MSSM can make
-that model more fine tuned due to large RGE effects.
-
-To further illustrate this point we looked at how the tuning compares
-for low tuning benchmarks in the MSSM and E6SSM when the highscale
-boundary condition, $M_X$ is raised. These benchmarks are defined in
-table \ref{} and the results are shown in
-Fig.~\ref{Fig:BMs-varyMX}. Since the behaviour is a quite complicated
-we now discuss these in detail as it provides some insight into the
-many differences in the tuning between the two models.
+high scale boundary, $M_X$, where the parameters are assumed to be set
+by some SUSY breaking mechanism.  Indeed in \cite{Athron:2013ipa} a
+constrained version of the E$_6$SSM, with the highscale boundary at
+the GUT scale, is considered and there the cE$_6$SSM was found to be
+less tuned than the cMSSM. Since a 125 GeV Higgs can be achieved in
+the E$_6$SSM with ligher stops, then if the cutoff is large, the
+larger stop masses of the MSSM can make that model more fine tuned due
+to large RGE effects.
+
+To further illustrate this point we looked at how the tuning varies
+with $M_X$ for low tuning benchmarks in the MSSM and E6SSM. These
+benchmarks are defined in table \ref{} and the results are shown in
+Fig.~\ref{Fig:BMs-varyMX}. Since the behaviour is quite complicated we
+now discuss these in detail as it provides some insight into the many
+differences in the tuning between the two models.
+
+\begin{figure}
+\begin{center}
+\resizebox{!}{5.5cm}{%
+\includegraphics{e6ssm_mssm_cutoff_scan_3_points_tuning_plot.png}} 
+\resizebox{!}{5.5cm}{%
+\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
+\\
+\resizebox{!}{5.5cm}{%
+\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}
+\resizebox{!}{5.5cm}{%
+\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_mssm_mixing_small_M3_all_tuning_data.png}}%%
+\caption{{\it Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in (?).
+{\it Top right panel:}  Individual sensitivites of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.
+{\it Bottom left panel:} Individual sensitivites of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.
+{\it Bottom right panel:} Individual sensitivites of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.
+}
+\label{Fig:BMs-varyMX}
+\end{center}
+\end{figure}
 
@@
 over, leading to the small kink in overall tuning which can be seen in
-the green curve in the top left panel. In thus case we have chosen a
-point with large mixing which is known to reduce the MSSM tuning.  We
+the green curve in the top left panel. In this case we have chosen a
+point with large mixing, which is known to reduce the MSSM tuning.  We
 found this does not eliminate the tuning as there is still a strong
@@
 which point is more fine tuned depends on the scale at which the
-parameters are defined.  This illustrates that any statement about which
-model is more tuned depends on the cutoff scale considered.
+parameters are defined.  This illustrates that any statement about
+which model is more tuned depends on the high scale boundary, $M_X$.
 
 For E$_6$SSM BM1 the fine tuning is shown by the blue curve in top
-left panel of Fig.~\ref{Fig:BMs-varyMX} and the individual sensitivities
-are given in the bottom left panel. The tuning actually reduces
-initially as the cutoff is is increased from $20$ TeV.  This occurs
-because the tuning is initially dominated by $\Delta_\lambda$ (shown in
-solid blue in the bottom left panel) that contains some terms
-proportional to $M_Z^{\prime \, 2}$, which currently dominate the
-tuning.  However as the cutoff scale is increased contributions from
-the soft masses become more important and these actually start to
-cancel the large contribution to $\Delta_\lambda$ coming from
-$M_{Z^\prime}$ until $\Delta_\lambda$ passes through zero.  However at
-the same time these large soft masses also cause other sensitivities
-to grow, leading the overall tuning to start rising with $M_X$
-once. Nonetheless due to the lower stop masses and lower mixing [I'm
-  guessing slightly: Dylan I need to be able to refer to numbers
-  here!]  compared to both of the other points until $M_X \approx
-10^{11}$ GeV.  After this the tuning from $M_3$ starts to dominate in
-this point.  Although at $M_{SUSY}$ this point as the same $M_3$ value
-as the MSSM point, in the E$_6$SSM $M_3$ will be larger at $M_X$ due
-to the altered RGE running from exotic matter\footnote{This altered
-  RGE running is a result of the exotic matter introduced to keep the
-  $U(1)$ anomaly free rather than being a direct consequence of the
-  extra $U(1)$. }.  At the same time larger $M_3$ at higher scales
-reduces the soft squark masses at $M_X$.  Therefore the stop mass
-contributions are ameliorated, compared to the MSSM, both by allowing
-lighter stops at $M_{SUSY}$ and by the modified RGE running.
-Nonetheless the stops still have an impact, pushing up the sensitivity
-to $m_{H_u}^2$\footnote{$m_{H_u}^2(M_{SUSY})$ receives a positive
-  contribution to it's mass from $m_{H_u}^2(M_X)$ and a negative
-  contribution from $m_{Q_3}^2$. If $m_{H_u}^2(M_{SUSY})$ is held
-  fixed so that then as the cutoff increases the values of these
-  softmasses at $M_X$ will be larger and there we be a bigger
-  cancellation between them, making the sensitivity of $M_Z$ to both of
-  these parameters larger.}  showing the most commonly discussed
-aspect of the little hierarchy problem.
+left panel of Fig.~\ref{Fig:BMs-varyMX} and the individual
+sensitivities are given in the bottom left panel. The tuning actually
+reduces initially as the cutoff is is increased from $20$ TeV.  This
+occurs because the largest sensitivity is initially $\Delta_\lambda$
+(shown in solid blue in the bottom left panel).  This contains some
+terms proportional to $M_Z^{\prime \, 2}$, which provide the dominant
+contribution to this sensitivity at very low $M_X$.  However as $M_X$
+is increased contributions from the soft masses become more important
+and these actually start to cancel the large contribution to
+$\Delta_\lambda$ coming from $M_{Z^\prime}$ until $\Delta_\lambda$
+passes through zero.  At the same time though these large soft masses
+also cause other sensitivities to grow, in particular $\Delta_{M_3}$.
+The fine tuning rises with $M_X$ once $M_X \gtrsim 10^5-10^6$ GeV,
+but remains lower than that of the other points, until $M_X \approx
+10^{11}$ GeV.  Eventuially the $\Delta_{M_3}$ sensitivity leads to
+this point being the most fine tuned of the three shown in
+Fig.~\ref{Fig:BMs-varyMX}.
+
+ Although the gluino mass and $M_3(M_{SUSY})$ have similar values to
+ those in the MSSM point, in the E$_6$SSM $M_3(M_X)$ is larger
+ due to the altered RGE running from exotic matter\footnote{This
+   altered RGE running is a result of the exotic matter introduced to
+   keep the extra $U(1)$ anomaly free. }. This is why the E$_6$SSM
+ point has the much larger tuning, coming from $\Delta_{M_3}$.
+
+Interstingly other sensitivities are suppressed by this effect since
+at the same time larger $M_3$ at higher scales reduces the soft squark
+masses at $M_X$.  Therefore the stop mass contributions are
+ameliorated, compared to the MSSM, both by allowing lighter stops at
+$M_{SUSY}$ and by the modified RGE running.  Nonetheless the stops
+still do lead to $\Delta_{m_{H_u}^2}$ increasing with the cutoff
+through the usual mecahnism \footnote{Wherein $m_{H_u}^2(M_{SUSY})$
+  receives a positive contribution to it's mass from $m_{H_u}^2(M_X)$
+  and a negative contribution from $m_{Q_3}^2(M_X)$ and
+  $m_{U_3}^2(M_X)$, allowing heavy stop masses to cause fine
+  tuning. In this case $m_{H_u}^2(M_{SUSY})$ is held fixed so as the
+  cutoff increases the values of these softmasses at $M_X$ will be
+  larger and there we be a bigger cancellation between them,
+  increasing the sensitivity of $M_Z$ to both $m_{H_u}^2$ and the soft
+  scalar masses for the stops.}.
 
@@
 but i need to see the numbers to know.]
-
-\begin{figure}
-\begin{center}
-\resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_mssm_cutoff_scan_3_points_tuning_plot.png}} 
-\resizebox{!}{5.5cm}{%
-\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
-\\
-\resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}
-\resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_mssm_mixing_small_M3_all_tuning_data.png}}%%
-\caption{{\bf Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in (?).
-{\bf Top right panel:}  Individual sensitivites of MSSM BM plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.
-{\bf Bottom left panel:} Individual sensitivites of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.
-{\bf Bottom right panel:}Individual sensitivites of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.
-}
-\label{Fig:BMs-varyMX}
-\end{center}
-\end{figure}
 

### 2015-01-20 paper/e6ssm-tuning-paper.tex
Edited introduction for clarity and to account for what we now have.
E6SSM parts still need to be heavily edited.

@@
 
-The Higgs causes a naturalness problem because at tree level it has an
-upper bound of the mass of the $Z$ boson, $M_Z$. The dominant higher
-order corrections to the Higgs mass come from stops and to obtain a
-$125$ GeV Higgs they need be rather heavy. Heavy stops will provide a
-large contribution to the soft breaking mass for the up-type Higgs
-scalar, $m_{H_u}^2$ at low energies, through the evolution of the
-renormalisation group equations (RGEs) from the grand unification
-(GUT) scale to the electroweak (EW) scale. This affects the SUSY
-prediction of the electroweak VEV, $v$, or $M_Z$.  This naturalness
-problem motivates both further examination of non-minimal SUSY models
-that can raise the Higgs mass without the need for heavy stops and
-alternative possibilities for how the soft breaking parameters get
-generated, which might set them them at lower energies, reducing the
-influence the stops have on the soft breaking mass for the up-type
-Higgs scalar, $m_{H_u}^2$.
+In the MSSM the Higgs mass causes a naturalness problem because at
+tree level it has an upper bound of the mass of the $Z$ boson,
+$M_Z$. The dominant higher order corrections to the Higgs mass come
+from stops and to obtain a $125$ GeV Higgs they need be rather
+heavy. Heavy stops will provide a large contribution to the low energy
+value of $m_{H_u}^2$, the soft breaking mass for the up-type Higgs
+scalar, through the evolution of the renormalisation group equations
+(RGEs) from the grand unification (GUT) scale to the electroweak (EW)
+scale. This affects the SUSY prediction of the electroweak VEV, $v$,
+or $M_Z$.  This naturalness problem motivates both further examination
+of non-minimal SUSY models that can raise the Higgs mass without the
+need for heavy stops and alternative possibilities for how the soft
+breaking parameters get generated, which might set them at lower
+energies, reducing the influence the stops have on $m_{H_u}^2$.
 
@@
 from the stops. We find that the $Z^\prime$ limit is enough to already
-require moderate fine tuning.  We also show this is comparable to the
-situation in the MSSM defined at the same scale if chargino limit is
-$700$ GeV, which is the most conservative limit on can obtain and
-above the tuning from the stops, in both the MSSM and U(1) extensions.
-We also show that the tuning from the stops becomes larger when the
-high scale is raised to ?? whereas for the E$_6$SSM the minimum tuning
-is lower than the MSSM above this scale.  Therefore it is clear that
-which model is preferred and how large the tuning is depends on our
-assumptions about SUSY breaking models.
-
-However we also show that if the $Z^\prime$ limit is the extended to
-?? then $U(1)$ extensions of the MSSM will already suffer from a
-severe tuning, irrespective of the UV boundary condition for the RGE
-evolution.  Therefore the $Z^\prime$ constraint is amongst the most
-important in terms of tuning and attacking natural supersymmetry
-experimentally and the next run of the LHC will be crucial.
+require moderate fine tuning in the E6SSM.  We also show this is
+comparable to the situation in the MSSM defined at the same scale if
+chargino's could be ruled out below $700$ GeV.  We then show how this
+tuning from the $Z^\prime$ mass looks for different $U(1)$ extensions,
+finding that the current severity depends upon the charges but that
+$Z^\prime$ limits are important in constraining the most natural
+scenarios in all of these models.  Therefore the $Z^\prime$ constraint
+is amongst the most important in terms of tuning and attacking natural
+supersymmetry experimentally and the next run of the LHC will be
+crucial in this respect.
+
+Finally we make a case study, for a few benchmarks, of the impact of
+raising the high scale boundary condition, $M_X$, at which the SUSY
+breaking parameters must be fixed by some SUSY breaking mechanism. We
+show that which model has less fine tuning depends on $M_X$.  We also
+see rather complicated behaviour in the tuning for the E$_6$SSM points
+due to the combination of different sources of tuning.
 
@@
 $\mu$-problem as the USSM \cite{Cvetic:1995rj, Jain:1995cb,
-  Nir:1995bu, Cvetic:1996mf, Cvetic:1997ky}, while we will sometimes
-specify that the models are inspired by $E_6$ by referring to them as
-such. Finally we will also discuss specific models with complete $E_6$
-matter multiplets at low energies and an extra $U(1)$ under which the
-right handed neutrino remains interaction-less as
-E$_6$SSM-variants\cite{Howl:2007zi, Braam:2009fi, Braam:2010sy,
-  Hall:2011zq, Nevzorov:2012hs, Athron:2014pua}, with the E$_6$SSM
-reserved for the original formulation of this model
-\cite{King:2005jy,King:2005my,Athron:2010zz} original formulation of
-the model.
+  Nir:1995bu, Cvetic:1996mf, Cvetic:1997ky}, but since avoiding gauge
+anomalies is straightforward in the when the $U(1)$appears from the
+breakdown of $E_6$ and complete matter multiplets are present at low
+energies, we will sometimes refer to such models as $E_6$ inspired.
+Models with with complete $E_6$ matter multiplets at low energies and
+an extra $U(1)$ under which the right handed neutrino remains
+interaction-less are often refered to as the exceptional supersymmtric
+standard models (E$_6$SSM). However we will reserve the name E$_6$SSM
+to the original formulation of models
+\cite{King:2005jy,King:2005my,Athron:2010zz}, and refer to similar
+models as E$_6$SSM-variants\cite{Howl:2007zi, Braam:2009fi,
+  Braam:2010sy, Hall:2011zq, Nevzorov:2012hs, Athron:2014pua}.
 

### 2015-01-20 paper/e6ssm-tuning-paper.tex
Merged some of the U(1) and E6 literature review into model section and hopefully thereby reduced repitition and improved clarity. may still be a bit waffly.

@@
 due to the combination of different sources of tuning.
-
-Here we will refer to U(1) extensions of the MSSM, which solve the
-$\mu$-problem as the USSM \cite{Cvetic:1995rj, Jain:1995cb,
-  Nir:1995bu, Cvetic:1996mf, Cvetic:1997ky}, but since avoiding gauge
-anomalies is straightforward in the when the $U(1)$appears from the
-breakdown of $E_6$ and complete matter multiplets are present at low
-energies, we will sometimes refer to such models as $E_6$ inspired.
-Models with with complete $E_6$ matter multiplets at low energies and
-an extra $U(1)$ under which the right handed neutrino remains
-interaction-less are often refered to as the exceptional supersymmtric
-standard models (E$_6$SSM). However we will reserve the name E$_6$SSM
-to the original formulation of models
-\cite{King:2005jy,King:2005my,Athron:2010zz}, and refer to similar
-models as E$_6$SSM-variants\cite{Howl:2007zi, Braam:2009fi,
-  Braam:2010sy, Hall:2011zq, Nevzorov:2012hs, Athron:2014pua}.
-
-$U(1)$ and $E_6$ inspired extensions of the MSSM have been studied
-very widely in the literature \cite{Gunion:1989we, Gunion:1992hs,
-  Binetruy:1985xm, Ellis:1986yg, Ibanez:1986si, Gunion:1986ky,
-  Haber:1986gz, Baer:1987eb, Gunion:1987jd, Grifols:1986vr,
-  Ellis:1986ip, Morris:1987fm, Drees:1987tp, Ma:1995xk,
-  Suematsu:1997tv, Suematsu:1997qt, Suematsu:1997au, Keith:1996fv,
-  Keith:1997zb, Gherghetta:1996yr, Demir:1998dk, Langacker:1998tc,
-  Hambye:2000bn, Ma:2000jf} (or for reviews see
-\cite{Hewett:1988xc,Langacker:2008yv}).  There has also been a lot of
-work recently including investigations of the neutralino sector
-\cite{Hesselbach:2001ri, Barger:2005hb, Choi:2006fz,
-  Barger:2007nv};the relic abundance of dark matter
-\cite{Kalinowski:2008iq}; GUT scale family symmetries which can
-explain the hierarchy of masses in the fermion sector and their
-associated mixings \cite{Stech:2008wd}; neurtrino physics
-\cite{Kang:2004ix}; explanations of the matter-anti-matter asymmetry
-of the universe though EW baryogensis or leptogensis
-\cite{Hambye:2000bn,Ma:2000jf,Kang:2004pp}; dipole moments
-\cite{GutierrezRodriguez:2006hb}; anomaly mediated SUSY breaking with
-D-term contributions \cite{Asano:2008ju} and the (extended) Higgs
-sectors \cite{Daikoku:2000ep,Ham:2008xf}.
-
-In this paper we will often focus on a very well motivated $E_6$
-inspired $U(1)$ extension, the Exceptional Supersymmetric Standard
-Model (E$_6$SSM)\cite{King:2005jy,King:2005my,Athron:2010zz}.  In this
-model since the right handed neutrino remains interaction-less they
-may explain the tiny observed masses of neutrinos via the see-saw
-mechanism and the baryon asymmetry in the universe via leptogenesis
-\cite{Hambye:2000bn,King:2008qb, King:2008gw}.  Recently it has also
-been studied in the context of electroweak baryogenesis
-\cite{Chao:2014hya}.
-
-The gauge coupling running in the E$_6$SSM at the two-loop level leads
-to unification more precisely than in the MSSM \cite{King:2007uj} or
-in slightly modified scenarios two-step unification can take place
-\cite{Howl:2007hq,Howl:2007zi}. If the exotic particles are light in
-these models this can open up non-standard decays of the SM--like
-Higgs boson \cite{Hall:2010ix,Nevzorov:2013tta,Athron:2014pua}. The
-correct relic abundance could be obtained entirely through an almost
-decoupled ``inert'' neutralino sector \cite{Hall:2009aj},.  However
-this is no longer phenomenologically viable due to limits from direct
-detection of dark matter
-\cite{2011PhRvL.107m1302A,2012PhRvL.109r1301A, Akerib:2013tjd} and due
-to a significant suppression of the decay of the lightest Higgs boson
-into SM states, due to a new channel into inert singlinos opening up.
-
-There are still several remaining options. One may specialize to
-scenarios known as the EZSSM \cite{Hall:2011zq} where the inert
-singlinos, which cause these problems are entirely decoupled and the
-relic abundance is fitted with a bino-like candidate with a novel
-mechanism involving back-scattering into a Heavier inert
-Higgsino. Another well motivated scenario admits two possible dark
-matter candidates \cite{Nevzorov:2012hs}, where one will be an inert
-singlino and the other will have a similar composition to MSSM
-neutralinos. The simplest phenomenologically viable solution in that
-case is to make the singlinos extremely light hot dark matter
-candidate and explains almost all the relic abundance density with
-
-The impact of gauge kinetic mixing in the case where both of the extra
-U(1)'s appearing from the breakdown of E$_6$ are present at low energy
-was studied in \cite{Rizzo:2012rf}.  The E$_6$SSM was also included in
-a studies looking at how first or second generation sfermion masses
-can be used to constrain the GUT scale parameters \cite{Miller:2012vn}
-and the renormalization of VEVs \cite{Sperling:2013eva,
-  Sperling:2013xqa}.  The particle spectrum and collider signatures of
-constrained version of the E$_6$SSM have been studied in a series of
-papers,
-\cite{Athron:2009ue,Athron:2009bs,Athron:2011wu,Athron:2012sq}. The
-threshold corrections to the $\overline{DR}$ gauge and Yukawa
-couplings in the E$_6$SSM were calculated and the numerical impact in
-the constrained version examined \cite{Athron:2012pw}.
 
@@
 
-  The couplings for the $U(1)^\prime$ gauge group should allow the
-  following renormalisable superpotential terms required in the USSM,
-  \be W_{USSM} = y^U_{ij} \hat{u}^c_i \hat{H}_u \hat{Q}_j + y^D_{ij}
-  \hat{d}^c_i \hat{H}_d \hat{Q}_j + y^E_{ij} \hat{e}^c_i \hat{H}_d
-  \hat{L}_j + \lambda \hat{S} \hat{H}_d \hat{H}_u, \ee with $i,j \in
-  \{1,2,3\}$.
+%%%--------------Inserted from introduction-------------------%%%%
+
+Here we will refer to U(1) extensions of the MSSM, which solve the
+$\mu$-problem as the USSM \cite{Cvetic:1995rj, Jain:1995cb,
+  Nir:1995bu, Cvetic:1996mf, Cvetic:1997ky}.  The couplings for the
+$U(1)^\prime$ gauge group should allow the following renormalisable
+superpotential terms required in the USSM, \be W_{USSM} = y^U_{ij}
+\hat{u}^c_i \hat{H}_u \hat{Q}_j + y^D_{ij} \hat{d}^c_i \hat{H}_d
+\hat{Q}_j + y^E_{ij} \hat{e}^c_i \hat{H}_d \hat{L}_j + \lambda \hat{S}
+\hat{H}_d \hat{H}_u, \ee with $i,j \in \{1,2,3\}$.
 
@@
 gauge symmetry that can be obtained from the break down of the $E_6$
-gauge symmetry which is anomaly free and have all matter multiplets
-from the $Z7$-plet representation of $E_6$ survive down to low energies.
+gauge symmetry which is anomaly free and have all matter that fill the
+three generations of $27$-plet representations of $E_6$ survive down to
+low energies.  Such models are often referred to in the literature as
+$E_6$ inspired, and we will adopt this here.
 
@@
 
-To ensure anomaly cancellation in these cases the full matter content
-from three generations of $27$-plets should survive to low energies.
-the low energy matter content would then be extended to, \be
+$U(1)$ and $E_6$ inspired extensions of the MSSM have been studied
+very widely in the literature \cite{Gunion:1989we, Gunion:1992hs,
+  Binetruy:1985xm, Ellis:1986yg, Ibanez:1986si, Gunion:1986ky,
+  Haber:1986gz, Baer:1987eb, Gunion:1987jd, Grifols:1986vr,
+  Ellis:1986ip, Morris:1987fm, Drees:1987tp, Ma:1995xk,
+  Suematsu:1997tv, Suematsu:1997qt, Suematsu:1997au, Keith:1996fv,
+  Keith:1997zb, Gherghetta:1996yr, Demir:1998dk, Langacker:1998tc,
+  Hambye:2000bn, Ma:2000jf} (or for reviews see
+\cite{Hewett:1988xc,Langacker:2008yv}).  There has also been a lot of
+work recently including investigations of the neutralino sector
+\cite{Hesselbach:2001ri, Barger:2005hb, Choi:2006fz,
+  Barger:2007nv};the relic abundance of dark matter
+\cite{Kalinowski:2008iq}; GUT scale family symmetries which can
+explain the hierarchy of masses in the fermion sector and their
+associated mixings \cite{Stech:2008wd}; neurtrino physics
+\cite{Kang:2004ix}; explanations of the matter-anti-matter asymmetry
+of the universe though EW baryogensis or leptogensis
+\cite{Hambye:2000bn,Ma:2000jf,Kang:2004pp}; dipole moments
+\cite{GutierrezRodriguez:2006hb}; anomaly mediated SUSY breaking with
+D-term contributions \cite{Asano:2008ju} and the (extended) Higgs
+sectors \cite{Daikoku:2000ep,Ham:2008xf}.
+
+Here we will focus most on the special case where the gauge symmetry
+is $U()_N$,under which the right handed neutrino remains
+interaction-less. This is the case in the the exceptional
+supersymmtric standard models (E$_6$SSM)
+\cite{King:2005jy,King:2005my,Athron:2010zz}, and closely-related
+variants\cite{Howl:2007zi, Braam:2009fi, Braam:2010sy, Hall:2011zq,
+  Nevzorov:2012hs, Athron:2014pua}.  Since the right handed neutrino
+has no gauge symmetry protecting it's mass from becoming extremely
+heavy such models may explain the tiny observed masses of neutrinos
+via the see-saw mechanism and the baryon asymmetry in the universe via
+leptogenesis \cite{Hambye:2000bn,King:2008qb, King:2008gw}.  Recently
+it has also been studied in the context of electroweak baryogenesis
+\cite{Chao:2014hya}.
+
+The gauge coupling running in the E$_6$SSM at the two-loop level leads
+to unification more precisely than in the MSSM \cite{King:2007uj} or
+in slightly modified scenarios two-step unification can take place
+\cite{Howl:2007hq,Howl:2007zi}. If the exotic particles are light in
+these models this can open up non-standard decays of the SM--like
+Higgs boson \cite{Hall:2010ix,Nevzorov:2013tta,Athron:2014pua}. The
+correct relic abundance could be obtained entirely through an almost
+decoupled ``inert'' neutralino sector \cite{Hall:2009aj}.  However
+this is no longer phenomenologically viable due to limits from direct
+detection of dark matter
+\cite{2011PhRvL.107m1302A,2012PhRvL.109r1301A, Akerib:2013tjd} and due
+to a significant suppression of the decay of the lightest Higgs boson
+into SM states, due to a new channel into inert singlinos opening up.
+
+There are still several remaining options. One may specialize to
+scenarios known as the EZSSM \cite{Hall:2011zq} where the inert
+singlinos, which cause these problems are entirely decoupled and the
+relic abundance is fitted with a bino-like candidate with a novel
+mechanism involving back-scattering into a Heavier inert
+Higgsino. Another well motivated scenario admits two possible dark
+matter candidates \cite{Nevzorov:2012hs}, where one will be an inert
+singlino and the other will have a similar composition to MSSM
+neutralinos. The simplest phenomenologically viable solution in that
+case is to make the singlinos extremely light hot dark matter
+candidate and explains almost all the relic abundance density with
+
+The impact of gauge kinetic mixing in the case where both of the extra
+U(1)'s appearing from the breakdown of E$_6$ are present at low energy
+was studied in \cite{Rizzo:2012rf}.  The E$_6$SSM was also included in
+a studies looking at how first or second generation sfermion masses
+can be used to constrain the GUT scale parameters \cite{Miller:2012vn}
+and the renormalization of VEVs \cite{Sperling:2013eva,
+  Sperling:2013xqa}.  The particle spectrum and collider signatures of
+constrained version of the E$_6$SSM have been studied in a series of
+papers,
+\cite{Athron:2009ue,Athron:2009bs,Athron:2011wu,Athron:2012sq}. The
+threshold corrections to the $\overline{DR}$ gauge and Yukawa
+couplings in the E$_6$SSM were calculated and the numerical impact in
+the constrained version examined \cite{Athron:2012pw}.
+%%%%%%%%%%%%%%%%%%---inserted from introduction---%%%%%%%%%%%%%%%%5%%
+
+With three generations of matter $27$-plet representations of $E_6$
+surviving to low energies, the low energy matter content includes, \be
 (\hat{Q}_i,\,\hat{u}^c_i,\,\hat{d}^c_i,\,\hat{L}_i,\,\hat{e}^c_i)

### 2015-01-20 paper/e6ssm-tuning-paper.tex
More foxes of typos, rephrasings and soem significant edit of conclusions section.

@@
 
-In this paper we will examine this source of fine tuning in more
+However in this study we will examine this source of fine tuning in more
 detail by considering low energy constructions where the usual fine
@@
 the parameter $p$. The overall fine tuning is then taken to be $\Delta
-= \underset{i}{\max}\,\{\Delta_{p_i}\}$.\\ \\
+= \underset{i}{\max}\,\{\Delta_{p_i}\}$.\\
 
@@
 more fine tuning.  However for a low value of the UV scale this tuning
-is not so severe unless the stops are very heavy, and a 125 geV Higgs
+is not so severe unless the stops are very heavy, and a 125 GeV Higgs
 can be obtained without much tuning in this unrealistic case where we
@@
 $M_{Z^\prime}=4.5$ TeV, which should be in reach in run II at the LHC
-and then compare the fine tuning calculated in each case to the tuning
-in the MSSM.  For this, we have performed a large six dimensional
-parameter space scan in both the MSSM and E$_6$SSM, varying those
-parameters most relevant for the fine tuning and the Higgs mass.
-Therefore the set of parameters which we vary includes $\mu$, $B$ and
-$\tan \beta$ for the MSSM, and $\lambda$, $A_\lambda$ and $\tan
-\beta$, for the E$_6$SSM, which appear at tree level in the EWSB
-conditions of the models. While the contribution from large stop
-masses to the fine tuning is small for such a low cut-off scale, the
-stop contributions to the effective potential can play a significant
-role in reducing the fine tuning.  For this reason it is still
-important to properly treat the tuning associated with stop
-contributions to the one-loop effective potential, and so we also scan
-over the soft masses $m_{Q_3}^2$, $m_{u_3}^2$ and the stop mixing
-$A_t$.  The relevant parameters and ranges that were scanned over are
-summarised in Table \ref{tab:scanranges}. With the exception of the
-stop mixing $A_t$ and the soft trilinear $A_\lambda$, which are
-logarithmically scanned, all parameters are linearly scanned.  In
-addition to this we also repeat each scan for three different values
-of $M_2$ to allow more variation in the chargino masses.
+\cite{}[CITE PLEASE] and then compare the fine tuning calculated in
+each case to the tuning in the MSSM.  For this, we have performed a
+large six dimensional parameter space scan in both the MSSM and
+E$_6$SSM, varying those parameters most relevant for the fine tuning
+and the Higgs mass.  Therefore the set of parameters which we vary
+includes $\mu$, $B$ and $\tan \beta$ for the MSSM, and $\lambda$,
+$A_\lambda$ and $\tan \beta$, for the E$_6$SSM, which appear at tree
+level in the EWSB conditions of the models. While the RGE contribution
+from large stop masses to the fine tuning is small for such a low
+cut-off scale, the stop contributions to the effective potential can
+play a significant role in reducing the fine tuning [WE SHOULD DISCUSS
+  THIS].  For this reason it is still important to properly treat the
+tuning associated with stop contributions to the one-loop effective
+potential, and so we also scan over the soft masses $m_{Q_3}^2$,
+$m_{u_3}^2$ and the stop mixing $A_t$.  The relevant parameters and
+ranges that were scanned over are summarised in Table
+\ref{tab:scanranges}. With the exception of the stop mixing $A_t$ and
+the soft trilinear $A_\lambda$, which are logarithmically scanned, all
+parameters are linearly scanned.  In addition to this we also repeat
+each scan for three different values of $M_2$ to allow more variation
+in the chargino masses.
 
@@
 
-Nonetheless the MSSM the impact of chargino limit is shown in
-Fig.~\ref{Fig:chargino-plot}.  There we see that if the the full
-  parameter space with $m_{\chi^\pm} < 700$ GeV was excluded the
-  impact would be to make the tuning in the MSSM with a $20$ TeV
-  cutoff slightly worse than that of the E$_6$SSM with the same cutoff
-  and a $Z^\prime$ mass just larger than current limits.  would be
-  similar to that can also be attcked more directly by looking at
-  chargino mass limits as this rasies $\mu$ directly.  In the
-  E$_6$SSM, while raising the chargino limit can have the same impact
-  in principle, due to current limits on the $Z^\prime$ mass already
+Nonetheless the MSSM the impact of potential chargino mass limits is
+shown in Fig.~\ref{Fig:chargino-plot}.  There we see that if the the
+full parameter space with $m_{\chi^\pm} < 700$ GeV was excluded the
+impact would be to make the tuning in the MSSM with a $20$ TeV cutoff
+slightly worse than that of the E$_6$SSM with the same cutoff and a
+$Z^\prime$ mass just larger than current limits. In the E$_6$SSM,
+while raising the chargino limit can have the same impact in
+principle, due to current limits on the $Z^\prime$ mass already
 imposing a significant degree of tuning, chargino masses do not make
@@
 mass in the same way as happens in the other models and explaining why
-% DH:: I strongly suspect that they are invalid - but running scan
-% to check this currently
-the heavier Higgs values are less well populated [can't be obtained? -
-are we sure those scattered points are valid?]  than in the other
-models.  Therefore the fine tuining behaviour in this model is closer
-to that of the MSSM, though the LHC can still constrain the most
-natural scenarions from just placing tougher limits on the $Z^\prime$
-mass.
+heavier Higgs values in this model can't be obtained.  Therefore the fine
+tuning behaviour in this model is closer to that of the MSSM, though
+the LHC can still constrain the most natural scenarions from just
+placing tougher limits on the $Z^\prime$ mass.
 
@@
 To further illustrate this point we looked at how the tuning varies
-with $M_X$ for low tuning benchmarks in the MSSM and E6SSM. These
+with $M_X$ for low tuning benchmarks in the MSSM and E$_6$SSM. These
 benchmarks are defined in table \ref{} and the results are shown in
@@
 not amongst the lowest tuned points, since at that scale the tree
-level tuning from $M_{Z^\prime}$ dominates.  The reduction in $M_3$
-means that $\Delta_{M_3}$ is substantially lower and only becomes the
-dominant tuning very close to the GUT scale, giving a tuning at
-$10^{16}$ GeV of $\approx 900$, which is below that of the other two
-benchmark points.  Since large mixing was also used to reduce allow
-lighter stops, we see initially a large contribution from
-$\Delta_{A_t}$ as we did in the MSSM benchmark.
-[Last thing that needs to be explained - why do $\Delta_{M_3}$ and $\Delta_{m_{H_u}^2}$ start to decrease at large $M_X$.
-I'm guessing something funny to do with their values and also  $m_{Q}^2$ and $M_3$ at the highscales.
-but i need to see the numbers to know.]
+level tuning from $M_{Z^\prime}$ dominates.  However the reduction in
+$M_3$ means that $\Delta_{M_3}$ is substantially lower and only
+becomes the dominant tuning very close to the GUT scale, giving a
+tuning at $10^{16}$ GeV of $\approx 900$, which is below that of the
+other two benchmark points.  Since large mixing was also used to
+reduce allow lighter stops, we see initially a large contribution from
+$\Delta_{A_t}$ as we did in the MSSM benchmark.  [Last thing that
+  needs to be explained - why do $\Delta_{M_3}$ and
+  $\Delta_{m_{H_u}^2}$ start to decrease at large $M_X$.  I'm guessing
+  something funny to do with their values and also $m_{Q}^2$ and $M_3$
+  at the highscales.  but i need to see the numbers to know.]
 
@@
 GeV \cite{}, which already introduced significant tuning for
-constrained models,and then the LHC measured the Higgs to be around
-$125$ GeV, since heavy stops are required to raised the lightest
-Higgs mass above it's tree level bound.
+constrained models, since heavy stops are required to raised the
+lightest Higgs mass above it's tree level bound. Recently this problem
+got much worse since the LHC measured the Higgs to be around $125$
+GeV.
 
@@
 the most conservative limits one can place on naturalness on these
-models, the tuning in the E$_6$SSM is worse.  However if the chargino
-limits blah blah blah then the situation in the two models would be
-the same.
-
-This should also be contrasted with what happens as we raise the
-cutoff scale.  We showed that when the cutoff reaches $M_X =
-[insert]$ the tuning of the MSSM becomes larger than that of the
-E$_6$SSM.  Therefore the conclusion is not that one model is less
-tuned than another, but rather that the answer depends on what
-assumptions are made about the SUSY breaking.
-
-Finally we also looked at the tuning in different $U(1)$ extensions for
+models, the tuning in the E$_6$SSM is worse.  However if there are no
+charginos below $700$ GeV then the situation in the two models would
+be the same.
+
+This should also be contrasted with what happens as we raise the high
+scale boundary, $M_X$.  We showed that for benchmark points that which
+one is more tuned depends very strongly on $M_X$.  The E$_6$SSM tuning
+is sufficiently complicated by the interplay of tehse different
+sources of tesnion in the EWSB conditions that a small reduction in
+fine tuning can even occur for a moderate increase in $M_X$.  However
+as $M_X$ increases towards the scale where the gauge couplings unify,
+the familiar tunings do dominate, though with tunings from the Gluino
+mass appearing to be more significant relative to those from soft
+scalar masses.
+
+We also looked at the tuning in different $U(1)$ extensions for
 fixed $\tan \beta = 10$.  We found that in all cases the fine tuning

### 2015-01-21 fs-spectrum/models/lowE6SSM/lowE6SSM_two_scale_susy_scale_constraint.cpp
Modified SUSY scale constraint to correctly select for stop masses

@@ -194,10 +194,14 @@ void lowE6SSM_susy_scale_constraint<Two_scale>::initialize()
 
 void lowE6SSM_susy_scale_constraint<Two_scale>::update_scale()
 {
+   const auto ZU = MODELPARAMETER(ZU);
    const auto MSu = MODELPARAMETER(MSu);
 
-   scale = Sqrt(MSu(0)*MSu(5));
-
+   scale = Sqrt(Power(MSu(0),Sqr(Abs(ZU(0,2))) + Sqr(Abs(ZU(0,5))))*Power(MSu(1
+      ),Sqr(Abs(ZU(1,2))) + Sqr(Abs(ZU(1,5))))*Power(MSu(2),Sqr(Abs(ZU(2,2))) +
+      Sqr(Abs(ZU(2,5))))*Power(MSu(3),Sqr(Abs(ZU(3,2))) + Sqr(Abs(ZU(3,5))))*Power
+      (MSu(4),Sqr(Abs(ZU(4,2))) + Sqr(Abs(ZU(4,5))))*Power(MSu(5),Sqr(Abs(ZU(5,2))
+      ) + Sqr(Abs(ZU(5,5)))));
 
 }
 

### 2015-01-21 paper/e6ssm-tuning-paper.tex
Added plots with thicker lines and larger labels to the paper, labels probably still have to be a bit bigger to be legible

@@
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_mssm_cutoff_scan_3_points_tuning_plot.png}} 
+\includegraphics{e6ssm_mssm_cutoff_scan_all_benchmark_points_tuning_vs_cutoff.png}} 
 \resizebox{!}{5.5cm}{%
@@
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}
+\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM1_all_tuning_data.png}}
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_mssm_mixing_small_M3_all_tuning_data.png}}%%
+\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM2_all_tuning_data.png}}%%
 \caption{{\it Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in (?).

### 2015-01-21 paper/e6ssm-tuning-paper.tex
Added part of the table for the benchmark parameter values

@@
 with $M_X$ for low tuning benchmarks in the MSSM and E$_6$SSM. These
-benchmarks are defined in table \ref{} and the results are shown in
+benchmarks are defined in Table \ref{tab:benchmarks} and the results are shown in
 Fig.~\ref{Fig:BMs-varyMX}. Since the behaviour is quite complicated we
@@
 differences in the tuning between the two models.
+
+\begin{table}[h]
+\centering
+\begin{ruledtabular}
+\begin{tabular}{cccc}
+& MSSM & E$_6$SSM BM1 & E$_6$SSM BM2 \\
+\hline
+$\tan\beta(M_Z)$ & 10 & 10 & 10 \\
+$s(M_{\mathrm{SUSY}})$ [GeV] & $-$ & 6700 & 6700 \\
+$\mu_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 689.7 & 1093.3 & -1093.3 \\
+$B_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 345.7 & 3792.7 & -3792.7 \\
+$A_t(M_{\mathrm{SUSY}})$ [GeV] & -3335.7 & -1100 & -3335.7 \\
+$m_{Q3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.45379310\times 10^6$ & $4.49655\times 10^5$ & $6.5\times 10^5$ \\
+$m_{u3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4\times 10^6$ & $5.86207\times 10^5$ & $4.5\times 10^5$ \\
+$M_1(M_{\mathrm{SUSY}})$ [GeV] & 300 & 300 & 300 \\
+$M_2(M_{\mathrm{SUSY}})$ [GeV] & 2000 & 1050 & 2000 \\
+$M_3(M_{\mathrm{SUSY}})$ [GeV] & 2000 & 2000 & 1200 \\
+$M_1^\prime(M_{\mathrm{SUSY}})$ [GeV] & $-$ & 300 & 300 \\
+\hline
+$m_{h_1}$ [GeV] & 124.3 & 125.0 & 124.9 \\
+$m_{\tilde{g}}$ [GeV] & & 2290.0 & 1453.8\\
+\hline
+$\Delta(M_X=20\textrm{ TeV})$ & 157.3 & 165.3 & 228.5 \\
+$\Delta(M_X=10^{16}\textrm{ GeV})$ & 1089.0 & 1722.3 & 917.6
+\end{tabular}
+\end{ruledtabular}
+\caption{Parameters and masses for the MSSM point and the E$_6$SSM benchmark points 
+BM1 and BM2 for which the fine tuning as a function of cutoff scale is studied. For the
+E$_6$SSM benchmarks we define $\mu_{\mathrm{eff}}\equiv \lambda s/\sqrt{2}$ and
+$B_{\mathrm{eff}}=A_\lambda$.}
+\label{tab:benchmarks}
+\end{table}
 
@@
 \includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM2_all_tuning_data.png}}%%
-\caption{{\it Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in (?).
+\caption{{\it Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.
 {\it Top right panel:}  Individual sensitivites of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.

### 2015-01-21 fs-spectrum/models/lowE6SSM/cutoff_scan_lowE6SSM.cpp
Swapped M3 to 2 TeV, i.e. BM1 value

@@ -809,7 +809,7 @@ lowE6SSM_input_parameters get_default_inputs(double theta, Input_set point, bool
          input.mHpbar2Input = Sqr(5000.); // GeV^2
          
          input.MassBInput = 300.; // GeV
-         input.MassGInput = 1200.0;//2000.; // GeV
+         input.MassGInput = 2000.;//1200.0;//2000.; // GeV
          input.MassBpInput = 300.; // GeV
          break;
       }

### 2015-01-21 paper/e6ssm-tuning-paper.tex
Added more details on parameters to the table

--- 2015-01-21 paper/e6ssm-tuning-paper.tex
@@
 differences in the tuning between the two models.
+
+\begin{table}[h]
+\centering
+\begin{ruledtabular}
+\begin{tabular}{cccc}
+& MSSM & E$_6$SSM BM1 & E$_6$SSM BM2 \\
+\hline
+$\tan\beta(M_Z)$ & 10 & 10 & 10 \\
+$s(M_{\mathrm{SUSY}})$ [GeV] & $-$ & 6700 & 6700 \\
+$\kappa_{1,2,3}(M_{\mathrm{SUSY}})$ & $-$ & 0.6 & 0.6 \\
+$\lambda_{1,2}(M_{\mathrm{SUSY}})$ & $-$ & 0.2 & 0.2 \\
+$\mu_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 689.7 & 1093.3 & -1093.3 \\
+$B_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 345.7 & 3792.7 & -3792.7 \\
+$A_t(M_{\mathrm{SUSY}})$ [GeV] & -3335.7 & -1100 & -3335.7 \\
+$A_b(M_{\mathrm{SUSY}}), A_\tau (M_{\mathrm{SUSY}})$ [GeV] & 0 & 0 & 0 \\
+$m_{Q3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.45379310\times 10^6$ & $4.49655\times 10^5$ & $6.5\times 10^5$ \\
+$m_{u3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4\times 10^6$ & $5.86207\times 10^5$ & $4.5\times 10^5$ \\
+$M_1(M_{\mathrm{SUSY}})$ [GeV] & 300 & 300 & 300 \\
+$M_2(M_{\mathrm{SUSY}})$ [GeV] & 2000 & 1050 & 2000 \\
+$M_3(M_{\mathrm{SUSY}})$ [GeV] & 2000 & 2000 & 1200 \\
+$M_1^\prime(M_{\mathrm{SUSY}})$ [GeV] & $-$ & 300 & 300 \\
+\hline
+$M_{Z^\prime}$ [GeV] & $-$ & 2473.2 & 2473.1 \\
+$m_{h_1}$ [GeV] & 124.3 & 125.0 & 124.9 \\
+$m_{\tilde{t}_1}$ [GeV] & 1942.1 & 993.8 & 839.6 \\
+$m_{\tilde{t}_2}$ [GeV] & 2220.1 & 1174.8 & 1285.2 \\
+$m_{\tilde{g}}$ [GeV] & 2259.8 & 2290.0 & 1453.8\\
+\hline
+$\Delta(M_X=20\textrm{ TeV})$ & 157.3 & 165.3 & 228.5 \\
+$\Delta(M_X=10^{16}\textrm{ GeV})$ & 1089.0 & 1722.3 & 917.6
+\end{tabular}
+\end{ruledtabular}
+\caption{Parameters and masses for the MSSM point and the E$_6$SSM benchmark points 
+BM1 and BM2 for which the fine tuning as a function of cutoff scale is studied. For the
+E$_6$SSM benchmarks we define $\mu_{\mathrm{eff}}\equiv \lambda s/\sqrt{2}$ and
+$B_{\mathrm{eff}}=A_\lambda$.
+All other (diagonal) soft scalar squared masses not shown above are set to $2.5\times 10^7$ GeV$^2$, and all soft trilinears are set to zero.
+In the E$_6$SSM, we additionally set $\mu^\prime=5000$ GeV and $B\mu^\prime=5000$ GeV$^2$.}
+\label{tab:benchmarks}
+\end{table}
 

### 2015-01-21 paper/e6ssm-tuning-paper.tex
Commented out the placeholder abstract so that we don't forget to write a proper one

@@
 \begin{abstract}
+The abstract.
 % Copied SUSY2014 abstract as placeholder
-With the discovery of a 125 GeV Standard Model (SM) like Higgs boson
-and rising lower bounds on the masses of superpartners, minimal models
-of low energy supersymmetry (SUSY) appear to be increasingly fine
-tuned. In the Minimal Supersymmetric Standard Model (MSSM) large stop
-masses, needed to obtain the observed Higgs mass, give a significant
-contribution to fine tuning. $U(1)$ extensions of the MSSM that solve
-the $\mu$-problem have new F- and D-term contributions to the Higgs
-mass, allowing a 125 GeV Higgs with lighter stops and so alleviating
-the associated fine tuning. However, it was recently demonstrated,
-within a constrained version of the Exceptional Supersymmetric
-Standard Model (E$_6$SSM) defined at the Grand Unification (GUT)
-scale, that the presence of a massive $Z'$ boson introduces a
-substantial new source of tuning in these theories at tree level. Here
-we consider the impact of this tuning when we remove the fine tuning
-that depends on assumptions about the SUSY breaking scale, by setting
-the SUSY breaking parameters at low energies. We find that the
-existing experimental bounds on the $Z'$ mass impose an effective
-lower bound on the fine tuning, which does not depend on assumptions
-about SUSY breaking.  We compare our results against the tuning in the
-MSSM with the SUSY breaking terms also defined at low energies.
+% With the discovery of a 125 GeV Standard Model (SM) like Higgs boson
+% and rising lower bounds on the masses of superpartners, minimal models
+% of low energy supersymmetry (SUSY) appear to be increasingly fine
+% tuned. In the Minimal Supersymmetric Standard Model (MSSM) large stop
+% masses, needed to obtain the observed Higgs mass, give a significant
+% contribution to fine tuning. $U(1)$ extensions of the MSSM that solve
+% the $\mu$-problem have new F- and D-term contributions to the Higgs
+% mass, allowing a 125 GeV Higgs with lighter stops and so alleviating
+% the associated fine tuning. However, it was recently demonstrated,
+% within a constrained version of the Exceptional Supersymmetric
+% Standard Model (E$_6$SSM) defined at the Grand Unification (GUT)
+% scale, that the presence of a massive $Z'$ boson introduces a
+% substantial new source of tuning in these theories at tree level. Here
+% we consider the impact of this tuning when we remove the fine tuning
+% that depends on assumptions about the SUSY breaking scale, by setting
+% the SUSY breaking parameters at low energies. We find that the
+% existing experimental bounds on the $Z'$ mass impose an effective
+% lower bound on the fine tuning, which does not depend on assumptions
+% about SUSY breaking.  We compare our results against the tuning in the
+% MSSM with the SUSY breaking terms also defined at low energies.
 

### 2015-01-21 paper/e6ssm-tuning-paper.tex
Fixed some typos

@@
 The discovery of an approximately 125 GeV Higgs
-\cite{Aad:2012tfa,Chatrchyan:2012ufa} at the large hadron collider
+\cite{Aad:2012tfa,Chatrchyan:2012ufa} at the Large Hadron Collider
 (LHC) has interesting implications for physics beyond the standard
@@
 explain the hierarchy of masses in the fermion sector and their
-associated mixings \cite{Stech:2008wd}; neurtrino physics
+associated mixings \cite{Stech:2008wd}; neutrino physics
 \cite{Kang:2004ix}; explanations of the matter-anti-matter asymmetry
@@
 interaction-less. This is the case in the the exceptional
-supersymmtric standard models (E$_6$SSM)
+supersymmetric standard models (E$_6$SSM)
 \cite{King:2005jy,King:2005my,Athron:2010zz}, and closely-related
@@
 contributions. To scan over the MSSM parameter space, the equivalent
-MSSM fine tuning expressions were implemented into a modifed version
+MSSM fine tuning expressions were implemented into a modified version
 of SOFTSUSY 3.3.10 \cite{Allanach:2001kg,Allanach:2013kza}. For
@@
 from the $Z^\prime$ mass appears already at tree level and is
-therefore not heavily suprressed when the cutoff scale is low. We find
+therefore not heavily suppressed when the cutoff scale is low. We find
 that in the E$_6$SSM current limits on the mass of the $Z^\prime$
@@
 
-This demopnstrates two important points about these $U(1)$
+This demonstrates two important points about these $U(1)$
 extensions. Firstly that limits on the $Z^\prime$ mass play an
@@
 imposing a significant degree of tuning, chargino masses do not make
-much of a noticable change.
+much of a noticeable change.
 
@@
 tuning from the $U(1)_I$ symmetry.  This is a result of the $H_u$
-charge associated with $U(1)_I$ vansihing, which means that the
+charge associated with $U(1)_I$ vanishing, which means that the
 D-terms to the lightest Higgs which is predominantly $H_u$ at large
@@
 tuning behaviour in this model is closer to that of the MSSM, though
-the LHC can still constrain the most natural scenarions from just
+the LHC can still constrain the most natural scenarios from just
 placing tougher limits on the $Z^\prime$ mass.
@@
 by some SUSY breaking mechanism.  Indeed in \cite{Athron:2013ipa} a
-constrained version of the E$_6$SSM, with the highscale boundary at
+constrained version of the E$_6$SSM, with the high scale boundary at
 the GUT scale, is considered and there the cE$_6$SSM was found to be
 less tuned than the cMSSM. Since a 125 GeV Higgs can be achieved in
-the E$_6$SSM with ligher stops, then if the cutoff is large, the
+the E$_6$SSM with lighter stops, then if the cutoff is large, the
 larger stop masses of the MSSM can make that model more fine tuned due
@@
 \caption{{\it Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.
-{\it Top right panel:}  Individual sensitivites of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.
-{\it Bottom left panel:} Individual sensitivites of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.
-{\it Bottom right panel:} Individual sensitivites of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.
+{\it Top right panel:}  Individual sensitivities of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.
+{\it Bottom left panel:} Individual sensitivities of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.
+{\it Bottom right panel:} Individual sensitivities of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.
 }
@@
 but remains lower than that of the other points, until $M_X \approx
-10^{11}$ GeV.  Eventuially the $\Delta_{M_3}$ sensitivity leads to
+10^{11}$ GeV.  Eventually the $\Delta_{M_3}$ sensitivity leads to
 this point being the most fine tuned of the three shown in
@@
 
-Interstingly other sensitivities are suppressed by this effect since
+Interestingly other sensitivities are suppressed by this effect since
 at the same time larger $M_3$ at higher scales reduces the soft squark
@@
 still do lead to $\Delta_{m_{H_u}^2}$ increasing with the cutoff
-through the usual mecahnism \footnote{Wherein $m_{H_u}^2(M_{SUSY})$
+through the usual mechanism \footnote{Wherein $m_{H_u}^2(M_{SUSY})$
   receives a positive contribution to it's mass from $m_{H_u}^2(M_X)$
@@
   tuning. In this case $m_{H_u}^2(M_{SUSY})$ is held fixed so as the
-  cutoff increases the values of these softmasses at $M_X$ will be
+  cutoff increases the values of these soft masses at $M_X$ will be
   larger and there we be a bigger cancellation between them,
@@
   something funny to do with their values and also $m_{Q}^2$ and $M_3$
-  at the highscales.  but i need to see the numbers to know.]
+  at the high scales.  but i need to see the numbers to know.]
 
@@
 one is more tuned depends very strongly on $M_X$.  The E$_6$SSM tuning
-is sufficiently complicated by the interplay of tehse different
-sources of tesnion in the EWSB conditions that a small reduction in
+is sufficiently complicated by the interplay of these different
+sources of tension in the EWSB conditions that a small reduction in
 fine tuning can even occur for a moderate increase in $M_X$.  However

### 2015-01-21 paper/e6ssm-tuning-paper.tex
Added reference for Z' reach of LHC run II
added title/abstract options in comments.
added missing 'we'

@@
 The abstract.
-% Copied SUSY2014 abstract as placeholder
-% With the discovery of a 125 GeV Standard Model (SM) like Higgs boson
-% and rising lower bounds on the masses of superpartners, minimal models
-% of low energy supersymmetry (SUSY) appear to be increasingly fine
-% tuned. In the Minimal Supersymmetric Standard Model (MSSM) large stop
-% masses, needed to obtain the observed Higgs mass, give a significant
-% contribution to fine tuning. $U(1)$ extensions of the MSSM that solve
-% the $\mu$-problem have new F- and D-term contributions to the Higgs
-% mass, allowing a 125 GeV Higgs with lighter stops and so alleviating
-% the associated fine tuning. However, it was recently demonstrated,
-% within a constrained version of the Exceptional Supersymmetric
-% Standard Model (E$_6$SSM) defined at the Grand Unification (GUT)
-% scale, that the presence of a massive $Z'$ boson introduces a
-% substantial new source of tuning in these theories at tree level. Here
-% we consider the impact of this tuning when we remove the fine tuning
-% that depends on assumptions about the SUSY breaking scale, by setting
-% the SUSY breaking parameters at low energies. We find that the
-% existing experimental bounds on the $Z'$ mass impose an effective
-% lower bound on the fine tuning, which does not depend on assumptions
-% about SUSY breaking.  We compare our results against the tuning in the
-% MSSM with the SUSY breaking terms also defined at low energies.
+%%Original abstract
+% Copied SUSY2014 abstract.
+%% With the discovery of a 125 GeV Standard Model (SM) like Higgs boson
+%% and rising lower bounds on the masses of superpartners, minimal models
+%% of low energy supersymmetry (SUSY) appear to be increasingly fine
+%% tuned. In the Minimal Supersymmetric Standard Model (MSSM) large stop
+%% masses, needed to obtain the observed Higgs mass, give a significant
+%% contribution to fine tuning. $U(1)$ extensions of the MSSM that solve
+%% the $\mu$-problem have new F- and D-term contributions to the Higgs
+%% mass, allowing a 125 GeV Higgs with lighter stops and so alleviating
+%% the associated fine tuning. However, it was recently demonstrated,
+%% within a constrained version of the Exceptional Supersymmetric
+%% Standard Model (E$_6$SSM) defined at the Grand Unification (GUT)
+%% scale, that the presence of a massive $Z'$ boson introduces a
+%% substantial new source of tuning in these theories at tree level. Here
+%% we consider the impact of this tuning when we remove the fine tuning
+%% that depends on assumptions about the SUSY breaking scale, by setting
+%% the SUSY breaking parameters at low energies. We find that the
+%% existing experimental bounds on the $Z'$ mass impose an effective
+%% lower bound on the fine tuning, which does not depend on assumptions
+%% about SUSY breaking.  We compare our results against the tuning in the
+%% MSSM with the SUSY breaking terms also defined at low energies.
+
+%%Alternative 1
+%% Alt title: Probing natural SUSY in the most general way in the MSSM and U(1) extensions.
+
+%% The discovery of a 125 GeV Standard Model (SM) like Higgs boson and
+%% rising lower bounds on the masses of superpartners, have lead to
+%% concerns that supersymmetric models are now fine tuned.  In the
+%% Minimal Supersymmetric Standard Model (MSSM) large stop masses,
+%% required for a $125$ GeV Higgs, also feed into the EWSB conditions
+%% through renormalisation group equations forcing one to fine tune these
+%% parameters to obtain the correct electroweak vacuum expectation
+%% value. Nonetheless this fine tuning depends crucially on our
+%% assumptions about the SUSY breaking scale.  Here we consider what fine
+%% tuning may appear in supersymmetry at tree level, so that it is not so
+%% dependent on assumptions about the SUSY breaking mechanism.  We focus
+%% on U(1) extensions since these provide the most elegant solution to
+%% the $\mu$-problem, which is also a naturalness issue, but we also
+%% compare to the simplest SUSY model, the MSSM. In U(1) extensions anew
+%% F- and D-term contributions raise the Higgs mass, allowing a $125$ GeV
+%% Higgs with lighter stops which can alleviate this stop fine tuning in
+%% models with SUSY breaking fixed at the high scale. However the
+%% presence of a massive $Z'$ boson introduces a substantial new source
+%% of tuning in these theories at tree level.  By choosing a low scale
+%% boundary condition for where the SUSY breaking parameters are set we
+%% compare how this tree level tuning compares to that of the MSSM where
+%% chargino mass limits are the best way to probe tree level fine tuning,
+%% by raising $\mu$ directly.  We find that the $Z^\tprime$ tuning places
+%% more stringent limits on the fine tuning in most of the $U(1)$
+%% extensions and that increasing $Z^\prime$ limits will challenge the
+%% most natural scenarios of these models.
+
+%% Alternative 2
+
+%% Alt title: Z' mass limits and the naturalness of supersymmetry
+
+%% The discovery of a 125 GeV Higgs boson and rising lower bounds on the
+%% masses of superpartners, have lead to concerns that supersymmetric
+%% models are now fine tuned.  Large stop masses, required for a $125$
+%% GeV Higgs, feed into the EWSB conditions through renormalisation group
+%% equations forcing one to fine tune these parameters to obtain the
+%% correct electroweak vacuum expectation value.  Nonetheless this fine
+%% tuning depends crucially on our assumptions about the SUSY breaking
+%% scale.  At the same time U(1) extensions provide the most compelling
+%% solution to the $\mu$-problem, which is also a naturalness issue.
+%% These very well motovated supersymmetric models predict a new
+%% $Z^\prime$ boson which could be discovered at the LHC.  like the
+%% superpartners naturalness of the model requires that the $Z^\prime$
+%% boson mass should not be too \far above the TeV scale.  Moreover this
+%% fine tuning appears at the tree level, making it less dependent on a
+%% SUSY breaking mecahnism which has not been fully determnined.  Here we
+%% study this fine tuning for several $U(1)$ supesymmetric extensions of
+%% the standard model and compare it to the situation in the MSSM where
+%% the most direct tree level fine tuning can be probed through chargino
+%% mass limits.  we show that future LHC $Z^\prime$ searches are
+%% extremely important for challenging the most natural scenarios in
+%% these models.
 
@@
 
-While this approach has many merits here will employ the traditional
+While this approach has many merits here we will employ the traditional
 measure of fine tuning because it is both simple to apply and easy to
@@
 $M_{Z^\prime}=4.5$ TeV, which should be in reach in run II at the LHC
-\cite{}[CITE PLEASE] and then compare the fine tuning calculated in
+\cite{Godfrey:2013eta} and then compare the fine tuning calculated in
 each case to the tuning in the MSSM.  For this, we have performed a

### 2015-01-22 fs-spectrum/models/lowE6SSM/cutoff_scan_lowE6SSM.cpp
Small changes to parameter values for benchmark points

@@ -310,7 +310,7 @@ lowE6SSM_input_parameters get_default_inputs(double theta, Input_set point, bool
          input.TKappaInput = Eigen::Matrix<double,3,3>::Zero();
          input.TKappaInput(0,0) = -7.19207879e+02;
          input.TKappaInput(1,1) = -7.19207879e+02;
-         input.TKappaInput(2,2) = -7.19207879e+02;
+         input.TKappaInput(2,2) = 7.19207879e+02; // note sign change
 
          input.TLambda12Input = Eigen::Matrix<double,2,2>::Zero();
          input.TLambda12Input(0,0) = -7.08483859;
@@ -371,7 +371,7 @@ lowE6SSM_input_parameters get_default_inputs(double theta, Input_set point, bool
          input.mHpbar2Input = 3.85796087e+06; // GeV^2
          
          input.MassBInput = 1.73364059e+02; // GeV
-         input.MassGInput = 7.11480225e+02; // GeV
+         input.MassGInput = 1200.0;//7.11480225e+02; // GeV
          input.MassBpInput = 1.75249244e+02; // GeV
 
          break;
@@ -767,12 +767,12 @@ lowE6SSM_input_parameters get_default_inputs(double theta, Input_set point, bool
          input.ml2Input = Eigen::Matrix<double,3,3>::Zero();
          input.ml2Input(0,0) = Sqr(5000.); // GeV^2
          input.ml2Input(1,1) = Sqr(5000.); // GeV^2
-         input.ml2Input(2,2) = Sqr(5000.); // GeV^2
+         input.ml2Input(2,2) = Sqr(9000.); // GeV^2
          
          input.md2Input = Eigen::Matrix<double,3,3>::Zero();
          input.md2Input(0,0) = Sqr(5000.); // GeV^2
          input.md2Input(1,1) = Sqr(5000.); // GeV^2
-         input.md2Input(2,2) = Sqr(5000.); // GeV^2
+         input.md2Input(2,2) = Sqr(9000.); // GeV^2
          
          input.mu2Input = Eigen::Matrix<double,3,3>::Zero();
          input.mu2Input(0,0) = Sqr(5000.); // GeV^2
@@ -781,7 +781,7 @@ lowE6SSM_input_parameters get_default_inputs(double theta, Input_set point, bool
          input.me2Input = Eigen::Matrix<double,3,3>::Zero();
          input.me2Input(0,0) = Sqr(5000.); // GeV^2
          input.me2Input(1,1) = Sqr(5000.); // GeV^2
[…]

### 2015-01-22 fs-spectrum/models/lowE6SSM/full_tuning_scan_lowE6SSM.cpp

@@ -291,21 +291,21 @@ int main()
 
       try {
          input.LambdaxInput = boost::lexical_cast<double>(values[Lambdax_col]);
+         try {
+            input.TLambdaxInput = boost::lexical_cast<double>(values[ALambdax_col]);
+            input.TLambdaxInput *= input.LambdaxInput;
+
+         } catch (const boost::bad_lexical_cast& error) {
+            WARNING("Ignoring invalid input '" + values[ALambdax_col] + "'");
+            continue;
+         }
       } catch (const boost::bad_lexical_cast& error) {
          WARNING("Ignoring invalid input '" + values[Lambdax_col] + "'");
          continue;
       }
 
-      // note different interpretation
       try {
-         input.TLambdaxInput = boost::lexical_cast<double>(values[ALambdax_col]);
-      } catch (const boost::bad_lexical_cast& error) {
-         WARNING("Ignoring invalid input '" + values[ALambdax_col] + "'");
-         continue;
-      }
-
-      try {
-         input.TYuInput(2,2) = boost::lexical_cast<double>(values[AYu22_col]);
+         input.AYuInput(2,2) = boost::lexical_cast<double>(values[AYu22_col]);
       } catch (const boost::bad_lexical_cast& error) {
          WARNING("Ignoring invalid input '" + values[AYu22_col] + "'");
          continue;
@@ -361,8 +361,21 @@ int main()
       double max_tuning = 0;
       bool tuning_problem = false;
       if (!error) {
+
+         // solve ewsb
+         lowE6SSM_ew_derivs ew_derivs(model);
+         
+         double mHd2 = ew_derivs.get_model().get_mHd2();
+         double mHu2 = ew_derivs.get_model().get_mHu2();
+         double ms2 = ew_derivs.get_model().get_ms2();         
+         
+         lowE6SSM<Two_scale> tuning_model(model);
+         tuning_model.set_mHd2(mHd2);
+         tuning_model.set_mHu2(mHu2);
+         tuning_model.set_ms2(ms2);
+
          // calculate fine tuning
-         lowE6SSM_tuning_calculator tuning_calc(model);
+         lowE6SSM_tuning_calculator tuning_calc(tuning_model);
          tuning_calc.set_tuning_scale(Sqrt(model.get_MSu()(0) * model.get_MSu()(1)));
          tuning_calc.set_input_scale(mx);
          tuning_calc.set_tuning_ewsb_loop_order(1);

### 2015-01-22 paper/e6ssm-tuning-paper.tex
removed comment that doens't need further addressing.
changed comment on BM2 to refelect new point..

@@
 
-[We should add some discussion about the $U(1)_I$ and the physics of
-  that model here, since it has the lowest tuning.]
-
 Finally we want to emphasise that while in Fig.~\ref{Fig:e6ssmvsmssm}
@@
 By contrast the tuning for E$_6$SSM BM2 is very different.  This point
-was chosen as it had much lighter stops and a gluino mass that is just
+was chosen as it had much lighter gluino mass that is just
 above the experimental limit of $1.4$ TeV \cite{}.  At $20$ TeV it was
@@
 becomes the dominant tuning very close to the GUT scale, giving a
-tuning at $10^{16}$ GeV of $\approx 900$, which is below that of the
-other two benchmark points.  Since large mixing was also used to
-reduce allow lighter stops, we see initially a large contribution from
-$\Delta_{A_t}$ as we did in the MSSM benchmark.  [Last thing that
-  needs to be explained - why do $\Delta_{M_3}$ and
-  $\Delta_{m_{H_u}^2}$ start to decrease at large $M_X$.  I'm guessing
-  something funny to do with their values and also $m_{Q}^2$ and $M_3$
-  at the high scales.  but i need to see the numbers to know.]
+tuning at $10^{16}$ GeV of $\approx 550$, which is far below that of the
+other two benchmark points.
 

### 2015-01-22 paper/e6ssm-tuning-paper.tex
removed comment.

@@
 cut-off scale, the stop contributions to the effective potential can
-play a significant role in reducing the fine tuning [WE SHOULD DISCUSS
-  THIS].  For this reason it is still important to properly treat the
+play a significant role in reducing the fine tuning.  For this reason it is still important to properly treat the
 tuning associated with stop contributions to the one-loop effective

### 2015-01-23 fs-spectrum/models/lowE6SSM/cutoff_scan_lowE6SSM.cpp
Changed parameter values to bring up squark masses in BM2

@@ -323,52 +323,52 @@ lowE6SSM_input_parameters get_default_inputs(double theta, Input_set point, bool
          input.BMuPrInput = -4.20990207e+05; // GeV^2
          
          input.mq2Input = Eigen::Matrix<double,3,3>::Zero();
-         input.mq2Input(0,0) = 4.93021964e+06; // GeV^2
-         input.mq2Input(1,1) = 4.93017789e+06; // GeV^2
+         input.mq2Input(0,0) = 5.76210034E+06;//4.93021964e+06; // GeV^2
+         input.mq2Input(1,1) = 5.76205345E+06;//4.93017789e+06; // GeV^2
          
          input.ml2Input = Eigen::Matrix<double,3,3>::Zero();
-         input.ml2Input(0,0) = 3.96022681e+06; // GeV^2
-         input.ml2Input(1,1) = 3.96008182e+06; // GeV^2
-         input.ml2Input(2,2) = 3.91708183e+06; // GeV^2
+         input.ml2Input(0,0) = 4.93965102E+06;//3.96022681e+06; // GeV^2
+         input.ml2Input(1,1) = 4.93949052E+06;//3.96008182e+06; // GeV^2
+         input.ml2Input(2,2) = 4.89189756E+06;//3.91708183e+06; // GeV^2
          
          input.md2Input = Eigen::Matrix<double,3,3>::Zero();
-         input.md2Input(0,0) = 5.04926079e+06; // GeV^2
-         input.md2Input(1,1) = 5.04921454e+06; // GeV^2
-         input.md2Input(2,2) = 4.95687546e+06; // GeV^2
+         input.md2Input(0,0) = 5.88363593E+06;//5.04926079e+06; // GeV^2
+         input.md2Input(1,1) = 5.88358594E+06;//5.04921454e+06; // GeV^2
+         input.md2Input(2,2) = 5.78399108E+06;//4.95687546e+06; // GeV^2
          
          input.mu2Input = Eigen::Matrix<double,3,3>::Zero();
-         input.mu2Input(0,0) = 4.63796804e+06; // GeV^2
-         input.mu2Input(1,1) = 4.63792998e+06; // GeV^2
+         input.mu2Input(0,0) = 5.53534602E+06;//4.63796804e+06; // GeV^2
+         input.mu2Input(1,1) = 5.53530132E+06;//4.63792998e+06; // GeV^2
          
          input.me2Input = Eigen::Matrix<double,3,3>::Zero();
[…]

### 2015-01-23 paper/e6ssm-tuning-paper.tex
Added reference for gluino limits, updated table with new benchmark values, added short description of the constrained benchmark

@@
 $s(M_{\mathrm{SUSY}})$ [GeV] & $-$ & 6700 & 6700 \\
-$\kappa_{1,2,3}(M_{\mathrm{SUSY}})$ & $-$ & 0.6 & 0.6 \\
-$\lambda_{1,2}(M_{\mathrm{SUSY}})$ & $-$ & 0.2 & 0.2 \\
-$\mu_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 689.7 & 1093.3 & -1093.3 \\
-$B_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 345.7 & 3792.7 & -3792.7 \\
-$A_t(M_{\mathrm{SUSY}})$ [GeV] & -3335.7 & -1100 & -3335.7 \\
-$A_b(M_{\mathrm{SUSY}}), A_\tau (M_{\mathrm{SUSY}})$ [GeV] & 0 & 0 & 0 \\
-$m_{Q3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.45379310\times 10^6$ & $4.49655\times 10^5$ & $6.5\times 10^5$ \\
-$m_{u3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4\times 10^6$ & $5.86207\times 10^5$ & $4.5\times 10^5$ \\
-$M_1(M_{\mathrm{SUSY}})$ [GeV] & 300 & 300 & 300 \\
-$M_2(M_{\mathrm{SUSY}})$ [GeV] & 2000 & 1050 & 2000 \\
+$\kappa_{1,2,3}(M_{\mathrm{SUSY}})$ & $-$ & 0.6 & 0.52 \\
+$\lambda_{1,2}(M_{\mathrm{SUSY}})$ & $-$ & 0.2 & 0.13 \\
+$\mu_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 689.7 & 1093.3 & 1313.0 \\
+$B_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 345.7 & 3792.7 & 817.8 \\
+$A_t(M_{\mathrm{SUSY}})$ [GeV] & -3335.7 & -1100 & -1103.2 \\
+$m_{Q3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.45\times 10^6$ & $4.50\times 10^5$ & $3.61\times 10^6$ \\
+$m_{u3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4\times 10^6$ & $5.86\times 10^5$ & $2.04\times 10^6$ \\
+$M_1(M_{\mathrm{SUSY}})$ [GeV] & 300 & 300 & 173.4 \\
+$M_2(M_{\mathrm{SUSY}})$ [GeV] & 2000 & 1050 & 281.4 \\
 $M_3(M_{\mathrm{SUSY}})$ [GeV] & 2000 & 2000 & 1200 \\
-$M_1^\prime(M_{\mathrm{SUSY}})$ [GeV] & $-$ & 300 & 300 \\
+$M_1^\prime(M_{\mathrm{SUSY}})$ [GeV] & $-$ & 300 & 175.2 \\
 \hline
-$M_{Z^\prime}$ [GeV] & $-$ & 2473.2 & 2473.1 \\
-$m_{h_1}$ [GeV] & 124.3 & 125.0 & 124.9 \\
-$m_{\tilde{t}_1}$ [GeV] & 1942.1 & 993.8 & 839.6 \\
-$m_{\tilde{t}_2}$ [GeV] & 2220.1 & 1174.8 & 1285.2 \\
-$m_{\tilde{g}}$ [GeV] & 2259.8 & 2290.0 & 1453.8\\
+$M_{Z^\prime}$ [GeV] & $-$ & 2473.2 & 2512.7 \\
+$m_{h_1}$ [GeV] & 124.3 & 125.0 & 126.2 \\
+$m_{\tilde{t}_1}$ [GeV] & 1942.1 & 993.8 & 1665.0 \\
+$m_{\tilde{t}_2}$ [GeV] & 2220.1 & 1174.8 & 2094.4 \\
+$m_{\tilde{g}}$ [GeV] & 2259.8 & 2290.0 & 1407.4\\
 \hline
-$\Delta(M_X=20\textrm{ TeV})$ & 157.3 & 165.3 & 228.5 \\
-$\Delta(M_X=10^{16}\textrm{ GeV})$ & 1089.0 & 1722.3 & 917.6
+$\Delta(M_X=20\textrm{ TeV})$ & 157.3 & 165.3 & 402.1 \\
+$\Delta(M_X=10^{16}\textrm{ GeV})$ & 1089.0 & 1722.3 & 546.7
 \end{tabular}
@@
 \caption{Parameters and masses for the MSSM point and the E$_6$SSM benchmark points 
-BM1 and BM2 for which the fine tuning as a function of cutoff scale is studied. For the
-E$_6$SSM benchmarks we define $\mu_{\mathrm{eff}}\equiv \lambda s/\sqrt{2}$ and
+BM1 and BM2. For the
+E$_6$SSM we define $\mu_{\mathrm{eff}}\equiv \lambda s/\sqrt{2}$ and
 $B_{\mathrm{eff}}=A_\lambda$.
-All other (diagonal) soft scalar squared masses not shown above are set to $2.5\times 10^7$ GeV$^2$, and all soft trilinears are set to zero.
-In the E$_6$SSM, we additionally set $\mu^\prime=5000$ GeV and $B\mu^\prime=5000$ GeV$^2$.}
+In BM1 all other (diagonal) soft scalar squared masses not shown above are set to $(5\mathrm{ TeV})^2$, the soft trilinears $A_b$, $A_\tau=0$, $\mu^\prime=5000$ GeV and $B\mu^\prime=5000$ GeV$^2$.
+In BM2 the parameters not shown above are set to the values obtained by running the cE$_6$SSM point with $m_0=2.2$ TeV, $A_0=500$ GeV, $M_{1/2}=1003$ GeV, $\kappa_{1,2,3}(M_X)=0.1923$, $\lambda(M_X)=0.2646$ to the SUSY scale, and setting $\mu^\prime(M_{\mathrm{SUSY}})=897.9$ GeV and $B\mu^\prime(M_{\mathrm{SUSY}})=-4.2\times10^5$ GeV$^2$.}
 \label{tab:benchmarks}
@@
 was chosen as it had much lighter gluino mass that is just
-above the experimental limit of $1.4$ TeV \cite{}.  At $20$ TeV it was
-not amongst the lowest tuned points, since at that scale the tree
+above the experimental limit of $1.4$ TeV \cite{Aad:2014lra}. 
+At $20$ TeV this benchmark is not amongst the lowest tuned points, since at that scale the tree
 level tuning from $M_{Z^\prime}$ dominates.  However the reduction in
 $M_3$ means that $\Delta_{M_3}$ is substantially lower and only
-becomes the dominant tuning very close to the GUT scale, giving a
-tuning at $10^{16}$ GeV of $\approx 550$, which is far below that of the
+becomes the dominant tuning at a much larger scale of $M_X\gtrsim 10^{12}-10^{13}$ GeV, giving a
+tuning at $10^{16}$ GeV of $\approx 546$, which is far below that of the
 other two benchmark points.
+
+In addition to this, the soft parameters in BM2 follow a pattern similar to that found in the constrained
+model. With the exception of the parameters $m_{Q3}^2$, 
+$m_{u3}^2$, $m_{H_d}^2$, $m_{H_u}^2$, and $M_3$, the values of which are given in Table \ref{tab:benchmarks}, 
+the soft masses at the SUSY scale correspond to the values that result in the cE$_6$SSM with $m_0=2.2$ TeV, 
+$M_{1/2}=1003$ GeV, $A_0=500$ GeV, $\kappa_{1,2,3}(M_X)=0.1923$, $\lambda(M_X)=0.2646$ and
+$\lambda_{1,2}(M_X)=0.1$.
+This leads to a significant reduction in the contributions to the RG running of $m_{H_u}^2$ and $m_{Q3}^2$ coming from terms of the form $g_1^2\Sigma_1$ and, to a lesser extent, $g_1'^2\Sigma_1'$.
+Here we define (see also Eq.
+(\ref{}))
+\begin{align*}
+\Sigma_1&=\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2-m_{Li}^2+m_{H_{ui}}^2-m_{H_{di}}^2+m_{\overline{D}_i}^2-m_{Di}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\\
+\Sigma_1'&=\sum_{i=1}^3\left ( 6m_{Qi}^2+3m_{ui}^2+6m_{di}^2+m_{ei}^2+4m_{Li}^2-4m_{H_{ui}}^2-6m_{H_{di}}^2+5m_{Si}^2-9m_{\overline{D}_i}^2-6m_{Di}^2\right )\\
+&\quad{}+4m_{H'}^2-4m_{\overline{H'}}^2.
+\end{align*}
+In the unconstrained case, this contribution acts to drive up the values of $m_{Q3}^2$ and $m_{H_u}^2$, and thus the associated tuning sensitivities, at the input scale $M_X$.
+In the case of BM2, on the other hand, the reduced splitting between the soft masses leads to a much smaller contribution from these terms.
+Together with the reduction in $M_3$ described above, this allows to maintain the observed low fine tuning at very large values of $M_X$.
 

### 2015-01-23 paper/e6ssm-tuning-paper.tex
Filled in more precise values of minimum tunings in the conclusion

@@
 
+% DH:: I've given the minimum overall tunings for each, would it be
+% better to give the minimum for a 125 GeV Higgs (which is
+% ~38 for the MSSM, at a Higgs mass of 125.04 GeV, \tan\beta = 50,
+% vs. ~122 for a 2.5 TeV Z' and 393 for a 4.5 TeV Z' with m_h = 125.5 GeV
+% (this increases to ~416 for a 125 GeV Higgs exactly)
 In contrast we find that in $U(1)$ extensions of the MSSM there is an
@@
 the E$_6$SSM is compatible with a $Z^\prime$ mass of $2.5$ TeV was
-$\Delta \approx 100$, while if the LHC run II can place a limit of
-$4.5$ TeV on $M_Z^\prime$ then the tuning would be just under $400$.
+$\Delta \approx 112$, while if the LHC run II can place a limit of
+$4.5$ TeV on $M_Z^\prime$ then the tuning would be approximately $380$.
 By comparison the current situation in the MSSM only requires a tuning
-of around $20-30$. [Dylan: update numbers a bit -- I suck at reading
-  them off the graphs:)] This should be interpreted as saying that in
+of around $33$. This should be interpreted as saying that in
 the most conservative limits one can place on naturalness on these

### 2015-01-23 fs-spectrum/softsusy/cutoff_scan_mssm.cpp
Added an extra set of default parameters, for CMSSM points, to the MSSM cutoff scan

@@ -87,25 +87,48 @@ Eigen::VectorXd fill_log_values(std::size_t num_points, double lower, double upp
 
 void fill_default_input_pars(DoubleVector & pars)
 {
-   // default values used in scan
-   pars(1) = 300.; //< M1
-   pars(3) = 2000.; //< M3
-   pars(12) = 0.; //< AYd(2,2)
-   pars(13) = 0.; //< AYe(2,2)
-   pars(31) = 5000.; //< ml(0,0)
-   pars(32) = 5000.; //< ml(1,1)
-   pars(33) = 5000.; //< ml(2,2)
-   pars(34) = 5000.; //< me(0,0)
-   pars(35) = 5000.; //< me(1,1)
-   pars(36) = 5000.; //< me(2,2)
-   pars(41) = 5000.; //< mq(0,0)
-   pars(42) = 5000.; //< mq(1,1)
-   pars(44) = 5000.; //< mu(0,0)
-   pars(45) = 5000.; //< mu(1,1)
-   pars(46) = 5000.; //< mu(2,2)
-   pars(47) = 5000.; //< md(0,0)
-   pars(48) = 5000.; //< md(1,1)
-   pars(49) = 5000.; //< md(2,2)
+   const bool use_default_pars = false;
+
+   if (use_default_pars) {
+      // default values used in scan
+      pars(1) = 300.; //< M1
+      pars(3) = 1170.0;//2000.; //< M3
+      pars(12) = 0.; //< AYd(2,2)
+      pars(13) = 0.; //< AYe(2,2)
+      pars(31) = 5000.; //< ml(0,0)
+      pars(32) = 5000.; //< ml(1,1)
+      pars(33) = 5000.; //< ml(2,2)
+      pars(34) = 5000.; //< me(0,0)
+      pars(35) = 5000.; //< me(1,1)
+      pars(36) = 5000.; //< me(2,2)
+      pars(41) = 5000.; //< mq(0,0)
+      pars(42) = 5000.; //< mq(1,1)
+      pars(44) = 5000.; //< mu(0,0)
+      pars(45) = 5000.; //< mu(1,1)
+      pars(46) = 5000.; //< mu(2,2)
+      pars(47) = 5000.; //< md(0,0)
+      pars(48) = 5000.; //< md(1,1)
+      pars(49) = 5000.; //< md(2,2)
+   } else {
+      pars(1) = 4.35809794e+02; //< M1
[…]

### 2015-01-24 fs-spectrum/softsusy/cutoff_scan_mssm.cpp
Changed parameter values to be those of CMSSM point

@@ -110,24 +110,24 @@ void fill_default_input_pars(DoubleVector & pars)
       pars(48) = 5000.; //< md(1,1)
       pars(49) = 5000.; //< md(2,2)
    } else {
-      pars(1) = 4.35809794e+02; //< M1
-      pars(3) = 1160.0;//2.09996302e+03; //< M3
-      pars(12) = -1.92476064e+03; //< AYd(2,2)
-      pars(13) = -8.31473226e+01; //< AYe(2,2)
-      pars(31) = 2.28409908e+03; //< ml(0,0)
-      pars(32) = 2.28406934e+03; //< ml(1,1)
-      pars(33) = 2.27516902e+03; //< ml(2,2)
-      pars(34) = 2.22578992e+03; //< me(0,0)
-      pars(35) = 2.22572861e+03; //< me(1,1)
-      pars(36) = 2.20733853e+03; //< me(2,2)
-      pars(41) = 2.86004800e+03; //< mq(0,0)
-      pars(42) = 2.86003809e+03; //< mq(1,1)
-      pars(44) = 2.81426818e+03; //< mu(0,0)
-      pars(45) = 2.81425727e+03; //< mu(1,1)
-      pars(46) = 1.99865480e+03; //< mu(2,2)
-      pars(47) = 2.80871491e+03; //< md(0,0)
-      pars(48) = 2.80870549e+03; //< md(1,1)
-      pars(49) = 2.79059537e+03; //< md(2,2)
+      pars(1) = 2.60790587e+02;//4.35809794e+02; //< M1
+      pars(3) = 1.31226477e+03;//1160.0;//2.09996302e+03; //< M3
+      pars(12) = -5.70724514e+03;//-1.92476064e+03; //< AYd(2,2)
+      pars(13) = -5.05791595e+03;//-8.31473226e+01; //< AYe(2,2)
+      pars(31) = 2.51908311e+03;//2.28409908e+03; //< ml(0,0)
+      pars(32) = 2.51900237e+03;//2.28406934e+03; //< ml(1,1)
+      pars(33) = 2.49491895e+03;//2.27516902e+03; //< ml(2,2)
+      pars(34) = 2.50486775e+03;//2.22578992e+03; //< me(0,0)
+      pars(35) = 2.50470462e+03;//2.22572861e+03; //< me(1,1)
+      pars(36) = 2.45578715e+03;//2.20733853e+03; //< me(2,2)
[…]

### 2015-01-24 fs-spectrum/models/lowE6SSM/cutoff_scan_lowE6SSM.cpp
Various trace print statements commented out

@@ -1705,6 +1705,9 @@ int main()
             fine_tunings = tuning_calc.get_fine_tunings();
             max_tuning = maximum_tuning(fine_tunings);
 
+            //tuning_model.run_to(spectrum_generator.get_high_scale());
+            //tuning_model.print(std::cout);
+
             // tuning_model.run_to(mx_value);
             // std::cout << "In tuning, Q = " << tuning_model.get_scale() << "\n";
             // std::cout << "In tuning, Sigma1 = " << tuning_model.get_mq2().trace() - 2.0 * tuning_model.get_mu2().trace() + tuning_model.get_md2().trace() + tuning_model.get_me2().trace() - tuning_model.get_ml2().trace() + tuning_model.get_mHu2() - tuning_model.get_mHu2() + tuning_model.get_mH2I2().trace() - tuning_model.get_mH1I2().trace() + tuning_model.get_mDxbar2().trace() - tuning_model.get_mDx2().trace() - tuning_model.get_mHp2() + tuning_model.get_mHpbar2() << "\n";
@@ -1713,7 +1716,8 @@ int main()
          }
 
          // write out
-         //model.print(std::cout);
+         //tuning_model.run_to(spectrum_generator.get_high_scale());
+         //tuning_model.print(std::cout);
          // lowE6SSM_slha_io slha_io;
          // slha_io.set_spinfo(problems);
          // slha_io.set_sminputs(oneset);

### 2015-01-24 fs-spectrum/softsusy/cutoff_scan_mssm.cpp

@@ -501,7 +501,7 @@ int main() {
          // model output is at M_SUSY
          model.runto(model.displayMsusy());
 
-         //model.lesHouchesAccordOutput(cout, "nonUniversal", pars, sgnMu, TanBeta_value, 0.0,  
+         //model.lesHouchesAccordOutput(cout, "nonUniversal", pars, sgnMu, TanBeta_value, model.displayMxBC(),  
          //                             1, ewsb_BC_scale);
 
          // DH::note

### 2015-01-24 paper/e6ssm-tuning-paper.tex
Added references for LEP bounds on Higgs mass

@@
 placed constraints on the Higgs mass, requiring it to be above 114.4
-GeV \cite{}, which already introduced significant tuning for
+GeV \cite{Barate:2003sz,Schael:2006cr}, which already introduced significant tuning for
 constrained models, since heavy stops are required to raised the

### 2015-01-27 paper/e6ssm-tuning-paper.tex
added new abstract and title.  other options are still there in comments.

@@
 
-\title{Naturalness in U(1) extensions of the MSSM}
+\title {$Z^\prime$ mass limits and the naturalness of supersymmetry}
 
@@
 \begin{abstract}
-The abstract.
+%%The abstract.
 %%Original abstract
+%% title: Naturalness in U(1) extensions of the MSSM
 % Copied SUSY2014 abstract.
@@
 
-%% The discovery of a 125 GeV Higgs boson and rising lower bounds on the
-%% masses of superpartners, have lead to concerns that supersymmetric
-%% models are now fine tuned.  Large stop masses, required for a $125$
-%% GeV Higgs, feed into the EWSB conditions through renormalisation group
-%% equations forcing one to fine tune these parameters to obtain the
-%% correct electroweak vacuum expectation value.  Nonetheless this fine
-%% tuning depends crucially on our assumptions about the SUSY breaking
-%% scale.  At the same time U(1) extensions provide the most compelling
-%% solution to the $\mu$-problem, which is also a naturalness issue.
-%% These very well motovated supersymmetric models predict a new
-%% $Z^\prime$ boson which could be discovered at the LHC.  like the
-%% superpartners naturalness of the model requires that the $Z^\prime$
-%% boson mass should not be too \far above the TeV scale.  Moreover this
-%% fine tuning appears at the tree level, making it less dependent on a
-%% SUSY breaking mecahnism which has not been fully determnined.  Here we
-%% study this fine tuning for several $U(1)$ supesymmetric extensions of
-%% the standard model and compare it to the situation in the MSSM where
-%% the most direct tree level fine tuning can be probed through chargino
-%% mass limits.  we show that future LHC $Z^\prime$ searches are
-%% extremely important for challenging the most natural scenarios in
-%% these models.
+The discovery of a 125 GeV Higgs boson and rising lower bounds on the
+masses of superpartners, have lead to concerns that supersymmetric
+models are now fine tuned.  Large stop masses, required for a $125$
+GeV Higgs, feed into the EWSB conditions through renormalisation group
+equations forcing one to fine tune these parameters to obtain the
+correct electroweak vacuum expectation value.  Nonetheless this fine
+tuning depends crucially on our assumptions about the SUSY breaking
+scale.  At the same time U(1) extensions provide the most compelling
+solution to the $\mu$-problem, which is also a naturalness issue.
+These very well motivated supersymmetric models predict a new
+$Z^\prime$ boson which could be discovered at the LHC and the
+naturalness of the model requires that the $Z^\prime$ boson mass
+should not be too far above the TeV scale.  Moreover this fine tuning
+appears at the tree level, making it less dependent on assumptions
+about the SUSY breaking mechanism.  Here we study this fine tuning for
+several $U(1)$ supersymmetric extensions of the standard model and
+compare it to the situation in the MSSM where the most direct tree
+level fine tuning can be probed through chargino mass limits.  We show
+that future LHC $Z^\prime$ searches are extremely important for
+challenging the most natural scenarios in these models.
 
@@
 model (SM) and supersymmetry (SUSY).  On the one hand it provides a
-light Higgs boson in fitting with expectations from supersymmetry, and
+light Higgs boson, as expected from supersymmetry, and
 can be fitted in the minimal supersymmetric standard model (MSSM).  On
@@
 assumptions of these gravity mediated SUSY breaking motivated
-constrained models and in particular the way the universality
+constrained models and in particular that the universality
 constraints are applied at the GUT scale.  As mentioned above, given

### 2015-01-27 paper/e6ssm-tuning-paper.tex
E6SSM --> E.

@@
 from the stops. We find that the $Z^\prime$ limit is enough to already
-require moderate fine tuning in the E6SSM.  We also show this is
+require moderate fine tuning in the E$_6$SSM.  We also show this is
 comparable to the situation in the MSSM defined at the same scale if
@@
 {\it Top right panel:}  Individual sensitivities of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.
-{\it Bottom left panel:} Individual sensitivities of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.
-{\it Bottom right panel:} Individual sensitivities of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.
+{\it Bottom left panel:} Individual sensitivities of E$_6$SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.
+{\it Bottom right panel:} Individual sensitivities of E$_6$SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.
 }

### 2015-01-27 paper/e6ssm-tuning-paper.tex
More small fixes.

@@
 compare with previous results due to it's widespread use.  Fortunately
-the derivatives which appear in these tuning are also similar to the
+the derivatives which appear in these tunings are also similar to the
 Bayesian motivated measure so there should not be too large a
@@
 group at low energies is, \be SU(3)_C\times SU(2)_W\times U(1)_Y\times
-U(1)^\prime, \ee where $U(1)^\prime$ is the new gauge group beyond
+U(1)^\prime. \ee $U(1)^\prime$ is the new gauge group beyond
 that of the SM and MSSM. The minimal superfield content of $U(1)$
@@
 handed quark, $\hat{Q}_i$ and lepton $\hat{L}_i$
-($i=1,2,3$)superfields along with right handed superfields
+($i=1,2,3$) superfields along with right handed superfields
 $\hat{u}^c_i$, $\hat{d}^c_i$, $\hat{e}^c_i$ ($i=1,2,3$) for the
@@
 Here we will refer to U(1) extensions of the MSSM, which solve the
-$\mu$-problem as the USSM \cite{Cvetic:1995rj, Jain:1995cb,
+$\mu$-problem, as the USSM \cite{Cvetic:1995rj, Jain:1995cb,
   Nir:1995bu, Cvetic:1996mf, Cvetic:1997ky}.  The couplings for the
@@
 Here we will focus most on the special case where the gauge symmetry
-is $U()_N$,under which the right handed neutrino remains
+is $U(1)_N$, under which the right handed neutrino remains
 interaction-less. This is the case in the the exceptional
@@
 The gauge coupling running in the E$_6$SSM at the two-loop level leads
-to unification more precisely than in the MSSM \cite{King:2007uj} or
-in slightly modified scenarios two-step unification can take place
+to unification more precisely than in the MSSM \cite{King:2007uj} or,
+in slightly modified scenarios, two-step unification can take place
 \cite{Howl:2007hq,Howl:2007zi}. If the exotic particles are light in
@@
 relic abundance is fitted with a bino-like candidate with a novel
-mechanism involving back-scattering into a Heavier inert
+mechanism involving back-scattering into a heavier inert
 Higgsino. Another well motivated scenario admits two possible dark
@@
 the following unsuppressed superpotential terms, which follows the
-approach taking in work on the cE$_6$SSM \cite{Athron:2009ue,
+approach taken in work on the cE$_6$SSM \cite{Athron:2009ue,
   Athron:2009bs},
@@
 \subsection{\label{subsec:tuningmeasure}The Fine Tuning Measure}
-As stated above, in order to quantify the resulting fine tuning we
+As stated above, to quantify the resulting fine tuning we
 apply the traditional Ellis-Barbieri-Giudice measure
@@
 models defined at low energies, as we do here, we can take advantage
-of the fact that the amount of running involved is small. This makes
-it possible to use approximate analytic solutions to the RGEs that
-exhibit good accuracy over the range of scales considered. Given the
-two-loop RG equation for a parameter $q$,
+of the fact that the running is over much smaller scales than when
+evolving up to the GUT scale. This makes it possible to use
+approximate analytic solutions to the RGEs that exhibit good accuracy
+over the range of scales considered. Given the two-loop RG equation
+for a parameter $q$,
 \begin{equation}\label{eq:rge}

### 2015-01-27 paper/e6ssm-tuning-paper.tex
Added extra MSSM BM and tried to adjust text accordingly.

@@
 from the $Z^\prime$ mass appears already at tree level and is
-therefore not heavily suppressed when the cutoff scale is low. We find
+therefore not suppressed when the cutoff scale is low. We find
 that in the E$_6$SSM current limits on the mass of the $Z^\prime$
@@
 parameter (or effective $\mu$ parameter in these $U(1)$ extensions).
-However the chargino limits from the LHC are scenario dependent and
-depending on whether there are light sleptons or sneutralinos and the mass
-difference between the lightest chargino and lightest neutralino.
-Current limits placed by CMS and ATLAS extend up to $m_{\chi^\pm_1}
-\approx 700-740$ GeV if there are light
-sleptons\cite{Khachatryan:2014qwa,Aad:2014nua} with much weaker bounds
-if there are no light sleptons or sneutrinos\footnote{Useful summary
-  plots of these limit may be found on the public pages of ATLAS,
+However the chargino limits from the LHC depend on whether there are
+light sleptons or sneutrinos and the mass difference between the
+lightest chargino and lightest neutralino.  Current limits placed by
+CMS and ATLAS extend up to $m_{\chi^\pm_1} \approx 700-740$ GeV if
+there are light sleptons\cite{Khachatryan:2014qwa,Aad:2014nua} with
+much weaker bounds if there are no light sleptons or
+sneutrinos\footnote{Useful summary plots of these limit may be found
+  on the public pages of ATLAS,
   \url{https://atlas.web.cern.ch/Atlas/GROUPS/PHYSICS/CombinedSummaryPlots/SUSY/ATLAS_SUSY_EWSummary/ATLAS_SUSY_EWSummary.png}
@@
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_mssm_cutoff_scan_all_benchmark_points_tuning_vs_cutoff.png}} 
+\includegraphics{e6ssm_mssm_cutoff_scan_4_benchmark_points_tuning_vs_cutoff.png} } \\
 \resizebox{!}{5.5cm}{%
 \includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
-\\
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM1_all_tuning_data.png}}
+\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM1_all_tuning_data.png}} \\
+\resizebox{!}{5.5cm}{%
+\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_BM2_all_tuning_data.png}} 
 \resizebox{!}{5.5cm}{%
 \includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM2_all_tuning_data.png}}%%
-\caption{{\it Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.
-{\it Top right panel:}  Individual sensitivities of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.
-{\it Bottom left panel:} Individual sensitivities of E$_6$SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.
+\caption{{\it Top panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.
+{\it Middle left panel:}  Individual sensitivities of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.
+{\it Middle right panel:} Individual sensitivities of E$_6$SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.{\it Bottom right panel:} Individual sensitivities of MSSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.
 {\it Bottom right panel:} Individual sensitivities of E$_6$SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.
@@
 
-In the top left panel one can see that the MSSM tuning (green)
+In the top panel one can see that the MSSM BM1 tuning 
 steadily climbs as the cutoff scale is increased, as one would expect
 when the tuning originates from large soft masses entering from the
-RGEs. The panel on the top right confirms this, showing that the
+RGEs. The panel on the middle left confirms this, showing that the
 largest tuning contributions come from $\Delta_{A_t}$ and
@@
 over, leading to the small kink in overall tuning which can be seen in
-the green curve in the top left panel. In this case we have chosen a
+the green curve in the top panel. In this case we have chosen a
 point with large mixing, which is known to reduce the MSSM tuning.  We
@@
 
-Comparing the MSSM tuning to the E$_6$SSM tunings one can see that
+Comparing the MSSM tunings to the E$_6$SSM tunings one can see that
 which point is more fine tuned depends on the scale at which the
@@
 
-For E$_6$SSM BM1 the fine tuning is shown by the blue curve in top
-left panel of Fig.~\ref{Fig:BMs-varyMX} and the individual
-sensitivities are given in the bottom left panel. The tuning actually
-reduces initially as the cutoff is is increased from $20$ TeV.  This
-occurs because the largest sensitivity is initially $\Delta_\lambda$
-(shown in solid blue in the bottom left panel).  This contains some
-terms proportional to $M_Z^{\prime \, 2}$, which provide the dominant
+For E$_6$SSM BM1 the fine tuning is shown by the blue curve in the top
+panel of Fig.~\ref{Fig:BMs-varyMX} and the individual sensitivities
+are given in the middle right panel. The tuning actually reduces
+initially as the cutoff is is increased from $20$ TeV.  This occurs
+because the largest sensitivity is initially $\Delta_\lambda$ (shown
+in solid blue in the middle right panel).  This contains some terms
+proportional to $M_Z^{\prime \, 2}$, which provide the dominant
 contribution to this sensitivity at very low $M_X$.  However as $M_X$
@@
 also cause other sensitivities to grow, in particular $\Delta_{M_3}$.
-The fine tuning rises with $M_X$ once $M_X \gtrsim 10^5-10^6$ GeV,
-but remains lower than that of the other points, until $M_X \approx
-10^{11}$ GeV.  Eventually the $\Delta_{M_3}$ sensitivity leads to
-this point being the most fine tuned of the three shown in
+The fine tuning rises with $M_X$ once $M_X \gtrsim 10^5-10^6$ GeV, but
+remains lower than that of the other points, until $M_X \approx
+10^{11}$ GeV.  Eventually the $\Delta_{M_3}$ sensitivity leads to this
+point being the most fine tuned of the three shown in
 Fig.~\ref{Fig:BMs-varyMX}.
@@
 
-By contrast the tuning for E$_6$SSM BM2 is very different. This point
-was chosen as it had much lighter gluino mass that is just
-above the experimental limit of $1.4$ TeV \cite{Aad:2014lra}. 
-At $20$ TeV this benchmark is not amongst the lowest tuned points, since at that scale the tree
-level tuning from $M_{Z^\prime}$ dominates.  However the reduction in
-$M_3$ means that $\Delta_{M_3}$ is substantially lower and only
-becomes the dominant tuning at a much larger scale of $M_X\gtrsim 10^{12}-10^{13}$ GeV, giving a
-tuning at $10^{16}$ GeV of $\approx 546$, which is far below that of the
-other two benchmark points.
-
-In addition to this, the soft parameters in BM2 follow a pattern similar to that found in the constrained
+By contrast the tuning for E$_6$SSM BM2 is very different, as is shown
+in rd in the top panel, with the individual sensitivities given in the
+bottom right panel. This point was chosen as it had much lighter
+gluino mass that is just above the experimental limit of $1.4$ TeV
+\cite{Aad:2014lra}.  At $20$ TeV this benchmark is not amongst the
+lowest tuned points, since at that scale the tree level tuning from
+$M_{Z^\prime}$ dominates.  However the reduction in $M_3$ means that
+$\Delta_{M_3}$ is substantially lower and only becomes the dominant
+tuning at a much larger scale of $M_X\gtrsim 10^{12}-10^{13}$ GeV,
+giving a tuning at $10^{16}$ GeV of $\approx 546$, which is far below
+that of the other two benchmark points.
+
+In addition to this, the soft parameters in E$_6$SSM BM2 follow a pattern similar to that found in the constrained
 model. With the exception of the parameters $m_{Q3}^2$, 
@@
 This leads to a significant reduction in the contributions to the RG running of $m_{H_u}^2$ and $m_{Q3}^2$ coming from terms of the form $g_1^2\Sigma_1$ and, to a lesser extent, $g_1'^2\Sigma_1'$.
-Here we define (see also Eq.
-(\ref{}))
+Here we define (see also Eq.~(\ref{}))
 \begin{align*}
@@
 In the unconstrained case, this contribution acts to drive up the values of $m_{Q3}^2$ and $m_{H_u}^2$, and thus the associated tuning sensitivities, at the input scale $M_X$.
-In the case of BM2, on the other hand, the reduced splitting between the soft masses leads to a much smaller contribution from these terms.
+In the case of E$6$SSM BM2, on the other hand, the reduced splitting between the soft masses leads to a much smaller contribution from these terms.
 Together with the reduction in $M_3$ described above, this allows to maintain the observed low fine tuning at very large values of $M_X$.
+
+MSSM benchmark BM2 (yellow in top panel, individual sensitivities in bottom left panel) was designed to be similar to E$_6$SSM BM2, for a reasonable comparison.
+However from the individual sensitivities one can see that the behaviour is quite similar to MSSM BM1, though in this case the $\Delta_{m_{H-u}^2}$ becomes the largest tuning at a higher $M_X$ and does not reach such large values, since more of the tuning is from the mixing in this case.
 

### 2015-01-27 paper/e6ssm-tuning-paper.tex
fixes to last commit

@@
 The fine tuning rises with $M_X$ once $M_X \gtrsim 10^5-10^6$ GeV, but
-remains lower than that of the other points, until $M_X \approx
-10^{11}$ GeV.  Eventually the $\Delta_{M_3}$ sensitivity leads to this
-point being the most fine tuned of the three shown in
+remains lower than that of the other points, until $M_X \approx 10^8$
+GeV.  Eventually the $\Delta_{M_3}$ sensitivity leads to this point
+being the most fine tuned of the four shown in
 Fig.~\ref{Fig:BMs-varyMX}.
@@
  Although the gluino mass and $M_3(M_{SUSY})$ have similar values to
- those in the MSSM point, in the E$_6$SSM $M_3(M_X)$ is larger
+ those in the MSSM BM1 point, in the E$_6$SSM $M_3(M_X)$ is larger
  due to the altered RGE running from exotic matter\footnote{This
    altered RGE running is a result of the exotic matter introduced to
-   keep the extra $U(1)$ anomaly free. }. This is why the E$_6$SSM
+   keep the extra $U(1)$ anomaly free. }. This is why this E$_6$SSM
  point has the much larger tuning, coming from $\Delta_{M_3}$.
@@
 By contrast the tuning for E$_6$SSM BM2 is very different, as is shown
-in rd in the top panel, with the individual sensitivities given in the
+in red in the top panel, with the individual sensitivities given in the
 bottom right panel. This point was chosen as it had much lighter
@@
 In the unconstrained case, this contribution acts to drive up the values of $m_{Q3}^2$ and $m_{H_u}^2$, and thus the associated tuning sensitivities, at the input scale $M_X$.
-In the case of E$6$SSM BM2, on the other hand, the reduced splitting between the soft masses leads to a much smaller contribution from these terms.
+In the case of E$_6$SSM BM2, on the other hand, the reduced splitting between the soft masses leads to a much smaller contribution from these terms.
 Together with the reduction in $M_3$ described above, this allows to maintain the observed low fine tuning at very large values of $M_X$.
@@
 MSSM benchmark BM2 (yellow in top panel, individual sensitivities in bottom left panel) was designed to be similar to E$_6$SSM BM2, for a reasonable comparison.
-However from the individual sensitivities one can see that the behaviour is quite similar to MSSM BM1, though in this case the $\Delta_{m_{H-u}^2}$ becomes the largest tuning at a higher $M_X$ and does not reach such large values, since more of the tuning is from the mixing in this case.
+However from the individual sensitivities one can see that the behaviour is quite similar to MSSM BM1, though in this case the $\Delta_{m_{H_u}^2}$ becomes the largest tuning at a higher $M_X$ and does not reach such large values, since more of the tuning is from the mixing in this case.
 

### 2015-01-27 fs-spectrum/models/lowE6SSM/full_tuning_scan_lowE6SSM.cpp
Changed theta to be that for U(1)_\psi model

@@ -38,8 +38,12 @@ namespace flexiblesusy {
    lowE6SSM_input_parameters get_default_inputs()
    {
       lowE6SSM_input_parameters input;
-      
-      const double theta = ArcTan(Sqrt(15.));
+
+      // U(1)_N: theta = ArcTan(Sqrt(15.0))
+      // U(1)_I: theta = PI + ArcTan(Sqrt(0.6))
+      // U(1)_psi: theta = 0.5 * PI
+
+      const double theta = 0.5 * PI;
       
       initialize_e6_charges(theta, input);
       

### 2015-01-27 paper/e6ssm-tuning-paper.tex
typo fixed
Made some minor changes to the paper

@@
 \begin{equation}\label{eq:E6VeffOneLoop}
-V_{E_6}=V_{E_6}^F+V_{E_6}^D+V_{E_6}^{\textrm{soft}}+\Delta V_{E_6}.
+V=V_F+V_D+V_{\textrm{soft}}+\Delta V.
 \end{equation}
@@
 \begin{align}
-V_{E_6}^F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|(H_1\cdot
-H_2)|^2,\label{eq:E6VFterms}\\ V_{E_6}^D&=\frac{\bar{g}^2}{8}\left (
+V_F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|(H_1\cdot
+H_2)|^2,\label{eq:E6VFterms}\\ V_D&=\frac{\bar{g}^2}{8}\left (
 |H_2|^2-|H_1|^2\right )^2+\frac{g_2^2}{2}|H_1^\dagger
-H_2|^2+\frac{g_1'^2}{2}(\tilde{Q}_1|H_1|^2+\tilde{Q}_2|H_2|^2+\tilde{Q}_S|S|^2)^2,\label{eq:E6VDterms}\\ V_{E_6}^{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big
+H_2|^2+\frac{g_1'^2}{2}(\tilde{Q}_1|H_1|^2+\tilde{Q}_2|H_2|^2+\tilde{Q}_S|S|^2)^2,\label{eq:E6VDterms}\\ V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big
 [\lambda A_\lambda S(H_1\cdot H_2)+\textrm{h.c.}\Big
@@
 is defined by $A\cdot B\equiv \epsilon_{\alpha\beta}A^\alpha
-B^\beta=A^2B^1-A^1B^2$. The term $\Delta V_{E_6}$ contains the
+B^\beta=A^2B^1-A^1B^2$. The term $\Delta V$ contains the
 Coleman-Weinberg contributions to the effective potential. In the case
-of the $U(1)_\chi$ model, $V_{E_6}^F$ may also contain an elementary
+of the $U(1)_\chi$ model, $V_F$ may also contain an elementary
 $\mu$ term contribution, as occurs in the MSSM.\\ \\ Demanding that
@@
 \tilde{m}_{H_d}^2&=m_{H_d}^2+\frac{1}{v_1}\frac{\partial \Delta
-  V_{E_6}}{\partial
+  V}{\partial
   v_1},\\ \tilde{m}_{H_u}^2&=m_{H_u}^2+\frac{1}{v_2}\frac{\partial
-  \Delta V_{E_6}}{\partial v_2}.
+  \Delta V}{\partial v_2}.
 \end{align*}
@@
 2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim 2.62$ TeV in
-$U(1)_\chi$ models. To satisfy these limits typically requires large
+$U(1)_\chi$ models.
+Bounds on the $Z^\prime$ mass for other $E_6$ inspired models, such as the $U(1)_N$ of the E$_6$SSM, lie between those on the $U(1)_\psi$ and $U(1)_\chi$.
+To satisfy these limits typically requires large
 values of the singlet VEV $s$. For example $s\gtrsim 6$ TeV is
@@
 input scale $M_X$. For a given parameter $p$ in this set, one computes
-an associated sensitivity coefficient \cite{Feng:2013pwa}
+an associated sensitivity
 \begin{equation}\label{eq:bgmeasure}
@@
 \cite{Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta} and
-FlexibleSUSY \cite{Athron:2014yba}. The CP-even Higgs masses are
+FlexibleSUSY \cite{Athron:2014yba}, which also makes use of SOFTSUSY \cite{Allanach:2001kg,Allanach:2013kza}. The CP-even Higgs masses are
 calculated including the leading one-loop effective potential
@@
 MSSM fine tuning expressions were implemented into a modified version
-of SOFTSUSY 3.3.10 \cite{Allanach:2001kg,Allanach:2013kza}. For
+of SOFTSUSY 3.3.10 \cite{Allanach:2001kg}. For
 consistency with the results produced in the $E_6$ models, and for
@@
 masses. Current LHC limits on charginos are not model independent and
-thereby leave many gaps where on can have light charginos.
+thereby leave many gaps where one can have light charginos.
 

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Added MSSM BM2 to table, added rest of parameters to table as well

@@
 \usepackage{footmisc}
+\usepackage{longtable}
 % macros
@@
 of the $U(1)_\chi$ model, $V_F$ may also contain an elementary
-$\mu$ term contribution, as occurs in the MSSM.\\ \\ Demanding that
+$\mu$ term, as occurs in the MSSM.\\ \\ Demanding that
 the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real VEVs of
@@
 
+\begingroup
+\squeezetable
 \begin{table}[h]
@@
 \begin{ruledtabular}
-\begin{tabular}{cccc}
-& MSSM & E$_6$SSM BM1 & E$_6$SSM BM2 \\
+\begin{tabular}{ccccc}
+& MSSM BM1 & MSSM BM2 & E$_6$SSM BM1 & E$_6$SSM BM2 \\
 \hline
-$\tan\beta(M_Z)$ & 10 & 10 & 10 \\
-$s(M_{\mathrm{SUSY}})$ [GeV] & $-$ & 6700 & 6700 \\
-$\kappa_{1,2,3}(M_{\mathrm{SUSY}})$ & $-$ & 0.6 & 0.52 \\
-$\lambda_{1,2}(M_{\mathrm{SUSY}})$ & $-$ & 0.2 & 0.13 \\
-$\mu_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 689.7 & 1093.3 & 1313.0 \\
-$B_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 345.7 & 3792.7 & 817.8 \\
-$A_t(M_{\mathrm{SUSY}})$ [GeV] & -3335.7 & -1100 & -1103.2 \\
-$m_{Q3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.45\times 10^6$ & $4.50\times 10^5$ & $3.61\times 10^6$ \\
-$m_{u3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4\times 10^6$ & $5.86\times 10^5$ & $2.04\times 10^6$ \\
-$M_1(M_{\mathrm{SUSY}})$ [GeV] & 300 & 300 & 173.4 \\
-$M_2(M_{\mathrm{SUSY}})$ [GeV] & 2000 & 1050 & 281.4 \\
-$M_3(M_{\mathrm{SUSY}})$ [GeV] & 2000 & 2000 & 1200 \\
-$M_1^\prime(M_{\mathrm{SUSY}})$ [GeV] & $-$ & 300 & 175.2 \\
+$\tan\beta(M_Z)$ & $10$ & $10$ & $10$ & $10$ \\
+$s(M_{\mathrm{SUSY}})$ [GeV] & $-$ & $-$ & $6700$ & $6700$ \\
+$\kappa_{1,2,3}(M_{\mathrm{SUSY}})$ & $-$ & $-$ & $0.6$ & $0.52$ \\
+$\lambda_{1,2}(M_{\mathrm{SUSY}})$ & $-$ & $-$ & $0.2$ & $0.13$ \\
+$\mu_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & $689.7$ & $1013.5$ & $1093.3$ & $1313.0$ \\
+$B_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & $345.7$ & $1032.5$ & $3792.7$ & $817.8$ \\
+$A_\tau(M_{\mathrm{SUSY}})$ [GeV] & $0$ & $-5057.9$ & $0$ & $-88.5$ \\
+$A_b(M_{\mathrm{SUSY}})$ [GeV] & $0$ & $-5707.2$ & $0$ & $-1720.7$\\
+$A_t(M_{\mathrm{SUSY}})$ [GeV] & $-3335.7$ & $-2734.8$ & $-1100$ & $-1103.2$ \\
+$m_{L1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.35\times 10^6$ & $2.5\times 10^7$ & $4.94\times 10^6$ \\
+$m_{L3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.22\times 10^6$ & $2.5\times 10^7$ & $4.90\times 10^6$ \\
+$m_{e1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.27\times 10^6$ & $2.5\times 10^7$ & $5.21\times 10^6$ \\
+$m_{e3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.03\times 10^6$ & $2.5\times 10^7$ & $5.11\times 10^6$ \\
+$m_{Q1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.37\times 10^6$ & $2.5\times 10^7$ & $5.76\times 10^6$ \\
+$m_{Q3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.45\times 10^6$ & $3.97\times 10^6$ & $4.50\times 10^5$ & $3.61\times 10^6$ \\
+$m_{u1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.30\times 10^6$ & $2.5\times 10^7$ & $5.54\times 10^6$ \\
+$m_{u3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.0 \times 10^6$ & $6.60\times10^5$& $5.86\times 10^5$ & $2.04\times 10^6$ \\
+$m_{d1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.30\times 10^6$ & $2.5\times 10^7$ & $5.88\times 10^6$ \\
+$m_{d3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.03\times 10^6$ & $2.5\times 10^7$ & $5.78\times 10^6$ \\
+$m_{H_d}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & & & & \\
+$m_{H_u}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & & & & \\
+$m_S^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $-$ & $-$ & & \\
+$M_1(M_{\mathrm{SUSY}})$ [GeV] & $300$ & $260.8$ & $300$ & $173.4$ \\
+$M_2(M_{\mathrm{SUSY}})$ [GeV] & $2000$ & $479.2$ & $1050$ & $281.4$ \\
+$M_3(M_{\mathrm{SUSY}})$ [GeV] & $2000$ & $1312.3$ & $2000$ & $1200$ \\
+$M_1^\prime(M_{\mathrm{SUSY}})$ [GeV] & $-$ & $-$ & $300$ & $175.2$ \\
 \hline
-$M_{Z^\prime}$ [GeV] & $-$ & 2473.2 & 2512.7 \\
-$m_{h_1}$ [GeV] & 124.3 & 125.0 & 126.2 \\
-$m_{\tilde{t}_1}$ [GeV] & 1942.1 & 993.8 & 1665.0 \\
-$m_{\tilde{t}_2}$ [GeV] & 2220.1 & 1174.8 & 2094.4 \\
-$m_{\tilde{g}}$ [GeV] & 2259.8 & 2290.0 & 1407.4\\
+$M_{Z^\prime}$ [GeV] & $-$ & $-$ & $2473.2$ & $2512.7$ \\
+$m_{h_1}$ [GeV] & $124.3$ & $124.4$ & $125.0$ & $126.2$ \\
+$m_{\tilde{t}_1}$ [GeV] & $1942.1$ & $861.6$ & $993.8$ & $1665.0$ \\
+$m_{\tilde{t}_2}$ [GeV] & $2220.1$ & $2023.9$ & $1174.8$ & $2094.4$ \\
+$m_{\tilde{g}}$ [GeV] & $2259.8$ & $1472.9$ & $2290.0$ & $1407.4$ \\
 \hline
-$\Delta(M_X=20\textrm{ TeV})$ & 157.3 & 165.3 & 402.1 \\
-$\Delta(M_X=10^{16}\textrm{ GeV})$ & 1089.0 & 1722.3 & 546.7
+$\Delta(M_X=20\textrm{ TeV})$ & $157.3$ & $242.8$ & $165.3$ & $402.1$ \\
+$\Delta(M_X=10^{16}\textrm{ GeV})$ & $1089.0$ & $949.0$ & $1722.3$ & $546.7$
 \end{tabular}
 \end{ruledtabular}
-\caption{Parameters and masses for the MSSM point and the E$_6$SSM benchmark points 
-BM1 and BM2. For the
-E$_6$SSM we define $\mu_{\mathrm{eff}}\equiv \lambda s/\sqrt{2}$ and
+\caption{Parameters for the MSSM and E$_6$SSM benchmark points. In the E$_6$SSM we define $\mu_{\mathrm{eff}}\equiv \lambda s/\sqrt{2}$ and
 $B_{\mathrm{eff}}=A_\lambda$.
-In BM1 all other (diagonal) soft scalar squared masses not shown above are set to $(5\mathrm{ TeV})^2$, the soft trilinears $A_b$, $A_\tau=0$, $\mu^\prime=5000$ GeV and $B\mu^\prime=5000$ GeV$^2$.
-In BM2 the parameters not shown above are set to the values obtained by running the cE$_6$SSM point with $m_0=2.2$ TeV, $A_0=500$ GeV, $M_{1/2}=1003$ GeV, $\kappa_{1,2,3}(M_X)=0.1923$, $\lambda(M_X)=0.2646$ to the SUSY scale, and setting $\mu^\prime(M_{\mathrm{SUSY}})=897.9$ GeV and $B\mu^\prime(M_{\mathrm{SUSY}})=-4.2\times10^5$ GeV$^2$.}
+The soft masses $m_{H_d}^2$, $m_{H_u}^2$ and $m_S^2$ are those that satisfy the EWSB conditions including 1-loop Coleman-Weinberg corrections involving the top and stops.
+For E$_6$SSM BM1 (BM2) we also set $\mu^\prime = 5000.0$ $(897.9)$ GeV, $B\mu^\prime = 5000.0$ $(-4.21\times 10^5)$ GeV$^2$, $A_{\kappa 1,2,3} = 0$ $(-1389.2)$ GeV, $A_{\lambda 1,2} = 0$ $(-52.9)$ GeV, $m_{D1,2,3}^2 = 2.5\times 10^7$ $(4.81\times 10^6)$ GeV$^2$, $m_{\overline{D}1,2,3}^2 = 2.5\times 10^7$ $(4.90\times 10^6)$ GeV$^2$, $m_{H^d_{1,2}}^2 = 2.5\times 10^7$ $(4.46\times 10^6)$ GeV$^2$, $m_{H^u_{1,2}}^2 = 2.5\times 10^7$ $(4.81\times 10^6)$ GeV$^2$, $m_{S_{1,2}}^2 = 2.5\times 10^7$ $(5.28\times 10^6)$ GeV$^2$, $m_{H'}^2 = 2.5\times 10^7$ $(4.94\times 10^6)$ GeV$^2$ and $m_{\overline{H'}}^2 = 2.5\times 10^7$ $(4.87\times 10^6)$ GeV$^2$.
+}
 \label{tab:benchmarks}
 \end{table}
-
+\endgroup
 \begin{figure}

### 2015-01-28 fs-spectrum/models/lowE6SSM/cutoff_scan_lowE6SSM.cpp
Added some trace print statements

@@ -1680,10 +1680,16 @@ int main()
             double mHu2 = ew_derivs.get_model().get_mHu2();
             double ms2 = ew_derivs.get_model().get_ms2();         
 
+            std::cout << "1 loop mHd2 = " << mHd2 << "\n";
+            std::cout << "1 loop mHu2 = " << mHu2 << "\n";
+            std::cout << "1 loop ms2 = " << ms2 << "\n";
+
             lowE6SSM<Two_scale> tuning_model(model);
             tuning_model.set_mHd2(mHd2);
             tuning_model.set_mHu2(mHu2);
             tuning_model.set_ms2(ms2);
+
+            std::cout << "MassG = " << tuning_model.get_MassG() << "\n";
 
             lowE6SSM_tuning_calculator tuning_calc(tuning_model);
             tuning_calc.set_tuning_scale(tuning_model.get_scale());

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Added in E6SSM soft Higgs mass values to table
Replaced instances of cut-off with cutoff, added more precise values for minimum fine tunings in each scan

@@
 \cite{Ellis:1986yg,Barbieri:1987fn}. A specific model is characterised
-by a set of $n$ model parameters $\{p_i\}$ and is defined at some
-input scale $M_X$. For a given parameter $p$ in this set, one computes
+by a set of $n$ model parameters $\{p_i\}$ and is defined at the scale $M_X$. 
+For a given parameter $p$ in this set, one computes
 an associated sensitivity
@@
 side of Eqs. (\ref{eq:rgeapproxsoln}) and
-(\ref{eq:1loopbetaderivative}) are evaluated at the input scale $M_X$,
+(\ref{eq:1loopbetaderivative}) are evaluated at the scale $M_X$,
 giving a simple analytic expression for the parameters at the scale of
@@
 \caption{Left panel: Scatter plot of fine tuning in the MSSM as a function of
-the lightest stop mass, $m_{\tilde{t}_1}$, for the cut-off scales (from 
+the lightest stop mass, $m_{\tilde{t}_1}$, for the cutoff scales (from 
 bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV. 
 Right panel: Scatter plot of fine tuning in the MSSM as a function of
-the lightest Higgs mass, $m_{h_1}$, for the cut-off scales (from 
+the lightest Higgs mass, $m_{h_1}$, for the cutoff scales (from 
 bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
@@
 from large stop masses to the fine tuning is small for such a low
-cut-off scale, the stop contributions to the effective potential can
+cutoff scale, the stop contributions to the effective potential can
 play a significant role in reducing the fine tuning.  For this reason it is still important to properly treat the
@@
 from the $Z^\prime$ mass appears already at tree level and is
-therefore not suppressed when the cutoff scale is low. We find
-that in the E$_6$SSM current limits on the mass of the $Z^\prime$
-boson imply that the E$_6$SSM fine tuning is at least 100.
-Additionally if run II of the LHC pushes the limit on the $Z^\prime$
+therefore not suppressed when the cutoff scale is low.
+In our scan we find that, for the points satisfying the current limit on the mass of the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the minimum fine tuning that can be achieved is
+$\Delta_{\textrm{min}}\approx 121$.
+
+If run II of the LHC further pushes up the limit on the $Z^\prime$
 mass to be above $4.5$ TeV then the fine tuning in the model will be
-greater than at least 350.
+greater than at least $\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$ GeV and $125.5$ GeV.
 
@@
 $m_{d3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.03\times 10^6$ & $2.5\times 10^7$ & $5.78\times 10^6$ \\
-$m_{H_d}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & & & & \\
-$m_{H_u}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & & & & \\
-$m_S^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $-$ & $-$ & & \\
+$m_{H_d}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & & & $4.06\times 10^7$ & $1.04\times 10^7$ \\
+$m_{H_u}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & & & $5.0\times 10^5$ & $-2.66\times 10^5$ \\
+$m_S^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $-$ & $-$ & $-3.10\times 10^6$ & $-3.17 \times 10^6$ \\
 $M_1(M_{\mathrm{SUSY}})$ [GeV] & $300$ & $260.8$ & $300$ & $173.4$ \\
@@
 \includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM2_all_tuning_data.png}}%%
-\caption{{\it Top panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.
+\caption{{\it Top panel:} Scatter plot of fine tuning vs cutoff scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.
 {\it Middle left panel:}  Individual sensitivities of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.
@@
 \end{align*}
-In the unconstrained case, this contribution acts to drive up the values of $m_{Q3}^2$ and $m_{H_u}^2$, and thus the associated tuning sensitivities, at the input scale $M_X$.
+In the unconstrained case, this contribution acts to drive up the values of $m_{Q3}^2$ and $m_{H_u}^2$, and thus the associated tuning sensitivities, at the cutoff scale $M_X$.
 In the case of E$_6$SSM BM2, on the other hand, the reduced splitting between the soft masses leads to a much smaller contribution from these terms.
@@
 
-% DH:: I've given the minimum overall tunings for each, would it be
-% better to give the minimum for a 125 GeV Higgs (which is
-% ~38 for the MSSM, at a Higgs mass of 125.04 GeV, \tan\beta = 50,
-% vs. ~122 for a 2.5 TeV Z' and 393 for a 4.5 TeV Z' with m_h = 125.5 GeV
-% (this increases to ~416 for a 125 GeV Higgs exactly)
 In contrast we find that in $U(1)$ extensions of the MSSM there is an
@@
 the E$_6$SSM is compatible with a $Z^\prime$ mass of $2.5$ TeV was
-$\Delta \approx 112$, while if the LHC run II can place a limit of
-$4.5$ TeV on $M_Z^\prime$ then the tuning would be approximately $380$.
+$\Delta \approx 121$, while if the LHC run II can place a limit of
+$4.5$ TeV on $M_Z^\prime$ then the tuning would be approximately $394$.
 By comparison the current situation in the MSSM only requires a tuning
-of around $33$. This should be interpreted as saying that in
+of around $38$. This should be interpreted as saying that in
 the most conservative limits one can place on naturalness on these
@@
 as $M_X$ increases towards the scale where the gauge couplings unify,
-the familiar tunings do dominate, though with tunings from the Gluino
+the familiar tunings do dominate, though with tunings from the gluino
 mass appearing to be more significant relative to those from soft

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Fixed labels on benchmark plots

@@
 \resizebox{!}{5.5cm}{%
-\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
+\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_BM1_all_tuning_data.png}} 
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM1_all_tuning_data.png}} \\
+\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_BM1_all_tuning_data.png}} \\
 \resizebox{!}{5.5cm}{%
@@
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM2_all_tuning_data.png}}%%
+\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_BM2_all_tuning_data.png}}%%
 \caption{{\it Top panel:} Scatter plot of fine tuning vs cutoff scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Updated the caption on the benchmark points plot to reflect the fact there are now 4 benchmarks instead of 3

@@
 \includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_BM2_all_tuning_data.png}}%%
-\caption{{\it Top panel:} Scatter plot of fine tuning vs cutoff scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.
-{\it Middle left panel:}  Individual sensitivities of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.
-{\it Middle right panel:} Individual sensitivities of E$_6$SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.{\it Bottom right panel:} Individual sensitivities of MSSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.
-{\it Bottom right panel:} Individual sensitivities of E$_6$SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.
+\caption{{\it Top panel:} Scatter plot of the fine tuning as a function of the cutoff scale $M_X$ for the four benchmark points given in Table \ref{tab:benchmarks}.
+{\it Middle left panel:}  Individual sensitivities for MSSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the green line in the top panel.
+{\it Middle right panel:} Individual sensitivities for E$_6$SSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the blue line in the top panel.
+{\it Bottom left panel:} Individual sensitivities for MSSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the yellow line in the top panel.
+{\it Bottom right panel:} Individual sensitivities for E$_6$SSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the red line in the top panel.
 }

### 2015-01-28 fs-spectrum/softsusy/cutoff_scan_mssm.cpp
Added trace prints to cutoff scan in the MSSM

@@ -529,6 +529,10 @@ int main() {
                tuning_model.setMh1Squared(soft_masses_1lp(1));
                tuning_model.setMh2Squared(soft_masses_1lp(2));
                
+               // note
+               std::cout << "1 loop mHd2 = " << soft_masses_1lp(1) << "\n";
+               std::cout << "1 loop mHu2 = " << soft_masses_1lp(2) << "\n";
+
                f1 = MSSM_EWSBCondition1(tuning_model);
                f2 = MSSM_EWSBCondition2(tuning_model);
 

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Merged Tony Williams' revisions to the paper, added in soft Higgs mass values for the MSSM benchmarks to the table

@@
  \affiliation{
-ARC Centre of Excellence for Particle Physics at the Terascale, School of Chemistry and Physics, The University of Adelaide,
+ARC Centre of Excellence for Particle Physics at the Terascale, Department of Physics, The University of Adelaide,
 Adelaide, South Australia 5005, Australia}
@@
 can be fitted in the minimal supersymmetric standard model (MSSM).  On
-the other hand it is slightly heavier than the constrained version of the 
+the other hand the Higgs mass is slightly heavier than the constrained version of the 
 MSSM (cMSSM) can accommodate naturally \cite{Cassel:2011zd,Ghilencea:2012gz}.
@@
 in the $E_6$ inspired case, \be U(1)^\prime = \cos(\theta) U(1)_{\chi}
-+ \sin(\theta) U(1)_{\psi}. \ee In table \ref{tab:E6charges} the
++ \sin(\theta) U(1)_{\psi}. \ee In Table \ref{tab:E6charges} the
 charges for several popular $E_6$ inspired $U(1)$ extensions are
@@
 Nonetheless while this model is very elegant so far, the
-superpotential, (\ref{Eq:e6-superpot}) contains dangerous terms which
+superpotential of Eq.~(\ref{Eq:e6-superpot}) contains dangerous terms which
 can induce proton decay and lead to large flavour changing neutral
@@
 \begin{equation}\label{eq:E6VeffOneLoop}
-V=V_F+V_D+V_{\textrm{soft}}+\Delta V.
+V=V_F+V_D+V_{\textrm{soft}}+\Delta V \, ,
 \end{equation}
@@
 In these expressions $g_2$, $g'=\sqrt{3/5}g_1$, and $g_1'$ are the
-$SU(2)$, (non-GUT normalized) $U(1)_Y$ and $U(1)'$ gauge couplings,
-respectively, and $\bar{g}^2=g_2^2+g'^2$. The charges $\tilde{Q}_1$,
+$SU(2)$, (non-GUT normalized) $U(1)_Y$ and $U(1)'$ gauge couplings
+respectively and $\bar{g}^2=g_2^2+g'^2$. The charges $\tilde{Q}_1$,
 $\tilde{Q}_2$ and $\tilde{Q}_S$ are effective $U(1)'$ charges for
@@
 \cite{Ellis:1986yg,Barbieri:1987fn}. A specific model is characterised
-by a set of $n$ model parameters $\{p_i\}$ and is defined at the scale $M_X$. 
-For a given parameter $p$ in this set, one computes
+by a set of $n$ model parameters $\{p_i\}$ and is defined at some
+input scale $M_X$. For a given parameter $p$ in this set, one computes
 an associated sensitivity
@@
 \ee where the sum is over all low energy running parameters appearing
-in the tree level EWSB conditions, i.e. $q\in\{\lambda, A_\lambda,
+in the tree level EWSB conditions, i.e., $q\in\{\lambda, A_\lambda,
 m_{H_d}^2,m_{H_u}^2,m_S^2,g_1,g_2,g_1'\}$. Expressions for the
@@
   GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.  The remaining
-parameters we fix such that at $M_{SUSY}$ they have the values
+parameters we fix such that at $M_{\rm SUSY}$ they have the values
 $\mu=-97.5$ GeV, $B=-84.8$ GeV, $M_1=92.1$ GeV, $M_2=95.9$ GeV,
@@
 \caption{Scatter plot of fine tuning vs lightest Higgs mass for the
-  MSSM (green), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue) and
-  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red).}
+  MSSM (green, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue, middle band) and
+  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band).}
 \label{Fig:e6ssmvsmssm}
@@
 \includegraphics{mssm_chargino_plot.png}}%%
-\caption{Scatter plot of fine tuning vs lightest Higgs mass in the MSSM with $m_{\chi^\pm_1} = 200$ GeV shown in green $m_{\chi^\pm_1} = 500$ GeV in blue and $m_{\chi^\pm_1} = 700$ GeV in red.}
+\caption{Scatter plot of fine tuning vs lightest Higgs mass in the MSSM with $m_{\chi^\pm_1} = 200$ GeV shown in green 
+(bottom band) $m_{\chi^\pm_1} = 500$ GeV in blue (middle band) and $m_{\chi^\pm_1} = 700$ GeV in red
+(top band).}
 \label{Fig:chargino-plot}
@@
 \includegraphics{e6eta_tb10_tuning_vs_higgs.png}}%%
-\caption{Scatter plot of fine tuning vs lightest Higgs mass in ... with $M_{Z^\prime} = 2.5$ TeV shown in blue and $M_{Z^\prime} = 4.5$ TeV in red.}
+\caption{Scatter plot of fine tuning vs lightest Higgs mass in ... with $M_{Z^\prime} = 2.5$ TeV shown in blue
+(bottom band) and $M_{Z^\prime} = 4.5$ TeV in red (top band).}
 \label{Fig:othere6modelsvsmssm}
@@
 $m_{d3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.03\times 10^6$ & $2.5\times 10^7$ & $5.78\times 10^6$ \\
-$m_{H_d}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & & & $4.06\times 10^7$ & $1.04\times 10^7$ \\
-$m_{H_u}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & & & $5.0\times 10^5$ & $-2.66\times 10^5$ \\
+$m_{H_d}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $1.82\times 10^6$ & $8.96\times 10^6$ & $4.06\times 10^7$ & $1.04\times 10^7$ \\
+$m_{H_u}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $-3.60\times 10^5$ & $-9.35\times 10^5$ & $5.0\times 10^5$ & $-2.66\times 10^5$ \\
 $m_S^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $-$ & $-$ & $-3.10\times 10^6$ & $-3.17 \times 10^6$ \\
@@
 This should also be contrasted with what happens as we raise the high
-scale boundary, $M_X$.  We showed that for benchmark points that which
+scale boundary, $M_X$.  We showed that for our benchmark points, which
 one is more tuned depends very strongly on $M_X$.  The E$_6$SSM tuning
@@
 was much worse for the larger $Z^\prime$ mass, further emphasising
-the importance they play in these $U(1)$ extensions.  Interestingly
+the importance of this in $U(1)$ extensions.  Interestingly
 the actual level in tuning varied quite a bit between these models
@@
 mass. However one should remember we are looking at conservative limits
-on naturalness here and there is no solution to the usual tuning from
+on naturalness here and there is no solution to the usual tuning coming from
 the large stops needed to get a $125$ GeV Higgs in this model.  In any

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Denoted charginos with tildes, \tilde{\chi}^\pm, instead of just \chi^\pm

@@
 lightest chargino and lightest neutralino.  Current limits placed by
-CMS and ATLAS extend up to $m_{\chi^\pm_1} \approx 700-740$ GeV if
+CMS and ATLAS extend up to $m_{\tilde{\chi}^\pm_1} \approx 700-740$ GeV if
 there are light sleptons\cite{Khachatryan:2014qwa,Aad:2014nua} with
@@
 shown in Fig.~\ref{Fig:chargino-plot}.  There we see that if the the
-full parameter space with $m_{\chi^\pm} < 700$ GeV was excluded the
+full parameter space with $m_{\tilde{\chi}^\pm_1} < 700$ GeV was excluded the
 impact would be to make the tuning in the MSSM with a $20$ TeV cutoff
@@
 \includegraphics{mssm_chargino_plot.png}}%%
-\caption{Scatter plot of fine tuning vs lightest Higgs mass in the MSSM with $m_{\chi^\pm_1} = 200$ GeV shown in green 
-(bottom band) $m_{\chi^\pm_1} = 500$ GeV in blue (middle band) and $m_{\chi^\pm_1} = 700$ GeV in red
+\caption{Scatter plot of fine tuning vs lightest Higgs mass in the MSSM with $m_{\tilde{\chi}^\pm_1} = 200$ GeV shown in green 
+(bottom band) $m_{\tilde{\chi}^\pm_1} = 500$ GeV in blue (middle band) and $m_{\tilde{\chi}^\pm_1} = 700$ GeV in red
 (top band).}

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Removed an unused definition in the appendix on RGE contributions
Added start of gauge coupling beta functions to appendix

@@
 parameters that must be considered are $\lambda$, $A_\lambda$,
-$m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and $g_1'$. The
-one- and two-loop contributions to the $\beta$ function for $\lambda$
+$m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and $g_1'$. Neglecting kinetic
+mixing, the two-loop $\beta$ functions for the gauge couplings read
+\begin{subequations}\label{eq:USSMGaugeBetas}
+\begin{align}
+\beta_{g_1}^{(1)}&=\frac{48}{5}g_1^3,\label{eq:USSMg1BetaOneLoop}\\
+\beta_{g_1}^{(2)}&=\frac{2}{25},\label{eq:USSMg1BetaTwoLoop}\\
+\beta_{g_2}^{(1)}&=4g_2^3,\label{eq:USSMg2BetaOneLoop}\\
+\beta_{g_3}^{(1)}&=0,\label{eq:USSMg3BetaOneLoop}\\
+\beta_{g_1'}^{(1)}&=g_1'^3\Sigma_{\tilde{Q}},\label{eq:USSMg1pBetaOneLoop}
+\end{align}
+\end{subequations}
+In order to keep our expressions compact we have used the notation
+\begin{align*}
+\Sigma_{\tilde{Q}}=\sum_i \tilde{Q}_i^2
+\end{align*}
+to denote the trace over the $U(1)'$ charges, and
+\begin{align*}
+\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i\\
+&=-3\tilde{Q}_1+3\tilde{Q}_2+3\tilde{Q}_d-3\tilde{Q}_D+3\tilde{Q}_e-3\tilde{Q}_L+3\tilde{Q}_Q-6\tilde{Q}_u+3\tilde{Q}_{\overline{D}}+\tilde{Q}_{\overline{H'}}-\tilde{Q}_{H'}.
+\end{align*}
+Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised.\\ \\
+The one- and two-loop contributions to the $\beta$ function for $\lambda$
 are
@@
 \end{equation*}
-Additionally, in order to keep our expressions compact we also use the notation
-\begin{align*}
-\Sigma_{\tilde{Q}}=\sum_i \tilde{Q}_i^2, \qquad \Pi_{\tilde{Q}}=\sum_i \tilde{Q}_i^4
-\end{align*}
-to denote sums over the $U(1)'$ charges, and
-\begin{align*}
-\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i\\
-&=-3\tilde{Q}_1+3\tilde{Q}_2+3\tilde{Q}_d-3\tilde{Q}_D+3\tilde{Q}_e-3\tilde{Q}_L+3\tilde{Q}_Q-6\tilde{Q}_u+3\tilde{Q}_{\overline{D}}+\tilde{Q}_{\overline{H'}}-\tilde{Q}_{H'}.
-\end{align*}
-Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised.
 % NB before submission replace this with a copy-paste of the bbl file?

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Removed a comma, made sure abbreviations are defined in the abstract

@@
 The discovery of a 125 GeV Higgs boson and rising lower bounds on the
-masses of superpartners, have lead to concerns that supersymmetric
+masses of superpartners have lead to concerns that supersymmetric
 models are now fine tuned.  Large stop masses, required for a $125$
-GeV Higgs, feed into the EWSB conditions through renormalisation group
-equations forcing one to fine tune these parameters to obtain the
-correct electroweak vacuum expectation value.  Nonetheless this fine
-tuning depends crucially on our assumptions about the SUSY breaking
-scale.  At the same time U(1) extensions provide the most compelling
-solution to the $\mu$-problem, which is also a naturalness issue.
-These very well motivated supersymmetric models predict a new
-$Z^\prime$ boson which could be discovered at the LHC and the
+GeV Higgs, feed into the electroweak symmetry breaking conditions 
+through renormalisation group equations forcing one to fine tune these 
+parameters to obtain the correct electroweak vacuum expectation value.  
+Nonetheless this fine tuning depends crucially on our assumptions about 
+the supersymmetry (SUSY) breaking scale.  At the same time U(1) extensions
+provide the most compelling solution to the $\mu$-problem, which is also 
+a naturalness issue. These very well motivated supersymmetric models 
+predict a new $Z^\prime$ boson which could be discovered at the LHC and the
 naturalness of the model requires that the $Z^\prime$ boson mass
@@
 about the SUSY breaking mechanism.  Here we study this fine tuning for
-several $U(1)$ supersymmetric extensions of the standard model and
+several $U(1)$ supersymmetric extensions of the Standard Model and
 compare it to the situation in the MSSM where the most direct tree

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Removed abbreviations from abstract, might be easier, and capitalised Standard Model

@@
 Nonetheless this fine tuning depends crucially on our assumptions about 
-the supersymmetry (SUSY) breaking scale.  At the same time U(1) extensions
+the supersymmetry breaking scale.  At the same time U(1) extensions
 provide the most compelling solution to the $\mu$-problem, which is also 
@@
 appears at the tree level, making it less dependent on assumptions
-about the SUSY breaking mechanism.  Here we study this fine tuning for
+about the supersymmetry breaking mechanism.  Here we study this fine tuning for
 several $U(1)$ supersymmetric extensions of the Standard Model and
@@
 \cite{Aad:2012tfa,Chatrchyan:2012ufa} at the Large Hadron Collider
-(LHC) has interesting implications for physics beyond the standard
-model (SM) and supersymmetry (SUSY).  On the one hand it provides a
+(LHC) has interesting implications for physics beyond the Standard
+Model (SM) and supersymmetry (SUSY).  On the one hand it provides a
 light Higgs boson, as expected from supersymmetry, and

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Tried changing a 'nonetheless' to 'despite this' in the Introduction, added in what looked like a missing 'the'

@@
 $M_Z$. The dominant higher order corrections to the Higgs mass come
-from stops and to obtain a $125$ GeV Higgs they need be rather
+from stops and to obtain a $125$ GeV Higgs they need to be rather
 heavy. Heavy stops will provide a large contribution to the low energy
@@
 electroweak symmetry breaking conditions at tree level
-\cite{Athron:2013ipa}.  Nonetheless the constrained version of
-E$_6$SSM (cE$_6$SSM) \cite{Athron:2009ue, Athron:2009bs} still turned
-out to be significantly less tuned than the cMSSM.
+\cite{Athron:2013ipa}. Despite this the constrained version of
+the E$_6$SSM (cE$_6$SSM) \cite{Athron:2009ue, Athron:2009bs} was still found
+to be significantly less tuned than the cMSSM.
 

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Added another missing 'the'

@@
 In this paper we investigate how big this tuning is if we bring this
-scale all the way down to 20 TeV, effectively minimising contribution
+scale all the way down to 20 TeV, effectively minimising the contribution
 from the stops. We find that the $Z^\prime$ limit is enough to already

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Removed a stray apostrophe (chargino's --> charginos)
Defined NMSSM

@@
 comparable to the situation in the MSSM defined at the same scale if
-chargino's could be ruled out below $700$ GeV.  We then show how this
+charginos could be ruled out below $700$ GeV.  We then show how this
 tuning from the $Z^\prime$ mass looks for different $U(1)$ extensions,
@@
   Kim:2013uxa} suppressing the posterior.  Indeed in the MSSM and
-NMSSM if one transforms GUT scale parameters to the VEVs, the inverse
+the next-to-MSSM (NMSSM) if one transforms GUT scale parameters to the VEVs, the inverse
 of the Jacobian for this transformation looks quite like the

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Changed subsections to sections

@@
 numerical procedure we use to obtain our results is given in
-\ref{subsec:numericalprocedure} and then the results are specified in
+\ref{sec:numericalprocedure} and then the results are specified in
 section \ref{sec:results}.
@@
 % FlexibleSUSY (cite FlexibleSUSY and SARAH).
-\subsection{\label{subsec:tuningmeasure}The Fine Tuning Measure}
+\section{\label{sec:tuningmeasure}The Fine Tuning Measure}
 As stated above, to quantify the resulting fine tuning we
@@
 presented in Appendix \ref{app:rges}.
-\subsection{\label{subsec:numericalprocedure}Numerical Procedure}
+\section{\label{sec:numericalprocedure}Numerical Procedure}
 Using the approach outlined above, we are able to scan the low energy

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Fixed some typos, made the SU(2) dot products explicit, hopefully introduced a correct and consistent ordering for the dot products as well (with the right signs etc.)

@@
 superpotential terms required in the USSM, \be W_{USSM} = y^U_{ij}
-\hat{u}^c_i \hat{H}_u \hat{Q}_j + y^D_{ij} \hat{d}^c_i \hat{H}_d
-\hat{Q}_j + y^E_{ij} \hat{e}^c_i \hat{H}_d \hat{L}_j + \lambda \hat{S}
-\hat{H}_d \hat{H}_u, \ee with $i,j \in \{1,2,3\}$.
+\hat{u}^c_i \left ( \hat{H}_u \cdot \hat{Q}_j \right ) + y^D_{ij} \hat{d}^c_i 
+\left ( \hat{Q}_j \cdot \hat{H}_d \right )
+ + y^E_{ij} \hat{e}^c_i \left ( \hat{L}_j \cdot \hat{H}_d \right ) + \lambda \hat{S}
+\left ( \hat{H}_d \cdot \hat{H}_u \right ), \ee with $i,j \in \{1,2,3\}$. 
+For the $SU(2)$ dot product we follow the convention $\hat{A}\cdot \hat{B}\equiv \epsilon_{\alpha\beta}\hat{A}^\alpha\hat{B}^\beta=\hat{A}^2\hat{B}^1-\hat{A}^1\hat{B}^2$.
 
@@
 gauge symmetry that can be obtained from the break down of the $E_6$
-gauge symmetry which is anomaly free and have all matter that fill the
+gauge symmetry which is anomaly free and have all matter fields that fill the
 three generations of $27$-plet representations of $E_6$ survive down to
@@
 \cite{Hesselbach:2001ri, Barger:2005hb, Choi:2006fz,
-  Barger:2007nv};the relic abundance of dark matter
+  Barger:2007nv}; the relic abundance of dark matter
 \cite{Kalinowski:2008iq}; GUT scale family symmetries which can
@@
 is $U(1)_N$, under which the right handed neutrino remains
-interaction-less. This is the case in the the exceptional
-supersymmetric standard models (E$_6$SSM)
+interaction-less. This is the case in the E$_6$SSM
 \cite{King:2005jy,King:2005my,Athron:2010zz}, and closely-related
@@
 scenarios known as the EZSSM \cite{Hall:2011zq} where the inert
-singlinos, which cause these problems are entirely decoupled and the
+singlinos that cause these problems are entirely decoupled and the
 relic abundance is fitted with a bino-like candidate with a novel
@@
 case is to make the singlinos extremely light hot dark matter
-candidate and explains almost all the relic abundance density with
+candidates and explains almost all the relic abundance density with
+\textbf{[***How does this sentence end? Or is the with not meant to be there?***]}
 
@@
   Sperling:2013xqa}.  The particle spectrum and collider signatures of
-constrained version of the E$_6$SSM have been studied in a series of
+the cE$_6$SSM have been studied in a series of
 papers,
@@
 threshold corrections to the $\overline{DR}$ gauge and Yukawa
-couplings in the E$_6$SSM were calculated and the numerical impact in
+couplings in the E$_6$SSM have also been calculated and their numerical impact in
 the constrained version examined \cite{Athron:2012pw}.
@@
 \be
-W_{E6} = W_0 + W_1 + W_2,
+W_{E_6} = W_0 + W_1 + W_2,
 \label{Eq:e6-superpot}
@@
 \begin{eqnarray}
-W_0 &=& \lambda_{ijk} \hat{S}_i \hat{H}^d_{j} \hat{H}^u_{k} + \kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\bar{D}}_k + h^N_{ijk} \hat{N}^c_i \hat{H}^u_{j} \hat{L}_k \nonumber \\
-& & + h^U_{ijk} \hat{u}^c_i \hat{H}^u_{j} \hat{Q}_k + h^D_{ijk} \hat{d}^c_i \hat{H}^d_{j} \hat{Q}_k + h^E_{ijk} \hat{e}^c_i \hat{H}^d_{j} \hat{L}_k, \\
-W_1 &=& g^Q_{ijk} \hat{D}_i \hat{Q}_j \hat{Q}_k + g^q_{ijk} \hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k, \\
-W_2 &=& g^N_{ijk} \hat{N}^c_i \hat{D}_j \hat{d}^c_k + g^E_{ijk} \hat{e}^c_i \hat{D}_j \hat{u}^c_k + g^D_{ijk} \hat{Q}_i \hat{L}_j \hat{\bar{D}}_k.
+W_0 &=& \lambda_{ijk} \hat{S}_i \left ( \hat{H}^d_{j} \cdot\hat{H}^u_{k}\right ) + \kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\bar{D}}_k + h^N_{ijk} \hat{N}^c_i \left ( \hat{H}^u_{j} \cdot \hat{L}_k\right ) \nonumber \\
+& & + h^U_{ijk} \hat{u}^c_i \left ( \hat{H}^u_{j} \cdot \hat{Q}_k\right ) + h^D_{ijk} \hat{d}^c_i \left ( \hat{Q}_k\cdot\hat{H}^d_{j}\right )  + h^E_{ijk} \hat{e}^c_i \left ( \hat{L}_k\cdot\hat{H}^d_{j}\right ) , \\
+W_1 &=& g^Q_{ijk} \hat{D}_i \left ( \hat{Q}_j \cdot \hat{Q}_k \right )+ g^q_{ijk} \hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k, \\
+W_2 &=& g^N_{ijk} \hat{N}^c_i \hat{D}_j \hat{d}^c_k + g^E_{ijk} \hat{e}^c_i \hat{D}_j \hat{u}^c_k + g^D_{ijk} \left ( \hat{Q}_i \cdot \hat{L}_j \right )\hat{\bar{D}}_k.
 \label{Eq:e6-superpot-parts}
@@
     \ba
-    W &\approx& - y_{\tau} (\SuperField{H}_d
-    \SuperField{L}_3) \SuperField{e}^C_3 - y_b (\SuperField{H}_d
-    \SuperField{Q}_3) \SuperField{d}_3^C - y_t (\SuperField{Q}_3
-    \SuperField{H}_u) \SuperField{u}_3^C\\
+    W &\approx& y_{\tau} \left (\SuperField{L}_3 \cdot \SuperField{H}_d
+     \right ) \SuperField{e}^C_3 + y_b \left (\SuperField{Q}_3\cdot\SuperField{H}_d
+     \right ) \SuperField{d}_3^C + y_t \left (\SuperField{H}_u\cdot\SuperField{Q}_3
+     \right ) \SuperField{u}_3^C\\
     &&
-    + \lambda_i \SuperField{S} (\SuperField{H}_{1i}
-    \SuperField{H}_{2i}) + \kappa_i \SuperField{S} \SuperField{D}_i
-    \SuperField{\overline{D}}_i + \mu' (\SuperField{H}'
-    \SuperField{\overline{H'}}),
+    + \lambda_i \SuperField{S} \left (\SuperField{H}_{1i}
+    \cdot \SuperField{H}_{2i} \right ) + \kappa_i \SuperField{S} \SuperField{D}_i
+    \SuperField{\overline{D}}_i + \mu' \left (\SuperField{H}'\cdot
+    \SuperField{\overline{H'}}\right ),
     \ea
@@
 $\tilde{Q}_2$ and $\tilde{Q}_S$ are effective $U(1)'$ charges for
-$H_1$, $H_2$ and $S$, respectively. Note that the $SU(2)$ dot product
-is defined by $A\cdot B\equiv \epsilon_{\alpha\beta}A^\alpha
-B^\beta=A^2B^1-A^1B^2$. The term $\Delta V$ contains the
+$H_1$, $H_2$ and $S$, respectively. The term $\Delta V$ contains the
 Coleman-Weinberg contributions to the effective potential. In the case

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Fixed a typo

@@
 was studied in \cite{Rizzo:2012rf}.  The E$_6$SSM was also included in
-a studies looking at how first or second generation sfermion masses
+studies looking at how first or second generation sfermion masses
 can be used to constrain the GUT scale parameters \cite{Miller:2012vn}

### 2015-01-29 paper/e6ssm-tuning-paper.tex
Completed sentence that had end missing (I think the completion is correct, the relic density is accounted for by the ordinary neutralino?)

@@
 case is to make the singlinos extremely light hot dark matter
-candidates and explains almost all the relic abundance density with
-\textbf{[***How does this sentence end? Or is the with not meant to be there?***]}
+candidates and accounts for almost all the relic abundance density with
+the lightest ordinary neutralino.
 
@@
 % NB before submission replace this with a copy-paste of the bbl file?
+\bibliographystyle{apsrev4-1}
 \bibliography{bibliography}{}

### 2015-01-29 paper/e6ssm-tuning-paper.tex
Made figure boxes a little bit larger for plot of MSSM tuning as function of stop and Higgs mass, italicised 'Left panel

@@
 \begin{center}
-\resizebox{!}{6cm}{%
+\resizebox{!}{6.1cm}{%
 \includegraphics{mssm_stop_tuning.png}}
-\resizebox{!}{6cm}{%
+\resizebox{!}{6.1cm}{%
 \includegraphics{mssm_higgs_tuning.png}}
-\caption{Left panel: Scatter plot of fine tuning in the MSSM as a function of
+\caption{{\it Left panel:} Scatter plot of fine tuning in the MSSM as a function of
 the lightest stop mass, $m_{\tilde{t}_1}$, for the cutoff scales (from 
 bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV. 
-Right panel: Scatter plot of fine tuning in the MSSM as a function of
+{\it Right panel:} Scatter plot of fine tuning in the MSSM as a function of
 the lightest Higgs mass, $m_{h_1}$, for the cutoff scales (from 

### 2015-01-30 fs-spectrum/models/lowE6SSM/fill_scan_lowE6SSM.cpp
Added small scan routine for filling in plots

@@ -1,0 +1,744 @@
+// ====================================================================
+// Calculates the fine tuning at a set of points centred on 
+// read in points. For reference:
+// ====================================================================
+
+#include "lowE6SSM_input_parameters.hpp"
+#include "lowE6SSM_spectrum_generator.hpp"
+#include "lowE6SSM_two_scale_tuning_calculator.hpp"
+
+#include "error.hpp"
+#include "scan.hpp"
+#include "lowe.h"
+
+#include <boost/algorithm/string.hpp>
+#include <boost/lexical_cast.hpp>
+
+#include <chrono>
+#include <iostream>
+#include <map>
+#include <random>
+
+namespace flexiblesusy {
+   void initialize_e6_charges(double theta, lowE6SSM_input_parameters& input)
+   {
+      input.QQp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::QL, theta);
+      input.QLp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::LL, theta);
+      input.QH1p = lowE6SSM_info::get_e6_charge(lowE6SSM_info::Hd, theta);
+      input.QH2p = lowE6SSM_info::get_e6_charge(lowE6SSM_info::Hu, theta);
+      input.Qdp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::dR, theta);
+      input.Qup = lowE6SSM_info::get_e6_charge(lowE6SSM_info::uR, theta);
+      input.Qep = lowE6SSM_info::get_e6_charge(lowE6SSM_info::eR, theta);
+      input.QSp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::S, theta);
+      input.QDxp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::Dx, theta);
+      input.QDxbarp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::Dxbar, theta);
+      input.QHpp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::Hp, theta);
+      input.QHpbarp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::Hpbar, theta);
+}
+
+   void initialize_model_from_input(lowE6SSM_input_parameters input, lowE6SSM<Two_scale>& model)
+   {
+      const auto Yd = model.get_Yd();
+      const auto Ye = model.get_Ye();
[…]

### 2015-01-30 fs-spectrum/models/lowE6SSM/fill_scan_lowE6SSM.cpp
Reduced width of A_t interval from +/- 10000 to +/- 1000

@@ -560,7 +560,7 @@ int main()
          
          // generate additional points from read-in point
          const double ALambdax_width = 1000.0;
-         const double AYu22_width = 10000.0;
+         const double AYu22_width = 1000.0;
 
          for (std::size_t i = 0; i < num_points; ++i) {
             lowE6SSM_input_parameters random_input = input;

### 2015-01-31 fs-spectrum/models/lowE6SSM/full_tuning_scan_lowE6SSM.cpp
Changed value of theta for full tuning scan

@@ -42,8 +42,8 @@ namespace flexiblesusy {
       // U(1)_N: theta = ArcTan(Sqrt(15.0))
       // U(1)_I: theta = PI + ArcTan(Sqrt(0.6))
       // U(1)_psi: theta = 0.5 * PI
-
-      const double theta = 0.5 * PI;
+      // U(1)_eta: theta = -ArcTan(Sqrt(5.0 / 3.0))
+      const double theta = PI + ArcTan(Sqrt(0.6));
       
       initialize_e6_charges(theta, input);
       

### 2015-01-31 paper/e6ssm-tuning-paper.tex
Updated general U(1) plots, updated caption in the corresponding figure (which may be a bit awkwardly written, might consider rewriting), and changed occurrences of \it to \textit

@@
 \includegraphics{mssm_higgs_tuning.png}}
-\caption{{\it Left panel:} Scatter plot of fine tuning in the MSSM as a function of
+\caption{\textit{Left panel:} Scatter plot of fine tuning in the MSSM as a function of
 the lightest stop mass, $m_{\tilde{t}_1}$, for the cutoff scales (from 
 bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV. 
-{\it Right panel:} Scatter plot of fine tuning in the MSSM as a function of
+\textit{Right panel:} Scatter plot of fine tuning in the MSSM as a function of
 the lightest Higgs mass, $m_{h_1}$, for the cutoff scales (from 
@@
 \begin{center}
-\resizebox{!}{5cm}{%
+\resizebox{!}{6.1cm}{%
 \includegraphics{e6inert_tb10_tuning_vs_higgs.png}}
-\resizebox{!}{5cm}{%
+\resizebox{!}{6.1cm}{%
 \includegraphics{e6psi_tb10_tuning_vs_higgs.png}}\\
-\resizebox{!}{5cm}{%
+\resizebox{!}{6.1cm}{%
 \includegraphics{e6eta_tb10_tuning_vs_higgs.png}}%%
-\caption{Scatter plot of fine tuning vs lightest Higgs mass in ... with $M_{Z^\prime} = 2.5$ TeV shown in blue
-(bottom band) and $M_{Z^\prime} = 4.5$ TeV in red (top band).}
+\caption{\textit{Top left panel:} Scatter plot of the fine tuning vs lightest Higgs mass in the $U(1)_I$ model.
+\textit{Top right panel:} Scatter plot of the fine tuning vs lightest Higgs mass in the $U(1)_\psi$ model.
+\textit{Bottom panel:} Scatter plot of the fine tuning vs lightest Higgs mass in the $U(1)_\eta$ model.
+In each plot points with $M_{Z^\prime} = 2.5$ TeV are shown in blue
+(bottom band), and points with $M_{Z^\prime} = 4.5$ TeV are shown in red (top band).}
 \label{Fig:othere6modelsvsmssm}
@@
 \includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_BM2_all_tuning_data.png}}%%
-\caption{{\it Top panel:} Scatter plot of the fine tuning as a function of the cutoff scale $M_X$ for the four benchmark points given in Table \ref{tab:benchmarks}.
-{\it Middle left panel:}  Individual sensitivities for MSSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the green line in the top panel.
-{\it Middle right panel:} Individual sensitivities for E$_6$SSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the blue line in the top panel.
-{\it Bottom left panel:} Individual sensitivities for MSSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the yellow line in the top panel.
-{\it Bottom right panel:} Individual sensitivities for E$_6$SSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the red line in the top panel.
+\caption{\textit{Top panel:} Scatter plot of the fine tuning as a function of the cutoff scale $M_X$ for the four benchmark points given in Table \ref{tab:benchmarks}.
+\textit{Middle left panel:}  Individual sensitivities for MSSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the green line in the top panel.
+\textit{Middle right panel:} Individual sensitivities for E$_6$SSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the blue line in the top panel.
+\textit{Bottom left panel:} Individual sensitivities for MSSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the yellow line in the top panel.
+\textit{Bottom right panel:} Individual sensitivities for E$_6$SSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the red line in the top panel.
 }

### 2015-02-01 paper/e6ssm-tuning-paper.tex
Added Adelaide pre-preprint number to paper, ADP-15-4/T906
Added brief acknowledgements to start with, should there be anyone else added to them?
Added in 2-loop betas for gauge couplings

@@
                               %display desired
+\preprint{ADP-15-4/T906}
 \maketitle
@@
 
-% Our conclusions: at low scales stops are not a big contributor,
-% Z' causes a significant fine tuning in the E6SSM (dominant -> lower
-% bound), chargino bounds will be important for fine tuning in the MSSM
-% but not as much for the E6SSM, and possibly discuss different U(1)' charges.
+\acknowledgements
+We would like to thank R.
+Nevzorov for many useful discussions and comments.
+DH would also like to thank A.
+Ismail and T.
+Rizzo.
+This work was supported by the University of Adelaide and by the ARC Centre of Excellence for Particle Physics at the Terascale.
+
 \appendix
@@
 $m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and $g_1'$. Neglecting kinetic
-mixing, the two-loop $\beta$ functions for the gauge couplings read
+mixing, the two-loop $\beta$ functions for the relevant gauge couplings read
 \begin{subequations}\label{eq:USSMGaugeBetas}
@@
 \beta_{g_1}^{(1)}&=\frac{48}{5}g_1^3,\label{eq:USSMg1BetaOneLoop}\\
-\beta_{g_1}^{(2)}&=\frac{2}{25},\label{eq:USSMg1BetaTwoLoop}\\
+\beta_{g_1}^{(2)}&=\frac{2}{25} g_1^3 \left(30 g_1'^2 \Pi_{\tilde{Q}}^Y-35 y_b^2+117 g_1^2+135 g_2^2+300 g_3^2-10 \Sigma _{\kappa }-15
+   \Sigma _{\lambda }-65 y_t^2-45 y_{\tau }^2\right),\label{eq:USSMg1BetaTwoLoop}\\
 \beta_{g_2}^{(1)}&=4g_2^3,\label{eq:USSMg2BetaOneLoop}\\
-\beta_{g_3}^{(1)}&=0,\label{eq:USSMg3BetaOneLoop}\\
-\beta_{g_1'}^{(1)}&=g_1'^3\Sigma_{\tilde{Q}},\label{eq:USSMg1pBetaOneLoop}
+\beta_{g_2}^{(2)}&=\frac{2}{5} g_2^3 \left(5 g_1'^2 \Pi _{\tilde{Q}}^L-15 y_b^2+9 g_1^2+115 g_2^2+60 g_3^2-5 \Sigma _{\lambda }-15
+   y_t^2-5 y_{\tau }^2\right),\label{eq:USSMg2BetaTwoLoop}\\
+\beta_{g_1'}^{(1)}&=g_1'^3\Sigma_{\tilde{Q}},\label{eq:USSMg1pBetaOneLoop}\\
+\beta_{g_1'}^{(2)}&=\frac{2}{5} g_1'^3 \left(-15 \Sigma _{\kappa } \left(\tilde{Q}_{\bar{D}}^2+\tilde{Q}_D^2+\tilde{Q}_S^2\right)-30
+   y_b^2 \left(\tilde{Q}_d^2+\tilde{Q}_1^2+\tilde{Q}_Q^2\right)+120 g_3^2 \Pi _{\tilde{Q}}^C\right.\nonumber \\
+&\quad{}-10 y_{\tau }^2
+   \left(\tilde{Q}_e^2+\tilde{Q}_L^2+\tilde{Q}_1^2\right)+15 g_2^2 \Pi _{\tilde{Q}}^L+10 g_1'^2 \Pi _{\tilde{Q}}+6
+   g_1^2 \Pi _{\tilde{Q}}^Y\nonumber\\
+&\quad\left.{}-10 \Sigma _{\lambda } \left(\tilde{Q}_S^2+\tilde{Q}_1^2+\tilde{Q}_2^2\right)-30 y_t^2
+   \left(\tilde{Q}_u^2+\tilde{Q}_2^2+\tilde{Q}_Q^2\right)\right).\label{eq:USSMg1pBetaTwoLoop}
 \end{align}
@@
 \end{align*}
-to denote the trace over the $U(1)'$ charges, and
+to denote the trace over the $U(1)'$ charges, along with
 \begin{align*}
-\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i\\
-&=-3\tilde{Q}_1+3\tilde{Q}_2+3\tilde{Q}_d-3\tilde{Q}_D+3\tilde{Q}_e-3\tilde{Q}_L+3\tilde{Q}_Q-6\tilde{Q}_u+3\tilde{Q}_{\overline{D}}+\tilde{Q}_{\overline{H'}}-\tilde{Q}_{H'}.
+\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i,\\
+\Pi_{\tilde{Q}}&=\sum_i \tilde{Q}_i^4,\\
+\Pi_{\tilde{Q}}^Y&=\sum_i \left ( \sqrt{\frac{5}{3}}Q_i^Y\right )^2\tilde{Q}_i^2,\\
+\Pi_{\tilde{Q}}^L&=3\tilde{Q}_1^2+3\tilde{Q}_2^2+\tilde{Q}_{H'}^2+\tilde{Q}_{\overline{H'}}^2+3\tilde{Q}_L^2+9\tilde{Q}_Q^2,\\
+\Pi_{\tilde{Q}}^C&=\tilde{Q}_d^2+\tilde{Q}_D^2+\tilde{Q}_{\overline{D}}^2+2\tilde{Q}_Q^2+\tilde{Q}_u^2.
 \end{align*}
-Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised.\\ \\
+Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised. Similarly we have set
+\begin{equation*}
+\Sigma_\lambda=\lambda_1^2+\lambda_2^2+\lambda_3^2, \qquad \Sigma_\kappa=\kappa_1^2+\kappa_2^2+\kappa_3^2.
+\end{equation*}
+The corresponding $O(t^2)$ coefficients for the gauge couplings are simply
+\begin{subequations}\label{eq:USSMGaugeOt2Coeffs}
+\begin{align}
+b_{g_1}^{(2)}&=\frac{3456}{25}g_1^5,\label{eq:USSMg1Ot2Coeff}\\
+b_{g_2}^{(2)}&=24g_2^5,\label{eq:USSMg2Ot2Coeff}\\
+b_{g_1'}^{(2)}&=\frac{3}{2}g_1'^5\Sigma_{\tilde{Q}}^2.\label{eq:USSMg1pOt2Coeff}
+\end{align}
+\end{subequations}
 The one- and two-loop contributions to the $\beta$ function for $\lambda$
@@
 &{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2\tilde{Q}_1^4+2\tilde{Q}_2^4+2\tilde{Q}_S^4+\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\Sigma_{\tilde{Q}}\right ]\nonumber\\
-&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [\tilde{Q}_1^2+\tilde{Q}_2^2+\left ( \tilde{Q}_2-\tilde{Q}_1\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}
+&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [\tilde{Q}_1^2+\tilde{Q}_2^2+\left ( \tilde{Q}_2-\tilde{Q}_1\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \}.\label{eq:USSMLambdaBetaTwoLoop}
 \end{align}
 \end{subequations}
-where
-\begin{equation*}
-\Sigma_\lambda=\lambda_1^2+\lambda_2^2+\lambda_3^2, \qquad \Sigma_\kappa=\kappa_1^2+\kappa_2^2+\kappa_3^2.
-\end{equation*}
 % NB before submission replace this with a copy-paste of the bbl file?

### 2015-02-01 paper/g1_coefficients.m
Added Mathematica files with RGEs and 1-loop squared coefficients, note that the last element of each list is 2 * b, where b is the coefficient given in the paper

@@ -1,0 +1,13 @@
+(* Created with the Wolfram Language for Students - Personal Use Only : www.wolfram.com *)
+{g1, (48*g1^3)/5, (2*g1^3*(117*g1^2 + 135*g2^2 + 300*g3^2 - 
+    10*(Kappa00^2 + Kappa01^2 + Kappa02^2 + Kappa10^2 + Kappa11^2 + 
+      Kappa12^2 + Kappa20^2 + Kappa21^2 + Kappa22^2) - 
+    15*(Lambda1200^2 + Lambda1201^2 + Lambda1210^2 + Lambda1211^2) - 
+    15*Lambdax^2 + 30*gN^2*Qdp^2 + 30*gN^2*QDxbarp^2 + 30*gN^2*QDxp^2 + 
+    90*gN^2*Qep^2 + 45*gN^2*QH1p^2 + 45*gN^2*QH2p^2 + 15*gN^2*QHpbarp^2 + 
+    15*gN^2*QHpp^2 + 45*gN^2*QLp^2 + 15*gN^2*QQp^2 + 120*gN^2*Qup^2 - 
+    35*(Yd00^2 + Yd01^2 + Yd02^2 + Yd10^2 + Yd11^2 + Yd12^2 + Yd20^2 + 
+      Yd21^2 + Yd22^2) - 45*(Ye00^2 + Ye01^2 + Ye02^2 + Ye10^2 + Ye11^2 + 
+      Ye12^2 + Ye20^2 + Ye21^2 + Ye22^2) - 
+    65*(Yu00^2 + Yu01^2 + Yu02^2 + Yu10^2 + Yu11^2 + Yu12^2 + Yu20^2 + 
+      Yu21^2 + Yu22^2)))/25, (6912*g1^5)/25}

### 2015-02-01 paper/g2_coefficients.m

@@ -1,0 +1,10 @@
+(* Created with the Wolfram Language for Students - Personal Use Only : www.wolfram.com *)
+{g2, 4*g2^3, (2*g2^3*(9*g1^2 + 115*g2^2 + 60*g3^2 - 
+    5*(Lambda1200^2 + Lambda1201^2 + Lambda1210^2 + Lambda1211^2) - 
+    5*Lambdax^2 + 15*gN^2*QH1p^2 + 15*gN^2*QH2p^2 + 5*gN^2*QHpbarp^2 + 
+    5*gN^2*QHpp^2 + 15*gN^2*QLp^2 + 45*gN^2*QQp^2 - 
+    15*(Yd00^2 + Yd01^2 + Yd02^2 + Yd10^2 + Yd11^2 + Yd12^2 + Yd20^2 + 
+      Yd21^2 + Yd22^2) - 5*(Ye00^2 + Ye01^2 + Ye02^2 + Ye10^2 + Ye11^2 + 
+      Ye12^2 + Ye20^2 + Ye21^2 + Ye22^2) - 
+    15*(Yu00^2 + Yu01^2 + Yu02^2 + Yu10^2 + Yu11^2 + Yu12^2 + Yu20^2 + 
+      Yu21^2 + Yu22^2)))/5, 48*g2^5}

### 2015-02-01 paper/gN_coefficients.m

@@ -1,0 +1,35 @@
+(* Created with the Wolfram Language for Students - Personal Use Only : www.wolfram.com *)
+{gN, gN^3*(9*Qdp^2 + 9*QDxbarp^2 + 9*QDxp^2 + 3*Qep^2 + 6*QH1p^2 + 6*QH2p^2 + 
+   2*QHpbarp^2 + 2*QHpp^2 + 6*QLp^2 + 18*QQp^2 + 3*QSp^2 + 9*Qup^2), 
+ (2*gN^3*(6*g1^2*Qdp^2 + 120*g3^2*Qdp^2 + 90*gN^2*Qdp^4 + 6*g1^2*QDxbarp^2 + 
+    120*g3^2*QDxbarp^2 - 15*(Kappa00^2 + Kappa01^2 + Kappa02^2 + Kappa10^2 + 
+      Kappa11^2 + Kappa12^2 + Kappa20^2 + Kappa21^2 + Kappa22^2)*QDxbarp^2 + 
+    90*gN^2*QDxbarp^4 + 6*g1^2*QDxp^2 + 120*g3^2*QDxp^2 - 
+    15*(Kappa00^2 + Kappa01^2 + Kappa02^2 + Kappa10^2 + Kappa11^2 + 
+      Kappa12^2 + Kappa20^2 + Kappa21^2 + Kappa22^2)*QDxp^2 + 
+    90*gN^2*QDxp^4 + 18*g1^2*Qep^2 + 30*gN^2*Qep^4 + 9*g1^2*QH1p^2 + 
+    45*g2^2*QH1p^2 - 10*(Lambda1200^2 + Lambda1201^2 + Lambda1210^2 + 
+      Lambda1211^2)*QH1p^2 + 60*gN^2*QH1p^4 + 9*g1^2*QH2p^2 + 
+    45*g2^2*QH2p^2 - 10*(Lambda1200^2 + Lambda1201^2 + Lambda1210^2 + 
+      Lambda1211^2)*QH2p^2 + 60*gN^2*QH2p^4 + 3*g1^2*QHpbarp^2 + 
+    15*g2^2*QHpbarp^2 + 20*gN^2*QHpbarp^4 + 3*g1^2*QHpp^2 + 15*g2^2*QHpp^2 + 
[…]

### 2015-02-01 paper/lambda_coefficients.m

@@ -1,0 +1,554 @@
+(* Created with the Wolfram Language for Students - Personal Use Only : www.wolfram.com *)
+{Lambdax, (-3*g1^2*Lambdax)/5 - 3*g2^2*Lambdax + 
+  3*(Kappa00^2 + Kappa01^2 + Kappa02^2 + Kappa10^2 + Kappa11^2 + Kappa12^2 + 
+    Kappa20^2 + Kappa21^2 + Kappa22^2)*Lambdax + 
+  2*(Lambda1200^2 + Lambda1201^2 + Lambda1210^2 + Lambda1211^2)*Lambdax + 
+  4*Lambdax^3 - 2*gN^2*Lambdax*QH1p^2 - 2*gN^2*Lambdax*QH2p^2 - 
+  2*gN^2*Lambdax*QSp^2 + 3*Lambdax*(Yd00^2 + Yd01^2 + Yd02^2 + Yd10^2 + 
+    Yd11^2 + Yd12^2 + Yd20^2 + Yd21^2 + Yd22^2) + 
+  Lambdax*(Ye00^2 + Ye01^2 + Ye02^2 + Ye10^2 + Ye11^2 + Ye12^2 + Ye20^2 + 
+    Ye21^2 + Ye22^2) + 3*Lambdax*(Yu00^2 + Yu01^2 + Yu02^2 + Yu10^2 + 
+    Yu11^2 + Yu12^2 + Yu20^2 + Yu21^2 + Yu22^2), 
+ -(Lambdax*(-297*g1^4 - 90*g1^2*g2^2 - 825*g2^4 - 
+     40*g1^2*(Kappa00^2 + Kappa01^2 + Kappa02^2 + Kappa10^2 + Kappa11^2 + 
+       Kappa12^2 + Kappa20^2 + Kappa21^2 + Kappa22^2) - 
+     800*g3^2*(Kappa00^2 + Kappa01^2 + Kappa02^2 + Kappa10^2 + Kappa11^2 + 
+       Kappa12^2 + Kappa20^2 + Kappa21^2 + Kappa22^2) + 
+     300*(Kappa00*(Kappa00*(Kappa00^2 + Kappa01^2 + Kappa02^2) + 
+         Kappa10*(Kappa00*Kappa10 + Kappa01*Kappa11 + Kappa02*Kappa12) + 
[…]

### 2015-02-01 paper/mHd2_coefficients.m

@@ -1,0 +1,3290 @@
+(* Created with the Wolfram Language for Students - Personal Use Only : www.wolfram.com *)
+{mHd2, (-6*g1^2*MassB^2)/5 - 6*g2^2*MassWB^2 + 2*Lambdax^2*mHd2 + 
+  2*Lambdax^2*mHu2 + 2*Lambdax^2*ms2 - 
+  (3*g1^2*(md200 + md211 + md222 - mDx200 - mDx211 - mDx222 + mDxbar200 + 
+     mDxbar211 + mDxbar222 + me200 + me211 + me222 - mH1I200 - mH1I211 + 
+     mH2I200 + mH2I211 - mHd2 - mHp2 + mHpbar2 + mHu2 - ml200 - ml211 - 
+     ml222 + mq200 + mq211 + mq222 - 2*(mu200 + mu211 + mu222)))/5 - 
+  8*gN^2*MassBp^2*QH1p^2 + 2*gN^2*QH1p*(3*(md200 + md211 + md222)*Qdp + 
+    3*(mDxbar200 + mDxbar211 + mDxbar222)*QDxbarp + 
+    3*(mDx200 + mDx211 + mDx222)*QDxp + (me200 + me211 + me222)*Qep + 
+    2*(mH1I200 + mH1I211)*QH1p + 2*mHd2*QH1p + 2*(mH2I200 + mH2I211)*QH2p + 
+    2*mHu2*QH2p + 2*mHpbar2*QHpbarp + 2*mHp2*QHpp + 
+    2*(ml200 + ml211 + ml222)*QLp + 6*(mq200 + mq211 + mq222)*QQp + ms2*QSp + 
+    (msI200 + msI211)*QSp + 3*(mu200 + mu211 + mu222)*Qup) + 2*TLambdax^2 + 
+  6*(TYd00^2 + TYd01^2 + TYd02^2 + TYd10^2 + TYd11^2 + TYd12^2 + TYd20^2 + 
+    TYd21^2 + TYd22^2) + 2*(TYe00^2 + TYe01^2 + TYe02^2 + TYe10^2 + TYe11^2 + 
+    TYe12^2 + TYe20^2 + TYe21^2 + TYe22^2) + 
[…]

### 2015-02-01 paper/mHu2_coefficients.m

@@ -1,0 +1,2501 @@
+(* Created with the Wolfram Language for Students - Personal Use Only : www.wolfram.com *)
+{mHu2, (-6*g1^2*MassB^2)/5 - 6*g2^2*MassWB^2 + 2*Lambdax^2*mHd2 + 
+  2*Lambdax^2*mHu2 + 2*Lambdax^2*ms2 + 
+  (3*g1^2*(md200 + md211 + md222 - mDx200 - mDx211 - mDx222 + mDxbar200 + 
+     mDxbar211 + mDxbar222 + me200 + me211 + me222 - mH1I200 - mH1I211 + 
+     mH2I200 + mH2I211 - mHd2 - mHp2 + mHpbar2 + mHu2 - ml200 - ml211 - 
+     ml222 + mq200 + mq211 + mq222 - 2*(mu200 + mu211 + mu222)))/5 - 
+  8*gN^2*MassBp^2*QH2p^2 + 2*gN^2*QH2p*(3*(md200 + md211 + md222)*Qdp + 
+    3*(mDxbar200 + mDxbar211 + mDxbar222)*QDxbarp + 
+    3*(mDx200 + mDx211 + mDx222)*QDxp + (me200 + me211 + me222)*Qep + 
+    2*(mH1I200 + mH1I211)*QH1p + 2*mHd2*QH1p + 2*(mH2I200 + mH2I211)*QH2p + 
+    2*mHu2*QH2p + 2*mHpbar2*QHpbarp + 2*mHp2*QHpp + 
+    2*(ml200 + ml211 + ml222)*QLp + 6*(mq200 + mq211 + mq222)*QQp + ms2*QSp + 
+    (msI200 + msI211)*QSp + 3*(mu200 + mu211 + mu222)*Qup) + 2*TLambdax^2 + 
+  6*(TYu00^2 + TYu01^2 + TYu02^2 + TYu10^2 + TYu11^2 + TYu12^2 + TYu20^2 + 
+    TYu21^2 + TYu22^2) + 6*mHu2*(Yu00^2 + Yu01^2 + Yu02^2 + Yu10^2 + Yu11^2 + 
+    Yu12^2 + Yu20^2 + Yu21^2 + Yu22^2) + 
+  6*(Yu00*(mq200*Yu00 + mq201*Yu01 + mq202*Yu02) + 
[…]

### 2015-02-01 paper/mq222_coefficients.m

@@ -1,0 +1,2168 @@
+(* Created with the Wolfram Language for Students - Personal Use Only : www.wolfram.com *)
+{mq222, (-2*g1^2*MassB^2)/15 - (32*g3^2*MassG^2)/3 - 6*g2^2*MassWB^2 + 
+  (g1^2*(md200 + md211 + md222 - mDx200 - mDx211 - mDx222 + mDxbar200 + 
+     mDxbar211 + mDxbar222 + me200 + me211 + me222 - mH1I200 - mH1I211 + 
+     mH2I200 + mH2I211 - mHd2 - mHp2 + mHpbar2 + mHu2 - ml200 - ml211 - 
+     ml222 + mq200 + mq211 + mq222 - 2*(mu200 + mu211 + mu222)))/5 - 
+  8*gN^2*MassBp^2*QQp^2 + 2*gN^2*QQp*(3*(md200 + md211 + md222)*Qdp + 
+    3*(mDxbar200 + mDxbar211 + mDxbar222)*QDxbarp + 
+    3*(mDx200 + mDx211 + mDx222)*QDxp + (me200 + me211 + me222)*Qep + 
+    2*(mH1I200 + mH1I211)*QH1p + 2*mHd2*QH1p + 2*(mH2I200 + mH2I211)*QH2p + 
+    2*mHu2*QH2p + 2*mHpbar2*QHpbarp + 2*mHp2*QHpp + 
+    2*(ml200 + ml211 + ml222)*QLp + 6*(mq200 + mq211 + mq222)*QQp + ms2*QSp + 
+    (msI200 + msI211)*QSp + 3*(mu200 + mu211 + mu222)*Qup) + 
+  2*(TYd02^2 + TYd12^2 + TYd22^2) + 2*(TYu02^2 + TYu12^2 + TYu22^2) + 
+  Yd02*(mq220*Yd00 + mq221*Yd01 + mq222*Yd02) + 
+  Yd12*(mq220*Yd10 + mq221*Yd11 + mq222*Yd12) + 
+  Yd22*(mq220*Yd20 + mq221*Yd21 + mq222*Yd22) + 
+  mq202*(Yd00*Yd02 + Yd10*Yd12 + Yd20*Yd22) + 
[…]

### 2015-02-01 paper/ms2_coefficients.m

@@ -1,0 +1,2404 @@
+(* Created with the Wolfram Language for Students - Personal Use Only : www.wolfram.com *)
+{ms2, 6*((Kappa00^2 + Kappa01^2 + Kappa02^2)*mDx200 + 
+    (Kappa00*Kappa10 + Kappa01*Kappa11 + Kappa02*Kappa12)*mDx201 + 
+    (Kappa00*Kappa20 + Kappa01*Kappa21 + Kappa02*Kappa22)*mDx202 + 
+    (Kappa00*Kappa10 + Kappa01*Kappa11 + Kappa02*Kappa12)*mDx210 + 
+    (Kappa10^2 + Kappa11^2 + Kappa12^2)*mDx211 + 
+    (Kappa10*Kappa20 + Kappa11*Kappa21 + Kappa12*Kappa22)*mDx212 + 
+    (Kappa00*Kappa20 + Kappa01*Kappa21 + Kappa02*Kappa22)*mDx220 + 
+    (Kappa10*Kappa20 + Kappa11*Kappa21 + Kappa12*Kappa22)*mDx221 + 
+    (Kappa20^2 + Kappa21^2 + Kappa22^2)*mDx222) + 
+  6*(Kappa00*(Kappa00*mDxbar200 + Kappa01*mDxbar210 + Kappa02*mDxbar220) + 
+    Kappa10*(Kappa10*mDxbar200 + Kappa11*mDxbar210 + Kappa12*mDxbar220) + 
+    Kappa20*(Kappa20*mDxbar200 + Kappa21*mDxbar210 + Kappa22*mDxbar220) + 
+    Kappa01*(Kappa00*mDxbar201 + Kappa01*mDxbar211 + Kappa02*mDxbar221) + 
+    Kappa11*(Kappa10*mDxbar201 + Kappa11*mDxbar211 + Kappa12*mDxbar221) + 
+    Kappa21*(Kappa20*mDxbar201 + Kappa21*mDxbar211 + Kappa22*mDxbar221) + 
+    Kappa02*(Kappa00*mDxbar202 + Kappa01*mDxbar212 + Kappa02*mDxbar222) + 
+    Kappa12*(Kappa10*mDxbar202 + Kappa11*mDxbar212 + Kappa12*mDxbar222) + 
+    Kappa22*(Kappa20*mDxbar202 + Kappa21*mDxbar212 + Kappa22*mDxbar222)) + 
[…]

### 2015-02-01 paper/mu222_coefficients.m

@@ -1,0 +1,1824 @@
+(* Created with the Wolfram Language for Students - Personal Use Only : www.wolfram.com *)
+{mu222, (-32*g1^2*MassB^2)/15 - (32*g3^2*MassG^2)/3 - 
+  (4*g1^2*(md200 + md211 + md222 - mDx200 - mDx211 - mDx222 + mDxbar200 + 
+     mDxbar211 + mDxbar222 + me200 + me211 + me222 - mH1I200 - mH1I211 + 
+     mH2I200 + mH2I211 - mHd2 - mHp2 + mHpbar2 + mHu2 - ml200 - ml211 - 
+     ml222 + mq200 + mq211 + mq222 - 2*(mu200 + mu211 + mu222)))/5 - 
+  8*gN^2*MassBp^2*Qup^2 + 2*gN^2*Qup*(3*(md200 + md211 + md222)*Qdp + 
+    3*(mDxbar200 + mDxbar211 + mDxbar222)*QDxbarp + 
+    3*(mDx200 + mDx211 + mDx222)*QDxp + (me200 + me211 + me222)*Qep + 
+    2*(mH1I200 + mH1I211)*QH1p + 2*mHd2*QH1p + 2*(mH2I200 + mH2I211)*QH2p + 
+    2*mHu2*QH2p + 2*mHpbar2*QHpbarp + 2*mHp2*QHpp + 
+    2*(ml200 + ml211 + ml222)*QLp + 6*(mq200 + mq211 + mq222)*QQp + ms2*QSp + 
+    (msI200 + msI211)*QSp + 3*(mu200 + mu211 + mu222)*Qup) + 
+  4*(TYu20^2 + TYu21^2 + TYu22^2) + 4*mHu2*(Yu20^2 + Yu21^2 + Yu22^2) + 
+  4*(Yu20*(mq200*Yu20 + mq210*Yu21 + mq220*Yu22) + 
+    Yu21*(mq201*Yu20 + mq211*Yu21 + mq221*Yu22) + 
+    Yu22*(mq202*Yu20 + mq212*Yu21 + mq222*Yu22)) + 
+  2*(Yu20*(mu220*Yu00 + mu221*Yu10 + mu222*Yu20) + 
[…]

### 2015-02-01 paper/tlambda_coefficients.m

@@ -1,0 +1,1672 @@
+(* Created with the Wolfram Language for Students - Personal Use Only : www.wolfram.com *)
+{TLambdax, (6*g1^2*Lambdax*MassB)/5 + 6*g2^2*Lambdax*MassWB + 
+  4*gN^2*Lambdax*MassBp*QH1p^2 + 4*gN^2*Lambdax*MassBp*QH2p^2 + 
+  4*gN^2*Lambdax*MassBp*QSp^2 + 6*Lambdax*(Kappa00*TKappa00 + 
+    Kappa01*TKappa01 + Kappa02*TKappa02 + Kappa10*TKappa10 + 
+    Kappa11*TKappa11 + Kappa12*TKappa12 + Kappa20*TKappa20 + 
+    Kappa21*TKappa21 + Kappa22*TKappa22) + 
+  4*Lambdax*(Lambda1200*TLambda1200 + Lambda1201*TLambda1201 + 
+    Lambda1210*TLambda1210 + Lambda1211*TLambda1211) + 
+  6*Lambdax*(TYd00*Yd00 + TYd01*Yd01 + TYd02*Yd02 + TYd10*Yd10 + TYd11*Yd11 + 
+    TYd12*Yd12 + TYd20*Yd20 + TYd21*Yd21 + TYd22*Yd22) + 
+  2*Lambdax*(TYe00*Ye00 + TYe01*Ye01 + TYe02*Ye02 + TYe10*Ye10 + TYe11*Ye11 + 
+    TYe12*Ye12 + TYe20*Ye20 + TYe21*Ye21 + TYe22*Ye22) + 
+  6*Lambdax*(TYu00*Yu00 + TYu01*Yu01 + TYu02*Yu02 + TYu10*Yu10 + TYu11*Yu11 + 
+    TYu12*Yu12 + TYu20*Yu20 + TYu21*Yu21 + TYu22*Yu22) + 
+  TLambdax*((-3*g1^2)/5 - 3*g2^2 + 3*(Kappa00^2 + Kappa01^2 + Kappa02^2 + 
+      Kappa10^2 + Kappa11^2 + Kappa12^2 + Kappa20^2 + Kappa21^2 + 
+      Kappa22^2) + 2*(Lambda1200^2 + Lambda1201^2 + Lambda1210^2 + 
+      Lambda1211^2) + 12*Lambdax^2 - 2*gN^2*QH1p^2 - 2*gN^2*QH2p^2 - 
[…]

### 2015-02-01 paper/tyu22_coefficients.m

@@ -1,0 +1,1079 @@
+(* Created with the Wolfram Language for Students - Personal Use Only : www.wolfram.com *)
+{TYu22, (-13*g1^2*TYu22)/15 - 3*g2^2*TYu22 - (16*g3^2*TYu22)/3 + 
+  Lambdax^2*TYu22 - 2*gN^2*QH2p^2*TYu22 - 2*gN^2*QQp^2*TYu22 - 
+  2*gN^2*Qup^2*TYu22 + Yd02*(TYu20*Yd00 + TYu21*Yd01 + TYu22*Yd02) + 
+  Yd12*(TYu20*Yd10 + TYu21*Yd11 + TYu22*Yd12) + 
+  Yd22*(TYu20*Yd20 + TYu21*Yd21 + TYu22*Yd22) + 
+  3*TYu22*(Yu00^2 + Yu01^2 + Yu02^2 + Yu10^2 + Yu11^2 + Yu12^2 + Yu20^2 + 
+    Yu21^2 + Yu22^2) + 5*(Yu02*(TYu20*Yu00 + TYu21*Yu01 + TYu22*Yu02) + 
+    Yu12*(TYu20*Yu10 + TYu21*Yu11 + TYu22*Yu12) + 
+    Yu22*(TYu20*Yu20 + TYu21*Yu21 + TYu22*Yu22)) + 
+  Yu22*((26*g1^2*MassB)/15 + (32*g3^2*MassG)/3 + 6*g2^2*MassWB + 
+    4*gN^2*MassBp*QH2p^2 + 4*gN^2*MassBp*QQp^2 + 4*gN^2*MassBp*Qup^2 + 
+    2*Lambdax*TLambdax + 6*(TYu00*Yu00 + TYu01*Yu01 + TYu02*Yu02 + 
+      TYu10*Yu10 + TYu11*Yu11 + TYu12*Yu12 + TYu20*Yu20 + TYu21*Yu21 + 
+      TYu22*Yu22)) + 2*(TYd02*(Yd00*Yu20 + Yd01*Yu21 + Yd02*Yu22) + 
+    TYd12*(Yd10*Yu20 + Yd11*Yu21 + Yd12*Yu22) + 
+    TYd22*(Yd20*Yu20 + Yd21*Yu21 + Yd22*Yu22)) + 
[…]

### 2015-02-01 paper/yu22_coefficients.m

@@ -1,0 +1,399 @@
+(* Created with the Wolfram Language for Students - Personal Use Only : www.wolfram.com *)
+{Yu22, Yd02*(Yd00*Yu20 + Yd01*Yu21 + Yd02*Yu22) + 
+  Yd12*(Yd10*Yu20 + Yd11*Yu21 + Yd12*Yu22) + 
+  Yd22*(Yd20*Yu20 + Yd21*Yu21 + Yd22*Yu22) + 
+  3*(Yu02*(Yu00*Yu20 + Yu01*Yu21 + Yu02*Yu22) + 
+    Yu12*(Yu10*Yu20 + Yu11*Yu21 + Yu12*Yu22) + 
+    Yu22*(Yu20^2 + Yu21^2 + Yu22^2)) + 
+  Yu22*((-13*g1^2)/15 - 3*g2^2 - (16*g3^2)/3 + Lambdax^2 - 2*gN^2*QH2p^2 - 
+    2*gN^2*QQp^2 - 2*gN^2*Qup^2 + 3*(Yu00^2 + Yu01^2 + Yu02^2 + Yu10^2 + 
+      Yu11^2 + Yu12^2 + Yu20^2 + Yu21^2 + Yu22^2)), 
+ ((2*g1^2)/5 - Lambdax^2 + 2*gN^2*Qdp^2 + 2*gN^2*QH1p^2 - 2*gN^2*QQp^2 - 
+    3*(Yd00^2 + Yd01^2 + Yd02^2 + Yd10^2 + Yd11^2 + Yd12^2 + Yd20^2 + 
+      Yd21^2 + Yd22^2) - Ye00^2 - Ye01^2 - Ye02^2 - Ye10^2 - Ye11^2 - 
+    Ye12^2 - Ye20^2 - Ye21^2 - Ye22^2)*
+   (Yd02*(Yd00*Yu20 + Yd01*Yu21 + Yd02*Yu22) + 
+    Yd12*(Yd10*Yu20 + Yd11*Yu21 + Yd12*Yu22) + 
+    Yd22*(Yd20*Yu20 + Yd21*Yu21 + Yd22*Yu22)) + 
+  (2*g1^2*(Yu02*(Yu00*Yu20 + Yu01*Yu21 + Yu02*Yu22) + 
+     Yu12*(Yu10*Yu20 + Yu11*Yu21 + Yu12*Yu22) + 
[…]

### 2015-02-01 paper/genE6SSM/EWSB/TeX/genE6SSM-EWSB.tex
Added the SARAH generated TeX files for the RGEs

\documentclass[A4]{article} 
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{feynmp}
\usepackage{hyperref}
\usepackage{longtable}
\DeclareGraphicsRule{*}{mps}{*}{}
\graphicspath{{./Diagrams/}}
\newcommand{\Tr}{\mbox{Tr}}
\textwidth 18cm
\oddsidemargin -1.0cm
\evensidemargin -1.0cm
\renewcommand{\arraystretch}{1.3} 
\setlength{\parindent}{0em} 
\begin{document}
\title{Generic E6SSM\\ Superpotential, Rotations and Interactions for eigenstates {\tt'EWSB'} \\ including Renormalization Group Equations \\ 
including one-loop Self-Energies \\ 
} 
\author{SARAH 4.2.1} 
 \maketitle 
 \vspace{10cm} 
This file was automatically generated by SARAH version 4.2.1.  \\ 
References: {\bf arXiv: 1309.7223 }, {\bf Comput.Phys.Commun.184:1792-1809,2011 (1207.0906) }, {\bf Comput.Phys.Commun.182:808-833,2011 (1002.0840) }, {\bf Comput.Phys.Commun.181:1077-1086,2010 (0909.2863) }, {\bf arXiv: 0806.0538 } \\ 
Package Homepage: projects.hepforge.org/sarah/ \\ 
by {\bf Florian Staub, fnstaub@th.physik.uni-bonn.de} 
 \pagebreak 
 \tableofcontents 
 \pagebreak 
 \allowdisplaybreaks 
\input{SF}
\section{Renormalization Group Equations}
\input{rges} 
\section{Field Rotations}
\input{RotationsGaugeEWSB} 
\input{matricesScalarsEWSB} 
\input{matricesFermionsEWSB} 
\section{Vacuum Expectation Values}
\input{VEVsEWSB} 
\section{Tadpole Equations}
\input{TadpoleEquations} 
\section{Particle content for eigenstates {\tt 'EWSB'}}
\input{particles} 
\section{One Loop Self-Energy and One Loop Tadpoles for eigenstates {\tt 'EWSB'}}
\subsection{One Loop Self-Energy}
\input{SelfEnergy1Loop} 
\subsection{Tadpoles}
\input{Tadpoles1Loop} 
\section{Interactions for eigenstates {\tt 'EWSB'}}
\subsection{Three Scalar-Interaction}
\input{VerticesSSS}
\subsection{Two Scalar-One Vector Boson-Interaction}
\input{VerticesSSV}
\subsection{One Scalar-Two Vector Boson-Interaction}
\input{VerticesSVV}
\subsection{Two Fermion-One Vector Boson-Interaction}
\input{VerticesFFV}
\subsection{Two Fermion-One Scalar Boson-Interaction}
\input{VerticesFFS}
\subsection{Three Vector Boson-Interaction}
\input{VerticesVVV}
\subsection{Four Scalar-Interaction}
\input{VerticesSSSS}
\subsection{Two Scalar-Two Vector Boson-Interaction}
\input{VerticesSSVV}
\subsection{Four Vector Boson-Interaction}
\input{VerticesVVVV}
\subsection{Two Ghosts-One Vector Boson-Interaction}
\input{VerticesGGV}
\subsection{Two Ghosts-One Scalar-Interaction}
\input{VerticesGGS}
\input{CG}
\end{document}

### 2015-02-01 paper/genericE6SSM/genericE6SSM.m
Added SARAH model for E6SSM

@@ -1,0 +1,191 @@
+Off[General::spell]
+
+Model`Name = "genericE6SSM";
+Model`NameLaTeX ="Generic E6SSM";
+Model`Authors = "G.Hellwig, P.Diessner, P.Athron, A.Voigt";
+Model`Date = "2014-03-10";
+
+(*-------------------------------------------*)
+(*   Particle Content*)
+(*-------------------------------------------*)
+
+(* Global symmetries *)
+
+Global[[1]] = {Z[2],RParity};
+RpM = {-1,-1,1};
+RpP = {1,1,-1};
+
+(* Vector Superfields *)
+
+Gauge[[1]]={B,   U[1], hypercharge, g1,False,RpM};
+Gauge[[2]]={WB, SU[2], left,        g2,True, RpM};
+Gauge[[3]]={G,  SU[3], color,       g3,False,RpM};
+Gauge[[4]]={Bp,  U[1], Ncharge,    gN,False,RpM};
+
+(* Chiral Superfields *)
+(* Dylan:: Added in variable U(1)_N charges *)
+SuperFields[[1]] = {q, 3, {uL,  dL},     1/6, 2, 3, QQp, RpM};  
+SuperFields[[2]] = {l, 3, {vL,  eL},    -1/2, 2, 1, QLp, RpM};
+SuperFields[[3]] = {Hd,1, {Hd0, Hdm},   -1/2, 2, 1, QH1p, RpP};
+SuperFields[[4]] = {Hu,1, {Hup, Hu0},    1/2, 2, 1, QH2p, RpP};
+
+SuperFields[[5]] = {d, 3, conj[dR],    1/3, 1, -3, Qdp, RpM};
+SuperFields[[6]] = {u, 3, conj[uR],   -2/3, 1, -3, Qup, RpM};
+SuperFields[[7]] = {e, 3, conj[eR],      1, 1,  1, Qep, RpM};
+SuperFields[[8]] = {s, 1, sR,            0, 1,  1, QSp, RpP};
+
+SuperFields[[9]] = {H1I, 2, {H1I0, H1Im},  -1/2, 2, 1, QH1p, RpP};
+SuperFields[[10]] = {H2I, 2, {H2Ip, H2I0},   1/2, 2, 1, QH2p, RpP};
[…]

### 2015-02-01 paper/genericE6SSM/parameters.m

@@ -1,0 +1,394 @@
+ParameterDefinitions = {
+{g1,        { Description -> "Hypercharge-Coupling"}},
+{g2,        { Description -> "Left-Coupling"}},
+{g3,        { Description -> "Strong-Coupling"}},
+{gN,        { Description -> "Ncharge-Coupling",
+                 Dependence -> None,
+                 LaTeX -> "g_N",
+		 LesHouches -> {gauge,4},
+	         OutputName -> gN}},
+{g1gN,        {Description -> "Mixed Gauge Coupling 1"}},
+{gNg1,        {Description -> "Mixed Gauge Coupling 2"}},
+{AlphaS,       { Description -> "Alpha Strong"}},
+{aEWinv,       { Description -> "inverse weak coupling constant at mZ"}},
+{Gf,           { Description -> "Fermi's constant"}},
+{e,            { Description -> "electric charge"}},
+	       
+{Yu,           { Description -> "Up-Yukawa-Coupling",
+	         LaTeX -> "Y_u",
+		 Form -> Diagonal,
+	         Dependence -> None,
+	         Value -> None,
+		 OutputName -> Yu}},
+{Yd,           { Description -> "Down-Yukawa-Coupling",
+	         LaTeX -> "Y_d",
+		 Form -> Diagonal,
+	         Dependence -> None,
+	         Value -> None,
+		 OutputName -> Yd}},
+{Ye,           { Description -> "Lepton-Yukawa-Coupling",
+	         LaTeX -> "Y_e",
+		 Form -> Diagonal,
+	         Dependence -> None,
+	         Value -> None,
+		 OutputName -> Ye}},
+{T[Ye],        { Description -> "Trilinear-Lepton-Coupling",
+		 Form -> Diagonal,
+	         Dependence -> None,
+	         Value -> None}},
+{T[Yd],        { Description -> "Trilinear-Down-Coupling",
+		 Form -> Diagonal,
+	         Dependence -> None,
+	         Value -> None}},
+{T[Yu],        { Description -> "Trilinear-Up-Coupling",
+		 Form -> Diagonal,
+	         Dependence -> None,
+	         Value -> None}},	       
+{\[Mu],        { Description -> "Mu-parameter",
+      Dependence -> \[Lambda]*vs/Sqrt[2]}},
+{B[\[Mu]],     { Description -> "Bmu-parameter",
+      Dependence -> T[\[Lambda]]*vs/Sqrt[2]}},	       
[…]

### 2015-02-24 paper/e6ssm-tuning-paper.tex
Removed undefined reference
Simplified and added O(t^2) contribution to the series expansion of lambda
Factorised a term in the 2-loop beta function for lambda, added a missing label
Started adding beta functions and O(t^2) coefficient for A_\lambda

@@
 This leads to a significant reduction in the contributions to the RG running of $m_{H_u}^2$ and $m_{Q3}^2$ coming from terms of the form $g_1^2\Sigma_1$ and, to a lesser extent, $g_1'^2\Sigma_1'$.
-Here we define (see also Eq.~(\ref{}))
+Here we define
 \begin{align*}
@@
 \end{subequations}
-In order to keep our expressions compact we have used the notation
+In order to keep these expressions compact we have used the notation
 \begin{align*}
@@
 \end{align*}
-Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised. Similarly we have set
-\begin{equation*}
-\Sigma_\lambda=\lambda_1^2+\lambda_2^2+\lambda_3^2, \qquad \Sigma_\kappa=\kappa_1^2+\kappa_2^2+\kappa_3^2.
-\end{equation*}
+Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised. Similarly we will write
+\begin{align*}
+&\Sigma_\lambda=\lambda_1^2+\lambda_2^2+\lambda_3^2, \qquad \Sigma_\kappa=\kappa_1^2+\kappa_2^2+\kappa_3^2,\\
+&\Pi_\lambda=\lambda_1^4+\lambda_2^4+\lambda_3^4,\qquad \Pi_\kappa=\kappa_1^4+\kappa_2^4+\kappa_3^4.
+\end{align*}
 The corresponding $O(t^2)$ coefficients for the gauge couplings are simply
@@
 The one- and two-loop contributions to the $\beta$ function for $\lambda$
-are
+and the $O(t^2)$ coefficient in the series expansion are
 \begin{subequations}\label{eq:USSMLambdaBetas}
@@
 \beta_\lambda^{(2)}&=\lambda \bigg \{ -2\lambda^2\left ( \lambda^2+2\Sigma_\lambda+3\Sigma_\kappa\right )-4\Pi_\lambda-6\Pi_\kappa-3\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right ) \nonumber\\
-&{} -3\left ( 3y_t^4+3y_b^4+2y_t^2y_b^2+y_\tau^2 \right )+6g_2^2\Sigma_\lambda+g_1^2\left ( \frac{4}{5}y_t^2-\frac{2}{5}y_b^2+\frac{6}{5}y_\tau^2+\frac{4}{5}\Sigma_\kappa +\frac{6}{5}\Sigma_\lambda\right )\nonumber\\
+&{} -3\left ( 3y_t^4+3y_b^4+2y_t^2y_b^2+y_\tau^2 \right )+6g_2^2\Sigma_\lambda+\frac{2}{5}g_1^2\left ( 2y_t^2-y_b^2+3y_\tau^2+2\Sigma_\kappa +3\Sigma_\lambda\right )\nonumber\\
 &{}\left.+g_1'^2\left [ 4\tilde{Q}_S^2\lambda^2 -6\left ( \tilde{Q}_2^2-\tilde{Q}_Q^2-\tilde{Q}_u^2\right )y_t^2-6\left ( \tilde{Q}_1^2-\tilde{Q}_Q^2-\tilde{Q}_d^2\right )y_b^2 \right.\right.\nonumber\\
@@
 &{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2\tilde{Q}_1^4+2\tilde{Q}_2^4+2\tilde{Q}_S^4+\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\Sigma_{\tilde{Q}}\right ]\nonumber\\
-&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [\tilde{Q}_1^2+\tilde{Q}_2^2+\left ( \tilde{Q}_2-\tilde{Q}_1\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \}.\label{eq:USSMLambdaBetaTwoLoop}
+&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [\tilde{Q}_1^2+\tilde{Q}_2^2+\left ( \tilde{Q}_2-\tilde{Q}_1\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\
+b_\lambda^{(2)}&=\lambda \bigg \{ 2\lambda^2\left ( 3\lambda^2 +4\Sigma_\lambda +6\Sigma_\kappa \right )+4\Pi_\lambda + 6\Pi_\kappa +6\left ( \Sigma_\lambda+\frac{3}{2}\Sigma_\kappa\right )^2+7\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\nonumber\\
+&{}+\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\left (2\Sigma_\lambda+3\Sigma_\kappa\right ) +3\left ( \frac{15}{2}y_t^4+\frac{15}{2}y_b^4+\frac{3}{2}y_\tau^4 +5y_b^2y_t^2 +3y_b^2y_\tau^2 +y_t^2y_\tau^2\right )\nonumber\\
+&{}-\frac{1}{5}g_1^2\left ( 12\lambda^2+16y_b^2+22y_t^2+12y_\tau^2+12\Sigma_\lambda +13\Sigma_\kappa \right )\nonumber\\
+&{}-3g_2^2\left ( 4\lambda^2+6y_t^2+6y_b^2+2y_\tau^2+4\Sigma_\lambda+3\Sigma_\kappa\right )-16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa \right )\nonumber\\
+&{}-2g_1'^2\left [ 4\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\left ( \lambda^2 +\Sigma_\lambda \right )+3\Sigma_\kappa\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2+\tilde{Q}_D^2+\tilde{Q}_{\overline{D}}^2\right )\right .\nonumber\\
+&{}+3y_b^2\left ( 2\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_d^2+\tilde{Q}_Q^2+\tilde{Q}_S^2 \right )+3y_t^2\left ( \tilde{Q}_1^2+2\tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_S^2+\tilde{Q}_u^2\right )\nonumber\\
+&{}\left.+y_\tau^2\left ( 2\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_e^2+\tilde{Q}_L^2+\tilde{Q}_S^2\right )\right ]-\frac{15}{2}g_2^4-\frac{279}{50}g_1^4\nonumber\\
+&{}+2g_1'^4\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right )\left (\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2-\Sigma_{\tilde{Q}}\right )+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\nonumber\\
+&{}+\frac{6}{5}g_1^2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right ) \bigg \}.\label{eq:USSMLambdaOt2Coeff}
+\end{align}
+\end{subequations}
+It is sufficient to consider the trilinear coupling $a_\lambda\equiv \lambda A_\lambda$, for which the relevant expressions read
+\begin{subequations}
+\begin{align}
+\beta_{a_\lambda}^{(1)}&=,\label{eq:USSMTLambdaBetaOneLoop}\\
+\beta_{a_\lambda}^{(2)}&=,\label{eq:USSMTLambdaBetaTwoLoop}\\
+b_{a_\lambda}^{(2)}&=.\label{eq:USSMTLambdaOt2Coeff}
 \end{align}

### 2015-02-25 paper/e6ssm-tuning-paper.tex
Updated notation to not use SUGRA-style trilinears
Added 1-loop beta function for A_\lambda (actually T_\lambda is more convenient as that is what is used in the fine tuning code)
Added one-loop beta functions for soft Higgs and singlet masses, defined trace contributions in Appendix as well. Trace contributions also involve charges, this will have to be addressed in the body of the paper

@@
 \end{subequations}
-It is sufficient to consider the trilinear coupling $a_\lambda\equiv \lambda A_\lambda$, for which the relevant expressions read
+It is sufficient for our purposes to consider the trilinear coupling $a_\lambda\equiv \lambda A_\lambda$, rather than $A_\lambda$, for which the relevant expressions read
 \begin{subequations}
 \begin{align}
-\beta_{a_\lambda}^{(1)}&=,\label{eq:USSMTLambdaBetaOneLoop}\\
+\beta_{a_\lambda}^{(1)}&=2\lambda \left [ 2 \Sigma_{a_\lambda}+3\Sigma_{a_\kappa}+3y_ta_t+3y_ba_b+y_\tau a_\tau+\frac{3}{5}g_1^2M_1+3g_2^2 M_2+2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\right ]\nonumber\\
+&{}+a_\lambda \left [ 6\lambda^2+2\Sigma_\lambda+3\Sigma_\kappa+3y_t^2+3y_b^2+y_\tau^2-\frac{3}{5}g_1^2-3g_2^2-2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right )\right ],\label{eq:USSMTLambdaBetaOneLoop}\\
 \beta_{a_\lambda}^{(2)}&=,\label{eq:USSMTLambdaBetaTwoLoop}\\
-b_{a_\lambda}^{(2)}&=.\label{eq:USSMTLambdaOt2Coeff}
+b_{a_\lambda}^{(2)}&=,\label{eq:USSMTLambdaOt2Coeff}
+\end{align}
+\end{subequations}
+where
+\begin{align*}
+&\Sigma_{a_\lambda}=\lambda_1 a_{\lambda_1}+\lambda_2 a_{\lambda_2}+\lambda_3 a_{\lambda_3},\qquad \Sigma_{a_\kappa}=\kappa_1 a_{\kappa_1}+\kappa_2 a_{\kappa_2}+\kappa_3 a_{\kappa_3},\\
+&\Pi_{a_\lambda}=\lambda_1^3 a_{\lambda_1}+\lambda_2^3 a_{\lambda_2}+\lambda_3^3 a_{\lambda_3},\qquad \Pi_{a_\kappa}=\kappa_1^3 a_{\kappa_1}+\kappa_2^3 a_{\kappa_2}+\kappa_3^3 a_{\kappa_3},
+\end{align*}
+Note that $a_{\lambda_i}\equiv\lambda_i A_{\lambda_i}$, $a_{\kappa_i}\equiv\kappa_i A_{\kappa_i}$, $a_t\equiv y_t A_t$, $a_b\equiv y_b A_b$ and $a_\tau= y_\tau A_\tau$. Definining 
+\begin{align}
+\Sigma_1&=\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2-m_{Li}^2+m_{H_{ui}}^2-m_{H_{di}}^2+m_{\overline{D}_i}^2-m_{Di}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1}\\
+\Sigma_1'&=\sum_{i=1}^3\left ( 6\tilde{Q}_Qm_{Qi}^2+3\tilde{Q}_um_{ui}^2+3\tilde{Q}_dm_{di}^2+\tilde{Q}_em_{ei}^2+2\tilde{Q}_Lm_{Li}^2+2\tilde{Q}_2m_{H_{ui}}^2+2\tilde{Q}_1m_{H_{di}}^2\right.\nonumber\\
+&\quad{}\left.+\tilde{Q}_Sm_{Si}^2+3\tilde{Q}_{\overline{D}}m_{\overline{D}_i}^2+3\tilde{Q}_Dm_{Di}^2\right )+2\tilde{Q}_{H'}m_{H'}^2+2\tilde{Q}_{\overline{H'}}m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1Pr}
+\end{align}
+the one- and two-loop $\beta$ functions and the $O(t^2)$ coefficients for $m_{H_d}^2$ are
+\begin{subequations}
+\begin{align}
+\beta_{m_{H_d}^2}^{(1)}&=2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+2a_\lambda^2+6y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+6a_b^2\nonumber\\
+&{}+2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+2a_\tau^2-6g_2^2 M_2^2-\frac{6}{5}g_1^2 M_1^2-8\tilde{Q}_1^2g_1'^2 M_1'^2\nonumber\\
+&{}-\frac{3}{5}g_1^2\Sigma_1+2\tilde{Q}_1g_1'^2\Sigma_1',\label{eq:USSMmHd2BetaOneLoop}\\
+\beta_{m_{H_d}^2}^{(2)}&=,\label{eq:USSMmHd2BetaTwoLoop}\\
+b_{m_{H_d}^2}^{(2)}&=.\label{eq:USSMmHd2Ot2Coeff}
+\end{align}
+\end{subequations}
+Similarly, those for $m_{H_u}^2$ read
+\begin{subequations}
+\begin{align}
+\beta_{m_{H_u}^2}^{(1)}&=2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+2a_\lambda^2+6y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+6a_t^2\nonumber\\
+&{}-6g_2^2M_2^2-\frac{6}{5}g_1^2M_1^2-8\tilde{Q}_2^2g_1'^2M_1'^2+\frac{3}{5}g_1^2\Sigma_1+2\tilde{Q}_2g_1'^2\Sigma_1',\label{eq:USSMmHu2BetaOneLoop}\\
+\beta_{m_{H_u}^2}^{(2)}&=,\label{eq:USSMmHu2BetaTwoLoop}\\
+b_{m_{H_u}^2}^{(2)}&=,\label{eq:USSMmHu2Ot2Coeff}
+\end{align}
+\end{subequations}
+while those for $m_S^2$ are
+\begin{subequations}
+\begin{align}
+\beta_{m_S^2}^{(1)}&=\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2+6\kappa_i\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+6a_{\kappa_i}^2\right ]\nonumber\\
+&{}-8\tilde{Q}_S^2g_1'^2M_1'^2+2\tilde{Q}_Sg_1'^2\Sigma_1',\label{eq:USSMms2BetaOneLoop}\\
+\beta_{m_S^2}^{(2)}&=,\label{eq:USSMms2BetaTwoLoop}\\
+b_{m_S^2}^{(2)}&=.\label{eq:USSMms2Ot2Coeff}
 \end{align}

### 2015-02-25 paper/e6ssm-tuning-paper.tex
Added expressions for traces over U(1)' charges in terms of the E6 mixing angle, so as not to have to continuously be recalculating them when checking against the CE6SSM

@@
 \begin{align*}
-\Sigma_{\tilde{Q}}=\sum_i \tilde{Q}_i^2
+\Sigma_{\tilde{Q}}=\sum_i \tilde{Q}_i^2=\frac{321}{40}\cos^2\theta+\frac{217}{24}\sin^2\theta+\frac{27}{8\sqrt{15}}\sin 2\theta
 \end{align*}
@@
 \begin{align*}
-\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i,\\
-\Pi_{\tilde{Q}}&=\sum_i \tilde{Q}_i^4,\\
-\Pi_{\tilde{Q}}^Y&=\sum_i \left ( \sqrt{\frac{5}{3}}Q_i^Y\right )^2\tilde{Q}_i^2,\\
-\Pi_{\tilde{Q}}^L&=3\tilde{Q}_1^2+3\tilde{Q}_2^2+\tilde{Q}_{H'}^2+\tilde{Q}_{\overline{H'}}^2+3\tilde{Q}_L^2+9\tilde{Q}_Q^2,\\
-\Pi_{\tilde{Q}}^C&=\tilde{Q}_d^2+\tilde{Q}_D^2+\tilde{Q}_{\overline{D}}^2+2\tilde{Q}_Q^2+\tilde{Q}_u^2.
+\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i=-\frac{3}{\sqrt{10}}\cos\theta-\frac{1}{\sqrt{6}}\sin\theta,\\
+\Pi_{\tilde{Q}}&=\sum_i \tilde{Q}_i^4\\
+&=\frac{2049}{1600}\cos^4\theta+\frac{483}{80\sqrt{15}}\cos^3\theta\sin\theta+\frac{681}{160}\cos^2\theta\sin^2\theta+\frac{9}{16\sqrt{15}}\cos\theta\sin^3\theta+\frac{1297}{576}\sin^4\theta,\\
+\Pi_{\tilde{Q}}^Y&=\sum_i \left ( \sqrt{\frac{5}{3}}Q_i^Y\right )^2\tilde{Q}_i^2=\frac{59}{40}\cos^2\theta+\frac{31}{24}\sin^2\theta+\frac{3}{8\sqrt{15}}\sin 2\theta,\\
+\Pi_{\tilde{Q}}^L&=3\tilde{Q}_1^2+3\tilde{Q}_2^2+\tilde{Q}_{H'}^2+\tilde{Q}_{\overline{H'}}^2+3\tilde{Q}_L^2+9\tilde{Q}_Q^2=\frac{39}{20}\cos^2\theta+\frac{19}{12}\sin^2\theta+\frac{3}{4\sqrt{15}}\sin 2\theta,\\
+\Pi_{\tilde{Q}}^C&=\tilde{Q}_d^2+\tilde{Q}_D^2+\tilde{Q}_{\overline{D}}^2+2\tilde{Q}_Q^2+\tilde{Q}_u^2=\frac{1}{2}.
 \end{align*}
-Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised. Similarly we will write
+Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised.
+The expressions in terms of the $E_6$ mixing angle $\theta$ follow from the charge assignments given in Table \ref{tab:E6charges} and hold provided that $U(1)$ mixing is neglected.
+Similarly we will write
 \begin{align*}
@@
 \end{subequations}
+If the one-loop contributions to the effective potential from top and stop loops are also included it is necessary to consider the expansions for $y_t$, $a_t$, $m_{Q3}^2$ and $m_{u3}^2$.
+The necessary expressions for $y_t$ read
+\begin{subequations}
+\begin{align}
+\beta_{y_t}^{(1)}&=y_t\left [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2-2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )\right ],\label{eq:USSMYu22BetaOneLoop}\\
+\beta_{y_t}^{(2)}&=,\label{eq:USSMYu22BetaTwoLoop}\\
+b_{y_t}^{(2)}&=,\label{eq:USSMYu22Ot2Coeff}
+\end{align}
+\end{subequations}
+and those for $a_t$ read
+\begin{subequations}
+\begin{align}
+\beta_{a_t}^{(1)}&=,\label{eq:USSMTYu22BetaOneLoop}\\
+\beta_{a_t}^{(2)}&=,\label{eq:USSMTYu22BetaTwoLoop}\\
+b_{a_t}^{(2)}&=.\label{eq:USSMTYu22Ot2Coeff}
+\end{align}
+\end{subequations}
+The one- and two-loop $\beta$ functions and the resulting $O(t^2)$ coefficient for $m_{Q3}^2$ are 
+\begin{subequations}
+\begin{align}
+\beta_{m_{Q3}^2}^{(1)}&=,\label{eq:USSMmq222BetaOneLoop}\\
+\beta_{m_{Q3}^2}^{(2)}&=,\label{eq:USSMmq222BetaTwoLoop}\\
+b_{m_{Q3}^2}^{(2)}&=.\label{eq:USSMmq222Ot2Coeff}
+\end{align}
+\end{subequations}
+Finally, the relevant expressions for the soft mass $m_{u3}^2$ read
+\begin{subequations}
+\begin{align}
+\beta_{m_{u3}^2}^{(1)}&=,\label{eq:USSMmu222BetaOneLoop}\\
+\beta_{m_{u3}^2}^{(2)}&=,\label{eq:USSMmu222BetaTwoLoop}\\
+b_{m_{u3}^2}^{(2)}&=.\label{eq:USSMmu222Ot2Coeff}
+\end{align}
+\end{subequations}
 % NB before submission replace this with a copy-paste of the bbl file?

### 2015-02-25 fs-spectrum/test/test_lowE6SSM_Yu22_2lp_beta.cpp
Added additional test case for checking coefficients of two-loop beta function for Yu22; there appears to be another error (or at least difference to the SARAH RGEs) in the CE6SSM paper

@@ -1,0 +1,303 @@
+// ====================================================================
+// Test suite for checking coefficients of various terms in the
+// 2-loop betas
+// ====================================================================
+
+#include <limits>
+#include <random>
+#include <chrono>
+#include <Eigen/Core>
+
+#include "wrappers.hpp"
+#include "lowE6SSM_two_scale_model.hpp"
+
+#define BOOST_TEST_DYN_LINK
+#define BOOST_TEST_MODULE test_lowE6SSM_Yu22_2lp_beta
+
+#include <boost/test/unit_test.hpp>
+#include <boost/test/floating_point_comparison.hpp>
+
+using namespace std;
+using namespace flexiblesusy;
+
+lowE6SSM_input_parameters get_test_inputs(double theta)
+{
+   lowE6SSM_input_parameters input;
+
+   input.TanBeta = 10.0;
+
+   input.QQp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::QL, theta);
+   input.QLp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::LL, theta);
+   input.QH1p = lowE6SSM_info::get_e6_charge(lowE6SSM_info::Hd, theta);
+   input.QH2p = lowE6SSM_info::get_e6_charge(lowE6SSM_info::Hu, theta);
+   input.Qdp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::dR, theta);
+   input.Qup = lowE6SSM_info::get_e6_charge(lowE6SSM_info::uR, theta);
+   input.Qep = lowE6SSM_info::get_e6_charge(lowE6SSM_info::eR, theta);
+   input.QSp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::S, theta);
+   input.QDxp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::Dx, theta);
+   input.QDxbarp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::Dxbar, theta);
+   input.QHpp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::Hp, theta);
+   input.QHpbarp = lowE6SSM_info::get_e6_charge(lowE6SSM_info::Hpbar, theta);
+
+   input.KappaInput(0,0) = 0.5;
[…]

### 2015-02-27 paper/e6ssm-tuning-paper.tex
Added 2-loop beta function for y_t
Added simplified O(t^2) coefficient for y_t
Added in missing factor of 1/2
Added one-loop beta function for mq222
Added one-loop beta function for mu222
Fixed typo
Fixed some more typos
Added one-loop beta function for A_t
Rewrote one-loop beta for TYu22 in a form that makes the beta function for A_t easier to extract
Rewrote one-loop beta for TLambdax to make getting beta function for A_\lambda easier; there still appears to be a problem with the 2-loop beta for A_t (and maybe A_\lambda?), with disagreement between the CE6SSM results and the SARAH results
Ad

@@
 \cite{Kang:2004ix}; explanations of the matter-anti-matter asymmetry
-of the universe though EW baryogensis or leptogensis
+of the universe though EW baryogenesis or leptogenesis
 \cite{Hambye:2000bn,Ma:2000jf,Kang:2004pp}; dipole moments
@@
 \begin{align}
-\beta_{a_\lambda}^{(1)}&=2\lambda \left [ 2 \Sigma_{a_\lambda}+3\Sigma_{a_\kappa}+3y_ta_t+3y_ba_b+y_\tau a_\tau+\frac{3}{5}g_1^2M_1+3g_2^2 M_2+2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\right ]\nonumber\\
-&{}+a_\lambda \left [ 6\lambda^2+2\Sigma_\lambda+3\Sigma_\kappa+3y_t^2+3y_b^2+y_\tau^2-\frac{3}{5}g_1^2-3g_2^2-2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right )\right ],\label{eq:USSMTLambdaBetaOneLoop}\\
+\beta_{a_\lambda}^{(1)}&=a_\lambda \left[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2-\frac{3}{5} g_1^2 -2 \left ( \tilde{Q}_1^2 + \tilde{Q}_2^2 + \tilde{Q}_S^2\right )g_1'^2 \right]\nonumber\\
+&{}+\lambda \left [ 4\lambda a_\lambda +4\Sigma_{a_\lambda}+6\Sigma_{a_\kappa}+6y_ta_t+6y_ba_b+2y_\tau a_\tau +6g_2^2M_2+\frac{6}{5}g_1^2M_1\right.\nonumber\\
+&{}\left.+4g_1'^2M_1'\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right )\right ],\label{eq:USSMTLambdaBetaOneLoop}\\
 \beta_{a_\lambda}^{(2)}&=,\label{eq:USSMTLambdaBetaTwoLoop}\\
@@
 \end{align*}
-Note that $a_{\lambda_i}\equiv\lambda_i A_{\lambda_i}$, $a_{\kappa_i}\equiv\kappa_i A_{\kappa_i}$, $a_t\equiv y_t A_t$, $a_b\equiv y_b A_b$ and $a_\tau= y_\tau A_\tau$. Definining 
+Note that $a_{\lambda_i}\equiv\lambda_i A_{\lambda_i}$, $a_{\kappa_i}\equiv\kappa_i A_{\kappa_i}$, $a_t\equiv y_t A_t$, $a_b\equiv y_b A_b$ and $a_\tau= y_\tau A_\tau$. Defining 
 \begin{align}
@@
 \beta_{y_t}^{(1)}&=y_t\left [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2-2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )\right ],\label{eq:USSMYu22BetaOneLoop}\\
-\beta_{y_t}^{(2)}&=,\label{eq:USSMYu22BetaTwoLoop}\\
-b_{y_t}^{(2)}&=,\label{eq:USSMYu22Ot2Coeff}
+\beta_{y_t}^{(2)}&=y_t\bigg \{-22y_t^4-5y_b^4-5y_t^2y_b^2-y_b^2y_\tau^2-\lambda^2 \left ( \lambda^2+3y_t^2+4y_b^2+y_\tau^2+2\Sigma_\lambda + 3\Sigma_\kappa\right )\nonumber\\
+&{}+2g_1'^2\left [ \lambda^2\left ( \tilde{Q}_1^2-\tilde{Q}_2^2+\tilde{Q}_S^2 \right )+2y_t^2\left ( 2\tilde{Q}_Q^2+\tilde{Q}_u^2\right )+y_b^2\left ( \tilde{Q}_1^2-\tilde{Q}_Q^2+\tilde{Q}_d^2\right )\right ]\nonumber\\
+&{}+16g_3^2y_t^2+6g_2^2y_t^2+g_1^2\left ( \frac{6}{5}y_t^2+\frac{2}{5}y_b^2\right )+\frac{128}{9}g_3^4+\frac{33}{2}g_2^4+\frac{3913}{450}g_1^4\nonumber\\
+&{}+2g_1'^4\left [ 2\left ( \tilde{Q}_2^4+\tilde{Q}_Q^4+\tilde{Q}_u^4\right )+\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2\right )\Sigma_{\tilde{Q}}\right ]+8g_3^2g_2^2+\frac{136}{45}g_3^2g_1^2\nonumber\\
+&{}+\frac{32}{3}g_3^2g_1'^2\left ( \tilde{Q}_Q^2+\tilde{Q}_u^2\right )+g_2^2g_1^2+6g_2^2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2\right )\nonumber\\
+&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3\tilde{Q}_2^2+\frac{1}{3}\tilde{Q}_Q^2+\frac{16}{3}\tilde{Q}_u^2+\left ( 3\tilde{Q}_2+\tilde{Q}_Q-4\tilde{Q}_u\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\
+b_{y_t}^{(2)}&=y_t\bigg \{ 54y_t^4+\frac{13}{2}y_b^4+13y_t^2y_b^2+y_b^2y_\tau^2+\lambda^2\left ( \frac{5}{2}\lambda^2+15y_t^2+5y_b^2+y_\tau^2+2\Sigma_\lambda+3\Sigma_\kappa \right )\nonumber\\
+&{}-\frac{16}{3}g_3^2\left ( \lambda^2+2y_b^2+12y_t^2\right )-6g_2^2\left ( \lambda^2+y_b^2+6y_t^2\right )-g_1^2\left ( \frac{22}{15}\lambda^2+\frac{4}{3}y_b^2+\frac{52}{5}y_t^2\right )\nonumber\\
+&{}-2g_1'^2\left [ \lambda^2 \left (\tilde{Q}_1^2+2\tilde{Q}_2^2+\tilde{Q}_S^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )+y_b^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+2\tilde{Q}_Q^2+\tilde{Q}_u^2+\tilde{Q}_d^2\right )\right.\nonumber\\
+&{}\left.+12y_t^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2\right )\right ]+\frac{128}{9}g_3^4-\frac{15}{2}g_2^4-\frac{143}{18}g_1^4\nonumber\\
+&{}+2g_1'^4\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2\right )\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2-\Sigma_{\tilde{Q}}\right )+16g_3^2g_2^2+\frac{208}{45}g_3^2g_1^2\nonumber\\
+&{}+\frac{32}{3}g_3^2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2\right )+\frac{13}{5}g_2^2g_1^2+6g_2^2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )\nonumber\\
+&{}+\frac{26}{15}g_1^2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )\bigg \},\label{eq:USSMYu22Ot2Coeff}
 \end{align}
@@
 \begin{align}
-\beta_{a_t}^{(1)}&=,\label{eq:USSMTYu22BetaOneLoop}\\
+\beta_{a_t}^{(1)}&=a_t\left [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2-2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )\right ]\nonumber\\
+&{}+y_t\left [ 2\lambda a_\lambda + 12y_ta_t+2y_ba_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1\right.\nonumber\\
+&{}\left.+4g_1'^2M_1'\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )\right ],\label{eq:USSMTYu22BetaOneLoop}\\
 \beta_{a_t}^{(2)}&=,\label{eq:USSMTYu22BetaTwoLoop}\\
@@
 \begin{align}
-\beta_{m_{Q3}^2}^{(1)}&=,\label{eq:USSMmq222BetaOneLoop}\\
+\beta_{m_{Q3}^2}^{(1)}&=2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+2a_t^2+2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+2a_b^2\nonumber\\
+&{}-\frac{32}{3}g_3^2M_3^2-6g_2^2M_2^2-\frac{2}{15}g_1^2M_1^2-8\tilde{Q}_Q^2g_1'^2M_1'^2+\frac{1}{5}g_1^2\Sigma_1+2\tilde{Q}_Qg_1'^2\Sigma_1',\label{eq:USSMmq222BetaOneLoop}\\
 \beta_{m_{Q3}^2}^{(2)}&=,\label{eq:USSMmq222BetaTwoLoop}\\
@@
 \begin{align}
-\beta_{m_{u3}^2}^{(1)}&=,\label{eq:USSMmu222BetaOneLoop}\\
-\beta_{m_{u3}^2}^{(2)}&=,\label{eq:USSMmu222BetaTwoLoop}\\
+\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+4a_t^2-\frac{32}{3}g_3^2M_3^2-\frac{32}{15}g_1^1M_1^2-8\tilde{Q}_u^2g_1'^2M_1'^2\nonumber\\
+&{}-\frac{4}{5}g_1^2\Sigma_1+2\tilde{Q}_ug_1'^2\Sigma_1',\label{eq:USSMmu222BetaOneLoop}\\
+\beta_{m_{u3}^2}^{(2)}&=-32y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )-4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )\nonumber\\
+&{}-64y_t^2a_t^2-4\left ( y_ta_b+y_ba_t\right )^2-4\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )\nonumber\\
+&{}-4\left ( \lambda a_t + y_ta_\lambda \right )^2+12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_2^2\right )+12g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
+&{}-\frac{4}{5}g_1^2y_t^2\left ( -5m_{H_u}^2-m_{Q3}^2+9m_{u3}^2+2M_1^2\right )-\frac{4}{5}g_1^2\left ( a_t^2-2y_ta_tM_1 \right )\nonumber\\
+&{}-\frac{8}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q3}^2-2m_{d3}^2\right )-\frac{8}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
+&{}-\frac{8}{5}g_1^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_{Di}^2-m_{\overline{D}i}^2 \right )+\lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2 \right )\right ]\nonumber\\
+&{}+8g_1'^2y_t^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2-\tilde{Q}_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )\nonumber\\
+&{}+8g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2-\tilde{Q}_u^2\right )\left ( a_t^2-2y_ta_tM_1'\right )-24\tilde{Q}_ug_1'^2y_t^2\left (\tilde{Q}_2m_{H_u}^2+\tilde{Q}_Qm_{Q3}^2+\tilde{Q}_um_{u3}^2\right )\nonumber\\
+&{}-24\tilde{Q}_ug_1'^2y_b^2\left ( \tilde{Q}_1m_{H_d}^2+\tilde{Q}_Qm_{Q3}^2+\tilde{Q}_dm_{d3}^2\right )-8\tilde{Q}_ug_1'^2y_\tau^2\left ( \tilde{Q}_1m_{H_d}^2+\tilde{Q}_Lm_{L3}^2+\tilde{Q}_em_{e3}^2\right )\nonumber\\
+&{}-12\tilde{Q}_ug_1'^2\sum_{i=1}^3\kappa_i^2\left ( \tilde{Q}_Sm_S^2+\tilde{Q}_Dm_{Di}^2+\tilde{Q}_{\overline{D}}m_{\overline{D}i}^2\right )\nonumber\\
+&{}-8\tilde{Q}_ug_1'^2\sum_{i=1}^3\left ( \tilde{Q}_1m_{H_d}^2+\tilde{Q}_2m_{H_u}^2+\tilde{Q}_Sm_S^2\right )\nonumber\\
+&{}+\frac{16}{3}g_3^4\left [ 10M_3^2+\sum_{i=1}^3\left ( m_{di}^2+m_{Di}^2+m_{\overline{D}i}^2+2m_{Qi}^2+m_{ui}^2\right )\right ]\nonumber\\
+&{}+\frac{64}{45}g_3^2g_1^2\left [ 8\left (M_1^2+M_1M_3+M_3^2\right )-3\sum_{i=1}^3\left ( m_{di}^2-m_{Di}^2+m_{\overline{D}i}^2+m_{qi}^2-2m_{ui}^2\right )\right ]\nonumber\\
+&{}+\frac{8}{3}\tilde{Q}_ug_3^2g_1'^2\bigg [ 16\tilde{Q}_u\left (M_1'^2+M_1'M_3+M_3^2\right )\nonumber\\
+&{}+12\sum_{i=1}^3\left ( \tilde{Q}_dm_{di}^2+\tilde{Q}_Dm_{Di}^2+\tilde{Q}_{\overline{D}}m_{\overline{D}i}^2+2\tilde{Q}_Qm_{Qi}^2+\tilde{Q}_um_{ui}^2\right )\bigg ]\nonumber\\
+&{}+\frac{12}{5}g_2^2g_1^2\left [ m_{H'}^2-m_{\overline{H'}}^2+\sum_{i=1}^3\left ( m_{H_i^d}^2-m_{H_i^u}^2+m_{Li}^2-m_{Qi}^2\right )\right ]\nonumber\\
+&{}+12\tilde{Q}_ug_2^2g_1'^2\left [ \tilde{Q}_{H'}m_{H'}^2+\tilde{Q}_{\overline{H'}}m_{\overline{H'}}^2+\sum_{i=1}^3\left ( \tilde{Q}_1m_{H_i^d}^2+\tilde{Q}_2m_{H_i^u}^2+\tilde{Q}_Lm_{Li}^2+3\tilde{Q}_Qm_{Qi}^2\right )\right ]\nonumber\\
+&{}+\frac{4}{75}g_1^4\bigg [ 1261M_1^2+21m_{H'}^2+3m_{\overline{H'}}^2\nonumber\\
+&{}+\sum_{i=1}^3\left ( 4m_{di}^2+12m_{Di}^2+4m_{\overline{D}i}^2-12m_{ei}^2+21m_{H_i^d}^2+3m_{H_i^u}^2+21m_{Li}^2+3m_{Qi}^2+64m_{ui}^2\right )\bigg ]\nonumber\\
+&{}+\frac{4}{15}g_1^2g_1'^2\bigg [ -8\tilde{Q}_u\big ( 9\tilde{Q}_d+9\tilde{Q}_{\overline{D}}-9\tilde{Q}_D+9\tilde{Q}_e-9\tilde{Q}_1+9\tilde{Q}_2+3\tilde{Q}_{\overline{H'}}-3\tilde{Q}_{H'}-9\tilde{Q}_L\nonumber\\
+&{}+9\tilde{Q}_Q-22\tilde{Q}_u\big )\left ( M_1^2+M_1M_1'+M_1'^2 \right )+12\tilde{Q}_{H'}^2m_{H'}^2-\tilde{Q}_{\overline{H'}}^2m_{\overline{H'}}^2\nonumber\\
+&{}+12\sum_{i=1}^3\big ( -\tilde{Q}_d^2m_{di}^2-\tilde{Q}_{\overline{D}}^2m_{\overline{D}i}^2+\tilde{Q}_D^2m_{Di}^2-\tilde{Q}_e^2m_{ei}^2+\tilde{Q}_1^2m_{H_i^d}^2-\tilde{Q}_2^2m_{H_i^u}^2+\tilde{Q}_L^2m_{Li}^2\nonumber\\
+&{}-\tilde{Q}_Q^2m_{Qi}^2+\tilde{Q}_u^2m_{ui}^2\big )-15\tilde{Q}_{\overline{H'}}\tilde{Q}_um_{\overline{H'}}^2+33\tilde{Q}_{H'}\tilde{Q}_um_{H'}^2+\tilde{Q}_u\sum_{i=1}^3\big ( -18\tilde{Q}_dm_{di}^2\nonumber\\
+&{}-18\tilde{Q}_{\overline{D}}m_{\overline{D}i}^2+30\tilde{Q}_Dm_{Di}^2-6\tilde{Q}_em_{ei}^2+33\tilde{Q}_1m_{H_i^d}^2-15\tilde{Q}_2m_{H_i^u}^2+33\tilde{Q}_Lm_{Li}^2\nonumber\\
+&{}-21\tilde{Q}_Qm_{Qi}^2+84\tilde{Q}_um_{ui}^2\big )\bigg ]+8\tilde{Q}_ug_1'^4\bigg [ 3\tilde{Q}_uM_1'^2\big ( 9\tilde{Q}_d^2+9\tilde{Q}_{\overline{D}}^2+9\tilde{Q}_D^2+3\tilde{Q}_e^2+6\tilde{Q}_1^2\nonumber\\
+&{}+6\tilde{Q}_2^2+2\tilde{Q}_{\overline{H'}}^2+2\tilde{Q}_{H'}^2+6\tilde{Q}_L^2+18\tilde{Q}_Q^2+3\tilde{Q}_S^2+11\tilde{Q}_u^2 \big )+2\tilde{Q}_{H'}^3m_{H'}^2+2\tilde{Q}_{\overline{H'}}^3m_{\overline{H'}}^2\nonumber\\
+&{}+\sum_{i=1}^3\big ( 3\tilde{Q}_d^3m_{di}^2+3\tilde{Q}_{\overline{D}}^3m_{\overline{D}i}^2+3\tilde{Q}_D^3m_{Di}^2+\tilde{Q}_e^3m_{ei}^2+2\tilde{Q}_1^3m_{H_i^d}^2+2\tilde{Q}_2^3m_{H_i^u}^2+2\tilde{Q}_L^3m_{Li}^2\nonumber\\
+&{}+6\tilde{Q}_Q^3m_{Qi}^2+\tilde{Q}_S^3m_{Si}^2+3\tilde{Q}_u^3m_{ui}^2\big )+2\tilde{Q}_u\tilde{Q}_{H'}^2m_{H'}^2+2\tilde{Q}_u\tilde{Q}_{\overline{H'}}^2m_{\overline{H'}}^2\nonumber\\
+&{}+\tilde{Q}_u\sum_{i=1}^3\big ( 3\tilde{Q}_d^2m_{di}^2+3\tilde{Q}_{\overline{D}}^2m_{\overline{D}i}^2+3\tilde{Q}_D^2m_{Di}^2+\tilde{Q}_e^2m_{ei}^2+2\tilde{Q}_1^2m_{H_i^d}^2+2\tilde{Q}_2^2m_{H_i^u}^2+2\tilde{Q}_L^2m_{Li}^2\nonumber\\
+&{}+6\tilde{Q}_Q^2m_{Qi}^2+\tilde{Q}_S^2m_{Si}^2+3\tilde{Q}_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmu222BetaTwoLoop}\\
 b_{m_{u3}^2}^{(2)}&=.\label{eq:USSMmu222Ot2Coeff}

### 2015-03-02 paper/e6ssm-tuning-paper.tex
Removed tildes on U(1)_N charges to avoid potential confusion, especially since they should be unnecessary when ignoring U(1) mixing

--- 2015-02-25 paper/e6ssm-tuning-paper.tex
@@
 |H_2|^2-|H_1|^2\right )^2+\frac{g_2^2}{2}|H_1^\dagger
-H_2|^2+\frac{g_1'^2}{2}(\tilde{Q}_1|H_1|^2+\tilde{Q}_2|H_2|^2+\tilde{Q}_S|S|^2)^2,\label{eq:E6VDterms}\\ V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big
+H_2|^2+\frac{g_1'^2}{2}(Q_1|H_1|^2+Q_2|H_2|^2+Q_S|S|^2)^2,\label{eq:E6VDterms}\\ V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big
 [\lambda A_\lambda S(H_1\cdot H_2)+\textrm{h.c.}\Big
@@
 $SU(2)$, (non-GUT normalized) $U(1)_Y$ and $U(1)'$ gauge couplings
-respectively and $\bar{g}^2=g_2^2+g'^2$. The charges $\tilde{Q}_1$,
-$\tilde{Q}_2$ and $\tilde{Q}_S$ are effective $U(1)'$ charges for
+respectively and $\bar{g}^2=g_2^2+g'^2$. The charges $Q_1$,
+$Q_2$ and $Q_S$ are effective $U(1)'$ charges for
 $H_1$, $H_2$ and $S$, respectively. The term $\Delta V$ contains the
@@
 D_\phi\equiv \frac{g_1'^2}{2}\left (
-\tilde{Q}_1v_1^2+\tilde{Q}_2v_2^2+\tilde{Q}_Ss^2\right
-)\tilde{Q}_\phi.
+Q_1v_1^2+Q_2v_2^2+Q_Ss^2\right
+)Q_\phi.
 \end{equation}
@@
 required in the E$_6$SSM with $U(1)'=U(1)_N$, so that
-$|D_{H_1}|,|D_{H_2}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq
+$|D_{H_1}|,|D_{H_2}|\gg M_Z^2$ for $E_6$ models with $Q_S\neq
 0$. As a result the remaining terms on the right-hand side of
@@
 associated with having a reduced need for heavy superpartners. In
-$U(1)$ extended models for which $\tilde{Q}_S\neq 0$, the importance
+$U(1)$ extended models for which $Q_S\neq 0$, the importance
 of the $Z^\prime$ mass to the fine tuning in these models can be made
@@
 \begin{align}
-c(\theta,\tan\beta)&=1-\frac{4}{\left ( \tan^2\beta-1\right )}\frac{g_1'^2}{\bar{g}^2}\left ( \tilde{Q}_1-\tilde{Q}_2\tan^2\beta \right )\left ( \tilde{Q}_1\cos^2\beta+\tilde{Q}_2\sin^2\beta \right ),\label{eq:cdefn}\\
-d(\theta,\tan\beta)&= \frac{\tilde{Q}_1-\tilde{Q}_2\tan^2\beta}{\tilde{Q}_S\left ( \tan^2\beta - 1\right )}.\label{eq:ddefn}
+c(\theta,\tan\beta)&=1-\frac{4}{\left ( \tan^2\beta-1\right )}\frac{g_1'^2}{\bar{g}^2}\left ( Q_1-Q_2\tan^2\beta \right )\left ( Q_1\cos^2\beta+Q_2\sin^2\beta \right ),\label{eq:cdefn}\\
+d(\theta,\tan\beta)&= \frac{Q_1-Q_2\tan^2\beta}{Q_S\left ( \tan^2\beta - 1\right )}.\label{eq:ddefn}
 \end{align}
@@
 \ba
-\frac{\partial f_1}{\partial \tan\beta}&=&-\frac{2M_Z}{\bar{g}}\,\cos^2\beta\left \{ \frac{\lambda A_\lambda s}{\sqrt{2}}\,\cos\beta+\sin\beta \left [ m_{H_d}^2+\frac{s^2}{2}\left ( \lambda^2+g_1'^2\tilde{Q}_1\tilde{Q}_S \right )\right.\right.\nonumber\\
-&&\left.\left.+M_Z^2\left ( \frac{5}{2}-\frac{4\lambda^2}{\bar{g}^2}-\frac{4g_1'^2}{\bar{g}^2}\tilde{Q}_1\tilde{Q}_2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_1^2\right )\right ]+3M_Z^2\,\sin^3\beta\left [ \frac{2\lambda^2}{\bar{g}^2}-1\right.\right.\nonumber\\
-&&\left.\left.+\frac{2g_1'^2}{\bar{g}^2}\left ( \tilde{Q}_1\tilde{Q}_2-\tilde{Q}_1^2\right )\right ]\right \},\nonumber\\
-\frac{\partial f_1}{\partial s}&=&\frac{2M_Z}{\bar{g}}\left [ s\left ( \lambda^2+g_1'^2\tilde{Q}_1\tilde{Q}_S\right )\,\cos\beta-\frac{\lambda A_\lambda}{\sqrt{2}}\,\sin\beta \right ],\nonumber\\
-\frac{\partial f_2}{\partial \tan\beta}&=&\frac{2M_Z}{\bar{g}}\,\cos^2\beta\left \{ \frac{\lambda A_\lambda s}{\sqrt{2}}\,\sin\beta+\cos\beta\left [ m_{H_u}^2+\frac{s^2}{2}\left ( \lambda^2+g_1'^2\tilde{Q}_2\tilde{Q}_S \right )\right.\right.\nonumber\\
-&&\left.+M_Z^2\left ( \frac{5}{2}-\frac{4\lambda^2}{\bar{g}^2}-\frac{4g_1'^2}{\bar{g}^2}\tilde{Q}_1\tilde{Q}_2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_2^2\right )\right ]+3M_Z^2\,\cos^3\beta \left [ \frac{2\lambda^2}{\bar{g}^2}-1\right.\nonumber\\
-&&\left.\left.+\frac{2g_1'^2}{\bar{g}^2}\left ( \tilde{Q}_1\tilde{Q}_2-\tilde{Q}_2^2\right )\right ]\right \},\nonumber\\
-\frac{\partial f_2}{\partial s}&=&\frac{2M_Z}{\bar{g}}\left [ s\left ( \lambda^2+g_1'^2\tilde{Q}_2\tilde{Q}_S\right )\,\sin\beta-\frac{\lambda A_\lambda}{\sqrt{2}}\,\cos\beta\right ],\nonumber\\
-\frac{\partial f_3}{\partial \tan\beta}&=&\frac{2M_Z^2}{\bar{g}^2}\,\cos^2\beta\left [ g_1'^2\tilde{Q}_Ss\left ( \tilde{Q}_2-\tilde{Q}_1\right )\,\sin 2\beta-\sqrt{2}\lambda A_\lambda\,\cos 2\beta\right ],\nonumber\\
-\frac{\partial f_3}{\partial s}&=&m_S^2+\frac{2\lambda^2M_Z^2}{\bar{g}^2}+\frac{g_1'^2}{2}\tilde{Q}_S\left [\frac{4M_Z^2}{\bar{g}^2}\left ( \tilde{Q}_1\,\cos^2\beta+\tilde{Q}_2\,\sin^2\beta\right ) +3\tilde{Q}_S s^2\right ].\nonumber
+\frac{\partial f_1}{\partial \tan\beta}&=&-\frac{2M_Z}{\bar{g}}\,\cos^2\beta\left \{ \frac{\lambda A_\lambda s}{\sqrt{2}}\,\cos\beta+\sin\beta \left [ m_{H_d}^2+\frac{s^2}{2}\left ( \lambda^2+g_1'^2Q_1Q_S \right )\right.\right.\nonumber\\
+&&\left.\left.+M_Z^2\left ( \frac{5}{2}-\frac{4\lambda^2}{\bar{g}^2}-\frac{4g_1'^2}{\bar{g}^2}Q_1Q_2+\frac{6g_1'^2}{\bar{g}^2}Q_1^2\right )\right ]+3M_Z^2\,\sin^3\beta\left [ \frac{2\lambda^2}{\bar{g}^2}-1\right.\right.\nonumber\\
+&&\left.\left.+\frac{2g_1'^2}{\bar{g}^2}\left ( Q_1Q_2-Q_1^2\right )\right ]\right \},\nonumber\\
+\frac{\partial f_1}{\partial s}&=&\frac{2M_Z}{\bar{g}}\left [ s\left ( \lambda^2+g_1'^2Q_1Q_S\right )\,\cos\beta-\frac{\lambda A_\lambda}{\sqrt{2}}\,\sin\beta \right ],\nonumber\\
+\frac{\partial f_2}{\partial \tan\beta}&=&\frac{2M_Z}{\bar{g}}\,\cos^2\beta\left \{ \frac{\lambda A_\lambda s}{\sqrt{2}}\,\sin\beta+\cos\beta\left [ m_{H_u}^2+\frac{s^2}{2}\left ( \lambda^2+g_1'^2Q_2Q_S \right )\right.\right.\nonumber\\
+&&\left.+M_Z^2\left ( \frac{5}{2}-\frac{4\lambda^2}{\bar{g}^2}-\frac{4g_1'^2}{\bar{g}^2}Q_1Q_2+\frac{6g_1'^2}{\bar{g}^2}Q_2^2\right )\right ]+3M_Z^2\,\cos^3\beta \left [ \frac{2\lambda^2}{\bar{g}^2}-1\right.\nonumber\\
+&&\left.\left.+\frac{2g_1'^2}{\bar{g}^2}\left ( Q_1Q_2-Q_2^2\right )\right ]\right \},\nonumber\\
+\frac{\partial f_2}{\partial s}&=&\frac{2M_Z}{\bar{g}}\left [ s\left ( \lambda^2+g_1'^2Q_2Q_S\right )\,\sin\beta-\frac{\lambda A_\lambda}{\sqrt{2}}\,\cos\beta\right ],\nonumber\\
+\frac{\partial f_3}{\partial \tan\beta}&=&\frac{2M_Z^2}{\bar{g}^2}\,\cos^2\beta\left [ g_1'^2Q_Ss\left ( Q_2-Q_1\right )\,\sin 2\beta-\sqrt{2}\lambda A_\lambda\,\cos 2\beta\right ],\nonumber\\
+\frac{\partial f_3}{\partial s}&=&m_S^2+\frac{2\lambda^2M_Z^2}{\bar{g}^2}+\frac{g_1'^2}{2}Q_S\left [\frac{4M_Z^2}{\bar{g}^2}\left ( Q_1\,\cos^2\beta+Q_2\,\sin^2\beta\right ) +3Q_S s^2\right ].\nonumber
 \ea
@@
 \ba
-\frac{\partial f_1}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\cos\beta\left ( m_{H_d}^2+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}\tilde{Q}_1\tilde{Q}_Ss^2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_1^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\sin\beta\nonumber \\
-&&+\frac{3M_Z^2}{\bar{g}}\,\cos\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\sin\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left(\tilde{Q}_1\tilde{Q}_2-\tilde{Q}_1^2\right )\right ],\nonumber\\
-\frac{\partial f_2}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\sin\beta\left ( m_{H_u}^2+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}\tilde{Q}_2\tilde{Q}_Ss^2+\frac{6g_1'^2}{\bar{g}^2}\tilde{Q}_2^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\cos\beta \nonumber\\
-&&-\frac{3M_Z^2}{\bar{g}}\,\sin\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\cos\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left ( \tilde{Q}_1\tilde{Q}_2-\tilde{Q_2}^2\right )\right ],\nonumber \\
-\frac{\partial f_3}{\partial M_Z}&=&\frac{4M_Z}{\bar{g}^2}\left [ \lambda^2s-\frac{\lambda A_\lambda}{\sqrt{2}}\,\sin 2\beta+g_1'^2\tilde{Q}_Ss\left ( \tilde{Q}_1\,\cos^2\beta+\tilde{Q}_2\,\sin^2\beta \right )\right ].\nonumber
+\frac{\partial f_1}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\cos\beta\left ( m_{H_d}^2+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}Q_1Q_Ss^2+\frac{6g_1'^2}{\bar{g}^2}Q_1^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\sin\beta\nonumber \\
+&&+\frac{3M_Z^2}{\bar{g}}\,\cos\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\sin\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left(Q_1Q_2-Q_1^2\right )\right ],\nonumber\\
+\frac{\partial f_2}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\sin\beta\left ( m_{H_u}^2+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}Q_2Q_Ss^2+\frac{6g_1'^2}{\bar{g}^2}Q_2^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\cos\beta \nonumber\\
+&&-\frac{3M_Z^2}{\bar{g}}\,\sin\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\cos\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left ( Q_1Q_2-\tilde{Q_2}^2\right )\right ],\nonumber \\
+\frac{\partial f_3}{\partial M_Z}&=&\frac{4M_Z}{\bar{g}^2}\left [ \lambda^2s-\frac{\lambda A_\lambda}{\sqrt{2}}\,\sin 2\beta+g_1'^2Q_Ss\left ( Q_1\,\cos^2\beta+Q_2\,\sin^2\beta \right )\right ].\nonumber
 \ea
@@
 \beta_{g_1}^{(1)}&=\frac{48}{5}g_1^3,\label{eq:USSMg1BetaOneLoop}\\
-\beta_{g_1}^{(2)}&=\frac{2}{25} g_1^3 \left(30 g_1'^2 \Pi_{\tilde{Q}}^Y-35 y_b^2+117 g_1^2+135 g_2^2+300 g_3^2-10 \Sigma _{\kappa }-15
+\beta_{g_1}^{(2)}&=\frac{2}{25} g_1^3 \left(30 g_1'^2 \Pi_{Q}^Y-35 y_b^2+117 g_1^2+135 g_2^2+300 g_3^2-10 \Sigma _{\kappa }-15
    \Sigma _{\lambda }-65 y_t^2-45 y_{\tau }^2\right),\label{eq:USSMg1BetaTwoLoop}\\
 \beta_{g_2}^{(1)}&=4g_2^3,\label{eq:USSMg2BetaOneLoop}\\
-\beta_{g_2}^{(2)}&=\frac{2}{5} g_2^3 \left(5 g_1'^2 \Pi _{\tilde{Q}}^L-15 y_b^2+9 g_1^2+115 g_2^2+60 g_3^2-5 \Sigma _{\lambda }-15
+\beta_{g_2}^{(2)}&=\frac{2}{5} g_2^3 \left(5 g_1'^2 \Pi _{Q}^L-15 y_b^2+9 g_1^2+115 g_2^2+60 g_3^2-5 \Sigma _{\lambda }-15
    y_t^2-5 y_{\tau }^2\right),\label{eq:USSMg2BetaTwoLoop}\\
-\beta_{g_1'}^{(1)}&=g_1'^3\Sigma_{\tilde{Q}},\label{eq:USSMg1pBetaOneLoop}\\
-\beta_{g_1'}^{(2)}&=\frac{2}{5} g_1'^3 \left(-15 \Sigma _{\kappa } \left(\tilde{Q}_{\bar{D}}^2+\tilde{Q}_D^2+\tilde{Q}_S^2\right)-30
-   y_b^2 \left(\tilde{Q}_d^2+\tilde{Q}_1^2+\tilde{Q}_Q^2\right)+120 g_3^2 \Pi _{\tilde{Q}}^C\right.\nonumber \\
+\beta_{g_1'}^{(1)}&=g_1'^3\Sigma_{Q},\label{eq:USSMg1pBetaOneLoop}\\
+\beta_{g_1'}^{(2)}&=\frac{2}{5} g_1'^3 \left(-15 \Sigma _{\kappa } \left(Q_{\bar{D}}^2+Q_D^2+Q_S^2\right)-30
+   y_b^2 \left(Q_d^2+Q_1^2+Q_Q^2\right)+120 g_3^2 \Pi _{Q}^C\right.\nonumber \\
 &\quad{}-10 y_{\tau }^2
-   \left(\tilde{Q}_e^2+\tilde{Q}_L^2+\tilde{Q}_1^2\right)+15 g_2^2 \Pi _{\tilde{Q}}^L+10 g_1'^2 \Pi _{\tilde{Q}}+6
-   g_1^2 \Pi _{\tilde{Q}}^Y\nonumber\\
-&\quad\left.{}-10 \Sigma _{\lambda } \left(\tilde{Q}_S^2+\tilde{Q}_1^2+\tilde{Q}_2^2\right)-30 y_t^2
-   \left(\tilde{Q}_u^2+\tilde{Q}_2^2+\tilde{Q}_Q^2\right)\right).\label{eq:USSMg1pBetaTwoLoop}
+   \left(Q_e^2+Q_L^2+Q_1^2\right)+15 g_2^2 \Pi _{Q}^L+10 g_1'^2 \Pi _{Q}+6
+   g_1^2 \Pi _{Q}^Y\nonumber\\
+&\quad\left.{}-10 \Sigma _{\lambda } \left(Q_S^2+Q_1^2+Q_2^2\right)-30 y_t^2
+   \left(Q_u^2+Q_2^2+Q_Q^2\right)\right).\label{eq:USSMg1pBetaTwoLoop}
 \end{align}
@@
 \begin{align*}
-\Sigma_{\tilde{Q}}=\sum_i \tilde{Q}_i^2=\frac{321}{40}\cos^2\theta+\frac{217}{24}\sin^2\theta+\frac{27}{8\sqrt{15}}\sin 2\theta
+\Sigma_{Q}=\sum_i Q_i^2=\frac{321}{40}\cos^2\theta+\frac{217}{24}\sin^2\theta+\frac{27}{8\sqrt{15}}\sin 2\theta
 \end{align*}
@@
 \begin{align*}
-\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i=-\frac{3}{\sqrt{10}}\cos\theta-\frac{1}{\sqrt{6}}\sin\theta,\\
-\Pi_{\tilde{Q}}&=\sum_i \tilde{Q}_i^4\\
+\Sigma_{Q}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^YQ_i=-\frac{3}{\sqrt{10}}\cos\theta-\frac{1}{\sqrt{6}}\sin\theta,\\
+\Pi_{Q}&=\sum_i Q_i^4\\
 &=\frac{2049}{1600}\cos^4\theta+\frac{483}{80\sqrt{15}}\cos^3\theta\sin\theta+\frac{681}{160}\cos^2\theta\sin^2\theta+\frac{9}{16\sqrt{15}}\cos\theta\sin^3\theta+\frac{1297}{576}\sin^4\theta,\\
-\Pi_{\tilde{Q}}^Y&=\sum_i \left ( \sqrt{\frac{5}{3}}Q_i^Y\right )^2\tilde{Q}_i^2=\frac{59}{40}\cos^2\theta+\frac{31}{24}\sin^2\theta+\frac{3}{8\sqrt{15}}\sin 2\theta,\\
-\Pi_{\tilde{Q}}^L&=3\tilde{Q}_1^2+3\tilde{Q}_2^2+\tilde{Q}_{H'}^2+\tilde{Q}_{\overline{H'}}^2+3\tilde{Q}_L^2+9\tilde{Q}_Q^2=\frac{39}{20}\cos^2\theta+\frac{19}{12}\sin^2\theta+\frac{3}{4\sqrt{15}}\sin 2\theta,\\
-\Pi_{\tilde{Q}}^C&=\tilde{Q}_d^2+\tilde{Q}_D^2+\tilde{Q}_{\overline{D}}^2+2\tilde{Q}_Q^2+\tilde{Q}_u^2=\frac{1}{2}.
+\Pi_{Q}^Y&=\sum_i \left ( \sqrt{\frac{5}{3}}Q_i^Y\right )^2Q_i^2=\frac{59}{40}\cos^2\theta+\frac{31}{24}\sin^2\theta+\frac{3}{8\sqrt{15}}\sin 2\theta,\\
+\Pi_{Q}^L&=3Q_1^2+3Q_2^2+Q_{H'}^2+Q_{\overline{H'}}^2+3Q_L^2+9Q_Q^2=\frac{39}{20}\cos^2\theta+\frac{19}{12}\sin^2\theta+\frac{3}{4\sqrt{15}}\sin 2\theta,\\
+\Pi_{Q}^C&=Q_d^2+Q_D^2+Q_{\overline{D}}^2+2Q_Q^2+Q_u^2=\frac{1}{2}.
 \end{align*}
@@
 b_{g_2}^{(2)}&=24g_2^5,\label{eq:USSMg2Ot2Coeff}\\
-b_{g_1'}^{(2)}&=\frac{3}{2}g_1'^5\Sigma_{\tilde{Q}}^2.\label{eq:USSMg1pOt2Coeff}
+b_{g_1'}^{(2)}&=\frac{3}{2}g_1'^5\Sigma_{Q}^2.\label{eq:USSMg1pOt2Coeff}
 \end{align}
@@
 \begin{align}
-\beta_\lambda^{(1)}&=\lambda  \left[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2-\frac{3}{5} g_1^2 -2 \left ( \tilde{Q}_1^2 + \tilde{Q}_2^2 + \tilde{Q}_S^2\right )g_1'^2 \right],\label{eq:USSMLambdaBetaOneLoop}\\
+\beta_\lambda^{(1)}&=\lambda  \left[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2-\frac{3}{5} g_1^2 -2 \left ( Q_1^2 + Q_2^2 + Q_S^2\right )g_1'^2 \right],\label{eq:USSMLambdaBetaOneLoop}\\
 \beta_\lambda^{(2)}&=\lambda \bigg \{ -2\lambda^2\left ( \lambda^2+2\Sigma_\lambda+3\Sigma_\kappa\right )-4\Pi_\lambda-6\Pi_\kappa-3\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right ) \nonumber\\
 &{} -3\left ( 3y_t^4+3y_b^4+2y_t^2y_b^2+y_\tau^2 \right )+6g_2^2\Sigma_\lambda+\frac{2}{5}g_1^2\left ( 2y_t^2-y_b^2+3y_\tau^2+2\Sigma_\kappa +3\Sigma_\lambda\right )\nonumber\\
-&{}\left.+g_1'^2\left [ 4\tilde{Q}_S^2\lambda^2 -6\left ( \tilde{Q}_2^2-\tilde{Q}_Q^2-\tilde{Q}_u^2\right )y_t^2-6\left ( \tilde{Q}_1^2-\tilde{Q}_Q^2-\tilde{Q}_d^2\right )y_b^2 \right.\right.\nonumber\\
-&{}\left.-2\left ( \tilde{Q}_1^2-\tilde{Q}_L^2-\tilde{Q}_e^2\right )y_\tau^2-6\left ( \tilde{Q}_S^2-\tilde{Q}_D^2-\tilde{Q}_{\overline{D}}^2 \right )\Sigma_\kappa-4\left ( \tilde{Q}_S^2-\tilde{Q}_1^2-\tilde{Q}_2^2\right )\Sigma_\lambda\right ]\nonumber\\
-&{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2\tilde{Q}_1^4+2\tilde{Q}_2^4+2\tilde{Q}_S^4+\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\Sigma_{\tilde{Q}}\right ]\nonumber\\
-&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [\tilde{Q}_1^2+\tilde{Q}_2^2+\left ( \tilde{Q}_2-\tilde{Q}_1\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\
+&{}\left.+g_1'^2\left [ 4Q_S^2\lambda^2 -6\left ( Q_2^2-Q_Q^2-Q_u^2\right )y_t^2-6\left ( Q_1^2-Q_Q^2-Q_d^2\right )y_b^2 \right.\right.\nonumber\\
+&{}\left.-2\left ( Q_1^2-Q_L^2-Q_e^2\right )y_\tau^2-6\left ( Q_S^2-Q_D^2-Q_{\overline{D}}^2 \right )\Sigma_\kappa-4\left ( Q_S^2-Q_1^2-Q_2^2\right )\Sigma_\lambda\right ]\nonumber\\
+&{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2Q_1^4+2Q_2^4+2Q_S^4+\left ( Q_1^2+Q_2^2+Q_S^2\right )\Sigma_{Q}\right ]\nonumber\\
+&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [Q_1^2+Q_2^2+\left ( Q_2-Q_1\right )\Sigma_{Q}^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\
 b_\lambda^{(2)}&=\lambda \bigg \{ 2\lambda^2\left ( 3\lambda^2 +4\Sigma_\lambda +6\Sigma_\kappa \right )+4\Pi_\lambda + 6\Pi_\kappa +6\left ( \Sigma_\lambda+\frac{3}{2}\Sigma_\kappa\right )^2+7\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\nonumber\\
@@
 &{}-3g_2^2\left ( 4\lambda^2+6y_t^2+6y_b^2+2y_\tau^2+4\Sigma_\lambda+3\Sigma_\kappa\right )-16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa \right )\nonumber\\
-&{}-2g_1'^2\left [ 4\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\left ( \lambda^2 +\Sigma_\lambda \right )+3\Sigma_\kappa\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2+\tilde{Q}_D^2+\tilde{Q}_{\overline{D}}^2\right )\right .\nonumber\\
-&{}+3y_b^2\left ( 2\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_d^2+\tilde{Q}_Q^2+\tilde{Q}_S^2 \right )+3y_t^2\left ( \tilde{Q}_1^2+2\tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_S^2+\tilde{Q}_u^2\right )\nonumber\\
-&{}\left.+y_\tau^2\left ( 2\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_e^2+\tilde{Q}_L^2+\tilde{Q}_S^2\right )\right ]-\frac{15}{2}g_2^4-\frac{279}{50}g_1^4\nonumber\\
-&{}+2g_1'^4\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right )\left (\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2-\Sigma_{\tilde{Q}}\right )+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\nonumber\\
-&{}+\frac{6}{5}g_1^2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right ) \bigg \}.\label{eq:USSMLambdaOt2Coeff}
+&{}-2g_1'^2\left [ 4\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( \lambda^2 +\Sigma_\lambda \right )+3\Sigma_\kappa\left ( Q_1^2+Q_2^2+Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\right .\nonumber\\
+&{}+3y_b^2\left ( 2Q_1^2+Q_2^2+Q_d^2+Q_Q^2+Q_S^2 \right )+3y_t^2\left ( Q_1^2+2Q_2^2+Q_Q^2+Q_S^2+Q_u^2\right )\nonumber\\
+&{}\left.+y_\tau^2\left ( 2Q_1^2+Q_2^2+Q_e^2+Q_L^2+Q_S^2\right )\right ]-\frac{15}{2}g_2^4-\frac{279}{50}g_1^4\nonumber\\
+&{}+2g_1'^4\left ( Q_1^2+Q_2^2+Q_S^2 \right )\left (Q_1^2+Q_2^2+Q_S^2-\Sigma_{Q}\right )+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\nonumber\\
+&{}+\frac{6}{5}g_1^2g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2 \right ) \bigg \}.\label{eq:USSMLambdaOt2Coeff}
 \end{align}
@@
 \begin{align}
-\beta_{a_\lambda}^{(1)}&=2\lambda \left [ 2 \Sigma_{a_\lambda}+3\Sigma_{a_\kappa}+3y_ta_t+3y_ba_b+y_\tau a_\tau+\frac{3}{5}g_1^2M_1+3g_2^2 M_2+2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\right ]\nonumber\\
-&{}+a_\lambda \left [ 6\lambda^2+2\Sigma_\lambda+3\Sigma_\kappa+3y_t^2+3y_b^2+y_\tau^2-\frac{3}{5}g_1^2-3g_2^2-2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right )\right ],\label{eq:USSMTLambdaBetaOneLoop}\\
+\beta_{a_\lambda}^{(1)}&=a_\lambda \left[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2-\frac{3}{5} g_1^2 -2 \left ( Q_1^2 + Q_2^2 + Q_S^2\right )g_1'^2 \right]\nonumber\\
+&{}+\lambda \left [ 4\lambda a_\lambda +4\Sigma_{a_\lambda}+6\Sigma_{a_\kappa}+6y_ta_t+6y_ba_b+2y_\tau a_\tau +6g_2^2M_2+\frac{6}{5}g_1^2M_1\right.\nonumber\\
+&{}\left.+4g_1'^2M_1'\left ( Q_1^2+Q_2^2+Q_S^2 \right )\right ],\label{eq:USSMTLambdaBetaOneLoop}\\
 \beta_{a_\lambda}^{(2)}&=,\label{eq:USSMTLambdaBetaTwoLoop}\\
@@
 \end{align*}
-Note that $a_{\lambda_i}\equiv\lambda_i A_{\lambda_i}$, $a_{\kappa_i}\equiv\kappa_i A_{\kappa_i}$, $a_t\equiv y_t A_t$, $a_b\equiv y_b A_b$ and $a_\tau= y_\tau A_\tau$. Definining 
+Note that $a_{\lambda_i}\equiv\lambda_i A_{\lambda_i}$, $a_{\kappa_i}\equiv\kappa_i A_{\kappa_i}$, $a_t\equiv y_t A_t$, $a_b\equiv y_b A_b$ and $a_\tau= y_\tau A_\tau$. Defining 
 \begin{align}
 \Sigma_1&=\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2-m_{Li}^2+m_{H_{ui}}^2-m_{H_{di}}^2+m_{\overline{D}_i}^2-m_{Di}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1}\\
-\Sigma_1'&=\sum_{i=1}^3\left ( 6\tilde{Q}_Qm_{Qi}^2+3\tilde{Q}_um_{ui}^2+3\tilde{Q}_dm_{di}^2+\tilde{Q}_em_{ei}^2+2\tilde{Q}_Lm_{Li}^2+2\tilde{Q}_2m_{H_{ui}}^2+2\tilde{Q}_1m_{H_{di}}^2\right.\nonumber\\
-&\quad{}\left.+\tilde{Q}_Sm_{Si}^2+3\tilde{Q}_{\overline{D}}m_{\overline{D}_i}^2+3\tilde{Q}_Dm_{Di}^2\right )+2\tilde{Q}_{H'}m_{H'}^2+2\tilde{Q}_{\overline{H'}}m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1Pr}
+\Sigma_1'&=\sum_{i=1}^3\left ( 6Q_Qm_{Qi}^2+3Q_um_{ui}^2+3Q_dm_{di}^2+Q_em_{ei}^2+2Q_Lm_{Li}^2+2Q_2m_{H_{ui}}^2+2Q_1m_{H_{di}}^2\right.\nonumber\\
+&\quad{}\left.+Q_Sm_{Si}^2+3Q_{\overline{D}}m_{\overline{D}_i}^2+3Q_Dm_{Di}^2\right )+2Q_{H'}m_{H'}^2+2Q_{\overline{H'}}m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1Pr}
 \end{align}
@@
 \beta_{m_{H_d}^2}^{(1)}&=2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+2a_\lambda^2+6y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+6a_b^2\nonumber\\
-&{}+2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+2a_\tau^2-6g_2^2 M_2^2-\frac{6}{5}g_1^2 M_1^2-8\tilde{Q}_1^2g_1'^2 M_1'^2\nonumber\\
-&{}-\frac{3}{5}g_1^2\Sigma_1+2\tilde{Q}_1g_1'^2\Sigma_1',\label{eq:USSMmHd2BetaOneLoop}\\
+&{}+2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+2a_\tau^2-6g_2^2 M_2^2-\frac{6}{5}g_1^2 M_1^2-8Q_1^2g_1'^2 M_1'^2\nonumber\\
+&{}-\frac{3}{5}g_1^2\Sigma_1+2Q_1g_1'^2\Sigma_1',\label{eq:USSMmHd2BetaOneLoop}\\
 \beta_{m_{H_d}^2}^{(2)}&=,\label{eq:USSMmHd2BetaTwoLoop}\\
@@
 \beta_{m_{H_u}^2}^{(1)}&=2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+2a_\lambda^2+6y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+6a_t^2\nonumber\\
-&{}-6g_2^2M_2^2-\frac{6}{5}g_1^2M_1^2-8\tilde{Q}_2^2g_1'^2M_1'^2+\frac{3}{5}g_1^2\Sigma_1+2\tilde{Q}_2g_1'^2\Sigma_1',\label{eq:USSMmHu2BetaOneLoop}\\
+&{}-6g_2^2M_2^2-\frac{6}{5}g_1^2M_1^2-8Q_2^2g_1'^2M_1'^2+\frac{3}{5}g_1^2\Sigma_1+2Q_2g_1'^2\Sigma_1',\label{eq:USSMmHu2BetaOneLoop}\\
 \beta_{m_{H_u}^2}^{(2)}&=,\label{eq:USSMmHu2BetaTwoLoop}\\
@@
 \beta_{m_S^2}^{(1)}&=\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2+6\kappa_i\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+6a_{\kappa_i}^2\right ]\nonumber\\
-&{}-8\tilde{Q}_S^2g_1'^2M_1'^2+2\tilde{Q}_Sg_1'^2\Sigma_1',\label{eq:USSMms2BetaOneLoop}\\
+&{}-8Q_S^2g_1'^2M_1'^2+2Q_Sg_1'^2\Sigma_1',\label{eq:USSMms2BetaOneLoop}\\
 \beta_{m_S^2}^{(2)}&=,\label{eq:USSMms2BetaTwoLoop}\\
@@
 \begin{align}
-\beta_{y_t}^{(1)}&=y_t\left [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2-2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )\right ],\label{eq:USSMYu22BetaOneLoop}\\
-\beta_{y_t}^{(2)}&=,\label{eq:USSMYu22BetaTwoLoop}\\
-b_{y_t}^{(2)}&=,\label{eq:USSMYu22Ot2Coeff}
+\beta_{y_t}^{(1)}&=y_t\left [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2-2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\right ],\label{eq:USSMYu22BetaOneLoop}\\
+\beta_{y_t}^{(2)}&=y_t\bigg \{-22y_t^4-5y_b^4-5y_t^2y_b^2-y_b^2y_\tau^2-\lambda^2 \left ( \lambda^2+3y_t^2+4y_b^2+y_\tau^2+2\Sigma_\lambda + 3\Sigma_\kappa\right )\nonumber\\
+&{}+2g_1'^2\left [ \lambda^2\left ( Q_1^2-Q_2^2+Q_S^2 \right )+2y_t^2\left ( 2Q_Q^2+Q_u^2\right )+y_b^2\left ( Q_1^2-Q_Q^2+Q_d^2\right )\right ]\nonumber\\
+&{}+16g_3^2y_t^2+6g_2^2y_t^2+g_1^2\left ( \frac{6}{5}y_t^2+\frac{2}{5}y_b^2\right )+\frac{128}{9}g_3^4+\frac{33}{2}g_2^4+\frac{3913}{450}g_1^4\nonumber\\
+&{}+2g_1'^4\left [ 2\left ( Q_2^4+Q_Q^4+Q_u^4\right )+\left ( Q_2^2+Q_Q^2+Q_u^2\right )\Sigma_{Q}\right ]+8g_3^2g_2^2+\frac{136}{45}g_3^2g_1^2\nonumber\\
+&{}+\frac{32}{3}g_3^2g_1'^2\left ( Q_Q^2+Q_u^2\right )+g_2^2g_1^2+6g_2^2g_1'^2\left ( Q_2^2+Q_Q^2\right )\nonumber\\
+&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2+\left ( 3Q_2+Q_Q-4Q_u\right )\Sigma_{Q}^Y\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\
+b_{y_t}^{(2)}&=y_t\bigg \{ 54y_t^4+\frac{13}{2}y_b^4+13y_t^2y_b^2+y_b^2y_\tau^2+\lambda^2\left ( \frac{5}{2}\lambda^2+15y_t^2+5y_b^2+y_\tau^2+2\Sigma_\lambda+3\Sigma_\kappa \right )\nonumber\\
+&{}-\frac{16}{3}g_3^2\left ( \lambda^2+2y_b^2+12y_t^2\right )-6g_2^2\left ( \lambda^2+y_b^2+6y_t^2\right )-g_1^2\left ( \frac{22}{15}\lambda^2+\frac{4}{3}y_b^2+\frac{52}{5}y_t^2\right )\nonumber\\
+&{}-2g_1'^2\left [ \lambda^2 \left (Q_1^2+2Q_2^2+Q_S^2+Q_Q^2+Q_u^2 \right )+y_b^2\left ( Q_1^2+Q_2^2+2Q_Q^2+Q_u^2+Q_d^2\right )\right.\nonumber\\
+&{}\left.+12y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\right ]+\frac{128}{9}g_3^4-\frac{15}{2}g_2^4-\frac{143}{18}g_1^4\nonumber\\
+&{}+2g_1'^4\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( Q_2^2+Q_Q^2+Q_u^2-\Sigma_{Q}\right )+16g_3^2g_2^2+\frac{208}{45}g_3^2g_1^2\nonumber\\
+&{}+\frac{32}{3}g_3^2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )+\frac{13}{5}g_2^2g_1^2+6g_2^2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\nonumber\\
+&{}+\frac{26}{15}g_1^2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg \},\label{eq:USSMYu22Ot2Coeff}
 \end{align}
@@
 \begin{align}
-\beta_{a_t}^{(1)}&=,\label{eq:USSMTYu22BetaOneLoop}\\
+\beta_{a_t}^{(1)}&=a_t\left [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2-2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\right ]\nonumber\\
+&{}+y_t\left [ 2\lambda a_\lambda + 12y_ta_t+2y_ba_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1\right.\nonumber\\
+&{}\left.+4g_1'^2M_1'\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\right ],\label{eq:USSMTYu22BetaOneLoop}\\
 \beta_{a_t}^{(2)}&=,\label{eq:USSMTYu22BetaTwoLoop}\\
@@
 \begin{align}
-\beta_{m_{Q3}^2}^{(1)}&=,\label{eq:USSMmq222BetaOneLoop}\\
+\beta_{m_{Q3}^2}^{(1)}&=2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+2a_t^2+2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+2a_b^2\nonumber\\
+&{}-\frac{32}{3}g_3^2M_3^2-6g_2^2M_2^2-\frac{2}{15}g_1^2M_1^2-8Q_Q^2g_1'^2M_1'^2+\frac{1}{5}g_1^2\Sigma_1+2Q_Qg_1'^2\Sigma_1',\label{eq:USSMmq222BetaOneLoop}\\
 \beta_{m_{Q3}^2}^{(2)}&=,\label{eq:USSMmq222BetaTwoLoop}\\
@@
 \begin{align}
-\beta_{m_{u3}^2}^{(1)}&=,\label{eq:USSMmu222BetaOneLoop}\\
-\beta_{m_{u3}^2}^{(2)}&=,\label{eq:USSMmu222BetaTwoLoop}\\
+\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+4a_t^2-\frac{32}{3}g_3^2M_3^2-\frac{32}{15}g_1^1M_1^2-8Q_u^2g_1'^2M_1'^2\nonumber\\
+&{}-\frac{4}{5}g_1^2\Sigma_1+2Q_ug_1'^2\Sigma_1',\label{eq:USSMmu222BetaOneLoop}\\
+\beta_{m_{u3}^2}^{(2)}&=-32y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )-4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )\nonumber\\
+&{}-64y_t^2a_t^2-4\left ( y_ta_b+y_ba_t\right )^2-4\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )\nonumber\\
+&{}-4\left ( \lambda a_t + y_ta_\lambda \right )^2+12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_2^2\right )+12g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
+&{}-\frac{4}{5}g_1^2y_t^2\left ( -5m_{H_u}^2-m_{Q3}^2+9m_{u3}^2+2M_1^2\right )-\frac{4}{5}g_1^2\left ( a_t^2-2y_ta_tM_1 \right )\nonumber\\
+&{}-\frac{8}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q3}^2-2m_{d3}^2\right )-\frac{8}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
+&{}-\frac{8}{5}g_1^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_{Di}^2-m_{\overline{D}i}^2 \right )+\lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2 \right )\right ]\nonumber\\
+&{}+8g_1'^2y_t^2\left ( Q_2^2+Q_Q^2-Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )\nonumber\\
+&{}+8g_1'^2\left ( Q_2^2+Q_Q^2-Q_u^2\right )\left ( a_t^2-2y_ta_tM_1'\right )-24Q_ug_1'^2y_t^2\left (Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )\nonumber\\
+&{}-24Q_ug_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )-8Q_ug_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )\nonumber\\
+&{}-12Q_ug_1'^2\sum_{i=1}^3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2\right )\nonumber\\
+&{}-8Q_ug_1'^2\sum_{i=1}^3\left ( Q_1m_{H_d}^2+Q_2m_{H_u}^2+Q_Sm_S^2\right )\nonumber\\
+&{}+\frac{16}{3}g_3^4\left [ 10M_3^2+\sum_{i=1}^3\left ( m_{di}^2+m_{Di}^2+m_{\overline{D}i}^2+2m_{Qi}^2+m_{ui}^2\right )\right ]\nonumber\\
+&{}+\frac{64}{45}g_3^2g_1^2\left [ 8\left (M_1^2+M_1M_3+M_3^2\right )-3\sum_{i=1}^3\left ( m_{di}^2-m_{Di}^2+m_{\overline{D}i}^2+m_{qi}^2-2m_{ui}^2\right )\right ]\nonumber\\
+&{}+\frac{8}{3}Q_ug_3^2g_1'^2\bigg [ 16Q_u\left (M_1'^2+M_1'M_3+M_3^2\right )\nonumber\\
+&{}+12\sum_{i=1}^3\left ( Q_dm_{di}^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2+2Q_Qm_{Qi}^2+Q_um_{ui}^2\right )\bigg ]\nonumber\\
+&{}+\frac{12}{5}g_2^2g_1^2\left [ m_{H'}^2-m_{\overline{H'}}^2+\sum_{i=1}^3\left ( m_{H_i^d}^2-m_{H_i^u}^2+m_{Li}^2-m_{Qi}^2\right )\right ]\nonumber\\
+&{}+12Q_ug_2^2g_1'^2\left [ Q_{H'}m_{H'}^2+Q_{\overline{H'}}m_{\overline{H'}}^2+\sum_{i=1}^3\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Lm_{Li}^2+3Q_Qm_{Qi}^2\right )\right ]\nonumber\\
+&{}+\frac{4}{75}g_1^4\bigg [ 1261M_1^2+21m_{H'}^2+3m_{\overline{H'}}^2\nonumber\\
+&{}+\sum_{i=1}^3\left ( 4m_{di}^2+12m_{Di}^2+4m_{\overline{D}i}^2-12m_{ei}^2+21m_{H_i^d}^2+3m_{H_i^u}^2+21m_{Li}^2+3m_{Qi}^2+64m_{ui}^2\right )\bigg ]\nonumber\\
+&{}+\frac{4}{15}g_1^2g_1'^2\bigg [ -8Q_u\big ( 9Q_d+9Q_{\overline{D}}-9Q_D+9Q_e-9Q_1+9Q_2+3Q_{\overline{H'}}-3Q_{H'}-9Q_L\nonumber\\
+&{}+9Q_Q-22Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2 \right )+12Q_{H'}^2m_{H'}^2-Q_{\overline{H'}}^2m_{\overline{H'}}^2\nonumber\\
+&{}+12\sum_{i=1}^3\big ( -Q_d^2m_{di}^2-Q_{\overline{D}}^2m_{\overline{D}i}^2+Q_D^2m_{Di}^2-Q_e^2m_{ei}^2+Q_1^2m_{H_i^d}^2-Q_2^2m_{H_i^u}^2+Q_L^2m_{Li}^2\nonumber\\
+&{}-Q_Q^2m_{Qi}^2+Q_u^2m_{ui}^2\big )-15Q_{\overline{H'}}Q_um_{\overline{H'}}^2+33Q_{H'}Q_um_{H'}^2+Q_u\sum_{i=1}^3\big ( -18Q_dm_{di}^2\nonumber\\
+&{}-18Q_{\overline{D}}m_{\overline{D}i}^2+30Q_Dm_{Di}^2-6Q_em_{ei}^2+33Q_1m_{H_i^d}^2-15Q_2m_{H_i^u}^2+33Q_Lm_{Li}^2\nonumber\\
+&{}-21Q_Qm_{Qi}^2+84Q_um_{ui}^2\big )\bigg ]+8Q_ug_1'^4\bigg [ 3Q_uM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2\nonumber\\
+&{}+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2+18Q_Q^2+3Q_S^2+11Q_u^2 \big )+2Q_{H'}^3m_{H'}^2+2Q_{\overline{H'}}^3m_{\overline{H'}}^2\nonumber\\
+&{}+\sum_{i=1}^3\big ( 3Q_d^3m_{di}^2+3Q_{\overline{D}}^3m_{\overline{D}i}^2+3Q_D^3m_{Di}^2+Q_e^3m_{ei}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{Li}^2\nonumber\\
+&{}+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )+2Q_uQ_{H'}^2m_{H'}^2+2Q_uQ_{\overline{H'}}^2m_{\overline{H'}}^2\nonumber\\
+&{}+Q_u\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2\nonumber\\
+&{}+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmu222BetaTwoLoop}\\
 b_{m_{u3}^2}^{(2)}&=.\label{eq:USSMmu222Ot2Coeff}

### 2015-03-03 fs-spectrum/models/lowE6SSM/fill_scan_lowE6SSM.cpp
Added random scans over remaining parameters to try to fill plot in; however it seems difficult to fill in the gap in U(1)_\eta at low Higgs masses

@@ -285,6 +285,15 @@ namespace flexiblesusy {
       if (endpos != std::string::npos) str.erase(endpos+1);
    }
 
+   double get_random_Lambdax(const lowE6SSM_input_parameters& input, double Lambdax_width, std::default_random_engine& generator)
+   {
+      const double LambdaxInput = input.LambdaxInput;
+
+      std::uniform_real_distribution<double> Lambdax_distribution(LambdaxInput - Lambdax_width, LambdaxInput + Lambdax_width);
+
+      return Lambdax_distribution(generator);
+   }
+
    double get_random_TLambdax(const lowE6SSM_input_parameters& input, double ALambdax_width, std::default_random_engine& generator)
    {
       const double LambdaxInput = input.LambdaxInput;
@@ -303,6 +312,24 @@ namespace flexiblesusy {
       std::uniform_real_distribution<double> AYu22_distribution(AYu22Input - AYu22_width, AYu22Input + AYu22_width);
 
       return AYu22_distribution(generator);
+   }
+
+   double get_random_mq222(const lowE6SSM_input_parameters& input, double mq222_width, std::default_random_engine& generator)
+   {
+      const double mq222Input = input.mq2Input(2,2);
+
+      std::uniform_real_distribution<double> mq222_distribution(mq222Input - mq222_width, mq222Input + mq222_width);
+
+      return mq222_distribution(generator);
+   }
+
+   double get_random_mu222(const lowE6SSM_input_parameters& input, double mu222_width, std::default_random_engine& generator)
+   {
+      const double mu222Input = input.mu2Input(2,2);
+
+      std::uniform_real_distribution<double> mu222_distribution(mu222Input - mu222_width, mu222Input + mu222_width);
+
+      return mu222_distribution(generator);
    }
 
 }
@@ -561,11 +588,20 @@ int main()
          // generate additional points from read-in point
          const double ALambdax_width = 1000.0;
          const double AYu22_width = 1000.0;
+         const double Lambdax_width = 0.05;
+         const double mq222_width = 1000.0;
+         const double mu222_width = 1000.0;
 
          for (std::size_t i = 0; i < num_points; ++i) {
             lowE6SSM_input_parameters random_input = input;
             random_input.TLambdaxInput = get_random_TLambdax(input, ALambdax_width, generator);
             random_input.AYuInput(2,2) = get_random_AYu22(input, AYu22_width, generator);
+
+            // additional randomised values
[…]

### 2015-03-03 fs-spectrum/models/lowE6SSM/full_tuning_scan_lowE6SSM.cpp

@@ -43,7 +43,7 @@ namespace flexiblesusy {
       // U(1)_I: theta = PI + ArcTan(Sqrt(0.6))
       // U(1)_psi: theta = 0.5 * PI
       // U(1)_eta: theta = -ArcTan(Sqrt(5.0 / 3.0))
-      const double theta = PI + ArcTan(Sqrt(0.6));
+      const double theta = -ArcTan(Sqrt(5.0 / 3.0));
       
       initialize_e6_charges(theta, input);
       

### 2015-03-04 paper/e6ssm-tuning-paper.tex
Added O(t^2) coefficient for m_u3^2
Added two-loop beta function for m_Q3^2

@@
 &{}-\frac{32}{3}g_3^2M_3^2-6g_2^2M_2^2-\frac{2}{15}g_1^2M_1^2-8Q_Q^2g_1'^2M_1'^2+\frac{1}{5}g_1^2\Sigma_1+2Q_Qg_1'^2\Sigma_1',\label{eq:USSMmq222BetaOneLoop}\\
-\beta_{m_{Q3}^2}^{(2)}&=,\label{eq:USSMmq222BetaTwoLoop}\\
+\beta_{m_{Q3}^2}^{(2)}&=-20y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2 \right )-20y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2 \right )\nonumber\\
+&{}-2y_\tau^2y_b^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{L3}^2+m_{d3}^2+m_{e3}^2\right )-40y_t^2a_t^2-40y_b^2a_b^2\nonumber\\
+&{}-2\left ( y_ba_\tau+y_\tau a_b\right )^2-2\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )\nonumber\\
+&{}-2\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )-2\left ( \lambda a_t+y_t a_\lambda \right )^2-2\left ( \lambda a_b+y_b a_\lambda \right )^2\nonumber\\
+&{}+\frac{2}{5}g_1^2y_t^2\left ( m_{H_u}^2+3m_{Q3}^2+8m_{u3}^2 +8M_1^2\right )+\frac{8}{5}g_1^2\left ( a_t^2-2y_ta_tM_1 \right )\nonumber\\
+&{}+\frac{2}{5}g_1^2y_b^2\left ( 5m_{H_d}^2+m_{Q3}^2+4M_1^2\right )+\frac{4}{5}g_1^2\left ( a_b^2-2y_ba_bM_1 \right )+\frac{2}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
+&{}+\frac{2}{5}g_1^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_{Di}^2-m_{\overline{D}i}^2\right )+\lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )\right ]\nonumber\\
+&{}+4g_1'^2y_t^2\left ( Q_2^2-Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )\nonumber\\
+&{}+4g_1'^2\left ( Q_2^2-Q_Q^2+Q_u^2\right )\left ( a_t^2 -2y_ta_tM_1'\right )-24Q_Qg_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )\nonumber\\
+&{}+4g_1'^2y_b^2\left ( Q_1^2-Q_Q^2+Q_d^2 \right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1'^2\right )\nonumber\\
+&{}+4g_1'^2\left ( Q_1^2-Q_Q^2+Q_d^2\right )\left ( a_b^2-2y_ba_bM_1'\right )-24Q_Qg_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )\nonumber\\
+&{}-8Q_Qg_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )\nonumber\\
+&{}-4Q_Qg_1'^2\sum_{i=1}^3\left [ 3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2\right )+2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )\right ]\nonumber\\
+&{}+\frac{16}{3}g_3^4\left [ 10M_3^2+\sum_{i=1}^3\left ( 2m_{Qi}^2+m_{ui}^2+m_{di}^2+m_{Di}^2+m_{\overline{D}i}^2\right )\right ]+32g_3^2g_2^2\left ( M_2^2+M_2M_3+M_3^2\right )\nonumber\\
+&{}+\frac{16}{45}g_3^2g_1^2\left [ 2\left ( M_1^2+M_1M_3+M_3^2\right )+3\sum_{i=1}^3\left ( m_{Qi}^2+m_{di}^2-2m_{ui}^2-m_{Di}^2+m_{\overline{D}i}^2\right )\right ]\nonumber\\
+&{}+\frac{32}{3}Q_Qg_3^2g_1'^2\bigg [ 4Q_Q\left ( M_1'^2+M_1'M_3+M_3^2 \right )+3\sum_{i=1}^3\big ( 2Q_Qm_{Qi}^2+Q_um_{ui}^2+Q_dm_{di}^2\nonumber\\
+&{}+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2 \big )\bigg ]+g_2^4\left [ 87M_2^2+m_{\overline{H'}}^2+m_{H'}^2+3\sum_{i=1}^3\left ( 3m_{Qi}^2+m_{Li}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
+&{}+\frac{1}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2 \right )+3m_{\overline{H'}}^2-3m_{H'}^2+3\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
+&{}+12Q_Qg_2^2g_1'^2\bigg [ 2Q_Q\left ( M_1'^2+M_1'M_2+M_2^2\right )+Q_{\overline{H'}}m_{\overline{H'}}^2+Q_{H'}m_{H'}^2\nonumber\\
+&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Qi}^2+Q_Lm_{Li}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{75}g_1^4\bigg [ 289M_1^2+12m_{\overline{H'}}^2-6m_{H'}^2\nonumber\\
+&{}+\sum_{i=1}^3\left ( 6m_{di}^2-2m_{Di}^2+6m_{\overline{D}i}^2+42m_{ei}^2-6m_{H_i^d}^2+12m_{H_i^u}^2-6m_{Li}^2+2m_{Qi}^2-24m_{ui}^2\right )\bigg ]\nonumber\\
+&{}+\frac{4}{15}g_1^2g_1'^2\bigg [ 2Q_Q\big ( 9Q_d+9Q_{\overline{D}}-9Q_D+9Q_e-9Q_1+9Q_2+3Q_{\overline{H'}}-3Q_{H'}-9Q_L\nonumber\\
+&{}+10Q_Q-18Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}m_{H'}^2\nonumber\\
+&{}+3\sum_{i=1}^3\big ( Q_d^2m_{di}^2+Q_{\overline{D}}^2m_{\overline{D}i}^2-Q_D^2m_{Di}^2+Q_e^2m_{ei}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2\nonumber\\
+&{}-Q_L^2m_{Li}^2-Q_Q^2m_{Qi}^2-2Q_u^2m_{ui}^2\big )+15Q_QQ_{\overline{H'}}m_{\overline{H'}}^2+3Q_QQ_{H'}m_{H'}^2\nonumber\\
+&{}+Q_Q\sum_{i=1}^3\big ( 12Q_dm_{di}^2+12Q_{\overline{D}}m_{\overline{D}i}^2+24Q_em_{ei}^2+3Q_1m_{H_i^d}^2+15Q_2m_{H_i^u}^2+3Q_Lm_{Li}^2\nonumber\\
+&{}+15Q_Qm_{Qi}^2+12m_{ui}^2\big )\bigg ]+8Q_Qg_1'^4\bigg [ 3Q_QM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2\nonumber\\
+&{}+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2+20Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2\nonumber\\
+&{}+\sum_{i=1}^3\big ( 3Q_d^3m_{di}^2+3Q_{\overline{D}}^3m_{\overline{D}i}^2+3Q_D^3m_{Di}^2+Q_e^3m_{ei}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{Li}^2\nonumber\\
+&{}+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )+2Q_QQ_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_QQ_{H'}^2m_{H'}^2\nonumber\\
+&{}+Q_Q\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2\nonumber\\
+&{}+2Q_L^2m_{Li}^2+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmq222BetaTwoLoop}\\
 b_{m_{Q3}^2}^{(2)}&=.\label{eq:USSMmq222Ot2Coeff}
@@
 \begin{align}
-\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+4a_t^2-\frac{32}{3}g_3^2M_3^2-\frac{32}{15}g_1^1M_1^2-8Q_u^2g_1'^2M_1'^2\nonumber\\
+\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+4a_t^2-\frac{32}{3}g_3^2M_3^2-\frac{32}{15}g_1^2M_1^2-8Q_u^2g_1'^2M_1'^2\nonumber\\
 &{}-\frac{4}{5}g_1^2\Sigma_1+2Q_ug_1'^2\Sigma_1',\label{eq:USSMmu222BetaOneLoop}\\
@@
 &{}-12Q_ug_1'^2\sum_{i=1}^3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2\right )\nonumber\\
-&{}-8Q_ug_1'^2\sum_{i=1}^3\left ( Q_1m_{H_d}^2+Q_2m_{H_u}^2+Q_Sm_S^2\right )\nonumber\\
+&{}-8Q_ug_1'^2\sum_{i=1}^3\lambda_i^2\left ( Q_1m_{H_d}^2+Q_2m_{H_u}^2+Q_Sm_S^2\right )\nonumber\\
 &{}+\frac{16}{3}g_3^4\left [ 10M_3^2+\sum_{i=1}^3\left ( m_{di}^2+m_{Di}^2+m_{\overline{D}i}^2+2m_{Qi}^2+m_{ui}^2\right )\right ]\nonumber\\
@@
 &{}+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmu222BetaTwoLoop}\\
-b_{m_{u3}^2}^{(2)}&=.\label{eq:USSMmu222Ot2Coeff}
+b_{m_{u3}^2}^{(2)}&=48y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2 \right )+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+m_{Q3}^2+m_{u3}^2+m_{d3}^2 \right )+96y_t^2a_t^2\nonumber\\
+&{}+4\left ( y_ta_b+y_ba_t\right )^2+4\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2 \right )+4\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
+&{}-\frac{64}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_3^2\right )-\frac{64}{3}g_3^2\left ( a_t^2-2y_ta_tM_3 \right )\nonumber\\
+&{}-12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_2^2\right )-12g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
+&{}-\frac{52}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1^2\right )-\frac{52}{15}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
+&{}-8g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )\nonumber\\
+&{}-8g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( a_t^2-2y_ta_tM_1'\right )\nonumber\\
+&{}+4g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 3Q_um_{H_u}^2+3Q_um_{Q3}^2+3Q_um_{u3}^2+\Sigma_1'\right )\nonumber\\
+&{}+12Q_ug_1^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_ug_1'^2y_b^2\left ( Q_1+Q_Q+Q_d \right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
+&{}+12Q_ua_b^2\left ( Q_1+Q_Q+Q_d \right )\nonumber\\
+&{}+4Q_ug_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+4Q_ua_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
+&{}+Q_ug_1'^2\sum_{i=1}^3\bigg [ 6\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+6a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\nonumber\\
+&{}+4\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )\bigg ]\nonumber\\
+&{}-96Q_ug_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )\nonumber\\
+&{}-12Q_ug_2^2g_1'^2M_2^2\left ( 9Q_Q+3Q_L+3Q_1+3Q_2+Q_{H'}+Q_{\overline{H'}}\right )-\frac{384}{25}g_1^4\left ( \Sigma_1+4M_1^2\right )\nonumber\\
+&{}+\frac{2}{5}g_1^2g_1'^2\big [ 8M_1'^2 ( 3Q_d^2+3Q_{\overline{D}}^2-3Q_D^2+3Q_e^2-3Q_1^2+3Q_2^2+Q_{\overline{H'}}^2-Q_{H'}^2-3Q_L^2\nonumber\\
+&{}+3Q_Q^2-6Q_u^2 )+6Q_uM_1^2 ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\nonumber\\
+&{}+3Q_L+Q_Q+8Q_u )+\left ( 3Q_u\Sigma_1-2\Sigma_1^\prime\right ) ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+3Q_2\nonumber\\
+&{}+Q_{\overline{H'}}-Q_{H'}-3Q_L+3Q_Q-6Q_u )\big ]-4Q_ug_1'^4\big [ 2M_1'^2 ( 9Q_d^3+9Q_D^3+9Q_{\overline{D}}^3+3Q_e^2\nonumber\\
+&{}+6Q_1^2+6Q_2^2+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3 )\nonumber\\
+&{}+\left(6Q_uM_1'^2-\Sigma_1^\prime\right )( 9Q_d^2+9Q_D^2+9Q_{\overline{D}}^2+3Q_e^2+6Q_1^2+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2\nonumber\\
+&{}+6Q_L^2+18Q_Q^2+3Q_S^2+9Q_u^2 )\big ].\label{eq:USSMmu222Ot2Coeff}
 \end{align}

### 2015-03-04 paper/e6ssm-tuning-paper.tex
Fixed typo m_{qi} instead of m_{Qi}
Added two-loop beta for m_S^2

@@
 &{}-8Q_S^2g_1'^2M_1'^2+2Q_Sg_1'^2\Sigma_1',\label{eq:USSMms2BetaOneLoop}\\
-\beta_{m_S^2}^{(2)}&=,\label{eq:USSMms2BetaTwoLoop}\\
+\beta_{m_S^2}^{(2)}&=\sum_{i=1}^3\bigg [ -16\lambda_i^2\left ( m_{H_i^u}^2+m_{H_i^d}^2+m_S^2 \right )-24\kappa_i^2\left ( m_{Di}^2+m_{\overline{D}i}^2+m_S^2 \right )\nonumber\\
+&{}-32\lambda_i^2a_{\lambda_i}^2-48\kappa_i^2a_{\kappa_i}^2\bigg ]-12\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )\nonumber\\
+&{}-12\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
+&{}-4\lambda^2y_\tau^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )-12\left ( \lambda a_t+y_ta_\lambda\right )^2-12\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
+&{}-4\left ( \lambda a_\tau+y_\tau a_\lambda\right )^2+32g_3^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_3^2\right )+a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_3 \right ]\nonumber\\
+&{}+12g_2^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_2^2\right )+a_{\lambda_i}^2-2\lambda_ia_{\lambda_i}M_2\right ]\nonumber\\
+&{}+\frac{4}{5}g_1^2\sum_{i=1}^3\bigg [ 3\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1^2\right )+2\kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_1^2\right )\nonumber\\
+&{}+3\left (a_{\lambda_i}^2-2\lambda_ia_{\lambda_i}M_1\right )+2\left (a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_1\right )\bigg ]\nonumber\\
+&{}+4g_1'^2\sum_{i=1}^3\bigg [ 2\lambda_i^2\left ( Q_1^2+Q_2^2-Q_S^2\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1'^2\right )\nonumber\\
+&{}-2Q_S\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )+3\kappa_i^2\left ( Q_D^2+Q_{\overline{D}}^2-Q_S^2\right )\times\nonumber\\
+&{}\times\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_1'^2\right )-3Q_S\kappa_i^2\left ( Q_Sm_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )\nonumber\\
+&{}+2\left ( a_{\lambda_i}^2-2\lambda_ia_{\lambda_i}M_1'\right )\left ( Q_1^2+Q_2^2-Q_S^2\right )+3\left ( a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_1'\right )\left ( Q_D^2+Q_{\overline{D}}^2-Q_S^2\right )\bigg ]\nonumber\\
+&{}-24Q_Sg_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )-24Q_Sg_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )\nonumber\\
+&{}-8Q_Sg_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )+32Q_Sg_3^2g_1'^2\sum_{i=1}^3\big ( 2Q_Qm_{Qi}^2+Q_um_{ui}^2\nonumber\\
+&{}+Q_dm_{di}^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2\big )+12Q_Sg_2^2g_1'^2\bigg [ Q_{\overline{H'}}m_{\overline{H'}}^2+Q_{H'}m_{H'}^2\nonumber\\
+&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Qi}^2+Q_Lm_{Li}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{4}{5}Q_Sg_1^2g_1'^2\bigg [ 3Q_{\overline{H'}}m_{\overline{H'}}^2+3Q_{H'}m_{H'}^2\nonumber\\
+&{}+\sum_{i=1}^3\big ( 2Q_dm_{di}^2+2Q_{\overline{D}}m_{\overline{D}i}^2+2Q_Dm_{Di}^2+6Q_em_{ei}^2+3Q_1m_{H_i^d}^2+3Q_2m_{H_i^u}^2+3Q_Lm_{Li}^2\nonumber\\
+&{}+Q_Qm_{Qi}^2+8Q_um_{ui}^2\big )\bigg ]+8Q_Sg_1'^4\bigg [ 3Q_SM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2+6Q_2^2\nonumber\\
+&{}+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2+18Q_Q^2+5Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2\nonumber\\
+&{}+\sum_{i=1}^3\big ( 3Q_d^3m_{di}^2+3Q_{\overline{D}}^3m_{\overline{D}i}^2+3Q_D^3m_{Di}^2+Q_e^3m_{ei}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{Li}^2\nonumber\\
+&{}+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )+2Q_SQ_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_SQ_{H'}m_{H'}^2\nonumber\\
+&{}+Q_S\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2\nonumber\\
+&{}+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMms2BetaTwoLoop}\\
 b_{m_S^2}^{(2)}&=.\label{eq:USSMms2Ot2Coeff}
@@
 &{}+\frac{16}{3}g_3^4\left [ 10M_3^2+\sum_{i=1}^3\left ( m_{di}^2+m_{Di}^2+m_{\overline{D}i}^2+2m_{Qi}^2+m_{ui}^2\right )\right ]\nonumber\\
-&{}+\frac{64}{45}g_3^2g_1^2\left [ 8\left (M_1^2+M_1M_3+M_3^2\right )-3\sum_{i=1}^3\left ( m_{di}^2-m_{Di}^2+m_{\overline{D}i}^2+m_{qi}^2-2m_{ui}^2\right )\right ]\nonumber\\
+&{}+\frac{64}{45}g_3^2g_1^2\left [ 8\left (M_1^2+M_1M_3+M_3^2\right )-3\sum_{i=1}^3\left ( m_{di}^2-m_{Di}^2+m_{\overline{D}i}^2+m_{Qi}^2-2m_{ui}^2\right )\right ]\nonumber\\
 &{}+\frac{8}{3}Q_ug_3^2g_1'^2\bigg [ 16Q_u\left (M_1'^2+M_1'M_3+M_3^2\right )\nonumber\\

### 2015-03-05 paper/e6ssm-tuning-paper.tex
Added two-loop beta for m_{H_u}^2, fixed some typos in two-loop beta for m_{Q3}^2

@@
 &{}-6g_2^2M_2^2-\frac{6}{5}g_1^2M_1^2-8Q_2^2g_1'^2M_1'^2+\frac{3}{5}g_1^2\Sigma_1+2Q_2g_1'^2\Sigma_1',\label{eq:USSMmHu2BetaOneLoop}\\
-\beta_{m_{H_u}^2}^{(2)}&=,\label{eq:USSMmHu2BetaTwoLoop}\\
+\beta_{m_{H_u}^2}^{(2)}&=-36y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )-6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )\nonumber\\
+&{}-72y_t^2a_t^2-6\left ( y_ta_b+y_ba_t\right )^2-4\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )-8\lambda^2a_{\lambda}^2\nonumber\\
+&{}-\lambda^2\sum_{i=1}^3\bigg [ 4\lambda_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\nonumber\\
+&{}+6\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )\bigg ]-\sum_{i=1}^3 \big [4\left ( \lambda_ia_{\lambda}+\lambda a_{\lambda_i}\right )^2\nonumber\\
+&{}+6\left ( \kappa_i a_{\lambda}+\lambda a_{\kappa_i}\right )^2\big ]-6\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
+&{}-2\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )-6\left ( \lambda a_b+y_ba_{\lambda}\right )^2-2\left ( \lambda a_\tau+y_\tau a_{\lambda}\right )^2\nonumber\\
+&{}+32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_3^2\right )+32g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
+&{}+\frac{2}{5}g_1^2y_t^2\left ( -5m_{H_u}^2+m_{Q3}^2+16m_{u3}^2+8M_1^2\right )+\frac{8}{5}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
+&{}+\frac{6}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q3}^2-2m_{d3}^2\right )+\frac{6}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
+&{}+\frac{6}{5}g_1^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )+\kappa_i^2\left ( m_{Di}^2-m_{\overline{D}i}^2\right )\right ]\nonumber\\
+&{}+12g_1'^2y_t^2\left ( Q_Q^2+Q_u^2-Q_2^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )\nonumber\\
+&{}+12g_1'^2\left ( Q_Q^2+Q_u^2-Q_2^2\right )\left ( a_t^2-2y_ta_tM_1'\right )-24Q_2g_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )\nonumber\\
+&{}-24Q_2g_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )-8Q_2g_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )\nonumber\\
+&{}+4g_1'^2\lambda^2\left ( Q_1^2-Q_2^2+Q_S^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )\nonumber\\
+&{}+4g_1'^2\left ( Q_1^2-Q_2^2+Q_S^2\right )\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )\nonumber\\
+&{}-4Q_2g_1'^2\sum_{i=1}^3\left [ 2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )+3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2\right )\right ]\nonumber\\
+&{}+\frac{16}{5}g_3^2g_1^2\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{\overline{D}i}^2-m_{Di}^2\right )\nonumber\\
+&{}+32Q_2g_3^2g_1'^2\sum_{i=1}^3\left ( 2Q_Qm_{Qi}^2+Q_um_{ui}^2+Q_dm_{di}^2+Q_{\overline{D}}m_{\overline{D}i}^2+Q_Dm_{Di}^2\right )\nonumber\\
+&{}+3g_2^4\left [ 29M_2^2+m_{H'}^2+m_{\overline{H'}}^2+\sum_{i=1}^3\left ( 3m_{Qi}^2+m_{Li}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
+&{}+\frac{9}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2\right )+m_{\overline{H'}}^2-m_{H'}^2+\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
+&{}+12Q_2g_2^2g_1'^2\bigg [ 2Q_2\left ( M_1'^2+M_1'M_2+M_2^2\right )+Q_{H'}m_{H'}^2+Q_{\overline{H'}}m_{\overline{H'}}^2\nonumber\\
+&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Qi}^2+Q_Lm_{Li}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{25}g_1^4\bigg [ 891M_1^2+18m_{\overline{H'}}^2\nonumber\\
+&{}+\sum_{i=1}^3\left ( 10m_{di}^2+2m_{Di}^2+10m_{\overline{D}i}^2+54m_{ei}^2+18m_{H_i^u}^2+4m_{Qi}^2-8m_{ui}^2\right )\bigg ]\nonumber\\
+&{}+\frac{4}{5}g_1^2g_1'^2\bigg [ 6Q_2\big ( 3Q_d+Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+4Q_2+Q_{\overline{H'}}-Q_{H'}-3Q_L\nonumber\\
+&{}+3Q_Q-6Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}m_{H'}^2\nonumber\\
+&{}+3\sum_{i=1}^3\left ( Q_d^2m_{di}^2+Q_{\overline{D}}^2m_{\overline{D}i}^2-Q_D^2m_{Di}^2+Q_e^2m_{ei}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2-Q_L^2m_{Li}^2\right.\nonumber\\
+&{}\left.+Q_Q^2m_{Qi}^2-2Q_u^2m_{ui}^2\right )+9Q_2Q_{\overline{H'}}m_{\overline{H'}}^2-3Q_2Q_{H'}m_{H'}^2+Q_2\sum_{i=1}^3\left ( 8Q_dm_{di}^2+8Q_{\overline{D}}m_{\overline{D}i}^2\right.\nonumber\\
+&{}\left.-4Q_Dm_{Di}^2+12Q_em_{ei}^2-3Q_1m_{H_i^d}^2+9Q_2m_{H_i^u}^2-3Q_Lm_{Li}^2+7Q_Qm_{Qi}^2-4Q_um_{ui}^2\right )\bigg ]\nonumber\\
+&{}+8Q_2g_1'^4\bigg [ 3Q_2M_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2+8Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2\nonumber\\
+&{}+18Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^3m_{di}^2+3Q_{\overline{D}}^3m_{\overline{D}i}^2\nonumber\\
+&{}+3Q_D^3m_{Di}^2+Q_e^3m_{ei}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{Li}^2+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )\nonumber\\
+&{}+2Q_2Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_2Q_{H'}^2m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2\nonumber\\
+&{}+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmHu2BetaTwoLoop}\\
 b_{m_{H_u}^2}^{(2)}&=,\label{eq:USSMmHu2Ot2Coeff}
@@
 &{}+\frac{32}{3}Q_Qg_3^2g_1'^2\bigg [ 4Q_Q\left ( M_1'^2+M_1'M_3+M_3^2 \right )+3\sum_{i=1}^3\big ( 2Q_Qm_{Qi}^2+Q_um_{ui}^2+Q_dm_{di}^2\nonumber\\
-&{}+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2 \big )\bigg ]+g_2^4\left [ 87M_2^2+m_{\overline{H'}}^2+m_{H'}^2+3\sum_{i=1}^3\left ( 3m_{Qi}^2+m_{Li}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
+&{}+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2 \big )\bigg ]+3g_2^4\left [ 29M_2^2+m_{\overline{H'}}^2+m_{H'}^2+\sum_{i=1}^3\left ( 3m_{Qi}^2+m_{Li}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
 &{}+\frac{1}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2 \right )+3m_{\overline{H'}}^2-3m_{H'}^2+3\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
@@
 &{}+\frac{4}{15}g_1^2g_1'^2\bigg [ 2Q_Q\big ( 9Q_d+9Q_{\overline{D}}-9Q_D+9Q_e-9Q_1+9Q_2+3Q_{\overline{H'}}-3Q_{H'}-9Q_L\nonumber\\
-&{}+10Q_Q-18Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}m_{H'}^2\nonumber\\
+&{}+10Q_Q-18Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}^2m_{H'}^2\nonumber\\
 &{}+3\sum_{i=1}^3\big ( Q_d^2m_{di}^2+Q_{\overline{D}}^2m_{\overline{D}i}^2-Q_D^2m_{Di}^2+Q_e^2m_{ei}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2\nonumber\\

### 2015-03-05 paper/e6ssm-tuning-paper.tex
Added two-loop beta for m_{H_d}^2, fixed some typos in two-loop beta for m_{H_u}^2

@@
 &{}-\frac{3}{5}g_1^2\Sigma_1+2Q_1g_1'^2\Sigma_1',\label{eq:USSMmHd2BetaOneLoop}\\
-\beta_{m_{H_d}^2}^{(2)}&=,\label{eq:USSMmHd2BetaTwoLoop}\\
+\beta_{m_{H_d}^2}^{(2)}&=-36y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )-12y_\tau^4\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )-72y_b^2a_b^2-24y_\tau^2a_\tau^2\nonumber\\
+&{}-6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )-6\left ( y_t a_b+y_ba_t\right )^2\nonumber\\
+&{}-4\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )-8\lambda^2a_\lambda^2-\lambda^2\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{H_i^d}^2\right.\right.\nonumber\\
+&{}\left.\left.+m_{H_i^u}^2\right )+6\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )\right ]-\sum_{i=1}^3\left [ 4\left ( \lambda_i a_{\lambda}+\lambda a_{\lambda_i}\right )^2\right.\nonumber\\
+&{}\left.+6\left ( \kappa_ia_\lambda+\lambda a_{\kappa_i}\right )^2\right ]-6\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )-6\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
+&{}+32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_3^2\right )+32g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
+&{}+\frac{6}{5}g_1^2y_t^2\left ( 3m_{H_u}^2+m_{Q3}^2-4m_{u3}^2\right )-\frac{2}{5}g_1^2y_b^2\left ( 11m_{H_d}^2-m_{Q3}^2-4m_{d3}^2+4M_1^2\right )\nonumber\\
+&{}-\frac{4}{5}g_1^2\left ( a_b^2-2y_ba_bM_1\right )+\frac{6}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+4m_{e3}^2+4M_1^2\right )+\frac{12}{5}g_1^2\left ( a_\tau^2-2y_\tau a_\tau M_1\right )\nonumber\\
+&{}+\frac{6}{5}g_1^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )+\kappa_i^2\left ( m_{\overline{D}i}^2-m_{Di}^2\right )\right ]+12g_1'^2y_b^2\left ( Q_Q^2+Q_d^2-Q_1^2\right )\times\nonumber\\
+&{}\times\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1'^2\right )+12g_1'^2\left ( Q_Q^2+Q_d^2-Q_1^2\right )\left ( a_b^2-2y_ba_bM_1'\right )\nonumber\\
+&{}-24Q_1g_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )+4g_1'^2y_\tau^2\left ( Q_L^2+Q_e^2-Q_1^2\right )\times\nonumber\\
+&{}\times\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2M_1'^2\right )+4g_1'^2\left ( Q_L^2+Q_e^2-Q_1^2\right )\left ( a_\tau^2-2y_\tau a_\tau M_1'\right )\nonumber\\
+&{}-8Q_1g_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )-24Q_1g_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )\nonumber\\
+&{}+4g_1'^2\lambda^2\left ( Q_2^2+Q_S^2-Q_1^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )+4g_1'^2\left ( Q_2^2+Q_S^2-Q_1^2\right )\times\nonumber\\
+&{}\times\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )-4Q_1g_1'^2\sum_{i=1}^3\left [ 2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )\right.\nonumber\\
+&{}\left.+3\kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )\right ]-\frac{16}{5}g_3^2g_1^2\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{\overline{D}i}^2-m_{Di}^2\right )\nonumber\\
+&{}+32Q_1g_3^2g_1'^2\sum_{i=1}^3\left ( 2Q_Qm_{Qi}^2+Q_um_{ui}^2+Q_dm_{di}^2+Q_{\overline{D}}m_{\overline{D}i}^2+Q_Dm_{Di}^2\right )\nonumber\\
+&{}+3g_2^4\left [ 29M_2^2+m_{H'}^2+m_{\overline{H'}}^2+\sum_{i=1}^3\left ( 3m_{Qi}^2+m_{Li}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
+&{}+\frac{9}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2\right )+m_{H'}^2-m_{\overline{H'}}^2-\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
+&{}+12Q_1g_2^2g_1'^2\bigg [ 2Q_1\left ( M_1'^2+M_1'M_2+M_2^2\right )+Q_{H'}m_{H'}^2+Q_{\overline{H'}}m_{\overline{H'}}^2\nonumber\\
+&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Qi}^2+Q_Lm_{Li}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{25}g_1^4\bigg [ 891M_1^2+18m_{H'}^2\nonumber\\
+&{}+2\sum_{i=1}^3\left ( m_{di}^2+5m_{Di}^2+m_{\overline{D}i}^2-9m_{ei}^2+9m_{H_i^d}^2+9m_{Li}^2+m_{Qi}^2+28m_{ui}^2\right )\bigg ]\nonumber\\
+&{}-\frac{4}{5}g_1^2g_1'^2\bigg [ 6Q_1\big ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-4Q_1+3Q_2+Q_{\overline{H'}}-Q_{H'}-3Q_L\nonumber\\
+&{}+3Q_Q-6Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}^2m_{H'}^2\nonumber\\
+&{}+3\sum_{i=1}^3\big ( Q_d^2m_{di}^2+Q_{\overline{D}}^2m_{\overline{D}i}^2-Q_D^2m_{Di}^2+Q_e^2m_{ei}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2-Q_L^2m_{Li}^2\nonumber\\
+&{}+Q_Q^2m_{Qi}^2-2Q_u^2m_{ui}^2\big )+3Q_1Q_{\overline{H'}}m_{\overline{H'}}^2-9Q_1Q_{H'}m_{H'}^2+Q_1\sum_{i=1}^3\bigg ( 4Q_dm_{di}^2+4Q_{\overline{D}}m_{\overline{D}i}^2\nonumber\\
+&{}-8Q_Dm_{Di}^2-9Q_1m_{H_i^d}^2+3Q_2m_{H_i^u}^2-9Q_Lm_{Li}^2+5Q_Qm_{Qi}^2-20Q_um_{ui}^2\big )\bigg ]\nonumber\\
+&{}+8Q_1g_1'^4\bigg [ 3Q_1M_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+8Q_1^2+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2\nonumber\\
+&{}+18Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^3m_{di}^2+3Q_{\overline{D}}^3m_{\overline{D}i}^2+3Q_D^3m_{Di}^2\nonumber\\
+&{}+Q_e^3m_{ei}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{Li}^2+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )\nonumber\\
+&{}+2Q_1Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_1Q_{H'}m_{H'}^2+Q_1\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2\nonumber\\
+&{}+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmHd2BetaTwoLoop}\\
 b_{m_{H_d}^2}^{(2)}&=.\label{eq:USSMmHd2Ot2Coeff}
@@
 &{}+3Q_D^3m_{Di}^2+Q_e^3m_{ei}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{Li}^2+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )\nonumber\\
-&{}+2Q_2Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_2Q_{H'}^2m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2\nonumber\\
+&{}+2Q_2Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_2Q_{H'}^2m_{H'}^2+Q_2\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2\nonumber\\
 &{}+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmHu2BetaTwoLoop}\\

### 2015-03-06 paper/e6ssm-tuning-paper.tex
Removed terms from two-loop beta for y_t that appear to be due to a SARAH bug (in the coefficient of g_1^2g_1'^2)
Added two-loop beta for a_t, neglecting the additional terms that appear in the SARAH output. As written the beta function matches the one given in the CE6SSM paper, which should be correct
Removed additional U(1)_Y x U(1)' trace appearing in coefficient of g_1^2g_1'^2 in two-loop beta function for lambda. As for y_t, having this trace means 1) the coefficient doesn't match up with that given in the CE6SSM paper and 2) extra terms appear in the two-loop beta function for A_t, which

@@
 from the $Z^\prime$ mass appears already at tree level and is
-therefore not suppressed when the cutoff scale is low.
-In our scan we find that, for the points satisfying the current limit on the mass of the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the minimum fine tuning that can be achieved is
-$\Delta_{\textrm{min}}\approx 121$.
-
-If run II of the LHC further pushes up the limit on the $Z^\prime$
-mass to be above $4.5$ TeV then the fine tuning in the model will be
-greater than at least $\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$ GeV and $125.5$ GeV.
+therefore not suppressed when the cutoff scale is low. In our scan we
+find that, for the points satisfying the current limit on the mass of
+the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the
+minimum fine tuning that can be achieved is
+$\Delta_{\textrm{min}}\approx 121$. If run II of the LHC further
+pushes up the limit on the $Z^\prime$ mass to be above $4.5$ TeV then
+the fine tuning in the model will be greater than at least
+$\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$
+GeV and $125.5$ GeV.
 
@@
 
-In the top panel one can see that the MSSM BM1 tuning 
+In the top panel one can see that the MSSM BM1 tuning (green curve) 
 steadily climbs as the cutoff scale is increased, as one would expect
@@
 This leads to a significant reduction in the contributions to the RG running of $m_{H_u}^2$ and $m_{Q3}^2$ coming from terms of the form $g_1^2\Sigma_1$ and, to a lesser extent, $g_1'^2\Sigma_1'$.
-Here we define
+Here we define for the E$_6$SSM (see also Eqs.~(\ref{eq:USSMGaugeSigmaTerm1}-\ref{eq:USSMGaugeSigmaTerm1Pr}) for general $U(1)$ inspired models)
 \begin{align*}
@@
 &{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2Q_1^4+2Q_2^4+2Q_S^4+\left ( Q_1^2+Q_2^2+Q_S^2\right )\Sigma_{Q}\right ]\nonumber\\
-&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [Q_1^2+Q_2^2+\left ( Q_2-Q_1\right )\Sigma_{Q}^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\
+&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left (Q_1^2+Q_2^2\right )\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\
 b_\lambda^{(2)}&=\lambda \bigg \{ 2\lambda^2\left ( 3\lambda^2 +4\Sigma_\lambda +6\Sigma_\kappa \right )+4\Pi_\lambda + 6\Pi_\kappa +6\left ( \Sigma_\lambda+\frac{3}{2}\Sigma_\kappa\right )^2+7\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\nonumber\\
@@
 \beta_{a_\lambda}^{(1)}&=a_\lambda \left[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2-\frac{3}{5} g_1^2 -2 \left ( Q_1^2 + Q_2^2 + Q_S^2\right )g_1'^2 \right]\nonumber\\
-&{}+\lambda \left [ 4\lambda a_\lambda +4\Sigma_{a_\lambda}+6\Sigma_{a_\kappa}+6y_ta_t+6y_ba_b+2y_\tau a_\tau +6g_2^2M_2+\frac{6}{5}g_1^2M_1\right.\nonumber\\
-&{}\left.+4g_1'^2M_1'\left ( Q_1^2+Q_2^2+Q_S^2 \right )\right ],\label{eq:USSMTLambdaBetaOneLoop}\\
-\beta_{a_\lambda}^{(2)}&=,\label{eq:USSMTLambdaBetaTwoLoop}\\
+&{}+\lambda \bigg [ 4\lambda a_\lambda +4\Sigma_{a_\lambda}+6\Sigma_{a_\kappa}+6y_ta_t+6y_ba_b+2y_\tau a_\tau +6g_2^2M_2+\frac{6}{5}g_1^2M_1\nonumber\\
+&{}+4g_1'^2M_1'\left ( Q_1^2+Q_2^2+Q_S^2 \right )\bigg ],\label{eq:USSMTLambdaBetaOneLoop}\\
+\beta_{a_\lambda}^{(2)}&=a_\lambda \bigg \{ -2\lambda^2\left ( \lambda^2+2\Sigma_\lambda+3\Sigma_\kappa\right )-4\Pi_\lambda-6\Pi_\kappa-3\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right ) \nonumber\\
+&{} -3\left ( 3y_t^4+3y_b^4+2y_t^2y_b^2+y_\tau^2 \right )+6g_2^2\Sigma_\lambda+\frac{2}{5}g_1^2\left ( 2y_t^2-y_b^2+3y_\tau^2+2\Sigma_\kappa +3\Sigma_\lambda\right )\nonumber\\
+&{}\left.+g_1'^2\left [ 4Q_S^2\lambda^2 -6\left ( Q_2^2-Q_Q^2-Q_u^2\right )y_t^2-6\left ( Q_1^2-Q_Q^2-Q_d^2\right )y_b^2 \right.\right.\nonumber\\
+&{}\left.-2\left ( Q_1^2-Q_L^2-Q_e^2\right )y_\tau^2-6\left ( Q_S^2-Q_D^2-Q_{\overline{D}}^2 \right )\Sigma_\kappa-4\left ( Q_S^2-Q_1^2-Q_2^2\right )\Sigma_\lambda\right ]\nonumber\\
+&{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2Q_1^4+2Q_2^4+2Q_S^4+\left ( Q_1^2+Q_2^2+Q_S^2\right )\Sigma_{Q}\right ]\nonumber\\
+&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left (Q_1^2+Q_2^2\right )\bigg \}+\lambda \bigg \{ -4\lambda a_\lambda \left ( \lambda^2+2\Sigma_\lambda+3\Sigma_\kappa\right )\nonumber\\
+&{}-4\lambda^2\left ( \lambda a_\lambda+2\Sigma_{a_\lambda}+3\Sigma_{a_\kappa}\right )-16\Pi_{a_\lambda}-24\Pi_{a_\kappa}-6\lambda a_\lambda\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\nonumber\\
+&{}-6\lambda^2\left ( 3y_ta_t+3y_ba_b+y_\tau a_\tau\right )-12\left [ 3y_t^3a_t+3y_b^3a_b+y_ty_b\left ( y_ta_b+y_ba_t\right )+y_\tau^3 a_\tau\right ]\nonumber\\
+&{}+32g_3^2\left [ y_ta_t+y_ba_b+\Sigma_{a_\kappa}-\left ( y_t^2+y_b^2+\Sigma_\kappa\right )M_3\right ]+12g_2^2\left ( \Sigma_{a_\lambda}-\Sigma_\lambda M_2\right )\nonumber\\
+&{}+\frac{2}{5}g_1^2\left [ 4y_ta_t-2y_ba_b+6y_\tau a_\tau+4\Sigma_{a_\kappa}+6\Sigma_{a_\lambda}-2\left ( 2y_t^2-y_b^2+3y_\tau^2+2\Sigma_\kappa+3\Sigma_\lambda\right )M_1\right ]\nonumber\\
+&{}+4g_1'^2\big [ 3y_t\left ( Q_Q^2-Q_2^2+Q_u^2\right )\left ( a_t-y_t M_1'\right )+3y_b\left ( Q_Q^2-Q_1^2+Q_d^2\right )\left ( a_b-y_bM_1'\right )\nonumber\\
+&{}+y_\tau\left ( Q_L^2-Q_1^2+Q_e^2\right )\left ( a_\tau-y_\tau M_1'\right )+2Q_S^2\lambda\left ( a_\lambda-\lambda M_1'\right )\nonumber\\
+&{}+2\left ( Q_1^2+Q_2^2-Q_S^2\right )\left ( \Sigma_{a_\lambda}-\Sigma_\lambda M_1'\right )+3\left ( Q_D^2+Q_{\overline{D}}^2-Q_S^2\right )\left ( \Sigma_{a_\kappa}-\Sigma_\kappa M_1'\right ) \big ]\nonumber\\
+&{}-66g_2^4M_2-\frac{594}{25}g_1^4M_1-8g_1'^4M_1'\left [ 2\left ( Q_1^4+Q_2^4+Q_S^4\right )+\left ( Q_1^2+Q_2^2+Q_S^2\right )\Sigma_Q\right ]\nonumber\\
+&{}-\frac{18}{5}g_2^2g_1^2\left ( M_2+M_1\right )-12g_2^2g_1'^2\left ( Q_1^2+Q_2^2\right )\left ( M_2+M_1'\right )\nonumber\\
+&{}-\frac{12}{5}g_1^2g_1'^2\left ( Q_1^2+Q_2^2\right )\left ( M_1+M_1'\right )\bigg \},\label{eq:USSMTLambdaBetaTwoLoop}\\
 b_{a_\lambda}^{(2)}&=,\label{eq:USSMTLambdaOt2Coeff}
@@
 &{}+\frac{32}{3}g_3^2g_1'^2\left ( Q_Q^2+Q_u^2\right )+g_2^2g_1^2+6g_2^2g_1'^2\left ( Q_2^2+Q_Q^2\right )\nonumber\\
-&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2+\left ( 3Q_2+Q_Q-4Q_u\right )\Sigma_{Q}^Y\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\
+&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\
 b_{y_t}^{(2)}&=y_t\bigg \{ 54y_t^4+\frac{13}{2}y_b^4+13y_t^2y_b^2+y_b^2y_\tau^2+\lambda^2\left ( \frac{5}{2}\lambda^2+15y_t^2+5y_b^2+y_\tau^2+2\Sigma_\lambda+3\Sigma_\kappa \right )\nonumber\\
@@
 &{}\left.+4g_1'^2M_1'\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\right ],\label{eq:USSMTYu22BetaOneLoop}\\
-\beta_{a_t}^{(2)}&=,\label{eq:USSMTYu22BetaTwoLoop}\\
+\beta_{a_t}^{(2)}&=a_t\bigg \{-22y_t^4-5y_b^4-5y_t^2y_b^2-y_b^2y_\tau^2-\lambda^2 \left ( \lambda^2+3y_t^2+4y_b^2+y_\tau^2+2\Sigma_\lambda + 3\Sigma_\kappa\right )\nonumber\\
+&{}+2g_1'^2\left [ \lambda^2\left ( Q_1^2-Q_2^2+Q_S^2 \right )+2y_t^2\left ( 2Q_Q^2+Q_u^2\right )+y_b^2\left ( Q_1^2-Q_Q^2+Q_d^2\right )\right ]\nonumber\\
+&{}+16g_3^2y_t^2+6g_2^2y_t^2+g_1^2\left ( \frac{6}{5}y_t^2+\frac{2}{5}y_b^2\right )+\frac{128}{9}g_3^4+\frac{33}{2}g_2^4+\frac{3913}{450}g_1^4\nonumber\\
+&{}+2g_1'^4\left [ 2\left ( Q_2^4+Q_Q^4+Q_u^4\right )+\left ( Q_2^2+Q_Q^2+Q_u^2\right )\Sigma_{Q}\right ]+8g_3^2g_2^2+\frac{136}{45}g_3^2g_1^2\nonumber\\
+&{}+\frac{32}{3}g_3^2g_1'^2\left ( Q_Q^2+Q_u^2\right )+g_2^2g_1^2+6g_2^2g_1'^2\left ( Q_2^2+Q_Q^2\right )\nonumber\\
+&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2\right ]\bigg \}+y_t\bigg \{ -88y_t^3a_t-20y_b^3a_b-10y_ty_b\left ( y_ba_t+y_ta_b\right )\nonumber\\
+&{}-2y_by_\tau\left ( y_b a_\tau+y_\tau a_b\right )-2\lambda a_\lambda \left ( 2\lambda^2+3y_t^2+4y_b^2+y_\tau^2+2\Sigma_\lambda+3\Sigma_\kappa\right )\nonumber\\
+&{}-2\lambda^2\left ( 3y_t a_t+4y_b a_b+y_\tau a_\tau +2\Sigma_{a_\lambda}+3\Sigma_{a_\kappa}\right )+32g_3^2y_t\left ( a_t-y_tM_3\right )\nonumber\\
+&{}+12g_2^2y_t\left ( a_t-y_tM_2\right )+\frac{2}{5}g_1^2\left [ 6y_ta_t+2y_ba_b-\left ( 6y_t^2+2y_b^2\right )M_1\right ]\nonumber\\
+&{}+4g_1'^2\big [ \lambda\left (Q_1^2-Q_2^2+Q_S^2\right ) \left ( a_\lambda-\lambda M_1'\right )+2y_t\left ( 2Q_Q^2+Q_u^2\right )\left ( a_t-y_tM_1'\right )\nonumber\\
+&{}+y_b\left ( Q_1^2-Q_Q^2+Q_d^2\right )\left ( a_b-y_bM_1'\right )\big ]-\frac{512}{9}g_3^4M_3-66g_2^4M_2-\frac{7826}{225}g_1^4M_1\nonumber\\
+&{}-8g_1'^4M_1'\left [ 2\left ( Q_2^4+Q_Q^4+Q_u^4\right )+\left ( Q_2^2+Q_Q^2+Q_u^2\right )\Sigma_{Q}\right ]-16g_3^2g_2^2\left ( M_3+M_2\right )\nonumber\\
+&{}-\frac{272}{45}g_3^2g_1^2\left ( M_3+M_1\right )-\frac{64}{3}g_3^2g_1'^2\left ( Q_Q^2+Q_u^2\right )\left ( M_3+M_1'\right )-2g_2^2g_1^2\left ( M_2+M_1\right )\nonumber\\
+&{}-12g_2^2g_1'^2\left ( Q_2^2+Q_Q^2\right )\left ( M_2+M_1'\right )-\frac{4}{15}g_1^2g_1'^2\left ( 9Q_2^2+Q_Q^2+16Q_u^2\right )\left ( M_1+M_1'\right )\bigg \},\label{eq:USSMTYu22BetaTwoLoop}\\
 b_{a_t}^{(2)}&=.\label{eq:USSMTYu22Ot2Coeff}
@@
 &{}+2Q_L^2m_{Li}^2+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmq222BetaTwoLoop}\\
-b_{m_{Q3}^2}^{(2)}&=.\label{eq:USSMmq222Ot2Coeff}
+b_{m_{Q3}^2}^{(2)}&=24y_t^4\left ( m_{H_u^2}+m_{Q3}^2+m_{u3}^2\right )+24y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+48y_t^2a_t^2+48y_b^2a_b^2\nonumber\\
+&{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )+4\left ( y_ta_b+y_ba_t\right )^2\nonumber\\
+&{}+2y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{d3}^2+m_{L3}^2+m_{e3}^2\right )+2\left ( y_\tau a_b+y_ba_\tau\right )^2\nonumber\\
+&{}+2\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )+2\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
+&{}+2\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )+2\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
+&{}-\frac{32}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_3^2\right )-\frac{32}{3}g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
+&{}-\frac{32}{3}g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_3^2\right )-\frac{32}{3}g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
+&{}-6g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_2^2\right )-6g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
+&{}-6g_2^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_2^2\right )-6g_2^2\left ( a_b^2-2y_ba_bM_2\right )\nonumber\\
+&{}-\frac{26}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1^2\right )-\frac{26}{15}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
+&{}-\frac{14}{15}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1^2\right )-\frac{14}{15}g_1^2\left ( a_b^2-2y_ba_bM_1\right )\nonumber\\
+&{}-4g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )-4g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\times\nonumber\\
+&{}\times\left ( a_t^2-2y_ta_tM_1'\right )+2g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 6Q_Qm_{H_u}^2+6Q_Qm_{Q3}^2+6Q_Qm_{u3}^2+\Sigma_1'\right )\nonumber\\
+&{}+12Q_Qg_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )-4g_1'^2y_b^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1'^2\right )\nonumber\\
+&{}-4g_1'^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( a_b^2-2y_ba_bM_1'\right )+2g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\times\nonumber\\
+&{}\times\left ( 6Q_Qm_{H_d}^2+6Q_Qm_{Q3}^2+6Q_Qm_{d3}^2+\Sigma_1'\right )+12Q_Qg_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )\nonumber\\
+&{}+4Q_Qg_1'^2y_\tau^2\left (Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+4Q_Qg_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
+&{}+2Q_Qg_1'^2\sum_{i=1}^3\Big [ 2\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+2a_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )\nonumber\\
+&{}+3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+3a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\Big ]\nonumber\\
+&{}-96Q_Qg_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )-72g_2^4M_2^2\nonumber\\
+&{}-12Q_Qg_2^2g_1'^2M_2^2\left ( 9Q_Q+3Q_L+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\right )+\frac{96}{25}g_1^4\left ( \Sigma_1-M_1^2\right )\nonumber\\
+&{}-\frac{1}{5}g_1^2g_1'^2\big [ 12Q_QM_1^2\big ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}+3Q_L\nonumber\\
+&{}+Q_Q+8Q_u\big )+4M_1'^2\big ( 3Q_d^2+3Q_{\overline{D}}^2-3Q_D^2+3Q_e^2-3Q_1^2+3Q_2^2+Q_{\overline{H'}}^2-Q_{H'}^2-3Q_L^2\nonumber\\
+&{}+3Q_Q^2-6Q_u^2\big )-\left ( 6Q_Q\Sigma_1+\Sigma_1'\right )\big ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+3Q_2+Q_{\overline{H'}}\nonumber\\
+&{}-Q_{H'}-3Q_L+3Q_Q-6Q_u\big )\big ]-4Q_Qg_1'^4\big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3\nonumber\\
+&{}+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )+\left ( 6Q_QM_1'^2-\Sigma_1'\right )\Sigma_Q\big ].\label{eq:USSMmq222Ot2Coeff}
 \end{align}
@@
 &{}+4g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 3Q_um_{H_u}^2+3Q_um_{Q3}^2+3Q_um_{u3}^2+\Sigma_1'\right )\nonumber\\
-&{}+12Q_ug_1^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_ug_1'^2y_b^2\left ( Q_1+Q_Q+Q_d \right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
-&{}+12Q_ua_b^2\left ( Q_1+Q_Q+Q_d \right )\nonumber\\
-&{}+4Q_ug_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+4Q_ua_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
-&{}+Q_ug_1'^2\sum_{i=1}^3\bigg [ 6\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+6a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\nonumber\\
-&{}+4\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )\bigg ]\nonumber\\
+&{}+12Q_ug_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_ug_1'^2y_b^2\left ( Q_1+Q_Q+Q_d \right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
+&{}+12Q_ug_1'^2a_b^2\left ( Q_1+Q_Q+Q_d \right )\nonumber\\
+&{}+4Q_ug_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+4Q_ug_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
+&{}+2Q_ug_1'^2\sum_{i=1}^3\bigg [ 3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+3a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\nonumber\\
+&{}+2\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+2a_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )\bigg ]\nonumber\\
 &{}-96Q_ug_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )\nonumber\\
@@
 &{}+6Q_1^2+6Q_2^2+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3 )\nonumber\\
-&{}+\left(6Q_uM_1'^2-\Sigma_1^\prime\right )( 9Q_d^2+9Q_D^2+9Q_{\overline{D}}^2+3Q_e^2+6Q_1^2+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2\nonumber\\
-&{}+6Q_L^2+18Q_Q^2+3Q_S^2+9Q_u^2 )\big ].\label{eq:USSMmu222Ot2Coeff}
+&{}+\left(6Q_uM_1'^2-\Sigma_1^\prime\right )\Sigma_Q\big ].\label{eq:USSMmu222Ot2Coeff}
 \end{align}

### 2015-03-06 paper/e6ssm-tuning-paper.tex
rephrase comment on large mixing.

@@
 found this does not eliminate the tuning as there is still a strong
-sensitivity to $A_t$, but we did find that increasing $A_t$ lead less
-fine tuning overall for the points we looked at.
+sensitivity to $A_t$, but we did find that large mixing lead less
+fine tuning overall for the points we examined.
 

### 2015-03-06 paper/e6ssm-tuning-paper.tex
Added O(t^2) m_S^2 coefficient, think all algebraic errors have been accounted for in my simplification but it would be a good idea to check this numerically if there is time

--- 2015-03-06 paper/e6ssm-tuning-paper.tex
@@
 from the $Z^\prime$ mass appears already at tree level and is
-therefore not suppressed when the cutoff scale is low. In our scan we
-find that, for the points satisfying the current limit on the mass of
-the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the
-minimum fine tuning that can be achieved is
-$\Delta_{\textrm{min}}\approx 121$. If run II of the LHC further
-pushes up the limit on the $Z^\prime$ mass to be above $4.5$ TeV then
-the fine tuning in the model will be greater than at least
-$\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$
-GeV and $125.5$ GeV.
+therefore not suppressed when the cutoff scale is low.
+In our scan we find that, for the points satisfying the current limit on the mass of the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the minimum fine tuning that can be achieved is
+$\Delta_{\textrm{min}}\approx 121$.
+
+If run II of the LHC further pushes up the limit on the $Z^\prime$
+mass to be above $4.5$ TeV then the fine tuning in the model will be
+greater than at least $\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$ GeV and $125.5$ GeV.
 
@@
 
-In the top panel one can see that the MSSM BM1 tuning (green curve) 
+In the top panel one can see that the MSSM BM1 tuning 
 steadily climbs as the cutoff scale is increased, as one would expect
@@
 &{}+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMms2BetaTwoLoop}\\
-b_{m_S^2}^{(2)}&=.\label{eq:USSMms2Ot2Coeff}
+b_{m_S^2}^{(2)}&=8\sum_{i=1}^3\left [ 2\lambda_i^4\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4\lambda_i^2a_{\lambda_i}^2 +3\kappa_i^4\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+6\kappa_i^2a_{\kappa_i}^2\right ]\nonumber\\
+&{}+8\sum_{i=1}^3\sum_{j=1}^3\left [ \lambda_i^2\lambda_j^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_{H_j^d}^2+m_{H_j^u}^2+2m_S^2\right )+\left ( \lambda_i a_{\lambda_j}+\lambda_ja_{\lambda_i}\right )^2\right ]\nonumber\\
+&{}+24\sum_{i=1}^3\sum_{j=1}^3\left [ \lambda_i^2\kappa_j^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+\left ( \lambda_ia_{\kappa_j}+\kappa_ja_{\lambda_i}\right )^2\right ]\nonumber\\
+&{}+18\sum_{i=1}^3\sum_{j=1}^3\left [ \kappa_i^2\kappa_j^2\left ( 2m_S^2+m_{Di}^2+m_{\overline{D}i}^2+m_{Dj}^2+m_{\overline{D}j}^2\right )+\left ( \kappa_ia_{\kappa_j}+\kappa_ja_{\kappa_i}\right )^2\right ]\nonumber\\
+&{}+12\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )+12\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2\right.\nonumber\\
+&{}\left.+m_{Q3}^2+m_{d3}^2\right )+4\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )+12\left ( \lambda a_t+y_ta_{\lambda}\right )^2\nonumber\\
+&{}+12\left ( \lambda a_b+y_ba_{\lambda}\right )^2+4\left ( \lambda a_\tau+y_\tau a_{\lambda}\right )^2-32g_3^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_3^2\right )\right.\nonumber\\
+&{}\left.+a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_3\right ]-12g_2^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_2^2\right )+a_{\lambda_i}^2-2\lambda_i a_{\lambda_i}M_2\right ]\nonumber\\
+&{}-\frac{4}{5}g_1^2\sum_{i=1}^3\Big [ 3\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1^2\right )+3a_{\lambda_i}^2-6\lambda_i a_{\lambda_i}M_1\nonumber\\
+&{}+2\kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_1^2\right )+2a_{\kappa_i}^2-4\kappa_i a_{\kappa_i}M_1\Big ]\nonumber\\
+&{}+2g_1'^2\sum_{i=1}^3\Big [ -4\lambda_i^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1'^2\right )\nonumber\\
+&{}+2\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( Q_Sm_{H_i^d}^2+Q_Sm_{H_i^u}^2+Q_Sm_S^2+\Sigma_1'\right )-4\left ( Q_1^2+Q_2^2+Q_S^2\right )\times\nonumber\\
+&{}\times\left ( a_{\lambda_i}^2-2\lambda_i a_{\lambda_i}M_1'\right )+2Q_Sa_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )-6\kappa_i^2\left ( Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\times\nonumber\\
+&{}\times\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_1'^2\right )+3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( Q_Sm_S^2+Q_Sm_{Di}^2+Q_Sm_{\overline{D}i}^2+\Sigma_1'\right )\nonumber\\
+&{}-6\left ( Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\left ( a_{\kappa_i}^2-2\kappa_i a_{\kappa_i}M_1'\right )+3Q_Sa_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\Big ]\nonumber\\
+&{}+12Q_Sg_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+12Q_Sg_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )\nonumber\\
+&{}+12Q_Sg_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+12Q_Sg_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )\nonumber\\
+&{}+4Q_Sg_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+4Q_Sg_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
+&{}-96Q_Sg_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )-12Q_Sg_2^2g_1'^2M_2^2\big ( 9Q_Q+3Q_L+3Q_1\nonumber\\
+&{}+3Q_2+Q_{\overline{H'}}+Q_{H'}\big )-\frac{6}{5}Q_Sg_1^2g_1'^2\Big [ 2M_1^2\big ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}\nonumber\\
+&{}+Q_{H'}+3Q_L+Q_Q+8Q_u\big )-\Sigma_1\big ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+3Q_2+Q_{\overline{H'}}-Q_{H'}\nonumber\\
+&{}-3Q_L+3Q_Q-6Q_u\big )\Big ]-4Q_Sg_1'^4\Big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3+6Q_2^3+2Q_{\overline{H'}}^3\nonumber\\
+&{}+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )+\left ( 6Q_SM_1'^2-\Sigma_1'\right )\Sigma_Q\Big ].\label{eq:USSMms2Ot2Coeff}
 \end{align}

### 2015-03-06 paper/e6ssm-tuning-paper.tex
added tree ree level higgs mass raised to abstract. Plus other rephrasings.

--- 2015-03-06 paper/e6ssm-tuning-paper.tex
@@
 provide the most compelling solution to the $\mu$-problem, which is also 
-a naturalness issue. These very well motivated supersymmetric models 
+a naturalness issue, and allow the tree level Higgs mass to be raised substantially above $M_Z$. These very well motivated supersymmetric models 
 predict a new $Z^\prime$ boson which could be discovered at the LHC and the
@@
  Although the gluino mass and $M_3(M_{SUSY})$ have similar values to
- those in the MSSM BM1 point, in the E$_6$SSM $M_3(M_X)$ is larger
- due to the altered RGE running from exotic matter\footnote{This
-   altered RGE running is a result of the exotic matter introduced to
-   keep the extra $U(1)$ anomaly free. }. This is why this E$_6$SSM
- point has the much larger tuning, coming from $\Delta_{M_3}$.
+ those in the MSSM BM1 point, in the E$_6$SSM $M_3(M_X)$ is larger due
+ to the altered RGE running from exotic matter\footnote{This altered
+   RGE running is a result of the exotic matter introduced to keep the
+   extra $U(1)$ anomaly free. }. This is why this E$_6$SSM BM1 has a
+ larger tuning at larger values of $M_X$, coming from
+ $\Delta_{M_3}$.
 

### 2015-03-06 paper/e6ssm-tuning-paper.tex
deleted empty Fine Tuning section, merged Numerical section into results since it was too short to justify heading.

@@
 coefficient $d$.
-\section{\label{sec:tuning}Fine Tuning}
+%% \section{\label{sec:tuning}Fine Tuning}
 % Introduce tuning measure - BG measure (maybe Peter will add in a justification
@@
 presented in Appendix \ref{app:rges}.
-\section{\label{sec:numericalprocedure}Numerical Procedure}
+%%\section{\label{sec:numericalprocedure}Numerical Procedure}
+
+\section{\label{sec:results}Results}
+
 Using the approach outlined above, we are able to scan the low energy
@@
 
-\section{\label{sec:results}Results}
 % Our results. Plots to go in here:

### 2015-03-06 paper/e6ssm-tuning-paper.tex
More adjustments to phrasings and typos and a few cuts of uneeded or confusing claims.

@@
 how the $Z^\prime$ mass influences the prediction of $M_Z$.  Then in
-section \ref{sec:tuning} we introduce our fine tuning measure and our
-approach to evaluating it to obtain the individual sensitivities.  The
-numerical procedure we use to obtain our results is given in
-\ref{sec:numericalprocedure} and then the results are specified in
-section \ref{sec:results}.
+section \ref{sec:tuningmeasure} we introduce our fine tuning measure
+and our approach to evaluating it to obtain the individual
+sensitivities.  The results are then given in section
+\ref{sec:results}.
 
@@
 \cite{Hesselbach:2001ri, Barger:2005hb, Choi:2006fz,
-  Barger:2007nv}; the relic abundance of dark matter
+  Barger:2007nv}; the relic density of dark matter
 \cite{Kalinowski:2008iq}; GUT scale family symmetries which can
@@
 these models this can open up non-standard decays of the SM--like
-Higgs boson \cite{Hall:2010ix,Nevzorov:2013tta,Athron:2014pua}. The
-correct relic abundance could be obtained entirely through an almost
+Higgs boson \cite{Hall:2010ix,Nevzorov:2013tta,Athron:2014pua}.
+
+The correct relic density could be obtained entirely through an almost
 decoupled ``inert'' neutralino sector \cite{Hall:2009aj}.  However
@@
 case is to make the singlinos extremely light hot dark matter
-candidates and accounts for almost all the relic abundance density with
-the lightest ordinary neutralino.
+candidates, in which case the lightest ordinary neutralino accounts
+for almost all of the observed relic abundance.
 
 The impact of gauge kinetic mixing in the case where both of the extra
-U(1)'s appearing from the breakdown of E$_6$ are present at low energy
-was studied in \cite{Rizzo:2012rf}.  The E$_6$SSM was also included in
-studies looking at how first or second generation sfermion masses
-can be used to constrain the GUT scale parameters \cite{Miller:2012vn}
-and the renormalization of VEVs \cite{Sperling:2013eva,
-  Sperling:2013xqa}.  The particle spectrum and collider signatures of
-the cE$_6$SSM have been studied in a series of
+$U(1)$ symmetries appearing from the breakdown of E$_6$ are present at
+low energy was studied in \cite{Rizzo:2012rf}.  The E$_6$SSM was also
+included in studies looking at how first or second generation sfermion
+masses can be used to constrain the GUT scale parameters
+\cite{Miller:2012vn} and the renormalization of VEVs
+\cite{Sperling:2013eva, Sperling:2013xqa}.  The particle spectrum and
+collider signatures of the cE$_6$SSM have been studied in a series of
 papers,
@@
 threshold corrections to the $\overline{DR}$ gauge and Yukawa
-couplings in the E$_6$SSM have also been calculated and their numerical impact in
-the constrained version examined \cite{Athron:2012pw}.
+couplings in the E$_6$SSM have also been calculated and their
+numerical impact in the constrained version examined
+\cite{Athron:2012pw}.
 %%%%%%%%%%%%%%%%%%---inserted from introduction---%%%%%%%%%%%%%%%%5%%
@@
 $M_Z^2$. In particular, recent experimental limits \cite{Aad:2014cka}
-require that the $Z'$ mass be large, with bounds of $M_{Z'}\gtrsim
-2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim 2.62$ TeV in
-$U(1)_\chi$ models.
-Bounds on the $Z^\prime$ mass for other $E_6$ inspired models, such as the $U(1)_N$ of the E$_6$SSM, lie between those on the $U(1)_\psi$ and $U(1)_\chi$.
-To satisfy these limits typically requires large
-values of the singlet VEV $s$. For example $s\gtrsim 6$ TeV is
-required in the E$_6$SSM with $U(1)'=U(1)_N$, so that
-$|D_{H_1}|,|D_{H_2}|\gg M_Z^2$ for $E_6$ models with $Q_S\neq
-0$. As a result the remaining terms on the right-hand side of
-Eq. (\ref{eq:E6MZequation}) must be tuned to cancel the resulting very
-large contribution to $M_Z$. Moreover, because this is a large tree
-level fine tuning, it may negate the increase in naturalness that is
-associated with having a reduced need for heavy superpartners. In
-$U(1)$ extended models for which $Q_S\neq 0$, the importance
-of the $Z^\prime$ mass to the fine tuning in these models can be made
-even clearer by writing Eq. (\ref{eq:E6MZequation}) in the form given
-in \cite{Athron:2013ipa},
+require that the $Z'$ mass be large, with for example bounds of
+$M_{Z'}\gtrsim 2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim
+2.62$ TeV in $U(1)_\chi$ models. To satisfy these
+limits typically requires large values of the singlet VEV $s$. For
+example $s\gtrsim 6$ TeV is required in the E$_6$SSM with
+$U(1)'=U(1)_N$, so that $|D_{H_1}|,|D_{H_2}|\gg M_Z^2$ for $E_6$
+models with $Q_S\neq 0$. As a result the remaining terms on the
+right-hand side of Eq. (\ref{eq:E6MZequation}) must be tuned to cancel
+the resulting very large contribution to $M_Z$. Moreover, because this
+is a large tree level fine tuning, it may negate the increase in
+naturalness that is associated with having a reduced need for heavy
+superpartners. In $U(1)$ extended models for which $Q_S\neq 0$, the
+importance of the $Z^\prime$ mass to the fine tuning in these models
+can be made even clearer by writing Eq. (\ref{eq:E6MZequation}) in the
+form given in \cite{Athron:2013ipa},
 \begin{equation}\label{eq:originalE6MZequation}
@@
 
-The sensitivity coefficients $\Delta_p$ may be calculated directly
+The sensitivity $\Delta_p$ may be calculated directly
 from the expression for $M_Z^2$ in terms of the $p_i$ for a particular
@@
 RGEs. Once these have been obtained, it is straightforward to solve
-for the $\partial v_i /\partial p$. The sensitivity coefficients
+for the $\partial v_i /\partial p$. The sensitivities 
 $\Delta_p$ are then simply linear combinations of the $\partial
@@
 To illustrate this, in the left panel of Fig.~\ref{Fig:mssmstoptuning}
-we show the variation in fine tuning when we scan over the stop masses
-and mixing, with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq
-10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq A_t\leq -20\textrm{
-  GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.  The remaining
+we show the variation in fine tuning for $M_X=20$ TeV, $50$ TeV, $100$
+TeV and $10^{16}$ GeV when we scan over the stop masses and mixing,
+with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and
+$-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$.  The remaining
 parameters we fix such that at $M_{\rm SUSY}$ they have the values
@@
 10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
-tuning of $\approx 100 - 1000$ and the minimum tuning we see consistent
-with a $125$ GeV Higgs is $\approx 200$, as shown in
+tuning of $\approx 100 - 1000$ and the minimum tuning we see
+consistent with a $125$ GeV Higgs is $\approx 200$, as shown in
 Fig.~\ref{Fig:mssmstoptuning}.
@@
 select a fixed low cutoff of $M_X=20$ TeV and compare the fine tuning
-for two different values of the $Z^\prime$ mass. We choose to look at
-$M_{Z^\prime}=2.5$ TeV, which is just above the current limits, and
-$M_{Z^\prime}=4.5$ TeV, which should be in reach in run II at the LHC
-\cite{Godfrey:2013eta} and then compare the fine tuning calculated in
-each case to the tuning in the MSSM.  For this, we have performed a
-large six dimensional parameter space scan in both the MSSM and
-E$_6$SSM, varying those parameters most relevant for the fine tuning
-and the Higgs mass.  Therefore the set of parameters which we vary
-includes $\mu$, $B$ and $\tan \beta$ for the MSSM, and $\lambda$,
-$A_\lambda$ and $\tan \beta$, for the E$_6$SSM, which appear at tree
-level in the EWSB conditions of the models. While the RGE contribution
-from large stop masses to the fine tuning is small for such a low
-cutoff scale, the stop contributions to the effective potential can
-play a significant role in reducing the fine tuning.  For this reason it is still important to properly treat the
-tuning associated with stop contributions to the one-loop effective
-potential, and so we also scan over the soft masses $m_{Q_3}^2$,
-$m_{u_3}^2$ and the stop mixing $A_t$.  The relevant parameters and
-ranges that were scanned over are summarised in Table
-\ref{tab:scanranges}. With the exception of the stop mixing $A_t$ and
-the soft trilinear $A_\lambda$, which are logarithmically scanned, all
-parameters are linearly scanned.  In addition to this we also repeat
-each scan for three different values of $M_2$ to allow more variation
-in the chargino masses.
+between the MSSM and E$_6$SSM for two different values of the
+$Z^\prime$ mass. We choose to look at $M_{Z^\prime}=2.5$ TeV, which is
+just above the current limits, and $M_{Z^\prime}=4.5$ TeV, which
+should be in reach in run II at the LHC \cite{Godfrey:2013eta} and
+then compare the fine tuning calculated in each case to the tuning in
+the MSSM.  For this, we have performed a six dimensional parameter
+space scan in both the MSSM and E$_6$SSM, varying those parameters
+most relevant for the fine tuning and the Higgs mass.  Therefore the
+set of parameters which we vary includes $\mu$, $B$ and $\tan \beta$
+for the MSSM, and $\lambda$, $A_\lambda$ and $\tan \beta$, for the
+E$_6$SSM, which appear at tree level in the EWSB conditions of the
+models. While the RGE contribution from large stop masses to the fine
+tuning is small for such a low cutoff scale, the stop contributions to
+the effective potential can play a significant role in reducing the
+fine tuning.  For this reason it is still important to properly treat
+the tuning associated with stop contributions to the one-loop
+effective potential, and so we also scan over the soft masses
+$m_{Q_3}^2$, $m_{u_3}^2$ and the stop mixing $A_t$.  The relevant
+parameters and ranges that were scanned over are summarised in Table
+\ref{tab:scanranges}.  In addition to this we also repeat each scan
+for three different values of $M_2$ to allow more variation in the
+chargino masses.
 
@@
 
-MSSM benchmark BM2 (yellow in top panel, individual sensitivities in bottom left panel) was designed to be similar to E$_6$SSM BM2, for a reasonable comparison.
+MSSM benchmark BM2 (yellow in top panel, individual sensitivities in bottom left panel) is designed to be similar to E$_6$SSM BM2, for a reasonable comparison.
 However from the individual sensitivities one can see that the behaviour is quite similar to MSSM BM1, though in this case the $\Delta_{m_{H_u}^2}$ becomes the largest tuning at a higher $M_X$ and does not reach such large values, since more of the tuning is from the mixing in this case.
@@
 \ea
-For a running parameter $q$ appearing in the tree level EWSB conditions, the corresponding contribution to the sensitivity coefficient can then be written 
+For a running parameter $q$ appearing in the tree level EWSB conditions, the corresponding contribution to the individual sensitivity can then be written 
 \be

### 2015-03-17 fs-spectrum/models/lowE6SSM/fill_scan_lowE6SSM.cpp
Added switch allowing to scan over a single parameter only

@@ -349,8 +349,6 @@ int main()
    // U(1)_eta: theta = -ArcTan(Sqrt(5.0 / 3.0))
    const double theta = -ArcTan(Sqrt(5.0 / 3.0));
 
-   const std::size_t num_points = 10;
-
    Eigen::Matrix<double,3,3> YdInput; 
    Eigen::Matrix<double,3,3> YeInput;
    Eigen::Matrix<double,3,3> YuInput;
@@ -591,16 +589,64 @@ int main()
          const double Lambdax_width = 0.05;
          const double mq222_width = 1000.0;
          const double mu222_width = 1000.0;
+         const double MassWB_width = 50.0;
+
+         const std::size_t num_points = 50;
+         const bool is_random_scan = false;
+
+         const lowE6SSM_info::Parameters scan_parameter = lowE6SSM_info::TYu22;
+         
+         const double ALambdax_incr = (num_points > 1 ? ALambdax_width / (num_points - 1.0) : 0.0);
+         const double AYu22_incr = (num_points > 1 ? AYu22_width / (num_points - 1.0) : 0.0);
+         const double Lambdax_incr = (num_points > 1 ? Lambdax_width / (num_points - 1.0) : 0.0);
+         const double mq222_incr = (num_points > 1 ? mq222_width / (num_points - 1.0) : 0.0);
+         const double mu222_incr = (num_points > 1 ? mu222_width / (num_points - 1.0) : 0.0);
+         const double MassWB_incr = (num_points > 1 ? MassWB_width / (num_points - 1.0) : 0.0);
 
          for (std::size_t i = 0; i < num_points; ++i) {
-            lowE6SSM_input_parameters random_input = input;
-            random_input.TLambdaxInput = get_random_TLambdax(input, ALambdax_width, generator);
-            random_input.AYuInput(2,2) = get_random_AYu22(input, AYu22_width, generator);
+            lowE6SSM_input_parameters next_input = input;
 
-            // additional randomised values
-            random_input.LambdaxInput = get_random_Lambdax(input, Lambdax_width, generator);
-            random_input.mq2Input(2,2) = get_random_mq222(input, mq222_width, generator);
-            random_input.mu2Input(2,2) = get_random_mu222(input, mu222_width, generator);
+            // generate random values if random fill scan
+            if (is_random_scan) {
+               next_input.TLambdaxInput = get_random_TLambdax(input, ALambdax_width, generator);
[…]

### 2015-03-17 fs-spectrum/models/lowE6SSM/fill_scan_lowE6SSM.cpp
Changed printout so that for 1D scan all points are printed

@@ -586,15 +586,15 @@ int main()
          // generate additional points from read-in point
          const double ALambdax_width = 1000.0;
          const double AYu22_width = 1000.0;
-         const double Lambdax_width = 0.05;
-         const double mq222_width = 1000.0;
-         const double mu222_width = 1000.0;
+         const double Lambdax_width = 0.1;
+         const double mq222_width = 100000.0;
+         const double mu222_width = 100000.0;
          const double MassWB_width = 50.0;
 
-         const std::size_t num_points = 50;
-         const bool is_random_scan = false;
+         const std::size_t num_points = 10;
+         const bool is_random_scan = true;
 
-         const lowE6SSM_info::Parameters scan_parameter = lowE6SSM_info::TYu22;
+         const lowE6SSM_info::Parameters scan_parameter = lowE6SSM_info::Lambdax;
          
          const double ALambdax_incr = (num_points > 1 ? ALambdax_width / (num_points - 1.0) : 0.0);
          const double AYu22_incr = (num_points > 1 ? AYu22_width / (num_points - 1.0) : 0.0);
@@ -608,7 +608,7 @@ int main()
 
             // generate random values if random fill scan
             if (is_random_scan) {
-               next_input.TLambdaxInput = get_random_TLambdax(input, ALambdax_width, generator);
+               //next_input.TLambdaxInput = get_random_TLambdax(input, ALambdax_width, generator);
                next_input.AYuInput(2,2) = get_random_AYu22(input, AYu22_width, generator);
 
                // additional randomised values
@@ -747,7 +747,9 @@ int main()
                
 
                // print results
-               if (!has_serious_problem && !tuning_problem) {
+               // note that for 1D scans we print irrespective of whether or not
+               // there is an error
+               if (!is_random_scan || (!has_serious_problem && !tuning_problem)) {
                   const Problems<lowE6SSM_info::NUMBER_OF_PARTICLES>& problems = model.get_problems();
                   std::cout << " "
                             << std::setw(12) << std::left << next_input.TanBeta << ' '

### 2015-03-19 paper/e6ssm-tuning-paper.tex
Remove Ellis from name of FT measure.  we cite him thats enough.
Added O(t^2) coefficient for m_{H_u}^2, if time it would be good to check this expression numerically
Substituted several traces into coefficients of g_1^2*g_1'^2*Sigma_1 in O(t^2) coefficients of m_S^2, m_{Q3}^2 and m_{u3}^2 to make the expressions shorter
Added O(t^2) coefficient for m_{H_d}^2
Added O(t^2) coefficient for a_{\lambda}
Added O(t^2) coefficient for a_t
updated paper to include decription of gauge kinetic mixing terms.

@@
 As stated above, to quantify the resulting fine tuning we
-apply the traditional Ellis-Barbieri-Giudice measure
+apply the traditional Barbieri-Giudice measure
 \cite{Ellis:1986yg,Barbieri:1987fn}. A specific model is characterised
@@
 \section{\label{app:rges}RGE Contributions}
-% List the derivatives needed in the Taylor series approximation
-% to the RGE solutions.
+
 Provided that one does not run over too large a range of scales, the
@@
 MSSM, the relevant parameters for the fine tuning calculation are
-$\mu$, $B$, $m_{H_u}^2$, $m_{H_d}^2$ at tree level. The one- and
-two-loop RGEs for these parameters may be found in
-\cite{Martin:1993zk}. The corresponding $O(t^2)$ contributions are
+$\mu$, $B$, $m_{H_u}^2$, $m_{H_d}^2$ at tree level. For the
+renormalisation group running of the relevant parameters
+SOFTSUSY uses the one- and two-loop RGEs from
+\cite{Barger:1993gh,Martin:1993zk}. The corresponding $O(t^2)$
+contributions are
 \begin{subequations}\label{eq:MSSMTreeLevelCoeffs}
@@
 coefficients $b_p^{(2)}$ for a general set of $U(1)'$
-charges. Two-loop RGEs for the gauge and Yukawa couplings, gaugino
-masses and soft trilinears, along with the one-loop RGEs for the soft
-scalar masses, were given in \cite{Athron:2009bs} for the particular
-case of the E$_6$SSM. At tree level in the EWSB conditions the
-parameters that must be considered are $\lambda$, $A_\lambda$,
-$m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and $g_1'$. Neglecting kinetic
-mixing, the two-loop $\beta$ functions for the relevant gauge couplings read
+charges.
+
+ Two-loop RGEs for the gauge and Yukawa couplings, gaugino masses and
+ soft trilinears, along with the one-loop RGEs for the soft scalar
+ masses, were originally obtained in \cite{Athron:2009bs} for the
+ particular case of the E$_6$SSM.  FlexibleSUSY uses full one- and
+ two-loop RGEs from SARAH, which for the models considered here are
+ based on \cite{Martin:1993zk} and the recent extension\footnote{In
+   the version of SARAH which we used the extra terms from this
+   extension were included for all terms except the trilinear and
+   bilinear soft masses. We have been in contact with the SARAH author
+   about this and understand they will be included in future
+   versions.}  \cite{Fonseca:2011vn} to include models with multiple
+ $U(1)$ gauge groups, in the most general case where the trace of the
+ matrix formed from the charges $Q^Y_i$ of the $U(1)_Y$ gauge symmetry
+ and $Q_i$ of the extra $U(1)^\prime$ symmetry does not vanish,
+ i.e.~$\sum_i Q_i^YQ_i \neq 0$.
+
+When this trace is non-zero it will also induce gauge kinetic mixing
+to be generated during RGE evolution and this is the case in the
+models we consider here \footnote{In E$_6$ inspired models with only
+  complete $27$plet matter multiplets this trace would vanish.
+  However since we assume some incomplete multiplets so that our
+  models are consistent with gauge coupling unification this trace
+  doesn't vanish.}. However when these models are evolved down from
+the GUT scale the radiatively generated gauge kinetic mixing gives an
+off diagonal gauge coupling, $g_{11}$ of just $\approx 0.02$ at the
+electroweak scale \cite{King:2005jy} and so it does not play a large
+role.  At the same time if gauge kinetic mixing is included the RGE
+expressions become very large and unmanageable, so we neglected the
+gauge kinetic mixing by setting the SARAH flag NoU1Mixing to true.
+
+%% However for the results we present
+%%  here we set the SARAH flag NoU1Mixing to true to avoid generating
+%%  unmanageably large expressions.  It has previously been checked that
+%%  when these models are evolved down from the GUT scale the radiatively
+%%  generated gauge kinetic mixing gives an off diagonal gauge coupling,
+%%  $g_{11}$ of just $\approx 0.02$ at the electroweak scale
+%%  \cite{King:2005jy} and so it does not play a large role.
+
+At tree level in the EWSB
+conditions the parameters that must be considered are $\lambda$,
+$A_\lambda$, $m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and
+$g_1'$. Neglecting kinetic mixing, the two-loop $\beta$ functions for
+the relevant gauge couplings read
 \begin{subequations}\label{eq:USSMGaugeBetas}
@@
 \end{align*}
-to denote the trace over the $U(1)'$ charges, along with
+to denote the trace over the $U(1)'$ charges, along
+with \footnote{This is the trace which is assumed to vanish in
+  \cite{Martin:1993zk}.  Although we use the the NoU1Mixing to neglect
+  gauge kinetic mixing this is done in SARAH by removing the RGE for
+  the off diagonal gauge couplings and effectively setting them to
+  zero at all scales by removing all terms involving them from the
+  RGEs.  Therefore some terms with this trace remain and the RGEs here
+  do not reduce to those which one would obtain from
+  \cite{Martin:1993zk} nor those which appear in \cite{Athron:2009bs}.
+  Note however these contributions do not appear in the
+  corresponding trilinears due to the version of SARAH used. }
 \begin{align*}
@@
 &{}-\frac{12}{5}g_1^2g_1'^2\left ( Q_1^2+Q_2^2\right )\left ( M_1+M_1'\right )\bigg \},\label{eq:USSMTLambdaBetaTwoLoop}\\
-b_{a_\lambda}^{(2)}&=,\label{eq:USSMTLambdaOt2Coeff}
+b_{a_\lambda}^{(2)}&=\lambda \bigg [ 4\lambda a_\lambda +4\Sigma_{a_\lambda}+6\Sigma_{a_\kappa}+6y_ta_t+6y_ba_b+2y_\tau a_\tau +6g_2^2M_2+\frac{6}{5}g_1^2M_1\nonumber\\
+&{}+4g_1'^2M_1'\left ( Q_1^2+Q_2^2+Q_S^2 \right )\bigg ]\times\bigg[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2\nonumber\\
+&{}-\frac{3}{5} g_1^2 -2 \left ( Q_1^2 + Q_2^2 + Q_S^2\right )g_1'^2 \bigg]+a_\lambda\bigg \{ 2\lambda^2\left ( 3\lambda^2 +4\Sigma_\lambda +6\Sigma_\kappa \right )+4\Pi_\lambda + 6\Pi_\kappa \nonumber\\
+&{}+6\left ( \Sigma_\lambda+\frac{3}{2}\Sigma_\kappa\right )^2+7\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right )+\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\left (2\Sigma_\lambda+3\Sigma_\kappa\right ) \nonumber\\
+&{}+3\left ( \frac{15}{2}y_t^4+\frac{15}{2}y_b^4+\frac{3}{2}y_\tau^4 +5y_b^2y_t^2 +3y_b^2y_\tau^2 +y_t^2y_\tau^2\right )\nonumber\\
+&{}-\frac{1}{5}g_1^2\left ( 12\lambda^2+16y_b^2+22y_t^2+12y_\tau^2+12\Sigma_\lambda +13\Sigma_\kappa \right )\nonumber\\
+&{}-3g_2^2\left ( 4\lambda^2+6y_t^2+6y_b^2+2y_\tau^2+4\Sigma_\lambda+3\Sigma_\kappa\right )-16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa \right )\nonumber\\
+&{}-2g_1'^2\left [ 4\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( \lambda^2 +\Sigma_\lambda \right )+3\Sigma_\kappa\left ( Q_1^2+Q_2^2+Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\right .\nonumber\\
+&{}+3y_b^2\left ( 2Q_1^2+Q_2^2+Q_d^2+Q_Q^2+Q_S^2 \right )+3y_t^2\left ( Q_1^2+2Q_2^2+Q_Q^2+Q_S^2+Q_u^2\right )\nonumber\\
+&{}\left.+y_\tau^2\left ( 2Q_1^2+Q_2^2+Q_e^2+Q_L^2+Q_S^2\right )\right ]-\frac{15}{2}g_2^4-\frac{279}{50}g_1^4\nonumber\\
+&{}+2g_1'^4\left ( Q_1^2+Q_2^2+Q_S^2 \right )\left (Q_1^2+Q_2^2+Q_S^2-\Sigma_{Q}\right )+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\nonumber\\
+&{}+\frac{6}{5}g_1^2g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2 \right ) \bigg \}+\lambda \bigg [16\lambda^3a_{\lambda}+16\Pi_{a_\lambda}+24\Pi_{a_\kappa}+8\lambda\sum_{i=1}^3\lambda_i\left ( \lambda_i a_{\lambda}+a_{\lambda_i}\lambda\right )\nonumber\\
+&{}+12\lambda\sum_{i=1}^3\kappa_i\left ( \kappa_i a_\lambda + a_{\kappa_i} \lambda\right )+8\sum_{i=1}^3\sum_{j=1}^3\lambda_i\lambda_j\left ( a_{\lambda_i}\lambda_j+\lambda_ia_{\lambda_j}\right )\nonumber\\
+&{}+18\sum_{i=1}^3\sum_{j=1}^3\kappa_i\kappa_j\left ( \kappa_i a_{\kappa_j}+a_{\kappa_i}\kappa_j\right )+24\sum_{i=1}^3\sum_{j=1}^3\lambda_i\kappa_j\left ( \lambda_i a_{\kappa_j}+a_{\lambda_i}\kappa_j\right )+72y_t^3a_t+72y_b^3a_b\nonumber\\
+&{}+16y_\tau^3a_\tau+12y_ty_b\left ( a_ty_b+y_ta_b\right )+12y_by_\tau\left ( a_by_\tau+y_ba_\tau\right )+30\lambda y_t\left ( a_{\lambda}y_t+\lambda a_t\right )\nonumber\\
+&{}+30\lambda y_b\left ( a_{\lambda}y_b+\lambda a_b\right )+10\lambda y_\tau\left ( a_{\lambda}y_\tau+\lambda a_{\tau}\right )-32g_3^2y_t\left ( a_t-y_tM_3\right )-32g_3^2y_b\left ( a_b-y_bM_3\right )\nonumber\\
+&{}-32g_3^2\left ( \Sigma_{a_\kappa}-M_3\Sigma_\kappa\right )-12g_2^2\lambda\left ( a_\lambda-\lambda M_2\right )-18g_2^2y_t\left ( a_t-y_tM_2\right )-18g_2^2y_b\left ( a_b-y_bM_2\right )\nonumber\\
+&{}-6g_2^2y_\tau\left ( a_\tau-y_\tau M_2\right )-12g_2^2\left ( \Sigma_{a_\lambda}-M_2\Sigma_\lambda \right )-\frac{12}{5}g_1^2\lambda\left ( a_{\lambda}-\lambda M_1\right )-\frac{26}{5}g_1^2y_t\left ( a_t-y_tM_1\right )\nonumber\\
+&{}-\frac{14}{5}g_1^2y_b\left ( a_b-y_bM_1\right )-\frac{18}{5}g_1^2y_\tau\left ( a_\tau-y_\tau M_1\right )-\frac{12}{5}g_1^2\left ( \Sigma_{a_\lambda}-M_1\Sigma_\lambda\right )-\frac{8}{5}g_1^2\left ( \Sigma_{a_\kappa}-M_1\Sigma_\kappa\right )\nonumber\\
+&{}-8g_1'^2\lambda\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( a_\lambda-\lambda M_1'\right )-12g_1'^2y_t\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( a_t-y_tM_1'\right )\nonumber\\
+&{}-12g_1'^2y_b\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( a_b-y_bM_1'\right )-4g_1'^2y_\tau\left ( Q_1^2+Q_L^2+Q_e^2\right )\left ( a_\tau-y_\tau M_1'\right )\nonumber\\
+&{}-8g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( \Sigma_{a_\lambda}-M_1'\Sigma_\lambda \right )-12g_1'^2\left ( Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\left (\Sigma_{a_\kappa}-M_1'\Sigma_{\kappa}\right )\nonumber\\
+&{}+48g_2^4M_2+\frac{576}{25}g_1^4M_1+8g_1'^4M_1'\Sigma_Q\left ( Q_1^2+Q_2^2+Q_S^2\right )\bigg ],\label{eq:USSMTLambdaOt2Coeff}
 \end{align}
@@
 &{}+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmHd2BetaTwoLoop}\\
-b_{m_{H_d}^2}^{(2)}&=.\label{eq:USSMmHd2Ot2Coeff}
+b_{m_{H_d}^2}^{(2)}&=72y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+144y_b^2a_b^2+16y_\tau^4\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+32y_\tau^2 a_\tau^2\nonumber\\
+&{}+8\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+16\lambda^2 a_\lambda^2+6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )\nonumber\\
+&{}+6\left ( y_t a_b+y_b a_t\right )^2+12y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{d3}^2+m_{L3}^2+m_{e3}^2\right )+12\left ( y_b a_\tau + y_\tau a_b\right )^2\nonumber\\
+&{}+6\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )+6\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
+&{}+12\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )+12\left ( \lambda a_b+y_b a_\lambda\right )^2\nonumber\\
+&{}+4\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )+4\left ( \lambda a_\tau + y_\tau a_\lambda\right )^2\nonumber\\
+&{}+4\sum_{i=1}^3\left [ \lambda^2\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_{H_d}^2+m_{H_u}^2+2m_S^2\right )+\left ( \lambda a_{\lambda_i}+\lambda_i a_\lambda\right )^2\right ]\nonumber\\
+&{}+6\sum_{i=1}^3\left [ \lambda^2\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+\left ( \lambda a_{\kappa_i}+\kappa_i a_\lambda\right )^2\right ]\nonumber\\
+&{}-32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_3^2\right )-32g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
+&{}-18g_2^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_2^2\right )-18g_2^2\left ( a_b^2-2y_ba_bM_2\right )\nonumber\\
+&{}-6g_2^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2M_2^2\right )-6g_2^2\left ( a_\tau^2-2y_\tau a_\tau M_2\right )\nonumber\\
+&{}-6g_2^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_2^2\right )-6g_2^2\left ( a_\lambda^2-2\lambda a_\lambda M_2\right )\nonumber\\
+&{}-\frac{14}{5}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1^2\right )-\frac{14}{5}g_1^2\left ( a_b^2-2y_ba_bM_1\right )\nonumber\\
+&{}-\frac{18}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2M_1^2\right )-\frac{18}{5}g_1^2\left ( a_\tau^2-2y_\tau a_\tau M_1\right )\nonumber\\
+&{}-\frac{6}{5}g_1^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1^2\right )-\frac{6}{5}g_1^2\left ( a_\lambda^2-2\lambda a_\lambda M_1\right )\nonumber\\
+&{}-12g_1'^2y_b^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1'^2\right )-12g_1'^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\times\nonumber\\
+&{}\times\left ( a_b^2-2y_b a_b M_1'\right )+6g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( 2Q_1m_{H_d}^2+2Q_1m_{Q3}^2+2Q_1m_{d3}^2+\Sigma_1'\right )\nonumber\\
+&{}+12Q_1g_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )-4g_1'^2y_\tau^2\left ( Q_1^2+Q_L^2+Q_e^2\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2M_1'^2\right )\nonumber\\
+&{}-4g_1'^2\left ( Q_1^2+Q_L^2+Q_e^2\right )\left ( a_\tau^2-2y_\tau a_\tau M_1'\right )+2g_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\times\nonumber\\
+&{}\times\left ( 2Q_1m_{H_d}^2+2Q_1m_{L3}^2+2Q_1m_{e3}^2+\Sigma_1'\right )+4Q_1g_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
+&{}+12Q_1g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+12Q_1g_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )\nonumber\\
+&{}-4g_1'^2\lambda^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )-4g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\times\nonumber\\
+&{}\times\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )+2g_1'^2\lambda^2\left ( Q_1+Q_2+Q_S\right )\Sigma_1'+4Q_1g_1'^2\left ( Q_1+Q_2+Q_S\right )\times\nonumber\\
+&{}\times\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+a_{\lambda_i}^2\right ]+6Q_1g_1'^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\times\nonumber\\
+&{}\times\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+a_{\kappa_i}^2\right ]-96Q_1g_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )\nonumber\\
+&{}-72g_2^4M_2^2-12Q_1g_2^2g_1'^2M_2^2\left ( 9Q_Q+3Q_L+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\right )\nonumber\\
+&{}-\frac{288}{25}g_1^4\left ( \Sigma_1+3M_1^2\right )-\frac{3}{5}g_1^2g_1'^2\Big [ 4Q_1M_1^2\big ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2\nonumber\\
+&{}+Q_{\overline{H'}}+Q_{H'}+3Q_L+Q_Q+8Q_u\big )-4M_1'^2\big ( 3Q_d^2+3Q_{\overline{D}}^2-3Q_D^2+3Q_e^2-3Q_1^2+3Q_2^2\nonumber\\
+&{}+Q_{\overline{H'}}^2-Q_{H'}^2-3Q_L^2+3Q_Q^2-6Q_u^2\big )+\left ( \Sigma_1'-2Q_1\Sigma_1\right )\Sigma_Q^Y\Big ]-4Q_1g_1'^4\Big [ 2M_1'^2\big ( 9Q_d^3\nonumber\\
+&{}+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )\nonumber\\
+&{}+\left ( 6Q_1M_1'^2-\Sigma_1'\right )\Sigma_Q\Big ].\label{eq:USSMmHd2Ot2Coeff}
 \end{align}
@@
 &{}+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmHu2BetaTwoLoop}\\
-b_{m_{H_u}^2}^{(2)}&=,\label{eq:USSMmHu2Ot2Coeff}
+b_{m_{H_u}^2}^{(2)}&=72y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+144y_t^2a_t^2+8\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+16\lambda^2a_\lambda^2\nonumber\\
+&{}+6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )+6\left ( y_ta_b+y_ba_t\right )^2\nonumber\\
+&{}+12\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )+12\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
+&{}+6\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )+6\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
+&{}+2\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )+2\left ( \lambda a_\tau+y_\tau a_\lambda\right )^2\nonumber\\
+&{}+4\sum_{i=1}^3 \left [ \lambda^2\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_{H_d}^2+m_{H_u}^2+2m_S^2\right )+\left ( \lambda a_{\lambda_i}+\lambda_i a_{\lambda}\right )^2\right ] \nonumber\\
+&{}+6\sum_{i=1}^3\left [ \lambda^2\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )
++\left ( \lambda a_{\kappa_i}+\kappa_i a_\lambda\right )^2\right ]\nonumber\\
+&{}-32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_3^2\right )-32g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
+&{}-18g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_2^2\right )-18g_2^2\left ( a_t^2-2y_ta_tM_2\right )\\
+&{}-6g_2^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_2^2\right )-6g_2^2\left ( a_\lambda^2-2\lambda a_\lambda M_2\right )\nonumber\\
+&{}-\frac{26}{5}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1^2\right )-\frac{26}{5}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
+&{}-\frac{6}{5}g_1^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1^2\right )-\frac{6}{5}g_1^2\left ( a_\lambda^2-2\lambda a_\lambda M_1\right )\nonumber\\
+&{}-12g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )-12g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\times\nonumber\\
+&{}\times\left ( a_t^2-2y_ta_tM_1'\right )+6g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 2Q_2m_{H_u}^2+2Q_2m_{Q3}^2+2Q_2m_{u3}^2+\Sigma_1'\right )\nonumber\\
+&{}+12Q_2g_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_2g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
+&{}+12Q_2g_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )+4Q_2g_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )\nonumber\\
+&{}+4Q_2g_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )-4g_1'^2\lambda^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )\nonumber\\
+&{}-4g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )+2g_1'^2\lambda^2\left ( Q_1+Q_2+Q_S\right )\Sigma_1'\nonumber\\
+&{}+4Q_2g_1'^2\left ( Q_1+Q_2+Q_S\right )\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+a_{\lambda_i}^2\right ]\nonumber\\
+&{}+6Q_2g_1'^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+a_{\kappa_i}^2\right ]\nonumber\\
+&{}-96Q_2g_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )-72g_2^4M_2^2\nonumber\\
+&{}-12Q_2g_2^2g_1'^2M_2^2\left ( 9Q_Q+3Q_L+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\right )+\frac{288}{25}g_1^4\left ( \Sigma_1-3M_1^2\right )\nonumber\\
+&{}-\frac{3}{5}g_1^2g_1'^2\Big [ 4Q_2M_1^2\big ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}+3Q_L\nonumber\\
+&{}+Q_Q+8Q_u\big )+4M_1'^2\big ( 3Q_d^2+3Q_{\overline{D}}^2-3Q_D^2+3Q_e^2-3Q_1^2+3Q_2^2+Q_{\overline{H'}}^2-Q_{H'}^2\nonumber\\
+&{}-3Q_L^2+3Q_Q^2-6Q_u^2\big )-\left ( 2Q_2\Sigma_1+\Sigma_1'\right )\Sigma_Q^Y\Big ]-4Q_2g_1'^4\Big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3\nonumber\\
+&{}+3Q_e^3+6Q_1^3+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )\nonumber\\
+&{}+\left ( 6Q_2M_1'^2-\Sigma_1'\right )\Sigma_Q\Big ],\label{eq:USSMmHu2Ot2Coeff}
 \end{align}
@@
 &{}+3Q_2+Q_{\overline{H'}}+Q_{H'}\big )-\frac{6}{5}Q_Sg_1^2g_1'^2\Big [ 2M_1^2\big ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}\nonumber\\
-&{}+Q_{H'}+3Q_L+Q_Q+8Q_u\big )-\Sigma_1\big ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+3Q_2+Q_{\overline{H'}}-Q_{H'}\nonumber\\
-&{}-3Q_L+3Q_Q-6Q_u\big )\Big ]-4Q_Sg_1'^4\Big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3+6Q_2^3+2Q_{\overline{H'}}^3\nonumber\\
-&{}+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )+\left ( 6Q_SM_1'^2-\Sigma_1'\right )\Sigma_Q\Big ].\label{eq:USSMms2Ot2Coeff}
+&{}+Q_{H'}+3Q_L+Q_Q+8Q_u\big )-\Sigma_1\Sigma_Q^Y\Big ]-4Q_Sg_1'^4\Big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3\nonumber\\
+&{}+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )+\left ( 6Q_SM_1'^2-\Sigma_1'\right )\Sigma_Q\Big ].\label{eq:USSMms2Ot2Coeff}
 \end{align}
@@
 \beta_{a_t}^{(1)}&=a_t\left [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2-2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\right ]\nonumber\\
-&{}+y_t\left [ 2\lambda a_\lambda + 12y_ta_t+2y_ba_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1\right.\nonumber\\
-&{}\left.+4g_1'^2M_1'\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\right ],\label{eq:USSMTYu22BetaOneLoop}\\
+&{}+y_t\bigg [ 2\lambda a_\lambda + 12y_ta_t+2y_ba_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1\nonumber\\
+&{}+4g_1'^2M_1'\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg ],\label{eq:USSMTYu22BetaOneLoop}\\
 \beta_{a_t}^{(2)}&=a_t\bigg \{-22y_t^4-5y_b^4-5y_t^2y_b^2-y_b^2y_\tau^2-\lambda^2 \left ( \lambda^2+3y_t^2+4y_b^2+y_\tau^2+2\Sigma_\lambda + 3\Sigma_\kappa\right )\nonumber\\
@@
 &{}-12g_2^2g_1'^2\left ( Q_2^2+Q_Q^2\right )\left ( M_2+M_1'\right )-\frac{4}{15}g_1^2g_1'^2\left ( 9Q_2^2+Q_Q^2+16Q_u^2\right )\left ( M_1+M_1'\right )\bigg \},\label{eq:USSMTYu22BetaTwoLoop}\\
-b_{a_t}^{(2)}&=.\label{eq:USSMTYu22Ot2Coeff}
+b_{a_t}^{(2)}&=y_t\bigg [ 2\lambda a_\lambda + 12y_ta_t+2y_ba_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1\nonumber\\
+&{}+4g_1'^2M_1'\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg ]\times\bigg [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2\nonumber\\
+&{}-2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg ]+a_t\bigg \{ 54y_t^4+\frac{13}{2}y_b^4+13y_t^2y_b^2+y_b^2y_\tau^2\nonumber\\
+&{}+\lambda^2\left ( \frac{5}{2}\lambda^2+15y_t^2+5y_b^2+y_\tau^2+2\Sigma_\lambda+3\Sigma_\kappa \right )-\frac{16}{3}g_3^2\left ( \lambda^2+2y_b^2+12y_t^2\right )\nonumber\\
+&{}-6g_2^2\left ( \lambda^2+y_b^2+6y_t^2\right )-g_1^2\left ( \frac{22}{15}\lambda^2+\frac{4}{3}y_b^2+\frac{52}{5}y_t^2\right )\nonumber\\
+&{}-2g_1'^2\left [ \lambda^2 \left (Q_1^2+2Q_2^2+Q_S^2+Q_Q^2+Q_u^2 \right )+y_b^2\left ( Q_1^2+Q_2^2+2Q_Q^2+Q_u^2+Q_d^2\right )\right.\nonumber\\
+&{}\left.+12y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\right ]+\frac{128}{9}g_3^4-\frac{15}{2}g_2^4-\frac{143}{18}g_1^4\nonumber\\
+&{}+2g_1'^4\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( Q_2^2+Q_Q^2+Q_u^2-\Sigma_{Q}\right )+16g_3^2g_2^2+\frac{208}{45}g_3^2g_1^2\nonumber\\
+&{}+\frac{32}{3}g_3^2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )+\frac{13}{5}g_2^2g_1^2+6g_2^2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\nonumber\\
+&{}+\frac{26}{15}g_1^2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg \}+y_t\bigg [ 144y_t^3a_t+24y_b^3a_b+14y_ty_b\left ( y_ta_b+a_ty_b\right )\nonumber\\
+&{}+2y_by_\tau\left ( y_b a_\tau+a_by_\tau\right )+18\lambda y_t\left ( \lambda a_t+a_{\lambda}y_t\right )+8\lambda y_b\left ( \lambda a_b+a_{\lambda}y_b\right )+2\lambda y_\tau\left ( \lambda a_\tau+a_{\lambda}y_\tau\right )\nonumber\\
+&{}+8\lambda^3a_{\lambda}+4\lambda\sum_{i=1}^3\lambda_i\left ( \lambda a_{\lambda_i}+a_{\lambda}\lambda_i\right )+6\lambda\sum_{i=1}^3\kappa_i\left ( \lambda a_{\kappa_i}+a_{\lambda}\kappa_i\right )-64g_3^2y_t\left ( a_t-y_tM_3\right )\nonumber\\
+&{}-\frac{32}{3}g_3^2y_b\left ( a_b-y_bM_3\right )-36g_2^2y_t\left ( a_t-y_tM_2\right )-6g_2^2y_b\left ( a_b-y_bM_2\right )-6g_2^2\lambda\left ( a_\lambda-\lambda M_2\right )\nonumber\\
+&{}-\frac{52}{5}g_1^2y_t\left ( a_t-y_tM_1\right )-\frac{14}{15}g_1^2y_b\left ( a_b-y_bM_1\right )-\frac{18}{15}g_1^2\lambda \left ( a_\lambda-\lambda M_1\right )\nonumber\\
+&{}-24g_1'^2y_t\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( a_t-y_tM_1'\right )-4g_1'^2y_b\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( a_b-y_bM_1'\right )\nonumber\\
+&{}-4g_1'^2\lambda \left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( a_\lambda-\lambda M_1'\right )+48g_2^4M_2+\frac{832}{25}g_1^4M_1\nonumber\\
+&{}+8g_1'^4M_1'\Sigma_Q\left ( Q_2^2+Q_Q^2+Q_u^2\right )\bigg ].\label{eq:USSMTYu22Ot2Coeff}
 \end{align}
@@
 &{}+Q_Q+8Q_u\big )+4M_1'^2\big ( 3Q_d^2+3Q_{\overline{D}}^2-3Q_D^2+3Q_e^2-3Q_1^2+3Q_2^2+Q_{\overline{H'}}^2-Q_{H'}^2-3Q_L^2\nonumber\\
-&{}+3Q_Q^2-6Q_u^2\big )-\left ( 6Q_Q\Sigma_1+\Sigma_1'\right )\big ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+3Q_2+Q_{\overline{H'}}\nonumber\\
-&{}-Q_{H'}-3Q_L+3Q_Q-6Q_u\big )\big ]-4Q_Qg_1'^4\big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3\nonumber\\
+&{}+3Q_Q^2-6Q_u^2\big )-\left ( 6Q_Q\Sigma_1+\Sigma_1'\right )\Sigma_Q^Y\big ]-4Q_Qg_1'^4\big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3\nonumber\\
 &{}+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )+\left ( 6Q_QM_1'^2-\Sigma_1'\right )\Sigma_Q\big ].\label{eq:USSMmq222Ot2Coeff}
@@
 &{}+3Q_Q^2-6Q_u^2 )+6Q_uM_1^2 ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\nonumber\\
-&{}+3Q_L+Q_Q+8Q_u )+\left ( 3Q_u\Sigma_1-2\Sigma_1^\prime\right ) ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+3Q_2\nonumber\\
-&{}+Q_{\overline{H'}}-Q_{H'}-3Q_L+3Q_Q-6Q_u )\big ]-4Q_ug_1'^4\big [ 2M_1'^2 ( 9Q_d^3+9Q_D^3+9Q_{\overline{D}}^3+3Q_e^2\nonumber\\
-&{}+6Q_1^2+6Q_2^2+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3 )\nonumber\\
+&{}+3Q_L+Q_Q+8Q_u )+\left ( 3Q_u\Sigma_1-2\Sigma_1^\prime\right ) \Sigma_Q^Y\big ]-4Q_ug_1'^4\big [ 2M_1'^2 ( 9Q_d^3+9Q_D^3+9Q_{\overline{D}}^3\nonumber\\
+&{}+3Q_e^2+6Q_1^2+6Q_2^2+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3 )\nonumber\\
 &{}+\left(6Q_uM_1'^2-\Sigma_1^\prime\right )\Sigma_Q\big ].\label{eq:USSMmu222Ot2Coeff}

### 2015-03-19 paper/e6ssm-tuning-paper.tex
remove comments.
updated acknowldgements to add Florian Staub and FS collaborators.

@@
 \begin{abstract}
-%%The abstract.
-%%Original abstract
-%% title: Naturalness in U(1) extensions of the MSSM
-% Copied SUSY2014 abstract.
-%% With the discovery of a 125 GeV Standard Model (SM) like Higgs boson
-%% and rising lower bounds on the masses of superpartners, minimal models
-%% of low energy supersymmetry (SUSY) appear to be increasingly fine
-%% tuned. In the Minimal Supersymmetric Standard Model (MSSM) large stop
-%% masses, needed to obtain the observed Higgs mass, give a significant
-%% contribution to fine tuning. $U(1)$ extensions of the MSSM that solve
-%% the $\mu$-problem have new F- and D-term contributions to the Higgs
-%% mass, allowing a 125 GeV Higgs with lighter stops and so alleviating
-%% the associated fine tuning. However, it was recently demonstrated,
-%% within a constrained version of the Exceptional Supersymmetric
-%% Standard Model (E$_6$SSM) defined at the Grand Unification (GUT)
-%% scale, that the presence of a massive $Z'$ boson introduces a
-%% substantial new source of tuning in these theories at tree level. Here
-%% we consider the impact of this tuning when we remove the fine tuning
-%% that depends on assumptions about the SUSY breaking scale, by setting
-%% the SUSY breaking parameters at low energies. We find that the
-%% existing experimental bounds on the $Z'$ mass impose an effective
-%% lower bound on the fine tuning, which does not depend on assumptions
-%% about SUSY breaking.  We compare our results against the tuning in the
-%% MSSM with the SUSY breaking terms also defined at low energies.
-
-%%Alternative 1
-%% Alt title: Probing natural SUSY in the most general way in the MSSM and U(1) extensions.
-
-%% The discovery of a 125 GeV Standard Model (SM) like Higgs boson and
-%% rising lower bounds on the masses of superpartners, have lead to
-%% concerns that supersymmetric models are now fine tuned.  In the
-%% Minimal Supersymmetric Standard Model (MSSM) large stop masses,
-%% required for a $125$ GeV Higgs, also feed into the EWSB conditions
-%% through renormalisation group equations forcing one to fine tune these
-%% parameters to obtain the correct electroweak vacuum expectation
-%% value. Nonetheless this fine tuning depends crucially on our
-%% assumptions about the SUSY breaking scale.  Here we consider what fine
-%% tuning may appear in supersymmetry at tree level, so that it is not so
-%% dependent on assumptions about the SUSY breaking mechanism.  We focus
-%% on U(1) extensions since these provide the most elegant solution to
-%% the $\mu$-problem, which is also a naturalness issue, but we also
-%% compare to the simplest SUSY model, the MSSM. In U(1) extensions anew
-%% F- and D-term contributions raise the Higgs mass, allowing a $125$ GeV
-%% Higgs with lighter stops which can alleviate this stop fine tuning in
-%% models with SUSY breaking fixed at the high scale. However the
-%% presence of a massive $Z'$ boson introduces a substantial new source
-%% of tuning in these theories at tree level.  By choosing a low scale
-%% boundary condition for where the SUSY breaking parameters are set we
-%% compare how this tree level tuning compares to that of the MSSM where
-%% chargino mass limits are the best way to probe tree level fine tuning,
-%% by raising $\mu$ directly.  We find that the $Z^\tprime$ tuning places
-%% more stringent limits on the fine tuning in most of the $U(1)$
-%% extensions and that increasing $Z^\prime$ limits will challenge the
-%% most natural scenarios of these models.
-
-%% Alternative 2
-
-%% Alt title: Z' mass limits and the naturalness of supersymmetry
 
@@
 
-\acknowledgements
-We would like to thank R.
-Nevzorov for many useful discussions and comments.
-DH would also like to thank A.
-Ismail and T.
-Rizzo.
-This work was supported by the University of Adelaide and by the ARC Centre of Excellence for Particle Physics at the Terascale.
+\acknowledgements We would like to thank R. Nevzorov for many useful
+discussions and comments and Florian Staub for very helpful responses
+regarding the gauge kinetic mixing contributions in SARAH. DH would
+also like to thank A. Ismail and T. Rizzo. PA would like to thank
+J.H.~Park, A.~Voigt and D.~Stockinger for useful discussion regarding
+the use of FlexibleSUSY in this project. This work was supported by
+the University of Adelaide and by the ARC Centre of Excellence for
+Particle Physics at the Terascale.
 
@@
 gauge kinetic mixing by setting the SARAH flag NoU1Mixing to true.
-
-%% However for the results we present
-%%  here we set the SARAH flag NoU1Mixing to true to avoid generating
-%%  unmanageably large expressions.  It has previously been checked that
-%%  when these models are evolved down from the GUT scale the radiatively
-%%  generated gauge kinetic mixing gives an off diagonal gauge coupling,
-%%  $g_{11}$ of just $\approx 0.02$ at the electroweak scale
-%%  \cite{King:2005jy} and so it does not play a large role.
 

### 2015-03-19 paper/e6ssm-tuning-paper.tex
changed footnote to emphasise agreeemnt when trace vanishes.
remove duplicated the in several places.

@@
 Nonetheless the MSSM the impact of potential chargino mass limits is
-shown in Fig.~\ref{Fig:chargino-plot}.  There we see that if the the
+shown in Fig.~\ref{Fig:chargino-plot}.  There we see that if the 
 full parameter space with $m_{\tilde{\chi}^\pm_1} < 700$ GeV was excluded the
@@
 the stops and soft Higgs masses (which appear directly in the EWSB
-conditions) should appear in the the EWSB condition for $M_Z$ and
+conditions) should appear in the EWSB condition for $M_Z$ and
 therefore it was expected that these masses should not be much bigger
@@
 with \footnote{This is the trace which is assumed to vanish in
-  \cite{Martin:1993zk}.  Although we use the the NoU1Mixing to neglect
+  \cite{Martin:1993zk}.  Although we use the NoU1Mixing to neglect
   gauge kinetic mixing this is done in SARAH by removing the RGE for
@@
   do not reduce to those which one would obtain from
-  \cite{Martin:1993zk} nor those which appear in \cite{Athron:2009bs}.
-  Note however these contributions do not appear in the
+  \cite{Martin:1993zk} or \cite{Athron:2009bs} unless $\Sigma_{Q}^Y =
+  0$.  Note however these contributions do not appear in the
   corresponding trilinears due to the version of SARAH used. }

### 2015-03-27 fs-spectrum/models/lowE6SSM/fill_scan_lowE6SSM.cpp
Changed charges to be appropriate for U(1)_I, moved initialisation of spectrum generator in full tuning scan to avoid possibly changing initial conditions on each point

@@ -347,7 +347,7 @@ int main()
    // U(1)_I: theta = PI + ArcTan(Sqrt(0.6))
    // U(1)_psi: theta = 0.5 * PI
    // U(1)_eta: theta = -ArcTan(Sqrt(5.0 / 3.0))
-   const double theta = -ArcTan(Sqrt(5.0 / 3.0));
+   const double theta = PI + ArcTan(Sqrt(0.6));
 
    Eigen::Matrix<double,3,3> YdInput; 
    Eigen::Matrix<double,3,3> YeInput;
@@ -361,7 +361,7 @@ int main()
    YdInput(1,2) = 0.0;
    YdInput(2,0) = 0.0;
    YdInput(2,1) = 0.0;
-   YdInput(2,2) = 1.22357994e-01;
+   YdInput(2,2) = 1.26129729e-01; //1.24073356e-01; //1.25830060e-01; //1.23986233e-01; //1.26812790e-01; //1.22357994e-01;
 
    YeInput(0,0) = 0.0;
    YeInput(0,1) = 0.0;
@@ -371,7 +371,7 @@ int main()
    YeInput(1,2) = 0.0;
    YeInput(2,0) = 0.0;
    YeInput(2,1) = 0.0;
-   YeInput(2,2) = 9.88254141e-02;
+   YeInput(2,2) = 9.82521715e-02; //9.81978185e-02; //9.83300957e-02; //9.81211077e-02; //9.87082739e-02; //9.88254141e-02;
 
    YuInput(0,0) = 0.0;
    YuInput(0,1) = 0.0;
@@ -381,13 +381,13 @@ int main()
    YuInput(1,2) = 0.0;
    YuInput(2,0) = 0.0;
    YuInput(2,1) = 0.0;
-   YuInput(2,2) = 8.74991501e-01;
+   YuInput(2,2) = 8.81939505e-01; //8.81785907e-01; //8.81246710e-01; //8.75250164e-01; //8.74478241e-01; //8.74991501e-01;
 
-   const double g1Input = 4.71880484e-01;
-   const double g2Input = 6.36109014e-01;
-   const double g3Input = 9.99300252e-01;
-   const double gNInput = 5.10342303e-01;
-   const double vInput = 2.41460403e+02;
+   const double g1Input = 4.71996005e-01; //4.71290081e-01; //4.71922380e-01; //4.72062287e-01; //4.72742529e-01; //4.71880484e-01;
[…]

### 2015-03-27 fs-spectrum/models/lowE6SSM/full_tuning_scan_lowE6SSM.cpp

@@ -43,7 +43,7 @@ namespace flexiblesusy {
       // U(1)_I: theta = PI + ArcTan(Sqrt(0.6))
       // U(1)_psi: theta = 0.5 * PI
       // U(1)_eta: theta = -ArcTan(Sqrt(5.0 / 3.0))
-      const double theta = -ArcTan(Sqrt(5.0 / 3.0));
+      const double theta = PI + ArcTan(Sqrt(0.6)); 
       
       initialize_e6_charges(theta, input);
       
@@ -167,12 +167,6 @@ int main()
    lowE6SSM_input_parameters input;
    QedQcd oneset;
    oneset.toMz();
-
-   lowE6SSM_spectrum_generator<algorithm_type> spectrum_generator;
-   spectrum_generator.set_precision_goal(1.0e-4);
-   spectrum_generator.set_max_iterations(0);         // 0 == automatic
-   spectrum_generator.set_calculate_sm_masses(0);    // 0 == no
-   spectrum_generator.set_parameter_output_scale(0); // 0 == susy scale
 
    std::vector<double> TanBeta_vals = {2, 4, 6, 8, 10, 15, 20, 30, 40, 50};
 
@@ -352,6 +346,12 @@ int main()
       }
 
       // calculate spectrum
+      lowE6SSM_spectrum_generator<algorithm_type> spectrum_generator;
+      spectrum_generator.set_precision_goal(1.0e-4);
+      spectrum_generator.set_max_iterations(0);         // 0 == automatic
+      spectrum_generator.set_calculate_sm_masses(0);    // 0 == no
+      spectrum_generator.set_parameter_output_scale(0); // 0 == susy scale
+
       spectrum_generator.run(oneset, input);
 
       const lowE6SSM<algorithm_type>& model = spectrum_generator.get_model();

### 2015-03-27 paper/e6ssm-tuning-paper.tex
Fixed type in one-loop beta for m_S^2, restored two-loop trace terms to two-loop betas for \lambda and y_t that are missing in the trilinears
Removed brackets from SU(2) dot products but left the dots, added expression for loop contributions to effective potential, changed reference to NMSSM tuning paper to indicate that it has been previously used

@@
 $U(1)^\prime$ gauge group should allow the following renormalisable
-superpotential terms required in the USSM, \be W_{USSM} = y^U_{ij}
-\hat{u}^c_i \left ( \hat{H}_u \cdot \hat{Q}_j \right ) + y^D_{ij} \hat{d}^c_i 
-\left ( \hat{Q}_j \cdot \hat{H}_d \right )
- + y^E_{ij} \hat{e}^c_i \left ( \hat{L}_j \cdot \hat{H}_d \right ) + \lambda \hat{S}
-\left ( \hat{H}_d \cdot \hat{H}_u \right ), \ee with $i,j \in \{1,2,3\}$. 
+superpotential terms required in the USSM, \begin{equation}
+ W_{USSM} = y^U_{ij}
+\hat{u}^c_i  \hat{H}_u \cdot \hat{Q}_j + y^D_{ij} \hat{d}^c_i  \hat{Q}_j \cdot \hat{H}_d
+ + y^E_{ij} \hat{e}^c_i \hat{L}_j \cdot \hat{H}_d  + \lambda \hat{S} \hat{H}_d \cdot \hat{H}_u, 
+\end{equation} with $i,j \in \{1,2,3\}$. 
 For the $SU(2)$ dot product we follow the convention $\hat{A}\cdot \hat{B}\equiv \epsilon_{\alpha\beta}\hat{A}^\alpha\hat{B}^\beta=\hat{A}^2\hat{B}^1-\hat{A}^1\hat{B}^2$.
@@
 symmetry at low energies should then be a linear combination of these
-in the $E_6$ inspired case, \be U(1)^\prime = \cos(\theta) U(1)_{\chi}
-+ \sin(\theta) U(1)_{\psi}. \ee In Table \ref{tab:E6charges} the
+in the $E_6$ inspired case, \be U(1)^\prime = U(1)_{\chi}\cos\theta 
++ U(1)_{\psi}\sin\theta . \ee In Table \ref{tab:E6charges} the
 charges for several popular $E_6$ inspired $U(1)$ extensions are
@@
 \begin{eqnarray}
-W_0 &=& \lambda_{ijk} \hat{S}_i \left ( \hat{H}^d_{j} \cdot\hat{H}^u_{k}\right ) + \kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\bar{D}}_k + h^N_{ijk} \hat{N}^c_i \left ( \hat{H}^u_{j} \cdot \hat{L}_k\right ) \nonumber \\
-& & + h^U_{ijk} \hat{u}^c_i \left ( \hat{H}^u_{j} \cdot \hat{Q}_k\right ) + h^D_{ijk} \hat{d}^c_i \left ( \hat{Q}_k\cdot\hat{H}^d_{j}\right )  + h^E_{ijk} \hat{e}^c_i \left ( \hat{L}_k\cdot\hat{H}^d_{j}\right ) , \\
-W_1 &=& g^Q_{ijk} \hat{D}_i \left ( \hat{Q}_j \cdot \hat{Q}_k \right )+ g^q_{ijk} \hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k, \\
-W_2 &=& g^N_{ijk} \hat{N}^c_i \hat{D}_j \hat{d}^c_k + g^E_{ijk} \hat{e}^c_i \hat{D}_j \hat{u}^c_k + g^D_{ijk} \left ( \hat{Q}_i \cdot \hat{L}_j \right )\hat{\bar{D}}_k.
+W_0 &=& \lambda_{ijk} \hat{S}_i  \hat{H}^d_{j} \cdot\hat{H}^u_{k} + \kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\bar{D}}_k + h^N_{ijk} \hat{N}^c_i  \hat{H}^u_{j} \cdot \hat{L}_k \nonumber \\
+& & + h^U_{ijk} \hat{u}^c_i  \hat{H}^u_{j} \cdot \hat{Q}_k + h^D_{ijk} \hat{d}^c_i  \hat{Q}_k\cdot\hat{H}^d_{j}  + h^E_{ijk} \hat{e}^c_i  \hat{L}_k\cdot\hat{H}^d_{j} , \\
+W_1 &=& g^Q_{ijk} \hat{D}_i  \hat{Q}_j \cdot \hat{Q}_k + g^q_{ijk} \hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k, \\
+W_2 &=& g^N_{ijk} \hat{N}^c_i \hat{D}_j \hat{d}^c_k + g^E_{ijk} \hat{e}^c_i \hat{D}_j \hat{u}^c_k + g^D_{ijk}  \hat{Q}_i \cdot \hat{L}_j \hat{\bar{D}}_k.
 \label{Eq:e6-superpot-parts}
@@
     \ba
-    W &\approx& y_{\tau} \left (\SuperField{L}_3 \cdot \SuperField{H}_d
-     \right ) \SuperField{e}^C_3 + y_b \left (\SuperField{Q}_3\cdot\SuperField{H}_d
-     \right ) \SuperField{d}_3^C + y_t \left (\SuperField{H}_u\cdot\SuperField{Q}_3
-     \right ) \SuperField{u}_3^C\\
+    W &\approx& y_{\tau} \SuperField{L}_3 \cdot \SuperField{H}_d
+      \SuperField{e}^C_3 + y_b \SuperField{Q}_3\cdot\SuperField{H}_d
+      \SuperField{d}_3^C + y_t \SuperField{H}_u\cdot\SuperField{Q}_3
+      \SuperField{u}_3^C\\
     &&
-    + \lambda_i \SuperField{S} \left (\SuperField{H}_{1i}
-    \cdot \SuperField{H}_{2i} \right ) + \kappa_i \SuperField{S} \SuperField{D}_i
-    \SuperField{\overline{D}}_i + \mu' \left (\SuperField{H}'\cdot
-    \SuperField{\overline{H'}}\right ),
+    + \lambda_i \SuperField{S} \SuperField{H}_{1i}
+    \cdot \SuperField{H}_{2i}  + \kappa_i \SuperField{S} \SuperField{D}_i
+    \SuperField{\overline{D}}_i + \mu' \SuperField{H}'\cdot
+    \SuperField{\overline{H'}},
     \ea
@@
 \begin{align}
-V_F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|(H_1\cdot
-H_2)|^2,\label{eq:E6VFterms}\\ V_D&=\frac{\bar{g}^2}{8}\left (
+V_F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|H_1\cdot
+H_2|^2,\label{eq:E6VFterms}\\ 
+V_D&=\frac{\bar{g}^2}{8}\left (
 |H_2|^2-|H_1|^2\right )^2+\frac{g_2^2}{2}|H_1^\dagger
-H_2|^2+\frac{g_1'^2}{2}(Q_1|H_1|^2+Q_2|H_2|^2+Q_S|S|^2)^2,\label{eq:E6VDterms}\\ V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big
-[\lambda A_\lambda S(H_1\cdot H_2)+\textrm{h.c.}\Big
+H_2|^2+\frac{g_1'^2}{2}(Q_1|H_1|^2+Q_2|H_2|^2+Q_S|S|^2)^2,\label{eq:E6VDterms}\\ 
+V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big
+[\lambda A_\lambda SH_1\cdot H_2+\textrm{h.c.}\Big
 ].\label{eq:E6Vsoft}
@@
 $Q_2$ and $Q_S$ are effective $U(1)'$ charges for
-$H_1$, $H_2$ and $S$, respectively. The term $\Delta V$ contains the
-Coleman-Weinberg contributions to the effective potential. In the case
+$H_1$, $H_2$ and $S$, respectively. In the case
 of the $U(1)_\chi$ model, $V_F$ may also contain an elementary
-$\mu$ term, as occurs in the MSSM.\\ \\ Demanding that
-the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real VEVs of
-the form
+$\mu$ term, as occurs in the MSSM. The term $\Delta V$ contains the
+Coleman-Weinberg contributions to the effective potential. For the purposes of this study, 
+we include in $\Delta V$ only the one-loop contributions from the top quark and stop squarks,
+\begin{equation}
+\Delta V=\frac{3}{32\pi^2}\left [ m_{\tilde{t}_1}^4\left ( \log\frac{m_{\tilde{t}_1}^2}{Q^2}-\frac{3}{2}\right )+m_{\tilde{t}_2}^4\left ( \log\frac{m_{\tilde{t}_2}^2}{Q^2}-\frac{3}{2}\right )-2m_t^4\left ( \log\frac{m_t^2}{Q^2}-\frac{3}{2}\right )\right ].
+\end{equation}
+Explicit expressions for the running $\overline{\textrm{DR}}$ top mass $m_t$ and stop masses $m_{\tilde{t}_{1,2}}$ are given 
+below.\\ \\
+Demanding that the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real VEVs of the form
 \begin{equation}\label{eq:E6vevs}
@@
 &f_1=m_{H_d}^2v_1+\frac{\lambda^2}{2}(v_2^2+s^2)v_1-\frac{\lambda A_\lambda}{\sqrt{2}}sv_2-\frac{\bar{g}^2}{8}
-(v_2^2-v_1^2)v_1+D_{H_1}v_1+\frac{\partial \Delta V_{E_6}}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\
+(v_2^2-v_1^2)v_1+D_{H_1}v_1+\frac{\partial \Delta V}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\
 &f_2=m_{H_u}^2v_2+\frac{\lambda^2}{2}(v_1^2+s^2)v_2-\frac{\lambda A_\lambda}{\sqrt{2}}sv_1+\frac{\bar{g}^2}{8}
-(v_2^2-v_1^2)v_2+D_{H_2}v_2+\frac{\partial \Delta V_{E_6}}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\
-&f_3=m_S^2s+\frac{\lambda^2}{2}(v_2^2+v_1^2)s-\frac{\lambda A_\lambda}{\sqrt{2}}v_2v_1+D_Ss+\frac{\partial \Delta V_{E_6}}{\partial s}=0.\label{eq:E6EWSBcondition3}
+(v_2^2-v_1^2)v_2+D_{H_2}v_2+\frac{\partial \Delta V}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\
+&f_3=m_S^2s+\frac{\lambda^2}{2}(v_2^2+v_1^2)s-\frac{\lambda A_\lambda}{\sqrt{2}}v_2v_1+D_Ss+\frac{\partial \Delta V}{\partial s}=0.\label{eq:E6EWSBcondition3}
 \end{align}
@@
 \begin{equation}\label{eq:E6Dterms}
-D_\phi\equiv \frac{g_1'^2}{2}\left (
-Q_1v_1^2+Q_2v_2^2+Q_Ss^2\right
-)Q_\phi.
+D_\phi\equiv \frac{g_1'^2}{2}\left (Q_1v_1^2+Q_2v_2^2+Q_Ss^2\right )Q_\phi.
 \end{equation}
-As was noted in \cite{Athron:2013ipa}, the first two of these
-conditions may be rewritten in the form
+We also include these $U(1)'$ $D$-term contributions in the diagonalised stop masses,
+\begin{align}
+  m_{\tilde{t}_{1,2}}^2&=\frac{1}{2}\bigg \{ m_{Q3}^2+m_{u3}^2+\frac{1}{2}M_Z^2\cos 2\beta+D_Q+D_u+2m_t^2\nonumber\\
+&\quad{}\mp\sqrt{\left [ m_{Q3}^2+m_{u3}^2+\left ( \frac{1}{2}-\frac{4}{3}\sin^2\theta_W\right )M_Z^2\cos 2\beta + D_Q-D_u\right ]^2+4m_t^2X_t^2}\bigg \},
+\end{align}
+where $m_t^2=y_t^2v_2^2/2$ and $X_t=A_t-\frac{\lambda s v_1}{\sqrt{2}v_2}$. By definition we take $m_{\tilde{t}_1}$ to correspond to the lighter of the two states.\\ \\
+As was noted in \cite{Athron:2013ipa}, the first two of these conditions may be rewritten in the form
 \begin{equation}\label{eq:E6MZequation}
@@
 Eq. (\ref{eq:E6EWSBConditions}), rather than
-Eq. (\ref{eq:E6MZequation}). The general procedure is as follows
-\cite{Ellwanger:2011mu}. For a model in which $m$ fields develop real
+Eq. (\ref{eq:E6MZequation}). The general procedure that we use is as follows
+(this method has also previously been applied in the NMSSM, see for example \cite{Ellwanger:2011mu}). For a model in which $m$ fields develop real
 VEVs (e.g. $m=2$ in the MSSM, $m=3$ in the NMSSM and in the $E_6$
@@
 &{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2Q_1^4+2Q_2^4+2Q_S^4+\left ( Q_1^2+Q_2^2+Q_S^2\right )\Sigma_{Q}\right ]\nonumber\\
-&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left (Q_1^2+Q_2^2\right )\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\
+&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [Q_1^2+Q_2^2+\left ( Q_2 - Q_1 \right )\Sigma_Q^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\
 b_\lambda^{(2)}&=\lambda \bigg \{ 2\lambda^2\left ( 3\lambda^2 +4\Sigma_\lambda +6\Sigma_\kappa \right )+4\Pi_\lambda + 6\Pi_\kappa +6\left ( \Sigma_\lambda+\frac{3}{2}\Sigma_\kappa\right )^2+7\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\nonumber\\
@@
 \begin{align}
-\beta_{m_S^2}^{(1)}&=\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2+6\kappa_i\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+6a_{\kappa_i}^2\right ]\nonumber\\
+\beta_{m_S^2}^{(1)}&=\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2+6\kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+6a_{\kappa_i}^2\right ]\nonumber\\
 &{}-8Q_S^2g_1'^2M_1'^2+2Q_Sg_1'^2\Sigma_1',\label{eq:USSMms2BetaOneLoop}\\
@@
 &{}+\frac{32}{3}g_3^2g_1'^2\left ( Q_Q^2+Q_u^2\right )+g_2^2g_1^2+6g_2^2g_1'^2\left ( Q_2^2+Q_Q^2\right )\nonumber\\
-&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\
+&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2+\left ( 3Q_2+Q_Q-4Q_u\right )\Sigma_Q^Y\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\
 b_{y_t}^{(2)}&=y_t\bigg \{ 54y_t^4+\frac{13}{2}y_b^4+13y_t^2y_b^2+y_b^2y_\tau^2+\lambda^2\left ( \frac{5}{2}\lambda^2+15y_t^2+5y_b^2+y_\tau^2+2\Sigma_\lambda+3\Sigma_\kappa \right )\nonumber\\

### 2015-03-27 paper/e6ssm-tuning-paper.tex
Added comment explaining that derivatives come straight from EWSB conditions (rather than including trivial extra equations), changed newlines \ \ to \

@@
 Explicit expressions for the running $\overline{\textrm{DR}}$ top mass $m_t$ and stop masses $m_{\tilde{t}_{1,2}}$ are given 
-below.\\ \\
+below.\\
 Demanding that the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real VEVs of the form
@@
 \end{align}
-where $m_t^2=y_t^2v_2^2/2$ and $X_t=A_t-\frac{\lambda s v_1}{\sqrt{2}v_2}$. By definition we take $m_{\tilde{t}_1}$ to correspond to the lighter of the two states.\\ \\
+where $m_t^2=y_t^2v_2^2/2$ and $X_t=A_t-\frac{\lambda s v_1}{\sqrt{2}v_2}$. By definition we take $m_{\tilde{t}_1}$ to correspond to the lighter of the two states.\\
 As was noted in \cite{Athron:2013ipa}, the first two of these conditions may be rewritten in the form
@@
 \end{align*}
-Written in the form of Eq. (\ref{eq:E6MZequation}) we see the
+Written in the form of Eq.~(\ref{eq:E6MZequation}) we see the
 potential new source of fine tuning alluded to above, in the form of
@@
 models with $Q_S\neq 0$. As a result the remaining terms on the
-right-hand side of Eq. (\ref{eq:E6MZequation}) must be tuned to cancel
+right-hand side of Eq.~(\ref{eq:E6MZequation}) must be tuned to cancel
 the resulting very large contribution to $M_Z$. Moreover, because this
@@
 importance of the $Z^\prime$ mass to the fine tuning in these models
-can be made even clearer by writing Eq. (\ref{eq:E6MZequation}) in the
+can be made even clearer by writing Eq.~(\ref{eq:E6MZequation}) in the
 form given in \cite{Athron:2013ipa},
@@
 coefficient $d$.
-%% \section{\label{sec:tuning}Fine Tuning}
-% Introduce tuning measure - BG measure (maybe Peter will add in a justification
-% here).
-% Explain that we derived the master formula in the E6SSM as given in Maien's 
-% paper, but including extra effects not in that formula. 
-% Full result is given in appendix.
-% Numerical technique for calculating 1-loop tunings and including RG effects
-% Outline is given here, full equations for RGE effects etc. given in appendix.
-% How we calculate the tuning using spectrum generator, for E6SSM uses
-% FlexibleSUSY (cite FlexibleSUSY and SARAH).
 \section{\label{sec:tuningmeasure}The Fine Tuning Measure}
@@
 of $U(1)$ mixing are neglected in deriving
-Eq. (\ref{eq:E6masterformula}).\\ \\ However, it is well known in the
+Eq.~(\ref{eq:E6masterformula}).\\
+However, it is well known in the
 MSSM that radiative corrections can significantly change (indeed,
@@
 most convenient to work in terms of the EWSB conditions
-Eq. (\ref{eq:E6EWSBConditions}), rather than
-Eq. (\ref{eq:E6MZequation}). The general procedure that we use is as follows
+Eq.~(\ref{eq:E6EWSBConditions}), rather than
+Eq.~(\ref{eq:E6MZequation}). The general procedure that we use is as follows
 (this method has also previously been applied in the NMSSM, see for example \cite{Ellwanger:2011mu}). For a model in which $m$ fields develop real
@@
 The quantities forming the first matrix on the right-hand side, along
-with $M_h^2$, are easily calculated analytically. The remaining
-derivatives $\partial q_k /\partial p$ must be determined using the
+with $M_h^2$, are easily calculated by differentiating the conditions in Eq.~(\ref{eq:E6EWSBConditions})
+with respect to the VEVs and the running parameters. 
+The remaining derivatives $\partial q_k /\partial p$ must be determined using the
 RGEs. Once these have been obtained, it is straightforward to solve
@@
 $\Delta_p$ are then simply linear combinations of the $\partial
-v_i/\partial p$ and $\partial q_k/\partial p$. Radiative corrections
-may be easily incorporated by including the Coleman-Weinberg potential
-contributions in the EWSB conditions.\\ \\ Evaluating the derivatives
+v_i/\partial p$ and $\partial q_k/\partial p$. The effects of radiative corrections
+may be easily included by including the Coleman-Weinberg potential
+contributions $\Delta V$ in the EWSB conditions.\\
+Evaluating the derivatives
 $\partial q_k/\partial p$ must (in general) be done by numerically
@@
 the $Z^\prime$ mass in the EWSB condition.  These charges change the
-value of the coefficient $d$ in Eq. (\ref{eq:originalE6MZequation}).
+value of the coefficient $d$ in Eq.~(\ref{eq:originalE6MZequation}).
 The values of the coefficient $d$ in each model, for $\tan\beta = 10$,
@@
 \end{equation}
-with $f_1,f_2,f_3$ as given in Eq. (\ref{eq:E6EWSBConditions}). The relevant partial derivatives are
+with $f_1,f_2,f_3$ as given in Eq.~(\ref{eq:E6EWSBConditions}). The relevant partial derivatives are
 \ba
@@
 It is straightforward to compute the appropriate derivatives directly from the EWSB conditions (\ref{eq:E6EWSBConditions}).
-Similarly, the quantity $C$ appearing in Eq.
-(\ref{eq:E6masterformula}) is given by
+Similarly, the quantity $C$ appearing in Eq.~(\ref{eq:E6masterformula}) is given by
 \be
@@
 solutions to the RG equations for a model can be reasonably well
-approximated by a Taylor series, Eq. (\ref{eq:rgeapproxsoln}).  For a
+approximated by a Taylor series, Eq.~(\ref{eq:rgeapproxsoln}).  For a
 parameter $p$, this reads
@@
 likewise omitted. Additionally, all soft mass matrices are assumed
-diagonal, and the gaugino masses are taken to be real.\\ \\ In the
+diagonal, and the gaugino masses are taken to be real.\\
+In the
 MSSM, the relevant parameters for the fine tuning calculation are

### 2015-03-27 paper/e6ssm-tuning-paper.tex
Added comment explaining that the heavy Z' data is plotted on top of the MSSM and light Z' points

@@
 
-%   Since the stop mass does not have a large impact on the fine tuning
-%   when the cutoff scale is very low we can use this to see more clearly
-%   the impact of the $Z^\prime$ mass on fine tuning. To do se we choose a
-%   cutoff of  look at the fine tuning for two different
-%   values of the $Z^\prime$ mass, $2.5$ TeV, which is just above the
-%   current limits and $4.5$ TeV which could be in reach of the LHC run
-%   II, and compare these to the MSSM.
-
-%   For this we also fix [what we fix + explain different choices to
-%   before and their impact].
 \begin{figure}[h]
@@
   MSSM (green, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue, middle band) and
-  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band).}
+  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band). Note that there are points for which
+the fine tuning in the MSSM and E$_6$SSM with $M_{Z'}=2.5$ TeV is larger than is visible on this plot
+and those below;
+however these points are obscured by the overlaid data for the E$_6$SSM with $M_{Z'}=4.5$ TeV, and it is the 
+lower bound on the achievable tuning that is of interest here.}
 \label{Fig:e6ssmvsmssm}
@@
 to denote the trace over the $U(1)'$ charges, along
-with \footnote{This is the trace which is assumed to vanish in
+with \footnote{The first of these is the trace which is assumed to vanish in
   \cite{Martin:1993zk}.  Although we use the NoU1Mixing to neglect

### 2015-03-27 paper/e6ssm-tuning-paper.tex
Added comment explaining smaller scans were used to fill in the general U(1)' model plots

@@
 \caption{The parameters scanned over and the ranges of values used in
-  the MSSM and the $E_6SSM$ models.}
+  the MSSM and the E$_6SSM$ models.}
 \label{tab:scanranges}
@@
 the rest to the same values we did in the scan carried out for
-Fig.~\ref{Fig:e6ssmvsmssm}.
+Fig.~\ref{Fig:e6ssmvsmssm}. In order to more clearly identify the lower bound
+on the obtainable tuning in each model, the parameter values for points in
+these main grid scans with a low fine tuning were then used as the starting points for
+smaller scans about those values. In these smaller scans the parameters were more finely
+varied to populate the low fine tuning regions.
 

### 2015-03-27 paper/e6ssm-tuning-paper.tex
Added updated U(1)_I plot, added missing second half of sentence in acknowledgements

@@
 
-\acknowledgements We would like to thank R. Nevzorov for many useful
-discussions and comments and Florian Staub for very helpful responses
+\acknowledgements We would like to thank R.~Nevzorov for many useful
+discussions and comments and F.~Staub for very helpful responses
 regarding the gauge kinetic mixing contributions in SARAH. DH would
-also like to thank A. Ismail and T. Rizzo. PA would like to thank
-J.H.~Park, A.~Voigt and D.~Stockinger for useful discussion regarding
-the use of FlexibleSUSY in this project. This work was supported by
-the University of Adelaide and by the ARC Centre of Excellence for
-Particle Physics at the Terascale.
+also like to thank A.~Ismail and T.~Rizzo for their helpful comments
+regarding fine tuning in the MSSM. 
+PA would like to thank J.H.~Park, A.~Voigt and D.~Stockinger for 
+useful discussion regarding the use of FlexibleSUSY in this project. 
+This work was supported by the University of Adelaide and by the ARC 
+Centre of Excellence for Particle Physics at the Terascale.
 

### 2015-03-27 paper/e6ssm-tuning-paper.tex
small rephrasing for clarity.

--- 2015-03-27 paper/e6ssm-tuning-paper.tex
@@
 $U(1)^\prime$ gauge group should allow the following renormalisable
-superpotential terms required in the USSM, \begin{equation}
- W_{USSM} = y^U_{ij}
-\hat{u}^c_i  \hat{H}_u \cdot \hat{Q}_j + y^D_{ij} \hat{d}^c_i  \hat{Q}_j \cdot \hat{H}_d
- + y^E_{ij} \hat{e}^c_i \hat{L}_j \cdot \hat{H}_d  + \lambda \hat{S} \hat{H}_d \cdot \hat{H}_u, 
-\end{equation} with $i,j \in \{1,2,3\}$. 
+superpotential terms required in the USSM, \be W_{USSM} = y^U_{ij}
+\hat{u}^c_i \left ( \hat{H}_u \cdot \hat{Q}_j \right ) + y^D_{ij} \hat{d}^c_i 
+\left ( \hat{Q}_j \cdot \hat{H}_d \right )
+ + y^E_{ij} \hat{e}^c_i \left ( \hat{L}_j \cdot \hat{H}_d \right ) + \lambda \hat{S}
+\left ( \hat{H}_d \cdot \hat{H}_u \right ), \ee with $i,j \in \{1,2,3\}$. 
 For the $SU(2)$ dot product we follow the convention $\hat{A}\cdot \hat{B}\equiv \epsilon_{\alpha\beta}\hat{A}^\alpha\hat{B}^\beta=\hat{A}^2\hat{B}^1-\hat{A}^1\hat{B}^2$.
@@
 symmetry at low energies should then be a linear combination of these
-in the $E_6$ inspired case, \be U(1)^\prime = U(1)_{\chi}\cos\theta 
-+ U(1)_{\psi}\sin\theta . \ee In Table \ref{tab:E6charges} the
+in the $E_6$ inspired case, \be U(1)^\prime = \cos(\theta) U(1)_{\chi}
++ \sin(\theta) U(1)_{\psi}. \ee In Table \ref{tab:E6charges} the
 charges for several popular $E_6$ inspired $U(1)$ extensions are
@@
 \begin{eqnarray}
-W_0 &=& \lambda_{ijk} \hat{S}_i  \hat{H}^d_{j} \cdot\hat{H}^u_{k} + \kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\bar{D}}_k + h^N_{ijk} \hat{N}^c_i  \hat{H}^u_{j} \cdot \hat{L}_k \nonumber \\
-& & + h^U_{ijk} \hat{u}^c_i  \hat{H}^u_{j} \cdot \hat{Q}_k + h^D_{ijk} \hat{d}^c_i  \hat{Q}_k\cdot\hat{H}^d_{j}  + h^E_{ijk} \hat{e}^c_i  \hat{L}_k\cdot\hat{H}^d_{j} , \\
-W_1 &=& g^Q_{ijk} \hat{D}_i  \hat{Q}_j \cdot \hat{Q}_k + g^q_{ijk} \hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k, \\
-W_2 &=& g^N_{ijk} \hat{N}^c_i \hat{D}_j \hat{d}^c_k + g^E_{ijk} \hat{e}^c_i \hat{D}_j \hat{u}^c_k + g^D_{ijk}  \hat{Q}_i \cdot \hat{L}_j \hat{\bar{D}}_k.
+W_0 &=& \lambda_{ijk} \hat{S}_i \left ( \hat{H}^d_{j} \cdot\hat{H}^u_{k}\right ) + \kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\bar{D}}_k + h^N_{ijk} \hat{N}^c_i \left ( \hat{H}^u_{j} \cdot \hat{L}_k\right ) \nonumber \\
+& & + h^U_{ijk} \hat{u}^c_i \left ( \hat{H}^u_{j} \cdot \hat{Q}_k\right ) + h^D_{ijk} \hat{d}^c_i \left ( \hat{Q}_k\cdot\hat{H}^d_{j}\right )  + h^E_{ijk} \hat{e}^c_i \left ( \hat{L}_k\cdot\hat{H}^d_{j}\right ) , \\
+W_1 &=& g^Q_{ijk} \hat{D}_i \left ( \hat{Q}_j \cdot \hat{Q}_k \right )+ g^q_{ijk} \hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k, \\
+W_2 &=& g^N_{ijk} \hat{N}^c_i \hat{D}_j \hat{d}^c_k + g^E_{ijk} \hat{e}^c_i \hat{D}_j \hat{u}^c_k + g^D_{ijk} \left ( \hat{Q}_i \cdot \hat{L}_j \right )\hat{\bar{D}}_k.
 \label{Eq:e6-superpot-parts}
@@
     \ba
-    W &\approx& y_{\tau} \SuperField{L}_3 \cdot \SuperField{H}_d
-      \SuperField{e}^C_3 + y_b \SuperField{Q}_3\cdot\SuperField{H}_d
-      \SuperField{d}_3^C + y_t \SuperField{H}_u\cdot\SuperField{Q}_3
-      \SuperField{u}_3^C\\
+    W &\approx& y_{\tau} \left (\SuperField{L}_3 \cdot \SuperField{H}_d
+     \right ) \SuperField{e}^C_3 + y_b \left (\SuperField{Q}_3\cdot\SuperField{H}_d
+     \right ) \SuperField{d}_3^C + y_t \left (\SuperField{H}_u\cdot\SuperField{Q}_3
+     \right ) \SuperField{u}_3^C\\
     &&
-    + \lambda_i \SuperField{S} \SuperField{H}_{1i}
-    \cdot \SuperField{H}_{2i}  + \kappa_i \SuperField{S} \SuperField{D}_i
-    \SuperField{\overline{D}}_i + \mu' \SuperField{H}'\cdot
-    \SuperField{\overline{H'}},
+    + \lambda_i \SuperField{S} \left (\SuperField{H}_{1i}
+    \cdot \SuperField{H}_{2i} \right ) + \kappa_i \SuperField{S} \SuperField{D}_i
+    \SuperField{\overline{D}}_i + \mu' \left (\SuperField{H}'\cdot
+    \SuperField{\overline{H'}}\right ),
     \ea
@@
 \begin{align}
-V_F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|H_1\cdot
-H_2|^2,\label{eq:E6VFterms}\\ 
-V_D&=\frac{\bar{g}^2}{8}\left (
+V_F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|(H_1\cdot
+H_2)|^2,\label{eq:E6VFterms}\\ V_D&=\frac{\bar{g}^2}{8}\left (
 |H_2|^2-|H_1|^2\right )^2+\frac{g_2^2}{2}|H_1^\dagger
-H_2|^2+\frac{g_1'^2}{2}(Q_1|H_1|^2+Q_2|H_2|^2+Q_S|S|^2)^2,\label{eq:E6VDterms}\\ 
-V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big
-[\lambda A_\lambda SH_1\cdot H_2+\textrm{h.c.}\Big
+H_2|^2+\frac{g_1'^2}{2}(Q_1|H_1|^2+Q_2|H_2|^2+Q_S|S|^2)^2,\label{eq:E6VDterms}\\ V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big
+[\lambda A_\lambda S(H_1\cdot H_2)+\textrm{h.c.}\Big
 ].\label{eq:E6Vsoft}
@@
 $Q_2$ and $Q_S$ are effective $U(1)'$ charges for
-$H_1$, $H_2$ and $S$, respectively. In the case
+$H_1$, $H_2$ and $S$, respectively. The term $\Delta V$ contains the
+Coleman-Weinberg contributions to the effective potential. In the case
 of the $U(1)_\chi$ model, $V_F$ may also contain an elementary
-$\mu$ term, as occurs in the MSSM. The term $\Delta V$ contains the
-Coleman-Weinberg contributions to the effective potential. For the purposes of this study, 
-we include in $\Delta V$ only the one-loop contributions from the top quark and stop squarks,
-\begin{equation}
-\Delta V=\frac{3}{32\pi^2}\left [ m_{\tilde{t}_1}^4\left ( \log\frac{m_{\tilde{t}_1}^2}{Q^2}-\frac{3}{2}\right )+m_{\tilde{t}_2}^4\left ( \log\frac{m_{\tilde{t}_2}^2}{Q^2}-\frac{3}{2}\right )-2m_t^4\left ( \log\frac{m_t^2}{Q^2}-\frac{3}{2}\right )\right ].
-\end{equation}
-Explicit expressions for the running $\overline{\textrm{DR}}$ top mass $m_t$ and stop masses $m_{\tilde{t}_{1,2}}$ are given 
-below.\\
-Demanding that the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real VEVs of the form
+$\mu$ term, as occurs in the MSSM.\\ \\ Demanding that
+the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real VEVs of
+the form
 \begin{equation}\label{eq:E6vevs}
@@
 &f_1=m_{H_d}^2v_1+\frac{\lambda^2}{2}(v_2^2+s^2)v_1-\frac{\lambda A_\lambda}{\sqrt{2}}sv_2-\frac{\bar{g}^2}{8}
-(v_2^2-v_1^2)v_1+D_{H_1}v_1+\frac{\partial \Delta V}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\
+(v_2^2-v_1^2)v_1+D_{H_1}v_1+\frac{\partial \Delta V_{E_6}}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\
 &f_2=m_{H_u}^2v_2+\frac{\lambda^2}{2}(v_1^2+s^2)v_2-\frac{\lambda A_\lambda}{\sqrt{2}}sv_1+\frac{\bar{g}^2}{8}
-(v_2^2-v_1^2)v_2+D_{H_2}v_2+\frac{\partial \Delta V}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\
-&f_3=m_S^2s+\frac{\lambda^2}{2}(v_2^2+v_1^2)s-\frac{\lambda A_\lambda}{\sqrt{2}}v_2v_1+D_Ss+\frac{\partial \Delta V}{\partial s}=0.\label{eq:E6EWSBcondition3}
+(v_2^2-v_1^2)v_2+D_{H_2}v_2+\frac{\partial \Delta V_{E_6}}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\
+&f_3=m_S^2s+\frac{\lambda^2}{2}(v_2^2+v_1^2)s-\frac{\lambda A_\lambda}{\sqrt{2}}v_2v_1+D_Ss+\frac{\partial \Delta V_{E_6}}{\partial s}=0.\label{eq:E6EWSBcondition3}
 \end{align}
@@
 \begin{equation}\label{eq:E6Dterms}
-D_\phi\equiv \frac{g_1'^2}{2}\left (Q_1v_1^2+Q_2v_2^2+Q_Ss^2\right )Q_\phi.
+D_\phi\equiv \frac{g_1'^2}{2}\left (
+Q_1v_1^2+Q_2v_2^2+Q_Ss^2\right
+)Q_\phi.
 \end{equation}
-We also include these $U(1)'$ $D$-term contributions in the diagonalised stop masses,
-\begin{align}
-  m_{\tilde{t}_{1,2}}^2&=\frac{1}{2}\bigg \{ m_{Q3}^2+m_{u3}^2+\frac{1}{2}M_Z^2\cos 2\beta+D_Q+D_u+2m_t^2\nonumber\\
-&\quad{}\mp\sqrt{\left [ m_{Q3}^2+m_{u3}^2+\left ( \frac{1}{2}-\frac{4}{3}\sin^2\theta_W\right )M_Z^2\cos 2\beta + D_Q-D_u\right ]^2+4m_t^2X_t^2}\bigg \},
-\end{align}
-where $m_t^2=y_t^2v_2^2/2$ and $X_t=A_t-\frac{\lambda s v_1}{\sqrt{2}v_2}$. By definition we take $m_{\tilde{t}_1}$ to correspond to the lighter of the two states.\\
-As was noted in \cite{Athron:2013ipa}, the first two of these conditions may be rewritten in the form
+As was noted in \cite{Athron:2013ipa}, the first two of these
+conditions may be rewritten in the form
 \begin{equation}\label{eq:E6MZequation}
@@
 \end{align*}
-Written in the form of Eq.~(\ref{eq:E6MZequation}) we see the
+Written in the form of Eq. (\ref{eq:E6MZequation}) we see the
 potential new source of fine tuning alluded to above, in the form of
@@
 models with $Q_S\neq 0$. As a result the remaining terms on the
-right-hand side of Eq.~(\ref{eq:E6MZequation}) must be tuned to cancel
+right-hand side of Eq. (\ref{eq:E6MZequation}) must be tuned to cancel
 the resulting very large contribution to $M_Z$. Moreover, because this
@@
 importance of the $Z^\prime$ mass to the fine tuning in these models
-can be made even clearer by writing Eq.~(\ref{eq:E6MZequation}) in the
+can be made even clearer by writing Eq. (\ref{eq:E6MZequation}) in the
 form given in \cite{Athron:2013ipa},
@@
 coefficient $d$.
+%% \section{\label{sec:tuning}Fine Tuning}
+% Introduce tuning measure - BG measure (maybe Peter will add in a justification
+% here).
+% Explain that we derived the master formula in the E6SSM as given in Maien's 
+% paper, but including extra effects not in that formula. 
+% Full result is given in appendix.
+% Numerical technique for calculating 1-loop tunings and including RG effects
+% Outline is given here, full equations for RGE effects etc. given in appendix.
+% How we calculate the tuning using spectrum generator, for E6SSM uses
+% FlexibleSUSY (cite FlexibleSUSY and SARAH).
 \section{\label{sec:tuningmeasure}The Fine Tuning Measure}
@@
 of $U(1)$ mixing are neglected in deriving
-Eq.~(\ref{eq:E6masterformula}).\\
-However, it is well known in the
+Eq. (\ref{eq:E6masterformula}).\\ \\ However, it is well known in the
 MSSM that radiative corrections can significantly change (indeed,
@@
 most convenient to work in terms of the EWSB conditions
-Eq.~(\ref{eq:E6EWSBConditions}), rather than
-Eq.~(\ref{eq:E6MZequation}). The general procedure that we use is as follows
-(this method has also previously been applied in the NMSSM, see for example \cite{Ellwanger:2011mu}). For a model in which $m$ fields develop real
+Eq. (\ref{eq:E6EWSBConditions}), rather than
+Eq. (\ref{eq:E6MZequation}). The general procedure is as follows
+\cite{Ellwanger:2011mu}. For a model in which $m$ fields develop real
 VEVs (e.g. $m=2$ in the MSSM, $m=3$ in the NMSSM and in the $E_6$
@@
 The quantities forming the first matrix on the right-hand side, along
-with $M_h^2$, are easily calculated by differentiating the conditions in Eq.~(\ref{eq:E6EWSBConditions})
-with respect to the VEVs and the running parameters. 
-The remaining derivatives $\partial q_k /\partial p$ must be determined using the
+with $M_h^2$, are easily calculated analytically. The remaining
+derivatives $\partial q_k /\partial p$ must be determined using the
 RGEs. Once these have been obtained, it is straightforward to solve
@@
 $\Delta_p$ are then simply linear combinations of the $\partial
-v_i/\partial p$ and $\partial q_k/\partial p$. The effects of radiative corrections
-may be easily included by including the Coleman-Weinberg potential
-contributions $\Delta V$ in the EWSB conditions.\\
-Evaluating the derivatives
+v_i/\partial p$ and $\partial q_k/\partial p$. Radiative corrections
+may be easily incorporated by including the Coleman-Weinberg potential
+contributions in the EWSB conditions.\\ \\ Evaluating the derivatives
 $\partial q_k/\partial p$ must (in general) be done by numerically
@@
 
+%   Since the stop mass does not have a large impact on the fine tuning
+%   when the cutoff scale is very low we can use this to see more clearly
+%   the impact of the $Z^\prime$ mass on fine tuning. To do se we choose a
+%   cutoff of  look at the fine tuning for two different
+%   values of the $Z^\prime$ mass, $2.5$ TeV, which is just above the
+%   current limits and $4.5$ TeV which could be in reach of the LHC run
+%   II, and compare these to the MSSM.
+
+%   For this we also fix [what we fix + explain different choices to
+%   before and their impact].
 \begin{figure}[h]
@@
   MSSM (green, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue, middle band) and
-  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band). Note that there are points for which
-the fine tuning in the MSSM and E$_6$SSM with $M_{Z'}=2.5$ TeV is larger than is visible on this plot
-and those below;
-however these points are obscured by the overlaid data for the E$_6$SSM with $M_{Z'}=4.5$ TeV, and it is the 
-lower bound on the achievable tuning that is of interest here.}
+  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band).}
 \label{Fig:e6ssmvsmssm}
@@
 the $Z^\prime$ mass in the EWSB condition.  These charges change the
-value of the coefficient $d$ in Eq.~(\ref{eq:originalE6MZequation}).
+value of the coefficient $d$ in Eq. (\ref{eq:originalE6MZequation}).
 The values of the coefficient $d$ in each model, for $\tan\beta = 10$,
@@
 \end{equation}
-with $f_1,f_2,f_3$ as given in Eq.~(\ref{eq:E6EWSBConditions}). The relevant partial derivatives are
+with $f_1,f_2,f_3$ as given in Eq. (\ref{eq:E6EWSBConditions}). The relevant partial derivatives are
 \ba
@@
 It is straightforward to compute the appropriate derivatives directly from the EWSB conditions (\ref{eq:E6EWSBConditions}).
-Similarly, the quantity $C$ appearing in Eq.~(\ref{eq:E6masterformula}) is given by
+Similarly, the quantity $C$ appearing in Eq.
+(\ref{eq:E6masterformula}) is given by
 \be
@@
 solutions to the RG equations for a model can be reasonably well
-approximated by a Taylor series, Eq.~(\ref{eq:rgeapproxsoln}).  For a
+approximated by a Taylor series, Eq. (\ref{eq:rgeapproxsoln}).  For a
 parameter $p$, this reads
@@
 likewise omitted. Additionally, all soft mass matrices are assumed
-diagonal, and the gaugino masses are taken to be real.\\
-In the
+diagonal, and the gaugino masses are taken to be real.\\ \\ In the
 MSSM, the relevant parameters for the fine tuning calculation are
@@
 to denote the trace over the $U(1)'$ charges, along
-with \footnote{The first of these is the trace which is assumed to vanish in
+with \footnote{This is the trace which is assumed to vanish in
   \cite{Martin:1993zk}.  Although we use the NoU1Mixing to neglect
-  gauge kinetic mixing this is done in SARAH by removing the RGE for
+  gauge kinetic mixing, SARAH does this by removing the RGE for
   the off diagonal gauge couplings and effectively setting them to
@@
 &{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2Q_1^4+2Q_2^4+2Q_S^4+\left ( Q_1^2+Q_2^2+Q_S^2\right )\Sigma_{Q}\right ]\nonumber\\
-&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [Q_1^2+Q_2^2+\left ( Q_2 - Q_1 \right )\Sigma_Q^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\
+&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left (Q_1^2+Q_2^2\right )\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\
 b_\lambda^{(2)}&=\lambda \bigg \{ 2\lambda^2\left ( 3\lambda^2 +4\Sigma_\lambda +6\Sigma_\kappa \right )+4\Pi_\lambda + 6\Pi_\kappa +6\left ( \Sigma_\lambda+\frac{3}{2}\Sigma_\kappa\right )^2+7\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\nonumber\\
@@
 \begin{align}
-\beta_{m_S^2}^{(1)}&=\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2+6\kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+6a_{\kappa_i}^2\right ]\nonumber\\
+\beta_{m_S^2}^{(1)}&=\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2+6\kappa_i\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+6a_{\kappa_i}^2\right ]\nonumber\\
 &{}-8Q_S^2g_1'^2M_1'^2+2Q_Sg_1'^2\Sigma_1',\label{eq:USSMms2BetaOneLoop}\\
@@
 &{}+\frac{32}{3}g_3^2g_1'^2\left ( Q_Q^2+Q_u^2\right )+g_2^2g_1^2+6g_2^2g_1'^2\left ( Q_2^2+Q_Q^2\right )\nonumber\\
-&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2+\left ( 3Q_2+Q_Q-4Q_u\right )\Sigma_Q^Y\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\
+&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\
 b_{y_t}^{(2)}&=y_t\bigg \{ 54y_t^4+\frac{13}{2}y_b^4+13y_t^2y_b^2+y_b^2y_\tau^2+\lambda^2\left ( \frac{5}{2}\lambda^2+15y_t^2+5y_b^2+y_\tau^2+2\Sigma_\lambda+3\Sigma_\kappa \right )\nonumber\\

### 2015-03-29 paper/e6ssm-tuning-paper.tex
U(1) --> (1)$

--- 2015-03-27 paper/e6ssm-tuning-paper.tex
@@
 Nonetheless this fine tuning depends crucially on our assumptions about 
-the supersymmetry breaking scale.  At the same time U(1) extensions
+the supersymmetry breaking scale.  At the same time $U(1)$ extensions
 provide the most compelling solution to the $\mu$-problem, which is also 
@@
 
-U(1) extensions of the MSSM provide a very elegant solution to this
+$U(1)$ extensions of the MSSM provide a very elegant solution to this
 $\mu$-problem \cite{Fayet:1977yc, Kim:1983dt, Suematsu:1994qm,
@@
 suffer from naturalness problems with the mass of the new $Z^\prime$
-associated with break down of the new U(1) appearing in the
+associated with break down of the new $U(1)$ appearing in the
 electroweak symmetry breaking conditions at tree level
@@
 
-At the same time in U(1) extensions, lowering the UV boundary scale
+At the same time in $U(1)$ extensions, lowering the UV boundary scale
 for the RGE evolution also allows even larger $F$-term contributions
@@
 
-\section{\label{sec:model}U(1) extensions and the E$_6$SSM}
-In this paper we consider U(1) extensions of the MSSM where the gauge
+\section{\label{sec:model}$U(1)$ extensions and the E$_6$SSM}
+In this paper we consider $U(1)$ extensions of the MSSM where the gauge
 group at low energies is, \be SU(3)_C\times SU(2)_W\times U(1)_Y\times
@@
 
-Here we will refer to U(1) extensions of the MSSM, which solve the
+Here we will refer to $U(1)$ extensions of the MSSM, which solve the
 $\mu$-problem, as the USSM \cite{Cvetic:1995rj, Jain:1995cb,
@@
 Fig.~\ref{Fig:othere6modelsvsmssm} we look at the fine tuning for
-other U(1) extensions for the same $Z^\prime$ masses as we did for the
+other $U(1)$ extensions for the same $Z^\prime$ masses as we did for the
 E$_6$SSM.  To simplify the analysis we fix $\tan \beta = 10$, but scan
@@
 We have investigated this question here in the context of the MSSM and
-U(1) extensions.  Since the RG evolution links the soft masses
+$U(1)$ extensions.  Since the RG evolution links the soft masses
 together and causes these problems from stop and gluino masses the
@@
   \cite{Martin:1993zk}.  Although we use the NoU1Mixing to neglect
-  gauge kinetic mixing this is done in SARAH by removing the RGE for
+  gauge kinetic mixing, SARAH does this by removing the RGE for
   the off diagonal gauge couplings and effectively setting them to

### 2015-03-29 paper/e6ssm-tuning-paper.tex
remove 'all of' since no longer the case.

@@
 $Z^\prime$ limits are important in constraining the most natural
-scenarios in all of these models.  Therefore the $Z^\prime$ constraint
+scenarios of these models.  Therefore the $Z^\prime$ constraint
 is amongst the most important in terms of tuning and attacking natural

### 2015-03-29 paper/e6ssm-tuning-paper.tex
more fixes due to corrected U(1)_I results.

@@
 CMS and ATLAS extend up to $m_{\tilde{\chi}^\pm_1} \approx 700-740$ GeV if
-there are light sleptons\cite{Khachatryan:2014qwa,Aad:2014nua} with
+there are light sleptons\cite{Khachatryan:2014qwa, Aad:2014nua} with
 much weaker bounds if there are no light sleptons or
@@
 mass in the same way as happens in the other models and explaining why
-heavier Higgs values in this model can't be obtained.  Therefore the fine
-tuning behaviour in this model is closer to that of the MSSM, though
-the LHC can still constrain the most natural scenarios from just
-placing tougher limits on the $Z^\prime$ mass.
+heavier Higgs values in this model can't be obtained.  Therefore the
+fine tuning behaviour in this model is closer to that of the MSSM, and
+in this case raising the $Z^\prime$ mass limit to $4.5$ TeV will have
+little impact on naturalness.  From naively estimating the tuning
+using the $d$ coeffioceint one can estimate that $Z^\prime$ limits
+need to be around $15$ TeV before they will raise the tuning in this
+model.
 
@@
 with $M_X$ for low tuning benchmarks in the MSSM and E$_6$SSM. These
-benchmarks are defined in Table \ref{tab:benchmarks} and the results are shown in
-Fig.~\ref{Fig:BMs-varyMX}. Since the behaviour is quite complicated we
-now discuss these in detail as it provides some insight into the many
-differences in the tuning between the two models.
+benchmarks are defined in Table \ref{tab:benchmarks} and the results
+are shown in Fig.~\ref{Fig:BMs-varyMX}. Since the behaviour is quite
+complicated we now discuss these in detail as it provides some insight
+into the many differences in the tuning between the two models.
 
@@
 of around $38$. This should be interpreted as saying that in
-the most conservative limits one can place on naturalness on these
+the most conservative limits one can place on naturalness in these
 models, the tuning in the E$_6$SSM is worse.  However if there are no
@@
 
-We also looked at the tuning in different $U(1)$ extensions for
-fixed $\tan \beta = 10$.  We found that in all cases the fine tuning
-was much worse for the larger $Z^\prime$ mass, further emphasising
-the importance of this in $U(1)$ extensions.  Interestingly
-the actual level in tuning varied quite a bit between these models
-with the $U(1)_I$ model showing the least tuning due to the vanishing
-charge of the $H_u$ state. This model is quite interesting in the
-sense that it provides a solution to the $\mu$-problem while avoiding
-the large tuning (with current limits) from the $Z^\prime$
-mass. However one should remember we are looking at conservative limits
-on naturalness here and there is no solution to the usual tuning coming from
-the large stops needed to get a $125$ GeV Higgs in this model.  In any
-case future LHC limits on the $Z^\prime$ mass would be especially
-interesting for this case as they would significantly raise the
-minimum level of tuning which can be obtained.
+We also looked at the tuning in different $U(1)$ extensions for fixed
+$\tan \beta = 10$.  We found that in every case except for the
+$U(1)_I$ the fine tuning was much worse for the larger $Z^\prime$
+mass, further emphasising the importance of this in $U(1)$ extensions.
+The $U(1)_I$ model showed the least tuning due to
+the vanishing charge of the $H_u$ state. This model is quite
+interesting in the sense that it provides a solution to the
+$\mu$-problem while avoiding the large tuning (with current limits)
+from the $Z^\prime$ mass. However one should remember we are looking
+at conservative limits on naturalness here and there is no solution to
+the usual tuning coming from the large stops needed to get a $125$ GeV
+Higgs in this model.
 

### 2015-03-29 paper/e6ssm-tuning-paper.tex
on less --> less on.

@@
 models and secondly that the tuning from the $Z^\prime$ limits in
-these models depends on less assumptions about SUSY breaking than the
+these models depends less on assumptions about SUSY breaking than the
 tuning required by the $125$ GeV Higgs measurement which concerns
@@
 placed constraints on the Higgs mass, requiring it to be above 114.4
-GeV \cite{Barate:2003sz,Schael:2006cr}, which already introduced significant tuning for
-constrained models, since heavy stops are required to raised the
-lightest Higgs mass above it's tree level bound. Recently this problem
-got much worse since the LHC measured the Higgs to be around $125$
-GeV.
+GeV \cite{Barate:2003sz,Schael:2006cr}, which already introduced
+significant tuning for constrained models, since heavy stops are
+required to raised the lightest Higgs mass above it's tree level
+bound. Recently this problem got much worse since the LHC measured the
+Higgs to be around $125$ GeV.
 
@@
 the usual tuning coming from the large stops needed to get a $125$ GeV
-Higgs in this model.
+Higgs in this model, which will be a problem as the UV scale is raised.
 

### 2015-03-29 paper/e6ssm-tuning-paper.tex
simlify statement introducing chargno limits.
simplify statement in conclusions.

@@
 
-However we should also acknowledge that there are other limits which
-play a similar role.  Chargino limits directly constrain the $\mu$
-parameter (or effective $\mu$ parameter in these $U(1)$ extensions).
-However the chargino limits from the LHC depend on whether there are
-light sleptons or sneutrinos and the mass difference between the
-lightest chargino and lightest neutralino.  Current limits placed by
-CMS and ATLAS extend up to $m_{\tilde{\chi}^\pm_1} \approx 700-740$ GeV if
-there are light sleptons\cite{Khachatryan:2014qwa, Aad:2014nua} with
-much weaker bounds if there are no light sleptons or
-sneutrinos\footnote{Useful summary plots of these limit may be found
-  on the public pages of ATLAS,
+There is another limit which play a similar role.  Chargino limits
+directly constrain the $\mu$ parameter (or effective $\mu$ parameter
+in these $U(1)$ extensions).  However the chargino limits from the LHC
+depend on whether there are light sleptons or sneutrinos and the mass
+difference between the lightest chargino and lightest neutralino.
+Current limits placed by CMS and ATLAS extend up to
+$m_{\tilde{\chi}^\pm_1} \approx 700-740$ GeV if there are light
+sleptons\cite{Khachatryan:2014qwa, Aad:2014nua} with much weaker
+bounds if there are no light sleptons or sneutrinos\footnote{Useful
+  summary plots of these limit may be found on the public pages of
+  ATLAS,
   \url{https://atlas.web.cern.ch/Atlas/GROUPS/PHYSICS/CombinedSummaryPlots/SUSY/ATLAS_SUSY_EWSummary/ATLAS_SUSY_EWSummary.png}
@@
 renormalisation group running one can then see that at the EW scale
-the stops and soft Higgs masses (which appear directly in the EWSB
-conditions) should appear in the EWSB condition for $M_Z$ and
-therefore it was expected that these masses should not be much bigger
-than $100$ GeV.  However to disturb this elegant picture first LEP
-placed constraints on the Higgs mass, requiring it to be above 114.4
-GeV \cite{Barate:2003sz,Schael:2006cr}, which already introduced
+the stops enter the EWSB condition for $M_Z$, therefore it was
+expected that these masses should not be much bigger than $100$ GeV.
+However to disturb this elegant picture first LEP placed constraints
+on the Higgs mass, requiring it to be above 114.4 GeV
+\cite{Barate:2003sz,Schael:2006cr}, which already introduced
 significant tuning for constrained models, since heavy stops are

### 2015-03-30 paper/e6ssm-tuning-paper.tex
Recently -> Then recently.
Fixed some typos, added some missing definitions of symbols and made notation consistent across sections

@@
 (RGEs) from the grand unification (GUT) scale to the electroweak (EW)
-scale. This affects the SUSY prediction of the electroweak VEV, $v$,
+scale. This affects the SUSY prediction of the electroweak vacuum expectation value (VEV), $v$,
 or $M_Z$.  This naturalness problem motivates both further examination
@@
 suffer from naturalness problems with the mass of the new $Z^\prime$
-associated with break down of the new $U(1)$ appearing in the
+associated with the break down of the new $U(1)$ appearing in the
 electroweak symmetry breaking conditions at tree level
@@
 extensions which solve the $\mu$-problem should be ordinary left
-handed quark, $\hat{Q}_i$ and lepton $\hat{L}_i$
+handed quark $\hat{Q}_i$ and lepton $\hat{L}_i$
 ($i=1,2,3$) superfields along with right handed superfields
@@
 \begin{tabular}{cccccccccccccc}
- & $\hat{Q}$ & $\hat{u}^C$ & $\hat{d}^C$ & $\hat{L}$ & $\hat{e}^C$ & $\hat{N}^C$ & $\hat{S}$ & $\hat{H}_2$ & $\hat{H}_1$ & $\hat{D}$ & $\hat{\overline{D}}$ & $\hat{H}'$ & $\hat{\overline{H'}}$ \\[1mm]
+ & $\hat{Q}$ & $\hat{u}^c$ & $\hat{d}^c$ & $\hat{L}$ & $\hat{e}^c$ & $\hat{N}^c$ & $\hat{S}$ & $\hat{H}_2$ & $\hat{H}_1$ & $\hat{D}$ & $\hat{\overline{D}}$ & $\hat{H}'$ & $\hat{\overline{H'}}$ \\[1mm]
 \hline
@@
 Here we will focus most on the special case where the gauge symmetry
-is $U(1)_N$, under which the right handed neutrino remains
+is $U(1)_N$, under which the right handed neutrino $\hat{N}^c$ remains
 interaction-less. This is the case in the E$_6$SSM
@@
 The impact of gauge kinetic mixing in the case where both of the extra
-$U(1)$ symmetries appearing from the breakdown of E$_6$ are present at
+$U(1)$ symmetries appearing from the breakdown of $E_6$ are present at
 low energy was studied in \cite{Rizzo:2012rf}.  The E$_6$SSM was also
@@
 With three generations of matter $27$-plet representations of $E_6$
-surviving to low energies, the low energy matter content includes, \be
+surviving to low energies, the low energy matter content in each generation 
+includes, \be
 (\hat{Q}_i,\,\hat{u}^c_i,\,\hat{d}^c_i,\,\hat{L}_i,\,\hat{e}^c_i)
 +(\hat{D}_i,\,\hat{\overline{D}}_i)+(\hat{S}_{i})+(\hat{H}^u_i)+(\hat{H}^d_i),\ee
-where the $\hat{S}_{i}$, $\hat{H}^u_i$ and $\hat{H}^d_i$ are three
-generations of doublets, whose quantum numbers will be like the
-singlet, and up-, down-type Higgs fields and the $\hat{D}_i$ and
-$\hat{\overline{D}}_i$ being $SU(3)_C$ triplets that reside in the
+where the $\hat{S}_{i}$, $\hat{H}^u_i$ and $\hat{H}^d_i$ have the quantum numbers of a
+SM singlet, and up-, down-type Higgs fields, respectively, and the $\hat{D}_i$ and
+$\hat{\overline{D}}_i$ are $SU(3)_C$ triplets that reside in the
 same $SU(5)$ multiplets as these Higgs-like states.
@@
 \begin{eqnarray}
-W_0 &=& \lambda_{ijk} \hat{S}_i  \hat{H}^d_{j} \cdot\hat{H}^u_{k} + \kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\bar{D}}_k + h^N_{ijk} \hat{N}^c_i  \hat{H}^u_{j} \cdot \hat{L}_k \nonumber \\
-& & + h^U_{ijk} \hat{u}^c_i  \hat{H}^u_{j} \cdot \hat{Q}_k + h^D_{ijk} \hat{d}^c_i  \hat{Q}_k\cdot\hat{H}^d_{j}  + h^E_{ijk} \hat{e}^c_i  \hat{L}_k\cdot\hat{H}^d_{j} , \\
+W_0 &=& \lambda_{ijk} \hat{S}_i  \hat{H}^d_{j} \cdot\hat{H}^u_{k} + \kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\overline{D}}_k + h^N_{ijk} \hat{N}^c_i  \hat{H}^u_{j} \cdot \hat{L}_k \nonumber \\
+& & + y^U_{ijk} \hat{u}^c_i  \hat{H}^u_{j} \cdot \hat{Q}_k + y^D_{ijk} \hat{d}^c_i  \hat{Q}_k\cdot\hat{H}^d_{j}  + y^E_{ijk} \hat{e}^c_i  \hat{L}_k\cdot\hat{H}^d_{j} , \\
 W_1 &=& g^Q_{ijk} \hat{D}_i  \hat{Q}_j \cdot \hat{Q}_k + g^q_{ijk} \hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k, \\
@@
     W &\approx& y_{\tau} \SuperField{L}_3 \cdot \SuperField{H}_d
-      \SuperField{e}^C_3 + y_b \SuperField{Q}_3\cdot\SuperField{H}_d
-      \SuperField{d}_3^C + y_t \SuperField{H}_u\cdot\SuperField{Q}_3
-      \SuperField{u}_3^C\\
+      \SuperField{e}^c_3 + y_b \SuperField{Q}_3\cdot\SuperField{H}_d
+      \SuperField{d}_3^c + y_t \SuperField{H}_u\cdot\SuperField{Q}_3
+      \SuperField{u}_3^c\\
     &&
-    + \lambda_i \SuperField{S} \SuperField{H}_{1i}
-    \cdot \SuperField{H}_{2i}  + \kappa_i \SuperField{S} \SuperField{D}_i
+    + \lambda_i \SuperField{S} \SuperField{H}_i^d
+    \cdot \SuperField{H}_i^u  + \kappa_i \SuperField{S} \SuperField{D}_i
     \SuperField{\overline{D}}_i + \mu' \SuperField{H}'\cdot
@@
 %  
-
+where the third generation Higgs fields $\SuperField{H}_d^3\equiv \SuperField{H}_d$,
+$\SuperField{H}_u^3\equiv\SuperField{H}_u$ and SM singlet field $\SuperField{S}_3\equiv\SuperField{S}$ 
+are allowed to get VEVs. 
 \section{\label{sec:ewsb}Electroweak Symmetry Breaking}
 % EWSB conditions in E6SSM
-The Higgs scalar potential for the E$_6$ model considered is \cite{King:2005jy} 
+The Higgs scalar potential for the $E_6$ models considered can be written as \cite{King:2005jy} 
 \begin{equation}\label{eq:E6VeffOneLoop}
@@
 \begin{align}
-V_F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|H_1\cdot
-H_2|^2,\label{eq:E6VFterms}\\ 
+V_F&=\lambda^2|S|^2(|H_d|^2+|H_u|^2)+\lambda^2|H_d\cdot
+H_u|^2,\label{eq:E6VFterms}\\ 
 V_D&=\frac{\bar{g}^2}{8}\left (
-|H_2|^2-|H_1|^2\right )^2+\frac{g_2^2}{2}|H_1^\dagger
-H_2|^2+\frac{g_1'^2}{2}(Q_1|H_1|^2+Q_2|H_2|^2+Q_S|S|^2)^2,\label{eq:E6VDterms}\\ 
-V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big
-[\lambda A_\lambda SH_1\cdot H_2+\textrm{h.c.}\Big
+|H_u|^2-|H_d|^2\right )^2+\frac{g_2^2}{2}|H_d^\dagger
+H_u|^2+\frac{g_1'^2}{2}(Q_1|H_d|^2+Q_2|H_u|^2+Q_S|S|^2)^2,\label{eq:E6VDterms}\\ 
+V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_d|^2+m_{H_u}^2|H_u|^2+\Big
+[\lambda A_\lambda SH_d\cdot H_u+\textrm{h.c.}\Big
 ].\label{eq:E6Vsoft}
@@
 $Q_2$ and $Q_S$ are effective $U(1)'$ charges for
-$H_1$, $H_2$ and $S$, respectively. In the case
+$H_d$, $H_u$ and $S$, respectively, and $\lambda\equiv \lambda_3$. In the case
 of the $U(1)_\chi$ model, $V_F$ may also contain an elementary
@@
 \begin{equation}\label{eq:E6vevs}
-\langle H_1 \rangle = \frac{1}{\sqrt{2}}\begin{pmatrix} v_1 \\ 0\end{pmatrix}, \; \langle H_2 \rangle = \frac{1}{\sqrt{2}}\begin{pmatrix} 0 \\ v_2 \end{pmatrix}, \; \langle S \rangle =\frac{s}{\sqrt{2}}
+\langle H_d \rangle = \frac{1}{\sqrt{2}}\begin{pmatrix} v_1 \\ 0\end{pmatrix}, \; \langle H_u \rangle = \frac{1}{\sqrt{2}}\begin{pmatrix} 0 \\ v_2 \end{pmatrix}, \; \langle S \rangle =\frac{s}{\sqrt{2}}
 \end{equation}
@@
 &f_1=m_{H_d}^2v_1+\frac{\lambda^2}{2}(v_2^2+s^2)v_1-\frac{\lambda A_\lambda}{\sqrt{2}}sv_2-\frac{\bar{g}^2}{8}
-(v_2^2-v_1^2)v_1+D_{H_1}v_1+\frac{\partial \Delta V}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\
+(v_2^2-v_1^2)v_1+D_{H_d}v_1+\frac{\partial \Delta V}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\
 &f_2=m_{H_u}^2v_2+\frac{\lambda^2}{2}(v_1^2+s^2)v_2-\frac{\lambda A_\lambda}{\sqrt{2}}sv_1+\frac{\bar{g}^2}{8}
-(v_2^2-v_1^2)v_2+D_{H_2}v_2+\frac{\partial \Delta V}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\
+(v_2^2-v_1^2)v_2+D_{H_u}v_2+\frac{\partial \Delta V}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\
 &f_3=m_S^2s+\frac{\lambda^2}{2}(v_2^2+v_1^2)s-\frac{\lambda A_\lambda}{\sqrt{2}}v_2v_1+D_Ss+\frac{\partial \Delta V}{\partial s}=0.\label{eq:E6EWSBcondition3}
@@
 \end{subequations}
-The quantities $D_{H_1}$, $D_{H_2}$ and $D_S$ appearing above are
+The quantities $D_{H_d}$, $D_{H_u}$ and $D_S$ appearing above are
 $U(1)'$ $D$-term contributions that are absent in the MSSM and NMSSM
@@
 \begin{align}
-  m_{\tilde{t}_{1,2}}^2&=\frac{1}{2}\bigg \{ m_{Q3}^2+m_{u3}^2+\frac{1}{2}M_Z^2\cos 2\beta+D_Q+D_u+2m_t^2\nonumber\\
-&\quad{}\mp\sqrt{\left [ m_{Q3}^2+m_{u3}^2+\left ( \frac{1}{2}-\frac{4}{3}\sin^2\theta_W\right )M_Z^2\cos 2\beta + D_Q-D_u\right ]^2+4m_t^2X_t^2}\bigg \},
+  m_{\tilde{t}_{1,2}}^2&=\frac{1}{2}\bigg \{ m_{Q_3}^2+m_{u_3}^2+\frac{\bar{g}^2}{8}\left ( v_1^2-v_2^2\right )+D_Q+D_u+2m_t^2\nonumber\\
+&\quad{}\mp\sqrt{\left [ m_{Q_3}^2+m_{u_3}^2+\frac{1}{8}\left ( g_2^2-g_1^2\right )\left ( v_1^2-v_2^2\right ) + D_Q-D_u\right ]^2+4m_t^2X_t^2}\bigg \},
 \end{align}
-where $m_t^2=y_t^2v_2^2/2$ and $X_t=A_t-\frac{\lambda s v_1}{\sqrt{2}v_2}$. By definition we take $m_{\tilde{t}_1}$ to correspond to the lighter of the two states.\\
-As was noted in \cite{Athron:2013ipa}, the first two of these conditions may be rewritten in the form
+where $m_t^2=y_t^2v_2^2/2$, $X_t=A_t-\frac{\lambda s v_1}{\sqrt{2}v_2}$, $m_{Q_3}^2$, $m_{u_3}^2$ are soft breaking scalar masses and $A_t$ is a soft trilinear coupling.
+By definition we take $m_{\tilde{t}_1}$ to correspond to the lighter of the two states.\\
+As was noted in \cite{Athron:2013ipa}, the first two of the conditions Eq.~\ref{eq:E6EWSBConditions} may be rewritten in the form
 \begin{equation}\label{eq:E6MZequation}
-\frac{M_Z^2}{2}=-\frac{\lambda^2s^2}{2}+\frac{\tilde{m}_{H_d}^2-\tilde{m}_{H_u}^2\tan^2\beta}{\tan^2\beta-1}+\frac{D_{H_1}-D_{H_2}\tan^2\beta}{\tan^2\beta-1},
+\frac{M_Z^2}{2}=-\frac{\lambda^2s^2}{2}+\frac{\tilde{m}_{H_d}^2-\tilde{m}_{H_u}^2\tan^2\beta}{\tan^2\beta-1}+\frac{D_{H_d}-D_{H_u}\tan^2\beta}{\tan^2\beta-1},
 \end{equation}
 \begin{equation}\label{eq:E6sin2bequation}
-\sin 2\beta=\frac{\sqrt{2}\lambda A_{\lambda} s}{\tilde{m}_{H_d}^2+\tilde{m}_{H_u}^2+\lambda^2s^2+D_{H_1}+D_{H_2}},
+\sin 2\beta=\frac{\sqrt{2}\lambda A_{\lambda} s}{\tilde{m}_{H_d}^2+\tilde{m}_{H_u}^2+\lambda^2s^2+D_{H_d}+D_{H_u}},
 \end{equation}
@@
 right-hand side of Eq.~(\ref{eq:E6MZequation}) must be tuned to cancel
-the resulting very large contribution to $M_Z$. Moreover, because this
-is a large tree level fine tuning, it may negate the increase in
+this very large contribution to $M_Z$. Moreover, because this
+is a large tree level fine tuning, it may negate the improvement in
 naturalness that is associated with having a reduced need for heavy
@@
 \Delta_p=\left | \frac{\partial \log M_Z^2}{\partial \log p}\right
-|=\left | \frac{p}{M_Z^2}\frac{\partial M_Z^2}{\partial p}\right |,
+|=\left | \frac{p}{M_Z^2}\frac{\partial M_Z^2}{\partial p}\right |.
 \end{equation}
-where $M_Z^2=\bar{g}^2v^2/4$. The coefficient $\Delta_p$ measures the
-fractional variation in $M_Z^2$ resulting from a given variation in
-the parameter $p$. The overall fine tuning is then taken to be $\Delta
+The coefficient $\Delta_p$ measures the fractional variation in $M_Z^2$ resulting 
+from a given variation in the parameter $p$. The overall fine tuning is then taken to be $\Delta
 = \underset{i}{\max}\,\{\Delta_{p_i}\}$.\\
@@
 conditions, greatly simplifying the final result. For the purposes of
-exploring a wider class of $E_6$ inspired models, we have rederived
+exploring a wider class of $E_6$ inspired models, we have derived
 the master formula without neglecting any $O(v^2)$ terms. The more
@@
 Evaluating the derivatives
-$\partial q_k/\partial p$ must (in general) be done by numerically
+$\partial q_k/\partial p$ must in general be done by numerically
 integrating the two-loop RGEs. This is time consuming and presents an
@@
 \begin{equation}\label{eq:rge}
-\frac{\textrm{d}q}{\mathrm{d}t}=\frac{1}{16\pi^2}\beta_q^{(1)}+\frac{1}{(16\pi^2)^2}\beta_q^{(2)},\qquad t\equiv \log\frac{Q}{M_X},
+\frac{\textrm{d}q}{\mathrm{d}t}\equiv \beta_q =\frac{1}{16\pi^2}\beta_q^{(1)}+\frac{1}{(16\pi^2)^2}\beta_q^{(2)},\qquad t\equiv \log\frac{Q}{M_X},
 \end{equation}
@@
 \begin{align}\label{eq:rgeapproxsoln}
-q(Q)&=q(M_X)+\int_0^t q(t')\;\textrm{d}t'\approx q(M_X)+\frac{t}{16\pi^2}\left ( \beta_q^{(1)}+\frac{\beta_q^{(2)}}{16\pi^2}\right )+\frac{t^2}{32\pi^2}\frac{\textrm{d}\beta_q^{(1)}}{\textrm{d}t}+\mathcal{O}(t^2).
+q(Q)&=q(M_X)+\int_0^t \beta_q(t')\;\textrm{d}t'\approx q(M_X)+\frac{t}{16\pi^2}\left ( \beta_q^{(1)}+\frac{\beta_q^{(2)}}{16\pi^2}\right )+\frac{t^2}{32\pi^2}\frac{\textrm{d}\beta_q^{(1)}}{\textrm{d}t}+\mathcal{O}(t^2).
 \end{align}
@@
 GeV Higgs boson and light stops simultaneously and much experimental
-efforts to search for light stops.  This is entirely appropriate since
+effort to search for light stops.  This is entirely appropriate since
 there are many good reasons to expect the soft masses to be set at
@@
 $m_{e_i}=204$ GeV, $m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and
-$m_{d_i}=438$ GeV ($i=1,2,3$). Although we should stress that making
+$m_{d_i}=438$ GeV ($i=1,2,3$). Here we denote by $M_1$, $M_2$ and $M_3$
+the soft gaugino masses for $U(1)$, $SU(2)$ and $SU(3)$, while $A_b$ and
+$A_\tau$ are soft trilinear couplings and the $m_\phi$ are soft scalar
+masses for the indicated fields. The soft bilinear
+coupling $B$ is defined such that at tree level the mass of the CP-odd MSSM Higgs boson
+reads $m_A^2=2B\mu/\sin 2\beta$. All off-diagonal couplings and scalar masses
+are set to zero, as are the first and second generation Yukawa couplings
+and soft trilinears. Although we should stress that making
 this choice will lead to a spectrum which is in conflict with the LHC
@@
 \caption{The parameters scanned over and the ranges of values used in
-  the MSSM and the E$_6SSM$ models.}
+  the MSSM and the E$_6$SSM models.}
 \label{tab:scanranges}
@@
 
-There is another limit which play a similar role.  Chargino limits
+There is another limit which plays a similar role.  Chargino limits
 directly constrain the $\mu$ parameter (or effective $\mu$ parameter
@@
 
-Nonetheless the MSSM the impact of potential chargino mass limits is
+Nonetheless for the MSSM the impact of potential chargino mass limits is
 shown in Fig.~\ref{Fig:chargino-plot}.  There we see that if the 
@@
 little impact on naturalness. From naively estimating the tuning
-using the $d$ coeffioceint one can estimate that $Z^\prime$ limits
+using the $d$ coefficient one can estimate that $Z^\prime$ limits
 need to be around $15$ TeV before they will raise the tuning in this
@@
 $A_t(M_{\mathrm{SUSY}})$ [GeV] & $-3335.7$ & $-2734.8$ & $-1100$ & $-1103.2$ \\
-$m_{L1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.35\times 10^6$ & $2.5\times 10^7$ & $4.94\times 10^6$ \\
-$m_{L3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.22\times 10^6$ & $2.5\times 10^7$ & $4.90\times 10^6$ \\
-$m_{e1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.27\times 10^6$ & $2.5\times 10^7$ & $5.21\times 10^6$ \\
-$m_{e3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.03\times 10^6$ & $2.5\times 10^7$ & $5.11\times 10^6$ \\
-$m_{Q1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.37\times 10^6$ & $2.5\times 10^7$ & $5.76\times 10^6$ \\
-$m_{Q3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.45\times 10^6$ & $3.97\times 10^6$ & $4.50\times 10^5$ & $3.61\times 10^6$ \\
-$m_{u1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.30\times 10^6$ & $2.5\times 10^7$ & $5.54\times 10^6$ \\
-$m_{u3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.0 \times 10^6$ & $6.60\times10^5$& $5.86\times 10^5$ & $2.04\times 10^6$ \\
-$m_{d1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.30\times 10^6$ & $2.5\times 10^7$ & $5.88\times 10^6$ \\
-$m_{d3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.03\times 10^6$ & $2.5\times 10^7$ & $5.78\times 10^6$ \\
+$m_{L_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.35\times 10^6$ & $2.5\times 10^7$ & $4.94\times 10^6$ \\
+$m_{L_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.22\times 10^6$ & $2.5\times 10^7$ & $4.90\times 10^6$ \\
+$m_{e_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.27\times 10^6$ & $2.5\times 10^7$ & $5.21\times 10^6$ \\
+$m_{e_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.03\times 10^6$ & $2.5\times 10^7$ & $5.11\times 10^6$ \\
+$m_{Q_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.37\times 10^6$ & $2.5\times 10^7$ & $5.76\times 10^6$ \\
+$m_{Q_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.45\times 10^6$ & $3.97\times 10^6$ & $4.50\times 10^5$ & $3.61\times 10^6$ \\
+$m_{u_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.30\times 10^6$ & $2.5\times 10^7$ & $5.54\times 10^6$ \\
+$m_{u_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.0 \times 10^6$ & $6.60\times10^5$& $5.86\times 10^5$ & $2.04\times 10^6$ \\
+$m_{d_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.30\times 10^6$ & $2.5\times 10^7$ & $5.88\times 10^6$ \\
+$m_{d_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.03\times 10^6$ & $2.5\times 10^7$ & $5.78\times 10^6$ \\
 $m_{H_d}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $1.82\times 10^6$ & $8.96\times 10^6$ & $4.06\times 10^7$ & $1.04\times 10^7$ \\
@@
 The soft masses $m_{H_d}^2$, $m_{H_u}^2$ and $m_S^2$ are those that satisfy the EWSB conditions including 1-loop Coleman-Weinberg corrections involving the top and stops.
-For E$_6$SSM BM1 (BM2) we also set $\mu^\prime = 5000.0$ $(897.9)$ GeV, $B\mu^\prime = 5000.0$ $(-4.21\times 10^5)$ GeV$^2$, $A_{\kappa 1,2,3} = 0$ $(-1389.2)$ GeV, $A_{\lambda 1,2} = 0$ $(-52.9)$ GeV, $m_{D1,2,3}^2 = 2.5\times 10^7$ $(4.81\times 10^6)$ GeV$^2$, $m_{\overline{D}1,2,3}^2 = 2.5\times 10^7$ $(4.90\times 10^6)$ GeV$^2$, $m_{H^d_{1,2}}^2 = 2.5\times 10^7$ $(4.46\times 10^6)$ GeV$^2$, $m_{H^u_{1,2}}^2 = 2.5\times 10^7$ $(4.81\times 10^6)$ GeV$^2$, $m_{S_{1,2}}^2 = 2.5\times 10^7$ $(5.28\times 10^6)$ GeV$^2$, $m_{H'}^2 = 2.5\times 10^7$ $(4.94\times 10^6)$ GeV$^2$ and $m_{\overline{H'}}^2 = 2.5\times 10^7$ $(4.87\times 10^6)$ GeV$^2$.
+For E$_6$SSM BM1 (BM2) we also set $\mu^\prime = 5000.0$ $(897.9)$ GeV, $B\mu^\prime = 5000.0$ $(-4.21\times 10^5)$ GeV$^2$, $A_{\kappa_{1,2,3}} = 0$ $(-1389.2)$ GeV, $A_{\lambda_{1,2}} = 0$ $(-52.9)$ GeV, $m_{D_{1,2,3}}^2 = 2.5\times 10^7$ $(4.81\times 10^6)$ GeV$^2$, $m_{\overline{D}_{1,2,3}}^2 = 2.5\times 10^7$ $(4.90\times 10^6)$ GeV$^2$, $m_{H^d_{1,2}}^2 = 2.5\times 10^7$ $(4.46\times 10^6)$ GeV$^2$, $m_{H^u_{1,2}}^2 = 2.5\times 10^7$ $(4.81\times 10^6)$ GeV$^2$, $m_{S_{1,2}}^2 = 2.5\times 10^7$ $(5.28\times 10^6)$ GeV$^2$, $m_{H'}^2 = 2.5\times 10^7$ $(4.94\times 10^6)$ GeV$^2$ and $m_{\overline{H'}}^2 = 2.5\times 10^7$ $(4.87\times 10^6)$ GeV$^2$.
 }
@@
 found this does not eliminate the tuning as there is still a strong
-sensitivity to $A_t$, but we did find that large mixing lead less
+sensitivity to $A_t$, but we did find that large mixing lead to less
 fine tuning overall for the points we examined.
@@
   and a negative contribution from $m_{Q_3}^2(M_X)$ and
-  $m_{U_3}^2(M_X)$, allowing heavy stop masses to cause fine
+  $m_{u_3}^2(M_X)$, allowing heavy stop masses to cause fine
   tuning. In this case $m_{H_u}^2(M_{SUSY})$ is held fixed so as the
@@
 giving a tuning at $10^{16}$ GeV of $\approx 546$, which is far below
-that of the other two benchmark points.
+that of the other three benchmark points.
 
 In addition to this, the soft parameters in E$_6$SSM BM2 follow a pattern similar to that found in the constrained
-model. With the exception of the parameters $m_{Q3}^2$, 
-$m_{u3}^2$, $m_{H_d}^2$, $m_{H_u}^2$, and $M_3$, the values of which are given in Table \ref{tab:benchmarks}, 
+model. With the exception of the parameters $m_{Q_3}^2$, 
+$m_{u_3}^2$, $m_{H_d}^2$, $m_{H_u}^2$, and $M_3$, the values of which are given in Table \ref{tab:benchmarks}, 
 the soft masses at the SUSY scale correspond to the values that result in the cE$_6$SSM with $m_0=2.2$ TeV, 
@@
 $\lambda_{1,2}(M_X)=0.1$.
-This leads to a significant reduction in the contributions to the RG running of $m_{H_u}^2$ and $m_{Q3}^2$ coming from terms of the form $g_1^2\Sigma_1$ and, to a lesser extent, $g_1'^2\Sigma_1'$.
+This leads to a significant reduction in the contributions to the RG running of $m_{H_u}^2$ and $m_{Q_3}^2$ coming from terms of the form $g_1^2\Sigma_1$ and, to a lesser extent, $g_1'^2\Sigma_1'$.
 Here we define for the E$_6$SSM (see also Eqs.~(\ref{eq:USSMGaugeSigmaTerm1}-\ref{eq:USSMGaugeSigmaTerm1Pr}) for general $U(1)$ inspired models)
 \begin{align*}
-\Sigma_1&=\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2-m_{Li}^2+m_{H_{ui}}^2-m_{H_{di}}^2+m_{\overline{D}_i}^2-m_{Di}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\\
-\Sigma_1'&=\sum_{i=1}^3\left ( 6m_{Qi}^2+3m_{ui}^2+6m_{di}^2+m_{ei}^2+4m_{Li}^2-4m_{H_{ui}}^2-6m_{H_{di}}^2+5m_{Si}^2-9m_{\overline{D}_i}^2-6m_{Di}^2\right )\\
+\Sigma_1&=\sum_{i=1}^3\left ( m_{Q_i}^2-2m_{u_i}^2+m_{d_i}^2+m_{e_i}^2-m_{L_i}^2+m_{H_i^u}^2-m_{H_i^d}^2+m_{\overline{D}_i}^2-m_{D_i}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\\
+\Sigma_1'&=\sum_{i=1}^3\left ( 6m_{Q_i}^2+3m_{u_i}^2+6m_{d_i}^2+m_{e_i}^2+4m_{L_i}^2-4m_{H_i^u}^2-6m_{H_i^d}^2+5m_{Si}^2-9m_{\overline{D}_i}^2-6m_{D_i}^2\right )\\
 &\quad{}+4m_{H'}^2-4m_{\overline{H'}}^2.
 \end{align*}
-In the unconstrained case, this contribution acts to drive up the values of $m_{Q3}^2$ and $m_{H_u}^2$, and thus the associated tuning sensitivities, at the cutoff scale $M_X$.
+In the unconstrained case, this contribution acts to drive up the values of $m_{Q_3}^2$ and $m_{H_u}^2$, and thus the associated tuning sensitivities, at the cutoff scale $M_X$.
 In the case of E$_6$SSM BM2, on the other hand, the reduced splitting between the soft masses leads to a much smaller contribution from these terms.
@@
 required to raised the lightest Higgs mass above it's tree level
-bound. Recently this problem got much worse since the LHC measured the
-Higgs to be around $125$ GeV.
+bound. Then recently this problem got much worse since the LHC measured the
+Higgs mass to be around $125$ GeV.
 
@@
 a low cutoff. We find that in the MSSM the most direct way to
-constrain naturalness of the model, without making assumptions about
+constrain naturalness in the model without making assumptions about
 the SUSY breaking scale is through limits on the chargino
@@
 \ee
-It is straightforward to compute the appropriate derivatives directly from the EWSB conditions (\ref{eq:E6EWSBConditions}).
+It is straightforward to compute the appropriate derivatives directly from the EWSB conditions, Eq.~(\ref{eq:E6EWSBConditions}).
 Similarly, the quantity $C$ appearing in Eq.~(\ref{eq:E6masterformula}) is given by
@@
 \begin{align}
-b_\mu^{(2)}&=\frac{\mu}{2}\Bigg [ 45y_t^4+45y_b^4+9y_\tau^2+30y_t^2y_b^2+6y_t^2y_\tau^2+18y_b^2y_\tau^2-32g_3^2(y_t^2+y_b^2)\nonumber\\
+b_\mu^{(2)}&=\frac{\mu}{2}\Bigg [ 45y_t^4+45y_b^4+9y_\tau^4+30y_t^2y_b^2+6y_t^2y_\tau^2+18y_b^2y_\tau^2-32g_3^2(y_t^2+y_b^2)\nonumber\\
 &\quad{}-12g_2^2(3y_t^2+3y_b^2+y_\tau^2)-\frac{4}{5}g_1^2(11y_t^2+8y_b^2+6y_\tau^2)+3g_2^4-\frac{189}{25}g_1^4+\frac{18}{5}g_1^2g_2^2\Bigg ],\label{eq:MSSMmub2}\\
@@
 &\quad{}+12g_2^4M_2+\frac{396}{25}g_1^4M_1,\label{eq:MSSMBb2}\\
-b_{m_{H_d}^2}^{(2)}&=72y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
-&\quad{}+6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
-&\quad{}+12y_\tau^2y_b^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{d3}^2+m_{L3}^2+m_{e3}^2+(A_\tau+A_b)^2\right )\nonumber\\
-&\quad{}+16y_\tau^4\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2A_\tau^2\right )\nonumber\\
-&\quad{}-32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_3A_b+2M_3^2\right )\nonumber\\
-&\quad{}-18g_2^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_2A_b+2M_2^2\right )\nonumber\\
-&\quad{}-6g_2^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+A_\tau^2-2M_2A_\tau+2M_2^2\right )\nonumber\\
-&\quad{}-\frac{14}{5}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_1A_b+2M_1^2\right )\nonumber\\
-&\quad{}-\frac{18}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+A_\tau^2-2M_1A_\tau+2M_1^2\right )\nonumber\\
+b_{m_{H_d}^2}^{(2)}&=72y_b^4\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2A_b^2\right )\nonumber\\
+&\quad{}+6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2+(A_t+A_b)^2\right )\nonumber\\
+&\quad{}+12y_\tau^2y_b^2\left ( 2m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+m_{L_3}^2+m_{e_3}^2+(A_\tau+A_b)^2\right )\nonumber\\
+&\quad{}+16y_\tau^4\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+2A_\tau^2\right )\nonumber\\
+&\quad{}-32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+A_b^2-2M_3A_b+2M_3^2\right )\nonumber\\
+&\quad{}-18g_2^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+A_b^2-2M_2A_b+2M_2^2\right )\nonumber\\
+&\quad{}-6g_2^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+A_\tau^2-2M_2A_\tau+2M_2^2\right )\nonumber\\
+&\quad{}-\frac{14}{5}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+A_b^2-2M_1A_b+2M_1^2\right )\nonumber\\
+&\quad{}-\frac{18}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+A_\tau^2-2M_1A_\tau+2M_1^2\right )\nonumber\\
 &\quad{}-18g_2^4M_2^2-\frac{198}{25}g_1^4\left ( \mathcal{S}+3M_1^2\right ),\label{eq:MSSMmHd2b2}\\
-b_{m_{H_u}^2}^{(2)}&=72y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
-&\quad{}+6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
-&\quad{}-32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2A_tM_3+2M_3^2\right )\nonumber\\
-&\quad{}-18g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2A_tM_2+2M_2^2\right )\nonumber\\
-&\quad{}-\frac{26}{5}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2A_tM_1+2M_1^2\right )\nonumber\\
+b_{m_{H_u}^2}^{(2)}&=72y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2A_t^2\right )\nonumber\\
+&\quad{}+6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2+(A_t+A_b)^2\right )\nonumber\\
+&\quad{}-32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2A_tM_3+2M_3^2\right )\nonumber\\
+&\quad{}-18g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2A_tM_2+2M_2^2\right )\nonumber\\
+&\quad{}-\frac{26}{5}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2A_tM_1+2M_1^2\right )\nonumber\\
 &\quad{}+\frac{198}{25}g_1^4\left ( \mathcal{S}-3M_1^2\right )-18g_2^4M_2^2.\label{eq:MSSMmHu2b2}
@@
 \begin{equation}\label{eq:MSSMgaugeBetaContribution}
-\mathcal{S}=m_{H_u}^2-m_{H_d}^2+\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2\right ).
+\mathcal{S}=m_{H_u}^2-m_{H_d}^2+\sum_{i=1}^3\left ( m_{Q_i}^2-m_{L_i}^2-2m_{u_i}^2+m_{d_i}^2+m_{e_i}^2\right ).
 \end{equation}
@@
 from top and stop loops are included, it is also necessary to
-construct the expansions for $m_{Q3}^2$, $m_{u3}^2$ and $A_t$. The
+construct the expansions for $m_{Q_3}^2$, $m_{u_3}^2$ and $A_t$. The
 coefficients read
@@
 \begin{align}
-b_{m_{Q3}^2}^{(2)}&=24y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )+24y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2A_b^2\right )\nonumber\\
-&\quad{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
-&\quad{}+2y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{L3}^2+m_{d3}^2+m_{e3}^2+(A_b+A_\tau)^2\right )\nonumber\\
-&\quad{}-\frac{32}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_3A_t+2M_3^2\right )\nonumber\\
-&\quad{}-\frac{32}{3}g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_3A_b+2M_3^2\right )\nonumber\\
-&\quad{}-6g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_2A_t+2M_2^2\right )\nonumber\\
-&\quad{}-6g_2^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_2A_b+2M_2^2\right )\nonumber\\
-&\quad{}-\frac{26}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
-&\quad{}-\frac{14}{15}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+A_b^2-2M_1A_b+2M_1^2\right )\nonumber\\
+b_{m_{Q_3}^2}^{(2)}&=24y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2A_t^2\right )+24y_b^4\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2A_b^2\right )\nonumber\\
+&\quad{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2+(A_t+A_b)^2\right )\nonumber\\
+&\quad{}+2y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q_3}^2+m_{L_3}^2+m_{d_3}^2+m_{e_3}^2+(A_b+A_\tau)^2\right )\nonumber\\
+&\quad{}-\frac{32}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2M_3A_t+2M_3^2\right )\nonumber\\
+&\quad{}-\frac{32}{3}g_3^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+A_b^2-2M_3A_b+2M_3^2\right )\nonumber\\
+&\quad{}-6g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2M_2A_t+2M_2^2\right )\nonumber\\
+&\quad{}-6g_2^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+A_b^2-2M_2A_b+2M_2^2\right )\nonumber\\
+&\quad{}-\frac{26}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
+&\quad{}-\frac{14}{15}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+A_b^2-2M_1A_b+2M_1^2\right )\nonumber\\
 &\quad{}+96g_3^4M_3^2-18g_2^4M_2^2+\frac{66}{25}g_1^4(\mathcal{S}-M_1^2),\label{eq:MSSMmQ32b2}\\
-b_{m_{u3}^2}^{(2)}&=48y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2A_t^2\right )\nonumber\\
-&\quad{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2+(A_t+A_b)^2\right )\nonumber\\
-&\quad{}-\frac{64}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_3A_t+2M_3^2\right )\nonumber\\
-&\quad{}-12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_2A_t+2M_2^2\right )\nonumber\\
-&\quad{}-\frac{52}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
+b_{m_{u_3}^2}^{(2)}&=48y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2A_t^2\right )\nonumber\\
+&\quad{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2+(A_t+A_b)^2\right )\nonumber\\
+&\quad{}-\frac{64}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2M_3A_t+2M_3^2\right )\nonumber\\
+&\quad{}-12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2M_2A_t+2M_2^2\right )\nonumber\\
+&\quad{}-\frac{52}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
 &\quad{}+96g_3^4M_3^2-\frac{264}{25}g_1^4\left ( \mathcal{S}+4M_1^2\right ),\label{eq:MSSMmu32b2}\\
@@
 \end{subequations}
-Similarly we can obtain the two-loop $\beta$ functions and
+We can similarly obtain the two-loop $\beta$ functions and
 coefficients $b_p^{(2)}$ for a general set of $U(1)'$
-charges.
-
- Two-loop RGEs for the gauge and Yukawa couplings, gaugino masses and
+charges. Two-loop RGEs for the gauge and Yukawa couplings, gaugino masses and
 soft trilinears, along with the one-loop RGEs for the soft scalar
@@
 to be generated during RGE evolution and this is the case in the
-models we consider here \footnote{In E$_6$ inspired models with only
-  complete $27$plet matter multiplets this trace would vanish.
+models we consider here \footnote{In $E_6$ inspired models with only
+  complete $27$-plet matter multiplets this trace would vanish.
   However since we assume some incomplete multiplets so that our
@@
 the GUT scale the radiatively generated gauge kinetic mixing gives an
-off diagonal gauge coupling, $g_{11}$ of just $\approx 0.02$ at the
+off diagonal gauge coupling, $g_{11}$, of just $\approx 0.02$ at the
 electroweak scale \cite{King:2005jy} and so it does not play a large
@@
 expressions become very large and unmanageable, so we neglected the
-gauge kinetic mixing by setting the SARAH flag NoU1Mixing to true.
-
-At tree level in the EWSB
-conditions the parameters that must be considered are $\lambda$,
+gauge kinetic mixing by setting the SARAH flag \texttt{NoU1Mixing} to true.
+
+At tree level in the EWSB conditions the parameters that must be considered are $\lambda$,
 $A_\lambda$, $m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and
@@
 \beta_{g_1}^{(1)}&=\frac{48}{5}g_1^3,\label{eq:USSMg1BetaOneLoop}\\
-\beta_{g_1}^{(2)}&=\frac{2}{25} g_1^3 \left(30 g_1'^2 \Pi_{Q}^Y-35 y_b^2+117 g_1^2+135 g_2^2+300 g_3^2-10 \Sigma _{\kappa }-15
-   \Sigma _{\lambda }-65 y_t^2-45 y_{\tau }^2\right),\label{eq:USSMg1BetaTwoLoop}\\
+\beta_{g_1}^{(2)}&=\frac{2}{25} g_1^3 \left(30 g_1'^2 \Pi_{Q}^Y+117 g_1^2+135 g_2^2+300 g_3^2-10 \Sigma _{\kappa }-15
+   \Sigma _{\lambda }-65 y_t^2-35 y_b^2-45 y_{\tau }^2\right),\label{eq:USSMg1BetaTwoLoop}\\
 \beta_{g_2}^{(1)}&=4g_2^3,\label{eq:USSMg2BetaOneLoop}\\
-\beta_{g_2}^{(2)}&=\frac{2}{5} g_2^3 \left(5 g_1'^2 \Pi _{Q}^L-15 y_b^2+9 g_1^2+115 g_2^2+60 g_3^2-5 \Sigma _{\lambda }-15
-   y_t^2-5 y_{\tau }^2\right),\label{eq:USSMg2BetaTwoLoop}\\
+\beta_{g_2}^{(2)}&=\frac{2}{5} g_2^3 \left(5 g_1'^2 \Pi _{Q}^L+9 g_1^2+115 g_2^2+60 g_3^2-5 \Sigma _{\lambda }-15 y_t^2-15 y_b^2-5 y_{\tau }^2\right),\label{eq:USSMg2BetaTwoLoop}\\
 \beta_{g_1'}^{(1)}&=g_1'^3\Sigma_{Q},\label{eq:USSMg1pBetaOneLoop}\\
@@
 with \footnote{The first of these is the trace which is assumed to vanish in
-  \cite{Martin:1993zk}.  Although we use the NoU1Mixing to neglect
+  \cite{Martin:1993zk}.  Although we use the \texttt{NoU1Mixing} flag to neglect
   gauge kinetic mixing, SARAH does this by removing the RGE for
@@
   zero at all scales by removing all terms involving them from the
-  RGEs.  Therefore some terms with this trace remain and the RGEs here
+  RGEs.  Therefore some terms with this trace remain and the RGEs shown here
   do not reduce to those which one would obtain from
@@
 The expressions in terms of the $E_6$ mixing angle $\theta$ follow from the charge assignments given in Table \ref{tab:E6charges} and hold provided that $U(1)$ mixing is neglected.
-Similarly we will write
+Similarly we write
 \begin{align*}
@@
 \begin{align}
-\Sigma_1&=\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2-m_{Li}^2+m_{H_{ui}}^2-m_{H_{di}}^2+m_{\overline{D}_i}^2-m_{Di}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1}\\
-\Sigma_1'&=\sum_{i=1}^3\left ( 6Q_Qm_{Qi}^2+3Q_um_{ui}^2+3Q_dm_{di}^2+Q_em_{ei}^2+2Q_Lm_{Li}^2+2Q_2m_{H_{ui}}^2+2Q_1m_{H_{di}}^2\right.\nonumber\\
-&\quad{}\left.+Q_Sm_{Si}^2+3Q_{\overline{D}}m_{\overline{D}_i}^2+3Q_Dm_{Di}^2\right )+2Q_{H'}m_{H'}^2+2Q_{\overline{H'}}m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1Pr}
+\Sigma_1&=\sum_{i=1}^3\left ( m_{Q_i}^2-2m_{u_i}^2+m_{d_i}^2+m_{e_i}^2-m_{L_i}^2+m_{H_i^u}^2-m_{H_i^d}^2+m_{\overline{D}_i}^2-m_{D_i}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1}\\
+\Sigma_1'&=\sum_{i=1}^3\left ( 6Q_Qm_{Q_i}^2+3Q_um_{u_i}^2+3Q_dm_{d_i}^2+Q_em_{e_i}^2+2Q_Lm_{L_i}^2+2Q_2m_{H_i^u}^2+2Q_1m_{H_i^d}^2\right.\nonumber\\
+&\quad{}\left.+Q_Sm_{Si}^2+3Q_{\overline{D}}m_{\overline{D}_i}^2+3Q_Dm_{D_i}^2\right )+2Q_{H'}m_{H'}^2+2Q_{\overline{H'}}m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1Pr}
 \end{align}
@@
 \begin{align}
-\beta_{m_{H_d}^2}^{(1)}&=2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+2a_\lambda^2+6y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+6a_b^2\nonumber\\
-&{}+2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+2a_\tau^2-6g_2^2 M_2^2-\frac{6}{5}g_1^2 M_1^2-8Q_1^2g_1'^2 M_1'^2\nonumber\\
+\beta_{m_{H_d}^2}^{(1)}&=2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+2a_\lambda^2+6y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )+6a_b^2\nonumber\\
+&{}+2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )+2a_\tau^2-6g_2^2 M_2^2-\frac{6}{5}g_1^2 M_1^2-8Q_1^2g_1'^2 M_1'^2\nonumber\\
 &{}-\frac{3}{5}g_1^2\Sigma_1+2Q_1g_1'^2\Sigma_1',\label{eq:USSMmHd2BetaOneLoop}\\
-\beta_{m_{H_d}^2}^{(2)}&=-36y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )-12y_\tau^4\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )-72y_b^2a_b^2-24y_\tau^2a_\tau^2\nonumber\\
-&{}-6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )-6\left ( y_t a_b+y_ba_t\right )^2\nonumber\\
+\beta_{m_{H_d}^2}^{(2)}&=-36y_b^4\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )-12y_\tau^4\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )-72y_b^2a_b^2-24y_\tau^2a_\tau^2\nonumber\\
+&{}-6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2\right )-6\left ( y_t a_b+y_ba_t\right )^2\nonumber\\
 &{}-4\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )-8\lambda^2a_\lambda^2-\lambda^2\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{H_i^d}^2\right.\right.\nonumber\\
-&{}\left.\left.+m_{H_i^u}^2\right )+6\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )\right ]-\sum_{i=1}^3\left [ 4\left ( \lambda_i a_{\lambda}+\lambda a_{\lambda_i}\right )^2\right.\nonumber\\
-&{}\left.+6\left ( \kappa_ia_\lambda+\lambda a_{\kappa_i}\right )^2\right ]-6\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )-6\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
-&{}+32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_3^2\right )+32g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
-&{}+\frac{6}{5}g_1^2y_t^2\left ( 3m_{H_u}^2+m_{Q3}^2-4m_{u3}^2\right )-\frac{2}{5}g_1^2y_b^2\left ( 11m_{H_d}^2-m_{Q3}^2-4m_{d3}^2+4M_1^2\right )\nonumber\\
-&{}-\frac{4}{5}g_1^2\left ( a_b^2-2y_ba_bM_1\right )+\frac{6}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+4m_{e3}^2+4M_1^2\right )+\frac{12}{5}g_1^2\left ( a_\tau^2-2y_\tau a_\tau M_1\right )\nonumber\\
-&{}+\frac{6}{5}g_1^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )+\kappa_i^2\left ( m_{\overline{D}i}^2-m_{Di}^2\right )\right ]+12g_1'^2y_b^2\left ( Q_Q^2+Q_d^2-Q_1^2\right )\times\nonumber\\
-&{}\times\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1'^2\right )+12g_1'^2\left ( Q_Q^2+Q_d^2-Q_1^2\right )\left ( a_b^2-2y_ba_bM_1'\right )\nonumber\\
-&{}-24Q_1g_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )+4g_1'^2y_\tau^2\left ( Q_L^2+Q_e^2-Q_1^2\right )\times\nonumber\\
-&{}\times\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2M_1'^2\right )+4g_1'^2\left ( Q_L^2+Q_e^2-Q_1^2\right )\left ( a_\tau^2-2y_\tau a_\tau M_1'\right )\nonumber\\
-&{}-8Q_1g_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )-24Q_1g_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )\nonumber\\
+&{}\left.\left.+m_{H_i^u}^2\right )+6\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )\right ]-\sum_{i=1}^3\left [ 4\left ( \lambda_i a_{\lambda}+\lambda a_{\lambda_i}\right )^2\right.\nonumber\\
+&{}\left.+6\left ( \kappa_ia_\lambda+\lambda a_{\kappa_i}\right )^2\right ]-6\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )-6\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
+&{}+32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_3^2\right )+32g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
+&{}+\frac{6}{5}g_1^2y_t^2\left ( 3m_{H_u}^2+m_{Q_3}^2-4m_{u_3}^2\right )-\frac{2}{5}g_1^2y_b^2\left ( 11m_{H_d}^2-m_{Q_3}^2-4m_{d_3}^2+4M_1^2\right )\nonumber\\
+&{}-\frac{4}{5}g_1^2\left ( a_b^2-2y_ba_bM_1\right )+\frac{6}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2+4m_{e_3}^2+4M_1^2\right )+\frac{12}{5}g_1^2\left ( a_\tau^2-2y_\tau a_\tau M_1\right )\nonumber\\
+&{}+\frac{6}{5}g_1^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )+\kappa_i^2\left ( m_{\overline{D}_i}^2-m_{D_i}^2\right )\right ]+12g_1'^2y_b^2\left ( Q_Q^2+Q_d^2-Q_1^2\right )\times\nonumber\\
+&{}\times\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_1'^2\right )+12g_1'^2\left ( Q_Q^2+Q_d^2-Q_1^2\right )\left ( a_b^2-2y_ba_bM_1'\right )\nonumber\\
+&{}-24Q_1g_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q_3}^2+Q_dm_{d_3}^2\right )+4g_1'^2y_\tau^2\left ( Q_L^2+Q_e^2-Q_1^2\right )\times\nonumber\\
+&{}\times\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+2M_1'^2\right )+4g_1'^2\left ( Q_L^2+Q_e^2-Q_1^2\right )\left ( a_\tau^2-2y_\tau a_\tau M_1'\right )\nonumber\\
+&{}-8Q_1g_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L_3}^2+Q_em_{e_3}^2\right )-24Q_1g_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q_3}^2+Q_um_{u_3}^2\right )\nonumber\\
 &{}+4g_1'^2\lambda^2\left ( Q_2^2+Q_S^2-Q_1^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )+4g_1'^2\left ( Q_2^2+Q_S^2-Q_1^2\right )\times\nonumber\\
 &{}\times\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )-4Q_1g_1'^2\sum_{i=1}^3\left [ 2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )\right.\nonumber\\
-&{}\left.+3\kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )\right ]-\frac{16}{5}g_3^2g_1^2\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{\overline{D}i}^2-m_{Di}^2\right )\nonumber\\
-&{}+32Q_1g_3^2g_1'^2\sum_{i=1}^3\left ( 2Q_Qm_{Qi}^2+Q_um_{ui}^2+Q_dm_{di}^2+Q_{\overline{D}}m_{\overline{D}i}^2+Q_Dm_{Di}^2\right )\nonumber\\
-&{}+3g_2^4\left [ 29M_2^2+m_{H'}^2+m_{\overline{H'}}^2+\sum_{i=1}^3\left ( 3m_{Qi}^2+m_{Li}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
-&{}+\frac{9}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2\right )+m_{H'}^2-m_{\overline{H'}}^2-\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
+&{}\left.+3\kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )\right ]-\frac{16}{5}g_3^2g_1^2\sum_{i=1}^3\left ( m_{Q_i}^2-2m_{u_i}^2+m_{d_i}^2+m_{\overline{D}_i}^2-m_{D_i}^2\right )\nonumber\\
+&{}+32Q_1g_3^2g_1'^2\sum_{i=1}^3\left ( 2Q_Qm_{Q_i}^2+Q_um_{u_i}^2+Q_dm_{d_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2+Q_Dm_{D_i}^2\right )\nonumber\\
+&{}+3g_2^4\left [ 29M_2^2+m_{H'}^2+m_{\overline{H'}}^2+\sum_{i=1}^3\left ( 3m_{Q_i}^2+m_{L_i}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
+&{}+\frac{9}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2\right )+m_{H'}^2-m_{\overline{H'}}^2-\sum_{i=1}^3\left ( m_{Q_i}^2-m_{L_i}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
 &{}+12Q_1g_2^2g_1'^2\bigg [ 2Q_1\left ( M_1'^2+M_1'M_2+M_2^2\right )+Q_{H'}m_{H'}^2+Q_{\overline{H'}}m_{\overline{H'}}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Qi}^2+Q_Lm_{Li}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{25}g_1^4\bigg [ 891M_1^2+18m_{H'}^2\nonumber\\
-&{}+2\sum_{i=1}^3\left ( m_{di}^2+5m_{Di}^2+m_{\overline{D}i}^2-9m_{ei}^2+9m_{H_i^d}^2+9m_{Li}^2+m_{Qi}^2+28m_{ui}^2\right )\bigg ]\nonumber\\
+&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Q_i}^2+Q_Lm_{L_i}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{25}g_1^4\bigg [ 891M_1^2+18m_{H'}^2\nonumber\\
+&{}+2\sum_{i=1}^3\left ( m_{d_i}^2+5m_{D_i}^2+m_{\overline{D}_i}^2-9m_{e_i}^2+9m_{H_i^d}^2+9m_{L_i}^2+m_{Q_i}^2+28m_{u_i}^2\right )\bigg ]\nonumber\\
 &{}-\frac{4}{5}g_1^2g_1'^2\bigg [ 6Q_1\big ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-4Q_1+3Q_2+Q_{\overline{H'}}-Q_{H'}-3Q_L\nonumber\\
 &{}+3Q_Q-6Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}^2m_{H'}^2\nonumber\\
-&{}+3\sum_{i=1}^3\big ( Q_d^2m_{di}^2+Q_{\overline{D}}^2m_{\overline{D}i}^2-Q_D^2m_{Di}^2+Q_e^2m_{ei}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2-Q_L^2m_{Li}^2\nonumber\\
-&{}+Q_Q^2m_{Qi}^2-2Q_u^2m_{ui}^2\big )+3Q_1Q_{\overline{H'}}m_{\overline{H'}}^2-9Q_1Q_{H'}m_{H'}^2+Q_1\sum_{i=1}^3\bigg ( 4Q_dm_{di}^2+4Q_{\overline{D}}m_{\overline{D}i}^2\nonumber\\
-&{}-8Q_Dm_{Di}^2-9Q_1m_{H_i^d}^2+3Q_2m_{H_i^u}^2-9Q_Lm_{Li}^2+5Q_Qm_{Qi}^2-20Q_um_{ui}^2\big )\bigg ]\nonumber\\
+&{}+3\sum_{i=1}^3\big ( Q_d^2m_{d_i}^2+Q_{\overline{D}}^2m_{\overline{D}_i}^2-Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2-Q_L^2m_{L_i}^2\nonumber\\
+&{}+Q_Q^2m_{Q_i}^2-2Q_u^2m_{u_i}^2\big )+3Q_1Q_{\overline{H'}}m_{\overline{H'}}^2-9Q_1Q_{H'}m_{H'}^2+Q_1\sum_{i=1}^3\bigg ( 4Q_dm_{d_i}^2+4Q_{\overline{D}}m_{\overline{D}_i}^2\nonumber\\
+&{}-8Q_Dm_{D_i}^2-9Q_1m_{H_i^d}^2+3Q_2m_{H_i^u}^2-9Q_Lm_{L_i}^2+5Q_Qm_{Q_i}^2-20Q_um_{u_i}^2\big )\bigg ]\nonumber\\
 &{}+8Q_1g_1'^4\bigg [ 3Q_1M_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+8Q_1^2+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2\nonumber\\
-&{}+18Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^3m_{di}^2+3Q_{\overline{D}}^3m_{\overline{D}i}^2+3Q_D^3m_{Di}^2\nonumber\\
-&{}+Q_e^3m_{ei}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{Li}^2+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )\nonumber\\
-&{}+2Q_1Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_1Q_{H'}m_{H'}^2+Q_1\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2\nonumber\\
-&{}+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmHd2BetaTwoLoop}\\
-b_{m_{H_d}^2}^{(2)}&=72y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+144y_b^2a_b^2+16y_\tau^4\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+32y_\tau^2 a_\tau^2\nonumber\\
-&{}+8\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+16\lambda^2 a_\lambda^2+6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )\nonumber\\
-&{}+6\left ( y_t a_b+y_b a_t\right )^2+12y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{d3}^2+m_{L3}^2+m_{e3}^2\right )+12\left ( y_b a_\tau + y_\tau a_b\right )^2\nonumber\\
-&{}+6\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )+6\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
-&{}+12\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )+12\left ( \lambda a_b+y_b a_\lambda\right )^2\nonumber\\
-&{}+4\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )+4\left ( \lambda a_\tau + y_\tau a_\lambda\right )^2\nonumber\\
+&{}+18Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^3m_{d_i}^2+3Q_{\overline{D}}^3m_{\overline{D}_i}^2+3Q_D^3m_{D_i}^2\nonumber\\
+&{}+Q_e^3m_{e_i}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{L_i}^2+6Q_Q^3m_{Q_i}^2+Q_S^3m_{Si}^2+3Q_u^3m_{u_i}^2\big )\nonumber\\
+&{}+2Q_1Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_1Q_{H'}^2m_{H'}^2+Q_1\sum_{i=1}^3\big ( 3Q_d^2m_{d_i}^2+3Q_{\overline{D}}^2m_{\overline{D}_i}^2+3Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2\nonumber\\
+&{}+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{L_i}^2+6Q_Q^2m_{Q_i}^2+Q_S^2m_{Si}^2+3Q_u^2m_{u_i}^2\big )\bigg ],\label{eq:USSMmHd2BetaTwoLoop}\\
+b_{m_{H_d}^2}^{(2)}&=72y_b^4\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )+144y_b^2a_b^2+16y_\tau^4\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )+32y_\tau^2 a_\tau^2\nonumber\\
+&{}+8\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+16\lambda^2 a_\lambda^2+6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2\right )\nonumber\\
+&{}+6\left ( y_t a_b+y_b a_t\right )^2+12y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+m_{L_3}^2+m_{e_3}^2\right )+12\left ( y_b a_\tau + y_\tau a_b\right )^2\nonumber\\
+&{}+6\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )+6\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
+&{}+12\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{d_3}^2\right )+12\left ( \lambda a_b+y_b a_\lambda\right )^2\nonumber\\
+&{}+4\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L_3}^2+m_{e_3}^2\right )+4\left ( \lambda a_\tau + y_\tau a_\lambda\right )^2\nonumber\\
 &{}+4\sum_{i=1}^3\left [ \lambda^2\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_{H_d}^2+m_{H_u}^2+2m_S^2\right )+\left ( \lambda a_{\lambda_i}+\lambda_i a_\lambda\right )^2\right ]\nonumber\\
-&{}+6\sum_{i=1}^3\left [ \lambda^2\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+\left ( \lambda a_{\kappa_i}+\kappa_i a_\lambda\right )^2\right ]\nonumber\\
-&{}-32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_3^2\right )-32g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
-&{}-18g_2^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_2^2\right )-18g_2^2\left ( a_b^2-2y_ba_bM_2\right )\nonumber\\
-&{}-6g_2^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2M_2^2\right )-6g_2^2\left ( a_\tau^2-2y_\tau a_\tau M_2\right )\nonumber\\
+&{}+6\sum_{i=1}^3\left [ \lambda^2\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+\left ( \lambda a_{\kappa_i}+\kappa_i a_\lambda\right )^2\right ]\nonumber\\
+&{}-32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_3^2\right )-32g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
+&{}-18g_2^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_2^2\right )-18g_2^2\left ( a_b^2-2y_ba_bM_2\right )\nonumber\\
+&{}-6g_2^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+2M_2^2\right )-6g_2^2\left ( a_\tau^2-2y_\tau a_\tau M_2\right )\nonumber\\
 &{}-6g_2^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_2^2\right )-6g_2^2\left ( a_\lambda^2-2\lambda a_\lambda M_2\right )\nonumber\\
-&{}-\frac{14}{5}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1^2\right )-\frac{14}{5}g_1^2\left ( a_b^2-2y_ba_bM_1\right )\nonumber\\
-&{}-\frac{18}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2M_1^2\right )-\frac{18}{5}g_1^2\left ( a_\tau^2-2y_\tau a_\tau M_1\right )\nonumber\\
+&{}-\frac{14}{5}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_1^2\right )-\frac{14}{5}g_1^2\left ( a_b^2-2y_ba_bM_1\right )\nonumber\\
+&{}-\frac{18}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+2M_1^2\right )-\frac{18}{5}g_1^2\left ( a_\tau^2-2y_\tau a_\tau M_1\right )\nonumber\\
 &{}-\frac{6}{5}g_1^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1^2\right )-\frac{6}{5}g_1^2\left ( a_\lambda^2-2\lambda a_\lambda M_1\right )\nonumber\\
-&{}-12g_1'^2y_b^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1'^2\right )-12g_1'^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\times\nonumber\\
-&{}\times\left ( a_b^2-2y_b a_b M_1'\right )+6g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( 2Q_1m_{H_d}^2+2Q_1m_{Q3}^2+2Q_1m_{d3}^2+\Sigma_1'\right )\nonumber\\
-&{}+12Q_1g_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )-4g_1'^2y_\tau^2\left ( Q_1^2+Q_L^2+Q_e^2\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2M_1'^2\right )\nonumber\\
+&{}-12g_1'^2y_b^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_1'^2\right )-12g_1'^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\times\nonumber\\
+&{}\times\left ( a_b^2-2y_b a_b M_1'\right )+6g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( 2Q_1m_{H_d}^2+2Q_1m_{Q_3}^2+2Q_1m_{d_3}^2+\Sigma_1'\right )\nonumber\\
+&{}+12Q_1g_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )-4g_1'^2y_\tau^2\left ( Q_1^2+Q_L^2+Q_e^2\right )\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+2M_1'^2\right )\nonumber\\
 &{}-4g_1'^2\left ( Q_1^2+Q_L^2+Q_e^2\right )\left ( a_\tau^2-2y_\tau a_\tau M_1'\right )+2g_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\times\nonumber\\
-&{}\times\left ( 2Q_1m_{H_d}^2+2Q_1m_{L3}^2+2Q_1m_{e3}^2+\Sigma_1'\right )+4Q_1g_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
-&{}+12Q_1g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+12Q_1g_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )\nonumber\\
+&{}\times\left ( 2Q_1m_{H_d}^2+2Q_1m_{L_3}^2+2Q_1m_{e_3}^2+\Sigma_1'\right )+4Q_1g_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
+&{}+12Q_1g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )+12Q_1g_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )\nonumber\\
 &{}-4g_1'^2\lambda^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )-4g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\times\nonumber\\
@@
 &{}\times\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+a_{\lambda_i}^2\right ]+6Q_1g_1'^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\times\nonumber\\
-&{}\times\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+a_{\kappa_i}^2\right ]-96Q_1g_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )\nonumber\\
+&{}\times\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+a_{\kappa_i}^2\right ]-96Q_1g_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )\nonumber\\
 &{}-72g_2^4M_2^2-12Q_1g_2^2g_1'^2M_2^2\left ( 9Q_Q+3Q_L+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\right )\nonumber\\
@@
 \begin{align}
-\beta_{m_{H_u}^2}^{(1)}&=2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+2a_\lambda^2+6y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+6a_t^2\nonumber\\
+\beta_{m_{H_u}^2}^{(1)}&=2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+2a_\lambda^2+6y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )+6a_t^2\nonumber\\
 &{}-6g_2^2M_2^2-\frac{6}{5}g_1^2M_1^2-8Q_2^2g_1'^2M_1'^2+\frac{3}{5}g_1^2\Sigma_1+2Q_2g_1'^2\Sigma_1',\label{eq:USSMmHu2BetaOneLoop}\\
-\beta_{m_{H_u}^2}^{(2)}&=-36y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )-6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )\nonumber\\
+\beta_{m_{H_u}^2}^{(2)}&=-36y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )-6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2\right )\nonumber\\
 &{}-72y_t^2a_t^2-6\left ( y_ta_b+y_ba_t\right )^2-4\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )-8\lambda^2a_{\lambda}^2\nonumber\\
 &{}-\lambda^2\sum_{i=1}^3\bigg [ 4\lambda_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\nonumber\\
-&{}+6\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )\bigg ]-\sum_{i=1}^3 \big [4\left ( \lambda_ia_{\lambda}+\lambda a_{\lambda_i}\right )^2\nonumber\\
-&{}+6\left ( \kappa_i a_{\lambda}+\lambda a_{\kappa_i}\right )^2\big ]-6\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
-&{}-2\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )-6\left ( \lambda a_b+y_ba_{\lambda}\right )^2-2\left ( \lambda a_\tau+y_\tau a_{\lambda}\right )^2\nonumber\\
-&{}+32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_3^2\right )+32g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
-&{}+\frac{2}{5}g_1^2y_t^2\left ( -5m_{H_u}^2+m_{Q3}^2+16m_{u3}^2+8M_1^2\right )+\frac{8}{5}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
-&{}+\frac{6}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q3}^2-2m_{d3}^2\right )+\frac{6}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
-&{}+\frac{6}{5}g_1^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )+\kappa_i^2\left ( m_{Di}^2-m_{\overline{D}i}^2\right )\right ]\nonumber\\
-&{}+12g_1'^2y_t^2\left ( Q_Q^2+Q_u^2-Q_2^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )\nonumber\\
-&{}+12g_1'^2\left ( Q_Q^2+Q_u^2-Q_2^2\right )\left ( a_t^2-2y_ta_tM_1'\right )-24Q_2g_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )\nonumber\\
-&{}-24Q_2g_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )-8Q_2g_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )\nonumber\\
+&{}+6\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )\bigg ]-\sum_{i=1}^3 \big [4\left ( \lambda_ia_{\lambda}+\lambda a_{\lambda_i}\right )^2\nonumber\\
+&{}+6\left ( \kappa_i a_{\lambda}+\lambda a_{\kappa_i}\right )^2\big ]-6\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{d_3}^2\right )\nonumber\\
+&{}-2\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L_3}^2+m_{e_3}^2\right )-6\left ( \lambda a_b+y_ba_{\lambda}\right )^2-2\left ( \lambda a_\tau+y_\tau a_{\lambda}\right )^2\nonumber\\
+&{}+32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_3^2\right )+32g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
+&{}+\frac{2}{5}g_1^2y_t^2\left ( -5m_{H_u}^2+m_{Q_3}^2+16m_{u_3}^2+8M_1^2\right )+\frac{8}{5}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
+&{}+\frac{6}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q_3}^2-2m_{d_3}^2\right )+\frac{6}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2-2m_{e_3}^2\right )\nonumber\\
+&{}+\frac{6}{5}g_1^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )+\kappa_i^2\left ( m_{D_i}^2-m_{\overline{D}_i}^2\right )\right ]\nonumber\\
+&{}+12g_1'^2y_t^2\left ( Q_Q^2+Q_u^2-Q_2^2\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1'^2\right )\nonumber\\
+&{}+12g_1'^2\left ( Q_Q^2+Q_u^2-Q_2^2\right )\left ( a_t^2-2y_ta_tM_1'\right )-24Q_2g_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q_3}^2+Q_um_{u_3}^2\right )\nonumber\\
+&{}-24Q_2g_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q_3}^2+Q_dm_{d_3}^2\right )-8Q_2g_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L_3}^2+Q_em_{e_3}^2\right )\nonumber\\
 &{}+4g_1'^2\lambda^2\left ( Q_1^2-Q_2^2+Q_S^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )\nonumber\\
 &{}+4g_1'^2\left ( Q_1^2-Q_2^2+Q_S^2\right )\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )\nonumber\\
-&{}-4Q_2g_1'^2\sum_{i=1}^3\left [ 2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )+3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2\right )\right ]\nonumber\\
-&{}+\frac{16}{5}g_3^2g_1^2\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{\overline{D}i}^2-m_{Di}^2\right )\nonumber\\
-&{}+32Q_2g_3^2g_1'^2\sum_{i=1}^3\left ( 2Q_Qm_{Qi}^2+Q_um_{ui}^2+Q_dm_{di}^2+Q_{\overline{D}}m_{\overline{D}i}^2+Q_Dm_{Di}^2\right )\nonumber\\
-&{}+3g_2^4\left [ 29M_2^2+m_{H'}^2+m_{\overline{H'}}^2+\sum_{i=1}^3\left ( 3m_{Qi}^2+m_{Li}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
-&{}+\frac{9}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2\right )+m_{\overline{H'}}^2-m_{H'}^2+\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
+&{}-4Q_2g_1'^2\sum_{i=1}^3\left [ 2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )+3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{D_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2\right )\right ]\nonumber\\
+&{}+\frac{16}{5}g_3^2g_1^2\sum_{i=1}^3\left ( m_{Q_i}^2-2m_{u_i}^2+m_{d_i}^2+m_{\overline{D}_i}^2-m_{D_i}^2\right )\nonumber\\
+&{}+32Q_2g_3^2g_1'^2\sum_{i=1}^3\left ( 2Q_Qm_{Q_i}^2+Q_um_{u_i}^2+Q_dm_{d_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2+Q_Dm_{D_i}^2\right )\nonumber\\
+&{}+3g_2^4\left [ 29M_2^2+m_{H'}^2+m_{\overline{H'}}^2+\sum_{i=1}^3\left ( 3m_{Q_i}^2+m_{L_i}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
+&{}+\frac{9}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2\right )+m_{\overline{H'}}^2-m_{H'}^2+\sum_{i=1}^3\left ( m_{Q_i}^2-m_{L_i}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
 &{}+12Q_2g_2^2g_1'^2\bigg [ 2Q_2\left ( M_1'^2+M_1'M_2+M_2^2\right )+Q_{H'}m_{H'}^2+Q_{\overline{H'}}m_{\overline{H'}}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Qi}^2+Q_Lm_{Li}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{25}g_1^4\bigg [ 891M_1^2+18m_{\overline{H'}}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 10m_{di}^2+2m_{Di}^2+10m_{\overline{D}i}^2+54m_{ei}^2+18m_{H_i^u}^2+4m_{Qi}^2-8m_{ui}^2\right )\bigg ]\nonumber\\
+&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Q_i}^2+Q_Lm_{L_i}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{25}g_1^4\bigg [ 891M_1^2+18m_{\overline{H'}}^2\nonumber\\
+&{}+\sum_{i=1}^3\left ( 10m_{d_i}^2+2m_{D_i}^2+10m_{\overline{D}_i}^2+54m_{e_i}^2+18m_{H_i^u}^2+4m_{Q_i}^2-8m_{u_i}^2\right )\bigg ]\nonumber\\
 &{}+\frac{4}{5}g_1^2g_1'^2\bigg [ 6Q_2\big ( 3Q_d+Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+4Q_2+Q_{\overline{H'}}-Q_{H'}-3Q_L\nonumber\\
-&{}+3Q_Q-6Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}m_{H'}^2\nonumber\\
-&{}+3\sum_{i=1}^3\left ( Q_d^2m_{di}^2+Q_{\overline{D}}^2m_{\overline{D}i}^2-Q_D^2m_{Di}^2+Q_e^2m_{ei}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2-Q_L^2m_{Li}^2\right.\nonumber\\
-&{}\left.+Q_Q^2m_{Qi}^2-2Q_u^2m_{ui}^2\right )+9Q_2Q_{\overline{H'}}m_{\overline{H'}}^2-3Q_2Q_{H'}m_{H'}^2+Q_2\sum_{i=1}^3\left ( 8Q_dm_{di}^2+8Q_{\overline{D}}m_{\overline{D}i}^2\right.\nonumber\\
-&{}\left.-4Q_Dm_{Di}^2+12Q_em_{ei}^2-3Q_1m_{H_i^d}^2+9Q_2m_{H_i^u}^2-3Q_Lm_{Li}^2+7Q_Qm_{Qi}^2-4Q_um_{ui}^2\right )\bigg ]\nonumber\\
+&{}+3Q_Q-6Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}^2m_{H'}^2\nonumber\\
+&{}+3\sum_{i=1}^3\left ( Q_d^2m_{d_i}^2+Q_{\overline{D}}^2m_{\overline{D}_i}^2-Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2-Q_L^2m_{L_i}^2\right.\nonumber\\
+&{}\left.+Q_Q^2m_{Q_i}^2-2Q_u^2m_{u_i}^2\right )+9Q_2Q_{\overline{H'}}m_{\overline{H'}}^2-3Q_2Q_{H'}m_{H'}^2+Q_2\sum_{i=1}^3\left ( 8Q_dm_{d_i}^2+8Q_{\overline{D}}m_{\overline{D}_i}^2\right.\nonumber\\
+&{}\left.-4Q_Dm_{D_i}^2+12Q_em_{e_i}^2-3Q_1m_{H_i^d}^2+9Q_2m_{H_i^u}^2-3Q_Lm_{L_i}^2+7Q_Qm_{Q_i}^2-4Q_um_{u_i}^2\right )\bigg ]\nonumber\\
 &{}+8Q_2g_1'^4\bigg [ 3Q_2M_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2+8Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2\nonumber\\
-&{}+18Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^3m_{di}^2+3Q_{\overline{D}}^3m_{\overline{D}i}^2\nonumber\\
-&{}+3Q_D^3m_{Di}^2+Q_e^3m_{ei}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{Li}^2+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )\nonumber\\
-&{}+2Q_2Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_2Q_{H'}^2m_{H'}^2+Q_2\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2\nonumber\\
-&{}+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmHu2BetaTwoLoop}\\
-b_{m_{H_u}^2}^{(2)}&=72y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+144y_t^2a_t^2+8\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+16\lambda^2a_\lambda^2\nonumber\\
-&{}+6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )+6\left ( y_ta_b+y_ba_t\right )^2\nonumber\\
-&{}+12\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )+12\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
-&{}+6\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )+6\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
-&{}+2\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )+2\left ( \lambda a_\tau+y_\tau a_\lambda\right )^2\nonumber\\
+&{}+18Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^3m_{d_i}^2+3Q_{\overline{D}}^3m_{\overline{D}_i}^2\nonumber\\
+&{}+3Q_D^3m_{D_i}^2+Q_e^3m_{e_i}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{L_i}^2+6Q_Q^3m_{Q_i}^2+Q_S^3m_{Si}^2+3Q_u^3m_{u_i}^2\big )\nonumber\\
+&{}+2Q_2Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_2Q_{H'}^2m_{H'}^2+Q_2\sum_{i=1}^3\big ( 3Q_d^2m_{d_i}^2+3Q_{\overline{D}}^2m_{\overline{D}_i}^2+3Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2\nonumber\\
+&{}+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{L_i}^2+6Q_Q^2m_{Q_i}^2+Q_S^2m_{Si}^2+3Q_u^2m_{u_i}^2\big )\bigg ],\label{eq:USSMmHu2BetaTwoLoop}\\
+b_{m_{H_u}^2}^{(2)}&=72y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )+144y_t^2a_t^2+8\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+16\lambda^2a_\lambda^2\nonumber\\
+&{}+6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2\right )+6\left ( y_ta_b+y_ba_t\right )^2\nonumber\\
+&{}+12\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )+12\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
+&{}+6\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{d_3}^2\right )+6\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
+&{}+2\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L_3}^2+m_{e_3}^2\right )+2\left ( \lambda a_\tau+y_\tau a_\lambda\right )^2\nonumber\\
 &{}+4\sum_{i=1}^3 \left [ \lambda^2\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_{H_d}^2+m_{H_u}^2+2m_S^2\right )+\left ( \lambda a_{\lambda_i}+\lambda_i a_{\lambda}\right )^2\right ] \nonumber\\
-&{}+6\sum_{i=1}^3\left [ \lambda^2\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )
+&{}+6\sum_{i=1}^3\left [ \lambda^2\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )
 +\left ( \lambda a_{\kappa_i}+\kappa_i a_\lambda\right )^2\right ]\nonumber\\
-&{}-32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_3^2\right )-32g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
-&{}-18g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_2^2\right )-18g_2^2\left ( a_t^2-2y_ta_tM_2\right )\\
+&{}-32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_3^2\right )-32g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
+&{}-18g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_2^2\right )-18g_2^2\left ( a_t^2-2y_ta_tM_2\right )\\
 &{}-6g_2^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_2^2\right )-6g_2^2\left ( a_\lambda^2-2\lambda a_\lambda M_2\right )\nonumber\\
-&{}-\frac{26}{5}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1^2\right )-\frac{26}{5}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
+&{}-\frac{26}{5}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1^2\right )-\frac{26}{5}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
 &{}-\frac{6}{5}g_1^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1^2\right )-\frac{6}{5}g_1^2\left ( a_\lambda^2-2\lambda a_\lambda M_1\right )\nonumber\\
-&{}-12g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )-12g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\times\nonumber\\
-&{}\times\left ( a_t^2-2y_ta_tM_1'\right )+6g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 2Q_2m_{H_u}^2+2Q_2m_{Q3}^2+2Q_2m_{u3}^2+\Sigma_1'\right )\nonumber\\
-&{}+12Q_2g_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_2g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
-&{}+12Q_2g_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )+4Q_2g_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )\nonumber\\
+&{}-12g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1'^2\right )-12g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\times\nonumber\\
+&{}\times\left ( a_t^2-2y_ta_tM_1'\right )+6g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 2Q_2m_{H_u}^2+2Q_2m_{Q_3}^2+2Q_2m_{u_3}^2+\Sigma_1'\right )\nonumber\\
+&{}+12Q_2g_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_2g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )\nonumber\\
+&{}+12Q_2g_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )+4Q_2g_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )\nonumber\\
 &{}+4Q_2g_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )-4g_1'^2\lambda^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )\nonumber\\
@@
 &{}+4Q_2g_1'^2\left ( Q_1+Q_2+Q_S\right )\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+a_{\lambda_i}^2\right ]\nonumber\\
-&{}+6Q_2g_1'^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+a_{\kappa_i}^2\right ]\nonumber\\
+&{}+6Q_2g_1'^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+a_{\kappa_i}^2\right ]\nonumber\\
 &{}-96Q_2g_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )-72g_2^4M_2^2\nonumber\\
@@
 &{}-8Q_S^2g_1'^2M_1'^2+2Q_Sg_1'^2\Sigma_1',\label{eq:USSMms2BetaOneLoop}\\
-\beta_{m_S^2}^{(2)}&=\sum_{i=1}^3\bigg [ -16\lambda_i^2\left ( m_{H_i^u}^2+m_{H_i^d}^2+m_S^2 \right )-24\kappa_i^2\left ( m_{Di}^2+m_{\overline{D}i}^2+m_S^2 \right )\nonumber\\
-&{}-32\lambda_i^2a_{\lambda_i}^2-48\kappa_i^2a_{\kappa_i}^2\bigg ]-12\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )\nonumber\\
-&{}-12\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
-&{}-4\lambda^2y_\tau^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )-12\left ( \lambda a_t+y_ta_\lambda\right )^2-12\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
-&{}-4\left ( \lambda a_\tau+y_\tau a_\lambda\right )^2+32g_3^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_3^2\right )+a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_3 \right ]\nonumber\\
+\beta_{m_S^2}^{(2)}&=\sum_{i=1}^3\bigg [ -16\lambda_i^4\left ( m_{H_i^u}^2+m_{H_i^d}^2+m_S^2 \right )-24\kappa_i^4\left ( m_{D_i}^2+m_{\overline{D}_i}^2+m_S^2 \right )\nonumber\\
+&{}-32\lambda_i^2a_{\lambda_i}^2-48\kappa_i^2a_{\kappa_i}^2\bigg ]-12\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )\nonumber\\
+&{}-12\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{d_3}^2\right )\nonumber\\
+&{}-4\lambda^2y_\tau^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{L_3}^2+m_{e_3}^2\right )-12\left ( \lambda a_t+y_ta_\lambda\right )^2-12\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
+&{}-4\left ( \lambda a_\tau+y_\tau a_\lambda\right )^2+32g_3^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+2M_3^2\right )+a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_3 \right ]\nonumber\\
 &{}+12g_2^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_2^2\right )+a_{\lambda_i}^2-2\lambda_ia_{\lambda_i}M_2\right ]\nonumber\\
-&{}+\frac{4}{5}g_1^2\sum_{i=1}^3\bigg [ 3\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1^2\right )+2\kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_1^2\right )\nonumber\\
+&{}+\frac{4}{5}g_1^2\sum_{i=1}^3\bigg [ 3\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1^2\right )+2\kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+2M_1^2\right )\nonumber\\
 &{}+3\left (a_{\lambda_i}^2-2\lambda_ia_{\lambda_i}M_1\right )+2\left (a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_1\right )\bigg ]\nonumber\\
@@
 &{}-2Q_S\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )+3\kappa_i^2\left ( Q_D^2+Q_{\overline{D}}^2-Q_S^2\right )\times\nonumber\\
-&{}\times\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_1'^2\right )-3Q_S\kappa_i^2\left ( Q_Sm_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )\nonumber\\
+&{}\times\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+2M_1'^2\right )-3Q_S\kappa_i^2\left ( Q_Sm_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )\nonumber\\
 &{}+2\left ( a_{\lambda_i}^2-2\lambda_ia_{\lambda_i}M_1'\right )\left ( Q_1^2+Q_2^2-Q_S^2\right )+3\left ( a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_1'\right )\left ( Q_D^2+Q_{\overline{D}}^2-Q_S^2\right )\bigg ]\nonumber\\
-&{}-24Q_Sg_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )-24Q_Sg_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )\nonumber\\
-&{}-8Q_Sg_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )+32Q_Sg_3^2g_1'^2\sum_{i=1}^3\big ( 2Q_Qm_{Qi}^2+Q_um_{ui}^2\nonumber\\
-&{}+Q_dm_{di}^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2\big )+12Q_Sg_2^2g_1'^2\bigg [ Q_{\overline{H'}}m_{\overline{H'}}^2+Q_{H'}m_{H'}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Qi}^2+Q_Lm_{Li}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{4}{5}Q_Sg_1^2g_1'^2\bigg [ 3Q_{\overline{H'}}m_{\overline{H'}}^2+3Q_{H'}m_{H'}^2\nonumber\\
-&{}+\sum_{i=1}^3\big ( 2Q_dm_{di}^2+2Q_{\overline{D}}m_{\overline{D}i}^2+2Q_Dm_{Di}^2+6Q_em_{ei}^2+3Q_1m_{H_i^d}^2+3Q_2m_{H_i^u}^2+3Q_Lm_{Li}^2\nonumber\\
-&{}+Q_Qm_{Qi}^2+8Q_um_{ui}^2\big )\bigg ]+8Q_Sg_1'^4\bigg [ 3Q_SM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2+6Q_2^2\nonumber\\
+&{}-24Q_Sg_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q_3}^2+Q_um_{u_3}^2\right )-24Q_Sg_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q_3}^2+Q_dm_{d_3}^2\right )\nonumber\\
+&{}-8Q_Sg_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L_3}^2+Q_em_{e_3}^2\right )+32Q_Sg_3^2g_1'^2\sum_{i=1}^3\big ( 2Q_Qm_{Q_i}^2+Q_um_{u_i}^2\nonumber\\
+&{}+Q_dm_{d_i}^2+Q_Dm_{D_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2\big )+12Q_Sg_2^2g_1'^2\bigg [ Q_{\overline{H'}}m_{\overline{H'}}^2+Q_{H'}m_{H'}^2\nonumber\\
+&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Q_i}^2+Q_Lm_{L_i}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{4}{5}Q_Sg_1^2g_1'^2\bigg [ 3Q_{\overline{H'}}m_{\overline{H'}}^2+3Q_{H'}m_{H'}^2\nonumber\\
+&{}+\sum_{i=1}^3\big ( 2Q_dm_{d_i}^2+2Q_{\overline{D}}m_{\overline{D}_i}^2+2Q_Dm_{D_i}^2+6Q_em_{e_i}^2+3Q_1m_{H_i^d}^2+3Q_2m_{H_i^u}^2+3Q_Lm_{L_i}^2\nonumber\\
+&{}+Q_Qm_{Q_i}^2+8Q_um_{u_i}^2\big )\bigg ]+8Q_Sg_1'^4\bigg [ 3Q_SM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2+6Q_2^2\nonumber\\
 &{}+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2+18Q_Q^2+5Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2\nonumber\\
-&{}+\sum_{i=1}^3\big ( 3Q_d^3m_{di}^2+3Q_{\overline{D}}^3m_{\overline{D}i}^2+3Q_D^3m_{Di}^2+Q_e^3m_{ei}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{Li}^2\nonumber\\
-&{}+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )+2Q_SQ_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_SQ_{H'}m_{H'}^2\nonumber\\
-&{}+Q_S\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2\nonumber\\
-&{}+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMms2BetaTwoLoop}\\
-b_{m_S^2}^{(2)}&=8\sum_{i=1}^3\left [ 2\lambda_i^4\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4\lambda_i^2a_{\lambda_i}^2 +3\kappa_i^4\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+6\kappa_i^2a_{\kappa_i}^2\right ]\nonumber\\
+&{}+\sum_{i=1}^3\big ( 3Q_d^3m_{d_i}^2+3Q_{\overline{D}}^3m_{\overline{D}_i}^2+3Q_D^3m_{D_i}^2+Q_e^3m_{e_i}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{L_i}^2\nonumber\\
+&{}+6Q_Q^3m_{Q_i}^2+Q_S^3m_{Si}^2+3Q_u^3m_{u_i}^2\big )+2Q_SQ_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_SQ_{H'}^2m_{H'}^2\nonumber\\
+&{}+Q_S\sum_{i=1}^3\big ( 3Q_d^2m_{d_i}^2+3Q_{\overline{D}}^2m_{\overline{D}_i}^2+3Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{L_i}^2\nonumber\\
+&{}+6Q_Q^2m_{Q_i}^2+Q_S^2m_{Si}^2+3Q_u^2m_{u_i}^2\big )\bigg ],\label{eq:USSMms2BetaTwoLoop}\\
+b_{m_S^2}^{(2)}&=8\sum_{i=1}^3\left [ 2\lambda_i^4\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4\lambda_i^2a_{\lambda_i}^2 +3\kappa_i^4\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+6\kappa_i^2a_{\kappa_i}^2\right ]\nonumber\\
 &{}+8\sum_{i=1}^3\sum_{j=1}^3\left [ \lambda_i^2\lambda_j^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_{H_j^d}^2+m_{H_j^u}^2+2m_S^2\right )+\left ( \lambda_i a_{\lambda_j}+\lambda_ja_{\lambda_i}\right )^2\right ]\nonumber\\
-&{}+24\sum_{i=1}^3\sum_{j=1}^3\left [ \lambda_i^2\kappa_j^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+\left ( \lambda_ia_{\kappa_j}+\kappa_ja_{\lambda_i}\right )^2\right ]\nonumber\\
-&{}+18\sum_{i=1}^3\sum_{j=1}^3\left [ \kappa_i^2\kappa_j^2\left ( 2m_S^2+m_{Di}^2+m_{\overline{D}i}^2+m_{Dj}^2+m_{\overline{D}j}^2\right )+\left ( \kappa_ia_{\kappa_j}+\kappa_ja_{\kappa_i}\right )^2\right ]\nonumber\\
-&{}+12\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )+12\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2\right.\nonumber\\
-&{}\left.+m_{Q3}^2+m_{d3}^2\right )+4\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )+12\left ( \lambda a_t+y_ta_{\lambda}\right )^2\nonumber\\
-&{}+12\left ( \lambda a_b+y_ba_{\lambda}\right )^2+4\left ( \lambda a_\tau+y_\tau a_{\lambda}\right )^2-32g_3^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_3^2\right )\right.\nonumber\\
+&{}+24\sum_{i=1}^3\sum_{j=1}^3\left [ \lambda_i^2\kappa_j^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+2m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+\left ( \lambda_ia_{\kappa_j}+\kappa_ja_{\lambda_i}\right )^2\right ]\nonumber\\
+&{}+18\sum_{i=1}^3\sum_{j=1}^3\left [ \kappa_i^2\kappa_j^2\left ( 2m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+m_{D_j}^2+m_{\overline{D}_j}^2\right )+\left ( \kappa_ia_{\kappa_j}+\kappa_ja_{\kappa_i}\right )^2\right ]\nonumber\\
+&{}+12\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )+12\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2\right.\nonumber\\
+&{}\left.+m_{Q_3}^2+m_{d_3}^2\right )+4\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L_3}^2+m_{e_3}^2\right )+12\left ( \lambda a_t+y_ta_{\lambda}\right )^2\nonumber\\
+&{}+12\left ( \lambda a_b+y_ba_{\lambda}\right )^2+4\left ( \lambda a_\tau+y_\tau a_{\lambda}\right )^2-32g_3^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+2M_3^2\right )\right.\nonumber\\
 &{}\left.+a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_3\right ]-12g_2^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_2^2\right )+a_{\lambda_i}^2-2\lambda_i a_{\lambda_i}M_2\right ]\nonumber\\
 &{}-\frac{4}{5}g_1^2\sum_{i=1}^3\Big [ 3\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1^2\right )+3a_{\lambda_i}^2-6\lambda_i a_{\lambda_i}M_1\nonumber\\
-&{}+2\kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_1^2\right )+2a_{\kappa_i}^2-4\kappa_i a_{\kappa_i}M_1\Big ]\nonumber\\
+&{}+2\kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+2M_1^2\right )+2a_{\kappa_i}^2-4\kappa_i a_{\kappa_i}M_1\Big ]\nonumber\\
 &{}+2g_1'^2\sum_{i=1}^3\Big [ -4\lambda_i^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1'^2\right )\nonumber\\
@@
 &{}\times\left ( a_{\lambda_i}^2-2\lambda_i a_{\lambda_i}M_1'\right )+2Q_Sa_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )-6\kappa_i^2\left ( Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\times\nonumber\\
-&{}\times\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_1'^2\right )+3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( Q_Sm_S^2+Q_Sm_{Di}^2+Q_Sm_{\overline{D}i}^2+\Sigma_1'\right )\nonumber\\
+&{}\times\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+2M_1'^2\right )+3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( Q_Sm_S^2+Q_Sm_{D_i}^2+Q_Sm_{\overline{D}_i}^2+\Sigma_1'\right )\nonumber\\
 &{}-6\left ( Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\left ( a_{\kappa_i}^2-2\kappa_i a_{\kappa_i}M_1'\right )+3Q_Sa_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\Big ]\nonumber\\
-&{}+12Q_Sg_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+12Q_Sg_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )\nonumber\\
-&{}+12Q_Sg_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+12Q_Sg_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )\nonumber\\
-&{}+4Q_Sg_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+4Q_Sg_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
+&{}+12Q_Sg_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )+12Q_Sg_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )\nonumber\\
+&{}+12Q_Sg_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )+12Q_Sg_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )\nonumber\\
+&{}+4Q_Sg_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )+4Q_Sg_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
 &{}-96Q_Sg_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )-12Q_Sg_2^2g_1'^2M_2^2\big ( 9Q_Q+3Q_L+3Q_1\nonumber\\
@@
 \end{subequations}
-If the one-loop contributions to the effective potential from top and stop loops are also included it is necessary to consider the expansions for $y_t$, $a_t$, $m_{Q3}^2$ and $m_{u3}^2$.
-The necessary expressions for $y_t$ read
+If the one-loop contributions to the effective potential from top and stop loops are also included it is necessary to consider the expansions for $y_t$, $a_t$, $m_{Q_3}^2$ and $m_{u_3}^2$.
+The required expressions for $y_t$ read
 \begin{subequations}
@@
 \end{subequations}
-The one- and two-loop $\beta$ functions and the resulting $O(t^2)$ coefficient for $m_{Q3}^2$ are 
+The one- and two-loop $\beta$ functions and the resulting $O(t^2)$ coefficient for $m_{Q_3}^2$ are 
 \begin{subequations}
 \begin{align}
-\beta_{m_{Q3}^2}^{(1)}&=2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+2a_t^2+2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+2a_b^2\nonumber\\
+\beta_{m_{Q_3}^2}^{(1)}&=2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )+2a_t^2+2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )+2a_b^2\nonumber\\
 &{}-\frac{32}{3}g_3^2M_3^2-6g_2^2M_2^2-\frac{2}{15}g_1^2M_1^2-8Q_Q^2g_1'^2M_1'^2+\frac{1}{5}g_1^2\Sigma_1+2Q_Qg_1'^2\Sigma_1',\label{eq:USSMmq222BetaOneLoop}\\
-\beta_{m_{Q3}^2}^{(2)}&=-20y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2 \right )-20y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2 \right )\nonumber\\
-&{}-2y_\tau^2y_b^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{L3}^2+m_{d3}^2+m_{e3}^2\right )-40y_t^2a_t^2-40y_b^2a_b^2\nonumber\\
-&{}-2\left ( y_ba_\tau+y_\tau a_b\right )^2-2\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )\nonumber\\
-&{}-2\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )-2\left ( \lambda a_t+y_t a_\lambda \right )^2-2\left ( \lambda a_b+y_b a_\lambda \right )^2\nonumber\\
-&{}+\frac{2}{5}g_1^2y_t^2\left ( m_{H_u}^2+3m_{Q3}^2+8m_{u3}^2 +8M_1^2\right )+\frac{8}{5}g_1^2\left ( a_t^2-2y_ta_tM_1 \right )\nonumber\\
-&{}+\frac{2}{5}g_1^2y_b^2\left ( 5m_{H_d}^2+m_{Q3}^2+4M_1^2\right )+\frac{4}{5}g_1^2\left ( a_b^2-2y_ba_bM_1 \right )+\frac{2}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
-&{}+\frac{2}{5}g_1^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_{Di}^2-m_{\overline{D}i}^2\right )+\lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )\right ]\nonumber\\
-&{}+4g_1'^2y_t^2\left ( Q_2^2-Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )\nonumber\\
-&{}+4g_1'^2\left ( Q_2^2-Q_Q^2+Q_u^2\right )\left ( a_t^2 -2y_ta_tM_1'\right )-24Q_Qg_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )\nonumber\\
-&{}+4g_1'^2y_b^2\left ( Q_1^2-Q_Q^2+Q_d^2 \right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1'^2\right )\nonumber\\
-&{}+4g_1'^2\left ( Q_1^2-Q_Q^2+Q_d^2\right )\left ( a_b^2-2y_ba_bM_1'\right )-24Q_Qg_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )\nonumber\\
-&{}-8Q_Qg_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )\nonumber\\
-&{}-4Q_Qg_1'^2\sum_{i=1}^3\left [ 3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2\right )+2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )\right ]\nonumber\\
-&{}+\frac{16}{3}g_3^4\left [ 10M_3^2+\sum_{i=1}^3\left ( 2m_{Qi}^2+m_{ui}^2+m_{di}^2+m_{Di}^2+m_{\overline{D}i}^2\right )\right ]+32g_3^2g_2^2\left ( M_2^2+M_2M_3+M_3^2\right )\nonumber\\
-&{}+\frac{16}{45}g_3^2g_1^2\left [ 2\left ( M_1^2+M_1M_3+M_3^2\right )+3\sum_{i=1}^3\left ( m_{Qi}^2+m_{di}^2-2m_{ui}^2-m_{Di}^2+m_{\overline{D}i}^2\right )\right ]\nonumber\\
-&{}+\frac{32}{3}Q_Qg_3^2g_1'^2\bigg [ 4Q_Q\left ( M_1'^2+M_1'M_3+M_3^2 \right )+3\sum_{i=1}^3\big ( 2Q_Qm_{Qi}^2+Q_um_{ui}^2+Q_dm_{di}^2\nonumber\\
-&{}+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2 \big )\bigg ]+3g_2^4\left [ 29M_2^2+m_{\overline{H'}}^2+m_{H'}^2+\sum_{i=1}^3\left ( 3m_{Qi}^2+m_{Li}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
-&{}+\frac{1}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2 \right )+3m_{\overline{H'}}^2-3m_{H'}^2+3\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
+\beta_{m_{Q_3}^2}^{(2)}&=-20y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2 \right )-20y_b^4\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2 \right )\nonumber\\
+&{}-2y_\tau^2y_b^2\left ( 2m_{H_d}^2+m_{Q_3}^2+m_{L_3}^2+m_{d_3}^2+m_{e_3}^2\right )-40y_t^2a_t^2-40y_b^2a_b^2\nonumber\\
+&{}-2\left ( y_ba_\tau+y_\tau a_b\right )^2-2\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )\nonumber\\
+&{}-2\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{d_3}^2\right )-2\left ( \lambda a_t+y_t a_\lambda \right )^2-2\left ( \lambda a_b+y_b a_\lambda \right )^2\nonumber\\
+&{}+\frac{2}{5}g_1^2y_t^2\left ( m_{H_u}^2+3m_{Q_3}^2+8m_{u_3}^2 +8M_1^2\right )+\frac{8}{5}g_1^2\left ( a_t^2-2y_ta_tM_1 \right )\nonumber\\
+&{}+\frac{2}{5}g_1^2y_b^2\left ( 5m_{H_d}^2+m_{Q_3}^2+4M_1^2\right )+\frac{4}{5}g_1^2\left ( a_b^2-2y_ba_bM_1 \right )+\frac{2}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2-2m_{e_3}^2\right )\nonumber\\
+&{}+\frac{2}{5}g_1^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_{D_i}^2-m_{\overline{D}_i}^2\right )+\lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )\right ]\nonumber\\
+&{}+4g_1'^2y_t^2\left ( Q_2^2-Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1'^2\right )\nonumber\\
+&{}+4g_1'^2\left ( Q_2^2-Q_Q^2+Q_u^2\right )\left ( a_t^2 -2y_ta_tM_1'\right )-24Q_Qg_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q_3}^2+Q_um_{u_3}^2\right )\nonumber\\
+&{}+4g_1'^2y_b^2\left ( Q_1^2-Q_Q^2+Q_d^2 \right )\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_1'^2\right )\nonumber\\
+&{}+4g_1'^2\left ( Q_1^2-Q_Q^2+Q_d^2\right )\left ( a_b^2-2y_ba_bM_1'\right )-24Q_Qg_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q_3}^2+Q_dm_{d_3}^2\right )\nonumber\\
+&{}-8Q_Qg_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L_3}^2+Q_em_{e_3}^2\right )\nonumber\\
+&{}-4Q_Qg_1'^2\sum_{i=1}^3\left [ 3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{D_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2\right )+2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )\right ]\nonumber\\
+&{}+\frac{16}{3}g_3^4\left [ 10M_3^2+\sum_{i=1}^3\left ( 2m_{Q_i}^2+m_{u_i}^2+m_{d_i}^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )\right ]+32g_3^2g_2^2\left ( M_2^2+M_2M_3+M_3^2\right )\nonumber\\
+&{}+\frac{16}{45}g_3^2g_1^2\left [ 2\left ( M_1^2+M_1M_3+M_3^2\right )+3\sum_{i=1}^3\left ( m_{Q_i}^2+m_{d_i}^2-2m_{u_i}^2-m_{D_i}^2+m_{\overline{D}_i}^2\right )\right ]\nonumber\\
+&{}+\frac{32}{3}Q_Qg_3^2g_1'^2\bigg [ 4Q_Q\left ( M_1'^2+M_1'M_3+M_3^2 \right )+3\sum_{i=1}^3\big ( 2Q_Qm_{Q_i}^2+Q_um_{u_i}^2+Q_dm_{d_i}^2\nonumber\\
+&{}+Q_Dm_{D_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2 \big )\bigg ]+3g_2^4\left [ 29M_2^2+m_{\overline{H'}}^2+m_{H'}^2+\sum_{i=1}^3\left ( 3m_{Q_i}^2+m_{L_i}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
+&{}+\frac{1}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2 \right )+3m_{\overline{H'}}^2-3m_{H'}^2+3\sum_{i=1}^3\left ( m_{Q_i}^2-m_{L_i}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
 &{}+12Q_Qg_2^2g_1'^2\bigg [ 2Q_Q\left ( M_1'^2+M_1'M_2+M_2^2\right )+Q_{\overline{H'}}m_{\overline{H'}}^2+Q_{H'}m_{H'}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Qi}^2+Q_Lm_{Li}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{75}g_1^4\bigg [ 289M_1^2+12m_{\overline{H'}}^2-6m_{H'}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 6m_{di}^2-2m_{Di}^2+6m_{\overline{D}i}^2+42m_{ei}^2-6m_{H_i^d}^2+12m_{H_i^u}^2-6m_{Li}^2+2m_{Qi}^2-24m_{ui}^2\right )\bigg ]\nonumber\\
+&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Q_i}^2+Q_Lm_{L_i}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{75}g_1^4\bigg [ 289M_1^2+12m_{\overline{H'}}^2-6m_{H'}^2\nonumber\\
+&{}+\sum_{i=1}^3\left ( 6m_{d_i}^2-2m_{D_i}^2+6m_{\overline{D}_i}^2+42m_{e_i}^2-6m_{H_i^d}^2+12m_{H_i^u}^2-6m_{L_i}^2+2m_{Q_i}^2-24m_{u_i}^2\right )\bigg ]\nonumber\\
 &{}+\frac{4}{15}g_1^2g_1'^2\bigg [ 2Q_Q\big ( 9Q_d+9Q_{\overline{D}}-9Q_D+9Q_e-9Q_1+9Q_2+3Q_{\overline{H'}}-3Q_{H'}-9Q_L\nonumber\\
 &{}+10Q_Q-18Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}^2m_{H'}^2\nonumber\\
-&{}+3\sum_{i=1}^3\big ( Q_d^2m_{di}^2+Q_{\overline{D}}^2m_{\overline{D}i}^2-Q_D^2m_{Di}^2+Q_e^2m_{ei}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2\nonumber\\
-&{}-Q_L^2m_{Li}^2-Q_Q^2m_{Qi}^2-2Q_u^2m_{ui}^2\big )+15Q_QQ_{\overline{H'}}m_{\overline{H'}}^2+3Q_QQ_{H'}m_{H'}^2\nonumber\\
-&{}+Q_Q\sum_{i=1}^3\big ( 12Q_dm_{di}^2+12Q_{\overline{D}}m_{\overline{D}i}^2+24Q_em_{ei}^2+3Q_1m_{H_i^d}^2+15Q_2m_{H_i^u}^2+3Q_Lm_{Li}^2\nonumber\\
-&{}+15Q_Qm_{Qi}^2+12m_{ui}^2\big )\bigg ]+8Q_Qg_1'^4\bigg [ 3Q_QM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2\nonumber\\
+&{}+3\sum_{i=1}^3\big ( Q_d^2m_{d_i}^2+Q_{\overline{D}}^2m_{\overline{D}_i}^2-Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2\nonumber\\
+&{}-Q_L^2m_{L_i}^2-Q_Q^2m_{Q_i}^2-2Q_u^2m_{u_i}^2\big )+15Q_QQ_{\overline{H'}}m_{\overline{H'}}^2+3Q_QQ_{H'}m_{H'}^2\nonumber\\
+&{}+Q_Q\sum_{i=1}^3\big ( 12Q_dm_{d_i}^2+12Q_{\overline{D}}m_{\overline{D}_i}^2+24Q_em_{e_i}^2+3Q_1m_{H_i^d}^2+15Q_2m_{H_i^u}^2+3Q_Lm_{L_i}^2\nonumber\\
+&{}+15Q_Qm_{Q_i}^2+12m_{u_i}^2\big )\bigg ]+8Q_Qg_1'^4\bigg [ 3Q_QM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2\nonumber\\
 &{}+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2+20Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2\nonumber\\
-&{}+\sum_{i=1}^3\big ( 3Q_d^3m_{di}^2+3Q_{\overline{D}}^3m_{\overline{D}i}^2+3Q_D^3m_{Di}^2+Q_e^3m_{ei}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{Li}^2\nonumber\\
-&{}+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )+2Q_QQ_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_QQ_{H'}^2m_{H'}^2\nonumber\\
-&{}+Q_Q\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2\nonumber\\
-&{}+2Q_L^2m_{Li}^2+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmq222BetaTwoLoop}\\
-b_{m_{Q3}^2}^{(2)}&=24y_t^4\left ( m_{H_u^2}+m_{Q3}^2+m_{u3}^2\right )+24y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+48y_t^2a_t^2+48y_b^2a_b^2\nonumber\\
-&{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )+4\left ( y_ta_b+y_ba_t\right )^2\nonumber\\
-&{}+2y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{d3}^2+m_{L3}^2+m_{e3}^2\right )+2\left ( y_\tau a_b+y_ba_\tau\right )^2\nonumber\\
-&{}+2\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )+2\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
-&{}+2\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )+2\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
-&{}-\frac{32}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_3^2\right )-\frac{32}{3}g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
-&{}-\frac{32}{3}g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_3^2\right )-\frac{32}{3}g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
-&{}-6g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_2^2\right )-6g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
-&{}-6g_2^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_2^2\right )-6g_2^2\left ( a_b^2-2y_ba_bM_2\right )\nonumber\\
-&{}-\frac{26}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1^2\right )-\frac{26}{15}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
-&{}-\frac{14}{15}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1^2\right )-\frac{14}{15}g_1^2\left ( a_b^2-2y_ba_bM_1\right )\nonumber\\
-&{}-4g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )-4g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\times\nonumber\\
-&{}\times\left ( a_t^2-2y_ta_tM_1'\right )+2g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 6Q_Qm_{H_u}^2+6Q_Qm_{Q3}^2+6Q_Qm_{u3}^2+\Sigma_1'\right )\nonumber\\
-&{}+12Q_Qg_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )-4g_1'^2y_b^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1'^2\right )\nonumber\\
+&{}+\sum_{i=1}^3\big ( 3Q_d^3m_{d_i}^2+3Q_{\overline{D}}^3m_{\overline{D}_i}^2+3Q_D^3m_{D_i}^2+Q_e^3m_{e_i}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{L_i}^2\nonumber\\
+&{}+6Q_Q^3m_{Q_i}^2+Q_S^3m_{Si}^2+3Q_u^3m_{u_i}^2\big )+2Q_QQ_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_QQ_{H'}^2m_{H'}^2\nonumber\\
+&{}+Q_Q\sum_{i=1}^3\big ( 3Q_d^2m_{d_i}^2+3Q_{\overline{D}}^2m_{\overline{D}_i}^2+3Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2\nonumber\\
+&{}+2Q_L^2m_{L_i}^2+6Q_Q^2m_{Q_i}^2+Q_S^2m_{Si}^2+3Q_u^2m_{u_i}^2\big )\bigg ],\label{eq:USSMmq222BetaTwoLoop}\\
+b_{m_{Q_3}^2}^{(2)}&=24y_t^4\left ( m_{H_u^2}+m_{Q_3}^2+m_{u_3}^2\right )+24y_b^4\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )+48y_t^2a_t^2+48y_b^2a_b^2\nonumber\\
+&{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2\right )+4\left ( y_ta_b+y_ba_t\right )^2\nonumber\\
+&{}+2y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+m_{L_3}^2+m_{e_3}^2\right )+2\left ( y_\tau a_b+y_ba_\tau\right )^2\nonumber\\
+&{}+2\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )+2\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
+&{}+2\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{d_3}^2\right )+2\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
+&{}-\frac{32}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_3^2\right )-\frac{32}{3}g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
+&{}-\frac{32}{3}g_3^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_3^2\right )-\frac{32}{3}g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
+&{}-6g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_2^2\right )-6g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
+&{}-6g_2^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_2^2\right )-6g_2^2\left ( a_b^2-2y_ba_bM_2\right )\nonumber\\
+&{}-\frac{26}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1^2\right )-\frac{26}{15}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
+&{}-\frac{14}{15}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_1^2\right )-\frac{14}{15}g_1^2\left ( a_b^2-2y_ba_bM_1\right )\nonumber\\
+&{}-4g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1'^2\right )-4g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\times\nonumber\\
+&{}\times\left ( a_t^2-2y_ta_tM_1'\right )+2g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 6Q_Qm_{H_u}^2+6Q_Qm_{Q_3}^2+6Q_Qm_{u_3}^2+\Sigma_1'\right )\nonumber\\
+&{}+12Q_Qg_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )-4g_1'^2y_b^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_1'^2\right )\nonumber\\
 &{}-4g_1'^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( a_b^2-2y_ba_bM_1'\right )+2g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\times\nonumber\\
-&{}\times\left ( 6Q_Qm_{H_d}^2+6Q_Qm_{Q3}^2+6Q_Qm_{d3}^2+\Sigma_1'\right )+12Q_Qg_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )\nonumber\\
-&{}+4Q_Qg_1'^2y_\tau^2\left (Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+4Q_Qg_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
+&{}\times\left ( 6Q_Qm_{H_d}^2+6Q_Qm_{Q_3}^2+6Q_Qm_{d_3}^2+\Sigma_1'\right )+12Q_Qg_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )\nonumber\\
+&{}+4Q_Qg_1'^2y_\tau^2\left (Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )+4Q_Qg_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
 &{}+2Q_Qg_1'^2\sum_{i=1}^3\Big [ 2\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+2a_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )\nonumber\\
-&{}+3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+3a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\Big ]\nonumber\\
+&{}+3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+3a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\Big ]\nonumber\\
 &{}-96Q_Qg_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )-72g_2^4M_2^2\nonumber\\
@@
 \end{subequations}
-Finally, the relevant expressions for the soft mass $m_{u3}^2$ read
+Finally, the relevant expressions for the soft mass $m_{u_3}^2$ read
 \begin{subequations}
 \begin{align}
-\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+4a_t^2-\frac{32}{3}g_3^2M_3^2-\frac{32}{15}g_1^2M_1^2-8Q_u^2g_1'^2M_1'^2\nonumber\\
+\beta_{m_{u_3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )+4a_t^2-\frac{32}{3}g_3^2M_3^2-\frac{32}{15}g_1^2M_1^2-8Q_u^2g_1'^2M_1'^2\nonumber\\
 &{}-\frac{4}{5}g_1^2\Sigma_1+2Q_ug_1'^2\Sigma_1',\label{eq:USSMmu222BetaOneLoop}\\
-\beta_{m_{u3}^2}^{(2)}&=-32y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )-4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )\nonumber\\
-&{}-64y_t^2a_t^2-4\left ( y_ta_b+y_ba_t\right )^2-4\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )\nonumber\\
-&{}-4\left ( \lambda a_t + y_ta_\lambda \right )^2+12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_2^2\right )+12g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
-&{}-\frac{4}{5}g_1^2y_t^2\left ( -5m_{H_u}^2-m_{Q3}^2+9m_{u3}^2+2M_1^2\right )-\frac{4}{5}g_1^2\left ( a_t^2-2y_ta_tM_1 \right )\nonumber\\
-&{}-\frac{8}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q3}^2-2m_{d3}^2\right )-\frac{8}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
-&{}-\frac{8}{5}g_1^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_{Di}^2-m_{\overline{D}i}^2 \right )+\lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2 \right )\right ]\nonumber\\
-&{}+8g_1'^2y_t^2\left ( Q_2^2+Q_Q^2-Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )\nonumber\\
-&{}+8g_1'^2\left ( Q_2^2+Q_Q^2-Q_u^2\right )\left ( a_t^2-2y_ta_tM_1'\right )-24Q_ug_1'^2y_t^2\left (Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )\nonumber\\
-&{}-24Q_ug_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )-8Q_ug_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )\nonumber\\
-&{}-12Q_ug_1'^2\sum_{i=1}^3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2\right )\nonumber\\
+\beta_{m_{u_3}^2}^{(2)}&=-32y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )-4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2\right )\nonumber\\
+&{}-64y_t^2a_t^2-4\left ( y_ta_b+y_ba_t\right )^2-4\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )\nonumber\\
+&{}-4\left ( \lambda a_t + y_ta_\lambda \right )^2+12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_2^2\right )+12g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
+&{}-\frac{4}{5}g_1^2y_t^2\left ( -5m_{H_u}^2-m_{Q_3}^2+9m_{u_3}^2+2M_1^2\right )-\frac{4}{5}g_1^2\left ( a_t^2-2y_ta_tM_1 \right )\nonumber\\
+&{}-\frac{8}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q_3}^2-2m_{d_3}^2\right )-\frac{8}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2-2m_{e_3}^2\right )\nonumber\\
+&{}-\frac{8}{5}g_1^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_{D_i}^2-m_{\overline{D}_i}^2 \right )+\lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2 \right )\right ]\nonumber\\
+&{}+8g_1'^2y_t^2\left ( Q_2^2+Q_Q^2-Q_u^2\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1'^2\right )\nonumber\\
+&{}+8g_1'^2\left ( Q_2^2+Q_Q^2-Q_u^2\right )\left ( a_t^2-2y_ta_tM_1'\right )-24Q_ug_1'^2y_t^2\left (Q_2m_{H_u}^2+Q_Qm_{Q_3}^2+Q_um_{u_3}^2\right )\nonumber\\
+&{}-24Q_ug_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q_3}^2+Q_dm_{d_3}^2\right )-8Q_ug_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L_3}^2+Q_em_{e_3}^2\right )\nonumber\\
+&{}-12Q_ug_1'^2\sum_{i=1}^3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{D_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2\right )\nonumber\\
 &{}-8Q_ug_1'^2\sum_{i=1}^3\lambda_i^2\left ( Q_1m_{H_d}^2+Q_2m_{H_u}^2+Q_Sm_S^2\right )\nonumber\\
-&{}+\frac{16}{3}g_3^4\left [ 10M_3^2+\sum_{i=1}^3\left ( m_{di}^2+m_{Di}^2+m_{\overline{D}i}^2+2m_{Qi}^2+m_{ui}^2\right )\right ]\nonumber\\
-&{}+\frac{64}{45}g_3^2g_1^2\left [ 8\left (M_1^2+M_1M_3+M_3^2\right )-3\sum_{i=1}^3\left ( m_{di}^2-m_{Di}^2+m_{\overline{D}i}^2+m_{Qi}^2-2m_{ui}^2\right )\right ]\nonumber\\
+&{}+\frac{16}{3}g_3^4\left [ 10M_3^2+\sum_{i=1}^3\left ( m_{d_i}^2+m_{D_i}^2+m_{\overline{D}_i}^2+2m_{Q_i}^2+m_{u_i}^2\right )\right ]\nonumber\\
+&{}+\frac{64}{45}g_3^2g_1^2\left [ 8\left (M_1^2+M_1M_3+M_3^2\right )-3\sum_{i=1}^3\left ( m_{d_i}^2-m_{D_i}^2+m_{\overline{D}_i}^2+m_{Q_i}^2-2m_{u_i}^2\right )\right ]\nonumber\\
 &{}+\frac{8}{3}Q_ug_3^2g_1'^2\bigg [ 16Q_u\left (M_1'^2+M_1'M_3+M_3^2\right )\nonumber\\
-&{}+12\sum_{i=1}^3\left ( Q_dm_{di}^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2+2Q_Qm_{Qi}^2+Q_um_{ui}^2\right )\bigg ]\nonumber\\
-&{}+\frac{12}{5}g_2^2g_1^2\left [ m_{H'}^2-m_{\overline{H'}}^2+\sum_{i=1}^3\left ( m_{H_i^d}^2-m_{H_i^u}^2+m_{Li}^2-m_{Qi}^2\right )\right ]\nonumber\\
-&{}+12Q_ug_2^2g_1'^2\left [ Q_{H'}m_{H'}^2+Q_{\overline{H'}}m_{\overline{H'}}^2+\sum_{i=1}^3\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Lm_{Li}^2+3Q_Qm_{Qi}^2\right )\right ]\nonumber\\
+&{}+12\sum_{i=1}^3\left ( Q_dm_{d_i}^2+Q_Dm_{D_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2+2Q_Qm_{Q_i}^2+Q_um_{u_i}^2\right )\bigg ]\nonumber\\
+&{}+\frac{12}{5}g_2^2g_1^2\left [ m_{H'}^2-m_{\overline{H'}}^2+\sum_{i=1}^3\left ( m_{H_i^d}^2-m_{H_i^u}^2+m_{L_i}^2-m_{Q_i}^2\right )\right ]\nonumber\\
+&{}+12Q_ug_2^2g_1'^2\left [ Q_{H'}m_{H'}^2+Q_{\overline{H'}}m_{\overline{H'}}^2+\sum_{i=1}^3\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Lm_{L_i}^2+3Q_Qm_{Q_i}^2\right )\right ]\nonumber\\
 &{}+\frac{4}{75}g_1^4\bigg [ 1261M_1^2+21m_{H'}^2+3m_{\overline{H'}}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 4m_{di}^2+12m_{Di}^2+4m_{\overline{D}i}^2-12m_{ei}^2+21m_{H_i^d}^2+3m_{H_i^u}^2+21m_{Li}^2+3m_{Qi}^2+64m_{ui}^2\right )\bigg ]\nonumber\\
+&{}+\sum_{i=1}^3\left ( 4m_{d_i}^2+12m_{D_i}^2+4m_{\overline{D}_i}^2-12m_{e_i}^2+21m_{H_i^d}^2+3m_{H_i^u}^2+21m_{L_i}^2+3m_{Q_i}^2+64m_{u_i}^2\right )\bigg ]\nonumber\\
 &{}+\frac{4}{15}g_1^2g_1'^2\bigg [ -8Q_u\big ( 9Q_d+9Q_{\overline{D}}-9Q_D+9Q_e-9Q_1+9Q_2+3Q_{\overline{H'}}-3Q_{H'}-9Q_L\nonumber\\
-&{}+9Q_Q-22Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2 \right )+12Q_{H'}^2m_{H'}^2-Q_{\overline{H'}}^2m_{\overline{H'}}^2\nonumber\\
-&{}+12\sum_{i=1}^3\big ( -Q_d^2m_{di}^2-Q_{\overline{D}}^2m_{\overline{D}i}^2+Q_D^2m_{Di}^2-Q_e^2m_{ei}^2+Q_1^2m_{H_i^d}^2-Q_2^2m_{H_i^u}^2+Q_L^2m_{Li}^2\nonumber\\
-&{}-Q_Q^2m_{Qi}^2+Q_u^2m_{ui}^2\big )-15Q_{\overline{H'}}Q_um_{\overline{H'}}^2+33Q_{H'}Q_um_{H'}^2+Q_u\sum_{i=1}^3\big ( -18Q_dm_{di}^2\nonumber\\
-&{}-18Q_{\overline{D}}m_{\overline{D}i}^2+30Q_Dm_{Di}^2-6Q_em_{ei}^2+33Q_1m_{H_i^d}^2-15Q_2m_{H_i^u}^2+33Q_Lm_{Li}^2\nonumber\\
-&{}-21Q_Qm_{Qi}^2+84Q_um_{ui}^2\big )\bigg ]+8Q_ug_1'^4\bigg [ 3Q_uM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2\nonumber\\
+&{}+9Q_Q-22Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2 \right )+12Q_{H'}^2m_{H'}^2-12Q_{\overline{H'}}^2m_{\overline{H'}}^2\nonumber\\
+&{}+12\sum_{i=1}^3\big ( -Q_d^2m_{d_i}^2-Q_{\overline{D}}^2m_{\overline{D}_i}^2+Q_D^2m_{D_i}^2-Q_e^2m_{e_i}^2+Q_1^2m_{H_i^d}^2-Q_2^2m_{H_i^u}^2+Q_L^2m_{L_i}^2\nonumber\\
+&{}-Q_Q^2m_{Q_i}^2+Q_u^2m_{u_i}^2\big )-15Q_{\overline{H'}}Q_um_{\overline{H'}}^2+33Q_{H'}Q_um_{H'}^2+Q_u\sum_{i=1}^3\big ( -18Q_dm_{d_i}^2\nonumber\\
+&{}-18Q_{\overline{D}}m_{\overline{D}_i}^2+30Q_Dm_{D_i}^2-6Q_em_{e_i}^2+33Q_1m_{H_i^d}^2-15Q_2m_{H_i^u}^2+33Q_Lm_{L_i}^2\nonumber\\
+&{}-21Q_Qm_{Q_i}^2+84Q_um_{u_i}^2\big )\bigg ]+8Q_ug_1'^4\bigg [ 3Q_uM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2\nonumber\\
 &{}+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2+18Q_Q^2+3Q_S^2+11Q_u^2 \big )+2Q_{H'}^3m_{H'}^2+2Q_{\overline{H'}}^3m_{\overline{H'}}^2\nonumber\\
-&{}+\sum_{i=1}^3\big ( 3Q_d^3m_{di}^2+3Q_{\overline{D}}^3m_{\overline{D}i}^2+3Q_D^3m_{Di}^2+Q_e^3m_{ei}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{Li}^2\nonumber\\
-&{}+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )+2Q_uQ_{H'}^2m_{H'}^2+2Q_uQ_{\overline{H'}}^2m_{\overline{H'}}^2\nonumber\\
-&{}+Q_u\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2\nonumber\\
-&{}+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmu222BetaTwoLoop}\\
-b_{m_{u3}^2}^{(2)}&=48y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2 \right )+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+m_{Q3}^2+m_{u3}^2+m_{d3}^2 \right )+96y_t^2a_t^2\nonumber\\
-&{}+4\left ( y_ta_b+y_ba_t\right )^2+4\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2 \right )+4\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
-&{}-\frac{64}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_3^2\right )-\frac{64}{3}g_3^2\left ( a_t^2-2y_ta_tM_3 \right )\nonumber\\
-&{}-12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_2^2\right )-12g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
-&{}-\frac{52}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1^2\right )-\frac{52}{15}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
-&{}-8g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )\nonumber\\
+&{}+\sum_{i=1}^3\big ( 3Q_d^3m_{d_i}^2+3Q_{\overline{D}}^3m_{\overline{D}_i}^2+3Q_D^3m_{D_i}^2+Q_e^3m_{e_i}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{L_i}^2\nonumber\\
+&{}+6Q_Q^3m_{Q_i}^2+Q_S^3m_{Si}^2+3Q_u^3m_{u_i}^2\big )+2Q_uQ_{H'}^2m_{H'}^2+2Q_uQ_{\overline{H'}}^2m_{\overline{H'}}^2\nonumber\\
+&{}+Q_u\sum_{i=1}^3\big ( 3Q_d^2m_{d_i}^2+3Q_{\overline{D}}^2m_{\overline{D}_i}^2+3Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{L_i}^2\nonumber\\
+&{}+6Q_Q^2m_{Q_i}^2+Q_S^2m_{Si}^2+3Q_u^2m_{u_i}^2\big )\bigg ],\label{eq:USSMmu222BetaTwoLoop}\\
+b_{m_{u_3}^2}^{(2)}&=48y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2 \right )+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2 \right )+96y_t^2a_t^2\nonumber\\
+&{}+4\left ( y_ta_b+y_ba_t\right )^2+4\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2 \right )+4\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
+&{}-\frac{64}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_3^2\right )-\frac{64}{3}g_3^2\left ( a_t^2-2y_ta_tM_3 \right )\nonumber\\
+&{}-12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_2^2\right )-12g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
+&{}-\frac{52}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1^2\right )-\frac{52}{15}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
+&{}-8g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1'^2\right )\nonumber\\
 &{}-8g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( a_t^2-2y_ta_tM_1'\right )\nonumber\\
-&{}+4g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 3Q_um_{H_u}^2+3Q_um_{Q3}^2+3Q_um_{u3}^2+\Sigma_1'\right )\nonumber\\
-&{}+12Q_ug_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_ug_1'^2y_b^2\left ( Q_1+Q_Q+Q_d \right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
+&{}+4g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 3Q_um_{H_u}^2+3Q_um_{Q_3}^2+3Q_um_{u_3}^2+\Sigma_1'\right )\nonumber\\
+&{}+12Q_ug_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_ug_1'^2y_b^2\left ( Q_1+Q_Q+Q_d \right )\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )\nonumber\\
 &{}+12Q_ug_1'^2a_b^2\left ( Q_1+Q_Q+Q_d \right )\nonumber\\
-&{}+4Q_ug_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+4Q_ug_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
-&{}+2Q_ug_1'^2\sum_{i=1}^3\bigg [ 3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+3a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\nonumber\\
+&{}+4Q_ug_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )+4Q_ug_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
+&{}+2Q_ug_1'^2\sum_{i=1}^3\bigg [ 3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+3a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\nonumber\\
 &{}+2\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+2a_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )\bigg ]\nonumber\\
@@
 &{}+3Q_L+Q_Q+8Q_u )+\left ( 3Q_u\Sigma_1-2\Sigma_1^\prime\right ) \Sigma_Q^Y\big ]-4Q_ug_1'^4\big [ 2M_1'^2 ( 9Q_d^3+9Q_D^3+9Q_{\overline{D}}^3\nonumber\\
-&{}+3Q_e^2+6Q_1^2+6Q_2^2+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3 )\nonumber\\
+&{}+3Q_e^3+6Q_1^3+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3 )\nonumber\\
 &{}+\left(6Q_uM_1'^2-\Sigma_1^\prime\right )\Sigma_Q\big ].\label{eq:USSMmu222Ot2Coeff}

### 2015-03-30 paper/e6ssm-tuning-paper.tex
Fixed double equation number for superpotential, reworked comment following the superpotential definition to read better
Replaced Fig --> Fig.

@@
       \SuperField{d}_3^c + y_t \SuperField{H}_u\cdot\SuperField{Q}_3
-      \SuperField{u}_3^c\\
+      \SuperField{u}_3^c\nonumber\\
     &&
@@
 %  
-where the third generation Higgs fields $\SuperField{H}_d^3\equiv \SuperField{H}_d$,
-$\SuperField{H}_u^3\equiv\SuperField{H}_u$ and SM singlet field $\SuperField{S}_3\equiv\SuperField{S}$ 
-are allowed to get VEVs. 
+where we denote by $\SuperField{H}_d^3\equiv \SuperField{H}_d$,
+$\SuperField{H}_u^3\equiv\SuperField{H}_u$ and $\SuperField{S}_3\equiv\SuperField{S}$ the third generation Higgs and SM singlet fields that are assumed to acquire non-zero VEVs.
 \section{\label{sec:ewsb}Electroweak Symmetry Breaking}
@@
 \end{figure}
-In Fig \ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
+In Fig.~\ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
 the tuning for each case against the lightest Higgs mass.  As expected

### 2015-03-30 paper/e6ssm-tuning-paper.tex
Fixed typo we --> will

@@
   cutoff increases the values of these soft masses at $M_X$ will be
-  larger and there we be a bigger cancellation between them,
+  larger and there will be a bigger cancellation between them,
   increasing the sensitivity of $M_Z$ to both $m_{H_u}^2$ and the soft

### 2015-03-31 paper/e6ssm-tuning-paper.tex
Modified plot of benchmark tunings to use dashed, dotted and dash-dotted lines for clarity, and amended text to include this description. Also changed 'it had much lighter gluino mass' to 'it had a much lighter gluino mass'

@@
 \caption{\textit{Top panel:} Scatter plot of the fine tuning as a function of the cutoff scale $M_X$ for the four benchmark points given in Table \ref{tab:benchmarks}.
-\textit{Middle left panel:}  Individual sensitivities for MSSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the green line in the top panel.
-\textit{Middle right panel:} Individual sensitivities for E$_6$SSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the blue line in the top panel.
-\textit{Bottom left panel:} Individual sensitivities for MSSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the yellow line in the top panel.
-\textit{Bottom right panel:} Individual sensitivities for E$_6$SSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the red line in the top panel.
+\textit{Middle left panel:}  Individual sensitivities for MSSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the green (dotted) line in the top panel.
+\textit{Middle right panel:} Individual sensitivities for E$_6$SSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the blue (solid) line in the top panel.
+\textit{Bottom left panel:} Individual sensitivities for MSSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the yellow (dash-dotted) line in the top panel.
+\textit{Bottom right panel:} Individual sensitivities for E$_6$SSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the red (dashed) line in the top panel.
 }
@@
 
-In the top panel one can see that the MSSM BM1 tuning (green curve) 
+In the top panel one can see that the MSSM BM1 tuning (dotted green curve) 
 steadily climbs as the cutoff scale is increased, as one would expect
@@
 
-For E$_6$SSM BM1 the fine tuning is shown by the blue curve in the top
+For E$_6$SSM BM1 the fine tuning is shown by the solid blue curve in the top
 panel of Fig.~\ref{Fig:BMs-varyMX} and the individual sensitivities
@@
 By contrast the tuning for E$_6$SSM BM2 is very different, as is shown
-in red in the top panel, with the individual sensitivities given in the
-bottom right panel. This point was chosen as it had much lighter
+in red (dashed) in the top panel, with the individual sensitivities given in the
+bottom right panel. This point was chosen as it had a much lighter
 gluino mass that is just above the experimental limit of $1.4$ TeV
@@
 
-MSSM benchmark BM2 (yellow in top panel, individual sensitivities in bottom left panel) is designed to be similar to E$_6$SSM BM2, for a reasonable comparison.
+MSSM benchmark BM2 (yellow, dash-dotted in top panel, individual sensitivities in bottom left panel) is designed to be similar to E$_6$SSM BM2, for a reasonable comparison.
 However from the individual sensitivities one can see that the behaviour is quite similar to MSSM BM1, though in this case the $\Delta_{m_{H_u}^2}$ becomes the largest tuning at a higher $M_X$ and does not reach such large values, since more of the tuning is from the mixing in this case.

### 2015-03-31 paper/e6ssm-tuning-paper.tex
Removed references to colours of lines when discussing top panel of Figure 5, in case it is necessary to swap out for different colours, and instead now refers to lines by the line style

@@
 \caption{\textit{Top panel:} Scatter plot of the fine tuning as a function of the cutoff scale $M_X$ for the four benchmark points given in Table \ref{tab:benchmarks}.
-\textit{Middle left panel:}  Individual sensitivities for MSSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the green (dotted) line in the top panel.
-\textit{Middle right panel:} Individual sensitivities for E$_6$SSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the blue (solid) line in the top panel.
-\textit{Bottom left panel:} Individual sensitivities for MSSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the yellow (dash-dotted) line in the top panel.
-\textit{Bottom right panel:} Individual sensitivities for E$_6$SSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the red (dashed) line in the top panel.
+\textit{Middle left panel:}  Individual sensitivities for MSSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the dotted line in the top panel.
+\textit{Middle right panel:} Individual sensitivities for E$_6$SSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the solid line in the top panel.
+\textit{Bottom left panel:} Individual sensitivities for MSSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the dash-dotted line in the top panel.
+\textit{Bottom right panel:} Individual sensitivities for E$_6$SSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the dashed line in the top panel.
 }
@@
 
-In the top panel one can see that the MSSM BM1 tuning (dotted green curve) 
+In the top panel one can see that the MSSM BM1 tuning (dotted curve) 
 steadily climbs as the cutoff scale is increased, as one would expect
@@
 over, leading to the small kink in overall tuning which can be seen in
-the green curve in the top panel. In this case we have chosen a
+the dotted curve in the top panel. In this case we have chosen a
 point with large mixing, which is known to reduce the MSSM tuning.  We
@@
 
-For E$_6$SSM BM1 the fine tuning is shown by the solid blue curve in the top
+For E$_6$SSM BM1 the fine tuning is shown by the solid curve in the top
 panel of Fig.~\ref{Fig:BMs-varyMX} and the individual sensitivities
@@
 By contrast the tuning for E$_6$SSM BM2 is very different, as is shown
-in red (dashed) in the top panel, with the individual sensitivities given in the
+by the dashed line in the top panel, with the individual sensitivities given in the
 bottom right panel. This point was chosen as it had a much lighter
@@
 
-MSSM benchmark BM2 (yellow, dash-dotted in top panel, individual sensitivities in bottom left panel) is designed to be similar to E$_6$SSM BM2, for a reasonable comparison.
+MSSM benchmark BM2 (dash-dotted in top panel, individual sensitivities in bottom left panel) is designed to be similar to E$_6$SSM BM2, for a reasonable comparison.
 However from the individual sensitivities one can see that the behaviour is quite similar to MSSM BM1, though in this case the $\Delta_{m_{H_u}^2}$ becomes the largest tuning at a higher $M_X$ and does not reach such large values, since more of the tuning is from the mixing in this case.

### 2015-03-31 paper/e6ssm-tuning-paper.tex
Added alternative colour palette plots and changed text to be consistent with new colours

@@
 \resizebox{!}{6.1cm}{%
-\includegraphics{mssm_stop_tuning.png}}
+\includegraphics{mssm_stop_tuning_bw_var.png}}
 \resizebox{!}{6.1cm}{%
-\includegraphics{mssm_higgs_tuning.png}}
+\includegraphics{mssm_higgs_tuning_bw_var.png}}
 \caption{\textit{Left panel:} Scatter plot of fine tuning in the MSSM as a function of
@@
 $M_3=352$ GeV, $A_b=-117.9$ GeV, $A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV,
-$m_{e_i}=204$ GeV, $m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and
+$m_{e_i}=204$ GeV, $m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}=436$ GeV and
 $m_{d_i}=438$ GeV ($i=1,2,3$). Here we denote by $M_1$, $M_2$ and $M_3$
@@
 \resizebox{!}{10cm}{%
-\includegraphics{all_models_tuning_vs_higgs.png}}
+\includegraphics{all_models_tuning_vs_higgs_bw_var.png}}
 \caption{Scatter plot of fine tuning vs lightest Higgs mass for the
-  MSSM (green, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue, middle band) and
-  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band). Note that there are points for which
+  MSSM (light blue, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (dark blue, middle band) and
+  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (dark yellow, top band). Note that there are points for which
 the fine tuning in the MSSM and E$_6$SSM with $M_{Z'}=2.5$ TeV is larger than is visible on this plot
@@
 \resizebox{!}{10cm}{%
-\includegraphics{mssm_chargino_plot.png}}%%
-\caption{Scatter plot of fine tuning vs lightest Higgs mass in the MSSM with $m_{\tilde{\chi}^\pm_1} = 200$ GeV shown in green 
-(bottom band) $m_{\tilde{\chi}^\pm_1} = 500$ GeV in blue (middle band) and $m_{\tilde{\chi}^\pm_1} = 700$ GeV in red
+\includegraphics{mssm_chargino_plot_bw_var.png}}%%
+\caption{Scatter plot of fine tuning vs lightest Higgs mass in the MSSM with $m_{\tilde{\chi}^\pm_1} = 200$ GeV shown in light blue 
+(bottom band), $m_{\tilde{\chi}^\pm_1} = 500$ GeV in dark blue (middle band), and $m_{\tilde{\chi}^\pm_1} = 700$ GeV in dark yellow
 (top band).}
@@
 \resizebox{!}{6.1cm}{%
-\includegraphics{e6inert_tb10_tuning_vs_higgs.png}}
+\includegraphics{e6inert_tb10_tuning_vs_higgs_bw_var.png}}
 \resizebox{!}{6.1cm}{%
-\includegraphics{e6psi_tb10_tuning_vs_higgs.png}}\\
+\includegraphics{e6psi_tb10_tuning_vs_higgs_bw_var.png}}\\
 \resizebox{!}{6.1cm}{%
-\includegraphics{e6eta_tb10_tuning_vs_higgs.png}}%%
+\includegraphics{e6eta_tb10_tuning_vs_higgs_bw_var.png}}%%
 \caption{\textit{Top left panel:} Scatter plot of the fine tuning vs lightest Higgs mass in the $U(1)_I$ model.
@@
 \textit{Bottom panel:} Scatter plot of the fine tuning vs lightest Higgs mass in the $U(1)_\eta$ model.
-In each plot points with $M_{Z^\prime} = 2.5$ TeV are shown in blue
-(bottom band), and points with $M_{Z^\prime} = 4.5$ TeV are shown in red (top band).}
+In each plot points with $M_{Z^\prime} = 2.5$ TeV are shown in dark blue
+(bottom band), and points with $M_{Z^\prime} = 4.5$ TeV are shown in dark yellow (top band).}
 \label{Fig:othere6modelsvsmssm}
@@
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_mssm_cutoff_scan_4_benchmark_points_tuning_vs_cutoff.png} } \\
+\includegraphics{e6ssm_mssm_cutoff_scan_4_benchmark_points_tuning_vs_cutoff_bw_var.png} } \\
 \resizebox{!}{5.5cm}{%
-\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_BM1_all_tuning_data.png}} 
+\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_BM1_all_tuning_data_bw_var.png}} 
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_BM1_all_tuning_data.png}} \\
+\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_BM1_all_tuning_data_bw_var.png}} \\
 \resizebox{!}{5.5cm}{%
-\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_BM2_all_tuning_data.png}} 
+\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_BM2_all_tuning_data_bw_var.png}} 
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_BM2_all_tuning_data.png}}%%
+\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_BM2_all_tuning_data_bw_var.png}}%%
 \caption{\textit{Top panel:} Scatter plot of the fine tuning as a function of the cutoff scale $M_X$ for the four benchmark points given in Table \ref{tab:benchmarks}.
@@
 because the largest sensitivity is initially $\Delta_\lambda$ (shown
-in solid blue in the middle right panel).  This contains some terms
+in solid light blue in the middle right panel).  This contains some terms
 proportional to $M_Z^{\prime \, 2}$, which provide the dominant

### 2015-03-31 paper/e6ssm-tuning-paper.tex
Added missing space before citation

@@
 $m_{\tilde{\chi}^\pm_1} \approx 700-740$ GeV if there are light
-sleptons\cite{Khachatryan:2014qwa, Aad:2014nua} with much weaker
+sleptons \cite{Khachatryan:2014qwa, Aad:2014nua} with much weaker
 bounds if there are no light sleptons or sneutrinos\footnote{Useful

### 2015-03-31 paper/e6ssm-tuning-paper.tex
Fixed 'slightly worse than' --> 'similar to'

@@
 impact would be to make the tuning in the MSSM with a $20$ TeV cutoff
-slightly worse than that of the E$_6$SSM with the same cutoff and a
+similar to that of the E$_6$SSM with the same cutoff and a
 $Z^\prime$ mass just larger than current limits. In the E$_6$SSM,
@@
 \end{subequations}
-% NB before submission replace this with a copy-paste of the bbl file?
+
 \bibliographystyle{apsrev4-1}

### 2015-04-10 paper/e6ssm-tuning-paper.tex
Added flag that arXiv apparently uses for pdf output?
added Z' decay references and updated my email address.
Imposed max line length of 80 characters for submission, tried to make spacing in TeX source for equations more consistent, corrected some typos, swapped log -> ln, removed repeated multiplication signs, changed to American English spellings of words

@@
-\documentclass[preprint,amsmath,amssymb,aps,superscriptaddress,prd,showpacs,floatfix,nofootinbib]{revtex4-1}
+\documentclass[preprint,amsmath,amssymb,aps,superscriptaddress,prd,
+showpacs,floatfix,nofootinbib]{revtex4-1}
+
+\pdfoutput=1
 
@@
 \usepackage{longtable}
+
 % macros
@@
 \author{P. Athron}
- \email{peter.athron@adelaide.edu.au}
+ \email{peter.athron@monash.edu}
  \affiliation{
-ARC Centre of Excellence for Particle Physics at the Terascale, School of Physics, Monash University, Melbourne VIC 3800, Australia
+ARC Centre of Excellence for Particle Physics at the Terascale,
+School of Physics, Monash University, Melbourne VIC 3800, Australia
 }
@@
  \affiliation{
-ARC Centre of Excellence for Particle Physics at the Terascale, Department of Physics, The University of Adelaide,
-Adelaide, South Australia 5005, Australia}
+ARC Centre of Excellence for Particle Physics at the Terascale,
+Department of Physics, The University of Adelaide, Adelaide,
+South Australia 5005, Australia}
 
@@
  \affiliation{
-ARC Centre of Excellence for Particle Physics at the Terascale, Department of Physics, The University of Adelaide,
-Adelaide, South Australia 5005, Australia}
-
-\date{\today}% It is always \today, today,
-             %  but any date may be explicitly specified
+ARC Centre of Excellence for Particle Physics at the Terascale,
+Department of Physics, The University of Adelaide, Adelaide,
+South Australia 5005, Australia}
+
+\date{\today}
 
@@
 GeV Higgs, feed into the electroweak symmetry breaking conditions
-through renormalisation group equations forcing one to fine tune these 
+through renormalization group equations forcing one to fine tune these
 parameters to obtain the correct electroweak vacuum expectation value.
@@
 provide the most compelling solution to the $\mu$-problem, which is also
-a naturalness issue, and allow the tree level Higgs mass to be raised substantially above $M_Z$. These very well motivated supersymmetric models 
+a naturalness issue, and allow the tree level Higgs mass to be raised
+substantially above $M_Z$.  These very well motivated supersymmetric models
 predict a new $Z^\prime$ boson which could be discovered at the LHC and the
@@
 appears at the tree level, making it less dependent on assumptions
-about the supersymmetry breaking mechanism.  Here we study this fine tuning for
-several $U(1)$ supersymmetric extensions of the Standard Model and
+about the supersymmetry breaking mechanism.  Here we study this fine tuning
+for several $U(1)$ supersymmetric extensions of the Standard Model and
 compare it to the situation in the MSSM where the most direct tree
@@
 \pacs{12.60.Jv, 11.30.Pb, 12.60.-i, 14.80.Bn}
-\keywords{naturalness, fine tuning, supersymmetry}%Use showkeys class option if keyword
-                              %display desired
+\keywords{naturalness, fine tuning, supersymmetry}
 \preprint{ADP-15-4/T906}
@@
 \section{\label{sec:intro}Introduction}
+
 The discovery of an approximately 125 GeV Higgs
-\cite{Aad:2012tfa,Chatrchyan:2012ufa} at the Large Hadron Collider
+\cite{Aad:2012tfa, Chatrchyan:2012ufa} at the Large Hadron Collider
 (LHC) has interesting implications for physics beyond the Standard
@@
 can be fitted in the minimal supersymmetric standard model (MSSM).  On
-the other hand the Higgs mass is slightly heavier than the constrained version of the 
-MSSM (cMSSM) can accommodate naturally \cite{Cassel:2011zd,Ghilencea:2012gz}.
+the other hand the Higgs mass is slightly heavier than the constrained
+version of the MSSM (cMSSM) can accommodate naturally
+\cite{Cassel:2011zd, Ghilencea:2012gz}.
 
@@
 value of $m_{H_u}^2$, the soft breaking mass for the up-type Higgs
-scalar, through the evolution of the renormalisation group equations
+scalar, through the evolution of the renormalization group equations
 (RGEs) from the grand unification (GUT) scale to the electroweak (EW)
-scale. This affects the SUSY prediction of the electroweak vacuum expectation value (VEV), $v$,
-or $M_Z$.  This naturalness problem motivates both further examination
-of non-minimal SUSY models that can raise the Higgs mass without the
-need for heavy stops and alternative possibilities for how the soft
-breaking parameters get generated, which might set them at lower
+scale.  This affects the SUSY prediction of the electroweak vacuum expectation
+value (VEV), $v$, or $M_Z$.  This naturalness problem motivates both
+further examination of non-minimal SUSY models that can raise the Higgs mass
+without the need for heavy stops and alternative possibilities for how the
+soft breaking parameters get generated, which might set them at lower
 energies, reducing the influence the stops have on $m_{H_u}^2$.
@@
 the exceptional supersymmetric standard model (E$_6$SSM)
-\cite{King:2005jy,King:2005my,Athron:2010zz}, such models can still
+\cite{King:2005jy, King:2005my, Athron:2010zz}, such models can still
 suffer from naturalness problems with the mass of the new $Z^\prime$
 associated with the break down of the new $U(1)$ appearing in the
-electroweak symmetry breaking conditions at tree level
-\cite{Athron:2013ipa}. Despite this the constrained version of
-the E$_6$SSM (cE$_6$SSM) \cite{Athron:2009ue, Athron:2009bs} was still found
-to be significantly less tuned than the cMSSM.
+electroweak symmetry breaking conditions at tree level \cite{Athron:2013ipa}.
+Despite this the constrained version of the E$_6$SSM (cE$_6$SSM)
+\cite{Athron:2009ue, Athron:2009bs} was still found to be significantly
+less tuned than the cMSSM.
 
@@
 In this paper we investigate how big this tuning is if we bring this
-scale all the way down to 20 TeV, effectively minimising the contribution
+scale all the way down to 20 TeV, effectively minimizing the contribution
 from the stops.  We find that the $Z^\prime$ limit is enough to already
@@
 detail by considering low energy constructions where the usual fine
-tuning problem from the Higgs is minimised.  We will also consider
+tuning problem from the Higgs is minimized.  We will also consider
 alternate charges for the extra $U(1)$ symmetry to relax the focus on
@@
 To quantify the fine tuning we will employ the traditional
-Barbieri-Giudice measure \cite{Ellis:1986yg,Barbieri:1987fn}.  This
+Barbieri-Giudice measure \cite{Ellis:1986yg, Barbieri:1987fn}.  This
 has been used extensively within the literature
@@
 Kim:2013uxa} suppressing the posterior.  Indeed in the MSSM and
-the next-to-MSSM (NMSSM) if one transforms GUT scale parameters to the VEVs, the inverse
-of the Jacobian for this transformation looks quite like the
-derivatives that appear in the traditional fine tuning measure
+the next-to-MSSM (NMSSM) if one transforms GUT scale parameters to the
+VEVs, the inverse of the Jacobian for this transformation looks quite like
+the derivatives that appear in the traditional fine tuning measure
 \cite{Allanach:2007qk, Cabrera:2008tj, Kim:2013uxa}.  If one thinks
@@
 
-\section{\label{sec:model}$U(1)$ extensions and the E$_6$SSM}
+\section{\label{sec:model}$U(1)$ extensions and the
+E$_6$SSM}
+
 In this paper we consider $U(1)$ extensions of the MSSM where the gauge
@@
 
-%%%--------------Inserted from introduction-------------------%%%%
-
 Here we will refer to $U(1)$ extensions of the MSSM, which solve the
@@
   Nir:1995bu, Cvetic:1996mf, Cvetic:1997ky}.  The couplings for the
-$U(1)^\prime$ gauge group should allow the following renormalisable
-superpotential terms required in the USSM, \begin{equation}
- W_{USSM} = y^U_{ij}
-\hat{u}^c_i  \hat{H}_u \cdot \hat{Q}_j + y^D_{ij} \hat{d}^c_i  \hat{Q}_j \cdot \hat{H}_d
- + y^E_{ij} \hat{e}^c_i \hat{L}_j \cdot \hat{H}_d  + \lambda \hat{S} \hat{H}_d \cdot \hat{H}_u, 
-\end{equation} with $i,j \in \{1,2,3\}$. 
-For the $SU(2)$ dot product we follow the convention $\hat{A}\cdot \hat{B}\equiv \epsilon_{\alpha\beta}\hat{A}^\alpha\hat{B}^\beta=\hat{A}^2\hat{B}^1-\hat{A}^1\hat{B}^2$.
+$U(1)^\prime$ gauge group should allow the following renormalizable
+superpotential terms required in the USSM,
+\begin{equation}
+ W_{USSM} = y^U_{ij} \hat{u}^c_i \hat{H}_u \cdot \hat{Q}_j + y^D_{ij}
+\hat{d}^c_i \hat{Q}_j \cdot \hat{H}_d + y^E_{ij} \hat{e}^c_i \hat{L}_j
+\cdot \hat{H}_d + \lambda \hat{S} \hat{H}_d \cdot \hat{H}_u ,
+\end{equation}
+with $i,j \in \{1,2,3\}$.  For the $SU(2)$ dot product we follow the
+convention $\hat{A} \cdot \hat{B} \equiv \epsilon_{\alpha \beta}
+\hat{A}^\alpha \hat{B}^\beta = \hat{A}^2 \hat{B}^1 - \hat{A}^1 \hat{B}^2$.
 
@@
 
-The breaking of $E_6$ into $SO(10)$, gives rise to $E_6\to
-SO(10)\times U(1)_{\psi}$, and the subsequent breaking of $SO(10)$
-into $SU(5)$, gives $SO(10)\to SU(5)\times U(1)_{\chi}$ (this is
+The breaking of $E_6$ into $SO(10)$, gives rise to $E_6 \to
+SO(10) \times U(1)_{\psi}$, and the subsequent breaking of $SO(10)$
+into $SU(5)$, gives $SO(10) \to SU(5) \times U(1)_{\chi}$ (this is
 reviewed in e.g.~\cite{Langacker:2008yv}).  The extra $U(1)$ gauge
 symmetry at low energies should then be a linear combination of these
-in the $E_6$ inspired case, \be U(1)^\prime = U(1)_{\chi}\cos\theta 
-+ U(1)_{\psi}\sin\theta . \ee In Table \ref{tab:E6charges} the
+in the $E_6$ inspired case, \be U(1)^\prime = U(1)_{\chi} \cos\theta
++ U(1)_{\psi} \sin\theta .  \ee In Table \ref{tab:E6charges} the
 charges for several popular $E_6$ inspired $U(1)$ extensions are
 shown.
-% Table of U(1)' charges, which may or may not be useful to include.
+
 \begin{table}[h]
@@
 \begin{tabular}{cccccccccccccc}
- & $\hat{Q}$ & $\hat{u}^c$ & $\hat{d}^c$ & $\hat{L}$ & $\hat{e}^c$ & $\hat{N}^c$ & $\hat{S}$ & $\hat{H}_2$ & $\hat{H}_1$ & $\hat{D}$ & $\hat{\overline{D}}$ & $\hat{H}'$ & $\hat{\overline{H'}}$ \\[1mm]
+ & $\hat{Q}$ & $\hat{u}^c$ & $\hat{d}^c$ & $\hat{L}$ & $\hat{e}^c$ &
+$\hat{N}^c$ & $\hat{S}$ & $\hat{H}_2$ & $\hat{H}_1$ & $\hat{D}$ &
+$\hat{\overline{D}}$ & $\hat{H}'$ & $\hat{\overline{H'}}$ \\[1mm]
 \hline
-$\sqrt{\frac{5}{3}}Q_i^Y$ & $\frac{1}{6}$ & $-\frac{2}{3}$ & $\frac{1}{3}$ & $-\frac{1}{2}$ & $1$ & $0$ & $0$ & $\frac{1}{2}$ & $-\frac{1}{2}$ & $-\frac{1}{3}$ & $\frac{1}{3}$ & $-\frac{1}{2}$ & $\frac{1}{2}$ \\[1mm]
-%\hline
-$2\sqrt{6}Q_i^\psi$ & $1$ & $1$ & $1$ & $1$ & $1$ & $1$ & $4$ & $-2$ & $-2$ & $-2$ & $-2$ & $1$ & $-1$\\[1mm]
-%\hline
-$2\sqrt{10}Q_i^\chi$ & $-1$ & $-1$ & $3$ & $3$ & $-1$ & $-5$ & $0$ & $2$ & $-2$ & $2$ & $-2$ & $3$ & $-3$\\[1mm]
-%\hline
-$\sqrt{40}Q_i^N$ & $1$ & $1$ & $2$ & $2$ & $1$ & $0$ & $5$ & $-2$ & $-3$ & $-2$ & $-3$ & $2$ & $-2$ \\[1mm]
+$\sqrt{\frac{5}{3}}Q_i^Y$ & $\frac{1}{6}$ & $-\frac{2}{3}$ & $\frac{1}{3}$ &
+$-\frac{1}{2}$ & $1$ & $0$ & $0$ & $\frac{1}{2}$ & $-\frac{1}{2}$ &
+$-\frac{1}{3}$ & $\frac{1}{3}$ & $-\frac{1}{2}$ & $\frac{1}{2}$ \\[1mm]
+$2\sqrt{6}Q_i^\psi$ & $1$ & $1$ & $1$ & $1$ & $1$ & $1$ & $4$ & $-2$ & $-2$ &
+$-2$ & $-2$ & $1$ & $-1$\\[1mm]
+$2\sqrt{10}Q_i^\chi$ & $-1$ & $-1$ & $3$ & $3$ & $-1$ & $-5$ & $0$ & $2$ &
+$-2$ & $2$ & $-2$ & $3$ & $-3$\\[1mm]
+$\sqrt{40}Q_i^N$ & $1$ & $1$ & $2$ & $2$ & $1$ & $0$ & $5$ & $-2$ & $-3$ &
+$-2$ & $-3$ & $2$ & $-2$ \\[1mm]
 \end{tabular}
 \end{ruledtabular}
-\caption{The $U(1)_Y$, $U(1)_\psi$, $U(1)_\chi$ and $U(1)_N$ charges of the chiral superfields in the $E_6$ model.
-The specific case of $U(1)_N$, corresponding to the E$_6$SSM, is obtained for $\theta=\arctan\sqrt{15}$.}
+\caption{The $U(1)_Y$, $U(1)_\psi$, $U(1)_\chi$ and $U(1)_N$ charges of the
+chiral superfields in the $E_6$ model.  The specific case of $U(1)_N$,
+corresponding to the E$_6$SSM, is obtained for $\theta = \arctan \sqrt{15}$.}
 \label{tab:E6charges}
@@
 Keith:1997zb, Gherghetta:1996yr, Demir:1998dk, Langacker:1998tc,
-  Hambye:2000bn, Ma:2000jf} (or for reviews see
-\cite{Hewett:1988xc,Langacker:2008yv}).  There has also been a lot of
-work recently including investigations of the neutralino sector
-\cite{Hesselbach:2001ri, Barger:2005hb, Choi:2006fz,
-  Barger:2007nv}; the relic density of dark matter
-\cite{Kalinowski:2008iq}; GUT scale family symmetries which can
-explain the hierarchy of masses in the fermion sector and their
-associated mixings \cite{Stech:2008wd}; neutrino physics
-\cite{Kang:2004ix}; explanations of the matter-anti-matter asymmetry
-of the universe though EW baryogenesis or leptogenesis
-\cite{Hambye:2000bn,Ma:2000jf,Kang:2004pp}; dipole moments
-\cite{GutierrezRodriguez:2006hb}; anomaly mediated SUSY breaking with
-D-term contributions \cite{Asano:2008ju} and the (extended) Higgs
-sectors \cite{Daikoku:2000ep,Ham:2008xf}.
+Hambye:2000bn, Ma:2000jf} (or for reviews see \cite{Hewett:1988xc,
+Langacker:2008yv}).  There has also been a lot of work recently including
+investigations of the neutralino sector \cite{Hesselbach:2001ri,
+Barger:2005hb, Choi:2006fz, Barger:2007nv}; the relic density of dark matter
+\cite{Kalinowski:2008iq}; GUT scale family symmetries which can explain the
+hierarchy of masses in the fermion sector and their associated mixings
+\cite{Stech:2008wd}; neutrino physics \cite{Kang:2004ix}; explanations of
+the matter-anti-matter asymmetry of the universe though EW baryogenesis or
+leptogenesis \cite{Hambye:2000bn, Ma:2000jf, Kang:2004pp}; decays of the
+$Z^\prime$ boson \cite{Kang:2004bz, Baumgart:2006pa, Athron:2011wu,
+Chang:2011be}; dipole moments \cite{GutierrezRodriguez:2006hb}; anomaly
+mediated SUSY breaking with D-term contributions \cite{Asano:2008ju} and
+the (extended) Higgs sectors \cite{Daikoku:2000ep, Ham:2008xf}.
 
@@
 is $U(1)_N$, under which the right handed neutrino $\hat{N}^c$ remains
-interaction-less. This is the case in the E$_6$SSM
-\cite{King:2005jy,King:2005my,Athron:2010zz}, and closely-related
-variants\cite{Howl:2007zi, Braam:2009fi, Braam:2010sy, Hall:2011zq,
-  Nevzorov:2012hs, Athron:2014pua}.  Since the right handed neutrino
-has no gauge symmetry protecting it's mass from becoming extremely
-heavy such models may explain the tiny observed masses of neutrinos
-via the see-saw mechanism and the baryon asymmetry in the universe via
-leptogenesis \cite{Hambye:2000bn,King:2008qb, King:2008gw}.  Recently
-it has also been studied in the context of electroweak baryogenesis
+interaction-less.  This is the case in the E$_6$SSM \cite{King:2005jy,
+King:2005my, Athron:2010zz}, and closely-related variants \cite{Howl:2007zi,
+Braam:2009fi, Braam:2010sy, Hall:2011zq, Nevzorov:2012hs, Athron:2014pua}.
+Since the right handed neutrino has no gauge symmetry protecting it's mass
+from becoming extremely heavy such models may explain the tiny observed
+masses of neutrinos via the see-saw mechanism and the baryon asymmetry in
+the universe via leptogenesis \cite{Hambye:2000bn, King:2008qb, King:2008gw}.
+Recently it has also been studied in the context of electroweak baryogenesis
 \cite{Chao:2014hya}.
@@
 in slightly modified scenarios, two-step unification can take place
-\cite{Howl:2007hq,Howl:2007zi}. If the exotic particles are light in
+\cite{Howl:2007hq, Howl:2007zi}.  If the exotic particles are light in
 these models this can open up non-standard decays of the SM--like
-Higgs boson \cite{Hall:2010ix,Nevzorov:2013tta,Athron:2014pua}.
+Higgs boson \cite{Hall:2010ix, Nevzorov:2013tta, Athron:2014pua}.
 
@@
 this is no longer phenomenologically viable due to limits from direct
-detection of dark matter
-\cite{2011PhRvL.107m1302A,2012PhRvL.109r1301A, Akerib:2013tjd} and due
-to a significant suppression of the decay of the lightest Higgs boson
-into SM states, due to a new channel into inert singlinos opening up.
+detection of dark matter \cite{2011PhRvL.107m1302A, 2012PhRvL.109r1301A,
+Akerib:2013tjd} and due to a significant suppression of the decay of the
+lightest Higgs boson into SM states, due to a new channel into inert
+singlinos opening up.
 
@@
 included in studies looking at how first or second generation sfermion
-masses can be used to constrain the GUT scale parameters
-\cite{Miller:2012vn} and the renormalization of VEVs
-\cite{Sperling:2013eva, Sperling:2013xqa}.  The particle spectrum and
-collider signatures of the cE$_6$SSM have been studied in a series of
-papers,
-\cite{Athron:2009ue,Athron:2009bs,Athron:2011wu,Athron:2012sq}. The
-threshold corrections to the $\overline{DR}$ gauge and Yukawa
-couplings in the E$_6$SSM have also been calculated and their
-numerical impact in the constrained version examined
+masses can be used to constrain the GUT scale parameters \cite{Miller:2012vn}
+and the renormalization of VEVs \cite{Sperling:2013eva, Sperling:2013xqa}.
+The particle spectrum and collider signatures of the cE$_6$SSM have been
+studied in a series of papers, \cite{Athron:2009ue, Athron:2009bs,
+Athron:2011wu,Athron:2012sq}.  The threshold corrections to the
+$\overline{DR}$ gauge and Yukawa couplings in the E$_6$SSM have also been
+calculated and their numerical impact in the constrained version examined
 \cite{Athron:2012pw}.
-%%%%%%%%%%%%%%%%%%---inserted from introduction---%%%%%%%%%%%%%%%%5%%
 
@@
 includes, \be
-(\hat{Q}_i,\,\hat{u}^c_i,\,\hat{d}^c_i,\,\hat{L}_i,\,\hat{e}^c_i)
-+(\hat{D}_i,\,\hat{\overline{D}}_i)+(\hat{S}_{i})+(\hat{H}^u_i)+(\hat{H}^d_i),\ee
-where the $\hat{S}_{i}$, $\hat{H}^u_i$ and $\hat{H}^d_i$ have the quantum numbers of a
-SM singlet, and up-, down-type Higgs fields, respectively, and the $\hat{D}_i$ and
-$\hat{\overline{D}}_i$ are $SU(3)_C$ triplets that reside in the
-same $SU(5)$ multiplets as these Higgs-like states.
-
-If one wishes to maintain gauge coupling unification this set of
-states should be augmented by two extra $SU(2)$ doublet states
-$H^\prime$ and $\overline{H}^\prime$ belonging to other $27^\prime$
-and $\overline{27}^\prime$ multiplets that must be incomplete at low
-energies.
+(\hat{Q}_i, \, \hat{u}^c_i, \, \hat{d}^c_i, \, \hat{L}_i, \, \hat{e}^c_i)
++ (\hat{D}_i, \, \hat{\overline{D}}_i) + (\hat{S}_{i}) + (\hat{H}^u_i)
++ (\hat{H}^d_i) ,\ee
+where the $\hat{S}_{i}$, $\hat{H}^u_i$ and $\hat{H}^d_i$ have the quantum
+numbers of a SM singlet, and up-, down-type Higgs fields, respectively, and
+the $\hat{D}_i$ and $\hat{\overline{D}}_i$ are $SU(3)_C$ triplets that reside
+in the same $SU(5)$ multiplets as these Higgs-like states.
+
+If one wishes to maintain gauge coupling unification this set of states should
+be augmented by two extra $SU(2)$ doublet states $H^\prime$ and
+$\overline{H}^\prime$ belonging to other $27^\prime$ and $\overline{27}^\prime$
+multiplets that must be incomplete at low energies.
 
 The full superpotential for $E_6$ inspired models will then be,
-
 \be
-W_{E_6} = W_0 + W_1 + W_2,
-\label{Eq:e6-superpot}
-\ee where
+W_{E_6} = W_0 + W_1 + W_2 , \label{Eq:e6-superpot}
+\ee
+where
 \begin{eqnarray}
-W_0 &=& \lambda_{ijk} \hat{S}_i  \hat{H}^d_{j} \cdot\hat{H}^u_{k} + \kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\overline{D}}_k + h^N_{ijk} \hat{N}^c_i  \hat{H}^u_{j} \cdot \hat{L}_k \nonumber \\
-& & + y^U_{ijk} \hat{u}^c_i  \hat{H}^u_{j} \cdot \hat{Q}_k + y^D_{ijk} \hat{d}^c_i  \hat{Q}_k\cdot\hat{H}^d_{j}  + y^E_{ijk} \hat{e}^c_i  \hat{L}_k\cdot\hat{H}^d_{j} , \\
-W_1 &=& g^Q_{ijk} \hat{D}_i  \hat{Q}_j \cdot \hat{Q}_k + g^q_{ijk} \hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k, \\
-W_2 &=& g^N_{ijk} \hat{N}^c_i \hat{D}_j \hat{d}^c_k + g^E_{ijk} \hat{e}^c_i \hat{D}_j \hat{u}^c_k + g^D_{ijk}  \hat{Q}_i \cdot \hat{L}_j \hat{\bar{D}}_k.
+W_0 &=& \lambda_{ijk} \hat{S}_i \hat{H}^d_{j} \cdot\hat{H}^u_{k} +
+\kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\overline{D}}_k + h^N_{ijk} \hat{N}^c_i
+\hat{H}^u_{j} \cdot \hat{L}_k \nonumber \\
+& & + y^U_{ijk} \hat{u}^c_i \hat{H}^u_{j} \cdot \hat{Q}_k + y^D_{ijk}
+\hat{d}^c_i \hat{Q}_k \cdot \hat{H}^d_{j} + y^E_{ijk} \hat{e}^c_i \hat{L}_k
+\cdot\hat{H}^d_{j} , \\
+W_1 &=& g^Q_{ijk} \hat{D}_i \hat{Q}_j \cdot \hat{Q}_k + g^q_{ijk}
+\hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k , \\
+W_2 &=& g^N_{ijk} \hat{N}^c_i \hat{D}_j \hat{d}^c_k + g^E_{ijk} \hat{e}^c_i
+\hat{D}_j \hat{u}^c_k + g^D_{ijk} \hat{Q}_i \cdot \hat{L}_j \hat{\bar{D}}_k .
 \label{Eq:e6-superpot-parts}
 \end{eqnarray}
-
 Nonetheless while this model is very elegant so far, the
@@
 terms, involving the use of different discrete symmetries.  Here for
-the purposes of renormalisation group running we will simply include
+the purposes of renormalization group running we will simply include
 the following unsuppressed superpotential terms, which follows the
-approach taken in work on the cE$_6$SSM \cite{Athron:2009ue,
-  Athron:2009bs},
+approach taken in work on the cE$_6$SSM \cite{Athron:2009ue, Athron:2009bs},
 %
@@
 %
-where we denote by $\SuperField{H}_d^3\equiv \SuperField{H}_d$,
-$\SuperField{H}_u^3\equiv\SuperField{H}_u$ and $\SuperField{S}_3\equiv\SuperField{S}$ the third generation Higgs and SM singlet fields that are assumed to acquire non-zero VEVs.
-\section{\label{sec:ewsb}Electroweak Symmetry Breaking}
-% EWSB conditions in E6SSM
-The Higgs scalar potential for the $E_6$ models considered can be written as \cite{King:2005jy} 
-\begin{equation}\label{eq:E6VeffOneLoop}
-V=V_F+V_D+V_{\textrm{soft}}+\Delta V \, ,
+where we denote by $\SuperField{H}_d^3 \equiv \SuperField{H}_d$,
+$\SuperField{H}_u^3 \equiv \SuperField{H}_u$ and $\SuperField{S}_3 \equiv
+\SuperField{S}$ the third generation Higgs and SM singlet fields that are
+assumed to acquire non-zero VEVs.
+
+\section{\label{sec:ewsb}Electroweak Symmetry
+Breaking}
+
+The Higgs scalar potential for the $E_6$ models considered can be written as
+\cite{King:2005jy}
+\begin{equation} \label{eq:E6VeffOneLoop}
+V = V_F + V_D + V_{\textrm{soft}} + \Delta V \, ,
 \end{equation}
@@
 \begin{align}
-V_F&=\lambda^2|S|^2(|H_d|^2+|H_u|^2)+\lambda^2|H_d\cdot
-H_u|^2,\label{eq:E6VFterms}\\ 
-V_D&=\frac{\bar{g}^2}{8}\left (
-|H_u|^2-|H_d|^2\right )^2+\frac{g_2^2}{2}|H_d^\dagger
-H_u|^2+\frac{g_1'^2}{2}(Q_1|H_d|^2+Q_2|H_u|^2+Q_S|S|^2)^2,\label{eq:E6VDterms}\\ 
-V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_d|^2+m_{H_u}^2|H_u|^2+\Big
-[\lambda A_\lambda SH_d\cdot H_u+\textrm{h.c.}\Big
-].\label{eq:E6Vsoft}
+V_F &= \lambda^2 |S|^2 (|H_d|^2 + |H_u|^2) + \lambda^2 |H_d \cdot H_u|^2 ,
+\label{eq:E6VFterms} \\
+V_D &= \frac{\bar{g}^2}{8} \left (|H_u|^2 - |H_d|^2 \right )^2 +
+\frac{g_2^2}{2} |H_d^\dagger H_u|^2 + \frac{g_1'^2}{2} (Q_1 |H_d|^2 +
+Q_2 |H_u|^2 + Q_S |S|^2)^2 , \label{eq:E6VDterms} \\
+V_{\textrm{soft}} &= m_S^2 |S|^2 + m_{H_d}^2 |H_d|^2 + m_{H_u}^2 |H_u|^2 +
+\Big [\lambda A_\lambda S H_d \cdot H_u + \textrm{h.c.} \Big ] .
+\label{eq:E6Vsoft}
 \end{align}
-In these expressions $g_2$, $g'=\sqrt{3/5}g_1$, and $g_1'$ are the
+In these expressions $g_2$, $g' = \sqrt{3/5} g_1$, and $g_1'$ are the
 $SU(2)$, (non-GUT normalized) $U(1)_Y$ and $U(1)'$ gauge couplings
-respectively and $\bar{g}^2=g_2^2+g'^2$. The charges $Q_1$,
-$Q_2$ and $Q_S$ are effective $U(1)'$ charges for
-$H_d$, $H_u$ and $S$, respectively, and $\lambda\equiv \lambda_3$. In the case
-of the $U(1)_\chi$ model, $V_F$ may also contain an elementary
-$\mu$ term, as occurs in the MSSM. The term $\Delta V$ contains the
-Coleman-Weinberg contributions to the effective potential. For the purposes of this study, 
-we include in $\Delta V$ only the one-loop contributions from the top quark and stop squarks,
+respectively and $\bar{g}^2 = g_2^2 + g'^2$.  The charges $Q_1$, $Q_2$ and
+$Q_S$ are effective $U(1)'$ charges for $H_d$, $H_u$ and $S$, respectively,
+and $\lambda \equiv \lambda_3$.  In the case of the $U(1)_\chi$ model, $V_F$
+may also contain an elementary $\mu$ term, as occurs in the MSSM.  The term
+$\Delta V$ contains the Coleman-Weinberg contributions to the effective
+potential.  For the purposes of this study, we include in $\Delta V$ only the
+one-loop contributions from the top quark and stop squarks,
 \begin{equation}
-\Delta V=\frac{3}{32\pi^2}\left [ m_{\tilde{t}_1}^4\left ( \log\frac{m_{\tilde{t}_1}^2}{Q^2}-\frac{3}{2}\right )+m_{\tilde{t}_2}^4\left ( \log\frac{m_{\tilde{t}_2}^2}{Q^2}-\frac{3}{2}\right )-2m_t^4\left ( \log\frac{m_t^2}{Q^2}-\frac{3}{2}\right )\right ].
+\Delta V = \frac{3}{32\pi^2} \left [ m_{\tilde{t}_1}^4 \left ( \ln
+\frac{m_{\tilde{t}_1}^2}{Q^2} - \frac{3}{2} \right ) + m_{\tilde{t}_2}^4
+\left ( \ln \frac{m_{\tilde{t}_2}^2}{Q^2} - \frac{3}{2} \right ) - 2m_t^4
+\left ( \ln \frac{m_t^2}{Q^2} - \frac{3}{2} \right ) \right ] .
 \end{equation}
-Explicit expressions for the running $\overline{\textrm{DR}}$ top mass $m_t$ and stop masses $m_{\tilde{t}_{1,2}}$ are given 
-below.\\
-Demanding that the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real VEVs of the form
-\begin{equation}\label{eq:E6vevs}
-\langle H_d \rangle = \frac{1}{\sqrt{2}}\begin{pmatrix} v_1 \\ 0\end{pmatrix}, \; \langle H_u \rangle = \frac{1}{\sqrt{2}}\begin{pmatrix} 0 \\ v_2 \end{pmatrix}, \; \langle S \rangle =\frac{s}{\sqrt{2}}
+Explicit expressions for the running $\overline{\textrm{DR}}$ top mass $m_t$
+and stop masses $m_{\tilde{t}_{1,2}}$ are given below.
+
+Demanding that the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real
+VEVs of the form
+\begin{equation} \label{eq:E6vevs}
+\langle H_d \rangle = \frac{1}{\sqrt{2}} \begin{pmatrix} v_1 \\ 0
+\end{pmatrix} , \;
+\langle H_u \rangle = \frac{1}{\sqrt{2}} \begin{pmatrix} 0 \\ v_2
+\end{pmatrix} , \;
+\langle S \rangle =\frac{s}{\sqrt{2}} ,
 \end{equation}
 at the physical minimum leads to the minimization conditions
-\begin{subequations}\label{eq:E6EWSBConditions}
+\begin{subequations} \label{eq:E6EWSBConditions}
 \begin{align}
-&f_1=m_{H_d}^2v_1+\frac{\lambda^2}{2}(v_2^2+s^2)v_1-\frac{\lambda A_\lambda}{\sqrt{2}}sv_2-\frac{\bar{g}^2}{8}
-(v_2^2-v_1^2)v_1+D_{H_d}v_1+\frac{\partial \Delta V}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\
-&f_2=m_{H_u}^2v_2+\frac{\lambda^2}{2}(v_1^2+s^2)v_2-\frac{\lambda A_\lambda}{\sqrt{2}}sv_1+\frac{\bar{g}^2}{8}
-(v_2^2-v_1^2)v_2+D_{H_u}v_2+\frac{\partial \Delta V}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\
-&f_3=m_S^2s+\frac{\lambda^2}{2}(v_2^2+v_1^2)s-\frac{\lambda A_\lambda}{\sqrt{2}}v_2v_1+D_Ss+\frac{\partial \Delta V}{\partial s}=0.\label{eq:E6EWSBcondition3}
+&f_1 = m_{H_d}^2 v_1 + \frac{\lambda^2}{2} (v_2^2 + s^2) v_1-
+\frac{\lambda A_\lambda}{\sqrt{2}} s v_2 - \frac{\bar{g}^2}{8}
+(v_2^2 - v_1^2) v_1 + D_{H_d} v_1 + \frac{\partial \Delta V}{\partial v_1} = 0 ,
+\label{eq:E6EWSBcondition1} \\
+&f_2 = m_{H_u}^2 v_2 + \frac{\lambda^2}{2} (v_1^2 + s^2) v_2 -
+\frac{\lambda A_\lambda}{\sqrt{2}} s v_1 + \frac{\bar{g}^2}{8}
+(v_2^2 - v_1^2) v_2 + D_{H_u} v_2 + \frac{\partial \Delta V}{\partial v_2} = 0 ,
+\label{eq:E6EWSBcondition2} \\
+&f_3 = m_S^2 s + \frac{\lambda^2}{2} (v_2^2 + v_1^2) s -
+\frac{\lambda A_\lambda}{\sqrt{2}} v_2 v_1 + D_S s +
+\frac{\partial \Delta V}{\partial s} = 0 . \label{eq:E6EWSBcondition3}
 \end{align}
 \end{subequations}
-The quantities $D_{H_d}$, $D_{H_u}$ and $D_S$ appearing above are
-$U(1)'$ $D$-term contributions that are absent in the MSSM and NMSSM
-and are given by
-\begin{equation}\label{eq:E6Dterms}
-D_\phi\equiv \frac{g_1'^2}{2}\left (Q_1v_1^2+Q_2v_2^2+Q_Ss^2\right )Q_\phi.
+The quantities $D_{H_d}$, $D_{H_u}$ and $D_S$ appearing above are $U(1)'$
+$D$-term contributions that are absent in the MSSM and NMSSM and are given by
+\begin{equation} \label{eq:E6Dterms}
+D_\phi \equiv \frac{g_1'^2}{2} \left (Q_1 v_1^2 + Q_2 v_2^2 + Q_S s^2
+\right ) Q_\phi .
 \end{equation}
-We also include these $U(1)'$ $D$-term contributions in the diagonalised stop masses,
+We also include these $U(1)'$ $D$-term contributions in the diagonalised stop
+masses,
 \begin{align}
-  m_{\tilde{t}_{1,2}}^2&=\frac{1}{2}\bigg \{ m_{Q_3}^2+m_{u_3}^2+\frac{\bar{g}^2}{8}\left ( v_1^2-v_2^2\right )+D_Q+D_u+2m_t^2\nonumber\\
-&\quad{}\mp\sqrt{\left [ m_{Q_3}^2+m_{u_3}^2+\frac{1}{8}\left ( g_2^2-g_1^2\right )\left ( v_1^2-v_2^2\right ) + D_Q-D_u\right ]^2+4m_t^2X_t^2}\bigg \},
+m_{\tilde{t}_{1,2}}^2 &= \frac{1}{2} \bigg \{ m_{Q_3}^2 + m_{u_3}^2 +
+\frac{\bar{g}^2}{8} \left ( v_1^2 - v_2^2 \right ) + D_Q + D_u + 2 m_t^2
+\nonumber \\
+& \quad {} \mp \sqrt{\left [ m_{Q_3}^2 + m_{u_3}^2 + \frac{1}{8} \left (g_2^2
+- g_1^2 \right ) \left (v_1^2 - v_2^2 \right ) + D_Q - D_u \right ]^2 +
+4 m_t^2 X_t^2} \bigg \} ,
 \end{align}
-where $m_t^2=y_t^2v_2^2/2$, $X_t=A_t-\frac{\lambda s v_1}{\sqrt{2}v_2}$, $m_{Q_3}^2$, $m_{u_3}^2$ are soft breaking scalar masses and $A_t$ is a soft trilinear coupling.
-By definition we take $m_{\tilde{t}_1}$ to correspond to the lighter of the two states.\\
-As was noted in \cite{Athron:2013ipa}, the first two of the conditions Eq.~\ref{eq:E6EWSBConditions} may be rewritten in the form
-\begin{equation}\label{eq:E6MZequation}
-\frac{M_Z^2}{2}=-\frac{\lambda^2s^2}{2}+\frac{\tilde{m}_{H_d}^2-\tilde{m}_{H_u}^2\tan^2\beta}{\tan^2\beta-1}+\frac{D_{H_d}-D_{H_u}\tan^2\beta}{\tan^2\beta-1},
+where $m_t^2 = y_t^2 v_2^2 / 2$, $X_t = A_t -
+\frac{\lambda s v_1}{\sqrt{2} v_2}$, $m_{Q_3}^2$, $m_{u_3}^2$ are soft
+breaking scalar masses and $A_t$ is a soft trilinear coupling.  By definition
+we take $m_{\tilde{t}_1}$ to correspond to the lighter of the two states.
+
+As was noted in \cite{Athron:2013ipa}, the first two of the conditions
+Eq.~\ref{eq:E6EWSBConditions} may be rewritten in the form
+\begin{equation} \label{eq:E6MZequation}
+\frac{M_Z^2}{2} = -\frac{\lambda^2 s^2}{2} + \frac{\tilde{m}_{H_d}^2 -
+\tilde{m}_{H_u}^2 \tan^2\beta}{\tan^2\beta - 1} +
+\frac{D_{H_d} - D_{H_u} \tan^2\beta}{\tan^2\beta - 1} ,
 \end{equation}
-\begin{equation}\label{eq:E6sin2bequation}
-\sin 2\beta=\frac{\sqrt{2}\lambda A_{\lambda} s}{\tilde{m}_{H_d}^2+\tilde{m}_{H_u}^2+\lambda^2s^2+D_{H_d}+D_{H_u}},
+\begin{equation} \label{eq:E6sin2bequation}
+\sin 2\beta = \frac{\sqrt{2} \lambda A_{\lambda} s}
+{\tilde{m}_{H_d}^2 + \tilde{m}_{H_u}^2 + \lambda^2 s^2 + D_{H_d} + D_{H_u}} ,
 \end{equation}
-with $M_Z^2=\bar{g}^2v^2/4$, $v^2=v_1^2+v_2^2$ and $\tan\beta =
-v_2/v_1$ and where we have for convenience absorbed the effects of the
+with $M_Z^2 = \bar{g}^2 v^2 / 4$, $v^2 = v_1^2 + v_2^2$ and $\tan\beta =
+v_2 / v_1$ and where we have for convenience absorbed the effects of the
 loop corrections into the soft masses,
 \begin{align*}
-\tilde{m}_{H_d}^2&=m_{H_d}^2+\frac{1}{v_1}\frac{\partial \Delta
-  V}{\partial
-  v_1},\\ \tilde{m}_{H_u}^2&=m_{H_u}^2+\frac{1}{v_2}\frac{\partial
-  \Delta V}{\partial v_2}.
+\tilde{m}_{H_d}^2 &= m_{H_d}^2 + \frac{1}{v_1} \frac{\partial \Delta V}
+{\partial v_1} , \\
+\tilde{m}_{H_u}^2 &= m_{H_u}^2 + \frac{1}{v_2} \frac{\partial \Delta V}
+{\partial v_2} .
 \end{align*}
@@
 require that the $Z'$ mass be large, with for example bounds of
-$M_{Z'}\gtrsim 2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim
-2.62$ TeV in $U(1)_\chi$ models. To satisfy these
-limits typically requires large values of the singlet VEV $s$. For
-example $s\gtrsim 6$ TeV is required in the E$_6$SSM with
-$U(1)'=U(1)_N$, so that $|D_{H_1}|,|D_{H_2}|\gg M_Z^2$ for $E_6$
-models with $Q_S\neq 0$. As a result the remaining terms on the
+$M_{Z'} \gtrsim 2.51$ TeV in $U(1)_\psi$ models and $M_{Z'} \gtrsim 2.62$ TeV
+in $U(1)_\chi$ models.  To satisfy these limits typically requires large
+values of the singlet VEV $s$.  For example $s \gtrsim 6$ TeV is required in
+the E$_6$SSM with $U(1)' = U(1)_N$, so that $|D_{H_1}| , |D_{H_2}| \gg M_Z^2$
+for $E_6$ models with $Q_S \neq 0$.  As a result the remaining terms on the
 right-hand side of Eq.~(\ref{eq:E6MZequation}) must be tuned to cancel
-this very large contribution to $M_Z$. Moreover, because this
-is a large tree level fine tuning, it may negate the improvement in
-naturalness that is associated with having a reduced need for heavy
-superpartners. In $U(1)$ extended models for which $Q_S\neq 0$, the
-importance of the $Z^\prime$ mass to the fine tuning in these models
-can be made even clearer by writing Eq.~(\ref{eq:E6MZequation}) in the
-form given in \cite{Athron:2013ipa},
+this very large contribution to $M_Z$.  Moreover, because this is a large tree
+level fine tuning, it may negate the improvement in naturalness that is
+associated with having a reduced need for heavy superpartners.  In $U(1)$
+extended models for which $Q_S\neq 0$, the importance of the $Z^\prime$ mass
+to the fine tuning in these models can be made even clearer by writing
+Eq.~(\ref{eq:E6MZequation}) in the form given in \cite{Athron:2013ipa},
 \begin{equation}\label{eq:originalE6MZequation}
-c(\theta,\tan\beta)\frac{M_Z^2}{2}=-\frac{\lambda^2 s^2}{2}+\frac{\tilde{m}_{H_d}^2-\tilde{m}_{H_u}^2\tan^2\beta}{\tan^2\beta-1}+d(\theta,\tan\beta)\frac{M_{Z^\prime}^2}{2}
+c(\theta , \tan\beta) \frac{M_Z^2}{2} = -\frac{\lambda^2 s^2}{2} +
+\frac{\tilde{m}_{H_d}^2 - \tilde{m}_{H_u}^2 \tan^2\beta}{\tan^2\beta - 1}
++ d(\theta , \tan\beta) \frac{M_{Z^\prime}^2}{2} ,
 \end{equation}
@@
 \begin{align}
-c(\theta,\tan\beta)&=1-\frac{4}{\left ( \tan^2\beta-1\right )}\frac{g_1'^2}{\bar{g}^2}\left ( Q_1-Q_2\tan^2\beta \right )\left ( Q_1\cos^2\beta+Q_2\sin^2\beta \right ),\label{eq:cdefn}\\
-d(\theta,\tan\beta)&= \frac{Q_1-Q_2\tan^2\beta}{Q_S\left ( \tan^2\beta - 1\right )}.\label{eq:ddefn}
+c(\theta , \tan\beta) &= 1 - \frac{4}{\left (\tan^2\beta - 1 \right )}
+\frac{g_1'^2}{\bar{g}^2} \left (Q_1 - Q_2 \tan^2\beta \right )
+\left (Q_1 \cos^2\beta + Q_2 \sin^2\beta \right ) , \label{eq:cdefn} \\
+d(\theta , \tan\beta) &= \frac{Q_1 - Q_2 \tan^2\beta}
+{Q_S \left (\tan^2\beta - 1\right )} . \label{eq:ddefn}
 \end{align}
@@
 coefficient $d$.
-\section{\label{sec:tuningmeasure}The Fine Tuning Measure}
-As stated above, to quantify the resulting fine tuning we
-apply the traditional Barbieri-Giudice measure
-\cite{Ellis:1986yg,Barbieri:1987fn}. A specific model is characterised
-by a set of $n$ model parameters $\{p_i\}$ and is defined at some
-input scale $M_X$. For a given parameter $p$ in this set, one computes
-an associated sensitivity
-\begin{equation}\label{eq:bgmeasure}
-\Delta_p=\left | \frac{\partial \log M_Z^2}{\partial \log p}\right
-|=\left | \frac{p}{M_Z^2}\frac{\partial M_Z^2}{\partial p}\right |.
+
+\section{\label{sec:tuningmeasure}The Fine Tuning
+Measure}
+
+As stated above, to quantify the resulting fine tuning we apply the
+traditional Barbieri-Giudice measure \cite{Ellis:1986yg, Barbieri:1987fn}.
+A specific model is characterised by a set of $n$ model parameters $\{p_i\}$
+and is defined at some input scale $M_X$. For a given parameter $p$ in this
+set, one computes an associated sensitivity
+\begin{equation} \label{eq:bgmeasure}
+\Delta_p = \left | \frac{\partial \ln M_Z^2}{\partial \ln p} \right
+| = \left | \frac{p}{M_Z^2} \frac{\partial M_Z^2}{\partial p} \right | .
 \end{equation}
-The coefficient $\Delta_p$ measures the fractional variation in $M_Z^2$ resulting 
-from a given variation in the parameter $p$. The overall fine tuning is then taken to be $\Delta
-= \underset{i}{\max}\,\{\Delta_{p_i}\}$.\\
-
-The sensitivity $\Delta_p$ may be calculated directly
-from the expression for $M_Z^2$ in terms of the $p_i$ for a particular
-model, which leads to a so-called master formula for calculating the
-fine tuning. A master formula for the E$_6$SSM, obtained from the tree
-level scalar potential, was presented in \cite{Athron:2013ipa}. In
-order to derive the expression presented there, the fact that $s \gg
-v$ was made use of to neglect certain $O(v^2)$ terms in the EWSB
-conditions, greatly simplifying the final result. For the purposes of
-exploring a wider class of $E_6$ inspired models, we have derived
-the master formula without neglecting any $O(v^2)$ terms. The more
+The coefficient $\Delta_p$ measures the fractional variation in $M_Z^2$
+resulting from a given variation in the parameter $p$.  The overall fine
+tuning is then taken to be
+$\Delta = \underset{i}{\max} \, \{ \Delta_{p_i} \}$.\\
+
+The sensitivity $\Delta_p$ may be calculated directly from the expression
+for $M_Z^2$ in terms of the $p_i$ for a particular model, which leads to a
+so-called master formula for calculating the fine tuning.  A master formula
+for the E$_6$SSM, obtained from the tree level scalar potential, was
+presented in \cite{Athron:2013ipa}.  In order to derive the expression
+presented there, the fact that $s \gg v$ was made use of to neglect certain
+$O(v^2)$ terms in the EWSB conditions, greatly simplifying the final result.
+For the purposes of exploring a wider class of $E_6$ inspired models, we have
+derived the master formula without neglecting any $O(v^2)$ terms.  The more
 complete tree-level master formula is somewhat complicated.  This is
@@
 solve explicitly for the VEVs $v_1$, $v_2$ in terms of the Lagrangian
-parameters. It may be written in the form \be \Delta_p=|C|^{-1}\times
-\frac{|p|}{M_Z}\bigg|\sum_{q}\tilde{\Delta}_q\frac{\partial
-  q}{\partial p}\bigg|,
-\label{eq:E6masterformula}
+parameters.  It may be written in the form \be \Delta_p = |C|^{-1} \times
+\frac{|p|}{M_Z} \bigg | \sum_{q} \tilde{\Delta}_q \frac{\partial q}
+{\partial p} \bigg | , \label{eq:E6masterformula}
 \ee where the sum is over all low energy running parameters appearing
-in the tree level EWSB conditions, i.e., $q\in\{\lambda, A_\lambda,
-m_{H_d}^2,m_{H_u}^2,m_S^2,g_1,g_2,g_1'\}$. Expressions for the
+in the tree level EWSB conditions, i.e., $q \in \{\lambda , A_\lambda ,
+m_{H_d}^2 , m_{H_u}^2 , m_S^2 , g_1 , g_2 , g_1'\}$.  Expressions for the
 quantity $C$ and the $\tilde{\Delta}_q$ appearing above are given in
 Appendix \ref{app:masterformula}.  It should be noted that the effects
-of $U(1)$ mixing are neglected in deriving
-Eq.~(\ref{eq:E6masterformula}).\\
-However, it is well known in the
-MSSM that radiative corrections can significantly change (indeed,
-reduce) the fine tuning \cite{Cassel:2010px}. It is therefore
-important when studying the fine tuning to include loop corrections to
-the effective potential in the fine tuning measure. To do so it is
-most convenient to work in terms of the EWSB conditions
-Eq.~(\ref{eq:E6EWSBConditions}), rather than
-Eq.~(\ref{eq:E6MZequation}). The general procedure that we use is as follows
-(this method has also previously been applied in the NMSSM, see for example \cite{Ellwanger:2011mu}). For a model in which $m$ fields develop real
+of $U(1)$ mixing are neglected in deriving Eq.~(\ref{eq:E6masterformula}).
+
+However, it is well known in the MSSM that radiative corrections can
+significantly change (indeed, reduce) the fine tuning \cite{Cassel:2010px}.
+It is therefore important when studying the fine tuning to include loop
+corrections to the effective potential in the fine tuning measure.  To do so
+it is most convenient to work in terms of the EWSB conditions
+Eq.~(\ref{eq:E6EWSBConditions}), rather than Eq.~(\ref{eq:E6MZequation}).
+The general procedure that we use is as follows (this method has also
+previously been applied in the NMSSM, see for example
+\cite{Ellwanger:2011mu}).  For a model in which $m$ fields develop real
 VEVs (e.g. $m=2$ in the MSSM, $m=3$ in the NMSSM and in the $E_6$
 models considered), we require that the $m$ minimization conditions
-\begin{equation}\label{eq:EWSBconditions}
-f_1=f_2=\dotsb=f_m=0
+\begin{equation} \label{eq:EWSBconditions}
+f_1 = f_2 = \dotsb = f_m = 0
 \end{equation}
 continue to hold under an arbitrary variation in a model parameter
-$p\rightarrow p+\delta p$, so that the variations $\delta f_i$ satisfy
-\begin{equation}\label{eq:EWSBvariations}
-\delta f_1 = \delta f_2=\dotsb =\delta f_m =0.
+$p \rightarrow p + \delta p$, so that the variations $\delta f_i$ satisfy
+\begin{equation} \label{eq:EWSBvariations}
+\delta f_1 = \delta f_2 = \dotsb = \delta f_m = 0 .
 \end{equation}
 Each $f_i$ is a function of the VEVs $v_j$ and $l$ running parameters
-$q_k$ evaluated at the scale of EWSB, $f_i=f_i(v_j,q_k)$. Thus for
+$q_k$ evaluated at the scale of EWSB, $f_i = f_i(v_j , q_k)$.  Thus for
 each $f_i$ we have that
-\begin{equation}\label{eq:EWSBchainrule}
-\delta f_i = \sum_{j=1}^m \frac{\partial f_i}{\partial
-  v_j}\frac{\partial v_j}{\partial p}+\sum_{k=1}^l \frac{\partial
-  f_i}{\partial q_k}\frac{\partial q_k}{\partial p}=0.
+\begin{equation} \label{eq:EWSBchainrule}
+\delta f_i = \sum_{j=1}^m \frac{\partial f_i}{\partial v_j}
+\frac{\partial v_j}{\partial p} + \sum_{k=1}^l \frac{\partial f_i}
+{\partial q_k} \frac{\partial q_k}{\partial p} = 0 .
 \end{equation}
@@
 expressed as
-\begin{equation}\label{eq:tuningsystem}
-M_h^2\begin{pmatrix}
-\frac{\partial v_1}{\partial p_1} & \cdots & \frac{\partial v_1}{\partial p_n} \\
+\begin{equation} \label{eq:tuningsystem}
+M_h^2 \begin{pmatrix}
+\frac{\partial v_1}{\partial p_1} & \cdots &
+\frac{\partial v_1}{\partial p_n} \\
 \vdots & \ddots & \vdots \\
 \frac{\partial v_m}{\partial p_1} & \cdots & \frac{\partial v_m}{\partial p_n}
-\end{pmatrix}=
--\begin{pmatrix}
-\frac{\partial f_1}{\partial q_1} & \cdots & \frac{\partial f_1}{\partial q_l} \\
+\end{pmatrix} = -\begin{pmatrix}
+\frac{\partial f_1}{\partial q_1} & \cdots & \frac{\partial f_1}
+{\partial q_l} \\
 \vdots & \ddots & \vdots \\
@@
 \begin{pmatrix}
-\frac{\partial q_1}{\partial p_1} & \cdots & \frac{\partial q_1}{\partial p_n} \\
+\frac{\partial q_1}{\partial p_1} & \cdots & \frac{\partial q_1}
+{\partial p_n} \\
 \vdots & \ddots & \vdots \\
 \frac{\partial q_l}{\partial p_1} & \cdots & \frac{\partial q_l}{\partial p_n}
-\end{pmatrix}.
+\end{pmatrix} .
 \end{equation}
 The quantities forming the first matrix on the right-hand side, along
-with $M_h^2$, are easily calculated by differentiating the conditions in Eq.~(\ref{eq:E6EWSBConditions})
-with respect to the VEVs and the running parameters. 
-The remaining derivatives $\partial q_k /\partial p$ must be determined using the
-RGEs. Once these have been obtained, it is straightforward to solve
-for the $\partial v_i /\partial p$. The sensitivities 
-$\Delta_p$ are then simply linear combinations of the $\partial
-v_i/\partial p$ and $\partial q_k/\partial p$. The effects of radiative corrections
-may be easily included by including the Coleman-Weinberg potential
-contributions $\Delta V$ in the EWSB conditions.\\
-Evaluating the derivatives
-$\partial q_k/\partial p$ must in general be done by numerically
-integrating the two-loop RGEs. This is time consuming and presents an
-obstacle to doing large scans of the parameter space. For studying
-models defined at low energies, as we do here, we can take advantage
+with $M_h^2$, are easily calculated by differentiating the conditions in
+Eq.~(\ref{eq:E6EWSBConditions}) with respect to the VEVs and the running
+parameters.  The remaining derivatives $\partial q_k /\partial p$ must be
+determined using the RGEs.  Once these have been obtained, it is
+straightforward to solve for the $\partial v_i / \partial p$.  The
+sensitivities $\Delta_p$ are then simply linear combinations of the
+$\partial v_i / \partial p$ and $\partial q_k / \partial p$.  The effects of
+radiative corrections may be easily included by including the
+Coleman-Weinberg potential contributions $\Delta V$ in the EWSB conditions.
+
+Evaluating the derivatives $\partial q_k / \partial p$ must in general be
+done by numerically integrating the two-loop RGEs.  This is time consuming
+and presents an obstacle to doing large scans of the parameter space.  For
+studying models defined at low energies, as we do here, we can take advantage
 of the fact that the running is over much smaller scales than when
-evolving up to the GUT scale. This makes it possible to use
-approximate analytic solutions to the RGEs that exhibit good accuracy
-over the range of scales considered. Given the two-loop RG equation
-for a parameter $q$,
-\begin{equation}\label{eq:rge}
-\frac{\textrm{d}q}{\mathrm{d}t}\equiv \beta_q =\frac{1}{16\pi^2}\beta_q^{(1)}+\frac{1}{(16\pi^2)^2}\beta_q^{(2)},\qquad t\equiv \log\frac{Q}{M_X},
+evolving up to the GUT scale.  This makes it possible to use approximate
+analytic solutions to the RGEs that exhibit good accuracy over the range of
+scales considered.  Given the two-loop RG equation for a parameter $q$,
+\begin{equation} \label{eq:rge}
+\frac{\textrm{d}q}{\mathrm{d}t} \equiv \beta_q = \frac{1}{16\pi^2}
+\beta_q^{(1)} + \frac{1}{(16\pi^2)^2} \beta_q^{(2)} , \qquad t \equiv
+\ln \frac{Q}{M_X} ,
 \end{equation}
@@
 parameter at the scale $Q$,
-\begin{align}\label{eq:rgeapproxsoln}
-q(Q)&=q(M_X)+\int_0^t \beta_q(t')\;\textrm{d}t'\approx q(M_X)+\frac{t}{16\pi^2}\left ( \beta_q^{(1)}+\frac{\beta_q^{(2)}}{16\pi^2}\right )+\frac{t^2}{32\pi^2}\frac{\textrm{d}\beta_q^{(1)}}{\textrm{d}t}+\mathcal{O}(t^2).
+\begin{align} \label{eq:rgeapproxsoln}
+q(Q) &= q(M_X) + \int_0^t \beta_q(t') \; \textrm{d}t' \approx q(M_X) +
+\frac{t}{16\pi^2} \left ( \beta_q^{(1)} + \frac{\beta_q^{(2)}}{16\pi^2}
+\right ) + \frac{t^2}{32\pi^2} \frac{\textrm{d}\beta_q^{(1)}}{\textrm{d}t}
++ O(t^2) .
 \end{align}
 Expanded to this order we obtain the leading log (LL) and next-to-LL
-(NLL) contributions at two-loop order. The $\mathcal{O}(t^2)$ terms
+(NLL) contributions at two-loop order.  The $O(t^2)$ terms
 not displayed above are formally of 3-loop order and are
 neglected. The derivative of the one-loop $\beta$ function is given by
-\begin{equation}\label{eq:1loopbetaderivative}
-\frac{\textrm{d}\beta_q^{(1)}}{\textrm{d}t}=\frac{1}{16\pi^2}\sum_{q_k}\beta_{q_k}^{(1)}\frac{\partial \beta_q^{(1)}}{\partial q_k},
+\begin{equation} \label{eq:1loopbetaderivative}
+\frac{\textrm{d}\beta_q^{(1)}}{\textrm{d}t} = \frac{1}{16\pi^2} \sum_{q_k}
+\beta_{q_k}^{(1)} \frac{\partial \beta_q^{(1)}}{\partial q_k} ,
 \end{equation}
 where the sum is over all running parameters appearing in
-$\beta_q^{(1)}$. The $\beta$ functions appearing on the right hand
-side of Eqs. (\ref{eq:rgeapproxsoln}) and
-(\ref{eq:1loopbetaderivative}) are evaluated at the scale $M_X$,
-giving a simple analytic expression for the parameters at the scale of
-EWSB in terms of the model parameters at $M_X$. Explicit results for
-the relevant series expansions in the MSSM and $E_6$ models are
-presented in Appendix \ref{app:rges}.
-%%\section{\label{sec:numericalprocedure}Numerical Procedure}
+$\beta_q^{(1)}$.  The $\beta$ functions appearing on the right hand side of
+Eqs.~(\ref{eq:rgeapproxsoln}) and (\ref{eq:1loopbetaderivative}) are
+evaluated at the scale $M_X$, giving a simple analytic expression for the
+parameters at the scale of EWSB in terms of the model parameters at $M_X$.
+Explicit results for the relevant series expansions in the MSSM and $E_6$
+models are presented in Appendix \ref{app:rges}.
 
@@
 make use of the two-loop RGEs generated by SARAH
-\cite{Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta} and
-FlexibleSUSY \cite{Athron:2014yba}, which also makes use of SOFTSUSY \cite{Allanach:2001kg,Allanach:2013kza}. The CP-even Higgs masses are
+\cite{Staub:2009bi, Staub:2010jh, Staub:2012pb, Staub:2013tta} and
+FlexibleSUSY \cite{Athron:2014yba}, which also makes use of SOFTSUSY
+\cite{Allanach:2001kg, Allanach:2013kza}.  The CP-even Higgs masses are
 calculated including the leading one-loop effective potential
@@
 MSSM fine tuning expressions were implemented into a modified version
-of SOFTSUSY 3.3.10 \cite{Allanach:2001kg}. For
-consistency with the results produced in the $E_6$ models, and for
-computational speed, for our main scans only the dominant one- and
-two-loop corrections to the CP-even Higgs masses were
-included. Finally, in all of the results below the fine tuning was
-evaluated at the scale
-$Q=M_{\textrm{SUSY}}=\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where
-$m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop
-masses evaluated at $Q=M_{\textrm{SUSY}}$.
-
-% Our results. Plots to go in here:
-%    - tuning as a function of stop mass for the MSSM and E6SSM
+of SOFTSUSY 3.3.10 \cite{Allanach:2001kg}.  For consistency with the results
+produced in the $E_6$ models, and for computational speed, for our main scans
+only the dominant one- and two-loop corrections to the CP-even Higgs masses
+were included.  Finally, in all of the results below the fine tuning was
+evaluated at the scale $Q = M_{\textrm{SUSY}} =
+\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$ are the
+running $\overline{\textrm{DR}}$ stop masses evaluated at
+$Q = M_{\textrm{SUSY}}$.
+
 As discussed in the introduction many recent papers interested in
@@
 \includegraphics{mssm_higgs_tuning_bw_var.png}}
-\caption{\textit{Left panel:} Scatter plot of fine tuning in the MSSM as a function of
-the lightest stop mass, $m_{\tilde{t}_1}$, for the cutoff scales (from 
-bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV. 
-\textit{Right panel:} Scatter plot of fine tuning in the MSSM as a function of
-the lightest Higgs mass, $m_{h_1}$, for the cutoff scales (from 
-bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
+\caption{\textit{Left panel:} Scatter plot of fine tuning in the MSSM as a
+function of the lightest stop mass, $m_{\tilde{t}_1}$, for the cutoff scales
+(from bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and
+$M_X=10^{16}$ GeV.  \textit{Right panel:} Scatter plot of fine tuning in the
+MSSM as a function of the lightest Higgs mass, $m_{h_1}$, for the cutoff
+scales (from bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and
+$M_X=10^{16}$ GeV.}
 \label{Fig:mssmstoptuning}
@@
 \end{figure}
+
 To illustrate this, in the left panel of Fig.~\ref{Fig:mssmstoptuning}
-we show the variation in fine tuning for $M_X=20$ TeV, $50$ TeV, $100$
+we show the variation in fine tuning for $M_X = 20$ TeV, $50$ TeV, $100$
 TeV and $10^{16}$ GeV when we scan over the stop masses and mixing,
-with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and
-$-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$.  The remaining
+with $500 \textrm{ GeV} \leq m_{Q_3} , m_{u_3} \leq 10 \textrm{ TeV}$ and
+$-3810\textrm{ GeV} \leq A_t \leq -20 \textrm{ GeV}$.  The remaining
 parameters we fix such that at $M_{\rm SUSY}$ they have the values
-$\mu=-97.5$ GeV, $B=-84.8$ GeV, $M_1=92.1$ GeV, $M_2=95.9$ GeV,
-$M_3=352$ GeV, $A_b=-117.9$ GeV, $A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV,
-$m_{e_i}=204$ GeV, $m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}=436$ GeV and
-$m_{d_i}=438$ GeV ($i=1,2,3$). Here we denote by $M_1$, $M_2$ and $M_3$
-the soft gaugino masses for $U(1)$, $SU(2)$ and $SU(3)$, while $A_b$ and
+$\mu = -97.5$ GeV, $B = -84.8$ GeV, $M_1 = 92.1$ GeV, $M_2 = 95.9$ GeV,
+$M_3 = 352$ GeV, $A_b = -117.9$ GeV, $A_\tau = -7.8$ GeV, $m_{L_i} = 400$ GeV,
+$m_{e_i} = 204$ GeV, $m_{Q_{1,2}} = 438$ GeV, $m_{u_{1,2}} = 436$ GeV and
+$m_{d_i} = 438$ GeV ($i = 1 , 2 , 3$).  Here we denote by $M_1$, $M_2$ and
+$M_3$ the soft gaugino masses for $U(1)$, $SU(2)$ and $SU(3)$, while $A_b$ and
 $A_\tau$ are soft trilinear couplings and the $m_\phi$ are soft scalar
-masses for the indicated fields. The soft bilinear
-coupling $B$ is defined such that at tree level the mass of the CP-odd MSSM Higgs boson
-reads $m_A^2=2B\mu/\sin 2\beta$. All off-diagonal couplings and scalar masses
+masses for the indicated fields.  The soft bilinear coupling $B$ is defined
+such that at tree level the mass of the CP-odd MSSM Higgs boson reads
+$m_A^2 = 2 B \mu / \sin 2\beta$.  All off-diagonal couplings and scalar masses
 are set to zero, as are the first and second generation Yukawa couplings
@@
 can be obtained without much tuning in this unrealistic case where we
-have minimised other sources of tuning.  On the other hand the tuning
+have minimized other sources of tuning.  On the other hand the tuning
 becomes more severe as we increase the cutoff such that for $M_X =
@@
 
-%    - full scatter plots of MSSM and E6SSM, including different
-%      M_Z' values
-
 Since the stop mass does not have such a large impact on the fine
@@
 between the MSSM and E$_6$SSM for two different values of the
-$Z^\prime$ mass. We choose to look at $M_{Z^\prime}=2.5$ TeV, which is
-just above the current limits, and $M_{Z^\prime}=4.5$ TeV, which
+$Z^\prime$ mass.  We choose to look at $M_{Z^\prime} = 2.5$ TeV, which is
+just above the current limits, and $M_{Z^\prime} = 4.5$ TeV, which
 should be in reach in run II at the LHC \cite{Godfrey:2013eta} and
@@
 most relevant for the fine tuning and the Higgs mass.  Therefore the
-set of parameters which we vary includes $\mu$, $B$ and $\tan \beta$
-for the MSSM, and $\lambda$, $A_\lambda$ and $\tan \beta$, for the
+set of parameters which we vary includes $\mu$, $B$ and $\tan\beta$
+for the MSSM, and $\lambda$, $A_\lambda$ and $\tan\beta$, for the
 E$_6$SSM, which appear at tree level in the EWSB conditions of the
@@
 assume their associated soft trilinears vanish.  Similarly we take
-$A_b=A_\tau=0$ GeV. The $U(1)$ gaugino soft mass $M_1$ was fixed to
- $M_1=300$ GeV, and we fix $M_3=2000$ GeV. Additionally, in the
+$A_b = A_\tau = 0$ GeV.  The $U(1)$ gaugino soft mass $M_1$ was fixed to
+$M_1 = 300$ GeV, and we fix $M_3 = 2000$ GeV.  Additionally, in the
 E$_6$SSM the $U(1)_N$ gaugino soft mass $M_1'$ is held fixed with
- $M_1'=M_1=300$ GeV, and $\mu^\prime=5$ TeV.
+$M_1' = M_1 = 300$ GeV, and $\mu^\prime = 5$ TeV.
 
@@
 \hline
-$2 \leq \tan\beta \leq 50$& $2 \leq \tan\beta \leq 50$ \\
-$-1\textrm{ TeV } \leq \mu \leq 1 \textrm{ TeV}$ & $-3 \leq \lambda \leq 3$\\
-$-1\textrm{ TeV } \leq B \leq 1\textrm{ TeV}$ & $-10\textrm{ TeV } \leq A_\lambda \leq 10\textrm{ TeV}$ \\
-$ 200 \textrm{ GeV } \leq m_{Q_3} \leq 2000 \textrm { GeV}$ & $ 200 \textrm{ GeV } \leq m_{Q_3} \leq 2000 \textrm { GeV}$\\
-$ 200 \textrm{ GeV } \leq m_{u_3} \leq 2000 \textrm { GeV}$ & $ 200 \textrm{ GeV } \leq m_{u_3} \leq 2000 \textrm { GeV}$\\
-$ -10 \textrm{ TeV } \leq A_t \leq 10 \textrm { TeV}$ & $ -10 \textrm{ TeV } \leq A_t \leq 10 \textrm { TeV}$\\
-$M_2=100\textrm{ GeV, } 1050\textrm{ GeV, } 2000 \textrm{ GeV}$ & $M_2=100\textrm{ GeV, } 1050\textrm{ GeV, } 2000 \textrm{ GeV}$ \\
+$2 \leq \tan\beta \leq 50$ & $2 \leq \tan\beta \leq 50$ \\
+$-1 \textrm{ TeV } \leq \mu \leq 1 \textrm{ TeV}$ & $-3 \leq \lambda \leq 3$\\
+$-1 \textrm{ TeV } \leq B \leq 1 \textrm{ TeV}$ & $-10 \textrm{ TeV } \leq
+A_\lambda \leq 10 \textrm{ TeV}$ \\
+$ 200 \textrm{ GeV } \leq m_{Q_3} \leq 2000 \textrm { GeV}$ & $200
+\textrm{ GeV } \leq m_{Q_3} \leq 2000 \textrm { GeV}$ \\
+$200 \textrm{ GeV } \leq m_{u_3} \leq 2000 \textrm { GeV}$ & $200
+\textrm{ GeV } \leq m_{u_3} \leq 2000 \textrm { GeV}$ \\
+$-10 \textrm{ TeV } \leq A_t \leq 10 \textrm { TeV}$ & $-10
+\textrm{ TeV } \leq A_t \leq 10 \textrm { TeV}$ \\
+$M_2 = 100 \textrm{ GeV, } 1050 \textrm{ GeV, } 2000 \textrm{ GeV}$ &
+$M_2 = 100 \textrm{ GeV, } 1050 \textrm{ GeV, } 2000 \textrm{ GeV}$ \\
 \end{tabular}
@@
 \caption{Scatter plot of fine tuning vs lightest Higgs mass for the
-  MSSM (light blue, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (dark blue, middle band) and
-  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (dark yellow, top band). Note that there are points for which
-the fine tuning in the MSSM and E$_6$SSM with $M_{Z'}=2.5$ TeV is larger than is visible on this plot
-and those below;
-however these points are obscured by the overlaid data for the E$_6$SSM with $M_{Z'}=4.5$ TeV, and it is the 
-lower bound on the achievable tuning that is of interest here.}
+MSSM (light blue, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV
+(dark blue, middle band) and E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV
+(dark yellow, top band).  Note that there are points for which
+the fine tuning in the MSSM and E$_6$SSM with $M_{Z'} = 2.5$ TeV is larger
+than is visible on this plot and those below; however these points are
+obscured by the overlaid data for the E$_6$SSM with $M_{Z'} = 4.5$ TeV, and
+it is the lower bound on the achievable tuning that is of interest here.}
 \label{Fig:e6ssmvsmssm}
@@
 \end{figure}
+
 In Fig.~\ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
@@
 minimum fine tuning that can be achieved is
-$\Delta_{\textrm{min}}\approx 121$. If run II of the LHC further
+$\Delta_{\textrm{min}} \approx 121$.  If run II of the LHC further
 pushes up the limit on the $Z^\prime$ mass to be above $4.5$ TeV then
 the fine tuning in the model will be greater than at least
-$\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$
+$\Delta_{\textrm{min}} \approx 394$ for a Higgs mass between $124.5$
 GeV and $125.5$ GeV.
@@
 Current limits placed by CMS and ATLAS extend up to
-$m_{\tilde{\chi}^\pm_1} \approx 700-740$ GeV if there are light
+$m_{\tilde{\chi}^\pm_1} \approx 700 - 740$ GeV if there are light
 sleptons \cite{Khachatryan:2014qwa, Aad:2014nua} with much weaker
@@
 summary plots of these limit may be found on the public pages of
-  ATLAS,
-  \url{https://atlas.web.cern.ch/Atlas/GROUPS/PHYSICS/CombinedSummaryPlots/SUSY/ATLAS_SUSY_EWSummary/ATLAS_SUSY_EWSummary.png}
-  and CMS
-  \url{http://cms.web.cern.ch/sites/cms.web.cern.ch/files/styles/large/public/field/image/Image_03_exclusion_Combined.png?itok=8FMBpu_1}.}.
+ATLAS, \url{https://atlas.web.cern.ch/Atlas/GROUPS/PHYSICS/CombinedSummaryPlots/SUSY/ATLAS_SUSY_EWSummary/ATLAS_SUSY_EWSummary.png}
+and CMS \url{http://cms.web.cern.ch/sites/cms.web.cern.ch/files/styles/large/public/field/image/Image_03_exclusion_Combined.png?itok=8FMBpu_1}.}.
 
@@
 \includegraphics{mssm_chargino_plot_bw_var.png}}%%
-\caption{Scatter plot of fine tuning vs lightest Higgs mass in the MSSM with $m_{\tilde{\chi}^\pm_1} = 200$ GeV shown in light blue 
-(bottom band), $m_{\tilde{\chi}^\pm_1} = 500$ GeV in dark blue (middle band), and $m_{\tilde{\chi}^\pm_1} = 700$ GeV in dark yellow
-(top band).}
+\caption{Scatter plot of fine tuning vs lightest Higgs mass in the MSSM with
+$m_{\tilde{\chi}^\pm_1} = 200$ GeV shown in light blue (bottom band),
+$m_{\tilde{\chi}^\pm_1} = 500$ GeV in dark blue (middle band), and
+$m_{\tilde{\chi}^\pm_1} = 700$ GeV in dark yellow (top band).}
 \label{Fig:chargino-plot}
@@
 other $U(1)$ extensions for the same $Z^\prime$ masses as we did for the
-E$_6$SSM.  To simplify the analysis we fix $\tan \beta = 10$, but scan
+E$_6$SSM.  To simplify the analysis we fix $\tan\beta = 10$, but scan
 over the remaining parameters as in Table \ref{tab:scanranges} and fix
@@
 on the obtainable tuning in each model, the parameter values for points in
-these main grid scans with a low fine tuning were then used as the starting points for
-smaller scans about those values. In these smaller scans the parameters were more finely
-varied to populate the low fine tuning regions.
+these main grid scans with a low fine tuning were then used as the starting
+points for smaller scans about those values.  In these smaller scans the
+parameters were more finely varied to populate the low fine tuning regions.
 
@@
 \includegraphics{e6eta_tb10_tuning_vs_higgs_bw_var.png}}%%
-\caption{\textit{Top left panel:} Scatter plot of the fine tuning vs lightest Higgs mass in the $U(1)_I$ model.
-\textit{Top right panel:} Scatter plot of the fine tuning vs lightest Higgs mass in the $U(1)_\psi$ model.
-\textit{Bottom panel:} Scatter plot of the fine tuning vs lightest Higgs mass in the $U(1)_\eta$ model.
-In each plot points with $M_{Z^\prime} = 2.5$ TeV are shown in dark blue
-(bottom band), and points with $M_{Z^\prime} = 4.5$ TeV are shown in dark yellow (top band).}
+\caption{\textit{Top left panel:} Scatter plot of the fine tuning vs lightest
+Higgs mass in the $U(1)_I$ model.  \textit{Top right panel:} Scatter plot of
+the fine tuning vs lightest Higgs mass in the $U(1)_\psi$ model.
+\textit{Bottom panel:} Scatter plot of the fine tuning vs lightest Higgs mass
+in the $U(1)_\eta$ model.  In each plot points with $M_{Z^\prime} = 2.5$ TeV
+are shown in dark blue (bottom band), and points with $M_{Z^\prime} = 4.5$
+TeV are shown in dark yellow (top band).}
 \label{Fig:othere6modelsvsmssm}
@@
 
-As can be seen in Fig.~\ref{Fig:othere6modelsvsmssm} the severity of the tunings varies quite
-a bit.  This is because the charges appear as coefficients in front of
-the $Z^\prime$ mass in the EWSB condition.  These charges change the
-value of the coefficient $d$ in Eq.~(\ref{eq:originalE6MZequation}).
-The values of the coefficient $d$ in each model, for $\tan\beta = 10$,
-is $\{-0.01, 0.40, 0.50, 0.81 \}$ for $\{U(1)_I, U(1)_N, U(1)_\psi,
-U(1)_\eta \}$ and this determines which of the models are most tuned.
+As can be seen in Fig.~\ref{Fig:othere6modelsvsmssm} the severity of the
+tunings varies quite a bit.  This is because the charges appear as
+coefficients in front of the $Z^\prime$ mass in the EWSB condition.  These
+charges change the value of the coefficient $d$ in
+Eq.~(\ref{eq:originalE6MZequation}).  The values of the coefficient $d$ in
+each model, for $\tan\beta = 10$, is $\{-0.01 , 0.40 , 0.50 , 0.81 \}$ for
+$\{U(1)_I , U(1)_N , U(1)_\psi , U(1)_\eta \}$ and this determines which of
+the models are most tuned.
 
@@
 D-terms to the lightest Higgs which is predominantly $H_u$ at large
-$\tan \beta$ are suppressed, making it difficult to raise the Higgs
+$\tan\beta$ are suppressed, making it difficult to raise the Higgs
 mass in the same way as happens in the other models and explaining why
@@
 $\lambda_{1,2}(M_{\mathrm{SUSY}})$ & $-$ & $-$ & $0.2$ & $0.13$ \\
-$\mu_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & $689.7$ & $1013.5$ & $1093.3$ & $1313.0$ \\
-$B_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & $345.7$ & $1032.5$ & $3792.7$ & $817.8$ \\
+$\mu_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & $689.7$ & $1013.5$ &
+$1093.3$ & $1313.0$ \\
+$B_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & $345.7$ & $1032.5$ &
+$3792.7$ & $817.8$ \\
 $A_\tau(M_{\mathrm{SUSY}})$ [GeV] & $0$ & $-5057.9$ & $0$ & $-88.5$ \\
@@
 $A_t(M_{\mathrm{SUSY}})$ [GeV] & $-3335.7$ & $-2734.8$ & $-1100$ & $-1103.2$ \\
-$m_{L_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.35\times 10^6$ & $2.5\times 10^7$ & $4.94\times 10^6$ \\
-$m_{L_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.22\times 10^6$ & $2.5\times 10^7$ & $4.90\times 10^6$ \\
-$m_{e_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.27\times 10^6$ & $2.5\times 10^7$ & $5.21\times 10^6$ \\
-$m_{e_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.03\times 10^6$ & $2.5\times 10^7$ & $5.11\times 10^6$ \\
-$m_{Q_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.37\times 10^6$ & $2.5\times 10^7$ & $5.76\times 10^6$ \\
-$m_{Q_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.45\times 10^6$ & $3.97\times 10^6$ & $4.50\times 10^5$ & $3.61\times 10^6$ \\
-$m_{u_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.30\times 10^6$ & $2.5\times 10^7$ & $5.54\times 10^6$ \\
-$m_{u_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.0 \times 10^6$ & $6.60\times10^5$& $5.86\times 10^5$ & $2.04\times 10^6$ \\
-$m_{d_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.30\times 10^6$ & $2.5\times 10^7$ & $5.88\times 10^6$ \\
-$m_{d_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.03\times 10^6$ & $2.5\times 10^7$ & $5.78\times 10^6$ \\
-$m_{H_d}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $1.82\times 10^6$ & $8.96\times 10^6$ & $4.06\times 10^7$ & $1.04\times 10^7$ \\
-$m_{H_u}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $-3.60\times 10^5$ & $-9.35\times 10^5$ & $5.0\times 10^5$ & $-2.66\times 10^5$ \\
-$m_S^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $-$ & $-$ & $-3.10\times 10^6$ & $-3.17 \times 10^6$ \\
+$m_{L_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ &
+$6.35\times 10^6$ & $2.5\times 10^7$ & $4.94\times 10^6$ \\
+$m_{L_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ &
+$6.22\times 10^6$ & $2.5\times 10^7$ & $4.90\times 10^6$ \\
+$m_{e_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ &
+$6.27\times 10^6$ & $2.5\times 10^7$ & $5.21\times 10^6$ \\
+$m_{e_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ &
+$6.03\times 10^6$ & $2.5\times 10^7$ & $5.11\times 10^6$ \\
+$m_{Q_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ &
+$7.37\times 10^6$ & $2.5\times 10^7$ & $5.76\times 10^6$ \\
+$m_{Q_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.45\times 10^6$ &
+$3.97\times 10^6$ & $4.50\times 10^5$ & $3.61\times 10^6$ \\
+$m_{u_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ &
+$7.30\times 10^6$ & $2.5\times 10^7$ & $5.54\times 10^6$ \\
+$m_{u_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.0 \times 10^6$ &
+$6.60\times10^5$& $5.86\times 10^5$ & $2.04\times 10^6$ \\
+$m_{d_{1,2}}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ &
+$7.30\times 10^6$ & $2.5\times 10^7$ & $5.88\times 10^6$ \\
+$m_{d_3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ &
+$7.03\times 10^6$ & $2.5\times 10^7$ & $5.78\times 10^6$ \\
+$m_{H_d}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $1.82\times 10^6$ &
+$8.96\times 10^6$ & $4.06\times 10^7$ & $1.04\times 10^7$ \\
+$m_{H_u}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $-3.60\times 10^5$ &
+$-9.35\times 10^5$ & $5.0\times 10^5$ & $-2.66\times 10^5$ \\
+$m_S^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $-$ & $-$ & $-3.10\times 10^6$ &
+$-3.17 \times 10^6$ \\
 $M_1(M_{\mathrm{SUSY}})$ [GeV] & $300$ & $260.8$ & $300$ & $173.4$ \\
@@
 \end{ruledtabular}
-\caption{Parameters for the MSSM and E$_6$SSM benchmark points. In the E$_6$SSM we define $\mu_{\mathrm{eff}}\equiv \lambda s/\sqrt{2}$ and
-$B_{\mathrm{eff}}=A_\lambda$.
-The soft masses $m_{H_d}^2$, $m_{H_u}^2$ and $m_S^2$ are those that satisfy the EWSB conditions including 1-loop Coleman-Weinberg corrections involving the top and stops.
-For E$_6$SSM BM1 (BM2) we also set $\mu^\prime = 5000.0$ $(897.9)$ GeV, $B\mu^\prime = 5000.0$ $(-4.21\times 10^5)$ GeV$^2$, $A_{\kappa_{1,2,3}} = 0$ $(-1389.2)$ GeV, $A_{\lambda_{1,2}} = 0$ $(-52.9)$ GeV, $m_{D_{1,2,3}}^2 = 2.5\times 10^7$ $(4.81\times 10^6)$ GeV$^2$, $m_{\overline{D}_{1,2,3}}^2 = 2.5\times 10^7$ $(4.90\times 10^6)$ GeV$^2$, $m_{H^d_{1,2}}^2 = 2.5\times 10^7$ $(4.46\times 10^6)$ GeV$^2$, $m_{H^u_{1,2}}^2 = 2.5\times 10^7$ $(4.81\times 10^6)$ GeV$^2$, $m_{S_{1,2}}^2 = 2.5\times 10^7$ $(5.28\times 10^6)$ GeV$^2$, $m_{H'}^2 = 2.5\times 10^7$ $(4.94\times 10^6)$ GeV$^2$ and $m_{\overline{H'}}^2 = 2.5\times 10^7$ $(4.87\times 10^6)$ GeV$^2$.
-}
+\caption{Parameters for the MSSM and E$_6$SSM benchmark points.  In the
+E$_6$SSM we define $\mu_{\mathrm{eff}} \equiv \lambda s/\sqrt{2}$ and
+$B_{\mathrm{eff}} = A_\lambda$.  The soft masses $m_{H_d}^2$, $m_{H_u}^2$
+and $m_S^2$ are those that satisfy the EWSB conditions including 1-loop
+Coleman-Weinberg corrections involving the top and stops.  For E$_6$SSM BM1
+(BM2) we also set $\mu^\prime = 5000.0$ $(897.9)$ GeV, $B\mu^\prime = 5000.0$
+$(-4.21\times 10^5)$ GeV$^2$, $A_{\kappa_{1,2,3}} = 0$ $(-1389.2)$ GeV,
+$A_{\lambda_{1,2}} = 0$ $(-52.9)$ GeV, $m_{D_{1,2,3}}^2 = 2.5\times 10^7$
+$(4.81\times 10^6)$ GeV$^2$, $m_{\overline{D}_{1,2,3}}^2 = 2.5\times 10^7$
+$(4.90\times 10^6)$ GeV$^2$, $m_{H^d_{1,2}}^2 = 2.5\times 10^7$
+$(4.46\times 10^6)$ GeV$^2$, $m_{H^u_{1,2}}^2 = 2.5\times 10^7$
+$(4.81\times 10^6)$ GeV$^2$, $m_{S_{1,2}}^2 = 2.5\times 10^7$
+$(5.28\times 10^6)$ GeV$^2$, $m_{H'}^2 = 2.5\times 10^7$ $(4.94\times 10^6)$
+GeV$^2$ and $m_{\overline{H'}}^2 = 2.5\times 10^7$ $(4.87\times 10^6)$ GeV$^2$.}
 \label{tab:benchmarks}
@@
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_mssm_cutoff_scan_4_benchmark_points_tuning_vs_cutoff_bw_var.png} } \\
+\includegraphics{e6ssm_mssm_benchmark_points_tuning_vs_cutoff_bw_var.png} } \\
 \resizebox{!}{5.5cm}{%
-\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_BM1_all_tuning_data_bw_var.png}} 
+\includegraphics{mssm_BM1_all_tuning_data_bw_var.png}}
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_BM1_all_tuning_data_bw_var.png}} \\
+\includegraphics{e6ssm_light_zprime_BM1_all_tuning_data_bw_var.png}} \\
 \resizebox{!}{5.5cm}{%
-\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_BM2_all_tuning_data_bw_var.png}} 
+\includegraphics{mssm_BM2_all_tuning_data_bw_var.png}}
 \resizebox{!}{5.5cm}{%
-\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_BM2_all_tuning_data_bw_var.png}}%%
-\caption{\textit{Top panel:} Scatter plot of the fine tuning as a function of the cutoff scale $M_X$ for the four benchmark points given in Table \ref{tab:benchmarks}.
-\textit{Middle left panel:}  Individual sensitivities for MSSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the dotted line in the top panel.
-\textit{Middle right panel:} Individual sensitivities for E$_6$SSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the solid line in the top panel.
-\textit{Bottom left panel:} Individual sensitivities for MSSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the dash-dotted line in the top panel.
-\textit{Bottom right panel:} Individual sensitivities for E$_6$SSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the dashed line in the top panel.
-}
+\includegraphics{e6ssm_light_zprime_BM2_all_tuning_data_bw_var.png}}%%
+\caption{\textit{Top panel:} Scatter plot of the fine tuning as a function
+of the cutoff scale $M_X$ for the four benchmark points given in
+Table \ref{tab:benchmarks}.  \textit{Middle left panel:}  Individual
+sensitivities for MSSM BM1 plotted against the high scale $M_X$ which give
+the overall tuning shown by the dotted line in the top panel.
+\textit{Middle right panel:} Individual sensitivities for E$_6$SSM BM1 plotted
+against the high scale $M_X$ which give the overall tuning shown by the solid
+line in the top panel.  \textit{Bottom left panel:} Individual sensitivities
+for MSSM BM2 plotted against the high scale $M_X$ which give the overall
+tuning shown by the dash-dotted line in the top panel.
+\textit{Bottom right panel:} Individual sensitivities for E$_6$SSM BM2 plotted
+against the high scale $M_X$ which give the overall tuning shown by the dashed
+line in the top panel.}
 \label{Fig:BMs-varyMX}
@@
 also cause other sensitivities to grow, in particular $\Delta_{M_3}$.
-The fine tuning rises with $M_X$ once $M_X \gtrsim 10^5-10^6$ GeV, but
+The fine tuning rises with $M_X$ once $M_X \gtrsim 10^5 - 10^6$ GeV, but
 remains lower than that of the other points, until $M_X \approx 10^8$
@@
 RGE running is a result of the exotic matter introduced to keep the
-   extra $U(1)$ anomaly free. }. This is why this E$_6$SSM BM1 has a
+extra $U(1)$ anomaly free.}.  This is why this E$_6$SSM BM1 has a
 larger tuning at larger values of $M_X$, coming from
@@
 By contrast the tuning for E$_6$SSM BM2 is very different, as is shown
-by the dashed line in the top panel, with the individual sensitivities given in the
-bottom right panel. This point was chosen as it had a much lighter
+by the dashed line in the top panel, with the individual sensitivities given
+in the bottom right panel.  This point was chosen as it had a much lighter
 gluino mass that is just above the experimental limit of $1.4$ TeV
@@
 $\Delta_{M_3}$ is substantially lower and only becomes the dominant
-tuning at a much larger scale of $M_X\gtrsim 10^{12}-10^{13}$ GeV,
+tuning at a much larger scale of $M_X \gtrsim 10^{12} - 10^{13}$ GeV,
 giving a tuning at $10^{16}$ GeV of $\approx 546$, which is far below
@@
 
-In addition to this, the soft parameters in E$_6$SSM BM2 follow a pattern similar to that found in the constrained
-model. With the exception of the parameters $m_{Q_3}^2$, 
-$m_{u_3}^2$, $m_{H_d}^2$, $m_{H_u}^2$, and $M_3$, the values of which are given in Table \ref{tab:benchmarks}, 
-the soft masses at the SUSY scale correspond to the values that result in the cE$_6$SSM with $m_0=2.2$ TeV, 
-$M_{1/2}=1003$ GeV, $A_0=500$ GeV, $\kappa_{1,2,3}(M_X)=0.1923$, $\lambda(M_X)=0.2646$ and
-$\lambda_{1,2}(M_X)=0.1$.
-This leads to a significant reduction in the contributions to the RG running of $m_{H_u}^2$ and $m_{Q_3}^2$ coming from terms of the form $g_1^2\Sigma_1$ and, to a lesser extent, $g_1'^2\Sigma_1'$.
-Here we define for the E$_6$SSM (see also Eqs.~(\ref{eq:USSMGaugeSigmaTerm1}-\ref{eq:USSMGaugeSigmaTerm1Pr}) for general $U(1)$ inspired models)
+In addition to this, the soft parameters in E$_6$SSM BM2 follow a pattern
+similar to that found in the constrained model.  With the exception of the
+parameters $m_{Q_3}^2$, $m_{u_3}^2$, $m_{H_d}^2$, $m_{H_u}^2$, and $M_3$,
+the values of which are given in Table \ref{tab:benchmarks}, the soft masses
+at the SUSY scale correspond to the values that result in the cE$_6$SSM with
+$m_0 = 2.2$ TeV, $M_{1/2} = 1003$ GeV, $A_0 = 500$ GeV,
+$\kappa_{1,2,3}(M_X) = 0.1923$, $\lambda(M_X) = 0.2646$ and
+$\lambda_{1,2}(M_X) = 0.1$.  This leads to a significant reduction in the
+contributions to the RG running of $m_{H_u}^2$ and $m_{Q_3}^2$ coming from
+terms of the form $g_1^2\Sigma_1$ and, to a lesser extent, $g_1'^2\Sigma_1'$.
+Here we define for the E$_6$SSM (see also
+Eqs.~(\ref{eq:USSMGaugeSigmaTerm1}-\ref{eq:USSMGaugeSigmaTerm1Pr}) for
+general $U(1)$ inspired models)
 \begin{align*}
-\Sigma_1&=\sum_{i=1}^3\left ( m_{Q_i}^2-2m_{u_i}^2+m_{d_i}^2+m_{e_i}^2-m_{L_i}^2+m_{H_i^u}^2-m_{H_i^d}^2+m_{\overline{D}_i}^2-m_{D_i}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\\
-\Sigma_1'&=\sum_{i=1}^3\left ( 6m_{Q_i}^2+3m_{u_i}^2+6m_{d_i}^2+m_{e_i}^2+4m_{L_i}^2-4m_{H_i^u}^2-6m_{H_i^d}^2+5m_{Si}^2-9m_{\overline{D}_i}^2-6m_{D_i}^2\right )\\
-&\quad{}+4m_{H'}^2-4m_{\overline{H'}}^2.
+\Sigma_1 &= \sum_{i=1}^3 \left ( m_{Q_i}^2 - 2 m_{u_i}^2 + m_{d_i}^2 +
+m_{e_i}^2 - m_{L_i}^2 + m_{H_i^u}^2 - m_{H_i^d}^2 + m_{\overline{D}_i}^2
+- m_{D_i}^2 \right ) -m_{H'}^2 + m_{\overline{H'}}^2 , \\
+\Sigma_1' &= \sum_{i=1}^3 \left ( 6 m_{Q_i}^2 + 3 m_{u_i}^2 + 6 m_{d_i}^2
++ m_{e_i}^2 + 4 m_{L_i}^2 - 4 m_{H_i^u}^2 - 6 m_{H_i^d}^2 + 5 m_{S_i}^2
+- 9 m_{\overline{D}_i}^2 - 6 m_{D_i}^2 \right ) \\
+& \quad {} + 4 m_{H'}^2 - 4 m_{\overline{H'}}^2 .
 \end{align*}
-In the unconstrained case, this contribution acts to drive up the values of $m_{Q_3}^2$ and $m_{H_u}^2$, and thus the associated tuning sensitivities, at the cutoff scale $M_X$.
-In the case of E$_6$SSM BM2, on the other hand, the reduced splitting between the soft masses leads to a much smaller contribution from these terms.
-Together with the reduction in $M_3$ described above, this allows to maintain the observed low fine tuning at very large values of $M_X$.
-
-MSSM benchmark BM2 (dash-dotted in top panel, individual sensitivities in bottom left panel) is designed to be similar to E$_6$SSM BM2, for a reasonable comparison.
-However from the individual sensitivities one can see that the behaviour is quite similar to MSSM BM1, though in this case the $\Delta_{m_{H_u}^2}$ becomes the largest tuning at a higher $M_X$ and does not reach such large values, since more of the tuning is from the mixing in this case.
+In the unconstrained case, this contribution acts to drive up the values of
+$m_{Q_3}^2$ and $m_{H_u}^2$, and thus the associated tuning sensitivities,
+at the cutoff scale $M_X$.  In the case of E$_6$SSM BM2, on the other hand,
+the reduced splitting between the soft masses leads to a much smaller
+contribution from these terms.  Together with the reduction in $M_3$ described
+above, this allows to maintain the observed low fine tuning at very large
+values of $M_X$.
+
+MSSM benchmark BM2 (dash-dotted in top panel, individual sensitivities in
+bottom left panel) is designed to be similar to E$_6$SSM BM2, for a reasonable
+comparison.  However from the individual sensitivities one can see that the
+behaviour is quite similar to MSSM BM1, though in this case the
+$\Delta_{m_{H_u}^2}$ becomes the largest tuning at a higher $M_X$ and does not
+reach such large values, since more of the tuning is from the mixing in this
+case.
 
@@
 gravity interactions with the hidden sector.  Through the use of
-renormalisation group running one can then see that at the EW scale
+renormalization group running one can then see that at the EW scale
 the stops enter the EWSB condition for $M_Z$, therefore it was
@@
 on the Higgs mass, requiring it to be above 114.4 GeV
-\cite{Barate:2003sz,Schael:2006cr}, which already introduced
+\cite{Barate:2003sz, Schael:2006cr}, which already introduced
 significant tuning for constrained models, since heavy stops are
@@
 We also looked at the tuning in different $U(1)$ extensions for fixed
-$\tan \beta = 10$.  We found that in every case except for the
+$\tan\beta = 10$.  We found that in every case except for the
 $U(1)_I$ the fine tuning was much worse for the larger $Z^\prime$
@@
 
-\acknowledgements We would like to thank R.~Nevzorov for many useful
+\begin{acknowledgments}
+We would like to thank R.~Nevzorov for many useful
 discussions and comments and F.~Staub for very helpful responses
@@
 also like to thank A.~Ismail and T.~Rizzo for their helpful comments
-regarding fine tuning in the MSSM. 
-PA would like to thank J.H.~Park, A.~Voigt and D.~Stockinger for 
-useful discussion regarding the use of FlexibleSUSY in this project. 
-This work was supported by the University of Adelaide and by the ARC 
-Centre of Excellence for Particle Physics at the Terascale.
+regarding fine tuning in the MSSM.  PA would like to thank J.H.~Park,
+A.~Voigt and D.~St\"{o}ckinger for useful discussion regarding the use of
+FlexibleSUSY in this project.  This work was supported by the University
+of Adelaide and by the ARC Centre of Excellence for Particle Physics at
+the Terascale.
+\end{acknowledgments}
 
 \appendix
-\section{\label{app:masterformula}Fine Tuning Master Formula}
-% Tree level master formula for the E6SSM
-To write down the tree level master formula, it is convenient to define the quantities
+
+\section{\label{app:masterformula}Fine Tuning Master
+Formula}
+
+To write down the tree level master formula, it is convenient to define the
+quantities
 \begin{equation}
-z_i =\epsilon_{ijk} \frac{\partial f_j}{\partial s}\frac{\partial f_k}{\partial \tan\beta}
+z_i =\epsilon_{ijk} \frac{\partial f_j}{\partial s}
+\frac{\partial f_k}{\partial \tan\beta}
 \label{eq:masterformulacoefficients}
 \end{equation}
-with $f_1,f_2,f_3$ as given in Eq.~(\ref{eq:E6EWSBConditions}). The relevant partial derivatives are
+with $f_1 , f_2 , f_3$ as given in Eq.~(\ref{eq:E6EWSBConditions}). The
+relevant partial derivatives are
 \ba
-\frac{\partial f_1}{\partial \tan\beta}&=&-\frac{2M_Z}{\bar{g}}\,\cos^2\beta\left \{ \frac{\lambda A_\lambda s}{\sqrt{2}}\,\cos\beta+\sin\beta \left [ m_{H_d}^2+\frac{s^2}{2}\left ( \lambda^2+g_1'^2Q_1Q_S \right )\right.\right.\nonumber\\
-&&\left.\left.+M_Z^2\left ( \frac{5}{2}-\frac{4\lambda^2}{\bar{g}^2}-\frac{4g_1'^2}{\bar{g}^2}Q_1Q_2+\frac{6g_1'^2}{\bar{g}^2}Q_1^2\right )\right ]+3M_Z^2\,\sin^3\beta\left [ \frac{2\lambda^2}{\bar{g}^2}-1\right.\right.\nonumber\\
-&&\left.\left.+\frac{2g_1'^2}{\bar{g}^2}\left ( Q_1Q_2-Q_1^2\right )\right ]\right \},\nonumber\\
-\frac{\partial f_1}{\partial s}&=&\frac{2M_Z}{\bar{g}}\left [ s\left ( \lambda^2+g_1'^2Q_1Q_S\right )\,\cos\beta-\frac{\lambda A_\lambda}{\sqrt{2}}\,\sin\beta \right ],\nonumber\\
-\frac{\partial f_2}{\partial \tan\beta}&=&\frac{2M_Z}{\bar{g}}\,\cos^2\beta\left \{ \frac{\lambda A_\lambda s}{\sqrt{2}}\,\sin\beta+\cos\beta\left [ m_{H_u}^2+\frac{s^2}{2}\left ( \lambda^2+g_1'^2Q_2Q_S \right )\right.\right.\nonumber\\
-&&\left.+M_Z^2\left ( \frac{5}{2}-\frac{4\lambda^2}{\bar{g}^2}-\frac{4g_1'^2}{\bar{g}^2}Q_1Q_2+\frac{6g_1'^2}{\bar{g}^2}Q_2^2\right )\right ]+3M_Z^2\,\cos^3\beta \left [ \frac{2\lambda^2}{\bar{g}^2}-1\right.\nonumber\\
-&&\left.\left.+\frac{2g_1'^2}{\bar{g}^2}\left ( Q_1Q_2-Q_2^2\right )\right ]\right \},\nonumber\\
-\frac{\partial f_2}{\partial s}&=&\frac{2M_Z}{\bar{g}}\left [ s\left ( \lambda^2+g_1'^2Q_2Q_S\right )\,\sin\beta-\frac{\lambda A_\lambda}{\sqrt{2}}\,\cos\beta\right ],\nonumber\\
-\frac{\partial f_3}{\partial \tan\beta}&=&\frac{2M_Z^2}{\bar{g}^2}\,\cos^2\beta\left [ g_1'^2Q_Ss\left ( Q_2-Q_1\right )\,\sin 2\beta-\sqrt{2}\lambda A_\lambda\,\cos 2\beta\right ],\nonumber\\
-\frac{\partial f_3}{\partial s}&=&m_S^2+\frac{2\lambda^2M_Z^2}{\bar{g}^2}+\frac{g_1'^2}{2}Q_S\left [\frac{4M_Z^2}{\bar{g}^2}\left ( Q_1\,\cos^2\beta+Q_2\,\sin^2\beta\right ) +3Q_S s^2\right ].\nonumber
+\frac{\partial f_1}{\partial \tan\beta} &=& -\frac{2 M_Z}{\bar{g}}
+\, \cos^2\beta \left \{ \frac{\lambda A_\lambda s}{\sqrt{2}} \, \cos\beta
++ \sin\beta \left [ m_{H_d}^2 + \frac{s^2}{2} \left ( \lambda^2 +
+g_1'^2 Q_1 Q_S \right ) \right . \right . \nonumber \\
+& & \left . \left . + M_Z^2 \left ( \frac{5}{2}-\frac{4 \lambda^2}{\bar{g}^2}
+- \frac{4 g_1'^2}{\bar{g}^2} Q_1 Q_2 + \frac{6 g_1'^2}{\bar{g}^2} Q_1^2
+\right ) \right ] + 3 M_Z^2 \, \sin^3\beta \left [
+\frac{2 \lambda^2}{\bar{g}^2} - 1 \right . \right . \nonumber \\
+& & \left . \left . + \frac{2 g_1'^2}{\bar{g}^2} \left ( Q_1 Q_2
+- Q_1^2 \right ) \right ] \right \} , \nonumber \\
+\frac{\partial f_1}{\partial s} &=& \frac{2 M_Z}{\bar{g}} \left [ s \left (
+\lambda^2 + g_1'^2 Q_1 Q_S \right ) \, \cos\beta -
+\frac{\lambda A_\lambda}{\sqrt{2}} \, \sin\beta \right ] , \nonumber \\
+\frac{\partial f_2}{\partial \tan\beta} &=& \frac{2 M_Z}{\bar{g}} \,
+\cos^2\beta \left \{ \frac{\lambda A_\lambda s}{\sqrt{2}} \, \sin\beta
++ \cos\beta \left [ m_{H_u}^2 + \frac{s^2}{2} \left ( \lambda^2 +
+g_1'^2 Q_2 Q_S \right ) \right . \right . \nonumber \\
+& & \left . + M_Z^2 \left ( \frac{5}{2}-\frac{4 \lambda^2}{\bar{g}^2}
+- \frac{4 g_1'^2}{\bar{g}^2} Q_1 Q_2 + \frac{6 g_1'^2}{\bar{g}^2} Q_2^2
+\right ) \right ] + 3 M_Z^2 \, \cos^3\beta \left [
+\frac{2 \lambda^2}{\bar{g}^2} - 1 \right . \nonumber \\
+& & \left . \left . + \frac{2 g_1'^2}{\bar{g}^2} \left ( Q_1 Q_2 - Q_2^2
+\right ) \right ] \right \} , \nonumber \\
+\frac{\partial f_2}{\partial s} &=& \frac{2 M_Z}{\bar{g}} \left [
+s \left ( \lambda^2 + g_1'^2 Q_2 Q_S \right ) \, \sin\beta -
+\frac{\lambda A_\lambda}{\sqrt{2}} \, \cos\beta \right ] , \nonumber \\
+\frac{\partial f_3}{\partial \tan\beta} &=& \frac{2 M_Z^2}{\bar{g}^2} \,
+\cos^2\beta \left [ g_1'^2 Q_S s \left ( Q_2 - Q_1 \right ) \, \sin 2\beta
+- \sqrt{2} \lambda A_\lambda \, \cos 2\beta \right ] , \nonumber \\
+\frac{\partial f_3}{\partial s} &=& m_S^2 +
+\frac{2 \lambda^2 M_Z^2}{\bar{g}^2} + \frac{g_1'^2}{2} Q_S \left [
+\frac{4 M_Z^2}{\bar{g}^2} \left ( Q_1 \, \cos^2\beta + Q_2 \, \sin^2\beta
+\right ) + 3 Q_S s^2 \right ] . \nonumber
 \ea
-For a running parameter $q$ appearing in the tree level EWSB conditions, the corresponding contribution to the individual sensitivity can then be written 
+For a running parameter $q$ appearing in the tree level EWSB conditions, the
+corresponding contribution to the individual sensitivity can then be written
 \be
-\tilde{\Delta}_q=z_1\frac{\partial f_1}{\partial q}+z_2\frac{\partial f_2}{\partial q}+z_3\frac{\partial f_3}{\partial q}.
+\tilde{\Delta}_q = z_1 \frac{\partial f_1}{\partial q} +
+z_2 \frac{\partial f_2}{\partial q} + z_3 \frac{\partial f_3}{\partial q} .
 \label{eq:tuningContribution}
 \ee
-It is straightforward to compute the appropriate derivatives directly from the EWSB conditions, Eq.~(\ref{eq:E6EWSBConditions}).
-Similarly, the quantity $C$ appearing in Eq.~(\ref{eq:E6masterformula}) is given by
+It is straightforward to compute the appropriate derivatives directly from the
+EWSB conditions, Eq.~(\ref{eq:E6EWSBConditions}).  Similarly, the quantity
+$C$ appearing in Eq.~(\ref{eq:E6masterformula}) is given by
 \be
-C=\frac{1}{2}\left ( z_1\frac{\partial f_1}{\partial M_Z}+z_2\frac{\partial f_2}{\partial M_Z}+z_3\frac{\partial f_3}{\partial M_Z}\right ),
+C = \frac{1}{2} \left ( z_1 \frac{\partial f_1}{\partial M_Z} +
+z_2 \frac{\partial f_2}{\partial M_Z} + z_3 \frac{\partial f_3}{\partial M_Z}
+\right ) ,
 \label{eq:tuningDenominator}
@@
 \ba
-\frac{\partial f_1}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\cos\beta\left ( m_{H_d}^2+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}Q_1Q_Ss^2+\frac{6g_1'^2}{\bar{g}^2}Q_1^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\sin\beta\nonumber \\
-&&+\frac{3M_Z^2}{\bar{g}}\,\cos\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\sin\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left(Q_1Q_2-Q_1^2\right )\right ],\nonumber\\
-\frac{\partial f_2}{\partial M_Z}&=&\frac{2}{\bar{g}}\,\sin\beta\left ( m_{H_u}^2+\frac{\lambda^2s^2}{2}+\frac{g_1'^2}{2}Q_2Q_Ss^2+\frac{6g_1'^2}{\bar{g}^2}Q_2^2M_Z^2\right )-\sqrt{2}\frac{\lambda A_\lambda s}{\bar{g}}\,\cos\beta \nonumber\\
-&&-\frac{3M_Z^2}{\bar{g}}\,\sin\beta\,\cos 2\beta+\frac{6}{\bar{g}^3}M_Z^2\,\cos\beta\,\sin 2\beta\left [ \lambda^2+g_1'^2\left ( Q_1Q_2-\tilde{Q_2}^2\right )\right ],\nonumber \\
-\frac{\partial f_3}{\partial M_Z}&=&\frac{4M_Z}{\bar{g}^2}\left [ \lambda^2s-\frac{\lambda A_\lambda}{\sqrt{2}}\,\sin 2\beta+g_1'^2Q_Ss\left ( Q_1\,\cos^2\beta+Q_2\,\sin^2\beta \right )\right ].\nonumber
+\frac{\partial f_1}{\partial M_Z} &=& \frac{2}{\bar{g}} \, \cos\beta
+\left ( m_{H_d}^2 + \frac{\lambda^2 s^2}{2} + \frac{g_1'^2}{2} Q_1 Q_S s^2
++ \frac{6 g_1'^2}{\bar{g}^2} Q_1^2 M_Z^2 \right ) - \sqrt{2}
+\frac{\lambda A_\lambda s}{\bar{g}} \, \sin\beta \nonumber \\
+& & + \frac{3 M_Z^2}{\bar{g}} \, \cos\beta \, \cos 2\beta +
+\frac{6}{\bar{g}^3} M_Z^2 \, \sin\beta \, \sin 2\beta \left [ \lambda^2 +
+g_1'^2 \left ( Q_1 Q_2 - Q_1^2 \right ) \right ] , \nonumber \\
+\frac{\partial f_2}{\partial M_Z} &=& \frac{2}{\bar{g}} \, \sin\beta
+\left ( m_{H_u}^2 + \frac{\lambda^2 s^2}{2} + \frac{g_1'^2}{2} Q_2 Q_S s^2
++ \frac{6 g_1'^2}{\bar{g}^2} Q_2^2 M_Z^2 \right ) - \sqrt{2}
+\frac{\lambda A_\lambda s}{\bar{g}} \, \cos\beta \nonumber \\
+& & - \frac{3 M_Z^2}{\bar{g}} \, \sin\beta \, \cos 2\beta +
+\frac{6}{\bar{g}^3} M_Z^2 \, \cos\beta \, \sin 2\beta \left [ \lambda^2 +
+g_1'^2 \left ( Q_1 Q_2 - \tilde{Q_2}^2 \right ) \right ] , \nonumber \\
+\frac{\partial f_3}{\partial M_Z} &=& \frac{4 M_Z}{\bar{g}^2}\left [
+\lambda^2 s - \frac{\lambda A_\lambda}{\sqrt{2}} \, \sin 2\beta + g_1'^2 Q_S s
+\left ( Q_1 \, \cos^2\beta + Q_2 \, \sin^2\beta \right ) \right ] . \nonumber
 \ea
+
 \section{\label{app:rges}RGE Contributions}
@@
 \begin{equation*}
-q(Q)=q(M_X)+\frac{t}{16\pi^2}\left ( \beta_q^{(1)}+\frac{\beta_q^{(2)}}{16\pi^2}\right )+\frac{t^2}{(16\pi^2)^2}b_q^{(2)}(M_X),
+q(Q) = q(M_X) + \frac{t}{16\pi^2} \left ( \beta_q^{(1)} +
+\frac{\beta_q^{(2)}}{16\pi^2} \right ) + \frac{t^2}{(16\pi^2)^2}
+b_q^{(2)}(M_X) ,
 \end{equation*}
@@
 \begin{equation*}
-b_q^{(2)}(M_X)=\frac{1}{2!}\left . \sum_{q_k}\beta_{q_k}^{(1)}\frac{\partial \beta_q}{\partial q_k}\right |_{M_X}.
+b_q^{(2)}(M_X) = \frac{1}{2!} \left . \sum_{q_k} \beta_{q_k}^{(1)}
+\frac{\partial \beta_q}{\partial q_k} \right |_{M_X} .
 \end{equation*}
@@
 likewise omitted.  Additionally, all soft mass matrices are assumed
-diagonal, and the gaugino masses are taken to be real.\\
-In the
-MSSM, the relevant parameters for the fine tuning calculation are
+diagonal, and the gaugino masses are taken to be real.
+
+In the MSSM, the relevant parameters for the fine tuning calculation are
 $\mu$, $B$, $m_{H_u}^2$, $m_{H_d}^2$ at tree level.  For the
-renormalisation group running of the relevant parameters
+renormalization group running of the relevant parameters
 SOFTSUSY uses the one- and two-loop RGEs from
-\cite{Barger:1993gh,Martin:1993zk}. The corresponding $O(t^2)$
+\cite{Barger:1993gh, Martin:1993zk}. The corresponding $O(t^2)$
 contributions are
-\begin{subequations}\label{eq:MSSMTreeLevelCoeffs}
+\begin{subequations} \label{eq:MSSMTreeLevelCoeffs}
 \begin{align}
-b_\mu^{(2)}&=\frac{\mu}{2}\Bigg [ 45y_t^4+45y_b^4+9y_\tau^4+30y_t^2y_b^2+6y_t^2y_\tau^2+18y_b^2y_\tau^2-32g_3^2(y_t^2+y_b^2)\nonumber\\
-&\quad{}-12g_2^2(3y_t^2+3y_b^2+y_\tau^2)-\frac{4}{5}g_1^2(11y_t^2+8y_b^2+6y_\tau^2)+3g_2^4-\frac{189}{25}g_1^4+\frac{18}{5}g_1^2g_2^2\Bigg ],\label{eq:MSSMmub2}\\
-b_B^{(2)}&=72y_t^4A_t+72y_b^4A_b+16y_\tau^4A_\tau+12y_t^2y_b^2(A_t+A_b)+12y_\tau^2y_b^2(A_b+A_\tau)\nonumber\\
-&\quad{}-32g_3^2y_t^2(A_t-M_3)-32g_3^2y_b^2(A_b-M_3)\nonumber\\
-&\quad{}-18g_2^2y_t^2(A_t-M_2)-18g_2^2y_b^2(A_b-M_2)-6g_2^2y_\tau^2(A_\tau-M_2)\nonumber\\
-&\quad{}-\frac{26}{5}g_1^2y_t^2(A_t-M_1)-\frac{14}{5}g_1^2y_b^2(A_b-M_1)-\frac{18}{5}g_1^2y_\tau^2(A_\tau-M_1)\nonumber\\
-&\quad{}+12g_2^4M_2+\frac{396}{25}g_1^4M_1,\label{eq:MSSMBb2}\\
-b_{m_{H_d}^2}^{(2)}&=72y_b^4\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2A_b^2\right )\nonumber\\
-&\quad{}+6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2+(A_t+A_b)^2\right )\nonumber\\
-&\quad{}+12y_\tau^2y_b^2\left ( 2m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+m_{L_3}^2+m_{e_3}^2+(A_\tau+A_b)^2\right )\nonumber\\
-&\quad{}+16y_\tau^4\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+2A_\tau^2\right )\nonumber\\
-&\quad{}-32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+A_b^2-2M_3A_b+2M_3^2\right )\nonumber\\
-&\quad{}-18g_2^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+A_b^2-2M_2A_b+2M_2^2\right )\nonumber\\
-&\quad{}-6g_2^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+A_\tau^2-2M_2A_\tau+2M_2^2\right )\nonumber\\
-&\quad{}-\frac{14}{5}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+A_b^2-2M_1A_b+2M_1^2\right )\nonumber\\
-&\quad{}-\frac{18}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+A_\tau^2-2M_1A_\tau+2M_1^2\right )\nonumber\\
-&\quad{}-18g_2^4M_2^2-\frac{198}{25}g_1^4\left ( \mathcal{S}+3M_1^2\right ),\label{eq:MSSMmHd2b2}\\
-b_{m_{H_u}^2}^{(2)}&=72y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2A_t^2\right )\nonumber\\
-&\quad{}+6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2+(A_t+A_b)^2\right )\nonumber\\
-&\quad{}-32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2A_tM_3+2M_3^2\right )\nonumber\\
-&\quad{}-18g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2A_tM_2+2M_2^2\right )\nonumber\\
-&\quad{}-\frac{26}{5}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2A_tM_1+2M_1^2\right )\nonumber\\
-&\quad{}+\frac{198}{25}g_1^4\left ( \mathcal{S}-3M_1^2\right )-18g_2^4M_2^2.\label{eq:MSSMmHu2b2}
+b_\mu^{(2)} &= \frac{\mu}{2} \Bigg [ 45 y_t^4 + 45 y_b^4 + 9 y_\tau^4
++ 30 y_t^2 y_b^2 + 6 y_t^2 y_\tau^2 + 18 y_b^2 y_\tau^2 - 32 g_3^2 ( y_t^2
++ y_b^2 ) \nonumber \\
+& \quad {} - 12 g_2^2 ( 3 y_t^2 + 3 y_b^2 + y_\tau^2 ) - \frac{4}{5} g_1^2
+( 11 y_t^2 + 8 y_b^2 + 6 y_\tau^2 ) + 3 g_2^4 - \frac{189}{25} g_1^4 +
+\frac{18}{5} g_1^2 g_2^2 \Bigg ] , \label{eq:MSSMmub2} \\
+b_B^{(2)} &= 72 y_t^4 A_t + 72 y_b^4 A_b + 16 y_\tau^4 A_\tau + 12 y_t^2 y_b^2
+( A_t + A_b ) + 12 y_\tau^2 y_b^2 ( A_b + A_\tau ) \nonumber \\
+& \quad {} - 32 g_3^2 y_t^2 ( A_t - M_3 ) - 32 g_3^2 y_b^2 ( A_b - M_3 )
+\nonumber \\
+& \quad {} - 18 g_2^2 y_t^2 ( A_t - M_2 ) - 18 g_2^2 y_b^2 ( A_b - M_2 )
+- 6 g_2^2 y_\tau^2 ( A_\tau - M_2 ) \nonumber \\
+& \quad {} - \frac{26}{5} g_1^2 y_t^2 ( A_t - M_1 ) - \frac{14}{5} g_1^2 y_b^2
+( A_b - M_1 ) - \frac{18}{5} g_1^2 y_\tau^2 ( A_\tau - M_1 ) \nonumber \\
+& \quad {} + 12 g_2^4 M_2 + \frac{396}{25} g_1^4 M_1 , \label{eq:MSSMBb2} \\
+b_{m_{H_d}^2}^{(2)} &= 72 y_b^4 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 +
+2 A_b^2 \right ) \nonumber \\
+& \quad {} + 6 y_t^2 y_b^2 \left ( m_{H_u}^2 + m_{H_d}^2 + 2 m_{Q_3}^2 +
+m_{u_3}^2 + m_{d_3}^2 + ( A_t + A_b )^2 \right ) \nonumber \\
+& \quad {} + 12 y_\tau^2 y_b^2 \left ( 2 m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 +
+m_{L_3}^2 + m_{e_3}^2 + ( A_\tau + A_b )^2 \right ) \nonumber \\
+& \quad {} + 16 y_\tau^4 \left ( m_{H_d}^2 + m_{L_3}^2 + m_{e_3}^2 +
+2 A_\tau^2 \right ) \nonumber \\
+& \quad {} - 32 g_3^2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 + A_b^2
+- 2 M_3 A_b + 2 M_3^2 \right ) \nonumber \\
+& \quad {} - 18 g_2^2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 + A_b^2
+- 2 M_2 A_b + 2 M_2^2 \right ) \nonumber \\
+& \quad {} - 6 g_2^2 y_\tau^2 \left ( m_{H_d}^2 + m_{L_3}^2 + m_{e_3}^2 +
+A_\tau^2 - 2 M_2 A_\tau + 2 M_2^2 \right ) \nonumber \\
+& \quad {} - \frac{14}{5} g_1^2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 +
+m_{d_3}^2 + A_b^2 - 2 M_1 A_b + 2 M_1^2 \right ) \nonumber \\
+& \quad {} - \frac{18}{5} g_1^2 y_\tau^2 \left ( m_{H_d}^2 + m_{L_3}^2 +
+m_{e_3}^2 + A_\tau^2 - 2 M_1 A_\tau + 2 M_1^2 \right ) \nonumber \\
+& \quad {} - 18 g_2^4 M_2^2 - \frac{198}{25} g_1^4 \left ( \mathcal{S} +
+3 M_1^2 \right ) , \label{eq:MSSMmHd2b2} \\
+b_{m_{H_u}^2}^{(2)} &= 72 y_t^4 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 +
+2 A_t^2 \right ) \nonumber \\
+& \quad {} + 6 y_t^2 y_b^2 \left ( m_{H_u}^2 + m_{H_d}^2 + 2 m_{Q_3}^2 +
+m_{u_3}^2 + m_{d_3}^2 + ( A_t + A_b )^2 \right ) \nonumber \\
+& \quad {} - 32 g_3^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 + A_t^2
+- 2 A_t M_3 + 2 M_3^2 \right ) \nonumber \\
+& \quad{} - 18 g_2^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 + A_t^2
+- 2 A_t M_2 + 2 M_2^2 \right ) \nonumber \\
+& \quad {} - \frac{26}{5} g_1^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 +
+m_{u_3}^2 + A_t^2 - 2 A_t M_1 + 2 M_1^2 \right ) \nonumber \\
+& \quad {} + \frac{198}{25} g_1^4 \left ( \mathcal{S} - 3 M_1^2 \right )
+- 18 g_2^4 M_2^2 . \label{eq:MSSMmHu2b2}
 \end{align}
@@
 In these expressions the quantity $\mathcal{S}$ is defined by
-\begin{equation}\label{eq:MSSMgaugeBetaContribution}
-\mathcal{S}=m_{H_u}^2-m_{H_d}^2+\sum_{i=1}^3\left ( m_{Q_i}^2-m_{L_i}^2-2m_{u_i}^2+m_{d_i}^2+m_{e_i}^2\right ).
+\begin{equation} \label{eq:MSSMgaugeBetaContribution}
+\mathcal{S} = m_{H_u}^2 - m_{H_d}^2 + \sum_{i=1}^3 \left ( m_{Q_i}^2 -
+m_{L_i}^2 - 2 m_{u_i}^2 + m_{d_i}^2 + m_{e_i}^2 \right ) .
 \end{equation}
@@
 coefficients read
-\begin{subequations}\label{eq:MSSMsEffPotCoeffs}
+\begin{subequations} \label{eq:MSSMsEffPotCoeffs}
 \begin{align}
-b_{m_{Q_3}^2}^{(2)}&=24y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2A_t^2\right )+24y_b^4\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2A_b^2\right )\nonumber\\
-&\quad{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2+(A_t+A_b)^2\right )\nonumber\\
-&\quad{}+2y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q_3}^2+m_{L_3}^2+m_{d_3}^2+m_{e_3}^2+(A_b+A_\tau)^2\right )\nonumber\\
-&\quad{}-\frac{32}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2M_3A_t+2M_3^2\right )\nonumber\\
-&\quad{}-\frac{32}{3}g_3^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+A_b^2-2M_3A_b+2M_3^2\right )\nonumber\\
-&\quad{}-6g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2M_2A_t+2M_2^2\right )\nonumber\\
-&\quad{}-6g_2^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+A_b^2-2M_2A_b+2M_2^2\right )\nonumber\\
-&\quad{}-\frac{26}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
-&\quad{}-\frac{14}{15}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+A_b^2-2M_1A_b+2M_1^2\right )\nonumber\\
-&\quad{}+96g_3^4M_3^2-18g_2^4M_2^2+\frac{66}{25}g_1^4(\mathcal{S}-M_1^2),\label{eq:MSSMmQ32b2}\\
-b_{m_{u_3}^2}^{(2)}&=48y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2A_t^2\right )\nonumber\\
-&\quad{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2+(A_t+A_b)^2\right )\nonumber\\
-&\quad{}-\frac{64}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2M_3A_t+2M_3^2\right )\nonumber\\
-&\quad{}-12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2M_2A_t+2M_2^2\right )\nonumber\\
-&\quad{}-\frac{52}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+A_t^2-2M_1A_t+2M_1^2\right )\nonumber\\
-&\quad{}+96g_3^4M_3^2-\frac{264}{25}g_1^4\left ( \mathcal{S}+4M_1^2\right ),\label{eq:MSSMmu32b2}\\
-b_{A_t}^{(2)}&=144y_t^4A_t+24y_b^4A_b+14y_t^2y_b^2(A_t+A_b)+2y_b^2y_\tau^2(A_b+A_\tau)\nonumber\\
-&\quad{}-64g_3^2y_t^2(A_t-M_3)-36g_2^2y_t^2(A_t-M_2)-\frac{52}{5}g_1^2y_t^2(A_t-M_1)\nonumber\\
-&\quad{}-\frac{32}{3}g_3^2y_b^2(A_b-M_3)-6g_2^2y_b^2(A_b-M_2)-\frac{14}{15}g_1^2y_b^2(A_b-M_1)\nonumber\\
-&\quad{}-64g_3^4M_3+12g_2^4M_2+\frac{572}{25}g_1^4M_1.\label{eq:MSSMAtb2}
+b_{m_{Q_3}^2}^{(2)} &= 24 y_t^4 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 +
+2 A_t^2 \right ) + 24 y_b^4 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 +
+2 A_b^2 \right ) \nonumber \\
+& \quad {} + 4 y_t^2 y_b^2 \left ( m_{H_u}^2 + m_{H_d}^2 + 2 m_{Q_3}^2 +
+m_{u_3}^2 + m_{d_3}^2 + ( A_t + A_b )^2 \right ) \nonumber \\
+& \quad {} + 2 y_b^2 y_\tau^2 \left ( 2 m_{H_d}^2 + m_{Q_3}^2 + m_{L_3}^2 +
+m_{d_3}^2 + m_{e_3}^2 + ( A_b + A_\tau )^2 \right ) \nonumber \\
+& \quad {} - \frac{32}{3} g_3^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 +
+m_{u_3}^2 + A_t^2 - 2 M_3 A_t + 2 M_3^2 \right ) \nonumber \\
+& \quad {} - \frac{32}{3} g_3^2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 +
+m_{d_3}^2 + A_b^2 - 2 M_3 A_b + 2 M_3^2 \right ) \nonumber \\
+& \quad {} - 6 g_2^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 + A_t^2
+- 2 M_2 A_t + 2 M_2^2 \right ) \nonumber \\
+& \quad {} - 6 g_2^2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 + A_b^2
+- 2 M_2 A_b + 2 M_2^2 \right ) \nonumber \\
+& \quad {} - \frac{26}{15} g_1^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 +
+m_{u_3}^2 + A_t^2 - 2 M_1 A_t + 2 M_1^2 \right ) \nonumber \\
+& \quad {} - \frac{14}{15} g_1^2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 +
+m_{d_3}^2 + A_b^2 - 2 M_1 A_b + 2 M_1^2 \right ) \nonumber \\
+& \quad {} + 96 g_3^4 M_3^2 - 18 g_2^4 M_2^2 + \frac{66}{25} g_1^4
+( \mathcal{S} - M_1^2 ) , \label{eq:MSSMmQ32b2} \\
+b_{m_{u_3}^2}^{(2)} &= 48 y_t^4 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 +
+2 A_t^2 \right ) \nonumber \\
+& \quad {} + 4 y_t^2 y_b^2 \left ( m_{H_u}^2 + m_{H_d}^2 + 2 m_{Q_3}^2 +
+m_{u_3}^2 + m_{d_3}^2 + ( A_t + A_b )^2 \right ) \nonumber \\
+& \quad {} - \frac{64}{3} g_3^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 +
+m_{u_3}^2 + A_t^2 - 2 M_3 A_t + 2 M_3^2 \right ) \nonumber \\
+& \quad {} - 12 g_2^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 +
+A_t^2 - 2 M_2 A_t + 2 M_2^2 \right ) \nonumber \\
+& \quad {} - \frac{52}{15} g_1^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 +
+m_{u_3}^2 + A_t^2 - 2 M_1 A_t + 2 M_1^2 \right ) \nonumber \\
+& \quad {} + 96 g_3^4 M_3^2 - \frac{264}{25} g_1^4 \left ( \mathcal{S} +
+4 M_1^2 \right ) , \label{eq:MSSMmu32b2} \\
+b_{A_t}^{(2)} &= 144 y_t^4 A_t + 24 y_b^4 A_b + 14 y_t^2 y_b^2 ( A_t + A_b )
++ 2 y_b^2 y_\tau^2 ( A_b + A_\tau ) \nonumber \\
+& \quad {} - 64 g_3^2 y_t^2 ( A_t - M_3 ) - 36 g_2^2 y_t^2 ( A_t - M_2) -
+\frac{52}{5} g_1^2 y_t^2 ( A_t - M_1 ) \nonumber \\
+& \quad {} - \frac{32}{3} g_3^2 y_b^2 ( A_b - M_3 ) - 6 g_2^2 y_b^2
+( A_b - M_2 ) - \frac{14}{15} g_1^2 y_b^2 ( A_b - M_1 ) \nonumber \\
+& \quad {} - 64 g_3^4 M_3 + 12 g_2^4 M_2 + \frac{572}{25} g_1^4 M_1
+\label{eq:MSSMAtb2}
 \end{align}
@@
 
-At tree level in the EWSB conditions the parameters that must be considered are $\lambda$,
-$A_\lambda$, $m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and
-$g_1'$. Neglecting kinetic mixing, the two-loop $\beta$ functions for
+At tree level in the EWSB conditions the parameters that must be considered
+are $\lambda$, $A_\lambda$, $m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$
+and $g_1'$.  Neglecting kinetic mixing, the two-loop $\beta$ functions for
 the relevant gauge couplings read
-\begin{subequations}\label{eq:USSMGaugeBetas}
+\begin{subequations} \label{eq:USSMGaugeBetas}
 \begin{align}
-\beta_{g_1}^{(1)}&=\frac{48}{5}g_1^3,\label{eq:USSMg1BetaOneLoop}\\
-\beta_{g_1}^{(2)}&=\frac{2}{25} g_1^3 \left(30 g_1'^2 \Pi_{Q}^Y+117 g_1^2+135 g_2^2+300 g_3^2-10 \Sigma _{\kappa }-15
-   \Sigma _{\lambda }-65 y_t^2-35 y_b^2-45 y_{\tau }^2\right),\label{eq:USSMg1BetaTwoLoop}\\
-\beta_{g_2}^{(1)}&=4g_2^3,\label{eq:USSMg2BetaOneLoop}\\
-\beta_{g_2}^{(2)}&=\frac{2}{5} g_2^3 \left(5 g_1'^2 \Pi _{Q}^L+9 g_1^2+115 g_2^2+60 g_3^2-5 \Sigma _{\lambda }-15 y_t^2-15 y_b^2-5 y_{\tau }^2\right),\label{eq:USSMg2BetaTwoLoop}\\
-\beta_{g_1'}^{(1)}&=g_1'^3\Sigma_{Q},\label{eq:USSMg1pBetaOneLoop}\\
-\beta_{g_1'}^{(2)}&=\frac{2}{5} g_1'^3 \left(-15 \Sigma _{\kappa } \left(Q_{\bar{D}}^2+Q_D^2+Q_S^2\right)-30
-   y_b^2 \left(Q_d^2+Q_1^2+Q_Q^2\right)+120 g_3^2 \Pi _{Q}^C\right.\nonumber \\
-&\quad{}-10 y_{\tau }^2
-   \left(Q_e^2+Q_L^2+Q_1^2\right)+15 g_2^2 \Pi _{Q}^L+10 g_1'^2 \Pi _{Q}+6
-   g_1^2 \Pi _{Q}^Y\nonumber\\
-&\quad\left.{}-10 \Sigma _{\lambda } \left(Q_S^2+Q_1^2+Q_2^2\right)-30 y_t^2
-   \left(Q_u^2+Q_2^2+Q_Q^2\right)\right).\label{eq:USSMg1pBetaTwoLoop}
+\beta_{g_1}^{(1)} &= \frac{48}{5} g_1^3 , \label{eq:USSMg1BetaOneLoop} \\
+\beta_{g_1}^{(2)} &= \frac{2}{25} g_1^3 \left ( 30 g_1'^2 \Pi_{Q}^Y +
+117 g_1^2 + 135 g_2^2 + 300 g_3^2 - 10 \Sigma_{\kappa } - 15 \Sigma_{\lambda }
+- 65 y_t^2 - 35 y_b^2 - 45 y_{\tau }^2 \right ) , \label{eq:USSMg1BetaTwoLoop}\\
+\beta_{g_2}^{(1)} &= 4 g_2^3 , \label{eq:USSMg2BetaOneLoop} \\
+\beta_{g_2}^{(2)} &= \frac{2}{5} g_2^3 \left ( 5 g_1'^2 \Pi _{Q}^L + 9 g_1^2
++ 115 g_2^2 + 60 g_3^2 - 5 \Sigma_{\lambda } - 15 y_t^2 - 15 y_b^2 -
+5 y_{\tau }^2 \right) , \label{eq:USSMg2BetaTwoLoop} \\
+\beta_{g_1'}^{(1)} &= g_1'^3 \Sigma_{Q} , \label{eq:USSMg1pBetaOneLoop} \\
+\beta_{g_1'}^{(2)} &= \frac{2}{5} g_1'^3 \left ( -15 \Sigma_{\kappa } \left (
+Q_{\bar{D}}^2 + Q_D^2 + Q_S^2 \right ) - 30 y_b^2 \left ( Q_d^2 + Q_1^2 +
+Q_Q^2 \right ) + 120 g_3^2 \Pi_{Q}^C \right . \nonumber \\
+& \quad {} - 10 y_{\tau }^2 \left ( Q_e^2 + Q_L^2 + Q_1^2 \right ) +
+15 g_2^2 \Pi_{Q}^L + 10 g_1'^2 \Pi_{Q} + 6 g_1^2 \Pi_{Q}^Y \nonumber \\
+& \quad \left . {} - 10 \Sigma_{\lambda } \left ( Q_S^2 + Q_1^2 + Q_2^2
+\right ) - 30 y_t^2 \left ( Q_u^2 + Q_2^2 + Q_Q^2 \right ) \right ) .
+\label{eq:USSMg1pBetaTwoLoop}
 \end{align}
@@
 \begin{align*}
-\Sigma_{Q}=\sum_i Q_i^2=\frac{321}{40}\cos^2\theta+\frac{217}{24}\sin^2\theta+\frac{27}{8\sqrt{15}}\sin 2\theta
+\Sigma_{Q} = \sum_i Q_i^2 = \frac{321}{40} \cos^2\theta +
+\frac{217}{24} \sin^2\theta + \frac{27}{8 \sqrt{15}} \sin 2\theta
 \end{align*}
@@
 do not reduce to those which one would obtain from
-  \cite{Martin:1993zk} or \cite{Athron:2009bs} unless $\Sigma_{Q}^Y =
-  0$.  Note however these contributions do not appear in the
-  corresponding trilinears due to the version of SARAH used. }
+\cite{Martin:1993zk} or \cite{Athron:2009bs} unless $\Sigma_{Q}^Y = 0$.
+Note however these contributions do not appear in the
+corresponding trilinears due to the version of SARAH used.}
 \begin{align*}
-\Sigma_{Q}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^YQ_i=-\frac{3}{\sqrt{10}}\cos\theta-\frac{1}{\sqrt{6}}\sin\theta,\\
-\Pi_{Q}&=\sum_i Q_i^4\\
-&=\frac{2049}{1600}\cos^4\theta+\frac{483}{80\sqrt{15}}\cos^3\theta\sin\theta+\frac{681}{160}\cos^2\theta\sin^2\theta+\frac{9}{16\sqrt{15}}\cos\theta\sin^3\theta+\frac{1297}{576}\sin^4\theta,\\
-\Pi_{Q}^Y&=\sum_i \left ( \sqrt{\frac{5}{3}}Q_i^Y\right )^2Q_i^2=\frac{59}{40}\cos^2\theta+\frac{31}{24}\sin^2\theta+\frac{3}{8\sqrt{15}}\sin 2\theta,\\
-\Pi_{Q}^L&=3Q_1^2+3Q_2^2+Q_{H'}^2+Q_{\overline{H'}}^2+3Q_L^2+9Q_Q^2=\frac{39}{20}\cos^2\theta+\frac{19}{12}\sin^2\theta+\frac{3}{4\sqrt{15}}\sin 2\theta,\\
-\Pi_{Q}^C&=Q_d^2+Q_D^2+Q_{\overline{D}}^2+2Q_Q^2+Q_u^2=\frac{1}{2}.
+\Sigma_{Q}^Y &= \sum_i \sqrt{\frac{5}{3}} Q_i^Y Q_i =
+-\frac{3}{\sqrt{10}} \cos\theta - \frac{1}{\sqrt{6}} \sin\theta , \\
+\Pi_{Q} &= \sum_i Q_i^4 \\
+&= \frac{2049}{1600} \cos^4\theta +
+\frac{483}{80\sqrt{15}} \cos^3\theta \sin\theta +
+\frac{681}{160} \cos^2\theta \sin^2\theta +
+\frac{9}{16\sqrt{15}} \cos\theta \sin^3\theta +
+\frac{1297}{576}\sin^4\theta , \\
+\Pi_{Q}^Y &= \sum_i \left ( \sqrt{\frac{5}{3}} Q_i^Y \right )^2 Q_i^2 =
+\frac{59}{40} \cos^2\theta + \frac{31}{24} \sin^2\theta +
+\frac{3}{8\sqrt{15}} \sin 2\theta , \\
+\Pi_{Q}^L &= 3 Q_1^2 + 3Q_2^2 + Q_{H'}^2 + Q_{\overline{H'}}^2 + 3 Q_L^2 +
+9 Q_Q^2 = \frac{39}{20} \cos^2\theta + \frac{19}{12} \sin^2\theta +
+\frac{3}{4\sqrt{15}} \sin 2\theta , \\
+\Pi_{Q}^C &= Q_d^2 + Q_D^2 + Q_{\overline{D}}^2 + 2 Q_Q^2 + Q_u^2 =
+\frac{1}{2} .
 \end{align*}
-Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised.
-The expressions in terms of the $E_6$ mixing angle $\theta$ follow from the charge assignments given in Table \ref{tab:E6charges} and hold provided that $U(1)$ mixing is neglected.
-Similarly we write
+Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to
+be GUT-normalised.  The expressions in terms of the $E_6$ mixing angle
+$\theta$ follow from the charge assignments given in Table \ref{tab:E6charges}
+and hold provided that $U(1)$ mixing is neglected.  Similarly we write
 \begin{align*}
-&\Sigma_\lambda=\lambda_1^2+\lambda_2^2+\lambda_3^2, \qquad \Sigma_\kappa=\kappa_1^2+\kappa_2^2+\kappa_3^2,\\
-&\Pi_\lambda=\lambda_1^4+\lambda_2^4+\lambda_3^4,\qquad \Pi_\kappa=\kappa_1^4+\kappa_2^4+\kappa_3^4.
+&\Sigma_\lambda = \lambda_1^2 + \lambda_2^2 + \lambda_3^2 ,
+\qquad \Sigma_\kappa = \kappa_1^2 + \kappa_2^2 + \kappa_3^2 , \\
+&\Pi_\lambda = \lambda_1^4 + \lambda_2^4 + \lambda_3^4 ,
+\qquad \Pi_\kappa = \kappa_1^4 + \kappa_2^4 + \kappa_3^4 .
 \end{align*}
 The corresponding $O(t^2)$ coefficients for the gauge couplings are simply
-\begin{subequations}\label{eq:USSMGaugeOt2Coeffs}
+\begin{subequations} \label{eq:USSMGaugeOt2Coeffs}
 \begin{align}
-b_{g_1}^{(2)}&=\frac{3456}{25}g_1^5,\label{eq:USSMg1Ot2Coeff}\\
-b_{g_2}^{(2)}&=24g_2^5,\label{eq:USSMg2Ot2Coeff}\\
-b_{g_1'}^{(2)}&=\frac{3}{2}g_1'^5\Sigma_{Q}^2.\label{eq:USSMg1pOt2Coeff}
+b_{g_1}^{(2)} &= \frac{3456}{25} g_1^5 , \label{eq:USSMg1Ot2Coeff} \\
+b_{g_2}^{(2)} &= 24 g_2^5 , \label{eq:USSMg2Ot2Coeff} \\
+b_{g_1'}^{(2)} &= \frac{3}{2} g_1'^5 \Sigma_{Q}^2 . \label{eq:USSMg1pOt2Coeff}
 \end{align}
@@
 and the $O(t^2)$ coefficient in the series expansion are
-\begin{subequations}\label{eq:USSMLambdaBetas}
+\begin{subequations} \label{eq:USSMLambdaBetas}
 \begin{align}
-\beta_\lambda^{(1)}&=\lambda  \left[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2-\frac{3}{5} g_1^2 -2 \left ( Q_1^2 + Q_2^2 + Q_S^2\right )g_1'^2 \right],\label{eq:USSMLambdaBetaOneLoop}\\
-\beta_\lambda^{(2)}&=\lambda \bigg \{ -2\lambda^2\left ( \lambda^2+2\Sigma_\lambda+3\Sigma_\kappa\right )-4\Pi_\lambda-6\Pi_\kappa-3\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right ) \nonumber\\
-&{} -3\left ( 3y_t^4+3y_b^4+2y_t^2y_b^2+y_\tau^2 \right )+6g_2^2\Sigma_\lambda+\frac{2}{5}g_1^2\left ( 2y_t^2-y_b^2+3y_\tau^2+2\Sigma_\kappa +3\Sigma_\lambda\right )\nonumber\\
-&{}\left.+g_1'^2\left [ 4Q_S^2\lambda^2 -6\left ( Q_2^2-Q_Q^2-Q_u^2\right )y_t^2-6\left ( Q_1^2-Q_Q^2-Q_d^2\right )y_b^2 \right.\right.\nonumber\\
-&{}\left.-2\left ( Q_1^2-Q_L^2-Q_e^2\right )y_\tau^2-6\left ( Q_S^2-Q_D^2-Q_{\overline{D}}^2 \right )\Sigma_\kappa-4\left ( Q_S^2-Q_1^2-Q_2^2\right )\Sigma_\lambda\right ]\nonumber\\
-&{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2Q_1^4+2Q_2^4+2Q_S^4+\left ( Q_1^2+Q_2^2+Q_S^2\right )\Sigma_{Q}\right ]\nonumber\\
-&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [Q_1^2+Q_2^2+\left ( Q_2 - Q_1 \right )\Sigma_Q^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\
-b_\lambda^{(2)}&=\lambda \bigg \{ 2\lambda^2\left ( 3\lambda^2 +4\Sigma_\lambda +6\Sigma_\kappa \right )+4\Pi_\lambda + 6\Pi_\kappa +6\left ( \Sigma_\lambda+\frac{3}{2}\Sigma_\kappa\right )^2+7\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\nonumber\\
-&{}+\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\left (2\Sigma_\lambda+3\Sigma_\kappa\right ) +3\left ( \frac{15}{2}y_t^4+\frac{15}{2}y_b^4+\frac{3}{2}y_\tau^4 +5y_b^2y_t^2 +3y_b^2y_\tau^2 +y_t^2y_\tau^2\right )\nonumber\\
-&{}-\frac{1}{5}g_1^2\left ( 12\lambda^2+16y_b^2+22y_t^2+12y_\tau^2+12\Sigma_\lambda +13\Sigma_\kappa \right )\nonumber\\
-&{}-3g_2^2\left ( 4\lambda^2+6y_t^2+6y_b^2+2y_\tau^2+4\Sigma_\lambda+3\Sigma_\kappa\right )-16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa \right )\nonumber\\
-&{}-2g_1'^2\left [ 4\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( \lambda^2 +\Sigma_\lambda \right )+3\Sigma_\kappa\left ( Q_1^2+Q_2^2+Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\right .\nonumber\\
-&{}+3y_b^2\left ( 2Q_1^2+Q_2^2+Q_d^2+Q_Q^2+Q_S^2 \right )+3y_t^2\left ( Q_1^2+2Q_2^2+Q_Q^2+Q_S^2+Q_u^2\right )\nonumber\\
-&{}\left.+y_\tau^2\left ( 2Q_1^2+Q_2^2+Q_e^2+Q_L^2+Q_S^2\right )\right ]-\frac{15}{2}g_2^4-\frac{279}{50}g_1^4\nonumber\\
-&{}+2g_1'^4\left ( Q_1^2+Q_2^2+Q_S^2 \right )\left (Q_1^2+Q_2^2+Q_S^2-\Sigma_{Q}\right )+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\nonumber\\
-&{}+\frac{6}{5}g_1^2g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2 \right ) \bigg \}.\label{eq:USSMLambdaOt2Coeff}
+\beta_\lambda^{(1)} &= \lambda \left [ 2 \lambda^2 + 2 \Sigma_\lambda +
+3 \Sigma_\kappa + 3 y_t^2 + 3 y_b^2 + y_{\tau }^2 - 3 g_2^2 - \frac{3}{5}
+g_1^2 - 2 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) g_1'^2 \right ] ,
+\label{eq:USSMLambdaBetaOneLoop} \\
+\beta_\lambda^{(2)} &= \lambda \bigg \{ -2 \lambda^2 \left ( \lambda^2 +
+2 \Sigma_\lambda + 3 \Sigma_\kappa \right ) - 4 \Pi_\lambda - 6 \Pi_\kappa
+- 3 \lambda^2 \left ( 3 y_t^2 + 3 y_b^2 + y_\tau^2 \right ) \nonumber \\
+& {} - 3 \left ( 3 y_t^4 + 3 y_b^4 + 2 y_t^2 y_b^2 + y_\tau^2 \right ) +
+6 g_2^2 \Sigma_\lambda + \frac{2}{5} g_1^2 \left ( 2 y_t^2 - y_b^2 +
+3 y_\tau^2 + 2 \Sigma_\kappa + 3 \Sigma_\lambda \right ) \nonumber \\
+& {} \left . + g_1'^2 \left [ 4 Q_S^2 \lambda^2 - 6 \left ( Q_2^2 - Q_Q^2
+- Q_u^2 \right ) y_t^2 - 6 \left ( Q_1^2 - Q_Q^2 - Q_d^2 \right ) y_b^2
+\right . \right . \nonumber \\
+& {} \left . - 2 \left ( Q_1^2 - Q_L^2 - Q_e^2 \right ) y_\tau^2 -
+6 \left ( Q_S^2 - Q_D^2 - Q_{\overline{D}}^2 \right ) \Sigma_\kappa -
+4 \left ( Q_S^2 - Q_1^2 - Q_2^2 \right ) \Sigma_\lambda \right ] \nonumber \\
+& {} + 16 g_3^2 \left ( y_t^2 + y_b^2 + \Sigma_\kappa \right ) +
+\frac{33}{2} g_2^4 + \frac{297}{50} g_1^4 + 2 g_1'^4 \left [ 2 Q_1^4 +
+2 Q_2^4 + 2 Q_S^4 + \left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) \Sigma_{Q}
+\right ] \nonumber \\
+& {} + \frac{9}{5} g_1^2 g_2^2 + 6 g_1'^2 g_2^2 \left ( Q_1^2 + Q_2^2 \right )
++ \frac{6}{5} g_1^2 g_1'^2 \left [ Q_1^2 + Q_2^2 + \left ( Q_2 - Q_1 \right )
+\Sigma_Q^Y \right ] \bigg \} , \label{eq:USSMLambdaBetaTwoLoop} \\
+b_\lambda^{(2)} &= \lambda \bigg \{ 2 \lambda^2 \left ( 3 \lambda^2 +
+4 \Sigma_\lambda + 6 \Sigma_\kappa \right ) + 4 \Pi_\lambda + 6\Pi_\kappa +
+6 \left ( \Sigma_\lambda + \frac{3}{2} \Sigma_\kappa \right )^2 +
+7 \lambda^2 \left ( 3 y_t^2 + 3 y_b^2 + y_\tau^2 \right ) \nonumber \\
+& {} + \left ( 3 y_t^2 + 3 y_b^2 + y_\tau^2 \right ) \left ( 2 \Sigma_\lambda
++ 3 \Sigma_\kappa \right ) + 3 \left ( \frac{15}{2} y_t^4 + \frac{15}{2} y_b^4
++ \frac{3}{2} y_\tau^4 + 5 y_b^2 y_t^2 + 3 y_b^2 y_\tau^2 + y_t^2 y_\tau^2
+\right ) \nonumber \\
+& {} - \frac{1}{5} g_1^2 \left ( 12 \lambda^2 + 16 y_b^2 + 22 y_t^2 +
+12 y_\tau^2 + 12 \Sigma_\lambda + 13 \Sigma_\kappa \right ) \nonumber \\
+& {} - 3 g_2^2 \left ( 4 \lambda^2 + 6 y_t^2 + 6 y_b^2 + 2 y_\tau^2 +
+4 \Sigma_\lambda + 3 \Sigma_\kappa \right ) - 16 g_3^2 \left ( y_t^2 + y_b^2
++ \Sigma_\kappa \right ) \nonumber \\
+& {} - 2 g_1'^2 \left [ 4 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right )
+\left ( \lambda^2 + \Sigma_\lambda \right ) + 3 \Sigma_\kappa
+\left ( Q_1^2 + Q_2^2 + Q_S^2 + Q_D^2 + Q_{\overline{D}}^2 \right )
+\right . \nonumber \\
+& {} + 3y_b^2 \left ( 2 Q_1^2 + Q_2^2 + Q_d^2 + Q_Q^2 + Q_S^2 \right ) +
+3 y_t^2 \left ( Q_1^2 + 2 Q_2^2 + Q_Q^2 + Q_S^2 + Q_u^2 \right ) \nonumber \\
+& {} \left . + y_\tau^2 \left ( 2 Q_1^2 + Q_2^2 + Q_e^2 + Q_L^2 + Q_S^2
+\right ) \right ] - \frac{15}{2} g_2^4 - \frac{279}{50} g_1^4 \nonumber \\
+& {} + 2 g_1'^4 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right )
+\left ( Q_1^2 + Q_2^2 + Q_S^2 - \Sigma_{Q} \right ) + \frac{9}{5} g_1^2 g_2^2
++ 6 g_1'^2 g_2^2 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) \nonumber \\
+& {} + \frac{6}{5} g_1^2 g_1'^2 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right )
+\bigg \} . \label{eq:USSMLambdaOt2Coeff}
 \end{align}
 \end{subequations}
-It is sufficient for our purposes to consider the trilinear coupling $a_\lambda\equiv \lambda A_\lambda$, rather than $A_\lambda$, for which the relevant expressions read
+It is sufficient for our purposes to consider the trilinear coupling
+$a_\lambda \equiv \lambda A_\lambda$, rather than $A_\lambda$, for which the
+relevant expressions read
 \begin{subequations}
 \begin{align}
-\beta_{a_\lambda}^{(1)}&=a_\lambda \left[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2-\frac{3}{5} g_1^2 -2 \left ( Q_1^2 + Q_2^2 + Q_S^2\right )g_1'^2 \right]\nonumber\\
-&{}+\lambda \bigg [ 4\lambda a_\lambda +4\Sigma_{a_\lambda}+6\Sigma_{a_\kappa}+6y_ta_t+6y_ba_b+2y_\tau a_\tau +6g_2^2M_2+\frac{6}{5}g_1^2M_1\nonumber\\
-&{}+4g_1'^2M_1'\left ( Q_1^2+Q_2^2+Q_S^2 \right )\bigg ],\label{eq:USSMTLambdaBetaOneLoop}\\
-\beta_{a_\lambda}^{(2)}&=a_\lambda \bigg \{ -2\lambda^2\left ( \lambda^2+2\Sigma_\lambda+3\Sigma_\kappa\right )-4\Pi_\lambda-6\Pi_\kappa-3\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right ) \nonumber\\
-&{} -3\left ( 3y_t^4+3y_b^4+2y_t^2y_b^2+y_\tau^2 \right )+6g_2^2\Sigma_\lambda+\frac{2}{5}g_1^2\left ( 2y_t^2-y_b^2+3y_\tau^2+2\Sigma_\kappa +3\Sigma_\lambda\right )\nonumber\\
-&{}\left.+g_1'^2\left [ 4Q_S^2\lambda^2 -6\left ( Q_2^2-Q_Q^2-Q_u^2\right )y_t^2-6\left ( Q_1^2-Q_Q^2-Q_d^2\right )y_b^2 \right.\right.\nonumber\\
-&{}\left.-2\left ( Q_1^2-Q_L^2-Q_e^2\right )y_\tau^2-6\left ( Q_S^2-Q_D^2-Q_{\overline{D}}^2 \right )\Sigma_\kappa-4\left ( Q_S^2-Q_1^2-Q_2^2\right )\Sigma_\lambda\right ]\nonumber\\
-&{}+16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa\right ) +\frac{33}{2}g_2^4+\frac{297}{50}g_1^4+2g_1'^4\left [ 2Q_1^4+2Q_2^4+2Q_S^4+\left ( Q_1^2+Q_2^2+Q_S^2\right )\Sigma_{Q}\right ]\nonumber\\
-&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left (Q_1^2+Q_2^2\right )\bigg \}+\lambda \bigg \{ -4\lambda a_\lambda \left ( \lambda^2+2\Sigma_\lambda+3\Sigma_\kappa\right )\nonumber\\
-&{}-4\lambda^2\left ( \lambda a_\lambda+2\Sigma_{a_\lambda}+3\Sigma_{a_\kappa}\right )-16\Pi_{a_\lambda}-24\Pi_{a_\kappa}-6\lambda a_\lambda\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\nonumber\\
-&{}-6\lambda^2\left ( 3y_ta_t+3y_ba_b+y_\tau a_\tau\right )-12\left [ 3y_t^3a_t+3y_b^3a_b+y_ty_b\left ( y_ta_b+y_ba_t\right )+y_\tau^3 a_\tau\right ]\nonumber\\
-&{}+32g_3^2\left [ y_ta_t+y_ba_b+\Sigma_{a_\kappa}-\left ( y_t^2+y_b^2+\Sigma_\kappa\right )M_3\right ]+12g_2^2\left ( \Sigma_{a_\lambda}-\Sigma_\lambda M_2\right )\nonumber\\
-&{}+\frac{2}{5}g_1^2\left [ 4y_ta_t-2y_ba_b+6y_\tau a_\tau+4\Sigma_{a_\kappa}+6\Sigma_{a_\lambda}-2\left ( 2y_t^2-y_b^2+3y_\tau^2+2\Sigma_\kappa+3\Sigma_\lambda\right )M_1\right ]\nonumber\\
-&{}+4g_1'^2\big [ 3y_t\left ( Q_Q^2-Q_2^2+Q_u^2\right )\left ( a_t-y_t M_1'\right )+3y_b\left ( Q_Q^2-Q_1^2+Q_d^2\right )\left ( a_b-y_bM_1'\right )\nonumber\\
-&{}+y_\tau\left ( Q_L^2-Q_1^2+Q_e^2\right )\left ( a_\tau-y_\tau M_1'\right )+2Q_S^2\lambda\left ( a_\lambda-\lambda M_1'\right )\nonumber\\
-&{}+2\left ( Q_1^2+Q_2^2-Q_S^2\right )\left ( \Sigma_{a_\lambda}-\Sigma_\lambda M_1'\right )+3\left ( Q_D^2+Q_{\overline{D}}^2-Q_S^2\right )\left ( \Sigma_{a_\kappa}-\Sigma_\kappa M_1'\right ) \big ]\nonumber\\
-&{}-66g_2^4M_2-\frac{594}{25}g_1^4M_1-8g_1'^4M_1'\left [ 2\left ( Q_1^4+Q_2^4+Q_S^4\right )+\left ( Q_1^2+Q_2^2+Q_S^2\right )\Sigma_Q\right ]\nonumber\\
-&{}-\frac{18}{5}g_2^2g_1^2\left ( M_2+M_1\right )-12g_2^2g_1'^2\left ( Q_1^2+Q_2^2\right )\left ( M_2+M_1'\right )\nonumber\\
-&{}-\frac{12}{5}g_1^2g_1'^2\left ( Q_1^2+Q_2^2\right )\left ( M_1+M_1'\right )\bigg \},\label{eq:USSMTLambdaBetaTwoLoop}\\
-b_{a_\lambda}^{(2)}&=\lambda \bigg [ 4\lambda a_\lambda +4\Sigma_{a_\lambda}+6\Sigma_{a_\kappa}+6y_ta_t+6y_ba_b+2y_\tau a_\tau +6g_2^2M_2+\frac{6}{5}g_1^2M_1\nonumber\\
-&{}+4g_1'^2M_1'\left ( Q_1^2+Q_2^2+Q_S^2 \right )\bigg ]\times\bigg[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2\nonumber\\
-&{}-\frac{3}{5} g_1^2 -2 \left ( Q_1^2 + Q_2^2 + Q_S^2\right )g_1'^2 \bigg]+a_\lambda\bigg \{ 2\lambda^2\left ( 3\lambda^2 +4\Sigma_\lambda +6\Sigma_\kappa \right )+4\Pi_\lambda + 6\Pi_\kappa \nonumber\\
-&{}+6\left ( \Sigma_\lambda+\frac{3}{2}\Sigma_\kappa\right )^2+7\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right )+\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\left (2\Sigma_\lambda+3\Sigma_\kappa\right ) \nonumber\\
-&{}+3\left ( \frac{15}{2}y_t^4+\frac{15}{2}y_b^4+\frac{3}{2}y_\tau^4 +5y_b^2y_t^2 +3y_b^2y_\tau^2 +y_t^2y_\tau^2\right )\nonumber\\
-&{}-\frac{1}{5}g_1^2\left ( 12\lambda^2+16y_b^2+22y_t^2+12y_\tau^2+12\Sigma_\lambda +13\Sigma_\kappa \right )\nonumber\\
-&{}-3g_2^2\left ( 4\lambda^2+6y_t^2+6y_b^2+2y_\tau^2+4\Sigma_\lambda+3\Sigma_\kappa\right )-16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa \right )\nonumber\\
-&{}-2g_1'^2\left [ 4\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( \lambda^2 +\Sigma_\lambda \right )+3\Sigma_\kappa\left ( Q_1^2+Q_2^2+Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\right .\nonumber\\
-&{}+3y_b^2\left ( 2Q_1^2+Q_2^2+Q_d^2+Q_Q^2+Q_S^2 \right )+3y_t^2\left ( Q_1^2+2Q_2^2+Q_Q^2+Q_S^2+Q_u^2\right )\nonumber\\
-&{}\left.+y_\tau^2\left ( 2Q_1^2+Q_2^2+Q_e^2+Q_L^2+Q_S^2\right )\right ]-\frac{15}{2}g_2^4-\frac{279}{50}g_1^4\nonumber\\
-&{}+2g_1'^4\left ( Q_1^2+Q_2^2+Q_S^2 \right )\left (Q_1^2+Q_2^2+Q_S^2-\Sigma_{Q}\right )+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\nonumber\\
-&{}+\frac{6}{5}g_1^2g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2 \right ) \bigg \}+\lambda \bigg [16\lambda^3a_{\lambda}+16\Pi_{a_\lambda}+24\Pi_{a_\kappa}+8\lambda\sum_{i=1}^3\lambda_i\left ( \lambda_i a_{\lambda}+a_{\lambda_i}\lambda\right )\nonumber\\
-&{}+12\lambda\sum_{i=1}^3\kappa_i\left ( \kappa_i a_\lambda + a_{\kappa_i} \lambda\right )+8\sum_{i=1}^3\sum_{j=1}^3\lambda_i\lambda_j\left ( a_{\lambda_i}\lambda_j+\lambda_ia_{\lambda_j}\right )\nonumber\\
-&{}+18\sum_{i=1}^3\sum_{j=1}^3\kappa_i\kappa_j\left ( \kappa_i a_{\kappa_j}+a_{\kappa_i}\kappa_j\right )+24\sum_{i=1}^3\sum_{j=1}^3\lambda_i\kappa_j\left ( \lambda_i a_{\kappa_j}+a_{\lambda_i}\kappa_j\right )+72y_t^3a_t+72y_b^3a_b\nonumber\\
-&{}+16y_\tau^3a_\tau+12y_ty_b\left ( a_ty_b+y_ta_b\right )+12y_by_\tau\left ( a_by_\tau+y_ba_\tau\right )+30\lambda y_t\left ( a_{\lambda}y_t+\lambda a_t\right )\nonumber\\
-&{}+30\lambda y_b\left ( a_{\lambda}y_b+\lambda a_b\right )+10\lambda y_\tau\left ( a_{\lambda}y_\tau+\lambda a_{\tau}\right )-32g_3^2y_t\left ( a_t-y_tM_3\right )-32g_3^2y_b\left ( a_b-y_bM_3\right )\nonumber\\
-&{}-32g_3^2\left ( \Sigma_{a_\kappa}-M_3\Sigma_\kappa\right )-12g_2^2\lambda\left ( a_\lambda-\lambda M_2\right )-18g_2^2y_t\left ( a_t-y_tM_2\right )-18g_2^2y_b\left ( a_b-y_bM_2\right )\nonumber\\
-&{}-6g_2^2y_\tau\left ( a_\tau-y_\tau M_2\right )-12g_2^2\left ( \Sigma_{a_\lambda}-M_2\Sigma_\lambda \right )-\frac{12}{5}g_1^2\lambda\left ( a_{\lambda}-\lambda M_1\right )-\frac{26}{5}g_1^2y_t\left ( a_t-y_tM_1\right )\nonumber\\
-&{}-\frac{14}{5}g_1^2y_b\left ( a_b-y_bM_1\right )-\frac{18}{5}g_1^2y_\tau\left ( a_\tau-y_\tau M_1\right )-\frac{12}{5}g_1^2\left ( \Sigma_{a_\lambda}-M_1\Sigma_\lambda\right )-\frac{8}{5}g_1^2\left ( \Sigma_{a_\kappa}-M_1\Sigma_\kappa\right )\nonumber\\
-&{}-8g_1'^2\lambda\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( a_\lambda-\lambda M_1'\right )-12g_1'^2y_t\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( a_t-y_tM_1'\right )\nonumber\\
-&{}-12g_1'^2y_b\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( a_b-y_bM_1'\right )-4g_1'^2y_\tau\left ( Q_1^2+Q_L^2+Q_e^2\right )\left ( a_\tau-y_\tau M_1'\right )\nonumber\\
-&{}-8g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( \Sigma_{a_\lambda}-M_1'\Sigma_\lambda \right )-12g_1'^2\left ( Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\left (\Sigma_{a_\kappa}-M_1'\Sigma_{\kappa}\right )\nonumber\\
-&{}+48g_2^4M_2+\frac{576}{25}g_1^4M_1+8g_1'^4M_1'\Sigma_Q\left ( Q_1^2+Q_2^2+Q_S^2\right )\bigg ],\label{eq:USSMTLambdaOt2Coeff}
+\beta_{a_\lambda}^{(1)} &= a_\lambda \left [ 2 \lambda ^2 + 2 \Sigma_\lambda +
+3 \Sigma_\kappa + 3 y_t^2 + 3 y_b^2 + y_{\tau }^2 - 3 g_2^2 -
+\frac{3}{5} g_1^2 - 2 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) g_1'^2 \right ]
+\nonumber \\
+& {} + \lambda \bigg [ 4 \lambda a_\lambda + 4 \Sigma_{a_\lambda} +
+6 \Sigma_{a_\kappa} + 6 y_t a_t + 6 y_b a_b + 2 y_\tau a_\tau + 6 g_2^2 M_2 +
+\frac{6}{5} g_1^2 M_1 \nonumber \\
+& {} + 4 g_1'^2 M_1' \left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) \bigg ] ,
+\label{eq:USSMTLambdaBetaOneLoop} \\
+\beta_{a_\lambda}^{(2)} &= a_\lambda \bigg \{ -2 \lambda^2 \left ( \lambda^2
++ 2 \Sigma_\lambda + 3 \Sigma_\kappa \right ) - 4 \Pi_\lambda - 6 \Pi_\kappa
+- 3 \lambda^2 \left ( 3 y_t^2 + 3 y_b^2 + y_\tau^2 \right ) \nonumber \\
+& {} - 3 \left ( 3 y_t^4 + 3 y_b^4 + 2 y_t^2 y_b^2 + y_\tau^2 \right ) +
+6 g_2^2 \Sigma_\lambda + \frac{2}{5} g_1^2 \left ( 2 y_t^2 - y_b^2 +
+3 y_\tau^2 + 2 \Sigma_\kappa + 3 \Sigma_\lambda \right ) \nonumber \\
+& {} \left . + g_1'^2 \left [ 4 Q_S^2 \lambda^2 - 6 \left ( Q_2^2 - Q_Q^2 -
+Q_u^2 \right ) y_t^2 - 6 \left ( Q_1^2 - Q_Q^2 - Q_d^2 \right ) y_b^2 \right .
+\right . \nonumber \\
+& {} \left . - 2 \left ( Q_1^2 - Q_L^2 - Q_e^2 \right ) y_\tau^2 -
+6 \left ( Q_S^2 - Q_D^2 - Q_{\overline{D}}^2 \right ) \Sigma_\kappa -
+4 \left ( Q_S^2 - Q_1^2 - Q_2^2 \right ) \Sigma_\lambda \right ] \nonumber \\
+& {} + 16 g_3^2 \left ( y_t^2 + y_b^2 + \Sigma_\kappa \right ) +
+\frac{33}{2} g_2^4 + \frac{297}{50} g_1^4 + 2 g_1'^4 \left [ 2 Q_1^4 +
+2 Q_2^4 + 2 Q_S^4 + \left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) \Sigma_{Q} \right ]
+\nonumber \\
+& {} + \frac{9}{5} g_1^2 g_2^2 +6 g_1'^2 g_2^2 \left ( Q_1^2 + Q_2^2 \right )
++ \frac{6}{5} g_1^2 g_1'^2 \left ( Q_1^2 + Q_2^2 \right ) \bigg \} +
+\lambda \bigg \{ -4 \lambda a_\lambda \left ( \lambda^2 + 2 \Sigma_\lambda +
+3 \Sigma_\kappa \right ) \nonumber \\
+& {} - 4 \lambda^2 \left ( \lambda a_\lambda + 2 \Sigma_{a_\lambda} +
+3 \Sigma_{a_\kappa} \right ) - 16 \Pi_{a_\lambda} - 24 \Pi_{a_\kappa} -
+6 \lambda a_\lambda \left ( 3 y_t^2 + 3 y_b^2 + y_\tau^2 \right ) \nonumber \\
+& {} - 6 \lambda^2 \left ( 3 y_t a_t + 3 y_b a_b + y_\tau a_\tau \right )
+- 12 \left [ 3 y_t^3 a_t + 3 y_b^3 a_b + y_t y_b \left ( y_t a_b + y_b a_t
+\right ) + y_\tau^3 a_\tau \right ] \nonumber \\
+& {} + 32 g_3^2 \left [ y_t a_t + y_b a_b + \Sigma_{a_\kappa} - \left ( y_t^2
++ y_b^2 + \Sigma_\kappa \right ) M_3 \right ] + 12 g_2^2 \left (
+\Sigma_{a_\lambda} - \Sigma_\lambda M_2 \right ) \nonumber \\
+& {} + \frac{2}{5} g_1^2 \left [ 4 y_t a_t - 2 y_b a_b + 6 y_\tau a_\tau +
+4 \Sigma_{a_\kappa} + 6 \Sigma_{a_\lambda} - 2 \left ( 2 y_t^2 - y_b^2 +
+3 y_\tau^2 + 2 \Sigma_\kappa + 3 \Sigma_\lambda \right ) M_1 \right ]
+\nonumber \\
+& {} + 4 g_1'^2 \big [ 3 y_t \left ( Q_Q^2 - Q_2^2 + Q_u^2 \right )
+\left ( a_t - y_t M_1' \right ) + 3 y_b \left ( Q_Q^2 - Q_1^2 + Q_d^2 \right )
+\left ( a_b - y_b M_1' \right ) \nonumber \\
+& {} + y_\tau \left ( Q_L^2 - Q_1^2 + Q_e^2 \right ) \left ( a_\tau -
+y_\tau M_1' \right ) + 2Q_S^2 \lambda \left ( a_\lambda - \lambda M_1'
+\right ) \nonumber \\
+& {} + 2 \left ( Q_1^2 + Q_2^2 - Q_S^2 \right ) \left ( \Sigma_{a_\lambda} -
+\Sigma_\lambda M_1' \right ) + 3 \left ( Q_D^2 + Q_{\overline{D}}^2 - Q_S^2
+\right ) \left ( \Sigma_{a_\kappa} - \Sigma_\kappa M_1' \right ) \big ]
+\nonumber \\
+& {} - 66 g_2^4 M_2 - \frac{594}{25} g_1^4 M_1 - 8 g_1'^4 M_1' \left [ 2
+\left ( Q_1^4 + Q_2^4 + Q_S^4 \right ) + \left ( Q_1^2 + Q_2^2 + Q_S^2
+\right ) \Sigma_Q \right ] \nonumber \\
+& {} - \frac{18}{5} g_2^2 g_1^2 \left ( M_2 + M_1 \right ) - 12 g_2^2 g_1'^2
+\left ( Q_1^2 + Q_2^2 \right ) \left ( M_2 + M_1' \right ) \nonumber \\
+& {} - \frac{12}{5} g_1^2 g_1'^2 \left ( Q_1^2 + Q_2^2 \right ) \left ( M_1 +
+M_1' \right ) \bigg \} , \label{eq:USSMTLambdaBetaTwoLoop} \\
+b_{a_\lambda}^{(2)} &= \lambda \bigg [ 4 \lambda a_\lambda +
+4 \Sigma_{a_\lambda} + 6 \Sigma_{a_\kappa} + 6 y_t a_t + 6 y_b a_b +
+2 y_\tau a_\tau + 6 g_2^2 M_2 + \frac{6}{5} g_1^2 M_1 \nonumber \\
+& {} + 4 g_1'^2 M_1' \left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) \bigg ] \times
+\bigg [ 2 \lambda^2 + 2 \Sigma_\lambda + 3 \Sigma_\kappa + 3 y_t^2 +
+3 y_b^2 + y_{\tau }^2 - 3 g_2^2 \nonumber \\
+& {} - \frac{3}{5} g_1^2 - 2 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) g_1'^2
+\bigg ] + a_\lambda \bigg \{ 2 \lambda^2 \left ( 3 \lambda^2 +
+4 \Sigma_\lambda + 6 \Sigma_\kappa \right ) + 4 \Pi_\lambda + 6 \Pi_\kappa
+\nonumber \\
+& {} + 6 \left ( \Sigma_\lambda + \frac{3}{2} \Sigma_\kappa \right )^2 +
+7 \lambda^2 \left ( 3 y_t^2 + 3 y_b^2 + y_\tau^2 \right ) + \left ( 3 y_t^2 +
+3 y_b^2 + y_\tau^2 \right ) \left ( 2 \Sigma_\lambda + 3 \Sigma_\kappa
+\right ) \nonumber \\
+& {} + 3 \left ( \frac{15}{2} y_t^4 + \frac{15}{2} y_b^4 +
+\frac{3}{2} y_\tau^4 + 5 y_b^2 y_t^2 + 3 y_b^2 y_\tau^2 + y_t^2 y_\tau^2
+\right ) \nonumber \\
+& {} - \frac{1}{5} g_1^2 \left ( 12 \lambda^2 + 16 y_b^2 + 22 y_t^2 +
+12 y_\tau^2 + 12 \Sigma_\lambda + 13 \Sigma_\kappa \right ) \nonumber \\
+& {} - 3 g_2^2 \left ( 4 \lambda^2 + 6 y_t^2 + 6 y_b^2 + 2 y_\tau^2 +
+4 \Sigma_\lambda + 3 \Sigma_\kappa \right ) - 16 g_3^2 \left ( y_t^2 + y_b^2
++ \Sigma_\kappa \right ) \nonumber \\
+& {} - 2 g_1'^2 \left [ 4 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right )
+\left ( \lambda^2 + \Sigma_\lambda \right ) + 3 \Sigma_\kappa \left ( Q_1^2 +
+Q_2^2 + Q_S^2 + Q_D^2 + Q_{\overline{D}}^2 \right ) \right . \nonumber \\
+& {} + 3 y_b^2 \left ( 2 Q_1^2 + Q_2^2 + Q_d^2 + Q_Q^2 + Q_S^2 \right ) +
+3 y_t^2 \left ( Q_1^2 + 2 Q_2^2 + Q_Q^2 + Q_S^2 + Q_u^2 \right ) \nonumber \\
+& {} \left . + y_\tau^2 \left ( 2 Q_1^2 + Q_2^2 + Q_e^2 + Q_L^2 + Q_S^2
+\right ) \right ] - \frac{15}{2} g_2^4 - \frac{279}{50} g_1^4 \nonumber \\
+& {} + 2 g_1'^4 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) \left (Q_1^2 + Q_2^2
++ Q_S^2 - \Sigma_{Q} \right ) + \frac{9}{5} g_1^2 g_2^2 + 6 g_1'^2 g_2^2
+\left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) \nonumber \\
+& {} + \frac{6}{5} g_1^2 g_1'^2 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right )
+\bigg \} + \lambda \bigg [ 16 \lambda^3 a_{\lambda} + 16\Pi_{a_\lambda} +
+24 \Pi_{a_\kappa} + 8 \lambda \sum_{i=1}^3 \lambda_i \left ( \lambda_i
+a_{\lambda} + a_{\lambda_i} \lambda \right ) \nonumber \\
+& {} + 12 \lambda \sum_{i=1}^3 \kappa_i \left ( \kappa_i a_\lambda +
+a_{\kappa_i} \lambda \right ) + 8 \sum_{i=1}^3 \sum_{j=1}^3 \lambda_i
+\lambda_j \left ( a_{\lambda_i} \lambda_j + \lambda_i a_{\lambda_j} \right )
+\nonumber \\
+& {} + 18 \sum_{i=1}^3 \sum_{j=1}^3 \kappa_i \kappa_j \left ( \kappa_i
+a_{\kappa_j} + a_{\kappa_i} \kappa_j \right ) + 24 \sum_{i=1}^3 \sum_{j=1}^3
+\lambda_i \kappa_j \left ( \lambda_i a_{\kappa_j} + a_{\lambda_i} \kappa_j
+\right ) + 72 y_t^3 a_t + 72 y_b^3 a_b \nonumber \\
+& {} + 16 y_\tau^3 a_\tau + 12 y_t y_b \left ( a_t y_b + y_t a_b \right ) +
+12 y_b y_\tau \left ( a_b y_\tau + y_b a_\tau \right ) + 30 \lambda y_t
+\left ( a_{\lambda} y_t + \lambda a_t \right ) \nonumber \\
+& {} + 30 \lambda y_b \left ( a_{\lambda} y_b + \lambda a_b \right ) +
+10 \lambda y_\tau \left ( a_{\lambda} y_\tau + \lambda a_{\tau} \right ) -
+32 g_3^2 y_t \left ( a_t - y_t M_3 \right ) - 32 g_3^2 y_b \left ( a_b -
+y_b M_3 \right ) \nonumber \\
+& {} - 32 g_3^2 \left ( \Sigma_{a_\kappa} - M_3 \Sigma_\kappa \right ) -
+12 g_2^2 \lambda \left ( a_\lambda - \lambda M_2 \right ) - 18 g_2^2 y_t
+\left ( a_t - y_t M_2 \right ) - 18 g_2^2 y_b \left ( a_b - y_b M_2 \right )
+\nonumber \\
+& {} - 6 g_2^2 y_\tau \left ( a_\tau - y_\tau M_2 \right ) - 12 g_2^2
+\left ( \Sigma_{a_\lambda} - M_2 \Sigma_\lambda \right ) -
+\frac{12}{5} g_1^2 \lambda \left ( a_{\lambda} - \lambda M_1 \right )
+- \frac{26}{5} g_1^2 y_t \left ( a_t - y_t M_1 \right ) \nonumber \\
+& {} - \frac{14}{5} g_1^2 y_b \left ( a_b - y_b M_1 \right ) -
+\frac{18}{5} g_1^2 y_\tau \left ( a_\tau - y_\tau M_1 \right ) -
+\frac{12}{5} g_1^2 \left ( \Sigma_{a_\lambda} - M_1 \Sigma_\lambda \right )
+- \frac{8}{5}g_1^2 \left ( \Sigma_{a_\kappa} - M_1 \Sigma_\kappa \right )
+\nonumber \\
+& {} - 8 g_1'^2 \lambda \left ( Q_1^2 + Q_2^2 + Q_S^2 \right )
+\left ( a_\lambda - \lambda M_1' \right ) - 12 g_1'^2 y_t \left ( Q_2^2 +
+Q_Q^2 + Q_u^2 \right ) \left ( a_t - y_t M_1' \right ) \nonumber \\
+& {} - 12 g_1'^2 y_b \left ( Q_1^2 + Q_Q^2 + Q_d^2 \right )
+\left ( a_b - y_b M_1' \right ) - 4 g_1'^2 y_\tau \left ( Q_1^2 + Q_L^2 +
+Q_e^2 \right ) \left ( a_\tau - y_\tau M_1' \right ) \nonumber \\
+& {} - 8 g_1'^2 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right )
+\left ( \Sigma_{a_\lambda} - M_1' \Sigma_\lambda \right ) - 12 g_1'^2
+\left ( Q_S^2 + Q_D^2 + Q_{\overline{D}}^2 \right ) \left (\Sigma_{a_\kappa}
+- M_1' \Sigma_{\kappa} \right ) \nonumber \\
+& {} + 48 g_2^4 M_2 + \frac{576}{25} g_1^4 M_1 + 8 g_1'^4 M_1' \Sigma_Q
+\left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) \bigg ] ,
+\label{eq:USSMTLambdaOt2Coeff}
 \end{align}
@@
 \begin{align*}
-&\Sigma_{a_\lambda}=\lambda_1 a_{\lambda_1}+\lambda_2 a_{\lambda_2}+\lambda_3 a_{\lambda_3},\qquad \Sigma_{a_\kappa}=\kappa_1 a_{\kappa_1}+\kappa_2 a_{\kappa_2}+\kappa_3 a_{\kappa_3},\\
-&\Pi_{a_\lambda}=\lambda_1^3 a_{\lambda_1}+\lambda_2^3 a_{\lambda_2}+\lambda_3^3 a_{\lambda_3},\qquad \Pi_{a_\kappa}=\kappa_1^3 a_{\kappa_1}+\kappa_2^3 a_{\kappa_2}+\kappa_3^3 a_{\kappa_3},
+&\Sigma_{a_\lambda} = \lambda_1 a_{\lambda_1} + \lambda_2 a_{\lambda_2} +
+\lambda_3 a_{\lambda_3} , \qquad \Sigma_{a_\kappa} = \kappa_1 a_{\kappa_1}
++ \kappa_2 a_{\kappa_2} + \kappa_3 a_{\kappa_3} , \\
+&\Pi_{a_\lambda} = \lambda_1^3 a_{\lambda_1} + \lambda_2^3 a_{\lambda_2} +
+\lambda_3^3 a_{\lambda_3} , \qquad \Pi_{a_\kappa} = \kappa_1^3 a_{\kappa_1}
++ \kappa_2^3 a_{\kappa_2} + \kappa_3^3 a_{\kappa_3} ,
 \end{align*}
-Note that $a_{\lambda_i}\equiv\lambda_i A_{\lambda_i}$, $a_{\kappa_i}\equiv\kappa_i A_{\kappa_i}$, $a_t\equiv y_t A_t$, $a_b\equiv y_b A_b$ and $a_\tau= y_\tau A_\tau$. Defining 
+Note that $a_{\lambda_i} \equiv \lambda_i A_{\lambda_i}$, $a_{\kappa_i}
+\equiv \kappa_i A_{\kappa_i}$, $a_t \equiv y_t A_t$, $a_b \equiv y_b A_b$ and
+$a_\tau \equiv y_\tau A_\tau$.  Defining
 \begin{align}
-\Sigma_1&=\sum_{i=1}^3\left ( m_{Q_i}^2-2m_{u_i}^2+m_{d_i}^2+m_{e_i}^2-m_{L_i}^2+m_{H_i^u}^2-m_{H_i^d}^2+m_{\overline{D}_i}^2-m_{D_i}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1}\\
-\Sigma_1'&=\sum_{i=1}^3\left ( 6Q_Qm_{Q_i}^2+3Q_um_{u_i}^2+3Q_dm_{d_i}^2+Q_em_{e_i}^2+2Q_Lm_{L_i}^2+2Q_2m_{H_i^u}^2+2Q_1m_{H_i^d}^2\right.\nonumber\\
-&\quad{}\left.+Q_Sm_{Si}^2+3Q_{\overline{D}}m_{\overline{D}_i}^2+3Q_Dm_{D_i}^2\right )+2Q_{H'}m_{H'}^2+2Q_{\overline{H'}}m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1Pr}
+\Sigma_1 &= \sum_{i=1}^3 \left ( m_{Q_i}^2 - 2 m_{u_i}^2 + m_{d_i}^2 +
+m_{e_i}^2 - m_{L_i}^2 + m_{H_i^u}^2 - m_{H_i^d}^2 + m_{\overline{D}_i}^2 -
+m_{D_i}^2 \right ) - m_{H'}^2 + m_{\overline{H'}}^2 ,
+\label{eq:USSMGaugeSigmaTerm1} \\
+\Sigma_1' &= \sum_{i=1}^3 \left ( 6 Q_Q m_{Q_i}^2 + 3 Q_u m_{u_i}^2 +
+3 Q_d m_{d_i}^2 + Q_e m_{e_i}^2 + 2 Q_L m_{L_i}^2 + 2 Q_2 m_{H_i^u}^2 +
+2 Q_1 m_{H_i^d}^2 \right . \nonumber \\
+& \quad {} \left . + Q_S m_{S_i}^2 + 3 Q_{\overline{D}} m_{\overline{D}_i}^2 +
+3 Q_D m_{D_i}^2 \right ) + 2 Q_{H'} m_{H'}^2 +
+2 Q_{\overline{H'}} m_{\overline{H'}}^2 , \label{eq:USSMGaugeSigmaTerm1Pr}
 \end{align}
-the one- and two-loop $\beta$ functions and the $O(t^2)$ coefficients for $m_{H_d}^2$ are
+the one- and two-loop $\beta$ functions and the $O(t^2)$ coefficients for
+$m_{H_d}^2$ are
 \begin{subequations}
 \begin{align}
-\beta_{m_{H_d}^2}^{(1)}&=2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+2a_\lambda^2+6y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )+6a_b^2\nonumber\\
-&{}+2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )+2a_\tau^2-6g_2^2 M_2^2-\frac{6}{5}g_1^2 M_1^2-8Q_1^2g_1'^2 M_1'^2\nonumber\\
-&{}-\frac{3}{5}g_1^2\Sigma_1+2Q_1g_1'^2\Sigma_1',\label{eq:USSMmHd2BetaOneLoop}\\
-\beta_{m_{H_d}^2}^{(2)}&=-36y_b^4\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )-12y_\tau^4\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )-72y_b^2a_b^2-24y_\tau^2a_\tau^2\nonumber\\
-&{}-6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2\right )-6\left ( y_t a_b+y_ba_t\right )^2\nonumber\\
-&{}-4\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )-8\lambda^2a_\lambda^2-\lambda^2\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{H_i^d}^2\right.\right.\nonumber\\
-&{}\left.\left.+m_{H_i^u}^2\right )+6\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )\right ]-\sum_{i=1}^3\left [ 4\left ( \lambda_i a_{\lambda}+\lambda a_{\lambda_i}\right )^2\right.\nonumber\\
-&{}\left.+6\left ( \kappa_ia_\lambda+\lambda a_{\kappa_i}\right )^2\right ]-6\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )-6\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
-&{}+32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_3^2\right )+32g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
-&{}+\frac{6}{5}g_1^2y_t^2\left ( 3m_{H_u}^2+m_{Q_3}^2-4m_{u_3}^2\right )-\frac{2}{5}g_1^2y_b^2\left ( 11m_{H_d}^2-m_{Q_3}^2-4m_{d_3}^2+4M_1^2\right )\nonumber\\
-&{}-\frac{4}{5}g_1^2\left ( a_b^2-2y_ba_bM_1\right )+\frac{6}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2+4m_{e_3}^2+4M_1^2\right )+\frac{12}{5}g_1^2\left ( a_\tau^2-2y_\tau a_\tau M_1\right )\nonumber\\
-&{}+\frac{6}{5}g_1^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )+\kappa_i^2\left ( m_{\overline{D}_i}^2-m_{D_i}^2\right )\right ]+12g_1'^2y_b^2\left ( Q_Q^2+Q_d^2-Q_1^2\right )\times\nonumber\\
-&{}\times\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_1'^2\right )+12g_1'^2\left ( Q_Q^2+Q_d^2-Q_1^2\right )\left ( a_b^2-2y_ba_bM_1'\right )\nonumber\\
-&{}-24Q_1g_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q_3}^2+Q_dm_{d_3}^2\right )+4g_1'^2y_\tau^2\left ( Q_L^2+Q_e^2-Q_1^2\right )\times\nonumber\\
-&{}\times\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+2M_1'^2\right )+4g_1'^2\left ( Q_L^2+Q_e^2-Q_1^2\right )\left ( a_\tau^2-2y_\tau a_\tau M_1'\right )\nonumber\\
-&{}-8Q_1g_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L_3}^2+Q_em_{e_3}^2\right )-24Q_1g_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q_3}^2+Q_um_{u_3}^2\right )\nonumber\\
-&{}+4g_1'^2\lambda^2\left ( Q_2^2+Q_S^2-Q_1^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )+4g_1'^2\left ( Q_2^2+Q_S^2-Q_1^2\right )\times\nonumber\\
-&{}\times\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )-4Q_1g_1'^2\sum_{i=1}^3\left [ 2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )\right.\nonumber\\
-&{}\left.+3\kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )\right ]-\frac{16}{5}g_3^2g_1^2\sum_{i=1}^3\left ( m_{Q_i}^2-2m_{u_i}^2+m_{d_i}^2+m_{\overline{D}_i}^2-m_{D_i}^2\right )\nonumber\\
-&{}+32Q_1g_3^2g_1'^2\sum_{i=1}^3\left ( 2Q_Qm_{Q_i}^2+Q_um_{u_i}^2+Q_dm_{d_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2+Q_Dm_{D_i}^2\right )\nonumber\\
-&{}+3g_2^4\left [ 29M_2^2+m_{H'}^2+m_{\overline{H'}}^2+\sum_{i=1}^3\left ( 3m_{Q_i}^2+m_{L_i}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
-&{}+\frac{9}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2\right )+m_{H'}^2-m_{\overline{H'}}^2-\sum_{i=1}^3\left ( m_{Q_i}^2-m_{L_i}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
-&{}+12Q_1g_2^2g_1'^2\bigg [ 2Q_1\left ( M_1'^2+M_1'M_2+M_2^2\right )+Q_{H'}m_{H'}^2+Q_{\overline{H'}}m_{\overline{H'}}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Q_i}^2+Q_Lm_{L_i}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{25}g_1^4\bigg [ 891M_1^2+18m_{H'}^2\nonumber\\
-&{}+2\sum_{i=1}^3\left ( m_{d_i}^2+5m_{D_i}^2+m_{\overline{D}_i}^2-9m_{e_i}^2+9m_{H_i^d}^2+9m_{L_i}^2+m_{Q_i}^2+28m_{u_i}^2\right )\bigg ]\nonumber\\
-&{}-\frac{4}{5}g_1^2g_1'^2\bigg [ 6Q_1\big ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-4Q_1+3Q_2+Q_{\overline{H'}}-Q_{H'}-3Q_L\nonumber\\
-&{}+3Q_Q-6Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}^2m_{H'}^2\nonumber\\
-&{}+3\sum_{i=1}^3\big ( Q_d^2m_{d_i}^2+Q_{\overline{D}}^2m_{\overline{D}_i}^2-Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2-Q_L^2m_{L_i}^2\nonumber\\
-&{}+Q_Q^2m_{Q_i}^2-2Q_u^2m_{u_i}^2\big )+3Q_1Q_{\overline{H'}}m_{\overline{H'}}^2-9Q_1Q_{H'}m_{H'}^2+Q_1\sum_{i=1}^3\bigg ( 4Q_dm_{d_i}^2+4Q_{\overline{D}}m_{\overline{D}_i}^2\nonumber\\
-&{}-8Q_Dm_{D_i}^2-9Q_1m_{H_i^d}^2+3Q_2m_{H_i^u}^2-9Q_Lm_{L_i}^2+5Q_Qm_{Q_i}^2-20Q_um_{u_i}^2\big )\bigg ]\nonumber\\
-&{}+8Q_1g_1'^4\bigg [ 3Q_1M_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+8Q_1^2+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2\nonumber\\
-&{}+18Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^3m_{d_i}^2+3Q_{\overline{D}}^3m_{\overline{D}_i}^2+3Q_D^3m_{D_i}^2\nonumber\\
-&{}+Q_e^3m_{e_i}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{L_i}^2+6Q_Q^3m_{Q_i}^2+Q_S^3m_{Si}^2+3Q_u^3m_{u_i}^2\big )\nonumber\\
-&{}+2Q_1Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_1Q_{H'}^2m_{H'}^2+Q_1\sum_{i=1}^3\big ( 3Q_d^2m_{d_i}^2+3Q_{\overline{D}}^2m_{\overline{D}_i}^2+3Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2\nonumber\\
-&{}+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{L_i}^2+6Q_Q^2m_{Q_i}^2+Q_S^2m_{Si}^2+3Q_u^2m_{u_i}^2\big )\bigg ],\label{eq:USSMmHd2BetaTwoLoop}\\
-b_{m_{H_d}^2}^{(2)}&=72y_b^4\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )+144y_b^2a_b^2+16y_\tau^4\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )+32y_\tau^2 a_\tau^2\nonumber\\
-&{}+8\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+16\lambda^2 a_\lambda^2+6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2\right )\nonumber\\
-&{}+6\left ( y_t a_b+y_b a_t\right )^2+12y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+m_{L_3}^2+m_{e_3}^2\right )+12\left ( y_b a_\tau + y_\tau a_b\right )^2\nonumber\\
-&{}+6\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )+6\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
-&{}+12\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{d_3}^2\right )+12\left ( \lambda a_b+y_b a_\lambda\right )^2\nonumber\\
-&{}+4\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L_3}^2+m_{e_3}^2\right )+4\left ( \lambda a_\tau + y_\tau a_\lambda\right )^2\nonumber\\
-&{}+4\sum_{i=1}^3\left [ \lambda^2\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_{H_d}^2+m_{H_u}^2+2m_S^2\right )+\left ( \lambda a_{\lambda_i}+\lambda_i a_\lambda\right )^2\right ]\nonumber\\
-&{}+6\sum_{i=1}^3\left [ \lambda^2\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+\left ( \lambda a_{\kappa_i}+\kappa_i a_\lambda\right )^2\right ]\nonumber\\
-&{}-32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_3^2\right )-32g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
-&{}-18g_2^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_2^2\right )-18g_2^2\left ( a_b^2-2y_ba_bM_2\right )\nonumber\\
-&{}-6g_2^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+2M_2^2\right )-6g_2^2\left ( a_\tau^2-2y_\tau a_\tau M_2\right )\nonumber\\
-&{}-6g_2^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_2^2\right )-6g_2^2\left ( a_\lambda^2-2\lambda a_\lambda M_2\right )\nonumber\\
-&{}-\frac{14}{5}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_1^2\right )-\frac{14}{5}g_1^2\left ( a_b^2-2y_ba_bM_1\right )\nonumber\\
-&{}-\frac{18}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+2M_1^2\right )-\frac{18}{5}g_1^2\left ( a_\tau^2-2y_\tau a_\tau M_1\right )\nonumber\\
-&{}-\frac{6}{5}g_1^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1^2\right )-\frac{6}{5}g_1^2\left ( a_\lambda^2-2\lambda a_\lambda M_1\right )\nonumber\\
-&{}-12g_1'^2y_b^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_1'^2\right )-12g_1'^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\times\nonumber\\
-&{}\times\left ( a_b^2-2y_b a_b M_1'\right )+6g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( 2Q_1m_{H_d}^2+2Q_1m_{Q_3}^2+2Q_1m_{d_3}^2+\Sigma_1'\right )\nonumber\\
-&{}+12Q_1g_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )-4g_1'^2y_\tau^2\left ( Q_1^2+Q_L^2+Q_e^2\right )\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2+2M_1'^2\right )\nonumber\\
-&{}-4g_1'^2\left ( Q_1^2+Q_L^2+Q_e^2\right )\left ( a_\tau^2-2y_\tau a_\tau M_1'\right )+2g_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\times\nonumber\\
-&{}\times\left ( 2Q_1m_{H_d}^2+2Q_1m_{L_3}^2+2Q_1m_{e_3}^2+\Sigma_1'\right )+4Q_1g_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
-&{}+12Q_1g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )+12Q_1g_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )\nonumber\\
-&{}-4g_1'^2\lambda^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )-4g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\times\nonumber\\
-&{}\times\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )+2g_1'^2\lambda^2\left ( Q_1+Q_2+Q_S\right )\Sigma_1'+4Q_1g_1'^2\left ( Q_1+Q_2+Q_S\right )\times\nonumber\\
-&{}\times\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+a_{\lambda_i}^2\right ]+6Q_1g_1'^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\times\nonumber\\
-&{}\times\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+a_{\kappa_i}^2\right ]-96Q_1g_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )\nonumber\\
-&{}-72g_2^4M_2^2-12Q_1g_2^2g_1'^2M_2^2\left ( 9Q_Q+3Q_L+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\right )\nonumber\\
-&{}-\frac{288}{25}g_1^4\left ( \Sigma_1+3M_1^2\right )-\frac{3}{5}g_1^2g_1'^2\Big [ 4Q_1M_1^2\big ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2\nonumber\\
-&{}+Q_{\overline{H'}}+Q_{H'}+3Q_L+Q_Q+8Q_u\big )-4M_1'^2\big ( 3Q_d^2+3Q_{\overline{D}}^2-3Q_D^2+3Q_e^2-3Q_1^2+3Q_2^2\nonumber\\
-&{}+Q_{\overline{H'}}^2-Q_{H'}^2-3Q_L^2+3Q_Q^2-6Q_u^2\big )+\left ( \Sigma_1'-2Q_1\Sigma_1\right )\Sigma_Q^Y\Big ]-4Q_1g_1'^4\Big [ 2M_1'^2\big ( 9Q_d^3\nonumber\\
-&{}+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )\nonumber\\
-&{}+\left ( 6Q_1M_1'^2-\Sigma_1'\right )\Sigma_Q\Big ].\label{eq:USSMmHd2Ot2Coeff}
+\beta_{m_{H_d}^2}^{(1)} &= 2 \lambda^2 \left ( m_{H_d}^2 + m_{H_u}^2 +
+m_S^2 \right ) + 2 a_\lambda^2 + 6 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 +
+m_{d_3}^2 \right ) + 6 a_b^2 \nonumber \\
+& {} + 2 y_\tau^2 \left ( m_{H_d}^2 + m_{L_3}^2 + m_{e_3}^2 \right ) +
+2 a_\tau^2 - 6 g_2^2 M_2^2 - \frac{6}{5} g_1^2 M_1^2 - 8 Q_1^2 g_1'^2 M_1'^2
+\nonumber \\
+& {} - \frac{3}{5} g_1^2 \Sigma_1 + 2 Q_1 g_1'^2 \Sigma_1' ,
+\label{eq:USSMmHd2BetaOneLoop} \\
+\beta_{m_{H_d}^2}^{(2)} &= -36 y_b^4 \left ( m_{H_d}^2 + m_{Q_3}^2 +
+m_{d_3}^2 \right ) - 12 y_\tau^4 \left ( m_{H_d}^2 + m_{L_3}^2 + m_{e_3}^2
+\right ) - 72 y_b^2 a_b^2 - 24 y_\tau^2 a_\tau^2 \nonumber \\
+& {} - 6 y_t^2 y_b^2 \left ( m_{H_d}^2 + m_{H_u}^2 + 2 m_{Q_3}^2 + m_{u_3}^2
++ m_{d_3}^2 \right ) - 6 \left ( y_t a_b + y_b a_t \right )^2 \nonumber \\
+& {} - 4 \lambda^4 \left ( m_{H_d}^2 + m_{H_u}^2 + m_S^2 \right ) -
+8 \lambda^2 a_\lambda^2 - \lambda^2 \sum_{i=1}^3 \left [ 4 \lambda_i^2
+\left ( m_{H_d}^2 + m_{H_u}^2 + 2 m_S^2 + m_{H_i^d}^2 \right . \right .
+\nonumber \\
+& {} \left . \left . + m_{H_i^u}^2 \right ) + 6 \kappa_i^2 \left ( m_{H_d}^2
++ m_{H_u}^2 + 2 m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2 \right ) \right ]
+- \sum_{i=1}^3 \left [ 4 \left ( \lambda_i a_{\lambda} + \lambda a_{\lambda_i}
+\right )^2 \right . \nonumber \\
+& {} \left . + 6 \left ( \kappa_i a_\lambda + \lambda a_{\kappa_i} \right )^2
+\right ] - 6 \lambda^2 y_t^2 \left ( m_{H_d}^2 + 2 m_{H_u}^2 + m_S^2 +
+m_{Q_3}^2 + m_{u_3}^2 \right ) - 6 \left ( \lambda a_t + y_t a_\lambda
+\right )^2 \nonumber \\
+& {} + 32 g_3^2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 + 2 M_3^2
+\right ) + 32 g_3^2 \left ( a_b^2 - 2 y_b a_b M_3 \right ) \nonumber \\
+& {} + \frac{6}{5} g_1^2 y_t^2 \left ( 3 m_{H_u}^2 + m_{Q_3}^2 -
+4 m_{u_3}^2 \right ) - \frac{2}{5} g_1^2 y_b^2 \left ( 11 m_{H_d}^2 -
+m_{Q_3}^2 - 4 m_{d_3}^2 + 4 M_1^2 \right ) \nonumber \\
+& {} - \frac{4}{5} g_1^2 \left ( a_b^2 - 2 y_b a_b M_1 \right ) +
+\frac{6}{5} g_1^2 y_\tau^2 \left ( m_{H_d}^2 + m_{L_3}^2 + 4 m_{e_3}^2 +
+4 M_1^2 \right ) + \frac{12}{5} g_1^2 \left ( a_\tau^2 - 2 y_\tau a_\tau M_1
+\right ) \nonumber \\
+& {} + \frac{6}{5} g_1^2 \sum_{i=1}^3 \left [ \lambda_i^2 \left ( m_{H_i^d}^2
+- m_{H_i^u}^2 \right ) + \kappa_i^2 \left ( m_{\overline{D}_i}^2 - m_{D_i}^2
+\right ) \right ] + 12 g_1'^2 y_b^2 \left ( Q_Q^2 + Q_d^2 - Q_1^2 \right )
+\nonumber \\
+& {} \times \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 + 2 M_1'^2 \right ) +
+12 g_1'^2 \left ( Q_Q^2 + Q_d^2 - Q_1^2 \right ) \left ( a_b^2 -
+2 y_b a_b M_1' \right ) \nonumber \\
+& {} - 24 Q_1 g_1'^2 y_b^2 \left ( Q_1 m_{H_d}^2 + Q_Q m_{Q_3}^2 +
+Q_d m_{d_3}^2 \right ) + 4 g_1'^2 y_\tau^2 \left ( Q_L^2 + Q_e^2 - Q_1^2
+\right ) \nonumber \\
+& {} \times \left ( m_{H_d}^2 + m_{L_3}^2 + m_{e_3}^2 + 2 M_1'^2 \right ) +
+4 g_1'^2 \left ( Q_L^2 + Q_e^2 - Q_1^2 \right ) \left ( a_\tau^2 -
+2 y_\tau a_\tau M_1' \right ) \nonumber \\
+& {} - 8 Q_1 g_1'^2 y_\tau^2 \left ( Q_1 m_{H_d}^2 + Q_L m_{L_3}^2 +
+Q_e m_{e_3}^2 \right ) -24 Q_1 g_1'^2 y_t^2 \left ( Q_2 m_{H_u}^2 +
+Q_Q m_{Q_3}^2 + Q_u m_{u_3}^2 \right ) \nonumber \\
+& {} + 4 g_1'^2 \lambda^2 \left ( Q_2^2 + Q_S^2 - Q_1^2 \right )
+\left ( m_{H_d}^2 + m_{H_u}^2 + m_S^2 + 2 M_1'^2 \right ) + 4 g_1'^2
+\left ( Q_2^2 + Q_S^2 - Q_1^2 \right ) \nonumber \\
+& {} \times \left ( a_\lambda^2 - 2 \lambda a_\lambda M_1' \right ) -
+4 Q_1 g_1'^2 \sum_{i=1}^3 \left [ 2 \lambda_i^2 \left ( Q_1 m_{H_i^d}^2 +
+Q_2 m_{H_i^u}^2 + Q_S m_S^2 \right ) \right . \nonumber \\
+& {} \left . + 3 \kappa_i^2 \left ( m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2
+\right ) \right ] - \frac{16}{5} g_3^2 g_1^2 \sum_{i=1}^3 \left ( m_{Q_i}^2
+- 2 m_{u_i}^2 + m_{d_i}^2 + m_{\overline{D}_i}^2 - m_{D_i}^2 \right )
+\nonumber \\
+& {} + 32 Q_1 g_3^2 g_1'^2 \sum_{i=1}^3 \left ( 2 Q_Q m_{Q_i}^2 +
+Q_u m_{u_i}^2 + Q_d m_{d_i}^2 + Q_{\overline{D}} m_{\overline{D}_i}^2 +
+Q_D m_{D_i}^2 \right ) \nonumber \\
+& {} + 3 g_2^4 \left [ 29 M_2^2 + m_{H'}^2 + m_{\overline{H'}}^2 +
+\sum_{i=1}^3 \left ( 3 m_{Q_i}^2 + m_{L_i}^2 + m_{H_i^d}^2 + m_{H_i^u}^2
+\right ) \right ] \nonumber \\
+& {} + \frac{9}{5} g_2^2 g_1^2 \left [ 2 \left ( M_1^2 + M_1 M_2 + M_2^2
+\right ) + m_{H'}^2 - m_{\overline{H'}}^2 - \sum_{i=1}^3 \left ( m_{Q_i}^2 -
+m_{L_i}^2 + m_{H_i^u}^2 - m_{H_i^d}^2 \right ) \right ] \nonumber \\
+& {} + 12 Q_1 g_2^2 g_1'^2 \bigg [ 2 Q_1 \left ( M_1'^2 + M_1' M_2 + M_2^2
+\right ) + Q_{H'} m_{H'}^2 + Q_{\overline{H'}} m_{\overline{H'}}^2 \nonumber \\
+& {} + \sum_{i=1}^3 \left ( 3 Q_Q m_{Q_i}^2 + Q_L m_{L_i}^2 + Q_1 m_{H_i^d}^2
++ Q_2 m_{H_i^u}^2 \right ) \bigg ] + \frac{1}{25} g_1^4 \bigg [ 891 M_1^2 +
+18 m_{H'}^2 \nonumber \\
+& {} + 2 \sum_{i=1}^3 \left ( m_{d_i}^2 + 5 m_{D_i}^2 + m_{\overline{D}_i}^2
+- 9 m_{e_i}^2 + 9 m_{H_i^d}^2 + 9 m_{L_i}^2 + m_{Q_i}^2 + 28 m_{u_i}^2
+\right ) \bigg ] \nonumber \\
+& {} - \frac{4}{5} g_1^2 g_1'^2 \bigg [ 6 Q_1 \big ( 3 Q_d +
+3 Q_{\overline{D}} - 3 Q_D + 3 Q_e - 4 Q_1 + 3 Q_2 + Q_{\overline{H'}} -
+Q_{H'} - 3 Q_L \nonumber \\
+& {} + 3 Q_Q - 6 Q_u \big ) \left ( M_1^2 + M_1 M_1' + M_1'^2 \right ) +
+3 Q_{\overline{H'}}^2 m_{\overline{H'}}^2 - 3 Q_{H'}^2 m_{H'}^2 \nonumber \\
+& {} + 3 \sum_{i=1}^3 \big ( Q_d^2 m_{d_i}^2 +
+Q_{\overline{D}}^2 m_{\overline{D}_i}^2 - Q_D^2 m_{D_i}^2 + Q_e^2 m_{e_i}^2
+- Q_1^2 m_{H_i^d}^2 + Q_2^2 m_{H_i^u}^2 - Q_L^2 m_{L_i}^2 \nonumber \\
+& {} + Q_Q^2 m_{Q_i}^2 - 2 Q_u^2 m_{u_i}^2 \big ) +
+3 Q_1 Q_{\overline{H'}} m_{\overline{H'}}^2 - 9 Q_1 Q_{H'} m_{H'}^2 +
+Q_1 \sum_{i=1}^3 \bigg ( 4 Q_d m_{d_i}^2 +
+4 Q_{\overline{D}} m_{\overline{D}_i}^2 \nonumber \\
+& {} - 8 Q_D m_{D_i}^2 - 9 Q_1 m_{H_i^d}^2 + 3 Q_2 m_{H_i^u}^2 -
+9 Q_L m_{L_i}^2 + 5 Q_Q m_{Q_i}^2 - 20 Q_u m_{u_i}^2 \big ) \bigg ] \nonumber \\
+& {} + 8 Q_1 g_1'^4 \bigg [ 3 Q_1 M_1'^2 \big ( 9 Q_d^2 + 9 Q_{\overline{D}}^2
++ 9 Q_D^2 + 3 Q_e^2 + 8 Q_1^2 + 6 Q_2^2 + 2 Q_{\overline{H'}}^2 + 2 Q_{H'}^2
++ 6 Q_L^2 \nonumber \\
+& {} + 18 Q_Q^2 + 3 Q_S^2 + 9 Q_u^2 \big ) +
+2 Q_{\overline{H'}}^3 m_{\overline{H'}}^2 + 2 Q_{H'}^3 m_{H'}^2 +
+\sum_{i=1}^3 \big ( 3 Q_d^3 m_{d_i}^2 +
+3 Q_{\overline{D}}^3 m_{\overline{D}_i}^2 + 3 Q_D^3 m_{D_i}^2 \nonumber \\
+& {} + Q_e^3 m_{e_i}^2 + 2 Q_1^3 m_{H_i^d}^2 + 2 Q_2^3 m_{H_i^u}^2 +
+2 Q_L^3 m_{L_i}^2 + 6 Q_Q^3 m_{Q_i}^2 + Q_S^3 m_{S_i}^2 + 3 Q_u^3 m_{u_i}^2
+\big ) \nonumber \\
+& {} + 2 Q_1 Q_{\overline{H'}}^2 m_{\overline{H'}}^2 + 2 Q_1 Q_{H'}^2 m_{H'}^2
++ Q_1 \sum_{i=1}^3 \big ( 3 Q_d^2 m_{d_i}^2 +
+3 Q_{\overline{D}}^2 m_{\overline{D}_i}^2 + 3 Q_D^2 m_{D_i}^2 +
+Q_e^2 m_{e_i}^2 \nonumber \\
+& {} + 2 Q_1^2 m_{H_i^d}^2 + 2 Q_2^2 m_{H_i^u}^2 + 2 Q_L^2 m_{L_i}^2 +
+6 Q_Q^2 m_{Q_i}^2 + Q_S^2 m_{S_i}^2 + 3 Q_u^2 m_{u_i}^2 \big ) \bigg ] ,
+\label{eq:USSMmHd2BetaTwoLoop} \\
+b_{m_{H_d}^2}^{(2)} &= 72 y_b^4 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2
+\right ) + 144 y_b^2 a_b^2 + 16 y_\tau^4 \left ( m_{H_d}^2 + m_{L_3}^2 +
+m_{e_3}^2 \right ) + 32 y_\tau^2 a_\tau^2 \nonumber \\
+& {} + 8 \lambda^4 \left ( m_{H_d}^2 + m_{H_u}^2 + m_S^2 \right ) +
+16 \lambda^2 a_\lambda^2 + 6 y_t^2 y_b^2 \left ( m_{H_d}^2 + m_{H_u}^2 +
+2 m_{Q_3}^2 + m_{u_3}^2 + m_{d_3}^2 \right ) \nonumber \\
+& {} + 6 \left ( y_t a_b + y_b a_t \right )^2 + 12 y_b^2 y_\tau^2
+\left ( 2 m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 + m_{L_3}^2 + m_{e_3}^2 \right )
++ 12 \left ( y_b a_\tau + y_\tau a_b \right )^2 \nonumber \\
+& {} + 6 \lambda^2 y_t^2 \left ( m_{H_d}^2 + 2 m_{H_u}^2 + m_S^2 + m_{Q_3}^2
++ m_{u_3}^2 \right ) + 6 \left ( \lambda a_t + y_t a_\lambda \right )^2
+\nonumber \\
+& {} + 12 \lambda^2 y_b^2 \left ( 2 m_{H_d}^2 + m_{H_u}^2 + m_S^2 +
+m_{Q_3}^2 + m_{d_3}^2 \right ) + 12 \left ( \lambda a_b + y_b a_\lambda
+\right )^2 \nonumber \\
+& {} + 4 \lambda^2 y_\tau^2 \left ( 2 m_{H_d}^2 + m_{H_u}^2 + m_S^2 +
+m_{L_3}^2 + m_{e_3}^2 \right ) + 4 \left ( \lambda a_\tau + y_\tau a_\lambda
+\right )^2 \nonumber \\
+& {} + 4 \sum_{i=1}^3 \left [ \lambda^2 \lambda_i^2 \left ( m_{H_i^d}^2 +
+m_{H_i^u}^2 + m_{H_d}^2 + m_{H_u}^2 + 2 m_S^2 \right ) +
+\left ( \lambda a_{\lambda_i} + \lambda_i a_\lambda \right )^2 \right ]
+\nonumber \\
+& {} + 6 \sum_{i=1}^3 \left [ \lambda^2 \kappa_i^2 \left ( m_{H_d}^2 +
+m_{H_u}^2 + 2 m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2 \right ) +
+\left ( \lambda a_{\kappa_i} + \kappa_i a_\lambda \right )^2 \right ]
+\nonumber \\
+& {} - 32 g_3^2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 + 2 M_3^2
+\right ) - 32 g_3^2 \left ( a_b^2 - 2 y_b a_b M_3 \right ) \nonumber \\
+& {} - 18 g_2^2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 + 2 M_2^2
+\right ) - 18 g_2^2 \left ( a_b^2 - 2 y_b a_b M_2 \right ) \nonumber \\
+& {} - 6 g_2^2 y_\tau^2 \left ( m_{H_d}^2 + m_{L_3}^2 + m_{e_3}^2 + 2 M_2^2
+\right ) - 6 g_2^2 \left ( a_\tau^2 - 2 y_\tau a_\tau M_2 \right ) \nonumber \\
+& {} - 6 g_2^2 \lambda^2 \left ( m_{H_d}^2 + m_{H_u}^2 + m_S^2 + 2 M_2^2
+\right ) - 6 g_2^2 \left ( a_\lambda^2 - 2 \lambda a_\lambda M_2 \right )
+\nonumber \\
+& {} - \frac{14}{5} g_1^2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 +
+2 M_1^2 \right ) - \frac{14}{5} g_1^2 \left ( a_b^2 - 2 y_b a_b M_1 \right )
+\nonumber \\
+& {} - \frac{18}{5} g_1^2 y_\tau^2 \left ( m_{H_d}^2 + m_{L_3}^2 + m_{e_3}^2 +
+ 2 M_1^2 \right ) - \frac{18}{5} g_1^2 \left ( a_\tau^2 - 2 y_\tau a_\tau M_1
+\right ) \nonumber \\
+& {} - \frac{6}{5} g_1^2 \lambda^2 \left ( m_{H_d}^2 + m_{H_u}^2 + m_S^2 +
+2 M_1^2 \right ) - \frac{6}{5} g_1^2 \left ( a_\lambda^2 -
+2 \lambda a_\lambda M_1 \right ) \nonumber \\
+& {} - 12 g_1'^2 y_b^2 \left ( Q_1^2 + Q_Q^2 + Q_d^2 \right )
+\left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 + 2 M_1'^2 \right ) -12 g_1'^2
+\left ( Q_1^2 + Q_Q^2 + Q_d^2 \right ) \nonumber \\
+& {} \times \left ( a_b^2 - 2 y_b a_b M_1'\right ) + 6 g_1'^2 y_b^2
+\left ( Q_1 + Q_Q + Q_d \right ) \left ( 2 Q_1 m_{H_d}^2 + 2 Q_1 m_{Q_3}^2 +
+2 Q_1 m_{d_3}^2 + \Sigma_1' \right ) \nonumber \\
+& {} + 12 Q_1 g_1'^2 a_b^2 \left ( Q_1 + Q_Q + Q_d \right ) -
+4 g_1'^2 y_\tau^2 \left ( Q_1^2 + Q_L^2 + Q_e^2 \right ) \left ( m_{H_d}^2 +
+m_{L_3}^2 + m_{e_3}^2 + 2 M_1'^2 \right ) \nonumber \\
+& {} - 4 g_1'^2 \left ( Q_1^2 + Q_L^2 + Q_e^2 \right ) \left ( a_\tau^2 -
+2 y_\tau a_\tau M_1' \right ) + 2 g_1'^2 y_\tau^2 \left ( Q_1 + Q_L +Q_e
+\right ) \nonumber \\
+& {} \times \left ( 2 Q_1 m_{H_d}^2 + 2 Q_1 m_{L_3}^2 + 2 Q_1 m_{e_3}^2 +
+\Sigma_1' \right ) + 4 Q_1 g_1'^2 a_\tau^2 \left ( Q_1 + Q_L + Q_e \right )
+\nonumber \\
+& {} + 12 Q_1 g_1'^2 y_t^2 \left ( Q_2 + Q_Q + Q_u \right ) \left ( m_{H_u}^2
++ m_{Q_3}^2 + m_{u_3}^2 \right ) + 12 Q_1 g_1'^2 a_t^2 \left ( Q_2 + Q_Q +
+Q_u \right ) \nonumber \\
+& {} - 4 g_1'^2 \lambda^2 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right )
+\left ( m_{H_d}^2 + m_{H_u}^2 + m_S^2 + 2 M_1'^2 \right ) - 4 g_1'^2
+\left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) \nonumber \\
+& {} \times \left ( a_\lambda^2 - 2 \lambda a_\lambda M_1' \right ) +
+2 g_1'^2 \lambda^2 \left ( Q_1 + Q_2 + Q_S \right ) \Sigma_1' +
+4 Q_1 g_1'^2 \left ( Q_1 + Q_2 + Q_S \right ) \nonumber \\
+& {} \times \sum_{i=1}^3 \left [ \lambda_i^2 \left ( m_{H_i^d}^2 + m_{H_i^u}^2
++ m_S^2 \right ) + a_{\lambda_i}^2 \right ] + 6 Q_1 g_1'^2 \left ( Q_S + Q_D
++ Q_{\overline{D}} \right ) \nonumber \\
+& {} \times \sum_{i=1}^3 \left [ \kappa_i^2 \left ( m_S^2 + m_{D_i}^2 +
+m_{\overline{D}_i}^2 \right ) + a_{\kappa_i}^2 \right ] -
+96 Q_1 g_3^2 g_1'^2 M_3^2 \left ( 2 Q_Q + Q_u + Q_d + Q_D + Q_{\overline{D}}
+\right ) \nonumber \\
+& {} - 72 g_2^4 M_2^2 - 12 Q_1 g_2^2 g_1'^2 M_2^2 \left ( 9 Q_Q + 3 Q_L +
+3 Q_1 + 3 Q_2 + Q_{\overline{H'}} + Q_{H'} \right ) \nonumber \\
+& {} - \frac{288}{25} g_1^4 \left ( \Sigma_1 + 3 M_1^2 \right ) -
+\frac{3}{5} g_1^2 g_1'^2 \Big [ 4 Q_1 M_1^2 \big ( 2 Q_d + 2 Q_{\overline{D}}
++ 2 Q_D + 6 Q_e + 3 Q_1 + 3 Q_2 \nonumber \\
+& {} + Q_{\overline{H'}} + Q_{H'} + 3 Q_L + Q_Q + 8 Q_u \big ) - 4 M_1'^2
+\big ( 3 Q_d^2 + 3 Q_{\overline{D}}^2 - 3 Q_D^2 + 3 Q_e^2 - 3 Q_1^2 +
+3 Q_2^2 \nonumber \\
+& {} + Q_{\overline{H'}}^2 - Q_{H'}^2 - 3 Q_L^2 + 3 Q_Q^2 - 6 Q_u^2 \big ) +
+\left ( \Sigma_1' - 2 Q_1 \Sigma_1 \right ) \Sigma_Q^Y \Big ] -
+4 Q_1 g_1'^4 \Big [ 2 M_1'^2 \big ( 9 Q_d^3 \nonumber \\
+& {} + 9 Q_{\overline{D}}^3 + 9 Q_D^3 + 3 Q_e^3 + 6 Q_1^3 + 6 Q_2^3 +
+2 Q_{\overline{H'}}^3 + 2 Q_{H'}^3 + 6 Q_L^3 + 18 Q_Q^3 + 3 Q_S^3 +
+9 Q_u^3 \big ) \nonumber \\
+& {} + \left ( 6 Q_1 M_1'^2 - \Sigma_1' \right ) \Sigma_Q \Big ] .
+\label{eq:USSMmHd2Ot2Coeff}
 \end{align}
@@
 \begin{align}
-\beta_{m_{H_u}^2}^{(1)}&=2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+2a_\lambda^2+6y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )+6a_t^2\nonumber\\
-&{}-6g_2^2M_2^2-\frac{6}{5}g_1^2M_1^2-8Q_2^2g_1'^2M_1'^2+\frac{3}{5}g_1^2\Sigma_1+2Q_2g_1'^2\Sigma_1',\label{eq:USSMmHu2BetaOneLoop}\\
-\beta_{m_{H_u}^2}^{(2)}&=-36y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )-6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2\right )\nonumber\\
-&{}-72y_t^2a_t^2-6\left ( y_ta_b+y_ba_t\right )^2-4\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )-8\lambda^2a_{\lambda}^2\nonumber\\
-&{}-\lambda^2\sum_{i=1}^3\bigg [ 4\lambda_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\nonumber\\
-&{}+6\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )\bigg ]-\sum_{i=1}^3 \big [4\left ( \lambda_ia_{\lambda}+\lambda a_{\lambda_i}\right )^2\nonumber\\
-&{}+6\left ( \kappa_i a_{\lambda}+\lambda a_{\kappa_i}\right )^2\big ]-6\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{d_3}^2\right )\nonumber\\
-&{}-2\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L_3}^2+m_{e_3}^2\right )-6\left ( \lambda a_b+y_ba_{\lambda}\right )^2-2\left ( \lambda a_\tau+y_\tau a_{\lambda}\right )^2\nonumber\\
-&{}+32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_3^2\right )+32g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
-&{}+\frac{2}{5}g_1^2y_t^2\left ( -5m_{H_u}^2+m_{Q_3}^2+16m_{u_3}^2+8M_1^2\right )+\frac{8}{5}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
-&{}+\frac{6}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q_3}^2-2m_{d_3}^2\right )+\frac{6}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2-2m_{e_3}^2\right )\nonumber\\
-&{}+\frac{6}{5}g_1^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )+\kappa_i^2\left ( m_{D_i}^2-m_{\overline{D}_i}^2\right )\right ]\nonumber\\
-&{}+12g_1'^2y_t^2\left ( Q_Q^2+Q_u^2-Q_2^2\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1'^2\right )\nonumber\\
-&{}+12g_1'^2\left ( Q_Q^2+Q_u^2-Q_2^2\right )\left ( a_t^2-2y_ta_tM_1'\right )-24Q_2g_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q_3}^2+Q_um_{u_3}^2\right )\nonumber\\
-&{}-24Q_2g_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q_3}^2+Q_dm_{d_3}^2\right )-8Q_2g_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L_3}^2+Q_em_{e_3}^2\right )\nonumber\\
-&{}+4g_1'^2\lambda^2\left ( Q_1^2-Q_2^2+Q_S^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )\nonumber\\
-&{}+4g_1'^2\left ( Q_1^2-Q_2^2+Q_S^2\right )\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )\nonumber\\
-&{}-4Q_2g_1'^2\sum_{i=1}^3\left [ 2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )+3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{D_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2\right )\right ]\nonumber\\
-&{}+\frac{16}{5}g_3^2g_1^2\sum_{i=1}^3\left ( m_{Q_i}^2-2m_{u_i}^2+m_{d_i}^2+m_{\overline{D}_i}^2-m_{D_i}^2\right )\nonumber\\
-&{}+32Q_2g_3^2g_1'^2\sum_{i=1}^3\left ( 2Q_Qm_{Q_i}^2+Q_um_{u_i}^2+Q_dm_{d_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2+Q_Dm_{D_i}^2\right )\nonumber\\
-&{}+3g_2^4\left [ 29M_2^2+m_{H'}^2+m_{\overline{H'}}^2+\sum_{i=1}^3\left ( 3m_{Q_i}^2+m_{L_i}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
-&{}+\frac{9}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2\right )+m_{\overline{H'}}^2-m_{H'}^2+\sum_{i=1}^3\left ( m_{Q_i}^2-m_{L_i}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
-&{}+12Q_2g_2^2g_1'^2\bigg [ 2Q_2\left ( M_1'^2+M_1'M_2+M_2^2\right )+Q_{H'}m_{H'}^2+Q_{\overline{H'}}m_{\overline{H'}}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Q_i}^2+Q_Lm_{L_i}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{25}g_1^4\bigg [ 891M_1^2+18m_{\overline{H'}}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 10m_{d_i}^2+2m_{D_i}^2+10m_{\overline{D}_i}^2+54m_{e_i}^2+18m_{H_i^u}^2+4m_{Q_i}^2-8m_{u_i}^2\right )\bigg ]\nonumber\\
-&{}+\frac{4}{5}g_1^2g_1'^2\bigg [ 6Q_2\big ( 3Q_d+Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+4Q_2+Q_{\overline{H'}}-Q_{H'}-3Q_L\nonumber\\
-&{}+3Q_Q-6Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}^2m_{H'}^2\nonumber\\
-&{}+3\sum_{i=1}^3\left ( Q_d^2m_{d_i}^2+Q_{\overline{D}}^2m_{\overline{D}_i}^2-Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2-Q_L^2m_{L_i}^2\right.\nonumber\\
-&{}\left.+Q_Q^2m_{Q_i}^2-2Q_u^2m_{u_i}^2\right )+9Q_2Q_{\overline{H'}}m_{\overline{H'}}^2-3Q_2Q_{H'}m_{H'}^2+Q_2\sum_{i=1}^3\left ( 8Q_dm_{d_i}^2+8Q_{\overline{D}}m_{\overline{D}_i}^2\right.\nonumber\\
-&{}\left.-4Q_Dm_{D_i}^2+12Q_em_{e_i}^2-3Q_1m_{H_i^d}^2+9Q_2m_{H_i^u}^2-3Q_Lm_{L_i}^2+7Q_Qm_{Q_i}^2-4Q_um_{u_i}^2\right )\bigg ]\nonumber\\
-&{}+8Q_2g_1'^4\bigg [ 3Q_2M_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2+8Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2\nonumber\\
-&{}+18Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^3m_{d_i}^2+3Q_{\overline{D}}^3m_{\overline{D}_i}^2\nonumber\\
-&{}+3Q_D^3m_{D_i}^2+Q_e^3m_{e_i}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{L_i}^2+6Q_Q^3m_{Q_i}^2+Q_S^3m_{Si}^2+3Q_u^3m_{u_i}^2\big )\nonumber\\
-&{}+2Q_2Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_2Q_{H'}^2m_{H'}^2+Q_2\sum_{i=1}^3\big ( 3Q_d^2m_{d_i}^2+3Q_{\overline{D}}^2m_{\overline{D}_i}^2+3Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2\nonumber\\
-&{}+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{L_i}^2+6Q_Q^2m_{Q_i}^2+Q_S^2m_{Si}^2+3Q_u^2m_{u_i}^2\big )\bigg ],\label{eq:USSMmHu2BetaTwoLoop}\\
-b_{m_{H_u}^2}^{(2)}&=72y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )+144y_t^2a_t^2+8\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+16\lambda^2a_\lambda^2\nonumber\\
-&{}+6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2\right )+6\left ( y_ta_b+y_ba_t\right )^2\nonumber\\
-&{}+12\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )+12\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
-&{}+6\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{d_3}^2\right )+6\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
-&{}+2\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L_3}^2+m_{e_3}^2\right )+2\left ( \lambda a_\tau+y_\tau a_\lambda\right )^2\nonumber\\
-&{}+4\sum_{i=1}^3 \left [ \lambda^2\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_{H_d}^2+m_{H_u}^2+2m_S^2\right )+\left ( \lambda a_{\lambda_i}+\lambda_i a_{\lambda}\right )^2\right ] \nonumber\\
-&{}+6\sum_{i=1}^3\left [ \lambda^2\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )
-+\left ( \lambda a_{\kappa_i}+\kappa_i a_\lambda\right )^2\right ]\nonumber\\
-&{}-32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_3^2\right )-32g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
-&{}-18g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_2^2\right )-18g_2^2\left ( a_t^2-2y_ta_tM_2\right )\\
-&{}-6g_2^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_2^2\right )-6g_2^2\left ( a_\lambda^2-2\lambda a_\lambda M_2\right )\nonumber\\
-&{}-\frac{26}{5}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1^2\right )-\frac{26}{5}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
-&{}-\frac{6}{5}g_1^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1^2\right )-\frac{6}{5}g_1^2\left ( a_\lambda^2-2\lambda a_\lambda M_1\right )\nonumber\\
-&{}-12g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1'^2\right )-12g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\times\nonumber\\
-&{}\times\left ( a_t^2-2y_ta_tM_1'\right )+6g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 2Q_2m_{H_u}^2+2Q_2m_{Q_3}^2+2Q_2m_{u_3}^2+\Sigma_1'\right )\nonumber\\
-&{}+12Q_2g_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_2g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )\nonumber\\
-&{}+12Q_2g_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )+4Q_2g_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )\nonumber\\
-&{}+4Q_2g_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )-4g_1'^2\lambda^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )\nonumber\\
-&{}-4g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )+2g_1'^2\lambda^2\left ( Q_1+Q_2+Q_S\right )\Sigma_1'\nonumber\\
-&{}+4Q_2g_1'^2\left ( Q_1+Q_2+Q_S\right )\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+a_{\lambda_i}^2\right ]\nonumber\\
-&{}+6Q_2g_1'^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+a_{\kappa_i}^2\right ]\nonumber\\
-&{}-96Q_2g_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )-72g_2^4M_2^2\nonumber\\
-&{}-12Q_2g_2^2g_1'^2M_2^2\left ( 9Q_Q+3Q_L+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\right )+\frac{288}{25}g_1^4\left ( \Sigma_1-3M_1^2\right )\nonumber\\
-&{}-\frac{3}{5}g_1^2g_1'^2\Big [ 4Q_2M_1^2\big ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}+3Q_L\nonumber\\
-&{}+Q_Q+8Q_u\big )+4M_1'^2\big ( 3Q_d^2+3Q_{\overline{D}}^2-3Q_D^2+3Q_e^2-3Q_1^2+3Q_2^2+Q_{\overline{H'}}^2-Q_{H'}^2\nonumber\\
-&{}-3Q_L^2+3Q_Q^2-6Q_u^2\big )-\left ( 2Q_2\Sigma_1+\Sigma_1'\right )\Sigma_Q^Y\Big ]-4Q_2g_1'^4\Big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3\nonumber\\
-&{}+3Q_e^3+6Q_1^3+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )\nonumber\\
-&{}+\left ( 6Q_2M_1'^2-\Sigma_1'\right )\Sigma_Q\Big ],\label{eq:USSMmHu2Ot2Coeff}
+\beta_{m_{H_u}^2}^{(1)} &= 2 \lambda^2 \left ( m_{H_d}^2 + m_{H_u}^2 +
+m_S^2 \right ) + 2 a_\lambda^2 + 6 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 +
+m_{u_3}^2 \right ) + 6 a_t^2 \nonumber \\
+& {} - 6 g_2^2 M_2^2 - \frac{6}{5} g_1^2 M_1^2 - 8 Q_2^2 g_1'^2 M_1'^2 +
+\frac{3}{5} g_1^2 \Sigma_1 + 2 Q_2 g_1'^2 \Sigma_1' ,
+\label{eq:USSMmHu2BetaOneLoop} \\
+\beta_{m_{H_u}^2}^{(2)} &= -36 y_t^4 \left ( m_{H_u}^2 + m_{Q_3}^2 +
+m_{u_3}^2 \right ) - 6 y_t^2 y_b^2 \left ( m_{H_u}^2 + m_{H_d}^2 + 2 m_{Q_3}^2
++ m_{u_3}^2 + m_{d_3}^2 \right ) \nonumber \\
+& {} - 72 y_t^2 a_t^2 - 6 \left ( y_t a_b + y_b a_t \right )^2 -
+4 \lambda^4 \left ( m_{H_d}^2 + m_{H_u}^2 + m_S^2 \right ) -
+8 \lambda^2 a_{\lambda}^2 \nonumber \\
+& {} - \lambda^2 \sum_{i=1}^3 \bigg [ 4 \lambda_i^2 \left ( m_{H_d}^2 +
+m_{H_u}^2 + 2 m_S^2 + m_{H_i^d}^2 + m_{H_i^u}^2 \right ) \nonumber \\
+& {} + 6 \kappa_i^2 \left ( m_{H_d}^2 + m_{H_u}^2 + 2 m_S^2 + m_{D_i}^2 +
+m_{\overline{D}_i}^2 \right ) \bigg ] - \sum_{i=1}^3 \big [
+4 \left ( \lambda_i a_{\lambda} + \lambda a_{\lambda_i} \right )^2
+\nonumber \\
+& {} + 6 \left ( \kappa_i a_{\lambda} + \lambda a_{\kappa_i} \right )^2
+\big ] - 6 \lambda^2 y_b^2 \left ( 2 m_{H_d}^2 + m_{H_u}^2 + m_S^2 +
+m_{Q_3}^2 + m_{d_3}^2 \right ) \nonumber \\
+& {} - 2 \lambda^2 y_\tau^2 \left ( 2 m_{H_d}^2 + m_{H_u}^2 + m_S^2 +
+m_{L_3}^2 + m_{e_3}^2 \right ) - 6 \left ( \lambda a_b + y_b a_{\lambda}
+\right )^2 - 2 \left ( \lambda a_\tau + y_\tau a_{\lambda} \right )^2
+\nonumber \\
+& {} + 32 g_3^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 + 2 M_3^2
+\right ) + 32 g_3^2 \left ( a_t^2 - 2 y_t a_t M_3 \right ) \nonumber \\
+& {} + \frac{2}{5} g_1^2 y_t^2 \left ( -5 m_{H_u}^2 + m_{Q_3}^2 +
+16 m_{u_3}^2 + 8 M_1^2 \right ) + \frac{8}{5} g_1^2 \left ( a_t^2 -
+2 y_t a_t M_1 \right ) \nonumber \\
+& {} + \frac{6}{5} g_1^2 y_b^2 \left ( 3 m_{H_d}^2 - m_{Q_3}^2 - 2 m_{d_3}^2
+\right ) + \frac{6}{5} g_1^2 y_\tau^2 \left ( m_{H_d}^2 + m_{L_3}^2 -
+2 m_{e_3}^2 \right ) \nonumber \\
+& {} + \frac{6}{5} g_1^2 \sum_{i=1}^3 \left [ \lambda_i^2 \left ( m_{H_i^d}^2
+- m_{H_i^u}^2 \right ) + \kappa_i^2 \left ( m_{D_i}^2 - m_{\overline{D}_i}^2
+\right ) \right ] \nonumber \\
+& {} + 12 g_1'^2 y_t^2 \left ( Q_Q^2 + Q_u^2 - Q_2^2 \right )
+\left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 + 2 M_1'^2 \right ) \nonumber \\
+& {} + 12 g_1'^2 \left ( Q_Q^2 + Q_u^2 - Q_2^2 \right ) \left ( a_t^2 -
+2 y_t a_t M_1' \right ) - 24 Q_2 g_1'^2 y_t^2 \left ( Q_2 m_{H_u}^2 +
+Q_Q m_{Q_3}^2 + Q_u m_{u_3}^2 \right ) \nonumber \\
+& {} - 24 Q_2 g_1'^2 y_b^2 \left ( Q_1 m_{H_d}^2 + Q_Q m_{Q_3}^2 +
+Q_d m_{d_3}^2 \right ) - 8 Q_2 g_1'^2 y_\tau^2 \left ( Q_1 m_{H_d}^2 +
+Q_L m_{L_3}^2 + Q_e m_{e_3}^2 \right ) \nonumber \\
+& {} + 4 g_1'^2 \lambda^2 \left ( Q_1^2 - Q_2^2 + Q_S^2 \right )
+\left ( m_{H_d}^2 + m_{H_u}^2 + m_S^2 + 2 M_1'^2 \right ) \nonumber \\
+& {} + 4 g_1'^2 \left ( Q_1^2 - Q_2^2 + Q_S^2 \right ) \left ( a_\lambda^2 -
+2 \lambda a_\lambda M_1' \right ) \nonumber \\
+& {} - 4 Q_2 g_1'^2 \sum_{i=1}^3 \left [ 2 \lambda_i^2 \left ( Q_1 m_{H_i^d}^2
++ Q_2 m_{H_i^u}^2 + Q_S m_S^2 \right ) + 3 \kappa_i^2 \left ( Q_S m_S^2 +
+Q_D m_{D_i}^2 + Q_{\overline{D}} m_{\overline{D}_i}^2 \right ) \right ]
+\nonumber \\
+& {} + \frac{16}{5} g_3^2 g_1^2 \sum_{i=1}^3 \left ( m_{Q_i}^2 - 2 m_{u_i}^2
++ m_{d_i}^2 + m_{\overline{D}_i}^2 - m_{D_i}^2 \right ) \nonumber \\
+& {} + 32 Q_2 g_3^2 g_1'^2 \sum_{i=1}^3 \left ( 2 Q_Q m_{Q_i}^2 +
+Q_u m_{u_i}^2 + Q_d m_{d_i}^2 + Q_{\overline{D}} m_{\overline{D}_i}^2
++ Q_D m_{D_i}^2 \right ) \nonumber \\
+& {} + 3 g_2^4 \left [ 29 M_2^2 + m_{H'}^2 + m_{\overline{H'}}^2 +
+\sum_{i=1}^3 \left ( 3 m_{Q_i}^2 + m_{L_i}^2 + m_{H_i^d}^2 + m_{H_i^u}^2
+\right ) \right ] \nonumber \\
+& {} + \frac{9}{5} g_2^2 g_1^2 \left [ 2 \left ( M_1^2 + M_1 M_2 + M_2^2
+\right ) + m_{\overline{H'}}^2 - m_{H'}^2 + \sum_{i=1}^3 \left ( m_{Q_i}^2 -
+m_{L_i}^2 + m_{H_i^u}^2 - m_{H_i^d}^2 \right ) \right ] \nonumber \\
+& {} + 12 Q_2 g_2^2 g_1'^2 \bigg [ 2 Q_2 \left ( M_1'^2 + M_1' M_2 + M_2^2
+\right ) + Q_{H'} m_{H'}^2 + Q_{\overline{H'}} m_{\overline{H'}}^2
+\nonumber \\
+& {} + \sum_{i=1}^3 \left ( 3 Q_Q m_{Q_i}^2 + Q_L m_{L_i}^2 + Q_1 m_{H_i^d}^2
++ Q_2 m_{H_i^u}^2 \right ) \bigg ] + \frac{1}{25} g_1^4 \bigg [ 891 M_1^2 +
+18 m_{\overline{H'}}^2 \nonumber \\
+& {} + \sum_{i=1}^3 \left ( 10 m_{d_i}^2 + 2 m_{D_i}^2 +
+10 m_{\overline{D}_i}^2 + 54 m_{e_i}^2 + 18 m_{H_i^u}^2 + 4 m_{Q_i}^2 -
+8 m_{u_i}^2 \right ) \bigg ] \nonumber \\
+& {} + \frac{4}{5} g_1^2 g_1'^2 \bigg [ 6 Q_2 \big ( 3 Q_d + Q_{\overline{D}}
+- 3 Q_D + 3 Q_e - 3 Q_1 + 4 Q_2 + Q_{\overline{H'}} - Q_{H'} - 3 Q_L
+\nonumber \\
+& {} + 3 Q_Q - 6 Q_u \big ) \left ( M_1^2 + M_1 M_1' + M_1'^2 \right ) +
+3 Q_{\overline{H'}}^2 m_{\overline{H'}}^2 - 3 Q_{H'}^2 m_{H'}^2 \nonumber \\
+& {} + 3 \sum_{i=1}^3 \left ( Q_d^2 m_{d_i}^2 +
+Q_{\overline{D}}^2 m_{\overline{D}_i}^2 - Q_D^2 m_{D_i}^2 + Q_e^2 m_{e_i}^2
+- Q_1^2 m_{H_i^d}^2 + Q_2^2 m_{H_i^u}^2 - Q_L^2 m_{L_i}^2 \right .
+\nonumber \\
+& {} \left . + Q_Q^2 m_{Q_i}^2 - 2 Q_u^2 m_{u_i}^2 \right ) +
+9 Q_2 Q_{\overline{H'}} m_{\overline{H'}}^2 - 3 Q_2 Q_{H'} m_{H'}^2 +
+Q_2 \sum_{i=1}^3 \left ( 8 Q_d m_{d_i}^2 +
+8 Q_{\overline{D}} m_{\overline{D}_i}^2 \right . \nonumber \\
+& {} \left . - 4 Q_D m_{D_i}^2 + 12 Q_e m_{e_i}^2 - 3 Q_1 m_{H_i^d}^2 +
+9 Q_2 m_{H_i^u}^2 - 3 Q_L m_{L_i}^2 + 7 Q_Q m_{Q_i}^2 - 4 Q_u m_{u_i}^2
+\right ) \bigg ] \nonumber \\
+& {} + 8 Q_2 g_1'^4 \bigg [ 3 Q_2 M_1'^2 \big ( 9 Q_d^2 +
+9 Q_{\overline{D}}^2 + 9 Q_D^2 + 3 Q_e^2 + 6 Q_1^2 + 8 Q_2^2 +
+2 Q_{\overline{H'}}^2 + 2 Q_{H'}^2 + 6 Q_L^2 \nonumber \\
+& {} + 18 Q_Q^2 + 3 Q_S^2 + 9 Q_u^2 \big ) +
+2 Q_{\overline{H'}}^3 m_{\overline{H'}}^2 + 2 Q_{H'}^3 m_{H'}^2 +
+\sum_{i=1}^3 \big ( 3 Q_d^3 m_{d_i}^2 +
+3 Q_{\overline{D}}^3 m_{\overline{D}_i}^2 \nonumber \\
+& {} + 3 Q_D^3 m_{D_i}^2 + Q_e^3 m_{e_i}^2 + 2 Q_1^3 m_{H_i^d}^2 +
+2 Q_2^3 m_{H_i^u}^2 + 2 Q_L^3 m_{L_i}^2 + 6 Q_Q^3 m_{Q_i}^2 + Q_S^3 m_{S_i}^2
++ 3 Q_u^3 m_{u_i}^2 \big ) \nonumber \\
+& {} + 2 Q_2 Q_{\overline{H'}}^2 m_{\overline{H'}}^2 +
+2 Q_2 Q_{H'}^2 m_{H'}^2 + Q_2 \sum_{i=1}^3 \big ( 3 Q_d^2 m_{d_i}^2 +
+3 Q_{\overline{D}}^2 m_{\overline{D}_i}^2 + 3 Q_D^2 m_{D_i}^2 +
+Q_e^2 m_{e_i}^2 \nonumber \\
+& {} + 2 Q_1^2 m_{H_i^d}^2 + 2 Q_2^2 m_{H_i^u}^2 + 2 Q_L^2 m_{L_i}^2 +
+6 Q_Q^2 m_{Q_i}^2 + Q_S^2 m_{S_i}^2 + 3 Q_u^2 m_{u_i}^2 \big ) \bigg ] ,
+\label{eq:USSMmHu2BetaTwoLoop} \\
+b_{m_{H_u}^2}^{(2)} &= 72 y_t^4 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2
+\right ) + 144 y_t^2 a_t^2 + 8 \lambda^4 \left ( m_{H_d}^2 + m_{H_u}^2 +
+m_S^2 \right ) + 16 \lambda^2 a_\lambda^2 \nonumber \\
+& {} + 6 y_t^2 y_b^2 \left ( m_{H_d}^2 + m_{H_u}^2 + 2 m_{Q_3}^2 +
+m_{u_3}^2 + m_{d_3}^2 \right ) + 6 \left ( y_t a_b + y_b a_t \right )^2
+\nonumber \\
+& {} + 12 \lambda^2 y_t^2 \left ( m_{H_d}^2 + 2 m_{H_u}^2 + m_S^2 + m_{Q_3}^2
++ m_{u_3}^2 \right ) + 12 \left ( \lambda a_t + y_t a_\lambda \right )^2
+\nonumber \\
+& {} + 6 \lambda^2 y_b^2 \left ( 2 m_{H_d}^2 + m_{H_u}^2 + m_S^2 + m_{Q_3}^2
++ m_{d_3}^2 \right ) + 6 \left ( \lambda a_b + y_b a_\lambda \right )^2
+\nonumber \\
+& {} + 2 \lambda^2 y_\tau^2 \left ( 2 m_{H_d}^2 + m_{H_u}^2 + m_S^2 +
+m_{L_3}^2 + m_{e_3}^2 \right ) + 2 \left ( \lambda a_\tau + y_\tau a_\lambda
+\right )^2 \nonumber \\
+& {} + 4 \sum_{i=1}^3 \left [ \lambda^2 \lambda_i^2 \left ( m_{H_i^d}^2 +
+m_{H_i^u}^2 + m_{H_d}^2 + m_{H_u}^2 + 2 m_S^2 \right ) + \left (
+\lambda a_{\lambda_i} + \lambda_i a_{\lambda} \right )^2 \right ] \nonumber \\
+& {} + 6 \sum_{i=1}^3 \left [ \lambda^2 \kappa_i^2 \left ( m_{H_d}^2 +
+m_{H_u}^2 + 2 m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2 \right )
++ \left ( \lambda a_{\kappa_i} + \kappa_i a_\lambda \right )^2 \right ]
+\nonumber \\
+& {} - 32 g_3^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 + 2 M_3^2
+\right ) - 32 g_3^2 \left ( a_t^2 - 2 y_t a_t M_3 \right ) \nonumber \\
+& {} - 18 g_2^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 + 2 M_2^2
+\right ) - 18 g_2^2 \left ( a_t^2 - 2 y_t a_t M_2 \right ) \nonumber \\
+& {} - 6 g_2^2 \lambda^2 \left ( m_{H_d}^2 + m_{H_u}^2 + m_S^2 + 2 M_2^2
+\right ) - 6 g_2^2 \left ( a_\lambda^2 - 2 \lambda a_\lambda M_2\right )
+\nonumber \\
+& {} - \frac{26}{5} g_1^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 +
+2 M_1^2 \right ) - \frac{26}{5} g_1^2 \left ( a_t^2 - 2 y_t a_t M_1 \right )
+\nonumber \\
+& {} - \frac{6}{5} g_1^2 \lambda^2 \left ( m_{H_d}^2 + m_{H_u}^2 + m_S^2 +
+2 M_1^2 \right ) - \frac{6}{5} g_1^2 \left ( a_\lambda^2 -
+2 \lambda a_\lambda M_1 \right ) \nonumber \\
+& {} - 12 g_1'^2 y_t^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right )
+\left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 + 2 M_1'^2 \right ) -
+12 g_1'^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \nonumber \\
+& {} \times \left ( a_t^2 - 2 y_t a_t M_1' \right ) +
+6 g_1'^2 y_t^2 \left ( Q_2 + Q_Q + Q_u \right )
+\left ( 2 Q_2 m_{H_u}^2 + 2 Q_2 m_{Q_3}^2 + 2 Q_2 m_{u_3}^2 + \Sigma_1'
+\right ) \nonumber \\
+& {} + 12 Q_2 g_1'^2 a_t^2 \left ( Q_2 + Q_Q + Q_u \right ) +
+12 Q_2 g_1'^2 y_b^2 \left ( Q_1 + Q_Q + Q_d \right ) \left ( m_{H_d}^2 +
+m_{Q_3}^2 + m_{d_3}^2 \right ) \nonumber \\
+& {} + 12 Q_2 g_1'^2 a_b^2 \left ( Q_1 + Q_Q + Q_d \right ) +
+4 Q_2 g_1'^2 y_\tau^2 \left ( Q_1 + Q_L + Q_e \right ) \left ( m_{H_d}^2 +
+m_{L_3}^2 + m_{e_3}^2 \right ) \nonumber \\
+& {} + 4 Q_2 g_1'^2 a_\tau^2 \left ( Q_1 + Q_L + Q_e \right ) -
+4 g_1'^2 \lambda^2 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) \left ( m_{H_d}^2 +
+m_{H_u}^2 + m_S^2 + 2 M_1'^2 \right ) \nonumber \\
+& {} - 4 g_1'^2 \left ( Q_1^2 + Q_2^2 + Q_S^2 \right ) \left ( a_\lambda^2 -
+2 \lambda a_\lambda M_1' \right ) + 2 g_1'^2 \lambda^2 \left ( Q_1 + Q_2 +
+Q_S \right ) \Sigma_1' \nonumber \\
+& {} + 4 Q_2 g_1'^2 \left ( Q_1 + Q_2 + Q_S \right ) \sum_{i=1}^3 \left [
+\lambda_i^2 \left ( m_{H_i^d}^2 + m_{H_i^u}^2 + m_S^2 \right ) +
+a_{\lambda_i}^2 \right ] \nonumber \\
+& {} + 6 Q_2 g_1'^2 \left ( Q_S + Q_D + Q_{\overline{D}} \right ) \sum_{i=1}^3
+\left [ \kappa_i^2 \left ( m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2 \right )
++ a_{\kappa_i}^2 \right ] \nonumber \\
+& {} - 96 Q_2 g_3^2 g_1'^2 M_3^2 \left ( 2 Q_Q + Q_u + Q_d + Q_D +
+Q_{\overline{D}} \right ) - 72 g_2^4 M_2^2 \nonumber \\
+& {} - 12 Q_2 g_2^2 g_1'^2 M_2^2 \left ( 9 Q_Q + 3 Q_L + 3 Q_1 + 3 Q_2 +
+Q_{\overline{H'}} + Q_{H'} \right ) + \frac{288}{25} g_1^4 \left ( \Sigma_1 -
+3 M_1^2 \right ) \nonumber \\
+& {} - \frac{3}{5} g_1^2 g_1'^2 \Big [ 4 Q_2 M_1^2 \big ( 2 Q_d +
+2 Q_{\overline{D}} + 2 Q_D + 6 Q_e + 3 Q_1 + 3 Q_2 + Q_{\overline{H'}} +
+Q_{H'} + 3 Q_L \nonumber \\
+& {} + Q_Q + 8 Q_u \big ) + 4 M_1'^2 \big ( 3 Q_d^2 + 3 Q_{\overline{D}}^2 -
+3 Q_D^2 + 3 Q_e^2 - 3 Q_1^2 + 3 Q_2^2 + Q_{\overline{H'}}^2 - Q_{H'}^2
+\nonumber \\
+& {} - 3 Q_L^2 + 3 Q_Q^2 - 6 Q_u^2 \big ) - \left ( 2 Q_2 \Sigma_1 + \Sigma_1'
+\right ) \Sigma_Q^Y \Big ] - 4 Q_2 g_1'^4 \Big [ 2 M_1'^2 \big ( 9 Q_d^3 +
+9 Q_{\overline{D}}^3 + 9 Q_D^3 \nonumber \\
+& {} + 3 Q_e^3 + 6 Q_1^3 + 6 Q_2^3 + 2 Q_{\overline{H'}}^3 + 2 Q_{H'}^3 +
+6 Q_L^3 + 18 Q_Q^3 + 3 Q_S^3 + 9 Q_u^3 \big ) \nonumber \\
+& {} + \left ( 6 Q_2 M_1'^2 - \Sigma_1' \right ) \Sigma_Q \Big ] ,
+\label{eq:USSMmHu2Ot2Coeff}
 \end{align}
@@
 \begin{align}
-\beta_{m_S^2}^{(1)}&=\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2+6\kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+6a_{\kappa_i}^2\right ]\nonumber\\
-&{}-8Q_S^2g_1'^2M_1'^2+2Q_Sg_1'^2\Sigma_1',\label{eq:USSMms2BetaOneLoop}\\
-\beta_{m_S^2}^{(2)}&=\sum_{i=1}^3\bigg [ -16\lambda_i^4\left ( m_{H_i^u}^2+m_{H_i^d}^2+m_S^2 \right )-24\kappa_i^4\left ( m_{D_i}^2+m_{\overline{D}_i}^2+m_S^2 \right )\nonumber\\
-&{}-32\lambda_i^2a_{\lambda_i}^2-48\kappa_i^2a_{\kappa_i}^2\bigg ]-12\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )\nonumber\\
-&{}-12\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{d_3}^2\right )\nonumber\\
-&{}-4\lambda^2y_\tau^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{L_3}^2+m_{e_3}^2\right )-12\left ( \lambda a_t+y_ta_\lambda\right )^2-12\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
-&{}-4\left ( \lambda a_\tau+y_\tau a_\lambda\right )^2+32g_3^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+2M_3^2\right )+a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_3 \right ]\nonumber\\
-&{}+12g_2^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_2^2\right )+a_{\lambda_i}^2-2\lambda_ia_{\lambda_i}M_2\right ]\nonumber\\
-&{}+\frac{4}{5}g_1^2\sum_{i=1}^3\bigg [ 3\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1^2\right )+2\kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+2M_1^2\right )\nonumber\\
-&{}+3\left (a_{\lambda_i}^2-2\lambda_ia_{\lambda_i}M_1\right )+2\left (a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_1\right )\bigg ]\nonumber\\
-&{}+4g_1'^2\sum_{i=1}^3\bigg [ 2\lambda_i^2\left ( Q_1^2+Q_2^2-Q_S^2\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1'^2\right )\nonumber\\
-&{}-2Q_S\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )+3\kappa_i^2\left ( Q_D^2+Q_{\overline{D}}^2-Q_S^2\right )\times\nonumber\\
-&{}\times\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+2M_1'^2\right )-3Q_S\kappa_i^2\left ( Q_Sm_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )\nonumber\\
-&{}+2\left ( a_{\lambda_i}^2-2\lambda_ia_{\lambda_i}M_1'\right )\left ( Q_1^2+Q_2^2-Q_S^2\right )+3\left ( a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_1'\right )\left ( Q_D^2+Q_{\overline{D}}^2-Q_S^2\right )\bigg ]\nonumber\\
-&{}-24Q_Sg_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q_3}^2+Q_um_{u_3}^2\right )-24Q_Sg_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q_3}^2+Q_dm_{d_3}^2\right )\nonumber\\
-&{}-8Q_Sg_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L_3}^2+Q_em_{e_3}^2\right )+32Q_Sg_3^2g_1'^2\sum_{i=1}^3\big ( 2Q_Qm_{Q_i}^2+Q_um_{u_i}^2\nonumber\\
-&{}+Q_dm_{d_i}^2+Q_Dm_{D_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2\big )+12Q_Sg_2^2g_1'^2\bigg [ Q_{\overline{H'}}m_{\overline{H'}}^2+Q_{H'}m_{H'}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Q_i}^2+Q_Lm_{L_i}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{4}{5}Q_Sg_1^2g_1'^2\bigg [ 3Q_{\overline{H'}}m_{\overline{H'}}^2+3Q_{H'}m_{H'}^2\nonumber\\
-&{}+\sum_{i=1}^3\big ( 2Q_dm_{d_i}^2+2Q_{\overline{D}}m_{\overline{D}_i}^2+2Q_Dm_{D_i}^2+6Q_em_{e_i}^2+3Q_1m_{H_i^d}^2+3Q_2m_{H_i^u}^2+3Q_Lm_{L_i}^2\nonumber\\
-&{}+Q_Qm_{Q_i}^2+8Q_um_{u_i}^2\big )\bigg ]+8Q_Sg_1'^4\bigg [ 3Q_SM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2+6Q_2^2\nonumber\\
-&{}+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2+18Q_Q^2+5Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2\nonumber\\
-&{}+\sum_{i=1}^3\big ( 3Q_d^3m_{d_i}^2+3Q_{\overline{D}}^3m_{\overline{D}_i}^2+3Q_D^3m_{D_i}^2+Q_e^3m_{e_i}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{L_i}^2\nonumber\\
-&{}+6Q_Q^3m_{Q_i}^2+Q_S^3m_{Si}^2+3Q_u^3m_{u_i}^2\big )+2Q_SQ_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_SQ_{H'}^2m_{H'}^2\nonumber\\
-&{}+Q_S\sum_{i=1}^3\big ( 3Q_d^2m_{d_i}^2+3Q_{\overline{D}}^2m_{\overline{D}_i}^2+3Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{L_i}^2\nonumber\\
-&{}+6Q_Q^2m_{Q_i}^2+Q_S^2m_{Si}^2+3Q_u^2m_{u_i}^2\big )\bigg ],\label{eq:USSMms2BetaTwoLoop}\\
-b_{m_S^2}^{(2)}&=8\sum_{i=1}^3\left [ 2\lambda_i^4\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4\lambda_i^2a_{\lambda_i}^2 +3\kappa_i^4\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+6\kappa_i^2a_{\kappa_i}^2\right ]\nonumber\\
-&{}+8\sum_{i=1}^3\sum_{j=1}^3\left [ \lambda_i^2\lambda_j^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_{H_j^d}^2+m_{H_j^u}^2+2m_S^2\right )+\left ( \lambda_i a_{\lambda_j}+\lambda_ja_{\lambda_i}\right )^2\right ]\nonumber\\
-&{}+24\sum_{i=1}^3\sum_{j=1}^3\left [ \lambda_i^2\kappa_j^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+2m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+\left ( \lambda_ia_{\kappa_j}+\kappa_ja_{\lambda_i}\right )^2\right ]\nonumber\\
-&{}+18\sum_{i=1}^3\sum_{j=1}^3\left [ \kappa_i^2\kappa_j^2\left ( 2m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+m_{D_j}^2+m_{\overline{D}_j}^2\right )+\left ( \kappa_ia_{\kappa_j}+\kappa_ja_{\kappa_i}\right )^2\right ]\nonumber\\
-&{}+12\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )+12\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2\right.\nonumber\\
-&{}\left.+m_{Q_3}^2+m_{d_3}^2\right )+4\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L_3}^2+m_{e_3}^2\right )+12\left ( \lambda a_t+y_ta_{\lambda}\right )^2\nonumber\\
-&{}+12\left ( \lambda a_b+y_ba_{\lambda}\right )^2+4\left ( \lambda a_\tau+y_\tau a_{\lambda}\right )^2-32g_3^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+2M_3^2\right )\right.\nonumber\\
-&{}\left.+a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_3\right ]-12g_2^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_2^2\right )+a_{\lambda_i}^2-2\lambda_i a_{\lambda_i}M_2\right ]\nonumber\\
-&{}-\frac{4}{5}g_1^2\sum_{i=1}^3\Big [ 3\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1^2\right )+3a_{\lambda_i}^2-6\lambda_i a_{\lambda_i}M_1\nonumber\\
-&{}+2\kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+2M_1^2\right )+2a_{\kappa_i}^2-4\kappa_i a_{\kappa_i}M_1\Big ]\nonumber\\
-&{}+2g_1'^2\sum_{i=1}^3\Big [ -4\lambda_i^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1'^2\right )\nonumber\\
-&{}+2\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( Q_Sm_{H_i^d}^2+Q_Sm_{H_i^u}^2+Q_Sm_S^2+\Sigma_1'\right )-4\left ( Q_1^2+Q_2^2+Q_S^2\right )\times\nonumber\\
-&{}\times\left ( a_{\lambda_i}^2-2\lambda_i a_{\lambda_i}M_1'\right )+2Q_Sa_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )-6\kappa_i^2\left ( Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\times\nonumber\\
-&{}\times\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2+2M_1'^2\right )+3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( Q_Sm_S^2+Q_Sm_{D_i}^2+Q_Sm_{\overline{D}_i}^2+\Sigma_1'\right )\nonumber\\
-&{}-6\left ( Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\left ( a_{\kappa_i}^2-2\kappa_i a_{\kappa_i}M_1'\right )+3Q_Sa_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\Big ]\nonumber\\
-&{}+12Q_Sg_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )+12Q_Sg_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )\nonumber\\
-&{}+12Q_Sg_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )+12Q_Sg_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )\nonumber\\
-&{}+4Q_Sg_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )+4Q_Sg_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
-&{}-96Q_Sg_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )-12Q_Sg_2^2g_1'^2M_2^2\big ( 9Q_Q+3Q_L+3Q_1\nonumber\\
-&{}+3Q_2+Q_{\overline{H'}}+Q_{H'}\big )-\frac{6}{5}Q_Sg_1^2g_1'^2\Big [ 2M_1^2\big ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}\nonumber\\
-&{}+Q_{H'}+3Q_L+Q_Q+8Q_u\big )-\Sigma_1\Sigma_Q^Y\Big ]-4Q_Sg_1'^4\Big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3\nonumber\\
-&{}+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )+\left ( 6Q_SM_1'^2-\Sigma_1'\right )\Sigma_Q\Big ].\label{eq:USSMms2Ot2Coeff}
+\beta_{m_S^2}^{(1)} &= \sum_{i=1}^3 \left [ 4 \lambda_i^2 \left ( m_{H_i^d}^2
++ m_{H_i^u}^2 + m_S^2 \right ) + 4 a_{\lambda_i}^2 + 6\kappa_i^2 \left ( m_S^2
++ m_{D_i}^2 + m_{\overline{D}_i}^2 \right ) + 6 a_{\kappa_i}^2 \right ]
+\nonumber \\
+& {} - 8 Q_S^2 g_1'^2 M_1'^2 + 2 Q_S g_1'^2 \Sigma_1' ,
+\label{eq:USSMms2BetaOneLoop} \\
+\beta_{m_S^2}^{(2)} &= \sum_{i=1}^3 \bigg [ -16 \lambda_i^4
+\left ( m_{H_i^u}^2 + m_{H_i^d}^2 + m_S^2 \right ) - 24 \kappa_i^4
+\left ( m_{D_i}^2 + m_{\overline{D}_i}^2 + m_S^2 \right ) \nonumber \\
+& {} - 32 \lambda_i^2 a_{\lambda_i}^2 - 48 \kappa_i^2 a_{\kappa_i}^2 \bigg ]
+- 12 \lambda^2 y_t^2 \left ( 2 m_{H_u}^2 + m_{H_d}^2 + m_S^2 + m_{Q_3}^2 +
+m_{u_3}^2 \right ) \nonumber \\
+& {} - 12 \lambda^2 y_b^2 \left ( m_{H_u}^2 + 2 m_{H_d}^2 + m_S^2 + m_{Q_3}^2
++ m_{d_3}^2 \right ) \nonumber \\
+& {} - 4 \lambda^2 y_\tau^2 \left ( m_{H_u}^2 + 2 m_{H_d}^2 + m_S^2 +
+m_{L_3}^2 + m_{e_3}^2 \right ) - 12 \left ( \lambda a_t + y_t a_\lambda
+\right )^2 - 12 \left ( \lambda a_b + y_b a_\lambda \right )^2 \nonumber \\
+& {} - 4 \left ( \lambda a_\tau + y_\tau a_\lambda \right )^2 +
+32 g_3^2 \sum_{i=1}^3 \left [ \kappa_i^2 \left ( m_S^2 + m_{D_i}^2 +
+m_{\overline{D}_i}^2 + 2 M_3^2 \right ) + a_{\kappa_i}^2 -
+2 \kappa_i a_{\kappa_i} M_3 \right ] \nonumber \\
+& {} + 12 g_2^2 \sum_{i=1}^3 \left [ \lambda_i^2 \left ( m_{H_i^d}^2 +
+m_{H_i^u}^2 + m_S^2 + 2 M_2^2 \right ) + a_{\lambda_i}^2 -
+2 \lambda_i a_{\lambda_i} M_2 \right ] \nonumber \\
+& {} + \frac{4}{5} g_1^2 \sum_{i=1}^3 \bigg [ 3 \lambda_i^2
+\left ( m_{H_i^d}^2 + m_{H_i^u}^2 + m_S^2 + 2 M_1^2 \right ) + 2 \kappa_i^2
+\left ( m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2 + 2 M_1^2 \right )
+\nonumber \\
+& {} + 3 \left ( a_{\lambda_i}^2 - 2 \lambda_i a_{\lambda_i} M_1 \right ) +
+2 \left ( a_{\kappa_i}^2 - 2 \kappa_i a_{\kappa_i} M_1 \right ) \bigg ]
+\nonumber \\
+& {} + 4 g_1'^2 \sum_{i=1}^3 \bigg [ 2 \lambda_i^2 \left ( Q_1^2 + Q_2^2 -
+Q_S^2 \right ) \left ( m_{H_i^d}^2 + m_{H_i^u}^2 + m_S^2 + 2 M_1'^2 \right )
+\nonumber \\
+& {} - 2 Q_S \lambda_i^2 \left ( Q_1 m_{H_i^d}^2 + Q_2 m_{H_i^u}^2 + Q_S m_S^2
+\right ) + 3 \kappa_i^2 \left ( Q_D^2 + Q_{\overline{D}}^2 - Q_S^2 \right )
+\nonumber \\
+& {} \times \left ( m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2 + 2 M_1'^2
+\right ) - 3 Q_S \kappa_i^2 \left ( Q_S m_S^2 + Q_D m_{D_i}^2 +
+Q_{\overline{D}} m_{\overline{D}_i}^2 \right ) \nonumber \\
+& {} + 2 \left ( a_{\lambda_i}^2 - 2 \lambda_i a_{\lambda_i} M_1' \right )
+\left ( Q_1^2 + Q_2^2 - Q_S^2 \right ) + 3 \left ( a_{\kappa_i}^2 -
+2 \kappa_i a_{\kappa_i} M_1' \right ) \left ( Q_D^2 + Q_{\overline{D}}^2 -
+Q_S^2 \right ) \bigg ] \nonumber \\
+& {} - 24 Q_S g_1'^2 y_t^2 \left ( Q_2 m_{H_u}^2 + Q_Q m_{Q_3}^2 +
+Q_u m_{u_3}^2 \right ) - 24 Q_S g_1'^2 y_b^2 \left ( Q_1 m_{H_d}^2 +
+Q_Q m_{Q_3}^2 + Q_d m_{d_3}^2 \right ) \nonumber \\
+& {} - 8 Q_S g_1'^2 y_\tau^2 \left ( Q_1 m_{H_d}^2 + Q_L m_{L_3}^2 +
+Q_e m_{e_3}^2 \right ) + 32 Q_S g_3^2 g_1'^2 \sum_{i=1}^3
+\big ( 2 Q_Q m_{Q_i}^2 + Q_u m_{u_i}^2 \nonumber \\
+& {} + Q_d m_{d_i}^2 + Q_D m_{D_i}^2 + Q_{\overline{D}} m_{\overline{D}_i}^2
+\big ) + 12 Q_S g_2^2 g_1'^2 \bigg [ Q_{\overline{H'}} m_{\overline{H'}}^2 +
+Q_{H'} m_{H'}^2 \nonumber \\
+& {} + \sum_{i=1}^3 \left ( 3 Q_Q m_{Q_i}^2 + Q_L m_{L_i}^2 + Q_1 m_{H_i^d}^2
++ Q_2 m_{H_i^u}^2 \right ) \bigg ] + \frac{4}{5} Q_S g_1^2 g_1'^2
+\bigg [ 3 Q_{\overline{H'}} m_{\overline{H'}}^2 + 3 Q_{H'} m_{H'}^2
+\nonumber \\
+& {} + \sum_{i=1}^3 \big ( 2 Q_d m_{d_i}^2 +
+2 Q_{\overline{D}} m_{\overline{D}_i}^2 + 2 Q_D m_{D_i}^2 + 6 Q_e m_{e_i}^2 +
+3 Q_1 m_{H_i^d}^2 + 3 Q_2 m_{H_i^u}^2 + 3 Q_L m_{L_i}^2 \nonumber \\
+& {} + Q_Q m_{Q_i}^2 + 8 Q_u m_{u_i}^2 \big ) \bigg ] + 8 Q_S g_1'^4 \bigg [
+3 Q_S M_1'^2 \big ( 9 Q_d^2 + 9 Q_{\overline{D}}^2 + 9 Q_D^2 + 3 Q_e^2 +
+6 Q_1^2 + 6 Q_2^2 \nonumber \\
+& {} + 2 Q_{\overline{H'}}^2 + 2 Q_{H'}^2 + 6 Q_L^2 + 18 Q_Q^2 + 5 Q_S^2 +
+9 Q_u^2 \big ) + 2 Q_{\overline{H'}}^3 m_{\overline{H'}}^2 +
+2 Q_{H'}^3 m_{H'}^2 \nonumber \\
+& {} + \sum_{i=1}^3 \big ( 3 Q_d^3 m_{d_i}^2 +
+3 Q_{\overline{D}}^3 m_{\overline{D}_i}^2 + 3 Q_D^3 m_{D_i}^2 +
+Q_e^3 m_{e_i}^2 + 2 Q_1^3 m_{H_i^d}^2 + 2 Q_2^3 m_{H_i^u}^2 +
+2 Q_L^3 m_{L_i}^2 \nonumber \\
+& {} + 6 Q_Q^3 m_{Q_i}^2 + Q_S^3 m_{S_i}^2 + 3 Q_u^3 m_{u_i}^2 \big ) +
+2 Q_S Q_{\overline{H'}}^2 m_{\overline{H'}}^2 + 2 Q_S Q_{H'}^2 m_{H'}^2
+\nonumber \\
+& {} + Q_S \sum_{i=1}^3 \big ( 3 Q_d^2 m_{d_i}^2 +
+3 Q_{\overline{D}}^2 m_{\overline{D}_i}^2 + 3 Q_D^2 m_{D_i}^2 +
+Q_e^2 m_{e_i}^2 + 2 Q_1^2 m_{H_i^d}^2 + 2 Q_2^2 m_{H_i^u}^2 +
+2 Q_L^2 m_{L_i}^2 \nonumber \\
+& {} + 6 Q_Q^2 m_{Q_i}^2 + Q_S^2 m_{S_i}^2 + 3 Q_u^2 m_{u_i}^2 \big ) \bigg ]
+, \label{eq:USSMms2BetaTwoLoop} \\
+b_{m_S^2}^{(2)} &= 8 \sum_{i=1}^3 \left [ 2 \lambda_i^4 \left ( m_{H_i^d}^2 +
+m_{H_i^u}^2 + m_S^2 \right ) + 4 \lambda_i^2 a_{\lambda_i}^2 + 3 \kappa_i^4
+\left ( m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2 \right ) +
+6 \kappa_i^2 a_{\kappa_i}^2 \right ] \nonumber \\
+& {} + 8 \sum_{i=1}^3 \sum_{j=1}^3 \left [ \lambda_i^2 \lambda_j^2
+\left ( m_{H_i^d}^2 + m_{H_i^u}^2 + m_{H_j^d}^2 + m_{H_j^u}^2 + 2 m_S^2
+\right ) + \left ( \lambda_i a_{\lambda_j} + \lambda_j a_{\lambda_i}
+\right )^2 \right ] \nonumber \\
+& {} + 24 \sum_{i=1}^3 \sum_{j=1}^3 \left [ \lambda_i^2 \kappa_j^2
+\left ( m_{H_i^d}^2 + m_{H_i^u}^2 + 2 m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2
+\right ) + \left ( \lambda_i a_{\kappa_j} + \kappa_j a_{\lambda_i} \right )^2
+\right ] \nonumber \\
+& {} + 18 \sum_{i=1}^3 \sum_{j=1}^3 \left [ \kappa_i^2 \kappa_j^2
+\left ( 2 m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2 + m_{D_j}^2 +
+m_{\overline{D}_j}^2 \right ) + \left ( \kappa_i a_{\kappa_j} +
+\kappa_j a_{\kappa_i} \right )^2 \right ] \nonumber \\
+& {} + 12 \lambda^2 y_t^2 \left ( 2 m_{H_u}^2 + m_{H_d}^2 + m_S^2 + m_{Q_3}^2
++ m_{u_3}^2 \right ) + 12 \lambda^2 y_b^2 \left ( m_{H_u}^2 + 2 m_{H_d}^2 +
+m_S^2 \right . \nonumber \\
+& {} \left . + m_{Q_3}^2 + m_{d_3}^2 \right ) + 4 \lambda^2 y_\tau^2
+\left ( 2 m_{H_d}^2 + m_{H_u}^2 + m_S^2 + m_{L_3}^2 + m_{e_3}^2 \right ) +
+12 \left ( \lambda a_t + y_t a_{\lambda} \right )^2 \nonumber \\
+& {} + 12 \left ( \lambda a_b + y_b a_{\lambda} \right )^2 +
+4 \left ( \lambda a_\tau + y_\tau a_{\lambda} \right )^2 -
+32 g_3^2 \sum_{i=1}^3 \left [ \kappa_i^2 \left ( m_S^2 + m_{D_i}^2 +
+m_{\overline{D}_i}^2 + 2 M_3^2 \right ) \right . \nonumber \\
+& {} \left . + a_{\kappa_i}^2 - 2 \kappa_i a_{\kappa_i} M_3 \right ] -
+12 g_2^2 \sum_{i=1}^3 \left [ \lambda_i^2 \left ( m_{H_i^d}^2 + m_{H_i^u}^2 +
+m_S^2 + 2 M_2^2 \right ) + a_{\lambda_i}^2 - 2 \lambda_i a_{\lambda_i} M_2
+\right ] \nonumber \\
+& {} - \frac{4}{5} g_1^2 \sum_{i=1}^3 \Big [ 3 \lambda_i^2 \left ( m_{H_i^d}^2
++ m_{H_i^u}^2 + m_S^2 + 2 M_1^2 \right ) + 3 a_{\lambda_i}^2 -
+6 \lambda_i a_{\lambda_i} M_1 \nonumber \\
+& {} + 2 \kappa_i^2 \left ( m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2 +
+2 M_1^2 \right ) + 2 a_{\kappa_i}^2 - 4 \kappa_i a_{\kappa_i} M_1 \Big ]
+\nonumber \\
+& {} + 2 g_1'^2 \sum_{i=1}^3 \Big [ -4 \lambda_i^2 \left ( Q_1^2 + Q_2^2 +
+Q_S^2 \right ) \left ( m_{H_i^d}^2 + m_{H_i^u}^2 + m_S^2 + 2 M_1'^2 \right )
+\nonumber \\
+& {} + 2 \lambda_i^2 \left ( Q_1 + Q_2 + Q_S \right ) \left ( Q_S m_{H_i^d}^2
++ Q_S m_{H_i^u}^2 + Q_S m_S^2 + \Sigma_1' \right ) - 4 \left ( Q_1^2 + Q_2^2
++ Q_S^2 \right ) \nonumber \\
+& {} \times \left ( a_{\lambda_i}^2 - 2 \lambda_i a_{\lambda_i} M_1' \right )
++ 2 Q_S a_{\lambda_i}^2 \left ( Q_1 + Q_2 + Q_S \right ) -
+6 \kappa_i^2 \left ( Q_S^2 + Q_D^2 + Q_{\overline{D}}^2 \right ) \nonumber \\
+& {} \times \left ( m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2 + 2 M_1'^2
+\right ) + 3 \kappa_i^2 \left ( Q_S + Q_D + Q_{\overline{D}} \right )
+\left ( Q_S m_S^2 + Q_S m_{D_i}^2 + Q_S m_{\overline{D}_i}^2 + \Sigma_1'
+\right ) \nonumber \\
+& {} - 6 \left ( Q_S^2 + Q_D^2 + Q_{\overline{D}}^2 \right )
+\left ( a_{\kappa_i}^2 - 2 \kappa_i a_{\kappa_i} M_1' \right ) +
+3 Q_S a_{\kappa_i}^2 \left ( Q_S + Q_D + Q_{\overline{D}} \right ) \Big ]
+\nonumber \\
+& {} + 12 Q_S g_1'^2 y_t^2 \left ( Q_2 + Q_Q + Q_u \right )
+\left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 \right ) + 12 Q_S g_1'^2 a_t^2
+\left ( Q_2 + Q_Q + Q_u \right ) \nonumber \\
+& {} + 12 Q_S g_1'^2 y_b^2 \left ( Q_1 + Q_Q + Q_d \right )
+\left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 \right ) + 12 Q_S g_1'^2 a_b^2
+\left ( Q_1 + Q_Q + Q_d \right ) \nonumber \\
+& {} + 4 Q_S g_1'^2 y_\tau^2 \left ( Q_1 + Q_L + Q_e \right )
+\left ( m_{H_d}^2 + m_{L_3}^2 + m_{e_3}^2 \right ) + 4 Q_S g_1'^2 a_\tau^2
+\left ( Q_1 + Q_L + Q_e \right ) \nonumber \\
+& {} - 96 Q_S g_3^2 g_1'^2 M_3^2 \left ( 2 Q_Q + Q_u + Q_d + Q_D +
+Q_{\overline{D}} \right ) - 12 Q_S g_2^2 g_1'^2 M_2^2 \big ( 9 Q_Q + 3 Q_L +
+3 Q_1 \nonumber \\
+& {} + 3 Q_2 + Q_{\overline{H'}} + Q_{H'} \big ) -
+\frac{6}{5} Q_S g_1^2 g_1'^2 \Big [ 2 M_1^2 \big ( 2 Q_d + 2 Q_{\overline{D}}
++ 2 Q_D + 6 Q_e + 3 Q_1 + 3 Q_2 + Q_{\overline{H'}} \nonumber \\
+& {} + Q_{H'} + 3 Q_L + Q_Q + 8 Q_u \big ) - \Sigma_1 \Sigma_Q^Y \Big ] -
+4 Q_S g_1'^4 \Big [ 2 M_1'^2 \big ( 9 Q_d^3 + 9 Q_{\overline{D}}^3 + 9 Q_D^3 +
+3 Q_e^3 + 6 Q_1^3 \nonumber \\
+& {} + 6 Q_2^3 + 2 Q_{\overline{H'}}^3 + 2 Q_{H'}^3 + 6 Q_L^3 + 18 Q_Q^3 +
+3 Q_S^3 + 9 Q_u^3 \big ) + \left ( 6 Q_S M_1'^2 - \Sigma_1' \right ) \Sigma_Q
+\Big ] . \label{eq:USSMms2Ot2Coeff}
 \end{align}
 \end{subequations}
-If the one-loop contributions to the effective potential from top and stop loops are also included it is necessary to consider the expansions for $y_t$, $a_t$, $m_{Q_3}^2$ and $m_{u_3}^2$.
-The required expressions for $y_t$ read
+If the one-loop contributions to the effective potential from top and stop
+loops are also included it is necessary to consider the expansions for $y_t$,
+$a_t$, $m_{Q_3}^2$ and $m_{u_3}^2$. The required expressions for $y_t$ read
 \begin{subequations}
 \begin{align}
-\beta_{y_t}^{(1)}&=y_t\left [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2-2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\right ],\label{eq:USSMYu22BetaOneLoop}\\
-\beta_{y_t}^{(2)}&=y_t\bigg \{-22y_t^4-5y_b^4-5y_t^2y_b^2-y_b^2y_\tau^2-\lambda^2 \left ( \lambda^2+3y_t^2+4y_b^2+y_\tau^2+2\Sigma_\lambda + 3\Sigma_\kappa\right )\nonumber\\
-&{}+2g_1'^2\left [ \lambda^2\left ( Q_1^2-Q_2^2+Q_S^2 \right )+2y_t^2\left ( 2Q_Q^2+Q_u^2\right )+y_b^2\left ( Q_1^2-Q_Q^2+Q_d^2\right )\right ]\nonumber\\
-&{}+16g_3^2y_t^2+6g_2^2y_t^2+g_1^2\left ( \frac{6}{5}y_t^2+\frac{2}{5}y_b^2\right )+\frac{128}{9}g_3^4+\frac{33}{2}g_2^4+\frac{3913}{450}g_1^4\nonumber\\
-&{}+2g_1'^4\left [ 2\left ( Q_2^4+Q_Q^4+Q_u^4\right )+\left ( Q_2^2+Q_Q^2+Q_u^2\right )\Sigma_{Q}\right ]+8g_3^2g_2^2+\frac{136}{45}g_3^2g_1^2\nonumber\\
-&{}+\frac{32}{3}g_3^2g_1'^2\left ( Q_Q^2+Q_u^2\right )+g_2^2g_1^2+6g_2^2g_1'^2\left ( Q_2^2+Q_Q^2\right )\nonumber\\
-&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2+\left ( 3Q_2+Q_Q-4Q_u\right )\Sigma_Q^Y\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\
-b_{y_t}^{(2)}&=y_t\bigg \{ 54y_t^4+\frac{13}{2}y_b^4+13y_t^2y_b^2+y_b^2y_\tau^2+\lambda^2\left ( \frac{5}{2}\lambda^2+15y_t^2+5y_b^2+y_\tau^2+2\Sigma_\lambda+3\Sigma_\kappa \right )\nonumber\\
-&{}-\frac{16}{3}g_3^2\left ( \lambda^2+2y_b^2+12y_t^2\right )-6g_2^2\left ( \lambda^2+y_b^2+6y_t^2\right )-g_1^2\left ( \frac{22}{15}\lambda^2+\frac{4}{3}y_b^2+\frac{52}{5}y_t^2\right )\nonumber\\
-&{}-2g_1'^2\left [ \lambda^2 \left (Q_1^2+2Q_2^2+Q_S^2+Q_Q^2+Q_u^2 \right )+y_b^2\left ( Q_1^2+Q_2^2+2Q_Q^2+Q_u^2+Q_d^2\right )\right.\nonumber\\
-&{}\left.+12y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\right ]+\frac{128}{9}g_3^4-\frac{15}{2}g_2^4-\frac{143}{18}g_1^4\nonumber\\
-&{}+2g_1'^4\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( Q_2^2+Q_Q^2+Q_u^2-\Sigma_{Q}\right )+16g_3^2g_2^2+\frac{208}{45}g_3^2g_1^2\nonumber\\
-&{}+\frac{32}{3}g_3^2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )+\frac{13}{5}g_2^2g_1^2+6g_2^2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\nonumber\\
-&{}+\frac{26}{15}g_1^2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg \},\label{eq:USSMYu22Ot2Coeff}
+\beta_{y_t}^{(1)} &= y_t \left [ \lambda^2 + 6 y_t^2 + y_b^2 -
+\frac{16}{3} g_3^2 - 3 g_2^2 - \frac{13}{15} g_1^2 - 2 g_1'^2 \left ( Q_2^2 +
+Q_Q^2 + Q_u^2 \right ) \right ] , \label{eq:USSMYu22BetaOneLoop} \\
+\beta_{y_t}^{(2)} &= y_t \bigg \{ -22 y_t^4 - 5 y_b^4 - 5 y_t^2 y_b^2 -
+y_b^2 y_\tau^2 - \lambda^2 \left ( \lambda^2 + 3 y_t^2 + 4 y_b^2 + y_\tau^2 +
+2 \Sigma_\lambda + 3 \Sigma_\kappa \right ) \nonumber \\
+& {} + 2 g_1'^2 \left [ \lambda^2 \left ( Q_1^2 - Q_2^2 + Q_S^2 \right ) +
+2 y_t^2 \left ( 2 Q_Q^2 + Q_u^2 \right ) + y_b^2 \left ( Q_1^2 - Q_Q^2 +
+Q_d^2 \right ) \right ] \nonumber \\
+& {} + 16 g_3^2 y_t^2 + 6 g_2^2 y_t^2 + g_1^2 \left ( \frac{6}{5} y_t^2 +
+\frac{2}{5} y_b^2 \right ) + \frac{128}{9} g_3^4 + \frac{33}{2} g_2^4 +
+\frac{3913}{450} g_1^4 \nonumber \\
+& {} + 2 g_1'^4 \left [ 2 \left ( Q_2^4 + Q_Q^4 + Q_u^4 \right ) +
+\left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \Sigma_{Q} \right ] + 8 g_3^2 g_2^2 +
+\frac{136}{45} g_3^2 g_1^2 \nonumber \\
+& {} + \frac{32}{3} g_3^2 g_1'^2 \left ( Q_Q^2 + Q_u^2 \right ) + g_2^2 g_1^2
++ 6 g_2^2 g_1'^2 \left ( Q_2^2 + Q_Q^2 \right ) \nonumber \\
+& {} + \frac{2}{5} g_1^2 g_1'^2 \left [ 3 Q_2^2 + \frac{1}{3} Q_Q^2 +
+\frac{16}{3} Q_u^2 + \left ( 3 Q_2 + Q_Q - 4 Q_u \right ) \Sigma_Q^Y \right ]
+\bigg \} , \label{eq:USSMYu22BetaTwoLoop} \\
+b_{y_t}^{(2)} &= y_t \bigg \{ 54 y_t^4 + \frac{13}{2} y_b^4 + 13 y_t^2 y_b^2
++ y_b^2 y_\tau^2 + \lambda^2 \left ( \frac{5}{2} \lambda^2 + 15 y_t^2 +
+5 y_b^2 + y_\tau^2 + 2 \Sigma_\lambda + 3 \Sigma_\kappa \right ) \nonumber \\
+& {} - \frac{16}{3} g_3^2 \left ( \lambda^2 + 2 y_b^2 + 12 y_t^2 \right ) -
+6 g_2^2 \left ( \lambda^2 + y_b^2 + 6 y_t^2 \right ) -
+g_1^2 \left ( \frac{22}{15} \lambda^2 + \frac{4}{3} y_b^2 + \frac{52}{5} y_t^2
+\right ) \nonumber \\
+& {} - 2 g_1'^2 \left [ \lambda^2 \left ( Q_1^2 + 2 Q_2^2 + Q_S^2 + Q_Q^2 +
+Q_u^2 \right ) + y_b^2 \left ( Q_1^2 + Q_2^2 + 2 Q_Q^2 + Q_u^2 + Q_d^2
+\right ) \right . \nonumber \\
+& {} \left . + 12 y_t^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \right ] +
+\frac{128}{9} g_3^4 - \frac{15}{2} g_2^4 - \frac{143}{18} g_1^4 \nonumber \\
+& {} + 2 g_1'^4 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \left ( Q_2^2 + Q_Q^2
++ Q_u^2 - \Sigma_{Q} \right ) + 16 g_3^2 g_2^2 + \frac{208}{45} g_3^2 g_1^2
+\nonumber \\
+& {} + \frac{32}{3} g_3^2 g_1'^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) +
+\frac{13}{5} g_2^2 g_1^2 + 6 g_2^2 g_1'^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2
+\right ) \nonumber \\
+& {} + \frac{26}{15} g_1^2 g_1'^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right )
+\bigg \} , \label{eq:USSMYu22Ot2Coeff}
 \end{align}
@@
 \begin{align}
-\beta_{a_t}^{(1)}&=a_t\left [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2-2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\right ]\nonumber\\
-&{}+y_t\bigg [ 2\lambda a_\lambda + 12y_ta_t+2y_ba_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1\nonumber\\
-&{}+4g_1'^2M_1'\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg ],\label{eq:USSMTYu22BetaOneLoop}\\
-\beta_{a_t}^{(2)}&=a_t\bigg \{-22y_t^4-5y_b^4-5y_t^2y_b^2-y_b^2y_\tau^2-\lambda^2 \left ( \lambda^2+3y_t^2+4y_b^2+y_\tau^2+2\Sigma_\lambda + 3\Sigma_\kappa\right )\nonumber\\
-&{}+2g_1'^2\left [ \lambda^2\left ( Q_1^2-Q_2^2+Q_S^2 \right )+2y_t^2\left ( 2Q_Q^2+Q_u^2\right )+y_b^2\left ( Q_1^2-Q_Q^2+Q_d^2\right )\right ]\nonumber\\
-&{}+16g_3^2y_t^2+6g_2^2y_t^2+g_1^2\left ( \frac{6}{5}y_t^2+\frac{2}{5}y_b^2\right )+\frac{128}{9}g_3^4+\frac{33}{2}g_2^4+\frac{3913}{450}g_1^4\nonumber\\
-&{}+2g_1'^4\left [ 2\left ( Q_2^4+Q_Q^4+Q_u^4\right )+\left ( Q_2^2+Q_Q^2+Q_u^2\right )\Sigma_{Q}\right ]+8g_3^2g_2^2+\frac{136}{45}g_3^2g_1^2\nonumber\\
-&{}+\frac{32}{3}g_3^2g_1'^2\left ( Q_Q^2+Q_u^2\right )+g_2^2g_1^2+6g_2^2g_1'^2\left ( Q_2^2+Q_Q^2\right )\nonumber\\
-&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2\right ]\bigg \}+y_t\bigg \{ -88y_t^3a_t-20y_b^3a_b-10y_ty_b\left ( y_ba_t+y_ta_b\right )\nonumber\\
-&{}-2y_by_\tau\left ( y_b a_\tau+y_\tau a_b\right )-2\lambda a_\lambda \left ( 2\lambda^2+3y_t^2+4y_b^2+y_\tau^2+2\Sigma_\lambda+3\Sigma_\kappa\right )\nonumber\\
-&{}-2\lambda^2\left ( 3y_t a_t+4y_b a_b+y_\tau a_\tau +2\Sigma_{a_\lambda}+3\Sigma_{a_\kappa}\right )+32g_3^2y_t\left ( a_t-y_tM_3\right )\nonumber\\
-&{}+12g_2^2y_t\left ( a_t-y_tM_2\right )+\frac{2}{5}g_1^2\left [ 6y_ta_t+2y_ba_b-\left ( 6y_t^2+2y_b^2\right )M_1\right ]\nonumber\\
-&{}+4g_1'^2\big [ \lambda\left (Q_1^2-Q_2^2+Q_S^2\right ) \left ( a_\lambda-\lambda M_1'\right )+2y_t\left ( 2Q_Q^2+Q_u^2\right )\left ( a_t-y_tM_1'\right )\nonumber\\
-&{}+y_b\left ( Q_1^2-Q_Q^2+Q_d^2\right )\left ( a_b-y_bM_1'\right )\big ]-\frac{512}{9}g_3^4M_3-66g_2^4M_2-\frac{7826}{225}g_1^4M_1\nonumber\\
-&{}-8g_1'^4M_1'\left [ 2\left ( Q_2^4+Q_Q^4+Q_u^4\right )+\left ( Q_2^2+Q_Q^2+Q_u^2\right )\Sigma_{Q}\right ]-16g_3^2g_2^2\left ( M_3+M_2\right )\nonumber\\
-&{}-\frac{272}{45}g_3^2g_1^2\left ( M_3+M_1\right )-\frac{64}{3}g_3^2g_1'^2\left ( Q_Q^2+Q_u^2\right )\left ( M_3+M_1'\right )-2g_2^2g_1^2\left ( M_2+M_1\right )\nonumber\\
-&{}-12g_2^2g_1'^2\left ( Q_2^2+Q_Q^2\right )\left ( M_2+M_1'\right )-\frac{4}{15}g_1^2g_1'^2\left ( 9Q_2^2+Q_Q^2+16Q_u^2\right )\left ( M_1+M_1'\right )\bigg \},\label{eq:USSMTYu22BetaTwoLoop}\\
-b_{a_t}^{(2)}&=y_t\bigg [ 2\lambda a_\lambda + 12y_ta_t+2y_ba_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1\nonumber\\
-&{}+4g_1'^2M_1'\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg ]\times\bigg [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2\nonumber\\
-&{}-2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg ]+a_t\bigg \{ 54y_t^4+\frac{13}{2}y_b^4+13y_t^2y_b^2+y_b^2y_\tau^2\nonumber\\
-&{}+\lambda^2\left ( \frac{5}{2}\lambda^2+15y_t^2+5y_b^2+y_\tau^2+2\Sigma_\lambda+3\Sigma_\kappa \right )-\frac{16}{3}g_3^2\left ( \lambda^2+2y_b^2+12y_t^2\right )\nonumber\\
-&{}-6g_2^2\left ( \lambda^2+y_b^2+6y_t^2\right )-g_1^2\left ( \frac{22}{15}\lambda^2+\frac{4}{3}y_b^2+\frac{52}{5}y_t^2\right )\nonumber\\
-&{}-2g_1'^2\left [ \lambda^2 \left (Q_1^2+2Q_2^2+Q_S^2+Q_Q^2+Q_u^2 \right )+y_b^2\left ( Q_1^2+Q_2^2+2Q_Q^2+Q_u^2+Q_d^2\right )\right.\nonumber\\
-&{}\left.+12y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\right ]+\frac{128}{9}g_3^4-\frac{15}{2}g_2^4-\frac{143}{18}g_1^4\nonumber\\
-&{}+2g_1'^4\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( Q_2^2+Q_Q^2+Q_u^2-\Sigma_{Q}\right )+16g_3^2g_2^2+\frac{208}{45}g_3^2g_1^2\nonumber\\
-&{}+\frac{32}{3}g_3^2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )+\frac{13}{5}g_2^2g_1^2+6g_2^2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\nonumber\\
-&{}+\frac{26}{15}g_1^2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg \}+y_t\bigg [ 144y_t^3a_t+24y_b^3a_b+14y_ty_b\left ( y_ta_b+a_ty_b\right )\nonumber\\
-&{}+2y_by_\tau\left ( y_b a_\tau+a_by_\tau\right )+18\lambda y_t\left ( \lambda a_t+a_{\lambda}y_t\right )+8\lambda y_b\left ( \lambda a_b+a_{\lambda}y_b\right )+2\lambda y_\tau\left ( \lambda a_\tau+a_{\lambda}y_\tau\right )\nonumber\\
-&{}+8\lambda^3a_{\lambda}+4\lambda\sum_{i=1}^3\lambda_i\left ( \lambda a_{\lambda_i}+a_{\lambda}\lambda_i\right )+6\lambda\sum_{i=1}^3\kappa_i\left ( \lambda a_{\kappa_i}+a_{\lambda}\kappa_i\right )-64g_3^2y_t\left ( a_t-y_tM_3\right )\nonumber\\
-&{}-\frac{32}{3}g_3^2y_b\left ( a_b-y_bM_3\right )-36g_2^2y_t\left ( a_t-y_tM_2\right )-6g_2^2y_b\left ( a_b-y_bM_2\right )-6g_2^2\lambda\left ( a_\lambda-\lambda M_2\right )\nonumber\\
-&{}-\frac{52}{5}g_1^2y_t\left ( a_t-y_tM_1\right )-\frac{14}{15}g_1^2y_b\left ( a_b-y_bM_1\right )-\frac{18}{15}g_1^2\lambda \left ( a_\lambda-\lambda M_1\right )\nonumber\\
-&{}-24g_1'^2y_t\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( a_t-y_tM_1'\right )-4g_1'^2y_b\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( a_b-y_bM_1'\right )\nonumber\\
-&{}-4g_1'^2\lambda \left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( a_\lambda-\lambda M_1'\right )+48g_2^4M_2+\frac{832}{25}g_1^4M_1\nonumber\\
-&{}+8g_1'^4M_1'\Sigma_Q\left ( Q_2^2+Q_Q^2+Q_u^2\right )\bigg ].\label{eq:USSMTYu22Ot2Coeff}
+\beta_{a_t}^{(1)} &= a_t \left [ \lambda^2 + 6 y_t^2 + y_b^2 -
+\frac{16}{3} g_3^2 - 3 g_2^2 - \frac{13}{15} g_1^2 - 2 g_1'^2 \left ( Q_2^2 +
+Q_Q^2 + Q_u^2 \right ) \right ] \nonumber \\
+& {} + y_t \bigg [ 2 \lambda a_\lambda + 12 y_t a_t + 2 y_b a_b +
+\frac{32}{3} g_3^2 M_3 + 6 g_2^2 M_2 + \frac{26}{15} g_1^2 M_1 \nonumber \\
+& {} + 4 g_1'^2 M_1' \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \bigg ] ,
+\label{eq:USSMTYu22BetaOneLoop} \\
+\beta_{a_t}^{(2)} &= a_t \bigg \{ -22 y_t^4 - 5 y_b^4 - 5 y_t^2 y_b^2 -
+y_b^2 y_\tau^2 - \lambda^2 \left ( \lambda^2 + 3 y_t^2 + 4 y_b^2 + y_\tau^2 +
+2 \Sigma_\lambda + 3 \Sigma_\kappa \right ) \nonumber \\
+& {} + 2 g_1'^2 \left [ \lambda^2 \left ( Q_1^2 - Q_2^2 + Q_S^2 \right ) +
+2 y_t^2 \left ( 2 Q_Q^2 + Q_u^2 \right ) + y_b^2 \left ( Q_1^2 - Q_Q^2 +
+Q_d^2 \right ) \right ] \nonumber \\
+& {} + 16 g_3^2 y_t^2 + 6 g_2^2 y_t^2 + g_1^2 \left ( \frac{6}{5} y_t^2 +
+\frac{2}{5} y_b^2 \right ) + \frac{128}{9} g_3^4 + \frac{33}{2} g_2^4 +
+\frac{3913}{450} g_1^4 \nonumber \\
+& {} + 2 g_1'^4 \left [ 2 \left ( Q_2^4 + Q_Q^4 + Q_u^4 \right ) +
+\left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \Sigma_{Q} \right ] + 8 g_3^2 g_2^2 +
+\frac{136}{45} g_3^2 g_1^2 \nonumber \\
+& {} + \frac{32}{3} g_3^2 g_1'^2 \left ( Q_Q^2 + Q_u^2 \right ) + g_2^2 g_1^2
++ 6 g_2^2 g_1'^2 \left ( Q_2^2 + Q_Q^2 \right ) \nonumber \\
+& {} + \frac{2}{5} g_1^2 g_1'^2 \left [ 3 Q_2^2 + \frac{1}{3} Q_Q^2 +
+\frac{16}{3} Q_u^2 \right ] \bigg \} + y_t \bigg \{ -88 y_t^3 a_t -
+20 y_b^3 a_b - 10 y_t y_b \left ( y_b a_t + y_t a_b \right ) \nonumber \\
+& {} - 2 y_b y_\tau \left ( y_b a_\tau + y_\tau a_b \right ) -
+2 \lambda a_\lambda \left ( 2 \lambda^2 + 3 y_t^2 + 4 y_b^2 + y_\tau^2 +
+2 \Sigma_\lambda + 3 \Sigma_\kappa \right ) \nonumber \\
+& {} - 2 \lambda^2 \left ( 3 y_t a_t + 4 y_b a_b + y_\tau a_\tau +
+2 \Sigma_{a_\lambda} + 3 \Sigma_{a_\kappa} \right ) +
+32 g_3^2 y_t \left ( a_t - y_t M_3 \right ) \nonumber \\
+& {} + 12 g_2^2 y_t \left ( a_t - y_t M_2 \right ) + \frac{2}{5} g_1^2 \left [
+6 y_t a_t + 2 y_b a_b - \left ( 6 y_t^2 + 2 y_b^2 \right ) M_1 \right ]
+\nonumber \\
+& {} + 4 g_1'^2 \big [ \lambda \left ( Q_1^2 - Q_2^2 + Q_S^2 \right )
+\left ( a_\lambda - \lambda M_1' \right ) + 2 y_t \left ( 2 Q_Q^2 + Q_u^2
+\right ) \left ( a_t - y_t M_1' \right ) \nonumber \\
+& {} + y_b \left ( Q_1^2 - Q_Q^2 + Q_d^2 \right ) \left ( a_b - y_b M_1'
+\right ) \big ] - \frac{512}{9} g_3^4 M_3 - 66 g_2^4 M_2 -
+\frac{7826}{225} g_1^4 M_1 \nonumber \\
+& {} - 8 g_1'^4 M_1' \left [ 2 \left ( Q_2^4 + Q_Q^4 + Q_u^4 \right ) +
+\left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \Sigma_{Q} \right ] -
+16 g_3^2 g_2^2 \left ( M_3 + M_2 \right ) \nonumber \\
+& {} - \frac{272}{45} g_3^2 g_1^2 \left ( M_3 + M_1 \right ) -
+\frac{64}{3} g_3^2 g_1'^2 \left ( Q_Q^2 + Q_u^2 \right )
+\left ( M_3 + M_1' \right ) - 2 g_2^2 g_1^2 \left ( M_2 + M_1 \right )
+\nonumber \\
+& {} - 12 g_2^2 g_1'^2 \left ( Q_2^2 + Q_Q^2 \right ) \left ( M_2 + M_1'
+\right ) - \frac{4}{15} g_1^2 g_1'^2 \left ( 9 Q_2^2 + Q_Q^2 + 16 Q_u^2
+\right ) \left ( M_1 + M_1' \right ) \bigg \} ,
+\label{eq:USSMTYu22BetaTwoLoop} \\
+b_{a_t}^{(2)} &= y_t \bigg [ 2 \lambda a_\lambda + 12 y_t a_t + 2 y_b a_b +
+\frac{32}{3} g_3^2 M_3 + 6 g_2^2 M_2 + \frac{26}{15} g_1^2 M_1 \nonumber \\
+& {} + 4 g_1'^2 M_1' \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \bigg ] \times
+\bigg [ \lambda^2 + 6 y_t^2 + y_b^2 - \frac{16}{3} g_3^2 - 3 g_2^2 -
+\frac{13}{15} g_1^2 \nonumber \\
+& {} - 2 g_1'^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \bigg ] +
+a_t \bigg \{ 54 y_t^4 + \frac{13}{2} y_b^4 + 13 y_t^2 y_b^2 + y_b^2 y_\tau^2
+\nonumber \\
+& {} + \lambda^2 \left ( \frac{5}{2} \lambda^2 + 15 y_t^2 + 5 y_b^2 + y_\tau^2
++ 2 \Sigma_\lambda + 3 \Sigma_\kappa \right ) -
+\frac{16}{3} g_3^2 \left ( \lambda^2 + 2 y_b^2 + 12 y_t^2 \right ) \nonumber \\
+& {} - 6 g_2^2 \left ( \lambda^2 + y_b^2 + 6 y_t^2 \right ) - g_1^2 \left (
+\frac{22}{15} \lambda^2 + \frac{4}{3} y_b^2 + \frac{52}{5} y_t^2 \right )
+\nonumber \\
+& {} - 2 g_1'^2 \left [ \lambda^2 \left ( Q_1^2 + 2 Q_2^2 + Q_S^2 + Q_Q^2 +
+Q_u^2 \right ) + y_b^2 \left ( Q_1^2 + Q_2^2 + 2 Q_Q^2 + Q_u^2 + Q_d^2
+\right ) \right . \nonumber \\
+& {} \left . + 12 y_t^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \right ] +
+\frac{128}{9} g_3^4 - \frac{15}{2} g_2^4 - \frac{143}{18} g_1^4 \nonumber \\
+& {} + 2 g_1'^4 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \left ( Q_2^2 + Q_Q^2
++ Q_u^2 - \Sigma_{Q} \right ) + 16 g_3^2 g_2^2 + \frac{208}{45} g_3^2 g_1^2
+\nonumber \\
+& {} + \frac{32}{3} g_3^2 g_1'^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) +
+\frac{13}{5} g_2^2 g_1^2 + 6 g_2^2 g_1'^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2
+\right ) \nonumber \\
+& {} + \frac{26}{15} g_1^2 g_1'^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right )
+\bigg \} + y_t \bigg [ 144 y_t^3 a_t + 24 y_b^3 a_b + 14 y_t y_b \left (
+y_t a_b + a_t y_b \right ) \nonumber \\
+& {} + 2 y_b y_\tau \left ( y_b a_\tau + a_b y_\tau \right ) +
+18 \lambda y_t \left ( \lambda a_t + a_{\lambda} y_t \right ) +
+8 \lambda y_b \left ( \lambda a_b + a_{\lambda} y_b \right ) +
+2 \lambda y_\tau \left ( \lambda a_\tau + a_{\lambda} y_\tau \right )
+\nonumber \\
+& {} + 8 \lambda^3 a_{\lambda} + 4 \lambda \sum_{i=1}^3 \lambda_i \left (
+\lambda a_{\lambda_i} + a_{\lambda} \lambda_i \right ) +
+6 \lambda \sum_{i=1}^3 \kappa_i \left ( \lambda a_{\kappa_i} +
+a_{\lambda} \kappa_i \right ) - 64 g_3^2 y_t \left ( a_t - y_t M_3 \right )
+\nonumber \\
+& {} - \frac{32}{3} g_3^2 y_b \left ( a_b - y_b M_3 \right ) -
+36 g_2^2 y_t \left ( a_t - y_t M_2 \right ) - 6 g_2^2 y_b \left ( a_b -
+y_b M_2 \right ) - 6 g_2^2 \lambda \left ( a_\lambda - \lambda M_2 \right )
+\nonumber \\
+& {} - \frac{52}{5} g_1^2 y_t \left ( a_t - y_t M_1 \right ) -
+\frac{14}{15} g_1^2 y_b \left ( a_b - y_b M_1 \right ) -
+\frac{18}{15} g_1^2 \lambda \left ( a_\lambda - \lambda M_1 \right )
+\nonumber \\
+& {} - 24 g_1'^2 y_t \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \left ( a_t -
+y_t M_1' \right ) - 4 g_1'^2 y_b \left ( Q_1^2 + Q_Q^2 + Q_d^2 \right )
+\left ( a_b - y_b M_1' \right ) \nonumber \\
+& {} - 4 g_1'^2 \lambda \left ( Q_1^2 + Q_2^2 + Q_S^2 \right )
+\left ( a_\lambda - \lambda M_1' \right ) + 48 g_2^4 M_2 +
+\frac{832}{25} g_1^4 M_1 \nonumber \\
+& {} + 8 g_1'^4 M_1' \Sigma_Q \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \bigg ] .
+\label{eq:USSMTYu22Ot2Coeff}
 \end{align}
 \end{subequations}
-The one- and two-loop $\beta$ functions and the resulting $O(t^2)$ coefficient for $m_{Q_3}^2$ are 
+The one- and two-loop $\beta$ functions and the resulting $O(t^2)$ coefficient
+for $m_{Q_3}^2$ are
 \begin{subequations}
 \begin{align}
-\beta_{m_{Q_3}^2}^{(1)}&=2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )+2a_t^2+2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )+2a_b^2\nonumber\\
-&{}-\frac{32}{3}g_3^2M_3^2-6g_2^2M_2^2-\frac{2}{15}g_1^2M_1^2-8Q_Q^2g_1'^2M_1'^2+\frac{1}{5}g_1^2\Sigma_1+2Q_Qg_1'^2\Sigma_1',\label{eq:USSMmq222BetaOneLoop}\\
-\beta_{m_{Q_3}^2}^{(2)}&=-20y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2 \right )-20y_b^4\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2 \right )\nonumber\\
-&{}-2y_\tau^2y_b^2\left ( 2m_{H_d}^2+m_{Q_3}^2+m_{L_3}^2+m_{d_3}^2+m_{e_3}^2\right )-40y_t^2a_t^2-40y_b^2a_b^2\nonumber\\
-&{}-2\left ( y_ba_\tau+y_\tau a_b\right )^2-2\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )\nonumber\\
-&{}-2\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{d_3}^2\right )-2\left ( \lambda a_t+y_t a_\lambda \right )^2-2\left ( \lambda a_b+y_b a_\lambda \right )^2\nonumber\\
-&{}+\frac{2}{5}g_1^2y_t^2\left ( m_{H_u}^2+3m_{Q_3}^2+8m_{u_3}^2 +8M_1^2\right )+\frac{8}{5}g_1^2\left ( a_t^2-2y_ta_tM_1 \right )\nonumber\\
-&{}+\frac{2}{5}g_1^2y_b^2\left ( 5m_{H_d}^2+m_{Q_3}^2+4M_1^2\right )+\frac{4}{5}g_1^2\left ( a_b^2-2y_ba_bM_1 \right )+\frac{2}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2-2m_{e_3}^2\right )\nonumber\\
-&{}+\frac{2}{5}g_1^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_{D_i}^2-m_{\overline{D}_i}^2\right )+\lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )\right ]\nonumber\\
-&{}+4g_1'^2y_t^2\left ( Q_2^2-Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1'^2\right )\nonumber\\
-&{}+4g_1'^2\left ( Q_2^2-Q_Q^2+Q_u^2\right )\left ( a_t^2 -2y_ta_tM_1'\right )-24Q_Qg_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q_3}^2+Q_um_{u_3}^2\right )\nonumber\\
-&{}+4g_1'^2y_b^2\left ( Q_1^2-Q_Q^2+Q_d^2 \right )\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_1'^2\right )\nonumber\\
-&{}+4g_1'^2\left ( Q_1^2-Q_Q^2+Q_d^2\right )\left ( a_b^2-2y_ba_bM_1'\right )-24Q_Qg_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q_3}^2+Q_dm_{d_3}^2\right )\nonumber\\
-&{}-8Q_Qg_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L_3}^2+Q_em_{e_3}^2\right )\nonumber\\
-&{}-4Q_Qg_1'^2\sum_{i=1}^3\left [ 3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{D_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2\right )+2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )\right ]\nonumber\\
-&{}+\frac{16}{3}g_3^4\left [ 10M_3^2+\sum_{i=1}^3\left ( 2m_{Q_i}^2+m_{u_i}^2+m_{d_i}^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )\right ]+32g_3^2g_2^2\left ( M_2^2+M_2M_3+M_3^2\right )\nonumber\\
-&{}+\frac{16}{45}g_3^2g_1^2\left [ 2\left ( M_1^2+M_1M_3+M_3^2\right )+3\sum_{i=1}^3\left ( m_{Q_i}^2+m_{d_i}^2-2m_{u_i}^2-m_{D_i}^2+m_{\overline{D}_i}^2\right )\right ]\nonumber\\
-&{}+\frac{32}{3}Q_Qg_3^2g_1'^2\bigg [ 4Q_Q\left ( M_1'^2+M_1'M_3+M_3^2 \right )+3\sum_{i=1}^3\big ( 2Q_Qm_{Q_i}^2+Q_um_{u_i}^2+Q_dm_{d_i}^2\nonumber\\
-&{}+Q_Dm_{D_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2 \big )\bigg ]+3g_2^4\left [ 29M_2^2+m_{\overline{H'}}^2+m_{H'}^2+\sum_{i=1}^3\left ( 3m_{Q_i}^2+m_{L_i}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
-&{}+\frac{1}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2 \right )+3m_{\overline{H'}}^2-3m_{H'}^2+3\sum_{i=1}^3\left ( m_{Q_i}^2-m_{L_i}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
-&{}+12Q_Qg_2^2g_1'^2\bigg [ 2Q_Q\left ( M_1'^2+M_1'M_2+M_2^2\right )+Q_{\overline{H'}}m_{\overline{H'}}^2+Q_{H'}m_{H'}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Q_i}^2+Q_Lm_{L_i}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{75}g_1^4\bigg [ 289M_1^2+12m_{\overline{H'}}^2-6m_{H'}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 6m_{d_i}^2-2m_{D_i}^2+6m_{\overline{D}_i}^2+42m_{e_i}^2-6m_{H_i^d}^2+12m_{H_i^u}^2-6m_{L_i}^2+2m_{Q_i}^2-24m_{u_i}^2\right )\bigg ]\nonumber\\
-&{}+\frac{4}{15}g_1^2g_1'^2\bigg [ 2Q_Q\big ( 9Q_d+9Q_{\overline{D}}-9Q_D+9Q_e-9Q_1+9Q_2+3Q_{\overline{H'}}-3Q_{H'}-9Q_L\nonumber\\
-&{}+10Q_Q-18Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}^2m_{H'}^2\nonumber\\
-&{}+3\sum_{i=1}^3\big ( Q_d^2m_{d_i}^2+Q_{\overline{D}}^2m_{\overline{D}_i}^2-Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2\nonumber\\
-&{}-Q_L^2m_{L_i}^2-Q_Q^2m_{Q_i}^2-2Q_u^2m_{u_i}^2\big )+15Q_QQ_{\overline{H'}}m_{\overline{H'}}^2+3Q_QQ_{H'}m_{H'}^2\nonumber\\
-&{}+Q_Q\sum_{i=1}^3\big ( 12Q_dm_{d_i}^2+12Q_{\overline{D}}m_{\overline{D}_i}^2+24Q_em_{e_i}^2+3Q_1m_{H_i^d}^2+15Q_2m_{H_i^u}^2+3Q_Lm_{L_i}^2\nonumber\\
-&{}+15Q_Qm_{Q_i}^2+12m_{u_i}^2\big )\bigg ]+8Q_Qg_1'^4\bigg [ 3Q_QM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2\nonumber\\
-&{}+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2+20Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2\nonumber\\
-&{}+\sum_{i=1}^3\big ( 3Q_d^3m_{d_i}^2+3Q_{\overline{D}}^3m_{\overline{D}_i}^2+3Q_D^3m_{D_i}^2+Q_e^3m_{e_i}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{L_i}^2\nonumber\\
-&{}+6Q_Q^3m_{Q_i}^2+Q_S^3m_{Si}^2+3Q_u^3m_{u_i}^2\big )+2Q_QQ_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_QQ_{H'}^2m_{H'}^2\nonumber\\
-&{}+Q_Q\sum_{i=1}^3\big ( 3Q_d^2m_{d_i}^2+3Q_{\overline{D}}^2m_{\overline{D}_i}^2+3Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2\nonumber\\
-&{}+2Q_L^2m_{L_i}^2+6Q_Q^2m_{Q_i}^2+Q_S^2m_{Si}^2+3Q_u^2m_{u_i}^2\big )\bigg ],\label{eq:USSMmq222BetaTwoLoop}\\
-b_{m_{Q_3}^2}^{(2)}&=24y_t^4\left ( m_{H_u^2}+m_{Q_3}^2+m_{u_3}^2\right )+24y_b^4\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )+48y_t^2a_t^2+48y_b^2a_b^2\nonumber\\
-&{}+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2\right )+4\left ( y_ta_b+y_ba_t\right )^2\nonumber\\
-&{}+2y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+m_{L_3}^2+m_{e_3}^2\right )+2\left ( y_\tau a_b+y_ba_\tau\right )^2\nonumber\\
-&{}+2\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )+2\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
-&{}+2\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q_3}^2+m_{d_3}^2\right )+2\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
-&{}-\frac{32}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_3^2\right )-\frac{32}{3}g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
-&{}-\frac{32}{3}g_3^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_3^2\right )-\frac{32}{3}g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
-&{}-6g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_2^2\right )-6g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
-&{}-6g_2^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_2^2\right )-6g_2^2\left ( a_b^2-2y_ba_bM_2\right )\nonumber\\
-&{}-\frac{26}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1^2\right )-\frac{26}{15}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
-&{}-\frac{14}{15}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_1^2\right )-\frac{14}{15}g_1^2\left ( a_b^2-2y_ba_bM_1\right )\nonumber\\
-&{}-4g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1'^2\right )-4g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\times\nonumber\\
-&{}\times\left ( a_t^2-2y_ta_tM_1'\right )+2g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 6Q_Qm_{H_u}^2+6Q_Qm_{Q_3}^2+6Q_Qm_{u_3}^2+\Sigma_1'\right )\nonumber\\
-&{}+12Q_Qg_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )-4g_1'^2y_b^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2+2M_1'^2\right )\nonumber\\
-&{}-4g_1'^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( a_b^2-2y_ba_bM_1'\right )+2g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\times\nonumber\\
-&{}\times\left ( 6Q_Qm_{H_d}^2+6Q_Qm_{Q_3}^2+6Q_Qm_{d_3}^2+\Sigma_1'\right )+12Q_Qg_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )\nonumber\\
-&{}+4Q_Qg_1'^2y_\tau^2\left (Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )+4Q_Qg_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
-&{}+2Q_Qg_1'^2\sum_{i=1}^3\Big [ 2\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+2a_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )\nonumber\\
-&{}+3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+3a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\Big ]\nonumber\\
-&{}-96Q_Qg_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )-72g_2^4M_2^2\nonumber\\
-&{}-12Q_Qg_2^2g_1'^2M_2^2\left ( 9Q_Q+3Q_L+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\right )+\frac{96}{25}g_1^4\left ( \Sigma_1-M_1^2\right )\nonumber\\
-&{}-\frac{1}{5}g_1^2g_1'^2\big [ 12Q_QM_1^2\big ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}+3Q_L\nonumber\\
-&{}+Q_Q+8Q_u\big )+4M_1'^2\big ( 3Q_d^2+3Q_{\overline{D}}^2-3Q_D^2+3Q_e^2-3Q_1^2+3Q_2^2+Q_{\overline{H'}}^2-Q_{H'}^2-3Q_L^2\nonumber\\
-&{}+3Q_Q^2-6Q_u^2\big )-\left ( 6Q_Q\Sigma_1+\Sigma_1'\right )\Sigma_Q^Y\big ]-4Q_Qg_1'^4\big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3\nonumber\\
-&{}+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )+\left ( 6Q_QM_1'^2-\Sigma_1'\right )\Sigma_Q\big ].\label{eq:USSMmq222Ot2Coeff}
+\beta_{m_{Q_3}^2}^{(1)} &= 2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2
+\right ) + 2 a_t^2 + 2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2
+\right ) + 2 a_b^2 \nonumber \\
+& {} - \frac{32}{3} g_3^2 M_3^2 - 6 g_2^2 M_2^2 - \frac{2}{15} g_1^2 M_1^2 -
+8 Q_Q^2 g_1'^2 M_1'^2 + \frac{1}{5} g_1^2 \Sigma_1 + 2 Q_Q g_1'^2 \Sigma_1' ,
+\label{eq:USSMmq222BetaOneLoop} \\
+\beta_{m_{Q_3}^2}^{(2)} &= -20 y_t^4 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2
+ \right ) - 20 y_b^4 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 \right )
+\nonumber \\
+& {} - 2 y_\tau^2 y_b^2 \left ( 2 m_{H_d}^2 + m_{Q_3}^2 + m_{L_3}^2 +
+m_{d_3}^2 + m_{e_3}^2 \right ) - 40 y_t^2 a_t^2 - 40 y_b^2 a_b^2 \nonumber \\
+& {} - 2 \left ( y_b a_\tau + y_\tau a_b \right )^2 - 2 \lambda^2 y_t^2
+\left ( 2 m_{H_u}^2 + m_{H_d}^2 + m_S^2 + m_{Q_3}^2 + m_{u_3}^2 \right )
+\nonumber \\
+& {} - 2 \lambda^2 y_b^2 \left ( m_{H_u}^2 + 2 m_{H_d}^2 + m_S^2 + m_{Q_3}^2
++ m_{d_3}^2 \right ) - 2 \left ( \lambda a_t + y_t a_\lambda \right )^2 -
+2 \left ( \lambda a_b + y_b a_\lambda \right )^2 \nonumber \\
+& {} + \frac{2}{5} g_1^2 y_t^2 \left ( m_{H_u}^2 + 3m_{Q_3}^2 + 8 m_{u_3}^2
++ 8 M_1^2 \right ) + \frac{8}{5} g_1^2 \left ( a_t^2 - 2 y_t a_t M_1 \right )
+\nonumber \\
+& {} + \frac{2}{5} g_1^2 y_b^2 \left ( 5 m_{H_d}^2 + m_{Q_3}^2 + 4 M_1^2
+\right ) + \frac{4}{5} g_1^2 \left ( a_b^2 - 2 y_b a_b M_1 \right ) +
+\frac{2}{5} g_1^2 y_\tau^2 \left ( m_{H_d}^2 + m_{L_3}^2 - 2 m_{e_3}^2
+\right ) \nonumber \\
+& {} + \frac{2}{5} g_1^2 \sum_{i=1}^3 \left [ \kappa_i^2 \left ( m_{D_i}^2 -
+m_{\overline{D}_i}^2 \right ) + \lambda_i^2 \left ( m_{H_i^d}^2 - m_{H_i^u}^2
+\right ) \right ] \nonumber \\
+& {} + 4 g_1'^2 y_t^2 \left ( Q_2^2 - Q_Q^2 + Q_u^2 \right )
+\left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 + 2 M_1'^2 \right ) \nonumber \\
+& {} + 4 g_1'^2 \left ( Q_2^2 - Q_Q^2 + Q_u^2 \right ) \left ( a_t^2 -
+2 y_t a_t M_1' \right ) - 24 Q_Q g_1'^2 y_t^2 \left ( Q_2 m_{H_u}^2 +
+Q_Q m_{Q_3}^2 + Q_um_{u_3}^2 \right ) \nonumber \\
+& {} + 4 g_1'^2 y_b^2 \left ( Q_1^2 - Q_Q^2 + Q_d^2 \right ) \left ( m_{H_d}^2
++ m_{Q_3}^2 + m_{d_3}^2 + 2 M_1'^2 \right ) \nonumber \\
+& {} + 4 g_1'^2 \left ( Q_1^2 - Q_Q^2 + Q_d^2 \right ) \left ( a_b^2 -
+2 y_b a_b M_1' \right ) - 24 Q_Q g_1'^2 y_b^2 \left ( Q_1 m_{H_d}^2 +
+Q_Q m_{Q_3}^2 + Q_d m_{d_3}^2 \right ) \nonumber \\
+& {} - 8 Q_Q g_1'^2 y_\tau^2 \left ( Q_1 m_{H_d}^2 + Q_L m_{L_3}^2 +
+Q_e m_{e_3}^2 \right ) \nonumber \\
+& {} - 4 Q_Q g_1'^2 \sum_{i=1}^3 \left [ 3 \kappa_i^2 \left ( Q_S m_S^2 +
+Q_D m_{D_i}^2 + Q_{\overline{D}} m_{\overline{D}_i}^2 \right ) +
+2 \lambda_i^2 \left ( Q_1 m_{H_i^d}^2 + Q_2 m_{H_i^u}^2 + Q_S m_S^2 \right )
+\right ] \nonumber \\
+& {} + \frac{16}{3} g_3^4 \left [ 10 M_3^2 + \sum_{i=1}^3 \left ( 2 m_{Q_i}^2
++ m_{u_i}^2 + m_{d_i}^2 + m_{D_i}^2 + m_{\overline{D}_i}^2 \right ) \right ]
++ 32 g_3^2 g_2^2 \left ( M_2^2 + M_2 M_3 + M_3^2 \right ) \nonumber \\
+& {} + \frac{16}{45} g_3^2 g_1^2 \left [ 2 \left ( M_1^2 + M_1 M_3 + M_3^2
+\right ) + 3 \sum_{i=1}^3 \left ( m_{Q_i}^2 + m_{d_i}^2 - 2 m_{u_i}^2 -
+m_{D_i}^2 + m_{\overline{D}_i}^2 \right ) \right ] \nonumber \\
+& {} + \frac{32}{3} Q_Q g_3^2 g_1'^2 \bigg [ 4 Q_Q \left ( M_1'^2 + M_1' M_3
++ M_3^2 \right ) + 3 \sum_{i=1}^3 \big ( 2 Q_Q m_{Q_i}^2 + Q_u m_{u_i}^2 +
+Q_d m_{d_i}^2 \nonumber \\
+& {} + Q_D m_{D_i}^2 + Q_{\overline{D}} m_{\overline{D}_i}^2 \big ) \bigg ]
++ 3 g_2^4 \left [ 29 M_2^2 + m_{\overline{H'}}^2 + m_{H'}^2 +
+\sum_{i=1}^3 \left ( 3 m_{Q_i}^2 + m_{L_i}^2 + m_{H_i^d}^2 + m_{H_i^u}^2
+\right ) \right ] \nonumber \\
+& {} + \frac{1}{5} g_2^2 g_1^2 \left [ 2 \left ( M_1^2 + M_1 M_2 + M_2^2
+\right ) + 3 m_{\overline{H'}}^2 - 3 m_{H'}^2 +
+3 \sum_{i=1}^3 \left ( m_{Q_i}^2 - m_{L_i}^2 + m_{H_i^u}^2 - m_{H_i^d}^2
+\right ) \right ] \nonumber \\
+& {} + 12 Q_Q g_2^2 g_1'^2 \bigg [ 2 Q_Q \left ( M_1'^2 + M_1' M_2 + M_2^2
+\right ) + Q_{\overline{H'}} m_{\overline{H'}}^2 + Q_{H'} m_{H'}^2 \nonumber \\
+& {} + \sum_{i=1}^3 \left ( 3 Q_Q m_{Q_i}^2 + Q_L m_{L_i}^2 + Q_1 m_{H_i^d}^2
++ Q_2 m_{H_i^u}^2 \right ) \bigg ] + \frac{1}{75} g_1^4 \bigg [ 289 M_1^2 +
+12 m_{\overline{H'}}^2 - 6 m_{H'}^2 \nonumber \\
+& {} + \sum_{i=1}^3 \left ( 6 m_{d_i}^2 - 2 m_{D_i}^2 + 6 m_{\overline{D}_i}^2
++ 42 m_{e_i}^2 - 6 m_{H_i^d}^2 + 12 m_{H_i^u}^2 - 6 m_{L_i}^2 + 2 m_{Q_i}^2
+- 24 m_{u_i}^2 \right ) \bigg ] \nonumber \\
+& {} + \frac{4}{15} g_1^2 g_1'^2 \bigg [ 2 Q_Q \big ( 9 Q_d +
+9 Q_{\overline{D}} - 9 Q_D + 9 Q_e - 9 Q_1 + 9 Q_2 + 3 Q_{\overline{H'}} -
+3 Q_{H'} - 9 Q_L \nonumber \\
+& {} + 10 Q_Q - 18 Q_u \big ) \left ( M_1^2 + M_1 M_1' + M_1'^2 \right ) +
+3 Q_{\overline{H'}}^2 m_{\overline{H'}}^2 - 3 Q_{H'}^2 m_{H'}^2 \nonumber \\
+& {} + 3 \sum_{i=1}^3 \big ( Q_d^2 m_{d_i}^2 +
+Q_{\overline{D}}^2 m_{\overline{D}_i}^2 - Q_D^2 m_{D_i}^2 + Q_e^2 m_{e_i}^2 -
+Q_1^2 m_{H_i^d}^2 + Q_2^2 m_{H_i^u}^2 \nonumber \\
+& {} - Q_L^2 m_{L_i}^2 - Q_Q^2 m_{Q_i}^2 - 2 Q_u^2 m_{u_i}^2 \big ) +
+15 Q_Q Q_{\overline{H'}} m_{\overline{H'}}^2 + 3 Q_Q Q_{H'} m_{H'}^2
+\nonumber \\
+& {} + Q_Q \sum_{i=1}^3 \big ( 12 Q_d m_{d_i}^2 +
+12 Q_{\overline{D}} m_{\overline{D}_i}^2 + 24 Q_e m_{e_i}^2 +
+3 Q_1 m_{H_i^d}^2 + 15 Q_2 m_{H_i^u}^2 + 3 Q_L m_{L_i}^2 \nonumber \\
+& {} + 15 Q_Q m_{Q_i}^2 + 12 m_{u_i}^2 \big ) \bigg ] + 8 Q_Q g_1'^4 \bigg [
+3 Q_Q M_1'^2 \big ( 9 Q_d^2 + 9 Q_{\overline{D}}^2 + 9 Q_D^2 + 3 Q_e^2 +
+6 Q_1^2 \nonumber \\
+& {} + 6 Q_2^2 + 2 Q_{\overline{H'}}^2 + 2 Q_{H'}^2 + 6 Q_L^2 + 20 Q_Q^2 +
+3 Q_S^2 + 9 Q_u^2 \big ) + 2 Q_{\overline{H'}}^3 m_{\overline{H'}}^2 +
+2 Q_{H'}^3 m_{H'}^2 \nonumber \\
+& {} + \sum_{i=1}^3 \big ( 3 Q_d^3 m_{d_i}^2 +
+3 Q_{\overline{D}}^3 m_{\overline{D}_i}^2 + 3 Q_D^3 m_{D_i}^2 +
+Q_e^3 m_{e_i}^2 + 2 Q_1^3 m_{H_i^d}^2 + 2 Q_2^3 m_{H_i^u}^2 +
+2 Q_L^3 m_{L_i}^2 \nonumber \\
+& {} + 6 Q_Q^3 m_{Q_i}^2 + Q_S^3 m_{S_i}^2 + 3 Q_u^3 m_{u_i}^2 \big ) +
+2 Q_Q Q_{\overline{H'}}^2 m_{\overline{H'}}^2 + 2 Q_Q Q_{H'}^2 m_{H'}^2
+\nonumber \\
+& {} + Q_Q \sum_{i=1}^3 \big ( 3 Q_d^2 m_{d_i}^2 +
+3 Q_{\overline{D}}^2 m_{\overline{D}_i}^2 + 3 Q_D^2 m_{D_i}^2 +
+Q_e^2 m_{e_i}^2 + 2 Q_1^2 m_{H_i^d}^2 + 2 Q_2^2 m_{H_i^u}^2 \nonumber \\
+& {} + 2 Q_L^2 m_{L_i}^2 + 6 Q_Q^2 m_{Q_i}^2 + Q_S^2 m_{S_i}^2 +
+3 Q_u^2 m_{u_i}^2 \big ) \bigg ] , \label{eq:USSMmq222BetaTwoLoop} \\
+b_{m_{Q_3}^2}^{(2)} &= 24 y_t^4 \left ( m_{H_u^2} + m_{Q_3}^2 + m_{u_3}^2
+\right ) + 24 y_b^4 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 \right ) +
+48 y_t^2 a_t^2 + 48 y_b^2 a_b^2 \nonumber \\
+& {} + 4 y_t^2 y_b^2 \left ( m_{H_u}^2 + m_{H_d}^2 + 2 m_{Q_3}^2 + m_{u_3}^2
++ m_{d_3}^2 \right ) + 4 \left ( y_t a_b + y_b a_t \right )^2 \nonumber \\
+& {} + 2 y_b^2 y_\tau^2 \left ( 2 m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 +
+m_{L_3}^2 + m_{e_3}^2 \right ) + 2 \left ( y_\tau a_b + y_b a_\tau \right )^2
+\nonumber \\
+& {} + 2 \lambda^2 y_t^2 \left ( m_{H_d}^2 + 2 m_{H_u}^2 + m_S^2 + m_{Q_3}^2
++ m_{u_3}^2 \right ) + 2 \left ( \lambda a_t + y_t a_\lambda \right )^2
+\nonumber \\
+& {} + 2 \lambda^2 y_b^2 \left ( 2 m_{H_d}^2 + m_{H_u}^2 + m_S^2 + m_{Q_3}^2
++ m_{d_3}^2 \right ) + 2 \left ( \lambda a_b + y_b a_\lambda \right )^2
+\nonumber \\
+& {} - \frac{32}{3} g_3^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 +
+2 M_3^2 \right ) - \frac{32}{3} g_3^2 \left ( a_t^2 - 2 y_t a_t M_3 \right )
+\nonumber \\
+& {} - \frac{32}{3} g_3^2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 +
+2 M_3^2 \right ) - \frac{32}{3} g_3^2 \left ( a_b^2 - 2 y_b a_b M_3 \right )
+\nonumber \\
+& {} - 6 g_2^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 + 2 M_2^2
+\right ) - 6 g_2^2 \left ( a_t^2 - 2 y_t a_t M_2 \right ) \nonumber \\
+& {} - 6 g_2^2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 + 2 M_2^2
+\right ) - 6 g_2^2 \left ( a_b^2 - 2 y_b a_b M_2 \right ) \nonumber \\
+& {} - \frac{26}{15} g_1^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 +
+2 M_1^2 \right ) - \frac{26}{15} g_1^2 \left ( a_t^2 - 2 y_t a_t M_1 \right )
+\nonumber \\
+& {} - \frac{14}{15} g_1^2 y_b^2 \left ( m_{H_d}^2 + m_{Q_3}^2 + m_{d_3}^2 +
+2 M_1^2 \right ) - \frac{14}{15} g_1^2 \left ( a_b^2 - 2 y_b a_b M_1 \right )
+\nonumber \\
+& {} - 4 g_1'^2 y_t^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \left ( m_{H_u}^2
++ m_{Q_3}^2 + m_{u_3}^2 + 2 M_1'^2 \right ) - 4 g_1'^2 \left ( Q_2^2 + Q_Q^2
++ Q_u^2 \right ) \nonumber \\
+& {} \times \left ( a_t^2 - 2 y_t a_t M_1' \right ) + 2 g_1'^2 y_t^2 \left (
+Q_2 + Q_Q + Q_u \right ) \left ( 6 Q_Q m_{H_u}^2 + 6 Q_Q m_{Q_3}^2 +
+6 Q_Q m_{u_3}^2 + \Sigma_1' \right ) \nonumber \\
+& {} + 12 Q_Q g_1'^2 a_t^2 \left ( Q_2 + Q_Q + Q_u \right ) -
+4 g_1'^2 y_b^2 \left ( Q_1^2 + Q_Q^2 + Q_d^2 \right ) \left ( m_{H_d}^2 +
+m_{Q_3}^2 + m_{d_3}^2 + 2 M_1'^2 \right ) \nonumber \\
+& {} - 4 g_1'^2 \left ( Q_1^2 + Q_Q^2 + Q_d^2 \right ) \left ( a_b^2 -
+2 y_b a_b M_1' \right ) + 2 g_1'^2 y_b^2 \left ( Q_1 + Q_Q + Q_d \right )
+\nonumber \\
+& {} \times \left ( 6 Q_Q m_{H_d}^2 + 6 Q_Q m_{Q_3}^2 + 6 Q_Q m_{d_3}^2 +
+\Sigma_1' \right ) + 12 Q_Q g_1'^2 a_b^2 \left ( Q_1 + Q_Q + Q_d \right )
+\nonumber \\
+& {} + 4 Q_Q g_1'^2 y_\tau^2 \left ( Q_1 + Q_L + Q_e \right ) \left (
+m_{H_d}^2 + m_{L_3}^2 + m_{e_3}^2 \right ) + 4 Q_Q g_1'^2 a_\tau^2 \left (
+Q_1 + Q_L + Q_e \right ) \nonumber \\
+& {} + 2 Q_Q g_1'^2 \sum_{i=1}^3 \Big [ 2 \lambda_i^2 \left ( Q_1 + Q_2 + Q_S
+\right ) \left ( m_{H_i^d}^2 + m_{H_i^u}^2 + m_S^2 \right ) +
+2 a_{\lambda_i}^2 \left ( Q_1 + Q_2 + Q_S \right ) \nonumber \\
+& {} + 3 \kappa_i^2 \left ( Q_S + Q_D + Q_{\overline{D}} \right ) \left (
+m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2 \right ) + 3 a_{\kappa_i}^2 \left (
+Q_S + Q_D + Q_{\overline{D}} \right ) \Big ] \nonumber \\
+& {} - 96 Q_Q g_3^2 g_1'^2 M_3^2 \left ( 2 Q_Q + Q_u + Q_d + Q_D +
+Q_{\overline{D}} \right ) - 72 g_2^4 M_2^2 \nonumber \\
+& {} - 12 Q_Q g_2^2 g_1'^2 M_2^2 \left ( 9 Q_Q + 3 Q_L + 3 Q_1 + 3 Q_2 +
+Q_{\overline{H'}} + Q_{H'} \right ) + \frac{96}{25} g_1^4 \left ( \Sigma_1 -
+M_1^2 \right ) \nonumber \\
+& {} - \frac{1}{5} g_1^2 g_1'^2 \big [ 12 Q_Q M_1^2 \big ( 2 Q_d +
+2 Q_{\overline{D}} + 2 Q_D + 6 Q_e + 3 Q_1 + 3 Q_2 + Q_{\overline{H'}} +
+Q_{H'} + 3 Q_L \nonumber \\
+& {} + Q_Q + 8 Q_u \big ) + 4 M_1'^2 \big ( 3 Q_d^2 + 3 Q_{\overline{D}}^2 -
+3 Q_D^2 + 3 Q_e^2 - 3 Q_1^2 + 3 Q_2^2 + Q_{\overline{H'}}^2 - Q_{H'}^2 -
+3 Q_L^2 \nonumber \\
+& {} + 3 Q_Q^2 - 6 Q_u^2 \big ) - \left ( 6 Q_Q \Sigma_1 + \Sigma_1' \right )
+\Sigma_Q^Y \big ] - 4 Q_Q g_1'^4 \big [ 2 M_1'^2 \big ( 9 Q_d^3 +
+9 Q_{\overline{D}}^3 + 9 Q_D^3 + 3 Q_e^3 + 6 Q_1^3 \nonumber \\
+& {} + 6 Q_2^3 + 2 Q_{\overline{H'}}^3 + 2 Q_{H'}^3 + 6 Q_L^3 + 18 Q_Q^3 +
+3 Q_S^3 + 9 Q_u^3 \big ) + \left ( 6 Q_Q M_1'^2 - \Sigma_1' \right )
+\Sigma_Q \big ] . \label{eq:USSMmq222Ot2Coeff}
 \end{align}
@@
 \begin{align}
-\beta_{m_{u_3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )+4a_t^2-\frac{32}{3}g_3^2M_3^2-\frac{32}{15}g_1^2M_1^2-8Q_u^2g_1'^2M_1'^2\nonumber\\
-&{}-\frac{4}{5}g_1^2\Sigma_1+2Q_ug_1'^2\Sigma_1',\label{eq:USSMmu222BetaOneLoop}\\
-\beta_{m_{u_3}^2}^{(2)}&=-32y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2\right )-4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2\right )\nonumber\\
-&{}-64y_t^2a_t^2-4\left ( y_ta_b+y_ba_t\right )^2-4\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2\right )\nonumber\\
-&{}-4\left ( \lambda a_t + y_ta_\lambda \right )^2+12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_2^2\right )+12g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
-&{}-\frac{4}{5}g_1^2y_t^2\left ( -5m_{H_u}^2-m_{Q_3}^2+9m_{u_3}^2+2M_1^2\right )-\frac{4}{5}g_1^2\left ( a_t^2-2y_ta_tM_1 \right )\nonumber\\
-&{}-\frac{8}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q_3}^2-2m_{d_3}^2\right )-\frac{8}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L_3}^2-2m_{e_3}^2\right )\nonumber\\
-&{}-\frac{8}{5}g_1^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_{D_i}^2-m_{\overline{D}_i}^2 \right )+\lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2 \right )\right ]\nonumber\\
-&{}+8g_1'^2y_t^2\left ( Q_2^2+Q_Q^2-Q_u^2\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1'^2\right )\nonumber\\
-&{}+8g_1'^2\left ( Q_2^2+Q_Q^2-Q_u^2\right )\left ( a_t^2-2y_ta_tM_1'\right )-24Q_ug_1'^2y_t^2\left (Q_2m_{H_u}^2+Q_Qm_{Q_3}^2+Q_um_{u_3}^2\right )\nonumber\\
-&{}-24Q_ug_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q_3}^2+Q_dm_{d_3}^2\right )-8Q_ug_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L_3}^2+Q_em_{e_3}^2\right )\nonumber\\
-&{}-12Q_ug_1'^2\sum_{i=1}^3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{D_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2\right )\nonumber\\
-&{}-8Q_ug_1'^2\sum_{i=1}^3\lambda_i^2\left ( Q_1m_{H_d}^2+Q_2m_{H_u}^2+Q_Sm_S^2\right )\nonumber\\
-&{}+\frac{16}{3}g_3^4\left [ 10M_3^2+\sum_{i=1}^3\left ( m_{d_i}^2+m_{D_i}^2+m_{\overline{D}_i}^2+2m_{Q_i}^2+m_{u_i}^2\right )\right ]\nonumber\\
-&{}+\frac{64}{45}g_3^2g_1^2\left [ 8\left (M_1^2+M_1M_3+M_3^2\right )-3\sum_{i=1}^3\left ( m_{d_i}^2-m_{D_i}^2+m_{\overline{D}_i}^2+m_{Q_i}^2-2m_{u_i}^2\right )\right ]\nonumber\\
-&{}+\frac{8}{3}Q_ug_3^2g_1'^2\bigg [ 16Q_u\left (M_1'^2+M_1'M_3+M_3^2\right )\nonumber\\
-&{}+12\sum_{i=1}^3\left ( Q_dm_{d_i}^2+Q_Dm_{D_i}^2+Q_{\overline{D}}m_{\overline{D}_i}^2+2Q_Qm_{Q_i}^2+Q_um_{u_i}^2\right )\bigg ]\nonumber\\
-&{}+\frac{12}{5}g_2^2g_1^2\left [ m_{H'}^2-m_{\overline{H'}}^2+\sum_{i=1}^3\left ( m_{H_i^d}^2-m_{H_i^u}^2+m_{L_i}^2-m_{Q_i}^2\right )\right ]\nonumber\\
-&{}+12Q_ug_2^2g_1'^2\left [ Q_{H'}m_{H'}^2+Q_{\overline{H'}}m_{\overline{H'}}^2+\sum_{i=1}^3\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Lm_{L_i}^2+3Q_Qm_{Q_i}^2\right )\right ]\nonumber\\
-&{}+\frac{4}{75}g_1^4\bigg [ 1261M_1^2+21m_{H'}^2+3m_{\overline{H'}}^2\nonumber\\
-&{}+\sum_{i=1}^3\left ( 4m_{d_i}^2+12m_{D_i}^2+4m_{\overline{D}_i}^2-12m_{e_i}^2+21m_{H_i^d}^2+3m_{H_i^u}^2+21m_{L_i}^2+3m_{Q_i}^2+64m_{u_i}^2\right )\bigg ]\nonumber\\
-&{}+\frac{4}{15}g_1^2g_1'^2\bigg [ -8Q_u\big ( 9Q_d+9Q_{\overline{D}}-9Q_D+9Q_e-9Q_1+9Q_2+3Q_{\overline{H'}}-3Q_{H'}-9Q_L\nonumber\\
-&{}+9Q_Q-22Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2 \right )+12Q_{H'}^2m_{H'}^2-12Q_{\overline{H'}}^2m_{\overline{H'}}^2\nonumber\\
-&{}+12\sum_{i=1}^3\big ( -Q_d^2m_{d_i}^2-Q_{\overline{D}}^2m_{\overline{D}_i}^2+Q_D^2m_{D_i}^2-Q_e^2m_{e_i}^2+Q_1^2m_{H_i^d}^2-Q_2^2m_{H_i^u}^2+Q_L^2m_{L_i}^2\nonumber\\
-&{}-Q_Q^2m_{Q_i}^2+Q_u^2m_{u_i}^2\big )-15Q_{\overline{H'}}Q_um_{\overline{H'}}^2+33Q_{H'}Q_um_{H'}^2+Q_u\sum_{i=1}^3\big ( -18Q_dm_{d_i}^2\nonumber\\
-&{}-18Q_{\overline{D}}m_{\overline{D}_i}^2+30Q_Dm_{D_i}^2-6Q_em_{e_i}^2+33Q_1m_{H_i^d}^2-15Q_2m_{H_i^u}^2+33Q_Lm_{L_i}^2\nonumber\\
-&{}-21Q_Qm_{Q_i}^2+84Q_um_{u_i}^2\big )\bigg ]+8Q_ug_1'^4\bigg [ 3Q_uM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2\nonumber\\
-&{}+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2+18Q_Q^2+3Q_S^2+11Q_u^2 \big )+2Q_{H'}^3m_{H'}^2+2Q_{\overline{H'}}^3m_{\overline{H'}}^2\nonumber\\
-&{}+\sum_{i=1}^3\big ( 3Q_d^3m_{d_i}^2+3Q_{\overline{D}}^3m_{\overline{D}_i}^2+3Q_D^3m_{D_i}^2+Q_e^3m_{e_i}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{L_i}^2\nonumber\\
-&{}+6Q_Q^3m_{Q_i}^2+Q_S^3m_{Si}^2+3Q_u^3m_{u_i}^2\big )+2Q_uQ_{H'}^2m_{H'}^2+2Q_uQ_{\overline{H'}}^2m_{\overline{H'}}^2\nonumber\\
-&{}+Q_u\sum_{i=1}^3\big ( 3Q_d^2m_{d_i}^2+3Q_{\overline{D}}^2m_{\overline{D}_i}^2+3Q_D^2m_{D_i}^2+Q_e^2m_{e_i}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{L_i}^2\nonumber\\
-&{}+6Q_Q^2m_{Q_i}^2+Q_S^2m_{Si}^2+3Q_u^2m_{u_i}^2\big )\bigg ],\label{eq:USSMmu222BetaTwoLoop}\\
-b_{m_{u_3}^2}^{(2)}&=48y_t^4\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2 \right )+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+m_{Q_3}^2+m_{u_3}^2+m_{d_3}^2 \right )+96y_t^2a_t^2\nonumber\\
-&{}+4\left ( y_ta_b+y_ba_t\right )^2+4\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q_3}^2+m_{u_3}^2 \right )+4\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
-&{}-\frac{64}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_3^2\right )-\frac{64}{3}g_3^2\left ( a_t^2-2y_ta_tM_3 \right )\nonumber\\
-&{}-12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_2^2\right )-12g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
-&{}-\frac{52}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1^2\right )-\frac{52}{15}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
-&{}-8g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q_3}^2+m_{u_3}^2+2M_1'^2\right )\nonumber\\
-&{}-8g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( a_t^2-2y_ta_tM_1'\right )\nonumber\\
-&{}+4g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 3Q_um_{H_u}^2+3Q_um_{Q_3}^2+3Q_um_{u_3}^2+\Sigma_1'\right )\nonumber\\
-&{}+12Q_ug_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_ug_1'^2y_b^2\left ( Q_1+Q_Q+Q_d \right )\left ( m_{H_d}^2+m_{Q_3}^2+m_{d_3}^2\right )\nonumber\\
-&{}+12Q_ug_1'^2a_b^2\left ( Q_1+Q_Q+Q_d \right )\nonumber\\
-&{}+4Q_ug_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L_3}^2+m_{e_3}^2\right )+4Q_ug_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
-&{}+2Q_ug_1'^2\sum_{i=1}^3\bigg [ 3\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+3a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\nonumber\\
-&{}+2\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+2a_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )\bigg ]\nonumber\\
-&{}-96Q_ug_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )\nonumber\\
-&{}-12Q_ug_2^2g_1'^2M_2^2\left ( 9Q_Q+3Q_L+3Q_1+3Q_2+Q_{H'}+Q_{\overline{H'}}\right )-\frac{384}{25}g_1^4\left ( \Sigma_1+4M_1^2\right )\nonumber\\
-&{}+\frac{2}{5}g_1^2g_1'^2\big [ 8M_1'^2 ( 3Q_d^2+3Q_{\overline{D}}^2-3Q_D^2+3Q_e^2-3Q_1^2+3Q_2^2+Q_{\overline{H'}}^2-Q_{H'}^2-3Q_L^2\nonumber\\
-&{}+3Q_Q^2-6Q_u^2 )+6Q_uM_1^2 ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\nonumber\\
-&{}+3Q_L+Q_Q+8Q_u )+\left ( 3Q_u\Sigma_1-2\Sigma_1^\prime\right ) \Sigma_Q^Y\big ]-4Q_ug_1'^4\big [ 2M_1'^2 ( 9Q_d^3+9Q_D^3+9Q_{\overline{D}}^3\nonumber\\
-&{}+3Q_e^3+6Q_1^3+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3 )\nonumber\\
-&{}+\left(6Q_uM_1'^2-\Sigma_1^\prime\right )\Sigma_Q\big ].\label{eq:USSMmu222Ot2Coeff}
+\beta_{m_{u_3}^2}^{(1)} &= 4 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2
+\right ) + 4 a_t^2 - \frac{32}{3} g_3^2 M_3^2 - \frac{32}{15} g_1^2 M_1^2
+- 8 Q_u^2 g_1'^2 M_1'^2 \nonumber \\
+& {} - \frac{4}{5} g_1^2 \Sigma_1 + 2 Q_u g_1'^2 \Sigma_1' ,
+\label{eq:USSMmu222BetaOneLoop} \\
+\beta_{m_{u_3}^2}^{(2)} &= -32 y_t^4 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2
+\right ) - 4 y_t^2 y_b^2 \left ( m_{H_u}^2 + m_{H_d}^2 + 2 m_{Q_3}^2 +
+m_{u_3}^2 + m_{d_3}^2 \right ) \nonumber \\
+& {} - 64 y_t^2 a_t^2 -4 \left ( y_t a_b + y_b a_t \right )^2 -
+4 \lambda^2 y_t^2 \left ( 2 m_{H_u}^2 + m_{H_d}^2 + m_S^2 + m_{Q_3}^2 +
+m_{u_3}^2 \right ) \nonumber \\
+& {} - 4 \left ( \lambda a_t + y_t a_\lambda \right )^2 + 12 g_2^2 y_t^2
+\left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 + 2 M_2^2 \right ) + 12 g_2^2
+\left ( a_t^2 - 2 y_t a_t M_2 \right ) \nonumber \\
+& {} - \frac{4}{5} g_1^2 y_t^2 \left ( -5 m_{H_u}^2 - m_{Q_3}^2 + 9 m_{u_3}^2
++ 2 M_1^2 \right ) - \frac{4}{5} g_1^2 \left ( a_t^2 - 2 y_t a_t M_1 \right )
+\nonumber \\
+& {} - \frac{8}{5} g_1^2 y_b^2 \left ( 3 m_{H_d}^2 - m_{Q_3}^2 - 2 m_{d_3}^2
+\right ) - \frac{8}{5} g_1^2 y_\tau^2 \left ( m_{H_d}^2 + m_{L_3}^2 -
+2 m_{e_3}^2 \right ) \nonumber \\
+& {} - \frac{8}{5} g_1^2 \sum_{i=1}^3 \left [ \kappa_i^2 \left ( m_{D_i}^2 -
+m_{\overline{D}_i}^2 \right ) + \lambda_i^2 \left ( m_{H_i^d}^2 - m_{H_i^u}^2
+\right ) \right ] \nonumber \\
+& {} + 8 g_1'^2 y_t^2 \left ( Q_2^2 + Q_Q^2 - Q_u^2 \right ) \left ( m_{H_u}^2
++ m_{Q_3}^2 + m_{u_3}^2 + 2 M_1'^2 \right ) \nonumber \\
+& {} + 8 g_1'^2 \left ( Q_2^2 + Q_Q^2 - Q_u^2 \right ) \left ( a_t^2 -
+2 y_t a_t M_1' \right ) - 24 Q_u g_1'^2 y_t^2 \left ( Q_2 m_{H_u}^2 +
+Q_Q m_{Q_3}^2 + Q_u m_{u_3}^2 \right ) \nonumber \\
+& {} - 24 Q_u g_1'^2 y_b^2 \left ( Q_1 m_{H_d}^2 + Q_Q m_{Q_3}^2 +
+Q_d m_{d_3}^2 \right ) - 8 Q_u g_1'^2 y_\tau^2 \left ( Q_1 m_{H_d}^2 +
+Q_L m_{L_3}^2 + Q_e m_{e_3}^2 \right ) \nonumber \\
+& {} - 12 Q_u g_1'^2 \sum_{i=1}^3 \kappa_i^2 \left ( Q_S m_S^2 + Q_D m_{D_i}^2
++ Q_{\overline{D}} m_{\overline{D}_i}^2 \right ) \nonumber \\
+& {} - 8 Q_u g_1'^2 \sum_{i=1}^3 \lambda_i^2 \left ( Q_1 m_{H_d}^2 +
+Q_2 m_{H_u}^2 + Q_S m_S^2 \right ) \nonumber \\
+& {} + \frac{16}{3} g_3^4 \left [ 10 M_3^2 + \sum_{i=1}^3 \left ( m_{d_i}^2
++ m_{D_i}^2 + m_{\overline{D}_i}^2 + 2 m_{Q_i}^2 + m_{u_i}^2 \right )
+\right ] \nonumber \\
+& {} + \frac{64}{45} g_3^2 g_1^2 \left [ 8 \left ( M_1^2 + M_1 M_3 + M_3^2
+\right ) - 3 \sum_{i=1}^3 \left ( m_{d_i}^2 - m_{D_i}^2 +
+m_{\overline{D}_i}^2 + m_{Q_i}^2 - 2 m_{u_i}^2 \right ) \right ] \nonumber \\
+& {} + \frac{8}{3} Q_u g_3^2 g_1'^2 \bigg [ 16 Q_u \left ( M_1'^2 + M_1' M_3 +
+M_3^2 \right ) \nonumber \\
+& {} + 12 \sum_{i=1}^3 \left ( Q_d m_{d_i}^2 + Q_D m_{D_i}^2 +
+Q_{\overline{D}} m_{\overline{D}_i}^2 + 2 Q_Q m_{Q_i}^2 + Q_u m_{u_i}^2
+\right ) \bigg ] \nonumber \\
+& {} + \frac{12}{5} g_2^2 g_1^2 \left [ m_{H'}^2 - m_{\overline{H'}}^2 +
+\sum_{i=1}^3 \left ( m_{H_i^d}^2 - m_{H_i^u}^2 + m_{L_i}^2 - m_{Q_i}^2
+\right ) \right ] \nonumber \\
+& {} + 12 Q_u g_2^2 g_1'^2 \left [ Q_{H'} m_{H'}^2 +
+Q_{\overline{H'}} m_{\overline{H'}}^2 + \sum_{i=1}^3 \left ( Q_1 m_{H_i^d}^2
++ Q_2 m_{H_i^u}^2 + Q_L m_{L_i}^2 + 3 Q_Q m_{Q_i}^2 \right ) \right ]
+\nonumber \\
+& {} + \frac{4}{75} g_1^4 \bigg [ 1261 M_1^2 + 21 m_{H'}^2 +
+3 m_{\overline{H'}}^2 \nonumber \\
+& {} + \sum_{i=1}^3 \left ( 4 m_{d_i}^2 + 12 m_{D_i}^2 +
+4 m_{\overline{D}_i}^2 - 12 m_{e_i}^2 + 21 m_{H_i^d}^2 + 3 m_{H_i^u}^2 +
+21 m_{L_i}^2 + 3 m_{Q_i}^2 + 64 m_{u_i}^2 \right ) \bigg ] \nonumber \\
+& {} + \frac{4}{15} g_1^2g_1'^2 \bigg [ -8 Q_u \big ( 9 Q_d +
+9 Q_{\overline{D}} - 9 Q_D + 9 Q_e - 9 Q_1 + 9 Q_2 + 3Q_{\overline{H'}} -
+3 Q_{H'} - 9 Q_L \nonumber \\
+& {} + 9 Q_Q - 22 Q_u \big ) \left ( M_1^2 + M_1 M_1' + M_1'^2 \right ) +
+12 Q_{H'}^2 m_{H'}^2 - 12 Q_{\overline{H'}}^2 m_{\overline{H'}}^2 \nonumber \\
+& {} + 12 \sum_{i=1}^3 \big ( -Q_d^2 m_{d_i}^2 -
+Q_{\overline{D}}^2 m_{\overline{D}_i}^2 + Q_D^2 m_{D_i}^2 - Q_e^2 m_{e_i}^2 +
+Q_1^2 m_{H_i^d}^2 - Q_2^2 m_{H_i^u}^2 + Q_L^2 m_{L_i}^2 \nonumber \\
+& {} - Q_Q^2 m_{Q_i}^2 + Q_u^2 m_{u_i}^2 \big ) -
+15 Q_{\overline{H'}} Q_u m_{\overline{H'}}^2 + 33 Q_{H'} Q_u m_{H'}^2 +
+Q_u \sum_{i=1}^3 \big ( -18 Q_d m_{d_i}^2 \nonumber \\
+& {} - 18 Q_{\overline{D}} m_{\overline{D}_i}^2 + 30 Q_D m_{D_i}^2 -
+6 Q_e m_{e_i}^2 + 33 Q_1 m_{H_i^d}^2 - 15 Q_2 m_{H_i^u}^2 + 33 Q_L m_{L_i}^2
+\nonumber \\
+& {} - 21 Q_Q m_{Q_i}^2 + 84 Q_u m_{u_i}^2 \big ) \bigg ] +
+8 Q_u g_1'^4 \bigg [ 3 Q_u M_1'^2 \big ( 9 Q_d^2 + 9 Q_{\overline{D}}^2 +
+9 Q_D^2 + 3 Q_e^2 + 6 Q_1^2 \nonumber \\
+& {} + 6 Q_2^2 + 2 Q_{\overline{H'}}^2 + 2 Q_{H'}^2 + 6 Q_L^2 + 18 Q_Q^2 +
+3 Q_S^2 + 11 Q_u^2 \big ) + 2 Q_{H'}^3 m_{H'}^2 +
+2 Q_{\overline{H'}}^3 m_{\overline{H'}}^2 \nonumber \\
+& {} + \sum_{i=1}^3 \big ( 3 Q_d^3 m_{d_i}^2 +
+3 Q_{\overline{D}}^3 m_{\overline{D}_i}^2 + 3 Q_D^3 m_{D_i}^2 +
+Q_e^3 m_{e_i}^2 + 2 Q_1^3 m_{H_i^d}^2 + 2 Q_2^3 m_{H_i^u}^2 +
+2 Q_L^3 m_{L_i}^2 \nonumber \\
+& {} + 6 Q_Q^3 m_{Q_i}^2 + Q_S^3 m_{S_i}^2 + 3 Q_u^3 m_{u_i}^2 \big ) +
+2 Q_u Q_{H'}^2 m_{H'}^2 + 2 Q_u Q_{\overline{H'}}^2 m_{\overline{H'}}^2
+\nonumber \\
+& {} + Q_u \sum_{i=1}^3 \big ( 3 Q_d^2 m_{d_i}^2 +
+3 Q_{\overline{D}}^2 m_{\overline{D}_i}^2 + 3 Q_D^2 m_{D_i}^2 +
+Q_e^2 m_{e_i}^2 + 2 Q_1^2 m_{H_i^d}^2 + 2 Q_2^2 m_{H_i^u}^2 +
+2 Q_L^2 m_{L_i}^2 \nonumber \\
+& {} + 6 Q_Q^2 m_{Q_i}^2 + Q_S^2 m_{S_i}^2 + 3 Q_u^2 m_{u_i}^2 \big )
+\bigg ] , \label{eq:USSMmu222BetaTwoLoop} \\
+b_{m_{u_3}^2}^{(2)} &= 48 y_t^4 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2
+\right ) + 4 y_t^2 y_b^2 \left ( m_{H_u}^2 + m_{H_d}^2 + m_{Q_3}^2 +
+m_{u_3}^2 + m_{d_3}^2 \right ) + 96 y_t^2 a_t^2 \nonumber \\
+& {} + 4 \left ( y_t a_b + y_b a_t \right )^2 + 4 \lambda^2 y_t^2 \left (
+2 m_{H_u}^2 + m_{H_d}^2 + m_S^2 + m_{Q_3}^2 + m_{u_3}^2 \right ) +
+4 \left ( \lambda a_t + y_t a_\lambda \right )^2 \nonumber \\
+& {} - \frac{64}{3} g_3^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 +
+2 M_3^2 \right ) - \frac{64}{3} g_3^2 \left ( a_t^2 - 2 y_t a_t M_3 \right )
+\nonumber \\
+& {} - 12 g_2^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 + 2 M_2^2
+\right ) - 12 g_2^2 \left ( a_t^2 - 2 y_t a_t M_2 \right ) \nonumber \\
+& {} - \frac{52}{15} g_1^2 y_t^2 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 +
+2 M_1^2 \right ) - \frac{52}{15} g_1^2 \left ( a_t^2 - 2 y_t a_t M_1 \right )
+\nonumber \\
+& {} - 8 g_1'^2 y_t^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \left ( m_{H_u}^2
++ m_{Q_3}^2 + m_{u_3}^2 + 2 M_1'^2 \right ) \nonumber \\
+& {} - 8 g_1'^2 \left ( Q_2^2 + Q_Q^2 + Q_u^2 \right ) \left ( a_t^2 -
+2 y_t a_t M_1' \right ) \nonumber \\
+& {} + 4 g_1'^2 y_t^2 \left ( Q_2 + Q_Q + Q_u \right ) \left ( 3 Q_u m_{H_u}^2
++ 3 Q_u m_{Q_3}^2 + 3 Q_u m_{u_3}^2 + \Sigma_1' \right ) \nonumber \\
+& {} + 12 Q_u g_1'^2 a_t^2 \left ( Q_2 + Q_Q + Q_u \right ) +
+12 Q_u g_1'^2 y_b^2 \left ( Q_1 + Q_Q + Q_d \right ) \left ( m_{H_d}^2 +
+m_{Q_3}^2 + m_{d_3}^2 \right ) \nonumber \\
+& {} + 12 Q_u g_1'^2 a_b^2 \left ( Q_1 + Q_Q + Q_d \right ) \nonumber \\
+& {} + 4 Q_u g_1'^2 y_\tau^2 \left ( Q_1 + Q_L + Q_e \right ) \left (
+m_{H_d}^2 + m_{L_3}^2 + m_{e_3}^2 \right ) + 4 Q_u g_1'^2 a_\tau^2 \left (
+Q_1 + Q_L + Q_e \right ) \nonumber \\
+& {} + 2 Q_u g_1'^2 \sum_{i=1}^3 \bigg [ 3 \kappa_i^2 \left ( Q_S + Q_D +
+Q_{\overline{D}} \right ) \left ( m_S^2 + m_{D_i}^2 + m_{\overline{D}_i}^2
+\right ) + 3 a_{\kappa_i}^2 \left ( Q_S + Q_D + Q_{\overline{D}} \right )
+\nonumber \\
+& {} + 2 \lambda_i^2 \left ( Q_1 + Q_2 + Q_S \right ) \left ( m_{H_i^d}^2 +
+m_{H_i^u}^2 + m_S^2 \right ) + 2 a_{\lambda_i}^2 \left ( Q_1 + Q_2 + Q_S
+\right ) \bigg ] \nonumber \\
+& {} - 96 Q_u g_3^2 g_1'^2 M_3^2 \left ( 2 Q_Q + Q_u + Q_d + Q_D +
+Q_{\overline{D}} \right ) \nonumber \\
+& {} - 12 Q_u g_2^2 g_1'^2 M_2^2 \left ( 9 Q_Q + 3 Q_L + 3 Q_1 + 3 Q_2 +
+Q_{H'} + Q_{\overline{H'}} \right ) - \frac{384}{25} g_1^4 \left ( \Sigma_1 +
+4 M_1^2 \right ) \nonumber \\
+& {} + \frac{2}{5} g_1^2 g_1'^2 \big [ 8 M_1'^2 ( 3 Q_d^2 +
+3 Q_{\overline{D}}^2 - 3 Q_D^2 + 3 Q_e^2 - 3 Q_1^2 + 3 Q_2^2 +
+Q_{\overline{H'}}^2 - Q_{H'}^2 - 3 Q_L^2 \nonumber \\
+& {} + 3 Q_Q^2 - 6 Q_u^2 ) + 6 Q_u M_1^2 ( 2 Q_d + 2 Q_{\overline{D}} + 2 Q_D
++ 6 Q_e + 3 Q_1 + 3 Q_2 + Q_{\overline{H'}} + Q_{H'} \nonumber \\
+& {} + 3 Q_L + Q_Q + 8 Q_u ) + \left ( 3 Q_u \Sigma_1 - 2 \Sigma_1^\prime
+\right ) \Sigma_Q^Y \big ] - 4 Q_u g_1'^4 \big [ 2 M_1'^2 ( 9 Q_d^3 + 9 Q_D^3
++ 9 Q_{\overline{D}}^3 \nonumber \\
+& {} + 3 Q_e^3 + 6 Q_1^3 + 6 Q_2^3 + 2 Q_{\overline{H'}}^3 + 2 Q_{H'}^3 +
+6 Q_L^3 + 18 Q_Q^3 + 3 Q_S^3 + 9 Q_u^3 ) \nonumber \\
+& {} + \left ( 6 Q_u M_1'^2 - \Sigma_1^\prime \right ) \Sigma_Q \big ] .
+\label{eq:USSMmu222Ot2Coeff}
 \end{align}

### 2015-04-10 paper/e6ssm-tuning-paper.tex
Corrected caption on chargino plot to match legend on plot

@@
 \caption{Scatter plot of fine tuning vs lightest Higgs mass in the MSSM with
-$m_{\tilde{\chi}^\pm_1} = 200$ GeV shown in light blue (bottom band),
-$m_{\tilde{\chi}^\pm_1} = 500$ GeV in dark blue (middle band), and
-$m_{\tilde{\chi}^\pm_1} = 700$ GeV in dark yellow (top band).}
+$200 \textrm{ GeV} \leq m_{\tilde{\chi}^\pm_1} \leq 400$ GeV shown in light
+blue (bottom band), $500 \textrm{ GeV} \leq m_{\tilde{\chi}^\pm_1} \leq 600$
+GeV in dark blue (middle band), and $700 \textrm { GeV} \leq
+m_{\tilde{\chi}^\pm_1} \leq 800$ GeV in dark yellow (top band).}
 \label{Fig:chargino-plot}

### 2015-05-11 paper/e6ssm-tuning-paper.tex

@@
 coefficient $d$.
+
+The extra $U(1)^\prime$ gauge symmetry may mix with the $U(1)_Y$ gauge
+symmetry associated with hypercharge through gauge kinetic mixing,
+\be
+\mathcal{L}_{mix}^{kin}=-\frac{\sin\chi}{2}F^{Y}_{\mu\nu}F^{N}_{\mu\nu}\,.
+\label{Eq:GKM}
+\ee
+where  $F_{\mu\nu}^Y$ and $F_{\mu\nu}^{N}$ are field strengths associated with the
+$U(1)_Y$ and $U(1)_{N}$ respectively.
+The gauge kinetic mixing can have a significant impact on the phenomenology \cite{Rizzo:1998ut,Salvioni:2009mt,Krauss:2012ku}, which may in particular reduce the $Z^\prime$ limit mass by up to $200$ GeV.
+
+However if the extra $U(1)$ gauge symmetries appears from the breakdown of $E_6$, then $\sin\chi$ should be zero at the GUT scale.
+Nonetheless even if this term is zero at the outset it will still be radiatively generated if the trace of their charges, $\sum_i Q_i^Y Q^\prime_i$, is non-zero.
+In the cases studied here the trace of the charges over states in the complete $27$-plets vanish, but to be consistent with single step gauge coupling unification we also included $\hat{H}^\prime$ and $\hat{\overline{H^\prime}}$ which lead to a non-zero value for $\sum_i Q_i^Y Q^\prime_i $.
+The value induced by this at the EW scale though is rather small as can be seen \footnote{The specific incomplete multiplets we consider here correspond to the third of the four possible embeddings they refer to.} in Fig.~3 of \cite{Rizzo:1998ut}, and this was also checked with two-loop RGEs in the E$_6$SSM \cite{King:2005jy,Athron:2009bs}.
+For this reason and due to the huge expansion in the number of terms in the two-loop RGEs when one allows for gauge kinetic mixing we will neglect this in our analysis here and throughout this paper.
+
+In general though it is possible for gauge kinetic mixing to be much larger as can be the case if one considers an additional $5 + \overline{5}$ pair of SU(5) multiplets \cite{Rizzo:1998ut} or as has been looked in the $U(1)_{B-L}$ \cite{Salvioni:2009mt,Krauss:2012ku}.
+In such a case this will  impact the results in two ways, firstly by altering the $Z^\prime$ limit from experiment and secondly by altering the charges which appear in the EWSB condition, which can be ween from examining Eqs.~\ref{eq:originalE6MZequation}-\ref{eq:ddefn}.
 

### 2015-05-11 paper/e6ssm-tuning-paper.tex
Fixed a typo

@@
 In general though it is possible for gauge kinetic mixing to be much larger as can be the case if one considers an additional $5 + \overline{5}$ pair of SU(5) multiplets \cite{Rizzo:1998ut} or as has been looked in the $U(1)_{B-L}$ \cite{Salvioni:2009mt,Krauss:2012ku}.
-In such a case this will  impact the results in two ways, firstly by altering the $Z^\prime$ limit from experiment and secondly by altering the charges which appear in the EWSB condition, which can be ween from examining Eqs.~\ref{eq:originalE6MZequation}-\ref{eq:ddefn}.
+In such a case this will  impact the results in two ways, firstly by altering the $Z^\prime$ limit from experiment and secondly by altering the charges which appear in the EWSB condition, which can be seen from examining Eqs.~(\ref{eq:originalE6MZequation})-(\ref{eq:ddefn}).
 

### 2015-05-11 paper/e6ssm-tuning-paper.tex
Added missing math delimiters around SU(5), and changed line lengths
to comply with APS guidelines for submissions

@@
 \ee
-where  $F_{\mu\nu}^Y$ and $F_{\mu\nu}^{N}$ are field strengths associated with the
-$U(1)_Y$ and $U(1)_{N}$ respectively.
-The gauge kinetic mixing can have a significant impact on the phenomenology \cite{Rizzo:1998ut,Salvioni:2009mt,Krauss:2012ku}, which may in particular reduce the $Z^\prime$ limit mass by up to $200$ GeV.
-
-However if the extra $U(1)$ gauge symmetries appears from the breakdown of $E_6$, then $\sin\chi$ should be zero at the GUT scale.
-Nonetheless even if this term is zero at the outset it will still be radiatively generated if the trace of their charges, $\sum_i Q_i^Y Q^\prime_i$, is non-zero.
-In the cases studied here the trace of the charges over states in the complete $27$-plets vanish, but to be consistent with single step gauge coupling unification we also included $\hat{H}^\prime$ and $\hat{\overline{H^\prime}}$ which lead to a non-zero value for $\sum_i Q_i^Y Q^\prime_i $.
-The value induced by this at the EW scale though is rather small as can be seen \footnote{The specific incomplete multiplets we consider here correspond to the third of the four possible embeddings they refer to.} in Fig.~3 of \cite{Rizzo:1998ut}, and this was also checked with two-loop RGEs in the E$_6$SSM \cite{King:2005jy,Athron:2009bs}.
-For this reason and due to the huge expansion in the number of terms in the two-loop RGEs when one allows for gauge kinetic mixing we will neglect this in our analysis here and throughout this paper.
-
-In general though it is possible for gauge kinetic mixing to be much larger as can be the case if one considers an additional $5 + \overline{5}$ pair of SU(5) multiplets \cite{Rizzo:1998ut} or as has been looked in the $U(1)_{B-L}$ \cite{Salvioni:2009mt,Krauss:2012ku}.
-In such a case this will  impact the results in two ways, firstly by altering the $Z^\prime$ limit from experiment and secondly by altering the charges which appear in the EWSB condition, which can be seen from examining Eqs.~(\ref{eq:originalE6MZequation})-(\ref{eq:ddefn}).
+where $F_{\mu\nu}^Y$ and $F_{\mu\nu}^{N}$ are field strengths associated
+with the $U(1)_Y$ and $U(1)_{N}$ respectively.  The gauge kinetic mixing
+can have a significant impact on the phenomenology
+\cite{Rizzo:1998ut,Salvioni:2009mt,Krauss:2012ku}, which may in particular
+reduce the $Z^\prime$ limit mass by up to $200$ GeV.
+
+However if the extra $U(1)$ gauge symmetries appears from the breakdown of
+$E_6$, then $\sin\chi$ should be zero at the GUT scale.  Nonetheless even
+if this term is zero at the outset it will still be radiatively generated
+if the trace of their charges, $\sum_i Q_i^Y Q^\prime_i$, is non-zero.  In
+the cases studied here the trace of the charges over states in the complete
+$27$-plets vanish, but to be consistent with single step gauge coupling
+unification we also included $\hat{H}^\prime$ and $\hat{\overline{H^\prime}}$
+which lead to a non-zero value for $\sum_i Q_i^Y Q^\prime_i $.  The value
+induced by this at the EW scale though is rather small as can be seen
+\footnote{The specific incomplete multiplets we consider here correspond
+to the third of the four possible embeddings they refer to.} in Fig.~3 of
+\cite{Rizzo:1998ut}, and this was also checked with two-loop RGEs in the
+E$_6$SSM \cite{King:2005jy,Athron:2009bs}.  For this reason and due to the
+huge expansion in the number of terms in the two-loop RGEs when one allows
+for gauge kinetic mixing we will neglect this in our analysis here and
+throughout this paper.
+
+In general though it is possible for gauge kinetic mixing to be much larger
+as can be the case if one considers an additional $5 + \overline{5}$ pair of
+$SU(5)$ multiplets \cite{Rizzo:1998ut} or as has been looked in the $U(1)_{B-L}$
+\cite{Salvioni:2009mt,Krauss:2012ku}.  In such a case this will impact the
+results in two ways, firstly by altering the $Z^\prime$ limit from experiment
+and secondly by altering the charges which appear in the EWSB condition,
+which can be seen from examining
+Eqs.~(\ref{eq:originalE6MZequation})-(\ref{eq:ddefn}).
 

### 2015-05-11 paper/e6ssm-tuning-paper.tex
Changed wording to address referee point 6

@@
 Here we will focus most on the special case where the gauge symmetry
-is $U(1)_N$, under which the right handed neutrino $\hat{N}^c$ remains
-interaction-less.  This is the case in the E$_6$SSM \cite{King:2005jy,
-King:2005my, Athron:2010zz}, and closely-related variants \cite{Howl:2007zi,
-Braam:2009fi, Braam:2010sy, Hall:2011zq, Nevzorov:2012hs, Athron:2014pua}.
-Since the right handed neutrino has no gauge symmetry protecting it's mass
-from becoming extremely heavy such models may explain the tiny observed
-masses of neutrinos via the see-saw mechanism and the baryon asymmetry in
-the universe via leptogenesis \cite{Hambye:2000bn, King:2008qb, King:2008gw}.
-Recently it has also been studied in the context of electroweak baryogenesis
-\cite{Chao:2014hya}.
+is $U(1)_N$, under which the right handed neutrino $\hat{N}^c$ does not
+participate in gauge interactions.  This is the case in the E$_6$SSM
+\cite{King:2005jy, King:2005my, Athron:2010zz}, and closely-related variants
+\cite{Howl:2007zi, Braam:2009fi, Braam:2010sy, Hall:2011zq, Nevzorov:2012hs,
+Athron:2014pua}.  Since the right handed neutrino has no gauge symmetry
+protecting it's mass from becoming extremely heavy such models may explain
+the tiny observed masses of neutrinos via the see-saw mechanism and the
+baryon asymmetry in the universe via leptogenesis \cite{Hambye:2000bn,
+King:2008qb, King:2008gw}.  Recently it has also been studied in the context
+of electroweak baryogenesis \cite{Chao:2014hya}.
 

### 2015-05-11 paper/e6ssm-tuning-paper.tex
Added comment to address referee point 7

@@
 With three generations of matter $27$-plet representations of $E_6$
-surviving to low energies, the low energy matter content in each generation
-includes, \be
+surviving to low energies, the low energy matter content in each generation,
+after integrating out the heavy right-handed neutrinos, includes, \be
 (\hat{Q}_i, \, \hat{u}^c_i, \, \hat{d}^c_i, \, \hat{L}_i, \, \hat{e}^c_i)

### 2015-05-11 paper/e6ssm-tuning-paper.tex
added refs for two-loop Higgs and tried to address referees point 4 by modifying wording.

@@
 $SU(3)$ gaugino soft mass $M_3$, we have extended the original code to
-make use of the two-loop RGEs generated by SARAH
-\cite{Staub:2009bi, Staub:2010jh, Staub:2012pb, Staub:2013tta} and
-FlexibleSUSY \cite{Athron:2014yba}, which also makes use of SOFTSUSY
-\cite{Allanach:2001kg, Allanach:2013kza}.  The CP-even Higgs masses are
-calculated including the leading one-loop effective potential
+make use of the two-loop RGEs generated by SARAH \cite{Staub:2009bi,
+  Staub:2010jh, Staub:2012pb, Staub:2013tta} and FlexibleSUSY
+\cite{Athron:2014yba}, which also makes use of SOFTSUSY
+\cite{Allanach:2001kg, Allanach:2013kza}.  The CP-even Higgs masses
+are calculated including the leading one-loop effective potential
 contributions given in \cite{Athron:2009bs} and the leading two-loop
-contributions.  To scan over the MSSM parameter space, the equivalent
-MSSM fine tuning expressions were implemented into a modified version
-of SOFTSUSY 3.3.10 \cite{Allanach:2001kg}.  For consistency with the results
-produced in the $E_6$ models, and for computational speed, for our main scans
-only the dominant one- and two-loop corrections to the CP-even Higgs masses
-were included.  Finally, in all of the results below the fine tuning was
-evaluated at the scale $Q = M_{\textrm{SUSY}} =
-\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$ are the
-running $\overline{\textrm{DR}}$ stop masses evaluated at
-$Q = M_{\textrm{SUSY}}$.
+contributions from \cite{King:2005jy} which are a generalsiation of
+the correctsions in the MSSM and NMSSM calculated using effective
+field theory techniques \cite{Carena:1995wu,Ellwanger:1999ji}.  To
+scan over the MSSM parameter space, the equivalent MSSM fine tuning
+expressions were implemented into a modified version of SOFTSUSY
+3.3.10 \cite{Allanach:2001kg}.  For consistency with the results
+produced in the $E_6$ models, and for computational speed, for our
+main scans only the dominant one- and two-loop corrections to the
+CP-even Higgs masses were included.  Finally, in all of the results
+below the fine tuning was evaluated at the scale $Q =
+M_{\textrm{SUSY}} = \sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where
+$m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop
+masses evaluated at $Q = M_{\textrm{SUSY}}$.
 
@@
 10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
-tuning of $\approx 100 - 1000$ and the minimum tuning we see
-consistent with a $125$ GeV Higgs is $\approx 200$, as shown in
+tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error even with leading two loop corrections, which should be considered when interpreting what such results for the miniumum fine tuining in the model, given the discovery of a 125 GeV Higgs.}
+for a $125$ GeV Higgs is $\approx 200$, as shown in
 Fig.~\ref{Fig:mssmstoptuning}.

### 2015-05-11 paper/e6ssm-tuning-paper.tex
Added a comment addressing referee point 1
by mentioning the additional bilinear term and
commenting that it has a negligible impact on
the fine tuning

--- 2015-05-11 paper/e6ssm-tuning-paper.tex
@@
 \SuperField{S}$ the third generation Higgs and SM singlet fields that are
-assumed to acquire non-zero VEVs.
+assumed to acquire non-zero VEVs.  In addition to the $E_6$ preserving terms
+following from Eq.~(\ref{Eq:e6-superpot}), this superpotential also contains a
+single $E_6$ violating bilinear term $\mu' \SuperField{H}'\cdot
+\SuperField{\overline{H'}}$.  This term is responsible for setting the masses of
+the components of the superfields $\SuperField{H}'$,
+$\SuperField{\overline{H'}}$, but it is not involved in the process of EWSB.
+Consequently the impact on the fine tuning of the value of $\mu'$ is much
+smaller than that coming from other sectors, and so can be safely neglected in
+our study. In all of the scans we present below the value of $\mu'$ is fixed
+to $\mu' = 5$ TeV.
 

### 2015-05-11 paper/e6ssm-tuning-paper.tex
emphasise that the leading two loop corrections are for the light Higgs.

--- 2015-05-11 paper/e6ssm-tuning-paper.tex
@@
 are calculated including the leading one-loop effective potential
-contributions given in \cite{Athron:2009bs} and the leading two-loop
-contributions from \cite{King:2005jy} which are a generalsiation of
-the correctsions in the MSSM and NMSSM calculated using effective
-field theory techniques \cite{Carena:1995wu,Ellwanger:1999ji}.  To
-scan over the MSSM parameter space, the equivalent MSSM fine tuning
-expressions were implemented into a modified version of SOFTSUSY
-3.3.10 \cite{Allanach:2001kg}.  For consistency with the results
-produced in the $E_6$ models, and for computational speed, for our
-main scans only the dominant one- and two-loop corrections to the
-CP-even Higgs masses were included.  Finally, in all of the results
-below the fine tuning was evaluated at the scale $Q =
-M_{\textrm{SUSY}} = \sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where
-$m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop
-masses evaluated at $Q = M_{\textrm{SUSY}}$.
+contributions given in \cite{Athron:2009bs} and for the light Higgs we
+use the leading two-loop contributions from \cite{King:2005jy} which
+are a generalsiation of the correctsions in the MSSM and NMSSM
+calculated using effective field theory techniques
+\cite{Carena:1995wu,Ellwanger:1999ji}.  To scan over the MSSM
+parameter space, the equivalent MSSM fine tuning expressions were
+implemented into a modified version of SOFTSUSY 3.3.10
+\cite{Allanach:2001kg}.  For consistency with the results produced in
+the $E_6$ models, and for computational speed, for our main scans only
+the dominant one- and two-loop corrections to the CP-even Higgs masses
+were included.  Finally, in all of the results below the fine tuning
+was evaluated at the scale $Q = M_{\textrm{SUSY}} =
+\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$
+are the running $\overline{\textrm{DR}}$ stop masses evaluated at $Q =
+M_{\textrm{SUSY}}$.
 

### 2015-05-11 paper/e6ssm-tuning-paper.tex
two loop -> two-loop.

@@
 10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
-tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error even with leading two loop corrections, which should be considered when interpreting what such results for the miniumum fine tuining in the model, given the discovery of a 125 GeV Higgs.}
+tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error even with leading two-loop corrections, which should be considered when interpreting what such results for the miniumum fine tuining in the model, given the discovery of a 125 GeV Higgs.}
 for a $125$ GeV Higgs is $\approx 200$, as shown in

### 2015-05-11 paper/e6ssm-tuning-paper.tex
make clear we use one loop DeltaV corrections of Eqn14.

@@
 \left ( \ln \frac{m_t^2}{Q^2} - \frac{3}{2} \right ) \right ] .
+\label{Eq:DeltaV}
 \end{equation}
@@
 The quantities forming the first matrix on the right-hand side, along
-with $M_h^2$, are easily calculated by differentiating the conditions in
-Eq.~(\ref{eq:E6EWSBConditions}) with respect to the VEVs and the running
-parameters.  The remaining derivatives $\partial q_k /\partial p$ must be
-determined using the RGEs.  Once these have been obtained, it is
-straightforward to solve for the $\partial v_i / \partial p$.  The
-sensitivities $\Delta_p$ are then simply linear combinations of the
-$\partial v_i / \partial p$ and $\partial q_k / \partial p$.  The effects of
-radiative corrections may be easily included by including the
-Coleman-Weinberg potential contributions $\Delta V$ in the EWSB conditions.
+with $M_h^2$, are easily calculated by differentiating the conditions
+in Eq.~(\ref{eq:E6EWSBConditions}) with respect to the VEVs and the
+running parameters.  The remaining derivatives $\partial q_k /\partial
+p$ must be determined using the RGEs.  Once these have been obtained,
+it is straightforward to solve for the $\partial v_i / \partial p$.
+The sensitivities $\Delta_p$ are then simply linear combinations of
+the $\partial v_i / \partial p$ and $\partial q_k / \partial p$.  The
+effects of radiative corrections may be easily included by including
+the Coleman-Weinberg potential contributions $\Delta V$ in the EWSB
+conditions.  Here we use the one-loop corrections given in Eq.~\ref{Eq:DeltaV}.
 

### 2015-05-11 paper/e6ssm-tuning-paper.tex
added ref to two-loop Higgs papers from SARAH.

@@
 contributions given in \cite{Athron:2009bs} and for the light Higgs we
-use the leading two-loop contributions from \cite{King:2005jy} which
-are a generalsiation of the correctsions in the MSSM and NMSSM
-calculated using effective field theory techniques
+use the leading two-loop\footnote{Two-loop corrections calculated for
+  a non-minimal SUSY model may now also be obtained from SARAH
+  \cite{Goodsell:2014pla,Goodsell:2015ira}.} contributions from
+\cite{King:2005jy} which are a generalsiation of the correctsions in
+the MSSM and NMSSM calculated using effective field theory techniques
 \cite{Carena:1995wu,Ellwanger:1999ji}.  To scan over the MSSM

### 2015-05-11 paper/e6ssm-tuning-paper.tex
extendeded last footnote.

@@
   a non-minimal SUSY model may now also be obtained from SARAH
-  \cite{Goodsell:2014pla,Goodsell:2015ira}.} contributions from
-\cite{King:2005jy} which are a generalsiation of the correctsions in
-the MSSM and NMSSM calculated using effective field theory techniques
+  \cite{Goodsell:2014pla,Goodsell:2015ira}.  However this was not part
+  of SARAH when we were doing the numerical work in this project and
+  not currently used in FlexibleSUSY.  Such corrections go beyond the
+  required precsion for studying fine tuning here.} contributions from \cite{King:2005jy} which
+are a generalsiation of the correctsions in the MSSM and NMSSM
+calculated using effective field theory techniques
 \cite{Carena:1995wu,Ellwanger:1999ji}.  To scan over the MSSM

### 2015-05-11 paper/e6ssm-tuning-paper.tex
add old references we missed.

@@
   Cvetic:1997ky} and also raise the Higgs mass with new $F$- and
-$D$-terms.  Nonetheless, as was recently demonstrated in the context of
-the exceptional supersymmetric standard model (E$_6$SSM)
+$D$-terms.  Nonetheless, as was recently demonstrated in the context
+of the exceptional supersymmetric standard model (E$_6$SSM)
 \cite{King:2005jy, King:2005my, Athron:2010zz}, such models can still
@@
 associated with the break down of the new $U(1)$ appearing in the
-electroweak symmetry breaking conditions at tree level \cite{Athron:2013ipa}.
-Despite this the constrained version of the E$_6$SSM (cE$_6$SSM)
-\cite{Athron:2009ue, Athron:2009bs} was still found to be significantly
-less tuned than the cMSSM.
+electroweak symmetry breaking conditions at tree level
+\cite{Athron:2013ipa}.  Despite this the constrained version of the
+E$_6$SSM (cE$_6$SSM) \cite{Athron:2009ue, Athron:2009bs} was still
+found to be significantly less tuned than the cMSSM.  It has recently
+been pointed out to us that this tree level fine tuning effect from
+the $Z^\prime$ mass was also considered previously \cite{Drees:1985js}.
 
@@
   CahillRowley:2012rv, Ross:2012nr, Basak:2012bd, Kang:2012sy,
-Athron:2013ipa,Miller:2013jra, Binjonaid:2014oga, Miller:2014jza}.
+  Athron:2013ipa, Boehm:2013qva, Miller:2013jra, Binjonaid:2014oga,
+  Miller:2014jza}.
 

### 2015-05-11 paper/Referee-response.tex
added referee response.

\documentclass[12pt]{article}
\usepackage{fullpage}
\begin{document}
\noindent Dear editor,
\\

\noindent Thanks for sending us the referee responses. We would like to thank
the referee for their helpful comments and questions regarding our
paper. In response we have made changes to our manuscript and feel
these have improved the paper, we therefore hope our paper will now be
accepted for publication in PRD.
\\
\noindent We respond to each point rasied by the referee below, exaplaining
where appropriate what we have done to address it in the paper.

\begin{itemize}
\item Dylan to addresss

\item {\it ``page 11: the authors state that they
  neglect gauge kinetic mixing. In view of possible effects on the LHC
  bounds: is this really justified by the size of the off-diagonal
  entries in the anomalous dimension matrix of the gauge fields? This
  can be in particular important because gauge kinetic mixing and
  additional decays in supersymmetric particles affect the mass bound
  on a Z obtained from LHC and can lower them by up to 200 GeV as has
  been discussed in arXiv:0909.1320, arXiv:1107.1133, arXiv:1205.5780,
  arXiv:1206.3513 or their ref. 102. How would such a shift affect
  their conclusions?''}

This is an important point which we neglected to comment on in our
origional article. In the models we investigate numerically in our
paper, if gauge kinetic mixing is absent at the GUT scale it, the
radiatively induced gauge kinetic mixing will be rather small at the
EW scale as has been shown in the literature.  Therefore we neglected
this. However the referee is correct that it is not the case in all
$U(1)$ extensions and this may have a significant impact on the
$Z^\prime$ mass limit.

To address this issue we have added remarks to the end of section III
explaining why it is small in the models we consider, with referemce
to the previous literature and comment on how it will impact on tuning
results if one considers a case with large gauge kinetic mixing.

\item {\it ``page 13: the author state that the include leading
  two-loop contribu- tions to the Higgs mass. Which are those? Are the
  corresponding contributions to the minimization equations 16
  included and, thus, in their measure of fine-tuning? Concerning the
  two-loop part: in eq.(9) the couplings κi SDi Di are included. As
  the extra D-quarks have to be heavy, one would naively expect that
  they give a sizable contribution to the Higgs masses at the 2-loop
  level, in particular as they take in their numerical studies |λ| ≤
  3. Are those included as well?''}

The referee is correct that we missed the references specifying what
we mean by the leading two-loop corrections, so this was unclear. We
included leading two-loop corrections calculated using effective field
theory methods, which have been generalised from well known
calculations in the MSSM and NMSSM.

To address this issue we have added references pointing out where we
obtained the leading two-loop Higgs corrections from.  For
completeness we also added a footnote pointing readers to the new tool
in the SARAH package which calculates the two-loop corrections to
Higgs masses in non-SUSY models.

We also understand why the referee
may expect $\kappa$ couplings to give a large contribution to the
light Higgs mass, however we find that already at one-loop the
contribution from this coupling is small. The main reason for this is
the fact that singlet mixing with lightest Higgs is highly suppressed
in these models, which is a result of the of the large singlet VEV
required to meet the $Z^\prime$ limit.  The impact of the $\kappa$
couplings on the Higgs mass was also looked at in section 5.2.2 of
hep-ph/0510419.

The leading two loop corrcetions to the effective potential are not
included in our calculation of the fine tuning.  Although the one loop
effective potential corrections are important they are already smaller
than the RGE corrections and so we do not expect the two loop
effective potential corrections to contribute at to the same level as
the terms we include nor one which would significantly alter our
conculusions.

To address this we have added a cooment specifying the precise one
loop corrections we use to the end of the paragraph below Eqn 30.

\item {\it ``on page 15 the authors claim that for MX = 1016 GeV a
  lower bound of 200 for the fine tuning taking mh = 125 GeV. Looking
  at their approximation in the calculation of mh this mass has most
  likely a theory uncertainty of about 10 GeV and, thus, I do not
  understand how they can make such a statement. This also concerns
  their statement on page 17.''}

The referee is correct to point out that there is a large theoretical
uncertainty on the Higgs mass and we did not mean to suggest
otherwise.  When we discuss the fine tuning dependence on the Higgs
mass we are trying to show the qualitative behavior of the tuning
increasing with the Higgs mass and how this changes depending on the
UV cuttoff. We agree that the theoretical error on the Higgs mass is
rather large and that this affects the impact the Higgs mass
measurement has on the minimum tuning that is consistent with
observation.  However such discussions raise difficult questions about
how large the theoretcial error and how to address that in the context
of fine tuning. Therefore we leave such tricky questions to papers
which are focussed on the impact on the Higgs rather than the fine
tuning from the $Z^\prime$ mass which we are interested in here.

To address the referees remarks we have adjusted the wording of the
first comment he refers to and have added a footnote pointing out that
there will be a sizable uncertainty of the Higgs mass.

\item Dylan to address

\item Dylan to address
\item Dylan to address
\item Dylan to address

\end{itemize}

In addition to the changes to address the referees comments we also took the opportuinity to add two references we had missed out when we submitted the article to PRD which are:
\begin{itemize}
\item [19]  M.~Drees, N.~K.~Falck and M.~Gluck,Phys.\ Lett.\ B {\bf 167}, 187 (1986).
\item [46]  C.~Boehm, P.~S.~B.~Dev, A.~Mazumdar and E.~Pukartas, JHEP {\bf 1306}, 113 (2013)
 \end{itemize}

\end{document}

### 2015-05-11 paper/e6ssm-tuning-paper.tex
altered phrasing in fottnote fot grammar and style.

@@
 10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
-tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error even with leading two-loop corrections, which should be considered when interpreting what such results for the miniumum fine tuining in the model, given the discovery of a 125 GeV Higgs.}
+tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error even with leading two-loop corrections, which should be considered when considering what the results imply regarding the miniumum fine tuining in the model consistent with the recent discovery of a 125 GeV Higgs.}
 for a $125$ GeV Higgs is $\approx 200$, as shown in

### 2015-05-11 paper/e6ssm-tuning-paper.tex
add comma.

--- 2015-05-11 paper/e6ssm-tuning-paper.tex
@@
 10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
-tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error even with leading two-loop corrections, which should be considered when interpreting what such results for the miniumum fine tuining in the model, given the discovery of a 125 GeV Higgs.}
+tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error, even with leading two-loop corrections, which should be considered when considering what the results imply regarding the miniumum fine tuining in the model consistent with the recent discovery of a 125 GeV Higgs.}
 for a $125$ GeV Higgs is $\approx 200$, as shown in

### 2015-05-11 paper/e6ssm-tuning-paper.tex
another change to footnote.

--- 2015-05-11 paper/e6ssm-tuning-paper.tex
@@
 10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
-tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error even with leading two-loop corrections, which should be considered when interpreting what such results for the miniumum fine tuining in the model, given the discovery of a 125 GeV Higgs.}
+tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error, even with leading two-loop corrections, which should be considered when thuinking about what the results imply for the miniumum fine tuining in the model consistent with the recent discovery of a 125 GeV Higgs.}
 for a $125$ GeV Higgs is $\approx 200$, as shown in

### 2015-05-11 paper/e6ssm-tuning-paper.tex
spelling.

@@
 10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
-tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error, even with leading two-loop corrections, which should be considered when thuinking about what the results imply for the miniumum fine tuining in the model consistent with the recent discovery of a 125 GeV Higgs.}
+tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error, even with leading two-loop corrections, which should be considered when thinking about what the results imply for the minimum fine tuning in the model consistent with the recent discovery of a 125 GeV Higgs.}
 for a $125$ GeV Higgs is $\approx 200$, as shown in

### 2015-05-11 paper/e6ssm-tuning-paper.tex
Added extra detail about superpotential bilinear term
Changed wording in comment slightly

@@
 following from Eq.~(\ref{Eq:e6-superpot}), this superpotential also contains a
-single $E_6$ violating bilinear term $\mu' \SuperField{H}'\cdot
-\SuperField{\overline{H'}}$.  This term is responsible for setting the masses of
-the components of the superfields $\SuperField{H}'$,
+bilinear term $\mu' \SuperField{H}'\cdot \SuperField{\overline{H'}}$ that
+violates the $E_6$ symmetry but is invariant with respect to the low energy SM
+gauge group and the additional $U(1)'$ symmetry.  This term is responsible for
+setting the masses of the components of the superfields $\SuperField{H}'$,
 $\SuperField{\overline{H'}}$, but it is not involved in the process of EWSB.
 Consequently the impact on the fine tuning of the value of $\mu'$ is much
-smaller than that coming from other sectors, and so can be safely neglected in
-our study. In all of the scans we present below the value of $\mu'$ is fixed
-to $\mu' = 5$ TeV.
+smaller than that coming from other sectors, and so can be safely neglected
+in our study. In all of the scans we present below the value of $\mu'$ is
+fixed to $\mu' = 5$ TeV.
 

### 2015-05-11 paper/Referee-response.tex
Added descriptions of some additional changes for referee report

@@
 \\
-\noindent We respond to each point rasied by the referee below, exaplaining
+\noindent We respond to each point raised by the referee below, explaining
 where appropriate what we have done to address it in the paper.
@@
 \begin{itemize}
-\item Dylan to addresss
+\item {\it ``in eq. (9) an additional parameter $\mu'$ appears.  Where
+does it come from?  Even though it is later fixed to 5 TeV, it is not
+clear if it has any impact on their study?  Even if it has no impact,
+this should be stated somewhere.''}
 
-\item {\it ``page 11: the authors state that they
-  neglect gauge kinetic mixing. In view of possible effects on the LHC
-  bounds: is this really justified by the size of the off-diagonal
-  entries in the anomalous dimension matrix of the gauge fields? This
-  can be in particular important because gauge kinetic mixing and
-  additional decays in supersymmetric particles affect the mass bound
-  on a Z obtained from LHC and can lower them by up to 200 GeV as has
-  been discussed in arXiv:0909.1320, arXiv:1107.1133, arXiv:1205.5780,
-  arXiv:1206.3513 or their ref. 102. How would such a shift affect
-  their conclusions?''}
+The referee is correct to point out that the bilinear coupling $\mu'$ is
+absent from the list of superpotential terms, and is lacking an explanation
+in our original submission. The $\mu'$ term violates the $E_6$ symmetry, as
+it is associated with the incomplete $27$ and $\overline{27}$ to which the
+fields $\hat{H'}$ and $\hat{\overline{H}'}$ belong, but is invariant under
+the Standard Model gauge group and the low energy $U(1)'$ symmetry. For this
+reason it is not given in the superpotential in eq. (5). Additionally, because
+this parameter does not appear in the EWSB conditions the impact from it on
+the fine tuning can be neglected, and so fixing the value of $\mu'$ does not
+impact the results.
+
+To address this, we have added a short discussion immediately
+following eq. (9) that explains the appearance of the additional parameter
+and states that the chosen value of $\mu'$ does not impact on the fine
+tuning in the study.
+
+\item {\it ``page 11: the authors state that they neglect gauge kinetic
+mixing.  In view of possible effects on the LHC bounds: is this really
+justified by the size of the off-diagonal entries in the anomalous
+dimension matrix of the gauge fields?  This can be in particular important
+because gauge kinetic mixing and additional decays in supersymmetric
+particles affect the mass bound on a Z obtained from LHC and can lower them
+by up to 200 GeV as has been discussed in arXiv:0909.1320, arXiv:1107.1133,
+arXiv:1205.5780, arXiv:1206.3513 or their ref. 102.  How would such a shift
+affect their conclusions?''}
 
 This is an important point which we neglected to comment on in our
-origional article. In the models we investigate numerically in our
+original article.  In the models we investigate numerically in our
 paper, if gauge kinetic mixing is absent at the GUT scale it, the
@@
 To address this issue we have added remarks to the end of section III
-explaining why it is small in the models we consider, with referemce
+explaining why it is small in the models we consider, with reference
 to the previous literature and comment on how it will impact on tuning
@@
 \item {\it ``page 13: the author state that the include leading
-  two-loop contribu- tions to the Higgs mass. Which are those? Are the
-  corresponding contributions to the minimization equations 16
-  included and, thus, in their measure of fine-tuning? Concerning the
-  two-loop part: in eq.(9) the couplings κi SDi Di are included. As
-  the extra D-quarks have to be heavy, one would naively expect that
-  they give a sizable contribution to the Higgs masses at the 2-loop
-  level, in particular as they take in their numerical studies |λ| ≤
-  3. Are those included as well?''}
+two-loop contributions to the Higgs mass.  Which are those?  Are the
+corresponding contributions to the minimization equations 16 included
+and, thus, in their measure of fine-tuning?  Concerning the two-loop part:
+in eq. (9) the couplings $\kappa_i S D_i D_i$ are included.  As the extra
+D-quarks have to be heavy, one would naively expect that they give a
+sizable contribution to the Higgs masses at the 2-loop level, in particular
+as they take in their numerical studies $|\lambda| \leq 3$.  Are those
+included as well?''}
 
@@
 
-We also understand why the referee
-may expect $\kappa$ couplings to give a large contribution to the
-light Higgs mass, however we find that already at one-loop the
-contribution from this coupling is small. The main reason for this is
-the fact that singlet mixing with lightest Higgs is highly suppressed
-in these models, which is a result of the of the large singlet VEV
+We also understand why the referee may expect $\kappa$ couplings to give
+a large contribution to the light Higgs mass, however we find that already
+at one-loop the contribution from this coupling is small. The main reason
+for this is the fact that singlet mixing with lightest Higgs is highly
+suppressed in these models, which is a result of the large singlet VEV
 required to meet the $Z^\prime$ limit.  The impact of the $\kappa$
@@
 
-The leading two loop corrcetions to the effective potential are not
-included in our calculation of the fine tuning.  Although the one loop
+The leading two-loop corrcetions to the effective potential are not
+included in our calculation of the fine tuning.  Although the one-loop
 effective potential corrections are important they are already smaller
-than the RGE corrections and so we do not expect the two loop
-effective potential corrections to contribute at to the same level as
+than the RGE corrections and so we do not expect the two-loop
+effective potential corrections to contribute at the same level as
 the terms we include nor one which would significantly alter our
-conculusions.
+conclusions.
 
-To address this we have added a cooment specifying the precise one
+To address this we have added a comment specifying the precise one
 loop corrections we use to the end of the paragraph below Eqn 30.
 
-\item {\it ``on page 15 the authors claim that for MX = 1016 GeV a
-  lower bound of 200 for the fine tuning taking mh = 125 GeV. Looking
-  at their approximation in the calculation of mh this mass has most
+\item {\it ``on page 15 the authors claim that for $M_X = 10^{16}$ GeV a
+lower bound of 200 for the fine tuning taking $m_h = 125$~GeV. Looking
+at their approximation in the calculation of $m_h$ this mass has most
 likely a theory uncertainty of about 10 GeV and, thus, I do not
@@
 increasing with the Higgs mass and how this changes depending on the
-UV cuttoff. We agree that the theoretical error on the Higgs mass is
+UV cutoff.  We agree that the theoretical error on the Higgs mass is
 rather large and that this affects the impact the Higgs mass
@@
 observation.  However such discussions raise difficult questions about
-how large the theoretcial error and how to address that in the context
+how large the theoretical error is and how to address that in the context
 of fine tuning.  Therefore we leave such tricky questions to papers
@@
 
-To address the referees remarks we have adjusted the wording of the
-first comment he refers to and have added a footnote pointing out that
+To address the referee's remarks we have adjusted the wording of the
+first comment referred to and have added a footnote pointing out that
 there will be a sizable uncertainty of the Higgs mass.
 
-\item Dylan to address
+\item {\it ``looking at their table II, one sees that in certain parts of
+the parameter space, $A_t$ can be much larger than the corresponding soft
+masses. This implies the danger of color and charge breaking minima as is
+known for long time. I guess that quite some points are excluded by this.
+Moreover, it seems that they allow also $|\mu|$ to be below 100 GeV which
+would conflict LEP2 data. Are such points really included in their analysis?''}
 
-\item Dylan to address
-\item Dylan to address
-\item Dylan to address
+\item {\it ``page 6: it is stated, that the $\hat N$ field remains
+interactionless. However, to obtain light neutrino masses, there should be
+at least Yukawa interactions.''}
+
+The referee is correct to point out this out, and the sentence should instead
+state that the $\hat N$ field does not participate in the gauge interactions
+under the choice of $U(1)_N$. We have corrected this to address the referee's
+comments.
+
+\item {\it ``page 7: the $\hat N$ field is missing in equation 4''}
+
+The referee's comment indicates that it was unclear the equation describes
+only the low energy matter content in each $27$-plet, once the heavy fields
+have been integrated out. The right-handed neutrinos are assumed to gain
+large masses at some intermediate scale above the electroweak scale in order
+to facilitate a see-saw mechanism for generating light neutrino masses.
+Consequently they do not appear in the low energy matter content, so that
+the equation is correct as currently written.
+
+In order to address this and clarify the discussion, we have added a comment
+immediately before the equation that explicitly mentions that the right-handed
+neutrinos have been integrated out of the low energy theory.
+
+\item {\it ``the journal is missing in ref. 57''}
+
+This has been corrected by adding the journal title.
 
@@
 
-In addition to the changes to address the referees comments we also took the opportuinity to add two references we had missed out when we submitted the article to PRD which are:
+In addition to the changes to address the referee's comments we also took the
+opportunity to add two references we had missed out when we submitted the
+article to PRD which are:
 \begin{itemize}
-\item [19]  M.~Drees, N.~K.~Falck and M.~Gluck,Phys.\ Lett.\ B {\bf 167}, 187 (1986).
-\item [46]  C.~Boehm, P.~S.~B.~Dev, A.~Mazumdar and E.~Pukartas, JHEP {\bf 1306}, 113 (2013)
+\item [19]  M.~Drees, N.~K.~Falck and M.~Gluck, Phys.\ Lett.\ B {\bf 167},
+187 (1986).
+\item [46]  C.~Boehm, P.~S.~B.~Dev, A.~Mazumdar and E.~Pukartas, JHEP
+{\bf 1306}, 113 (2013)
 \end{itemize}

### 2015-05-15 paper/e6ssm-tuning-paper.tex
Fixed typos

@@
 more generally then a model without fine tuning is one where the
-parametrisation is such that all the parameters are observables
+parametrization is such that all the parameters are observables
 \cite{Fichet:2012sn, Kim:2013uxa}.  This provides a quite general
@@
 \end{equation}
-We also include these $U(1)'$ $D$-term contributions in the diagonalised stop
+We also include these $U(1)'$ $D$-term contributions in the diagonalized stop
 masses,
@@
 traditional Barbieri-Giudice measure \cite{Ellis:1986yg, Barbieri:1987fn}.
-A specific model is characterised by a set of $n$ model parameters $\{p_i\}$
+A specific model is characterized by a set of $n$ model parameters $\{p_i\}$
 and is defined at some input scale $M_X$. For a given parameter $p$ in this
@@
 not currently used in FlexibleSUSY.  Such corrections go beyond the
-  required precsion for studying fine tuning here.} contributions from \cite{King:2005jy} which
-are a generalsiation of the correctsions in the MSSM and NMSSM
-calculated using effective field theory techniques
-\cite{Carena:1995wu,Ellwanger:1999ji}.  To scan over the MSSM
+required precision for studying fine tuning here.} contributions from
+\cite{King:2005jy} which are a generalization of the corrections in the
+MSSM and NMSSM calculated using effective field theory techniques
+\cite{Carena:1995wu, Ellwanger:1999ji}.  To scan over the MSSM
 parameter space, the equivalent MSSM fine tuning expressions were
@@
 10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
-tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error, even with leading two-loop corrections, which should be considered when thinking about what the results imply for the minimum fine tuning in the model consistent with the recent discovery of a 125 GeV Higgs.}
-for a $125$ GeV Higgs is $\approx 200$, as shown in
+tuning of $\approx 100 - 1000$ and the minimum tuning we find
+\footnote{Note that in the calculation of the Higgs mass there is a
+significant theoretical error, even with leading two-loop corrections,
+which should be considered when thinking about what the results imply for
+the minimum fine tuning in the model consistent with the recent discovery
+of a 125 GeV Higgs.} for a $125$ GeV Higgs is $\approx 200$, as shown in
 Fig.~\ref{Fig:mssmstoptuning}.
@@
 $m_{Q_3}^2$, $m_{u_3}^2$ and the stop mixing $A_t$.  The relevant
-parameters and ranges that were scanned over are summarised in Table
+parameters and ranges that were scanned over are summarized in Table
 \ref{tab:scanranges}.  In addition to this we also repeat each scan
@@
 
-Finally we want to emphasise that while in Fig.~\ref{Fig:e6ssmvsmssm}
+Finally we want to emphasize that while in Fig.~\ref{Fig:e6ssmvsmssm}
 the E$_6$SSM looks more fine tuned than the MSSM this depends on the
@@
 Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to
-be GUT-normalised.  The expressions in terms of the $E_6$ mixing angle
+be GUT-normalized.  The expressions in terms of the $E_6$ mixing angle
 $\theta$ follow from the charge assignments given in Table \ref{tab:E6charges}

### 2015-05-15 paper/Referee-response.tex
Fixed typos in referee response

@@
 the Standard Model gauge group and the low energy $U(1)'$ symmetry. For this
-reason it is not given in the superpotential in eq. (5). Additionally, because
+reason it is not given in the superpotential in Eq.~(5). Additionally, because
 this parameter does not appear in the EWSB conditions the impact from it on
@@
 To address this, we have added a short discussion immediately
-following eq. (9) that explains the appearance of the additional parameter
+following Eq.~(9) that explains the appearance of the additional parameter
 and states that the chosen value of $\mu'$ does not impact on the fine
@@
 included leading two-loop corrections calculated using effective field
-theory methods, which have been generalised from well known
+theory methods, which have been generalized from well known
 calculations in the MSSM and NMSSM.
@@
 
-The leading two-loop corrcetions to the effective potential are not
+The leading two-loop corrections to the effective potential are not
 included in our calculation of the fine tuning.  Although the one-loop
@@
 To address this we have added a comment specifying the precise one
-loop corrections we use to the end of the paragraph below Eqn 30.
+loop corrections we use to the end of the paragraph below Eq.~(30).
 

### 2015-05-15 paper/e6ssm-tuning-paper.tex
Added comment on LEP bounds and CCB constraints

@@
 both the MSSM and E$_6$SSM, all other soft scalar masses are set
-to $5$ TeV.  Since we work in the third family approximation, taking
-the first and second generation Yukawa couplings to be zero, we also
-assume their associated soft trilinears vanish.  Similarly we take
-$A_b = A_\tau = 0$ GeV.  The $U(1)$ gaugino soft mass $M_1$ was fixed to
-$M_1 = 300$ GeV, and we fix $M_3 = 2000$ GeV.  Additionally, in the
-E$_6$SSM the $U(1)_N$ gaugino soft mass $M_1'$ is held fixed with
-$M_1' = M_1 = 300$ GeV, and $\mu^\prime = 5$ TeV.
+to $5$ TeV.  In order to avoid being in conflict with LEP
+bounds on the chargino mass \cite{Kraan:2005vy} we exclude those points for
+which the lightest chargino mass $m_{\tilde{\chi}^\pm_1} < 104$ GeV\footnote{In
+fact this requirement has no impact on the bounds we find for the fine tuning
+below. We found that, in the parameter space covered by our scans, including
+points that violate the LEP bound does not lower the minimum fine tuning that
+is obtained}.  We also impose several theoretical constraints on the points
+included in the analysis.  In particular, we require a valid spectrum with no
+tachyonic states to exclude points which would have an unrealistic minimum,
+for example due to the appearance of charge or colour breaking (CCB) minima.
+As a further requirement in the MSSM we exclude any points that do not satisfy
+the well known CCB constraint \cite{Casas:1995pd},
+\begin{equation} \label{eq:MSSMCCBconstraint}
+A_t^2 < 3 \left ( \mu^2 + m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 \right ),
+\end{equation}
+or the unbounded from below (UFB) constraint,
+\begin{equation} \label{eq:MSSMUFBconstraint}
+m_{H_d}^2 + m_{H_u}^2 + 2 \mu^2 > 2 B \mu .
+\end{equation}
+We work in the third family approximation, taking the first and second
+generation Yukawa couplings to be zero, and we also assume their associated
+soft trilinears vanish.  Similarly we take $A_b = A_\tau = 0$ GeV.  The $U(1)$
+gaugino soft mass $M_1$ was fixed to $M_1 = 300$ GeV, and we fix $M_3 = 2000$
+GeV.  Additionally, in the E$_6$SSM the $U(1)_N$ gaugino soft mass $M_1'$ is
+held fixed with $M_1' = M_1 = 300$ GeV, and $\mu^\prime = 5$ TeV.
 

### 2015-05-15 paper/e6ssm-tuning-paper.tex
Fixed typo

@@
 tachyonic states to exclude points which would have an unrealistic minimum,
-for example due to the appearance of charge or colour breaking (CCB) minima.
+for example due to the appearance of charge or color breaking (CCB) minima.
 As a further requirement in the MSSM we exclude any points that do not satisfy

### 2015-05-15 paper/Referee-response.tex
Addressed point 5 in referee report

@@
 
+For parts of the parameter space scanned the referee is correct to point
+out that there is a danger of color or charge breaking minima, and that
+the range of values for $\mu$ scanned over includes values that would be in
+conflict with experimental limits.  In our analysis we excluded points
+that may lead to such minima by removing those which have tachyons in the
+spectrum, and for the MSSM we have additionally checked that included points
+satisfy known conditions for the dangerous minima to be avoided.  This however
+was not commented on in our submission.  Regarding the LEP2 data and chargino
+mass bounds, in Figures 2 and 4 the chargino mass limit was not imposed.
+Instead the impact of the chargino bounds is explored in Figure 2.  As can
+be inferred from this figure, and we confirmed that this is the case in
+detail for all of the models considered, excluding low mass charginos does not
+change the lower bound on fine tuning that is obtained.  Nevertheless the
+referee is correct in pointing out that it is more consistent to present only
+those points that are allowed by the experimental limits, as we have already
+done for other limits on sparticle masses.
+
+To address this point, we have updated Figures 2 and 4 to exclude those points
+that would conflict with the LEP2 data.  As noted above, this does not alter
+the results at all.  In addition, a short discussion has been added on page 17,
+prior to Table II, in which the constraints that are applied to the analysis
+are clarified.  In particular, we explicitly state that points violating the
+LEP chargino limits are now excluded from the analysis.  This is accompanied
+by a footnote pointing out that for the region of parameter space studied
+whether or not this constraint is applied does not in fact impact the results.
+We also explain that in order to exclude points that may have color and charge
+breaking minima we only allow points that do not lead to tachyonic sparticle
+masses and, in the MSSM, that satisfy the traditional conditions in the
+literature for color or charge breaking minima to be avoided.
+
 \item {\it ``page 6: it is stated, that the $\hat N$ field remains

### 2015-05-16 paper/Referee-response.tex
Modified comment on LEP bounds in paper and referee response

--- 2015-05-15 paper/Referee-response.tex
@@
 
+For parts of the parameter space scanned the referee is correct to point
+out that there is a danger of color or charge breaking minima, and that
+the range of values for $\mu$ scanned over includes values that would be in
+conflict with experimental limits.  In our analysis we excluded points
+that may lead to such minima by removing those which have tachyons in the
+spectrum, and for the MSSM we have additionally checked that included points
+satisfy known conditions for the dangerous minima to be avoided.  This however
+was not commented on in our submission.  Regarding the LEP2 data and chargino
+mass bounds, in Figures 2 and 4 the chargino mass limit was not imposed.  This
+is because the LEP bounds are not severe enough to effect the
+minimum obtainable fine tuning in the models we looked at.  On the other hand,
+much higher limits set at the LHC can have a meaningful impact, as is
+illustrated in  Figure 2.  Nevertheless the referee is correct in pointing out
+that this should be addressed in the text.
+
+To address these points, a short comment has been added on page 17,
+prior to Table II, in which the theoretical constraints that are applied to
+the analysis are clarified.  In particular, we explain that in order to
+exclude points that may have color and charge breaking minima we only allow
+points that do not lead to tachyonic sparticle masses and, in the MSSM, that
+satisfy the traditional conditions in the literature for color or charge
+breaking minima to be avoided.  In addition to this, we have added a remark
+on page 18 to point out that imposing the LEP bound does not have an effect
+on the results, but that LHC limits can have a significant impact.  We also
+have added a footnote stating that it is for this reason the LEP bounds are
+not imposed in Figures 2 and 4.
+
 \item {\it ``page 6: it is stated, that the $\hat N$ field remains

### 2015-05-16 paper/e6ssm-tuning-paper.tex
Modified comment on LEP bounds in paper and referee response

@@
 both the MSSM and E$_6$SSM, all other soft scalar masses are set
-to $5$ TeV.  In order to avoid being in conflict with LEP
-bounds on the chargino mass \cite{Kraan:2005vy} we exclude those points for
-which the lightest chargino mass $m_{\tilde{\chi}^\pm_1} < 104$ GeV\footnote{In
-fact this requirement has no impact on the bounds we find for the fine tuning
-below. We found that, in the parameter space covered by our scans, including
-points that violate the LEP bound does not lower the minimum fine tuning that
-is obtained}.  We also impose several theoretical constraints on the points
+to $5$ TeV.  We also impose several theoretical constraints on the points
 included in the analysis.  In particular, we require a valid spectrum with no
@@
 directly constrain the $\mu$ parameter (or effective $\mu$ parameter
-in these $U(1)$ extensions).  However the chargino limits from the LHC
-depend on whether there are light sleptons or sneutrinos and the mass
-difference between the lightest chargino and lightest neutralino.
+in these $U(1)$ extensions).  The LEP bound \cite{Kraan:2005vy} on
+chargino masses, excluding $m_{\tilde{\chi}^\pm_1} \lesssim 104$ GeV, implies
+that $|\mu|$ should only be greater than $\sim 100$ GeV, which is not
+substantially larger than $M_Z$.  Consequently the bound from LEP is not
+high enough to have an impact on the fine tuning obtained in the models and
+parameter space regions that we have studied, as we have checked explicitly
+\footnote{It is for this reason that we did not require the LEP bounds be
+satisfied for the points shown in Figure \ref{Fig:e6ssmvsmssm}
+and in Figure \ref{Fig:othere6modelsvsmssm} below.}.  Significantly larger
+lower bounds on the $\mu$ parameter, and therefore on the fine tuning, may
+arise from chargino limits coming from LHC searches.  However the chargino
+limits from the LHC depend on whether there are light sleptons or sneutrinos
+and the mass difference between the lightest chargino and lightest neutralino.
 Current limits placed by CMS and ATLAS extend up to

### 2015-05-17 paper/e6ssm-tuning-paper.tex
removed spaces bewtween words and footnotes as this looked weird.

@@
 
-However if the extra $U(1)$ gauge symmetries appears from the breakdown of
-$E_6$, then $\sin\chi$ should be zero at the GUT scale.  Nonetheless even
-if this term is zero at the outset it will still be radiatively generated
-if the trace of their charges, $\sum_i Q_i^Y Q^\prime_i$, is non-zero.  In
-the cases studied here the trace of the charges over states in the complete
-$27$-plets vanish, but to be consistent with single step gauge coupling
-unification we also included $\hat{H}^\prime$ and $\hat{\overline{H^\prime}}$
-which lead to a non-zero value for $\sum_i Q_i^Y Q^\prime_i $.  The value
-induced by this at the EW scale though is rather small as can be seen
-\footnote{The specific incomplete multiplets we consider here correspond
-to the third of the four possible embeddings they refer to.} in Fig.~3 of
-\cite{Rizzo:1998ut}, and this was also checked with two-loop RGEs in the
-E$_6$SSM \cite{King:2005jy,Athron:2009bs}.  For this reason and due to the
-huge expansion in the number of terms in the two-loop RGEs when one allows
-for gauge kinetic mixing we will neglect this in our analysis here and
-throughout this paper.
+However if the extra $U(1)$ gauge symmetries appears from the
+breakdown of $E_6$, then $\sin\chi$ should be zero at the GUT scale.
+Nonetheless even if this term is zero at the outset it will still be
+radiatively generated if the trace of their charges, $\sum_i Q_i^Y
+Q^\prime_i$, is non-zero.  In the cases studied here the trace of the
+charges over states in the complete $27$-plets vanish, but to be
+consistent with single step gauge coupling unification we also
+included $\hat{H}^\prime$ and $\hat{\overline{H^\prime}}$ which lead
+to a non-zero value for $\sum_i Q_i^Y Q^\prime_i $.  The value induced
+by this at the EW scale though is rather small as can be
+seen\footnote{The specific incomplete multiplets we consider here
+  correspond to the third of the four possible embeddings they refer
+  to.} in Fig.~3 of \cite{Rizzo:1998ut}, and this was also checked
+with two-loop RGEs in the E$_6$SSM \cite{King:2005jy,Athron:2009bs}.
+For this reason and due to the huge expansion in the number of terms
+in the two-loop RGEs when one allows for gauge kinetic mixing we will
+neglect this in our analysis here and throughout this paper.
 
@@
 To illustrate this, in the left panel of Fig.~\ref{Fig:mssmstoptuning}
-we show the variation in fine tuning for $M_X = 20$ TeV, $50$ TeV, $100$
-TeV and $10^{16}$ GeV when we scan over the stop masses and mixing,
-with $500 \textrm{ GeV} \leq m_{Q_3} , m_{u_3} \leq 10 \textrm{ TeV}$ and
-$-3810\textrm{ GeV} \leq A_t \leq -20 \textrm{ GeV}$.  The remaining
-parameters we fix such that at $M_{\rm SUSY}$ they have the values
-$\mu = -97.5$ GeV, $B = -84.8$ GeV, $M_1 = 92.1$ GeV, $M_2 = 95.9$ GeV,
-$M_3 = 352$ GeV, $A_b = -117.9$ GeV, $A_\tau = -7.8$ GeV, $m_{L_i} = 400$ GeV,
-$m_{e_i} = 204$ GeV, $m_{Q_{1,2}} = 438$ GeV, $m_{u_{1,2}} = 436$ GeV and
-$m_{d_i} = 438$ GeV ($i = 1 , 2 , 3$).  Here we denote by $M_1$, $M_2$ and
-$M_3$ the soft gaugino masses for $U(1)$, $SU(2)$ and $SU(3)$, while $A_b$ and
-$A_\tau$ are soft trilinear couplings and the $m_\phi$ are soft scalar
-masses for the indicated fields.  The soft bilinear coupling $B$ is defined
-such that at tree level the mass of the CP-odd MSSM Higgs boson reads
-$m_A^2 = 2 B \mu / \sin 2\beta$.  All off-diagonal couplings and scalar masses
-are set to zero, as are the first and second generation Yukawa couplings
-and soft trilinears.  Although we should stress that making
-this choice will lead to a spectrum which is in conflict with the LHC
-limits, doing so ensures that fine tuning due to the other parameters
-is small, so that we avoid washing out the fine tuning impact of the
-stops when the tuning is small\footnote{For models in which the
-spectrum is heavier, when the stop masses are small the fine tuning
-reaches a lower bound imposed by other heavier parameters.} as can
-be the case when the stop masses are less than 1 TeV.  Note that the
-Higgs mass is also allowed to vary in this scan, as shown in the right
-panel of Fig.~\ref{Fig:mssmstoptuning}.  This illustrates the tuning
-problem which people have been worrying about since the discovery of
-the 125 GeV Higgs boson as we see that raising the stop masses is also
-pushing up the Higgs mass, meaning that heavier Higgs masses require
-more fine tuning.  However for a low value of the UV scale this tuning
-is not so severe unless the stops are very heavy, and a 125 GeV Higgs
-can be obtained without much tuning in this unrealistic case where we
-have minimized other sources of tuning.  On the other hand the tuning
-becomes more severe as we increase the cutoff such that for $M_X =
-10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
-tuning of $\approx 100 - 1000$ and the minimum tuning we find
-\footnote{Note that in the calculation of the Higgs mass there is a
-significant theoretical error, even with leading two-loop corrections,
-which should be considered when thinking about what the results imply for
-the minimum fine tuning in the model consistent with the recent discovery
-of a 125 GeV Higgs.} for a $125$ GeV Higgs is $\approx 200$, as shown in
-Fig.~\ref{Fig:mssmstoptuning}.
+we show the variation in fine tuning for $M_X = 20$ TeV, $50$ TeV,
+$100$ TeV and $10^{16}$ GeV when we scan over the stop masses and
+mixing, with $500 \textrm{ GeV} \leq m_{Q_3} , m_{u_3} \leq 10
+\textrm{ TeV}$ and $-3810\textrm{ GeV} \leq A_t \leq -20 \textrm{
+  GeV}$.  The remaining parameters we fix such that at $M_{\rm SUSY}$
+they have the values $\mu = -97.5$ GeV, $B = -84.8$ GeV, $M_1 = 92.1$
+GeV, $M_2 = 95.9$ GeV, $M_3 = 352$ GeV, $A_b = -117.9$ GeV, $A_\tau =
+-7.8$ GeV, $m_{L_i} = 400$ GeV, $m_{e_i} = 204$ GeV, $m_{Q_{1,2}} =
+438$ GeV, $m_{u_{1,2}} = 436$ GeV and $m_{d_i} = 438$ GeV ($i = 1 , 2
+, 3$).  Here we denote by $M_1$, $M_2$ and $M_3$ the soft gaugino
+masses for $U(1)$, $SU(2)$ and $SU(3)$, while $A_b$ and $A_\tau$ are
+soft trilinear couplings and the $m_\phi$ are soft scalar masses for
+the indicated fields.  The soft bilinear coupling $B$ is defined such
+that at tree level the mass of the CP-odd MSSM Higgs boson reads
+$m_A^2 = 2 B \mu / \sin 2\beta$.  All off-diagonal couplings and
+scalar masses are set to zero, as are the first and second generation
+Yukawa couplings and soft trilinears.  Although we should stress that
+making this choice will lead to a spectrum which is in conflict with
+the LHC limits, doing so ensures that fine tuning due to the other
+parameters is small, so that we avoid washing out the fine tuning
+impact of the stops when the tuning is small\footnote{For models in
+  which the spectrum is heavier, when the stop masses are small the
+  fine tuning reaches a lower bound imposed by other heavier
+  parameters.} as can be the case when the stop masses are less than 1
+TeV.  Note that the Higgs mass is also allowed to vary in this scan,
+as shown in the right panel of Fig.~\ref{Fig:mssmstoptuning}.  This
+illustrates the tuning problem which people have been worrying about
+since the discovery of the 125 GeV Higgs boson as we see that raising
+the stop masses is also pushing up the Higgs mass, meaning that
+heavier Higgs masses require more fine tuning.  However for a low
+value of the UV scale this tuning is not so severe unless the stops
+are very heavy, and a 125 GeV Higgs can be obtained without much
+tuning in this unrealistic case where we have minimized other sources
+of tuning.  On the other hand the tuning becomes more severe as we
+increase the cutoff such that for $M_X = 10^{16}$ GeV a lightest stop
+masses of $1-3$ TeV can result in a fine tuning of $\approx 100 -
+1000$ and the minimum tuning we find\footnote{Note that in the
+  calculation of the Higgs mass there is a significant theoretical
+  error, even with leading two-loop corrections, which should be
+  considered when thinking about what the results imply for the
+  minimum fine tuning in the model consistent with the recent
+  discovery of a 125 GeV Higgs.} for a $125$ GeV Higgs is $\approx
+200$, as shown in Fig.~\ref{Fig:mssmstoptuning}.
 
@@
 high enough to have an impact on the fine tuning obtained in the models and
-parameter space regions that we have studied, as we have checked explicitly
-\footnote{It is for this reason that we did not require the LEP bounds be
+parameter space regions that we have studied, as we have checked explicitly\footnote{It is for this reason that we did not require the LEP bounds be
 satisfied for the points shown in Figure \ref{Fig:e6ssmvsmssm}
@@
 still do lead to $\Delta_{m_{H_u}^2}$ increasing with the cutoff
-through the usual mechanism \footnote{Wherein $m_{H_u}^2(M_{SUSY})$
+through the usual mechanism\footnote{Wherein $m_{H_u}^2(M_{SUSY})$
 receives a positive contribution to it's mass from $m_{H_u}^2(M_X)$
@@
 to be generated during RGE evolution and this is the case in the
-models we consider here \footnote{In $E_6$ inspired models with only
+models we consider here\footnote{In $E_6$ inspired models with only
 complete $27$-plet matter multiplets this trace would vanish.
@@
 to denote the trace over the $U(1)'$ charges, along
-with \footnote{The first of these is the trace which is assumed to vanish in
+with\footnote{The first of these is the trace which is assumed to vanish in
 \cite{Martin:1993zk}.  Although we use the \texttt{NoU1Mixing} flag to neglect

### 2015-05-17 paper/e6ssm-tuning-paper.tex
simplified some of the statements I added.

@@
 E$_6$SSM (cE$_6$SSM) \cite{Athron:2009ue, Athron:2009bs} was still
-found to be significantly less tuned than the cMSSM.  It has recently
-been pointed out to us that this tree level fine tuning effect from
-the $Z^\prime$ mass was also considered previously \cite{Drees:1985js}.
+found to be significantly less tuned than the cMSSM.  Tree level
+fine tuning from the $Z^\prime$ mass was also considered
+previously \cite{Drees:1985js}.
 
@@
 \label{Eq:GKM}
-\ee
-where $F_{\mu\nu}^Y$ and $F_{\mu\nu}^{N}$ are field strengths associated
-with the $U(1)_Y$ and $U(1)_{N}$ respectively.  The gauge kinetic mixing
-can have a significant impact on the phenomenology
-\cite{Rizzo:1998ut,Salvioni:2009mt,Krauss:2012ku}, which may in particular
-reduce the $Z^\prime$ limit mass by up to $200$ GeV.
+\ee where $F_{\mu\nu}^Y$ and $F_{\mu\nu}^{N}$ are field strengths
+associated with the $U(1)_Y$ and $U(1)_{N}$ respectively.  The gauge
+kinetic mixing can have a significant impact on the phenomenology
+\cite{Rizzo:1998ut,Salvioni:2009mt,Krauss:2012ku}, and may reduce the
+$Z^\prime$ mass limit.
 
@@
   a non-minimal SUSY model may now also be obtained from SARAH
-\cite{Goodsell:2014pla,Goodsell:2015ira}.  However this was not part
-of SARAH when we were doing the numerical work in this project and
-not currently used in FlexibleSUSY.  Such corrections go beyond the
-required precision for studying fine tuning here.} contributions from
-\cite{King:2005jy} which are a generalization of the corrections in the
-MSSM and NMSSM calculated using effective field theory techniques
-\cite{Carena:1995wu, Ellwanger:1999ji}.  To scan over the MSSM
-parameter space, the equivalent MSSM fine tuning expressions were
-implemented into a modified version of SOFTSUSY 3.3.10
-\cite{Allanach:2001kg}.  For consistency with the results produced in
-the $E_6$ models, and for computational speed, for our main scans only
-the dominant one- and two-loop corrections to the CP-even Higgs masses
-were included.  Finally, in all of the results below the fine tuning
-was evaluated at the scale $Q = M_{\textrm{SUSY}} =
+  \cite{Goodsell:2014pla,Goodsell:2015ira}.  However this was not
+  available when the numerical work for this paper was carried out and
+  such corrections go beyond the required precision for studying fine
+  tuning here.} contributions from \cite{King:2005jy} which are a
+generalization of the corrections in the MSSM and NMSSM calculated
+using effective field theory techniques \cite{Carena:1995wu,
+  Ellwanger:1999ji}.  To scan over the MSSM parameter space, the
+equivalent MSSM fine tuning expressions were implemented into a
+modified version of SOFTSUSY 3.3.10 \cite{Allanach:2001kg}.  For
+consistency with the results produced in the $E_6$ models, and for
+computational speed, for our main scans only the dominant one- and
+two-loop corrections to the CP-even Higgs masses were included.
+Finally, in all of the results below the fine tuning was evaluated at
+the scale $Q = M_{\textrm{SUSY}} =
 \sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$

### 2015-05-17 paper/Referee-response.tex
clarify more why we don't inlcude LEP limit.

@@
 increasing with the Higgs mass and how this changes depending on the
-UV cutoff.  We agree that the theoretical error on the Higgs mass is
-rather large and that this affects the impact the Higgs mass
-measurement has on the minimum tuning that is consistent with
-observation.  However such discussions raise difficult questions about
-how large the theoretical error is and how to address that in the context
-of fine tuning.  Therefore we leave such tricky questions to papers
-which are focussed on the impact on the Higgs rather than the fine
-tuning from the $Z^\prime$ mass which we are interested in here.
+UV cutoff, using the numbers we quote to illustrate this.  We agree
+that the theoretical error on the Higgs mass is rather large and that
+this affects the impact the Higgs mass measurement has on the minimum
+tuning that is consistent with observation.  However such discussions
+raise difficult questions about how large the theoretical error is and
+how to address that in the context of fine tuning.  Therefore we leave
+such tricky questions to papers which are focussed on the impact on
+the Higgs rather than the fine tuning from the $Z^\prime$ mass which
+we are interested in here.
 
@@
 
-For parts of the parameter space scanned the referee is correct to point
-out that there is a danger of color or charge breaking minima, and that
-the range of values for $\mu$ scanned over includes values that would be in
-conflict with experimental limits.  In our analysis we excluded points
-that may lead to such minima by removing those which have tachyons in the
-spectrum, and for the MSSM we have additionally checked that included points
-satisfy known conditions for the dangerous minima to be avoided.  This however
-was not commented on in our submission.  Regarding the LEP2 data and chargino
-mass bounds, in Figures 2 and 4 the chargino mass limit was not imposed.  This
-is because the LEP bounds are not severe enough to effect the
-minimum obtainable fine tuning in the models we looked at.  On the other hand,
-much higher limits set at the LHC can have a meaningful impact, as is
-illustrated in  Figure 2.  Nevertheless the referee is correct in pointing out
-that this should be addressed in the text.
+For parts of the parameter space scanned the referee is correct to
+point out that there is a danger of color or charge breaking minima,
+and that the range of values for $\mu$ scanned over includes values
+that would be in conflict with experimental limits.  In our analysis
+we excluded points that may lead to such minima by removing those
+which have tachyons in the spectrum, and for the MSSM we have
+additionally checked that included points satisfy known conditions for
+the dangerous minima to be avoided.  This however was not commented on
+in our submission.  Regarding the LEP2 data and chargino mass bounds,
+in Figures 2 and 4 the chargino mass limit was not imposed.  This is
+because the LEP bounds are not severe enough to effect the minimum
+obtainable fine tuning in the models we looked at and we wanted to
+consider the impact of the chargino mass seperately in Figure 3. There
+we show that much higher limits set at the LHC can have a meaningful
+impact.  Nevertheless the referee is
+correct in pointing out that this should be addressed in the text.
 

### 2015-05-17 paper/Referee-response.tex
Made changes to discussion about CCB minima and chargino limits
by deleting footnote explaining that points below the LEP limit
are included in main tuning plot, and removed comment about
additional MSSM check for CCB minima or UFB potential. Updated
referee response to match.

@@
 we excluded points that may lead to such minima by removing those
-which have tachyons in the spectrum, and for the MSSM we have
-additionally checked that included points satisfy known conditions for
-the dangerous minima to be avoided.  This however was not commented on
+which have tachyons in the spectrum.  This however was not commented on
 in our submission.  Regarding the LEP2 data and chargino mass bounds,
 in Figures 2 and 4 the chargino mass limit was not imposed.  This is
-because the LEP bounds are not severe enough to effect the minimum
+because the LEP bounds are not severe enough to affect the minimum
 obtainable fine tuning in the models we looked at and we wanted to
-consider the impact of the chargino mass seperately in Figure 3. There
+consider the impact of the chargino mass separately in Figure 3.  There
 we show that much higher limits set at the LHC can have a meaningful
-impact.  Nevertheless the referee is
-correct in pointing out that this should be addressed in the text.
+impact.  Nevertheless the referee is correct in pointing out that this should
+be addressed in the text.
 
@@
 exclude points that may have color and charge breaking minima we only allow
-points that do not lead to tachyonic sparticle masses and, in the MSSM, that
-satisfy the traditional conditions in the literature for color or charge
-breaking minima to be avoided.  In addition to this, we have added a remark
-on page 18 to point out that imposing the LEP bound does not have an effect
-on the results, but that LHC limits can have a significant impact.  We also
-have added a footnote stating that it is for this reason the LEP bounds are
-not imposed in Figures 2 and 4.
+points that do not lead to tachyonic sparticle masses.  In addition to this,
+we have added a remark on page 18 to point out that imposing the LEP bound
+does not have an effect on the results, but that LHC limits can have a
+significant impact.
 

### 2015-05-17 paper/e6ssm-tuning-paper.tex
Made changes to discussion about CCB minima and chargino limits
by deleting footnote explaining that points below the LEP limit
are included in main tuning plot, and removed comment about
additional MSSM check for CCB minima or UFB potential. Updated
referee response to match.

@@
 for example due to the appearance of charge or color breaking (CCB) minima.
-As a further requirement in the MSSM we exclude any points that do not satisfy
-the well known CCB constraint \cite{Casas:1995pd},
-\begin{equation} \label{eq:MSSMCCBconstraint}
-A_t^2 < 3 \left ( \mu^2 + m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 \right ),
-\end{equation}
-or the unbounded from below (UFB) constraint,
-\begin{equation} \label{eq:MSSMUFBconstraint}
-m_{H_d}^2 + m_{H_u}^2 + 2 \mu^2 > 2 B \mu .
-\end{equation}
 We work in the third family approximation, taking the first and second
@@
 high enough to have an impact on the fine tuning obtained in the models and
-parameter space regions that we have studied, as we have checked explicitly\footnote{It is for this reason that we did not require the LEP bounds be
-satisfied for the points shown in Figure \ref{Fig:e6ssmvsmssm}
-and in Figure \ref{Fig:othere6modelsvsmssm} below.}.  Significantly larger
-lower bounds on the $\mu$ parameter, and therefore on the fine tuning, may
-arise from chargino limits coming from LHC searches.  However the chargino
-limits from the LHC depend on whether there are light sleptons or sneutrinos
-and the mass difference between the lightest chargino and lightest neutralino.
-Current limits placed by CMS and ATLAS extend up to
+parameter space regions that we have studied, as we have checked explicitly.
+Significantly larger lower bounds on the $\mu$ parameter, and therefore on the
+fine tuning, may arise from chargino limits coming from LHC searches.  However
+the chargino limits from the LHC depend on whether there are light sleptons or
+sneutrinos and the mass difference between the lightest chargino and lightest
+neutralino.  Current limits placed by CMS and ATLAS extend up to
 $m_{\tilde{\chi}^\pm_1} \approx 700 - 740$ GeV if there are light

### 2015-05-20 paper/e6ssm-tuning-paper.tex
Deleted sentence that is not needed

@@
 both the MSSM and E$_6$SSM, all other soft scalar masses are set
-to $5$ TeV.  We also impose several theoretical constraints on the points
-included in the analysis.  In particular, we require a valid spectrum with no
+to $5$ TeV.  We require a valid spectrum with no
 tachyonic states to exclude points which would have an unrealistic minimum,

### 2015-05-21 paper/Referee-response.tex
Corrected minor typos

@@
 
-\noindent Thanks for sending us the referee responses. We would like to thank
-the referee for their helpful comments and questions regarding our
-paper. In response we have made changes to our manuscript and feel
-these have improved the paper, we therefore hope our paper will now be
-accepted for publication in PRD.
+\noindent Thank you for sending us the referee report.  We would like to
+sincerely thank the referee for their very helpful comments and questions
+about our paper.  In response to each of these we have made appropriate
+changes to our manuscript and feel these have improved the paper.  We
+therefore hope that our paper will now be considered acceptable for
+publication in Physical Review D.
 \\
 \noindent We respond to each point raised by the referee below, explaining
-where appropriate what we have done to address it in the paper.
+where appropriate what changes we have made in the paper to address the
+referee's concerns.
 

### 2015-05-21 paper/e6ssm-tuning-paper.tex
Corrected minor typos

@@
 more generally then a model without fine tuning is one where the
-parametrization is such that all the parameters are observables
+parameterization is such that all the parameters are observables
 \cite{Fichet:2012sn, Kim:2013uxa}.  This provides a quite general
@@
 seen\footnote{The specific incomplete multiplets we consider here
-  correspond to the third of the four possible embeddings they refer
-  to.} in Fig.~3 of \cite{Rizzo:1998ut}, and this was also checked
+  correspond to the third of the four possible embeddings referred to in
+  Ref.~\cite{Rizzo:1998ut}.} in Fig.~3 of Ref.~\cite{Rizzo:1998ut}, and this
+was also checked
 with two-loop RGEs in the E$_6$SSM \cite{King:2005jy,Athron:2009bs}.
@@
 As discussed in the introduction many recent papers interested in
-natural supersymmetry have focussed on light stops, with much
+natural supersymmetry have focused on light stops, with much
 theoretical effort to find models where it is easier to get a $125$

### 2015-05-24 paper/e6ssm-tuning-paper.tex
changed the way we describe the bilinear mass term.

--- 2015-05-17 paper/e6ssm-tuning-paper.tex
@@
 
-The full superpotential for $E_6$ inspired models will then be,
+The full superpotential for $E_6$ inspired models coming from $27\otimes 27 \otimes 27$ decomposition of the fundamental $E_6$ representation will then be,
 \be
@@
 where we denote by $\SuperField{H}_d^3 \equiv \SuperField{H}_d$,
-$\SuperField{H}_u^3 \equiv \SuperField{H}_u$ and $\SuperField{S}_3 \equiv
-\SuperField{S}$ the third generation Higgs and SM singlet fields that are
-assumed to acquire non-zero VEVs.  In addition to the $E_6$ preserving terms
-following from Eq.~(\ref{Eq:e6-superpot}), this superpotential also contains a
-bilinear term $\mu' \SuperField{H}'\cdot \SuperField{\overline{H'}}$ that
-violates the $E_6$ symmetry but is invariant with respect to the low energy SM
-gauge group and the additional $U(1)'$ symmetry.  This term is responsible for
-setting the masses of the components of the superfields $\SuperField{H}'$,
-$\SuperField{\overline{H'}}$, but it is not involved in the process of EWSB.
-Consequently the impact on the fine tuning of the value of $\mu'$ is much
-smaller than that coming from other sectors, and so can be safely neglected
-in our study. In all of the scans we present below the value of $\mu'$ is
-fixed to $\mu' = 5$ TeV.
+$\SuperField{H}_u^3 \equiv \SuperField{H}_u$ and $\SuperField{S}_3
+\equiv \SuperField{S}$ the third generation Higgs and SM singlet
+fields that are assumed to acquire non-zero VEVs.  In addition to the
+terms coming from the $27\otimes 27 \otimes 27$ interactions given in
+Eq.~(\ref{Eq:e6-superpot}), this superpotential also contains a
+bilinear term $\mu' \SuperField{H}'\cdot \SuperField{\overline{H'}}$,
+arising from $27^\prime \otimes \overline{27}^\prime$, which is
+invariant with respect to the low energy SM gauge group and the
+additional $U(1)'$ symmetry and also anomaly free.  This term is
+responsible for setting the masses of the components of the
+superfields $\SuperField{H}'$, $\SuperField{\overline{H'}}$, included
+to ensure gauge coupling unification, but it is not involved in the
+process of EWSB.  Consequently the impact on the fine tuning of the
+value of $\mu'$ is much smaller than that coming from other sectors,
+and so can be safely neglected in our study. In all of the scans we
+present below the value of $\mu'$ is fixed to $\mu' = 5$ TeV.
 
@@
 for example due to the appearance of charge or color breaking (CCB) minima.
+As a further requirement in the MSSM we exclude any points that do not satisfy
+the well known CCB constraint \cite{Casas:1995pd},
+\begin{equation} \label{eq:MSSMCCBconstraint}
+A_t^2 < 3 \left ( \mu^2 + m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 \right ),
+\end{equation}
+or the unbounded from below (UFB) constraint,
+\begin{equation} \label{eq:MSSMUFBconstraint}
+m_{H_d}^2 + m_{H_u}^2 + 2 \mu^2 > 2 B \mu .
+\end{equation}
 We work in the third family approximation, taking the first and second
@@
 high enough to have an impact on the fine tuning obtained in the models and
-parameter space regions that we have studied, as we have checked explicitly.
-Significantly larger lower bounds on the $\mu$ parameter, and therefore on the
-fine tuning, may arise from chargino limits coming from LHC searches.  However
-the chargino limits from the LHC depend on whether there are light sleptons or
-sneutrinos and the mass difference between the lightest chargino and lightest
-neutralino.  Current limits placed by CMS and ATLAS extend up to
+parameter space regions that we have studied, as we have checked explicitly\footnote{It is for this reason that we did not require the LEP bounds be
+satisfied for the points shown in Figure \ref{Fig:e6ssmvsmssm}
+and in Figure \ref{Fig:othere6modelsvsmssm} below.}.  Significantly larger
+lower bounds on the $\mu$ parameter, and therefore on the fine tuning, may
+arise from chargino limits coming from LHC searches.  However the chargino
+limits from the LHC depend on whether there are light sleptons or sneutrinos
+and the mass difference between the lightest chargino and lightest neutralino.
+Current limits placed by CMS and ATLAS extend up to
 $m_{\tilde{\chi}^\pm_1} \approx 700 - 740$ GeV if there are light

### 2015-05-24 paper/Referee-response.tex
changed referee response to reflect last chenge to paper.

--- 2015-05-17 paper/Referee-response.tex
@@
 
-The referee is correct to point out that the bilinear coupling $\mu'$ is
-absent from the list of superpotential terms, and is lacking an explanation
-in our original submission. The $\mu'$ term violates the $E_6$ symmetry, as
-it is associated with the incomplete $27$ and $\overline{27}$ to which the
-fields $\hat{H'}$ and $\hat{\overline{H}'}$ belong, but is invariant under
-the Standard Model gauge group and the low energy $U(1)'$ symmetry. For this
-reason it is not given in the superpotential in Eq.~(5). Additionally, because
-this parameter does not appear in the EWSB conditions the impact from it on
-the fine tuning can be neglected, and so fixing the value of $\mu'$ does not
-impact the results.
+The referee is correct to point out that the bilinear coupling $\mu'$
+is absent from the list of superpotential terms, and is lacking an
+explanation in our original submission. The $\mu'$ term is associated
+with the incomplete $27$ and $\overline{27}$ to which the fields
+$\hat{H'}$ and $\hat{\overline{H}'}$ belong, but is invariant under
+the Standard Model gauge group and the low energy $U(1)'$
+symmetry.  Additionally, because this parameter does not appear in the
+EWSB conditions the impact from it on the fine tuning can be
+neglected, and so fixing the value of $\mu'$ does not impact the
+results.
 

### 2015-05-24 paper/Referee-response.tex
Added missing primes to refereee response

@@
 explanation in our original submission. The $\mu'$ term is associated
-with the incomplete $27$ and $\overline{27}$ to which the fields
+with the incomplete $27'$ and $\overline{27}'$ to which the fields
 $\hat{H'}$ and $\hat{\overline{H}'}$ belong, but is invariant under

### 2015-05-24 paper/e6ssm-tuning-paper.tex
Fixed some more minor typos

@@
 has been used extensively within the literature
-e.g. \cite{deCarlos:1993yy, deCarlos:1993ca, Chankowski:1997zh,
+e.g. Refs.~\cite{deCarlos:1993yy, deCarlos:1993ca, Chankowski:1997zh,
   Agashe:1997kn, Wright:1998mk, Kane:1998im, BasteroGil:1999gu,
@@
 and the observables.  Interestingly this means the tuning is the ratio
-of the infinitesimal observable space space volume element to the
+of the infinitesimal observable space volume element to the
 infinitesimal parameter space element and coincides with the measure
-proposed in \cite{Athron:2007ry} when the interval of variation is
+proposed in Ref.~\cite{Athron:2007ry} when the interval of variation is
 taken to zero.
@@
 into $SU(5)$, gives $SO(10) \to SU(5) \times U(1)_{\chi}$ (this is
-reviewed in e.g.~\cite{Langacker:2008yv}).  The extra $U(1)$ gauge
+reviewed in e.g. Ref.~\cite{Langacker:2008yv}).  The extra $U(1)$ gauge
 symmetry at low energies should then be a linear combination of these
@@
 Keith:1997zb, Gherghetta:1996yr, Demir:1998dk, Langacker:1998tc,
-Hambye:2000bn, Ma:2000jf} (or for reviews see \cite{Hewett:1988xc,
+Hambye:2000bn, Ma:2000jf} (or for reviews see Refs.~\cite{Hewett:1988xc,
 Langacker:2008yv}).  There has also been a lot of work recently including
@@
 $U(1)$ symmetries appearing from the breakdown of $E_6$ are present at
-low energy was studied in \cite{Rizzo:2012rf}.  The E$_6$SSM was also
+low energy was studied in Ref.~\cite{Rizzo:2012rf}.  The E$_6$SSM was also
 included in studies looking at how first or second generation sfermion
@@
 
-As was noted in \cite{Athron:2013ipa}, the first two of the conditions
-Eq.~\ref{eq:E6EWSBConditions} may be rewritten in the form
+As was noted in Ref.~\cite{Athron:2013ipa}, the first two of the conditions in
+Eq.~(\ref{eq:E6EWSBConditions}) may be rewritten in the form
 \begin{equation} \label{eq:E6MZequation}
@@
 to the fine tuning in these models can be made even clearer by writing
-Eq.~(\ref{eq:E6MZequation}) in the form given in \cite{Athron:2013ipa},
+Eq.~(\ref{eq:E6MZequation}) in the form given in Ref.~\cite{Athron:2013ipa},
 \begin{equation}\label{eq:originalE6MZequation}
@@
 
-However if the extra $U(1)$ gauge symmetries appears from the
+However if the extra $U(1)$ gauge symmetry appears from the
 breakdown of $E_6$, then $\sin\chi$ should be zero at the GUT scale.
 Nonetheless even if this term is zero at the outset it will still be
-radiatively generated if the trace of their charges, $\sum_i Q_i^Y
+radiatively generated if the trace of the $U(1)$ charges, $\sum_i Q_i^Y
 Q^\prime_i$, is non-zero.  In the cases studied here the trace of the
@@
 as can be the case if one considers an additional $5 + \overline{5}$ pair of
-$SU(5)$ multiplets \cite{Rizzo:1998ut} or as has been looked in the $U(1)_{B-L}$
-\cite{Salvioni:2009mt,Krauss:2012ku}.  In such a case this will impact the
-results in two ways, firstly by altering the $Z^\prime$ limit from experiment
-and secondly by altering the charges which appear in the EWSB condition,
-which can be seen from examining
+$SU(5)$ multiplets \cite{Rizzo:1998ut} or as has been looked at in the
+$U(1)_{B-L}$ \cite{Salvioni:2009mt,Krauss:2012ku}.  In such a case this will
+impact the results in two ways, firstly by altering the $Z^\prime$ limit from
+experiment and secondly by altering the charges which appear in the EWSB
+condition, which can be seen from examining
 Eqs.~(\ref{eq:originalE6MZequation})-(\ref{eq:ddefn}).
@@
 tuning is then taken to be
-$\Delta = \underset{i}{\max} \, \{ \Delta_{p_i} \}$.\\
+$\Delta = \underset{i}{\max} \, \{ \Delta_{p_i} \}$.
 
@@
 for the E$_6$SSM, obtained from the tree level scalar potential, was
-presented in \cite{Athron:2013ipa}.  In order to derive the expression
+presented in Ref.~\cite{Athron:2013ipa}.  In order to derive the expression
 presented there, the fact that $s \gg v$ was made use of to neglect certain
@@
 previously been applied in the NMSSM, see for example
-\cite{Ellwanger:2011mu}).  For a model in which $m$ fields develop real
+Ref.~\cite{Ellwanger:2011mu}).  For a model in which $m$ fields develop real
 VEVs (e.g. $m=2$ in the MSSM, $m=3$ in the NMSSM and in the $E_6$
@@
 the Coleman-Weinberg potential contributions $\Delta V$ in the EWSB
-conditions.  Here we use the one-loop corrections given in Eq.~\ref{Eq:DeltaV}.
+conditions.  Here we use the one-loop corrections given in
+Eq.~(\ref{Eq:DeltaV}).
 
@@
 the fine tuning in a modified version of the E$_6$SSM spectrum
-generator that was used in \cite{Athron:2013ipa}.  This code
+generator that was used in Ref.~\cite{Athron:2013ipa}.  This code
 implemented two-loop RGEs for all parameters except the soft scalar
@@
 are calculated including the leading one-loop effective potential
-contributions given in \cite{Athron:2009bs} and for the light Higgs we
+contributions given in Ref.~\cite{Athron:2009bs} and for the light Higgs we
 use the leading two-loop\footnote{Two-loop corrections calculated for
@@
   such corrections go beyond the required precision for studying fine
-  tuning here.} contributions from \cite{King:2005jy} which are a
+  tuning here.} contributions from Ref.~\cite{King:2005jy} which are a
 generalization of the corrections in the MSSM and NMSSM calculated
@@
 charge associated with $U(1)_I$ vanishing, which means that the
-D-terms to the lightest Higgs which is predominantly $H_u$ at large
+$D$-terms to the lightest Higgs which is predominantly $H_u$ at large
 $\tan\beta$ are suppressed, making it difficult to raise the Higgs
@@
 high scale boundary, $M_X$, where the parameters are assumed to be set
-by some SUSY breaking mechanism.  Indeed in \cite{Athron:2013ipa} a
+by some SUSY breaking mechanism.  Indeed in Ref.~\cite{Athron:2013ipa} a
 constrained version of the E$_6$SSM, with the high scale boundary at
@@
 soft trilinears, along with the one-loop RGEs for the soft scalar
-masses, were originally obtained in \cite{Athron:2009bs} for the
+masses, were originally obtained in Ref.~\cite{Athron:2009bs} for the
 particular case of the E$_6$SSM.  FlexibleSUSY uses full one- and
 two-loop RGEs from SARAH, which for the models considered here are
-based on \cite{Martin:1993zk} and the recent extension\footnote{In
+based on Ref.~\cite{Martin:1993zk} and the recent extension\footnote{In
 the version of SARAH which we used the extra terms from this
@@
 about this and understand they will be included in future
-versions.} \cite{Fonseca:2011vn} to include models with multiple
+versions.} in Ref.~\cite{Fonseca:2011vn} to include models with multiple
 $U(1)$ gauge groups, in the most general case where the trace of the
@@
 with\footnote{The first of these is the trace which is assumed to vanish in
-\cite{Martin:1993zk}.  Although we use the \texttt{NoU1Mixing} flag to neglect
-gauge kinetic mixing, SARAH does this by removing the RGE for
+Ref.~\cite{Martin:1993zk}.  Although we use the \texttt{NoU1Mixing} flag to
+neglect gauge kinetic mixing, SARAH does this by removing the RGE for
 the off diagonal gauge couplings and effectively setting them to
@@
 do not reduce to those which one would obtain from
-\cite{Martin:1993zk} or \cite{Athron:2009bs} unless $\Sigma_{Q}^Y = 0$.
-Note however these contributions do not appear in the
+Ref.~\cite{Martin:1993zk} or Ref.~\cite{Athron:2009bs} unless
+$\Sigma_{Q}^Y = 0$.  Note however these contributions do not appear in the
 corresponding trilinears due to the version of SARAH used.}

### 2015-05-25 paper/Referee-response.tex
Fixed a typo

@@
 original article.  In the models we investigate numerically in our
-paper, if gauge kinetic mixing is absent at the GUT scale it, the
+paper, if gauge kinetic mixing is absent at the GUT scale the
 radiatively induced gauge kinetic mixing will be rather small at the

### 2015-05-25 paper/e6ssm-tuning-paper.tex
emphasising -> emphasizing

@@
 $U(1)_I$ the fine tuning was much worse for the larger $Z^\prime$
-mass, further emphasising the importance of this in $U(1)$ extensions.
+mass, further emphasizing the importance of this in $U(1)$ extensions.
 The $U(1)_I$ model showed the least tuning due to

### 2015-06-19 paper/e6ssm-tuning-paper.tex
Corrected several typos

@@
 associated with the break down of the new $U(1)$ appearing in the
-electroweak symmetry breaking conditions at tree level
+electroweak symmetry breaking (EWSB) conditions at tree level
 \cite{Athron:2013ipa}.  Despite this the constrained version of the
@@
 Higgs bosons, $H_u$ and $H_d$, to remain perturbative up to the UV
-scale and not the all the way up to the GUT scale.
+scale and not all of the way up to the GUT scale.
 
@@
 \nonumber \\
-& \quad {} \mp \sqrt{\left [ m_{Q_3}^2 + m_{u_3}^2 + \frac{1}{8} \left (g_2^2
+& \quad {} \mp \sqrt{\left [ m_{Q_3}^2 - m_{u_3}^2 + \frac{1}{8} \left (g_2^2
 - g_1^2 \right ) \left (v_1^2 - v_2^2 \right ) + D_Q - D_u \right ]^2 +
@@
 $q_k$ evaluated at the scale of EWSB, $f_i = f_i(v_j , q_k)$.  Thus for
-each $f_i$ we have that
+each $f_i$ we find that
 \begin{equation} \label{eq:EWSBchainrule}
-\delta f_i = \sum_{j=1}^m \frac{\partial f_i}{\partial v_j}
+\sum_{j=1}^m \frac{\partial f_i}{\partial v_j}
 \frac{\partial v_j}{\partial p} + \sum_{k=1}^l \frac{\partial f_i}
@@
 increase the cutoff such that for $M_X = 10^{16}$ GeV a lightest stop
-masses of $1-3$ TeV can result in a fine tuning of $\approx 100 -
+mass of $1-3$ TeV can result in a fine tuning of $\approx 100 -
 1000$ and the minimum tuning we find\footnote{Note that in the
@@
 comparison.  However from the individual sensitivities one can see that the
-behaviour is quite similar to MSSM BM1, though in this case the
+behaviour is quite similar to MSSM BM1, though in this case
 $\Delta_{m_{H_u}^2}$ becomes the largest tuning at a higher $M_X$ and does not
@@
 significant tuning for constrained models, since heavy stops are
-required to raised the lightest Higgs mass above it's tree level
+required to raise the lightest Higgs mass above it's tree level
 bound. Then recently this problem got much worse since the LHC measured the
@@
 cutoff of $20$ TeV for setting the soft masses, the lowest tuning in
-the E$_6$SSM is compatible with a $Z^\prime$ mass of $2.5$ TeV was
+the E$_6$SSM compatible with a $Z^\prime$ mass of $2.5$ TeV was
 $\Delta \approx 121$, while if the LHC run II can place a limit of
@@
 the GUT scale the radiatively generated gauge kinetic mixing gives an
-off diagonal gauge coupling, $g_{11}$, of just $\approx 0.02$ at the
+off-diagonal gauge coupling, $g_{11}$, of just $\approx 0.02$ at the
 electroweak scale \cite{King:2005jy} and so it does not play a large
@@
 - 3 \lambda^2 \left ( 3 y_t^2 + 3 y_b^2 + y_\tau^2 \right ) \nonumber \\
-& {} - 3 \left ( 3 y_t^4 + 3 y_b^4 + 2 y_t^2 y_b^2 + y_\tau^2 \right ) +
+& {} - 3 \left ( 3 y_t^4 + 3 y_b^4 + 2 y_t^2 y_b^2 + y_\tau^4 \right ) +
 6 g_2^2 \Sigma_\lambda + \frac{2}{5} g_1^2 \left ( 2 y_t^2 - y_b^2 +
@@
 b_{m_{u_3}^2}^{(2)} &= 48 y_t^4 \left ( m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2
-\right ) + 4 y_t^2 y_b^2 \left ( m_{H_u}^2 + m_{H_d}^2 + m_{Q_3}^2 +
+\right ) + 4 y_t^2 y_b^2 \left ( m_{H_u}^2 + m_{H_d}^2 + 2 m_{Q_3}^2 +
 m_{u_3}^2 + m_{d_3}^2 \right ) + 96 y_t^2 a_t^2 \nonumber \\

### 2015-06-19 paper/e6ssm-tuning-paper.tex
Applied corrections from proof

@@
 masses of superpartners have lead to concerns that supersymmetric
-models are now fine tuned.  Large stop masses, required for a $125$
+models are now fine-tuned.  Large stop masses, required for a $125$
 GeV Higgs, feed into the electroweak symmetry breaking conditions
-through renormalization group equations forcing one to fine tune these
+through renormalization group equations forcing one to fine-tune these
 parameters to obtain the correct electroweak vacuum expectation value.
-Nonetheless this fine tuning depends crucially on our assumptions about
-the supersymmetry breaking scale.  At the same time $U(1)$ extensions
-provide the most compelling solution to the $\mu$-problem, which is also
-a naturalness issue, and allow the tree level Higgs mass to be raised
-substantially above $M_Z$.  These very well motivated supersymmetric models
-predict a new $Z^\prime$ boson which could be discovered at the LHC and the
+Nonetheless, this fine-tuning depends crucially on our assumptions about
+the supersymmetry breaking scale.  At the same time, $U(1)$ extensions
+provide the most compelling solution to the $\mu$ problem, which is also
+a naturalness issue, and allow the tree-level Higgs mass to be raised
+substantially above $M_Z$.  These very well-motivated supersymmetric models
+predict a new $Z^\prime$ boson which could be discovered at the LHC, and the
 naturalness of the model requires that the $Z^\prime$ boson mass
-should not be too far above the TeV scale.  Moreover this fine tuning
+should not be too far above the TeV scale.  Moreover, this fine-tuning
 appears at the tree level, making it less dependent on assumptions
-about the supersymmetry breaking mechanism.  Here we study this fine tuning
+about the supersymmetry breaking mechanism.  Here we study this fine-tuning
 for several $U(1)$ supersymmetric extensions of the Standard Model and
-compare it to the situation in the MSSM where the most direct tree
-level fine tuning can be probed through chargino mass limits.  We show
+compare it to the situation in the MSSM where the most direct tree-level
+fine-tuning can be probed through chargino mass limits.  We show
 that future LHC $Z^\prime$ searches are extremely important for
@@
 (LHC) has interesting implications for physics beyond the Standard
-Model (SM) and supersymmetry (SUSY).  On the one hand it provides a
+Model (SM) and supersymmetry (SUSY).  On the one hand, it provides a
 light Higgs boson, as expected from supersymmetry, and
 can be fitted in the minimal supersymmetric standard model (MSSM).  On
-the other hand the Higgs mass is slightly heavier than the constrained
+the other hand, the Higgs mass is slightly heavier than the constrained
 version of the MSSM (cMSSM) can accommodate naturally
@@
 tree level it has an upper bound of the mass of the $Z$ boson,
-$M_Z$.  The dominant higher order corrections to the Higgs mass come
-from stops and to obtain a $125$ GeV Higgs they need to be rather
-heavy.  Heavy stops will provide a large contribution to the low energy
+$M_Z$.  The dominant higher-order corrections to the Higgs mass come
+from stops, and to obtain a $125$ GeV Higgs they need to be rather
+heavy.  Heavy stops will provide a large contribution to the low-energy
 value of $m_{H_u}^2$, the soft breaking mass for the up-type Higgs
@@
 value (VEV), $v$, or $M_Z$.  This naturalness problem motivates both
-further examination of non-minimal SUSY models that can raise the Higgs mass
+further examination of nonminimal SUSY models that can raise the Higgs mass
 without the need for heavy stops and alternative possibilities for how the
@@
 In addition to that naturalness issue, often referred to as the little
-hierarchy problem, the MSSM also suffers from the $\mu$-problem.  This
+hierarchy problem, the MSSM also suffers from the $\mu$ problem.  This
 is also a naturalness problem since there should be a natural explanation
@@
 $U(1)$ extensions of the MSSM provide a very elegant solution to this
-$\mu$-problem \cite{Fayet:1977yc, Kim:1983dt, Suematsu:1994qm,
+$\mu$ problem \cite{Fayet:1977yc, Kim:1983dt, Suematsu:1994qm,
   Cvetic:1995rj, Cvetic:1996mf, Jain:1995cb, Nir:1995bu,
-  Cvetic:1997ky} and also raise the Higgs mass with new $F$- and
-$D$-terms.  Nonetheless, as was recently demonstrated in the context
+  Cvetic:1997ky} and also raise the Higgs mass with new $F$ and
+$D$ terms.  Nonetheless, as was recently demonstrated in the context
 of the exceptional supersymmetric standard model (E$_6$SSM)
@@
 E$_6$SSM (cE$_6$SSM) \cite{Athron:2009ue, Athron:2009bs} was still
-found to be significantly less tuned than the cMSSM.  Tree level
-fine tuning from the $Z^\prime$ mass was also considered
+found to be significantly less tuned than the cMSSM.  Tree-level
+fine-tuning from the $Z^\prime$ mass was also considered
 previously \cite{Drees:1985js}.
 
-However this comparison of fine tuning depends crucially upon the
+However, this comparison of fine-tuning depends crucially upon the
 assumptions of these gravity mediated SUSY breaking motivated
-constrained models and in particular that the universality
-constraints are applied at the GUT scale.  As mentioned above, given
-the findings at the LHC it is worth considering other possibilities,
+constrained models and, in particular, the universality
+constraints being applied at the GUT scale.  As mentioned above, given
+the findings at the LHC, it is worth considering other possibilities,
 which may allow the soft masses to be set at lower energies.  As the
 scale at which the parameters fulfill some breaking inspired
-constraints is lowered the stop masses contribute less to the fine
-tuning.
+constraints is lowered the stop masses contribute less to the fine-tuning.
 
@@
 
-However the tuning from the $Z^\prime$ mass limit does not disappear
+However, the tuning from the $Z^\prime$ mass limit does not disappear
 as the UV boundary condition is lowered.  This tuning appears in the
@@
 from the stops.  We find that the $Z^\prime$ limit is enough to already
-require moderate fine tuning in the E$_6$SSM.  We also show this is
+require moderate fine-tuning in the E$_6$SSM.  We also show this is
 comparable to the situation in the MSSM defined at the same scale if
@@
 $Z^\prime$ limits are important in constraining the most natural
-scenarios of these models.  Therefore the $Z^\prime$ constraint
+scenarios of these models.  Therefore, the $Z^\prime$ constraint
 is amongst the most important in terms of tuning and attacking natural
@@
 
-Finally we make a case study, for a few benchmarks, of the impact of
-raising the high scale boundary condition, $M_X$, at which the SUSY
+Finally, we make a case study, for a few benchmarks, of the impact of
+raising the high-scale boundary condition, $M_X$, at which the SUSY
 breaking parameters must be fixed by some SUSY breaking mechanism.  We
-show that which model has less fine tuning depends on $M_X$.  We also
-see rather complicated behaviour in the tuning for the E$_6$SSM points
+show that which model has less fine-tuning depends on $M_X$.  We also
+see rather complicated behavior in the tuning for the E$_6$SSM points
 due to the combination of different sources of tuning.
 
-As mentioned earlier the fine tuning of the cE$_6$SSM was recently studied
+As mentioned earlier, the-fine tuning of the cE$_6$SSM was recently studied
 \cite{Athron:2013ipa} and there it was revealed that the associated
-$Z^\prime$ boson leads to a new source of fine tuning since it's mass
+$Z^\prime$ boson leads to a new source of fine-tuning since its mass
 appears in the EWSB conditions.
 
-However in this study we will examine this source of fine tuning in more
-detail by considering low energy constructions where the usual fine
-tuning problem from the Higgs is minimized.  We will also consider
+However in this study we will examine this source of fine-tuning in more
+detail by considering low-energy constructions where the usual fine-tuning
+problem from the Higgs is minimized.  We will also consider
 alternate charges for the extra $U(1)$ symmetry to relax the focus on
@@
 
-To quantify the fine tuning we will employ the traditional
+To quantify the fine-tuning we will employ the traditional
 Barbieri-Giudice measure \cite{Ellis:1986yg, Barbieri:1987fn}.  This
@@
 to work within a Bayesian analysis.  There the concept of naturalness
-is automatically incorporated since in models where one must fine tune
+is automatically incorporated since in models where one must fine-tune
 parameters to fit measured values of the observables, the region with
@@
 VEVs, the inverse of the Jacobian for this transformation looks quite like
-the derivatives that appear in the traditional fine tuning measure
+the derivatives that appear in the traditional fine-tuning measure
 \cite{Allanach:2007qk, Cabrera:2008tj, Kim:2013uxa}.  If one thinks
-more generally then a model without fine tuning is one where the
+more generally, then a model without fine-tuning is one where the
 parameterization is such that all the parameters are observables
 \cite{Fichet:2012sn, Kim:2013uxa}.  This provides a quite general
-definition of fine tuning as $1/|J|$ where $|J|$ is the determinant of
-the Jacobian for the co-ordinate transformation between the parameters
+definition of fine-tuning as $1/|J|$ where $|J|$ is the determinant of
+the Jacobian for the coordinate transformation between the parameters
 and the observables.  Interestingly this means the tuning is the ratio
@@
 While this approach has many merits here we will employ the traditional
-measure of fine tuning because it is both simple to apply and easy to
+measure of fine-tuning because it is both simple to apply and easy to
 compare with previous results due to it's widespread use.  Fortunately
@@
 
-The structure of this paper is as follows.  In section \ref{sec:model}
-we review the models we consider.  In section \ref{sec:ewsb} we
+The structure of this paper is as follows.  In Sec.~\ref{sec:model}
+we review the models we consider.  In Sec.~\ref{sec:ewsb} we
 specify the EWSB conditions of the models, with particular focus on
 how the $Z^\prime$ mass influences the prediction of $M_Z$.  Then in
-section \ref{sec:tuningmeasure} we introduce our fine tuning measure
+Sec.~\ref{sec:tuningmeasure} we introduce our fine-tuning measure
 and our approach to evaluating it to obtain the individual
-sensitivities.  The results are then given in section
-\ref{sec:results}.
+sensitivities.  The results are then given in Sec.~\ref{sec:results}.
 
@@
 In this paper we consider $U(1)$ extensions of the MSSM where the gauge
-group at low energies is, \be SU(3)_C\times SU(2)_W\times U(1)_Y\times
+group at low energies is \be SU(3)_C\times SU(2)_W\times U(1)_Y\times
 U(1)^\prime.  \ee $U(1)^\prime$ is the new gauge group beyond
 that of the SM and MSSM.  The minimal superfield content of $U(1)$
-extensions which solve the $\mu$-problem should be ordinary left
-handed quark $\hat{Q}_i$ and lepton $\hat{L}_i$
-($i=1,2,3$) superfields along with right handed superfields
+extensions which solve the $\mu$ problem should be ordinary left-handed
+quark $\hat{Q}_i$ and lepton $\hat{L}_i$
+($i=1,2,3$) superfields along with right-handed superfields
 $\hat{u}^c_i$, $\hat{d}^c_i$, $\hat{e}^c_i$ ($i=1,2,3$) for the
@@
 Here we will refer to $U(1)$ extensions of the MSSM, which solve the
-$\mu$-problem, as the USSM \cite{Cvetic:1995rj, Jain:1995cb,
+$\mu$ problem, as the USSM \cite{Cvetic:1995rj, Jain:1995cb,
   Nir:1995bu, Cvetic:1996mf, Cvetic:1997ky}.  The couplings for the
@@
 
-The breaking of $E_6$ into $SO(10)$, gives rise to $E_6 \to
+The breaking of $E_6$ into $SO(10)$ gives rise to $E_6 \to
 SO(10) \times U(1)_{\psi}$, and the subsequent breaking of $SO(10)$
-into $SU(5)$, gives $SO(10) \to SU(5) \times U(1)_{\chi}$ (this is
+into $SU(5)$ gives $SO(10) \to SU(5) \times U(1)_{\chi}$ (this is
 reviewed in e.g. Ref.~\cite{Langacker:2008yv}).  The extra $U(1)$ gauge
@@
 Keith:1997zb, Gherghetta:1996yr, Demir:1998dk, Langacker:1998tc,
-Hambye:2000bn, Ma:2000jf} (or for reviews see Refs.~\cite{Hewett:1988xc,
+Hambye:2000bn, Ma:2000jf} (or, for reviews, see Refs.~\cite{Hewett:1988xc,
 Langacker:2008yv}).  There has also been a lot of work recently including
@@
 \cite{Stech:2008wd}; neutrino physics \cite{Kang:2004ix}; explanations of
-the matter-anti-matter asymmetry of the universe though EW baryogenesis or
+the matter-antimatter asymmetry of the Universe though EW baryogenesis or
 leptogenesis \cite{Hambye:2000bn, Ma:2000jf, Kang:2004pp}; decays of the
@@
 Chang:2011be}; dipole moments \cite{GutierrezRodriguez:2006hb}; anomaly
-mediated SUSY breaking with D-term contributions \cite{Asano:2008ju} and
+mediated SUSY breaking with $D$-term contributions \cite{Asano:2008ju} and
 the (extended) Higgs sectors \cite{Daikoku:2000ep, Ham:2008xf}.
@@
 Here we will focus most on the special case where the gauge symmetry
-is $U(1)_N$, under which the right handed neutrino $\hat{N}^c$ does not
+is $U(1)_N$, under which the right-handed neutrino $\hat{N}^c$ does not
 participate in gauge interactions.  This is the case in the E$_6$SSM
-\cite{King:2005jy, King:2005my, Athron:2010zz}, and closely-related variants
+\cite{King:2005jy, King:2005my, Athron:2010zz}, and closely related variants
 \cite{Howl:2007zi, Braam:2009fi, Braam:2010sy, Hall:2011zq, Nevzorov:2012hs,
-Athron:2014pua}.  Since the right handed neutrino has no gauge symmetry
+Athron:2014pua}.  Since the right-handed neutrino has no gauge symmetry
 protecting it's mass from becoming extremely heavy such models may explain
 the tiny observed masses of neutrinos via the see-saw mechanism and the
-baryon asymmetry in the universe via leptogenesis \cite{Hambye:2000bn,
+baryon asymmetry in the Universe via leptogenesis \cite{Hambye:2000bn,
 King:2008qb, King:2008gw}.  Recently it has also been studied in the context
@@
 \cite{Howl:2007hq, Howl:2007zi}.  If the exotic particles are light in
-these models this can open up non-standard decays of the SM--like
+these models this can open up nonstandard decays of the SM-like
 Higgs boson \cite{Hall:2010ix, Nevzorov:2013tta, Athron:2014pua}.
@@
 The correct relic density could be obtained entirely through an almost
-decoupled ``inert'' neutralino sector \cite{Hall:2009aj}.  However
+decoupled ``inert'' neutralino sector \cite{Hall:2009aj}.  However,
 this is no longer phenomenologically viable due to limits from direct
@@
 singlinos that cause these problems are entirely decoupled and the
-relic abundance is fitted with a bino-like candidate with a novel
+relic abundance is fitted with a binolike candidate with a novel
 mechanism involving back-scattering into a heavier inert
@@
 low energy was studied in Ref.~\cite{Rizzo:2012rf}.  The E$_6$SSM was also
-included in studies looking at how first or second generation sfermion
+included in studies looking at how first- or second-generation sfermion
 masses can be used to constrain the GUT scale parameters \cite{Miller:2012vn}
@@
 With three generations of matter $27$-plet representations of $E_6$
-surviving to low energies, the low energy matter content in each generation,
+surviving to low energies, the low-energy matter content in each generation,
 after integrating out the heavy right-handed neutrinos, includes, \be
@@
 
-The full superpotential for $E_6$ inspired models coming from $27\otimes 27 \otimes 27$ decomposition of the fundamental $E_6$ representation will then be,
+The full superpotential for $E_6$ inspired models coming from
+$27 \otimes 27 \otimes 27$ decomposition of the fundamental $E_6$
+representation will then be
 \be
@@
 \end{eqnarray}
-Nonetheless while this model is very elegant so far, the
+Nonetheless, while this model is very elegant so far, the
 superpotential of Eq.~(\ref{Eq:e6-superpot}) contains dangerous terms which
-can induce proton decay and lead to large flavour changing neutral
+can induce proton decay and lead to large flavor changing neutral
 currents (FCNCs).  There are a number of approaches to suppress these
@@
 $\SuperField{H}_u^3 \equiv \SuperField{H}_u$ and $\SuperField{S}_3
-\equiv \SuperField{S}$ the third generation Higgs and SM singlet
-fields that are assumed to acquire non-zero VEVs.  In addition to the
+\equiv \SuperField{S}$ the third-generation Higgs and SM singlet
+fields that are assumed to acquire nonzero VEVs.  In addition to the
 terms coming from the $27\otimes 27 \otimes 27$ interactions given in
@@
 arising from $27^\prime \otimes \overline{27}^\prime$, which is
-invariant with respect to the low energy SM gauge group and the
+invariant with respect to the low-energy SM gauge group and the
 additional $U(1)'$ symmetry and also anomaly free.  This term is
@@
 to ensure gauge coupling unification, but it is not involved in the
-process of EWSB.  Consequently the impact on the fine tuning of the
+process of EWSB.  Consequently, the impact on the fine-tuning of the
 value of $\mu'$ is much smaller than that coming from other sectors,
@@
 V_{\textrm{soft}} &= m_S^2 |S|^2 + m_{H_d}^2 |H_d|^2 + m_{H_u}^2 |H_u|^2 +
-\Big [\lambda A_\lambda S H_d \cdot H_u + \textrm{h.c.} \Big ] .
+\Big [\lambda A_\lambda S H_d \cdot H_u + \textrm{H.c.} \Big ] .
 \label{eq:E6Vsoft}
@@
 In these expressions $g_2$, $g' = \sqrt{3/5} g_1$, and $g_1'$ are the
-$SU(2)$, (non-GUT normalized) $U(1)_Y$ and $U(1)'$ gauge couplings
-respectively and $\bar{g}^2 = g_2^2 + g'^2$.  The charges $Q_1$, $Q_2$ and
+$SU(2)$, (non-GUT normalized) $U(1)_Y$ and $U(1)'$ gauge couplings,
+respectively, and $\bar{g}^2 = g_2^2 + g'^2$.  The charges $Q_1$, $Q_2$ and
 $Q_S$ are effective $U(1)'$ charges for $H_d$, $H_u$ and $S$, respectively,
@@
 \end{align*}
-Written in the form of Eq.~(\ref{eq:E6MZequation}) we see the
-potential new source of fine tuning alluded to above, in the form of
+Written in the form of Eq.~(\ref{eq:E6MZequation}), we see the
+potential new source of fine-tuning alluded to above, in the form of
 the third term on the right-hand side.  For large values of the VEV
@@
 in $U(1)_\chi$ models.  To satisfy these limits typically requires large
-values of the singlet VEV $s$.  For example $s \gtrsim 6$ TeV is required in
+values of the singlet VEV $s$.  For example, $s \gtrsim 6$ TeV is required in
 the E$_6$SSM with $U(1)' = U(1)_N$, so that $|D_{H_1}| , |D_{H_2}| \gg M_Z^2$
@@
 right-hand side of Eq.~(\ref{eq:E6MZequation}) must be tuned to cancel
-this very large contribution to $M_Z$.  Moreover, because this is a large tree
-level fine tuning, it may negate the improvement in naturalness that is
+this very large contribution to $M_Z$.  Moreover, because this is a large
+tree-level fine-tuning, it may negate the improvement in naturalness that is
 associated with having a reduced need for heavy superpartners.  In $U(1)$
 extended models for which $Q_S\neq 0$, the importance of the $Z^\prime$ mass
-to the fine tuning in these models can be made even clearer by writing
+to the fine-tuning in these models can be made even clearer by writing
 Eq.~(\ref{eq:E6MZequation}) in the form given in Ref.~\cite{Athron:2013ipa},
@@
 \end{align}
-Written like so it is evident that the fine tuning contribution coming
-from the new $D$-terms depends both on the $U(1)'$ charges and the
+Written like so, it is evident that the fine-tuning contribution coming
+from the new $D$ terms depends both on the $U(1)'$ charges and the
 $Z^\prime$ mass, and that the tuning can be expected to increase with
@@
 \be
-\mathcal{L}_{mix}^{kin}=-\frac{\sin\chi}{2}F^{Y}_{\mu\nu}F^{N}_{\mu\nu}\,.
+\mathcal{L}_{mix}^{kin}=-\frac{\sin\chi}{2}F^{Y}_{\mu\nu}F^{N}_{\mu\nu}\, ,
 \label{Eq:GKM}
 \ee where $F_{\mu\nu}^Y$ and $F_{\mu\nu}^{N}$ are field strengths
-associated with the $U(1)_Y$ and $U(1)_{N}$ respectively.  The gauge
+associated with the $U(1)_Y$ and $U(1)_{N}$, respectively.  The gauge
 kinetic mixing can have a significant impact on the phenomenology
-\cite{Rizzo:1998ut,Salvioni:2009mt,Krauss:2012ku}, and may reduce the
+\cite{Rizzo:1998ut,Salvioni:2009mt,Krauss:2012ku} and may reduce the
 $Z^\prime$ mass limit.
 
-However if the extra $U(1)$ gauge symmetry appears from the
+However, if the extra $U(1)$ gauge symmetry appears from the
 breakdown of $E_6$, then $\sin\chi$ should be zero at the GUT scale.
-Nonetheless even if this term is zero at the outset it will still be
+Nonetheless, even if this term is zero at the outset, it will still be
 radiatively generated if the trace of the $U(1)$ charges, $\sum_i Q_i^Y
-Q^\prime_i$, is non-zero.  In the cases studied here the trace of the
-charges over states in the complete $27$-plets vanish, but to be
-consistent with single step gauge coupling unification we also
+Q^\prime_i$, is nonzero.  In the cases studied here, the trace of the
+charges over states in the complete $27$-plets vanishes, but to be
+consistent with single-step gauge coupling unification, we also
 included $\hat{H}^\prime$ and $\hat{\overline{H^\prime}}$ which lead
-to a non-zero value for $\sum_i Q_i^Y Q^\prime_i $.  The value induced
+to a nonzero value for $\sum_i Q_i^Y Q^\prime_i $.  The value induced
 by this at the EW scale though is rather small as can be
@@
 For this reason and due to the huge expansion in the number of terms
-in the two-loop RGEs when one allows for gauge kinetic mixing we will
+in the two-loop RGEs when one allows for gauge kinetic mixing, we will
 neglect this in our analysis here and throughout this paper.
 
-In general though it is possible for gauge kinetic mixing to be much larger
-as can be the case if one considers an additional $5 + \overline{5}$ pair of
-$SU(5)$ multiplets \cite{Rizzo:1998ut} or as has been looked at in the
-$U(1)_{B-L}$ \cite{Salvioni:2009mt,Krauss:2012ku}.  In such a case this will
+In general, though, it is possible for gauge kinetic mixing to be much larger,
+which can be the case if one considers an additional $5 + \overline{5}$ pair of
+$SU(5)$ multiplets \cite{Rizzo:1998ut} or which has been looked at in the
+$U(1)_{B-L}$ \cite{Salvioni:2009mt,Krauss:2012ku}.  In such a case, this will
 impact the results in two ways, firstly by altering the $Z^\prime$ limit from
@@
 condition, which can be seen from examining
-Eqs.~(\ref{eq:originalE6MZequation})-(\ref{eq:ddefn}).
-
-\section{\label{sec:tuningmeasure}The Fine Tuning
+Eqs.~(\ref{eq:originalE6MZequation})--(\ref{eq:ddefn}).
+
+\section{\label{sec:tuningmeasure}The Fine-Tuning
 Measure}
 
-As stated above, to quantify the resulting fine tuning we apply the
+As stated above, to quantify the resulting fine-tuning we apply the
 traditional Barbieri-Giudice measure \cite{Ellis:1986yg, Barbieri:1987fn}.
@@
 and is defined at some input scale $M_X$. For a given parameter $p$ in this
-set, one computes an associated sensitivity
+set, one computes an associated sensitivity,
 \begin{equation} \label{eq:bgmeasure}
@@
 The coefficient $\Delta_p$ measures the fractional variation in $M_Z^2$
-resulting from a given variation in the parameter $p$.  The overall fine
-tuning is then taken to be
+resulting from a given variation in the parameter $p$.  The overall fine-tuning
+is then taken to be
 $\Delta = \underset{i}{\max} \, \{ \Delta_{p_i} \}$.
@@
 for $M_Z^2$ in terms of the $p_i$ for a particular model, which leads to a
-so-called master formula for calculating the fine tuning.  A master formula
-for the E$_6$SSM, obtained from the tree level scalar potential, was
+so-called master formula for calculating the fine-tuning.  A master formula
+for the E$_6$SSM, obtained from the tree-level scalar potential, was
 presented in Ref.~\cite{Athron:2013ipa}.  In order to derive the expression
@@
 {\partial p} \bigg | , \label{eq:E6masterformula}
-\ee where the sum is over all low energy running parameters appearing
-in the tree level EWSB conditions, i.e., $q \in \{\lambda , A_\lambda ,
+\ee where the sum is over all low-energy running parameters appearing
+in the tree-level EWSB conditions, i.e., $q \in \{\lambda , A_\lambda ,
 m_{H_d}^2 , m_{H_u}^2 , m_S^2 , g_1 , g_2 , g_1'\}$.  Expressions for the
@@
 However, it is well known in the MSSM that radiative corrections can
-significantly change (indeed, reduce) the fine tuning \cite{Cassel:2010px}.
-It is therefore important when studying the fine tuning to include loop
-corrections to the effective potential in the fine tuning measure.  To do so
+significantly change (indeed, reduce) the fine-tuning \cite{Cassel:2010px}.
+It is, therefore, important when studying the fine-tuning to include loop
+corrections to the effective potential in the fine-tuning measure.  To do so
 it is most convenient to work in terms of the EWSB conditions
@@
 The general procedure that we use is as follows (this method has also
-previously been applied in the NMSSM, see for example
+previously been applied in the NMSSM; see, for example,
 Ref.~\cite{Ellwanger:2011mu}).  For a model in which $m$ fields develop real
 VEVs (e.g. $m=2$ in the MSSM, $m=3$ in the NMSSM and in the $E_6$
-models considered), we require that the $m$ minimization conditions
+models considered), we require that the $m$ minimization conditions,
 \begin{equation} \label{eq:EWSBconditions}
-f_1 = f_2 = \dotsb = f_m = 0
+f_1 = f_2 = \dotsb = f_m = 0 ,
 \end{equation}
@@
 
-Evaluating the derivatives $\partial q_k / \partial p$ must in general be
+Evaluating the derivatives $\partial q_k / \partial p$ must, in general, be
 done by numerically integrating the two-loop RGEs.  This is time consuming
@@
 \end{align}
-Expanded to this order we obtain the leading log (LL) and next-to-LL
+Expanded to this order, we obtain the leading log (LL) and next-to-LL
 (NLL) contributions at two-loop order.  The $O(t^2)$ terms
-not displayed above are formally of 3-loop order and are
+not displayed above are formally of three-loop order and are
 neglected. The derivative of the one-loop $\beta$ function is given by
@@
 where the sum is over all running parameters appearing in
-$\beta_q^{(1)}$.  The $\beta$ functions appearing on the right hand side of
+$\beta_q^{(1)}$.  The $\beta$ functions appearing on the right-hand side of
 Eqs.~(\ref{eq:rgeapproxsoln}) and (\ref{eq:1loopbetaderivative}) are
@@
 
-Using the approach outlined above, we are able to scan the low energy
-parameter space of the MSSM and E$_6$SSM and calculate the fine tuning
+Using the approach outlined above, we are able to scan the low-energy
+parameter space of the MSSM and E$_6$SSM and calculate the fine-tuning
 in each.  To do so, we implemented the above expressions for computing
-the fine tuning in a modified version of the E$_6$SSM spectrum
+the fine-tuning in a modified version of the E$_6$SSM spectrum
 generator that was used in Ref.~\cite{Athron:2013ipa}.  This code
 implemented two-loop RGEs for all parameters except the soft scalar
-masses.  In order to properly include the fine tuning impact of the
+masses.  In order to properly include the fine-tuning impact of the
 $SU(3)$ gaugino soft mass $M_3$, we have extended the original code to
@@
 use the leading two-loop\footnote{Two-loop corrections calculated for
-  a non-minimal SUSY model may now also be obtained from SARAH
-  \cite{Goodsell:2014pla,Goodsell:2015ira}.  However this was not
-  available when the numerical work for this paper was carried out and
-  such corrections go beyond the required precision for studying fine
-  tuning here.} contributions from Ref.~\cite{King:2005jy} which are a
+  a nonminimal SUSY model may now also be obtained from SARAH
+  \cite{Goodsell:2014pla,Goodsell:2015ira}.  However, this was not
+  available when the numerical work for this paper was carried out, and
+  such corrections go beyond the required precision for studying fine-tuning
+  here.} contributions from Ref.~\cite{King:2005jy} which are a
 generalization of the corrections in the MSSM and NMSSM calculated
@@
   Ellwanger:1999ji}.  To scan over the MSSM parameter space, the
-equivalent MSSM fine tuning expressions were implemented into a
+equivalent MSSM fine-tuning expressions were implemented into a
 modified version of SOFTSUSY 3.3.10 \cite{Allanach:2001kg}.  For
@@
 two-loop corrections to the CP-even Higgs masses were included.
-Finally, in all of the results below the fine tuning was evaluated at
+Finally, in all of the results below the fine-tuning was evaluated at
 the scale $Q = M_{\textrm{SUSY}} =
@@
 
-As discussed in the introduction many recent papers interested in
+As discussed in the Introduction, many recent papers interested in
 natural supersymmetry have focused on light stops, with much
@@
 there are many good reasons to expect the soft masses to be set at
-high energies.  However that is not the only possibility and the fine
-tuning problem depends strongly on the RG evolution from the GUT
+high energies.  However, that is not the only possibility and the fine-tuning
+problem depends strongly on the RG evolution from the GUT
 scale, as the soft Higgs masses that appear in the EWSB conditions
@@
 \includegraphics{mssm_higgs_tuning_bw_var.png}}
-\caption{\textit{Left panel:} Scatter plot of fine tuning in the MSSM as a
+\caption{Left panel: Scatter plot of fine-tuning in the MSSM as a
 function of the lightest stop mass, $m_{\tilde{t}_1}$, for the cutoff scales
 (from bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and
-$M_X=10^{16}$ GeV.  \textit{Right panel:} Scatter plot of fine tuning in the
+$M_X=10^{16}$ GeV.  Right panel: Scatter plot of fine-tuning in the
 MSSM as a function of the lightest Higgs mass, $m_{h_1}$, for the cutoff
@@
 To illustrate this, in the left panel of Fig.~\ref{Fig:mssmstoptuning}
-we show the variation in fine tuning for $M_X = 20$ TeV, $50$ TeV,
+we show the variation in fine-tuning for $M_X = 20$ TeV, $50$ TeV,
 $100$ TeV and $10^{16}$ GeV when we scan over the stop masses and
@@
   GeV}$.  The remaining parameters we fix such that at $M_{\rm SUSY}$
-they have the values $\mu = -97.5$ GeV, $B = -84.8$ GeV, $M_1 = 92.1$
-GeV, $M_2 = 95.9$ GeV, $M_3 = 352$ GeV, $A_b = -117.9$ GeV, $A_\tau =
--7.8$ GeV, $m_{L_i} = 400$ GeV, $m_{e_i} = 204$ GeV, $m_{Q_{1,2}} =
-438$ GeV, $m_{u_{1,2}} = 436$ GeV and $m_{d_i} = 438$ GeV ($i = 1 , 2
+they have the values $\mu = -97.5$, $B = -84.8$, $M_1 = 92.1$,
+$M_2 = 95.9$, $M_3 = 352$, $A_b = -117.9$, $A_\tau =
+-7.8$, $m_{L_i} = 400$, $m_{e_i} = 204$, $m_{Q_{1,2}} =
+438$, $m_{u_{1,2}} = 436$ and $m_{d_i} = 438$ GeV ($i = 1 , 2
 , 3$).  Here we denote by $M_1$, $M_2$ and $M_3$ the soft gaugino
@@
 $m_A^2 = 2 B \mu / \sin 2\beta$.  All off-diagonal couplings and
-scalar masses are set to zero, as are the first and second generation
+scalar masses are set to zero, as are the first- and second-generation
 Yukawa couplings and soft trilinears.  Although we should stress that
 making this choice will lead to a spectrum which is in conflict with
-the LHC limits, doing so ensures that fine tuning due to the other
-parameters is small, so that we avoid washing out the fine tuning
+the LHC limits, doing so ensures that fine-tuning due to the other
+parameters is small, so that we avoid washing out the fine-tuning
 impact of the stops when the tuning is small\footnote{For models in
@@
 the stop masses is also pushing up the Higgs mass, meaning that
-heavier Higgs masses require more fine tuning.  However for a low
+heavier Higgs masses require more fine-tuning.  However, for a low
 value of the UV scale this tuning is not so severe unless the stops
@@
 tuning in this unrealistic case where we have minimized other sources
-of tuning.  On the other hand the tuning becomes more severe as we
+of tuning.  On the other hand, the tuning becomes more severe as we
 increase the cutoff such that for $M_X = 10^{16}$ GeV a lightest stop
-mass of $1-3$ TeV can result in a fine tuning of $\approx 100 -
-1000$ and the minimum tuning we find\footnote{Note that in the
+mass of 1--3 TeV can result in a fine-tuning of $\approx$ 100 --
+1000 and the minimum tuning we find\footnote{Note that in the
   calculation of the Higgs mass there is a significant theoretical
@@
 
-Since the stop mass does not have such a large impact on the fine
-tuning when the cutoff scale is very low we can use this to see more
-clearly the impact of the $Z^\prime$ mass on fine tuning.  To do so we
+Since the stop mass does not have such a large impact on the fine-tuning
+when the cutoff scale is very low we can use this to see more
+clearly the impact of the $Z^\prime$ mass on fine-tuning.  To do so we
 select a fixed low cutoff of $M_X=20$ TeV and compare the fine tuning
@@
 then compare the fine tuning calculated in each case to the tuning in
-the MSSM.  For this, we have performed a six dimensional parameter
+the MSSM.  For this, we have performed a six-dimensional parameter
 space scan in both the MSSM and E$_6$SSM, varying those parameters
-most relevant for the fine tuning and the Higgs mass.  Therefore the
+most relevant for the fine tuning and the Higgs mass.  Therefore, the
 set of parameters which we vary includes $\mu$, $B$ and $\tan\beta$
@@
 
-In this case we now consider realistic scenarios, where the
+In this case, we now consider realistic scenarios, where the
 parameters that are not scanned over are set to values which keep the
@@
 for example due to the appearance of charge or color breaking (CCB) minima.
-We work in the third family approximation, taking the first and second
-generation Yukawa couplings to be zero, and we also assume their associated
-soft trilinears vanish.  Similarly we take $A_b = A_\tau = 0$ GeV.  The $U(1)$
-gaugino soft mass $M_1$ was fixed to $M_1 = 300$ GeV, and we fix $M_3 = 2000$
-GeV.  Additionally, in the E$_6$SSM the $U(1)_N$ gaugino soft mass $M_1'$ is
-held fixed with $M_1' = M_1 = 300$ GeV, and $\mu^\prime = 5$ TeV.
+We work in the third family approximation, taking the first- and
+second-generation Yukawa couplings to be zero, and we also assume that their
+associated soft trilinears vanish.  Similarly, we take $A_b = A_\tau = 0$ GeV.
+The $U(1)$ gaugino soft mass $M_1$ was fixed to $M_1 = 300$ GeV, and we fix
+$M_3 = 2000$ GeV.  Additionally, in the E$_6$SSM the $U(1)_N$ gaugino soft mass
+$M_1'$ is held fixed with $M_1' = M_1 = 300$ GeV, and $\mu^\prime = 5$ TeV.
 
@@
 \textrm{ TeV } \leq A_t \leq 10 \textrm { TeV}$ \\
-$M_2 = 100 \textrm{ GeV, } 1050 \textrm{ GeV, } 2000 \textrm{ GeV}$ &
-$M_2 = 100 \textrm{ GeV, } 1050 \textrm{ GeV, } 2000 \textrm{ GeV}$ \\
+$M_2 = 100 \textrm{, } 1050 \textrm{, } 2000 \textrm{ GeV}$ &
+$M_2 = 100 \textrm{, } 1050 \textrm{, } 2000 \textrm{ GeV}$ \\
 \end{tabular}
@@
 \includegraphics{all_models_tuning_vs_higgs_bw_var.png}}
-\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
+\caption{Scatter plot of fine-tuning vs lightest Higgs mass for the
 MSSM (light blue, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV
@@
 (dark yellow, top band).  Note that there are points for which
-the fine tuning in the MSSM and E$_6$SSM with $M_{Z'} = 2.5$ TeV is larger
-than is visible on this plot and those below; however these points are
+the fine-tuning in the MSSM and E$_6$SSM with $M_{Z'} = 2.5$ TeV is larger
+than is visible on this plot and those below; however, these points are
 obscured by the overlaid data for the E$_6$SSM with $M_{Z'} = 4.5$ TeV, and
@@
 
-In Fig.~\ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
-the tuning for each case against the lightest Higgs mass.  As expected
+In Fig.~\ref{Fig:e6ssmvsmssm}, results from the scan are plotted showing
+the tuning for each case against the lightest Higgs mass.  As expected,
 the dependence on the Higgs mass is now quite weak, while the minimum
@@
 $Z^\prime$ boson.  So in the case of a very low cutoff the tuning
-required to get a 125 GeV Higgs is not so large.  However the tuning
-from the $Z^\prime$ mass appears already at tree level and is
-therefore not suppressed when the cutoff scale is low.  In our scan we
+required to get a 125 GeV Higgs is not so large.  However, the tuning
+from the $Z^\prime$ mass appears already at tree level and is,
+therefore, not suppressed when the cutoff scale is low.  In our scan we
 find that, for the points satisfying the current limit on the mass of
 the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the
-minimum fine tuning that can be achieved is
+minimum fine-tuning that can be achieved is
 $\Delta_{\textrm{min}} \approx 121$.  If run II of the LHC further
 pushes up the limit on the $Z^\prime$ mass to be above $4.5$ TeV then
-the fine tuning in the model will be greater than at least
+the fine-tuning in the model will be greater than at least
 $\Delta_{\textrm{min}} \approx 394$ for a Higgs mass between $124.5$
-GeV and $125.5$ GeV.
+and $125.5$ GeV.
 
 This demonstrates two important points about these $U(1)$
-extensions.  Firstly that limits on the $Z^\prime$ mass play an
+extensions--first, that limits on the $Z^\prime$ mass play an
 incredibly important role in constraining natural scenarios in such
-models and secondly that the tuning from the $Z^\prime$ limits in
+models and, second, that the tuning from the $Z^\prime$ limits in
 these models depends less on assumptions about SUSY breaking than the
@@
 substantially larger than $M_Z$.  Consequently the bound from LEP is not
-high enough to have an impact on the fine tuning obtained in the models and
+high enough to have an impact on the fine-tuning obtained in the models and
 parameter space regions that we have studied, as we have checked explicitly.
 Significantly larger lower bounds on the $\mu$ parameter, and therefore on the
-fine tuning, may arise from chargino limits coming from LHC searches.  However
+fine-tuning, may arise from chargino limits coming from LHC searches.  However,
 the chargino limits from the LHC depend on whether there are light sleptons or
@@
 neutralino.  Current limits placed by CMS and ATLAS extend up to
-$m_{\tilde{\chi}^\pm_1} \approx 700 - 740$ GeV if there are light
+$m_{\tilde{\chi}^\pm_1} \approx$ 700--740 GeV if there are light
 sleptons \cite{Khachatryan:2014qwa, Aad:2014nua} with much weaker
-bounds if there are no light sleptons or sneutrinos\footnote{Useful
+bounds if there are no light sleptons or sneutrinos.\footnote{Useful
 summary plots of these limit may be found on the public pages of
 ATLAS, \url{https://atlas.web.cern.ch/Atlas/GROUPS/PHYSICS/CombinedSummaryPlots/SUSY/ATLAS_SUSY_EWSummary/ATLAS_SUSY_EWSummary.png}
-and CMS \url{http://cms.web.cern.ch/sites/cms.web.cern.ch/files/styles/large/public/field/image/Image_03_exclusion_Combined.png?itok=8FMBpu_1}.}.
-
-Nonetheless for the MSSM the impact of potential chargino mass limits is
+and CMS \url{http://cms.web.cern.ch/sites/cms.web.cern.ch/files/styles/large/public/field/image/Image_03_exclusion_Combined.png?itok=8FMBpu_1}.}
+
+Nonetheless, for the MSSM the impact of potential chargino mass limits is
 shown in Fig.~\ref{Fig:chargino-plot}.  There we see that if the
-full parameter space with $m_{\tilde{\chi}^\pm_1} < 700$ GeV was excluded the
+full parameter space with $m_{\tilde{\chi}^\pm_1} < 700$ GeV was excluded, the
 impact would be to make the tuning in the MSSM with a $20$ TeV cutoff
@@
 \includegraphics{mssm_chargino_plot_bw_var.png}}%%
-\caption{Scatter plot of fine tuning vs lightest Higgs mass in the MSSM with
+\caption{Scatter plot of fine-tuning vs lightest Higgs mass in the MSSM with
 $200 \textrm{ GeV} \leq m_{\tilde{\chi}^\pm_1} \leq 400$ GeV shown in light
@@
 of the extra $U(1)$ gauge symmetry it is associated with.  In
-Fig.~\ref{Fig:othere6modelsvsmssm} we look at the fine tuning for
+Fig.~\ref{Fig:othere6modelsvsmssm} we look at the fine-tuning for
 other $U(1)$ extensions for the same $Z^\prime$ masses as we did for the
@@
 on the obtainable tuning in each model, the parameter values for points in
-these main grid scans with a low fine tuning were then used as the starting
+these main grid scans with a low fine-tuning were then used as the starting
 points for smaller scans about those values.  In these smaller scans the
-parameters were more finely varied to populate the low fine tuning regions.
+parameters were more finely varied to populate the low fine-tuning regions.
 
@@
 \includegraphics{e6eta_tb10_tuning_vs_higgs_bw_var.png}}%%
-\caption{\textit{Top left panel:} Scatter plot of the fine tuning vs lightest
-Higgs mass in the $U(1)_I$ model.  \textit{Top right panel:} Scatter plot of
-the fine tuning vs lightest Higgs mass in the $U(1)_\psi$ model.
-\textit{Bottom panel:} Scatter plot of the fine tuning vs lightest Higgs mass
+\caption{Top left panel: Scatter plot of the fine-tuning vs lightest
+Higgs mass in the $U(1)_I$ model.  Top right panel: Scatter plot of
+the fine-tuning vs lightest Higgs mass in the $U(1)_\psi$ model.
+Bottom panel: Scatter plot of the fine-tuning vs lightest Higgs mass
 in the $U(1)_\eta$ model.  In each plot points with $M_{Z^\prime} = 2.5$ TeV
@@
 
-As can be seen in Fig.~\ref{Fig:othere6modelsvsmssm} the severity of the
+As can be seen in Fig.~\ref{Fig:othere6modelsvsmssm}, the severity of the
 tunings varies quite a bit.  This is because the charges appear as
@@
 
-Interestingly the coefficient $d$ is very small (and negative) in the
-case of the $U(1)_I$.  This allows a dramatic reduction in the fine
-tuning from the $U(1)_I$ symmetry.  This is a result of the $H_u$
+Interestingly, the coefficient $d$ is very small (and negative) in the
+case of the $U(1)_I$.  This allows a dramatic reduction in the fine-tuning
+from the $U(1)_I$ symmetry.  This is a result of the $H_u$
 charge associated with $U(1)_I$ vanishing, which means that the
-$D$-terms to the lightest Higgs which is predominantly $H_u$ at large
+$D$ terms to the lightest Higgs which is predominantly $H_u$ at large
 $\tan\beta$ are suppressed, making it difficult to raise the Higgs
 mass in the same way as happens in the other models and explaining why
-heavier Higgs values in this model can't be obtained.  Therefore the
-fine tuning behaviour in this model is closer to that of the MSSM, and
+heavier Higgs values in this model can't be obtained.  Therefore, the
+fine-tuning behaviour in this model is closer to that of the MSSM, and
 in this case raising the $Z^\prime$ mass limit to $4.5$ TeV will have
-little impact on naturalness.  From naively estimating the tuning
+little impact on naturalness.  From naively estimating the tuning,
 using the $d$ coefficient one can estimate that $Z^\prime$ limits
@@
 Finally we want to emphasize that while in Fig.~\ref{Fig:e6ssmvsmssm}
-the E$_6$SSM looks more fine tuned than the MSSM this depends on the
+the E$_6$SSM looks more fine-tuned than the MSSM this depends on the
 high scale boundary, $M_X$, where the parameters are assumed to be set
@@
 the E$_6$SSM with lighter stops, then if the cutoff is large, the
-larger stop masses of the MSSM can make that model more fine tuned due
+larger stop masses of the MSSM can make that model more fine-tuned due
 to large RGE effects.
 
-To further illustrate this point we looked at how the tuning varies
+To further illustrate this point, we looked at how the tuning varies
 with $M_X$ for low tuning benchmarks in the MSSM and E$_6$SSM.  These
 benchmarks are defined in Table \ref{tab:benchmarks} and the results
-are shown in Fig.~\ref{Fig:BMs-varyMX}.  Since the behaviour is quite
+are shown in Fig.~\ref{Fig:BMs-varyMX}.  Since the behavior is quite
 complicated we now discuss these in detail as it provides some insight
@@
 $\tan\beta(M_Z)$ & $10$ & $10$ & $10$ & $10$ \\
-$s(M_{\mathrm{SUSY}})$ [GeV] & $-$ & $-$ & $6700$ & $6700$ \\
-$\kappa_{1,2,3}(M_{\mathrm{SUSY}})$ & $-$ & $-$ & $0.6$ & $0.52$ \\
-$\lambda_{1,2}(M_{\mathrm{SUSY}})$ & $-$ & $-$ & $0.2$ & $0.13$ \\
+$s(M_{\mathrm{SUSY}})$ [GeV] & $\cdots$ & $\cdots$ & $6700$ & $6700$ \\
+$\kappa_{1,2,3}(M_{\mathrm{SUSY}})$ & $\cdots$ & $\cdots$ & $0.6$ & $0.52$ \\
+$\lambda_{1,2}(M_{\mathrm{SUSY}})$ & $\cdots$ & $\cdots$ & $0.2$ & $0.13$ \\
 $\mu_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & $689.7$ & $1013.5$ &
@@
 $-9.35\times 10^5$ & $5.0\times 10^5$ & $-2.66\times 10^5$ \\
-$m_S^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $-$ & $-$ & $-3.10\times 10^6$ &
-$-3.17 \times 10^6$ \\
+$m_S^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $\cdots$ & $\cdots$ &
+$-3.10\times 10^6$ & $-3.17 \times 10^6$ \\
 $M_1(M_{\mathrm{SUSY}})$ [GeV] & $300$ & $260.8$ & $300$ & $173.4$ \\
@@
 $M_3(M_{\mathrm{SUSY}})$ [GeV] & $2000$ & $1312.3$ & $2000$ & $1200$ \\
-$M_1^\prime(M_{\mathrm{SUSY}})$ [GeV] & $-$ & $-$ & $300$ & $175.2$ \\
+$M_1^\prime(M_{\mathrm{SUSY}})$ [GeV] & $\cdots$ & $\cdots$ & $300$ & $175.2$ \\
 \hline
-$M_{Z^\prime}$ [GeV] & $-$ & $-$ & $2473.2$ & $2512.7$ \\
+$M_{Z^\prime}$ [GeV] & $\cdots$ & $\cdots$ & $2473.2$ & $2512.7$ \\
 $m_{h_1}$ [GeV] & $124.3$ & $124.4$ & $125.0$ & $126.2$ \\
@@
 \caption{Parameters for the MSSM and E$_6$SSM benchmark points.  In the
-E$_6$SSM we define $\mu_{\mathrm{eff}} \equiv \lambda s/\sqrt{2}$ and
+E$_6$SSM, we define $\mu_{\mathrm{eff}} \equiv \lambda s/\sqrt{2}$ and
 $B_{\mathrm{eff}} = A_\lambda$.  The soft masses $m_{H_d}^2$, $m_{H_u}^2$
-and $m_S^2$ are those that satisfy the EWSB conditions including 1-loop
+and $m_S^2$ are those that satisfy the EWSB conditions including one-loop
 Coleman-Weinberg corrections involving the top and stops.  For E$_6$SSM BM1
@@
 \includegraphics{e6ssm_light_zprime_BM2_all_tuning_data_bw_var.png}}%%
-\caption{\textit{Top panel:} Scatter plot of the fine tuning as a function
+\caption{Top panel: Scatter plot of the fine-tuning as a function
 of the cutoff scale $M_X$ for the four benchmark points given in
-Table \ref{tab:benchmarks}.  \textit{Middle left panel:}  Individual
+Table \ref{tab:benchmarks}.  Middle left panel:  Individual
 sensitivities for MSSM BM1 plotted against the high scale $M_X$ which give
 the overall tuning shown by the dotted line in the top panel.
-\textit{Middle right panel:} Individual sensitivities for E$_6$SSM BM1 plotted
+Middle right panel: Individual sensitivities for E$_6$SSM BM1 plotted
 against the high scale $M_X$ which give the overall tuning shown by the solid
-line in the top panel.  \textit{Bottom left panel:} Individual sensitivities
+line in the top panel.  Bottom left panel: Individual sensitivities
 for MSSM BM2 plotted against the high scale $M_X$ which give the overall
 tuning shown by the dash-dotted line in the top panel.
-\textit{Bottom right panel:} Individual sensitivities for E$_6$SSM BM2 plotted
+Bottom right panel: Individual sensitivities for E$_6$SSM BM2 plotted
 against the high scale $M_X$ which give the overall tuning shown by the dashed
@@
 sensitivity to $A_t$, but we did find that large mixing lead to less
-fine tuning overall for the points we examined.
+fine-tuning overall for the points we examined.
 
 Comparing the MSSM tunings to the E$_6$SSM tunings one can see that
-which point is more fine tuned depends on the scale at which the
+which point is more fine-tuned depends on the scale at which the
 parameters are defined.  This illustrates that any statement about
@@
 
-For E$_6$SSM BM1 the fine tuning is shown by the solid curve in the top
+For E$_6$SSM BM1 the fine-tuning is shown by the solid curve in the top
 panel of Fig.~\ref{Fig:BMs-varyMX} and the individual sensitivities
@@
 proportional to $M_Z^{\prime \, 2}$, which provide the dominant
-contribution to this sensitivity at very low $M_X$.  However as $M_X$
+contribution to this sensitivity at very low $M_X$.  However, as $M_X$
 is increased contributions from the soft masses become more important
@@
 also cause other sensitivities to grow, in particular $\Delta_{M_3}$.
-The fine tuning rises with $M_X$ once $M_X \gtrsim 10^5 - 10^6$ GeV, but
+The fine-tuning rises with $M_X$ once $M_X \gtrsim 10^5 - 10^6$ GeV, but
 remains lower than that of the other points, until $M_X \approx 10^8$
 GeV.  Eventually the $\Delta_{M_3}$ sensitivity leads to this point
-being the most fine tuned of the four shown in
+being the most fine-tuned of the four shown in
 Fig.~\ref{Fig:BMs-varyMX}.
@@
 at the same time larger $M_3$ at higher scales reduces the soft squark
-masses at $M_X$.  Therefore the stop mass contributions are
+masses at $M_X$.  Therefore, the stop mass contributions are
 ameliorated, compared to the MSSM, both by allowing lighter stops at
@@
 and a negative contribution from $m_{Q_3}^2(M_X)$ and
-$m_{u_3}^2(M_X)$, allowing heavy stop masses to cause fine
-tuning.  In this case $m_{H_u}^2(M_{SUSY})$ is held fixed so as the
+$m_{u_3}^2(M_X)$, allowing heavy stop masses to cause fine-tuning.  In this
+case $m_{H_u}^2(M_{SUSY})$ is held fixed so as the
 cutoff increases the values of these soft masses at $M_X$ will be
@@
 \cite{Aad:2014lra}.  At $20$ TeV this benchmark is not amongst the
-lowest tuned points, since at that scale the tree level tuning from
-$M_{Z^\prime}$ dominates.  However the reduction in $M_3$ means that
+lowest tuned points, since at that scale the tree-level tuning from
+$M_{Z^\prime}$ dominates.  However, the reduction in $M_3$ means that
 $\Delta_{M_3}$ is substantially lower and only becomes the dominant
@@
 contribution from these terms.  Together with the reduction in $M_3$ described
-above, this allows to maintain the observed low fine tuning at very large
+above, this allows to maintain the observed low fine-tuning at very large
 values of $M_X$.
@@
 bottom left panel) is designed to be similar to E$_6$SSM BM2, for a reasonable
-comparison.  However from the individual sensitivities one can see that the
-behaviour is quite similar to MSSM BM1, though in this case
+comparison.  However, from the individual sensitivities one can see that the
+behavior is quite similar to MSSM BM1, though in this case
 $\Delta_{m_{H_u}^2}$ becomes the largest tuning at a higher $M_X$ and does not
@@
 gravity interactions with the hidden sector.  Through the use of
-renormalization group running one can then see that at the EW scale
-the stops enter the EWSB condition for $M_Z$, therefore it was
+renormalization group running, one can then see that at the EW scale
+the stops enter the EWSB condition for $M_Z$; therefore, it was
 expected that these masses should not be much bigger than $100$ GeV.
-However to disturb this elegant picture first LEP placed constraints
+However, to disturb this elegant picture, first LEP placed constraints
 on the Higgs mass, requiring it to be above 114.4 GeV
 \cite{Barate:2003sz, Schael:2006cr}, which already introduced
-significant tuning for constrained models, since heavy stops are
-required to raise the lightest Higgs mass above it's tree level
-bound. Then recently this problem got much worse since the LHC measured the
+significant tuning for constrained models since heavy stops are
+required to raise the lightest Higgs mass above its tree-level
+bound. Then, recently, this problem got much worse since the LHC measured the
 Higgs mass to be around $125$ GeV.
 
-$U(1)$ extensions motivated by the $\mu$-problem, $E_6$ GUT theories
-and the connection to string theory contain both $F-$ and $D-$ term
-contributions to the light Higgs mass which can raise the tree level
+$U(1)$ extensions motivated by the $\mu$ problem, $E_6$ GUT theories
+and the connection to string theory contain both $F$- and $D$- term
+contributions to the light Higgs mass which can raise the tree-level
 mass, evading the need for large radiative corrections to increase it.
-However such models come with their own fine tuning problem, where the
+However, such models come with their own fine-tuning problem, where the
 $Z^\prime$ mass appears in the EWSB condition for $M_Z$ at tree level.
@@
 the most conservative limits one can place on naturalness in these
-models, the tuning in the E$_6$SSM is worse.  However if there are no
+models, the tuning in the E$_6$SSM is worse.  However, if there are no
 charginos below $700$ GeV then the situation in the two models would
@@
 sources of tension in the EWSB conditions that a small reduction in
-fine tuning can even occur for a moderate increase in $M_X$.  However
+fine-tuning can even occur for a moderate increase in $M_X$.  However,
 as $M_X$ increases towards the scale where the gauge couplings unify,
@@
 $\tan\beta = 10$.  We found that in every case except for the
-$U(1)_I$ the fine tuning was much worse for the larger $Z^\prime$
+$U(1)_I$ the fine-tuning was much worse for the larger $Z^\prime$
 mass, further emphasizing the importance of this in $U(1)$ extensions.
@@
 interesting in the sense that it provides a solution to the
-$\mu$-problem while avoiding the large tuning (with current limits)
-from the $Z^\prime$ mass.  However one should remember we are looking
+$\mu$ problem while avoiding the large tuning (with current limits)
+from the $Z^\prime$ mass.  However, one should remember we are looking
 at conservative limits on naturalness here and there is no solution to
@@
 also like to thank A.~Ismail and T.~Rizzo for their helpful comments
-regarding fine tuning in the MSSM.  PA would like to thank J.H.~Park,
+regarding fine-tuning in the MSSM.  PA would like to thank J.H.~Park,
 A.~Voigt and D.~St\"{o}ckinger for useful discussion regarding the use of
@@
 
-\section{\label{app:masterformula}Fine Tuning Master
-Formula}
-
-To write down the tree level master formula, it is convenient to define the
+\section{\label{app:masterformula}FINE-TUNING MASTER
+FORMULA}
+
+To write down the tree-level master formula, it is convenient to define the
 quantities
@@
 \ea
-For a running parameter $q$ appearing in the tree level EWSB conditions, the
+For a running parameter $q$ appearing in the tree-level EWSB conditions, the
 corresponding contribution to the individual sensitivity can then be written
@@
 
-\section{\label{app:rges}RGE Contributions}
+\section{\label{app:rges}RGE CONTRIBUTIONS}
 
@@
 We have constructed the necessary series solutions in both the MSSM
-and the $U(1)$ extended models.  Due to the smallness of the first and
-second generation Yukawa couplings, we neglect them in our
+and the $U(1)$ extended models.  Due to the smallness of the first- and
+second-generation Yukawa couplings, we neglect them in our
 calculations.  The corresponding soft SUSY breaking trilinears are
@@
 
-In the MSSM, the relevant parameters for the fine tuning calculation are
+In the MSSM, the relevant parameters for the fine-tuning calculation are
 $\mu$, $B$, $m_{H_u}^2$, $m_{H_d}^2$ at tree level.  For the
@@
 \end{equation}
-If in addition the one-loop contributions to the effective potential
+If, in addition, the one-loop contributions to the effective potential
 from top and stop loops are included, it is also necessary to
@@
 
-When this trace is non-zero it will also induce gauge kinetic mixing
+When this trace is nonzero it will also induce gauge kinetic mixing
 to be generated during RGE evolution and this is the case in the
-models we consider here\footnote{In $E_6$ inspired models with only
+models we consider here.\footnote{In $E_6$ inspired models with only
 complete $27$-plet matter multiplets this trace would vanish.
@@
 models are consistent with gauge coupling unification this trace
-doesn't vanish.}.  However when these models are evolved down from
-the GUT scale the radiatively generated gauge kinetic mixing gives an
+doesn't vanish.}  However, when these models are evolved down from
+the GUT scale, the radiatively generated gauge kinetic mixing gives an
 off-diagonal gauge coupling, $g_{11}$, of just $\approx 0.02$ at the
@@
 \end{subequations}
-In order to keep these expressions compact we have used the notation
+In order to keep these expressions compact, we have used the notation
 \begin{align*}
@@
 zero at all scales by removing all terms involving them from the
-RGEs.  Therefore some terms with this trace remain and the RGEs shown here
+RGEs.  Therefore, some terms with this trace remain and the RGEs shown here
 do not reduce to those which one would obtain from
 Ref.~\cite{Martin:1993zk} or Ref.~\cite{Athron:2009bs} unless
-$\Sigma_{Q}^Y = 0$.  Note however these contributions do not appear in the
+$\Sigma_{Q}^Y = 0$.  Note, however, these contributions do not appear in the
 corresponding trilinears due to the version of SARAH used.}
@@
 $\theta$ follow from the charge assignments given in Table \ref{tab:E6charges}
-and hold provided that $U(1)$ mixing is neglected.  Similarly we write
+and hold provided that $U(1)$ mixing is neglected.  Similarly, we write
 \begin{align*}
@@
 If the one-loop contributions to the effective potential from top and stop
-loops are also included it is necessary to consider the expansions for $y_t$,
+loops are also included, it is necessary to consider the expansions for $y_t$,
 $a_t$, $m_{Q_3}^2$ and $m_{u_3}^2$. The required expressions for $y_t$ read
